### 2014-01-07 paper.tex
initialize the latex

% THIS IS SIGPROC-SP.TEX - VERSION 3.1
% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
% APRIL 2009
%
% It is an example file showing how to use the 'acm_proc_article-sp.cls' V3.2SP
% LaTeX2e document class file for Conference Proceedings submissions.
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls V3.2SP) *DOES NOT* produce:
%       1) The Permission Statement
%       2) The Conference (location) Info information
%       3) The Copyright Line with ACM data
%       4) Page numbering
% ---------------------------------------------------------------------------------------------------------------
% It is an example which *does* use the .bib file (from which the .bbl file
% is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission,
% you need to 'insert'  your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%
% Questions regarding SIGS should be sent to
% Adrienne Griscti ---> griscti@acm.org
%
% Questions/suggestions regarding the guidelines, .tex and .cls files, etc. to
% Gerald Murray ---> murray@hq.acm.org
%
% For tracking purposes - this is V3.1SP - APRIL 2009

\documentclass{article}
\usepackage{multicol}
\onecolumn
\begin{document}
\title{A Case Study in Preserving a High Energy Physics Application}
\author{Haiyan Meng\\ Department of Computer Science and Engineering\\ University of Notre Dame}
\date{January 2014}
\maketitle

dfdk\cite{Laboratories79make}lications in the fields of biology, physics, and many others involve a large amount of data and computation, and the size is continuing to grow. Ways of handling the execution of such applications has become a hot topic both in industry and academia. One answer is the use of distributed computing, which integrates the computational resources of many computers into one system. Distributed computing has been widely adopted to implement execution engines for large scale applications, examples of these engines include Condor

\bibliographystyle{abbrv}
\bibliography{cclpapers,this}

\end{document}

### 2014-01-07 paper.tex
from google driver without any figure and table

@@
 
+\section{Introduction}
+
+\indent The longevity of high Energy physics (HEP) experiments makes it become important to preserve data and software in HEP.
+The Tevatron, the second most powerful proton-antiproton collider, serviced until 2011 since its completion in 1883.
+The CDF experiment, which belongs to the Tevatron, involved three levels triggers.
+The output rates of Level-1 and Level-2 are about 30kHz and 350Hz respectively.
+Even if the event rate (with an average event size of 150KB) of the Level-3 trigger is reduced to about 100Hz, the total size of data needed to be preserved is still very large---about 15MB/s.It is necessary to preserve all these event data to to ensure the smooth progress of the whole experiment.\\
+
+The development of theory and experimental analysis technology in the physics field makes it become possible to re-evaluate the dataset of current HEP experiments several decades later.
+The software and hardware environment of current HEP experiments is also needed to be preserved to repeat the whole experimental process from scratch.
+\\
+
+The complexity of HEP experiments makes the collaboration of physicists from different countries and projects, become necessary.
+For example, the CDF collaboration consists of about 600 researchers from about 60 institutions in 15 countries.
+One efficient data preservation and sharing mechanism is necessary for the progress of the whole project.
+One ATLAS physicist might want to access the preserved CMS data and perform an analysis on it.
+How to preserve CMS data so that it can be accessed and utilized by physicists from different projects efficiently and flexibly becomes urgent.\\
+
+Facing with the huge amounts of original data and different upper-layer data analysis software environments, one preservation mechanism, which decides the minimal and essential set of data and software need to be stored, what sorts of metadata is necessary to be preserved, how to organize metadata to guarantee fast indexing and retrieval of data and software, is needed.\\
+
+To have a clear understanding of the core components of such a preservation mechanism, case study research can verify and supplement our origin design thought.
+Through detailed analysis of one case, which aims to preserve the data and software involved in one HEP application, data sources, software sources and the main analysis workflow of one HEP application can be obtained.
+The difficult points of designing one preservation scheme will become explicit.
+One tentative preservation mechanism considering all these factors will be deployed and verified, and the verification process will in turn help us figure out the points need to be modified and optimized.\\
+
+The remaining parts of the paper is organized as follows. \\
+
+\section{Motivation}
+
+\indent Matthias, one guy from physics department, finished one interesting tau analysis. We want to understand how the tau analysis works and repeat it.
+
+\section{This workflow of the example}
+\indent declare environment variables\\
+
+create a CMS release\\
+
+set up CMSSW environment\\
+
+install the Boson Exploration Analysis Ntuple (BEAN) packages\\
+
+install grid control, obtain CMS data from grid and store the data into HDFS mounted as one local file system.\\
+
+install the TauAnalysis package\\
+
+perform the instruction steps on a ttH-TT Ntuple analyzing package.\\
+
+actual data analysis.\\
+
+\section{First solution to repeat the program}
+First, Matthias introduced the general workflow of his tau analysis through one long email including notes, linux shell commands, web links.\\
+
+The drawbacks of this solution: The experience of repeating one tau analysis through emails is chaotic.
+You need constant jumps around multiple web links.
+There are overlap between the content of the email and the content of web links, which needs the new user to merge them.
+Multiple communication through emails is necessary to ensure the successful repeat of the whole analysis.
+For example, the original email refers to one environment variable called CMSSW\_base without clear declaration, the new user needs to send one email to the original writer to obtain its accurate value.\\
+
+what’s more, step 3 of this tau analysis requires the new user owning the access authority for grid, however, granting  everyone who wants to repeat the analysis the access authority for grid (grid certificate) is too wasteful and unsafe.\\
+
+\section{second solution to repeat the program}
+to make the repeat of one analysis convenient and feasible, we integrate the content of all the notes, commands and web links involved in the emails into one neat, complete shell script, which begins with the definition of environment variables, then data obtainance from grid, software obtainance from cmssw, git and other web resources, and software installation, ends with the execution of the actual analysis program.\\
+
+as for the data obtainance from grid, we directly use the local copy in hdfs to avoid the new user to obtain the grid certification.\\
+
+during the integration process of all the data and software dependencies, we notice that the data and software sources are rich, including cmssw, hadoop, grid, git, http and one personal main page. \\
+wget -r http://nd.edu/~abrinke1/electroneffectivearea.h -o electroneffectivearea.h\\
+
+the source and size of data and software involved in the program is as follows:\\
+data source: mathias makes use of grid to copy the subset of t3 to hadoop file system, which is mounted as one local file system.\\
+data size: the size of mathias’s sub-directory under hdfs.\\
+the total size of data stored in hdfs is 33tb\\
+software source: git http cmssw\\
+software size: the size of data from different software sources.\\
+cmssw\_5\_3\_11\_patch3          1.16 tb\\
+git https://github.com/cms-tth (7 public repos)   only use 3 repos: 16mb + 39mb + 6mb\\
+http (wget command)\\
+(http://cmsdoc.cern.ch/cms/data/cmssw/recoegamma/electronidentification/data/*xml  12 xml files)  52mb\\
+http://pyyaml.org/download/pyyaml/pyyaml-3.10.tar.gz    236kb\\
+http://nd.edu/~abrinke1/electroneffectivearea.h      41kb\\
+the benefits of the solution: the script includes all the necessary procedures for the repeat of one analysis program.
+the readability and friendliness of the script is higher than that of the email format.\\
+
+the drawbacks of this solution: using the data copy stored in the machine where mathias executed the experiment requires the new user have the authority to access the machine, which complicates the management of the original machine, even is impossible if the original machine executes rigid user access control.\\
+
+\section{third solution to repeat the program}
+the difficulty of data access authority obtainance enforces us to find out one independent solution, in which the repeat of the original analysis can be done without any external dependency.
+that is, one independent and self-contained package containing all the data and software dependencies is necessary.\\
+
+parrot is a virtual filesystem access tool which attaching existing programs to a variety of remote i/o systems including http, ftp, gridftp, irods, hdfs, xrootd, grow and chirp.
+it traps all system calls of one program through ptrace debugging interface, and replaces them with remote i/o operations as desired.
+through executing one program under parrot, all the paths of files involved in this program can be recorded.\\
+
+with the help of parrot, one packaging utility which generates one independent package for one program to make the repeat of the program convenient can be deployed.
+the basis of the packaging utility is one successful execution sandbox (the data from grid has been preserved in hdfs and the software from cmssw, git and http has been on the local machine.).
+we re-execute the actual data analysis code (shown in “the script of the third solution”) under parrot and get the name list of all the files actually accessed during the execution process of the actual data analysis.
+then, according to the file name list, one package containing all the necessary data and software for one analysis program is generated.
+next time, when another scholar wants to repeat the program, he only needs to obtain the package and directly execute the actual analysis program inside the package.\\
+
+the shell script of the second solution is simplified into one new version, which only contains the necessary environment variables, access authority and the actual analysis command.\\
+
+the workflow of generating one package for one analysis program  is as follows: \\
+(1) execute one analysis program under parrot and obtain filename list (l1) of it\\
+parrot is one virtual file system that can support user access to multiple underlying file systems.
+parrot traps each system call involved in the process of data access, figures out the type of file system and redirects it into corresponding operations to the accessed file system.
+during this process, each accessed file is recorded into one file with the access type of it, such as open, stat, read and write.\\
+command:\\
+parrot\_run –l namelist /bin/tcsh parrot\_cms.sh (installcms.sh)\\
+namelist size: 5.7mb     128711 lines\\
+de-duplicated namelist size: 2.2mb   42385 lines\\
+
+(2) generate one package containing the files of l1 \\
+the packaging utility iterates each filename inside l1 and copies it into the target package.
+after completing the packaging process, the target package together with its information, and one mountlist, which redirects the access of data from different file systems into the target package, will be provided to users.\\
+the packaging process also runs within parrot environment to access data from different file systems.\\
+command:\\
+/bin/bash ~/package1-4.sh –l ~/namelist\\
+– the path of pacakge is: /tmp/package1-4\\
+– the total size of package is: 21g\\
+– the total number of files is: 1204\\
+– the total number of directory is: 473\\
+– the total number of symbolic link files is: 195\\
+– the mountlist path is: /tmp/mountlist\\
+
+need to complement: explain the dir structure of the package:  directory ; file content + metadata; only file metadata; different process solutions\\
+
+the structure of the generated package is as follows.
+each file inside l1 is copied into the package, the final file path becomes the path of the package, followed by the original file path.
+in this program, the path of the package is /tmp/package1-4, so the final path of one file with the original path path1 is /tmp/package1-4/path1.
+to ensure the successful reproductivity, the filesystem structure of the original execution environment should be preserved as completely as possible.
+however, attempting to copy the whole content of one directory or one file is space-consuming and time-consuming, because the original program may only access the metadata of one directory with the size of 200gb.
+our solution is to determine the copy degree of one directory or one common file according to the system call type for each file.\\
+
+the map relationship between the file access path inside the actual analysis program and the actual file location is kept inside the mountlist file. the structure of the mountlist is as follows:\\
+
+/ /tmp/package1-4
+/tmp/package1-4 /tmp/package1-4
+/dev /dev
+/misc /misc
+/net /net
+/proc /proc
+/sys /sys
+/var /var
+/selinux /selinux
+
+need to complement: re-execute process: re-execution process will redirect all the data access into the package except for data under proc sys dev selinux\\
+
+(3) rerun the analysis program using the package\\
+when another scholar wants to repeat one analysis program, the accessed data field is limited into the target package with the help of the mountlist generated in step 2. \\
+
+command:\\
+parrot\_run –m /tmp/mountlist /bin/tcsh parrot\_cms.sh\\
+
+benefits of this solution: the repeat of one analysis program becomes easier, which would be executed in one independent package containing all the data and software dependencies of one analysis program.
+\\
+
+rethink mathias’s example, under this solution, the repeat of it only needs the necessary environment variables, svn login,  the last command (scripts/roaster -atfpvy data/generic\_ttl.yam) and the package.
+if different scholars want to repeat one analysis program, what they need to do is to obtain the package and rerun the actual analysis program.
+under the second solution, each scholar needs to get the necessary data and software, and then prepare software environment, which is time-consuming.
+\\
+
+drawbacks of this solution: however, different experimenters may execute different analysis programs on the same dataset using the same or overlapping sets of software.
+generating one new package for each analysis program from scratch is time-consuming and space-consuming, which makes one data and software preservation mechanism, which can integrate the preservation requirements of different analysis programs, become necessary.
+\\
+
+\section{fourth solution to repeat the program}
+to integrate the data and software from multiple analysis programs into one package, the concrete information of data and software, such as size, version, source and the number of files, need to be recorded.
+we also need to design one more instructive shell script format, in which the data dependencies and software dependencies can be clearly expressed and recognized.
+the packaging process needs to be re-organized.
+packaging utility needs to maintain one list of current software and data subset already stored in the package.
+when one user wants to generate one package, it will fork the packaging utility, the packaging utility will scan the script, get the data dependency part and software dependency part, judge whether each dependency has been inside the package, and only add the new data and software into the package, and update the package information and package retrieval information.\\
+
+as for data and software, need to ensure its identity. the software version.\\
+
+benefits of this solution: time saving (there are some overlap parts between different analysis programs, especially different analysis programs of one physicist); storage space saving (overlap parts between different analysis programs).
+the fourth-version script is very instructive so that physicists can repeat one analysis program or create one new analysis program more easily and efficiently.
+this is more manageable (data software sharing)\\
+
+maybe one lightweight database like sqlite, can be used to manage the metadata of data and software. \\
+
+difficulties: for parrot, how to recognize the start and end points of one dataset or one software. because up till now, the process unit of parrot is one single file, rather one single package.\\
+
+questions: how to set the unit of parrot: file or package\\
+
+the 4th version of script (how to design the new script still needs consideration):\\
+
+\section{the relationship of different solutions}
+
+the fourth solution should be based on the third solution.
+during the packaging process, packaging utility first checks whether the file has been inside the target package, (if exists, whether it is the latest version).
+only if the file does not exist in the target package or the file in the target package is not the latest version, the packaging utility copies the file into the target package.\\
+
+potential risk: different analysis programs share some common file names, but with different file contents. we should analyze the possibility of conflict: data.\\
+
+in the fourth version, let user to mark whether they change the data and software.
+if changed, one new package is generated to avoid data overlap and pollution.
+otherwise, directly starts packaging process based on the current target package.
+\\
+
+\section{comparison of the 2nd solution and the 3rd solution}
+\subsection{the breakdown of execution time of the second solution: }
+according to the table, about half of the total execution time is consumed to prepare relevant data and software.
+
+\subsection{the data size of the second solution:}
+according to the data and software resources involved in this example, the size of each category is shown in this table.
+
+the size of hadoop need to reconsidered. how to correctly illustrate the data size of this example?\\
+
+\subsection{the breakdown of execution time of the third solution: }
+the breakdown of execution time of the third solution is illustrated in this table.
+the time used to obtain file namelist and generate p1 is greatly longer than the execution time within the new package.
+however, the time consumption of file namelist obtainance and package generation is one-time.
+that is, once the package is generated, many users can directly obtain the package and re-execute it separately.
+
+\subsection{ the data size of the third solution}
+The data categories is more complex than our imagination.
+Except the experimental data stored in Hadoop and the software stored in CMSSW\_5\_3\_11\_patch3, files from /usr /lib /bin and other paths are also necessary for the execution of the program.\\
+
+\subsection{ Data size comparison of 2nd and 3rd solution}
+The packaging utility checks the system call of each file within the namelist, and maintains the minimum dataset, which makes the size of the final package is as small as possible.
+The total size of Hadoop under the second solution is astonished, while the size of Hadoop under the package is decreased to 20GB.
+The same trend applies to the size of CMSSW\_5\_3\_11\_patch3.
+Because the packaging utility tries to construct one independent and self-contained package, necessary files  from /usr, /bin, /lib are also copied into the package and denoted as “Data necessary for Package” in the table.\\
+
+\subsection{Execution time comparison of 2nd and 3rd solution}
+The time consumption of the repeat of one program from different scholars kept the same under the second solution, including software and data preparation.
+However, under the third solution, the data and software preparation is one-time.
+All the following repeat of the same program only need to obtain one copy of the package and execute the actual experimental analysis directly.\\
+
+make use of shell packaging utility to regenerate the package to test our the packaging time and package size.\\
+
+Another reason for the packaging utility is that not all the data and software generated by Peter’s script is used during the the actual data analysis.
+The packaging utility can help us find out the optimal subset of data and software involved in one actual data analysis.
+\\
+
+this point is not the motivation. but one achievement comes together. out of imagination.\\
+
+\section{Related Work }
+
+\section{Conclusion}
+
+\section{Future Work}
+
 dfdk\cite{Laboratories79make}lications in the fields of biology, physics, and many others involve a large amount of data and computation, and the size is continuing to grow.
@@
 One answer is the use of distributed computing, which integrates the computational resources of many computers into one system.
-Distributed computing has been widely adopted to implement execution engines for large scale applications, examples of these engines include Condor
+Distributed computing has been widely adopted to implement execution engines for large scale applications, examples of these engines include Condor\\
 

### 2014-01-08 paper.tex
add table

@@
 \documentclass{article}
-\usepackage{multicol}
+\usepackage{indentfirst, multicol}
 \onecolumn
@@
 \section{First solution to repeat the program}
-First, Matthias introduced the general workflow of his tau analysis through one long email including notes, linux shell commands, web links.\\
+\indent First, Matthias introduced the general workflow of his tau analysis through one long email including notes, linux shell commands, web links.\\
 
@@
 
-what’s more, step 3 of this tau analysis requires the new user owning the access authority for grid, however, granting  everyone who wants to repeat the analysis the access authority for grid (grid certificate) is too wasteful and unsafe.\\
+what’s more, step 3 of this tau analysis requires the new user owning the access authority for grid, however, granting  everyone who wants to repeat the analysis the access authority for grid (grid certificate) is too wasteful and unsafe.
+\\
+
+*****lack: the email content\\
 
 \section{second solution to repeat the program}
-to make the repeat of one analysis convenient and feasible, we integrate the content of all the notes, commands and web links involved in the emails into one neat, complete shell script, which begins with the definition of environment variables, then data obtainance from grid, software obtainance from cmssw, git and other web resources, and software installation, ends with the execution of the actual analysis program.\\
+\indent To make the repeat of one analysis convenient and feasible, we integrate the content of all the notes, commands and web links involved in the emails into one neat, complete shell script, which begins with the definition of environment variables, then data obtainance from grid, software obtainance from cmssw, git and other web resources, and software installation, ends with the execution of the actual analysis program.\\
+
+*****lack: the script of 2nd solution \\
 
@@
 \section{third solution to repeat the program}
-the difficulty of data access authority obtainance enforces us to find out one independent solution, in which the repeat of the original analysis can be done without any external dependency.
+\indent the difficulty of data access authority obtainance enforces us to find out one independent solution, in which the repeat of the original analysis can be done without any external dependency.
 that is, one independent and self-contained package containing all the data and software dependencies is necessary.\\
 
-parrot is a virtual filesystem access tool which attaching existing programs to a variety of remote i/o systems including http, ftp, gridftp, irods, hdfs, xrootd, grow and chirp.
-it traps all system calls of one program through ptrace debugging interface, and replaces them with remote i/o operations as desired.
+parrot is a virtual filesystem access tool which attaching existing programs to a variety of remote I/O systems including http, ftp, gridftp, irods, hdfs, xrootd, grow and chirp.
+it traps all system calls of one program through ptrace debugging interface, and replaces them with remote I/O operations as desired.
 through executing one program under parrot, all the paths of files involved in this program can be recorded.\\
@@
 the shell script of the second solution is simplified into one new version, which only contains the necessary environment variables, access authority and the actual analysis command.\\
+
+*****lack:script of 3rd solution\\
 
@@
 
-need to complement: explain the dir structure of the package:  directory ; file content + metadata; only file metadata; different process solutions\\
+*****lack: explain the dir structure of the package:  directory ; file content + metadata; only file metadata; different process solutions\\
 
@@
 /var /var
-/selinux /selinux
+/selinux /selinux\\
 
-need to complement: re-execute process: re-execution process will redirect all the data access into the package except for data under proc sys dev selinux\\
+*****lack: re-execute process: re-execution process will redirect all the data access into the package except for data under proc sys dev selinux\\
 
@@
 \section{fourth solution to repeat the program}
-to integrate the data and software from multiple analysis programs into one package, the concrete information of data and software, such as size, version, source and the number of files, need to be recorded.
+\indent To integrate the data and software from multiple analysis programs into one package, the concrete information of data and software, such as size, version, source and the number of files, need to be recorded.
 we also need to design one more instructive shell script format, in which the data dependencies and software dependencies can be clearly expressed and recognized.
@@
 
-maybe one lightweight database like sqlite, can be used to manage the metadata of data and software. \\
+*****hmeng-doubt: maybe one lightweight database like sqlite, can be used to manage the metadata of data and software. \\
 
-difficulties: for parrot, how to recognize the start and end points of one dataset or one software. because up till now, the process unit of parrot is one single file, rather one single package.\\
+*****hmeng-doubt: difficulties: for parrot, how to recognize the start and end points of one dataset or one software.
+because up till now, the process unit of parrot is one single file, rather one single package.\\
 
-questions: how to set the unit of parrot: file or package\\
+*****hmeng-doubt: questions: how to set the unit of parrot: file or package\\
 
-the 4th version of script (how to design the new script still needs consideration):\\
+*****lack: the 4th version of script (how to design the new script still needs consideration):\\
 
 \section{the relationship of different solutions}
+\indent The relationship of these four solutions to repeat one program is shown in Table~\ref{table:relationship}.\\
+
+\begin{table}
+    \centering
+    \begin{tabular}{|l|r|r|r|}
+        \hline
+        Solution ID & Data Resources & Software Resources & Operation Manual \\ \hline
+        1st Solution & grid & CMSSW Git HTTP & email \\ \hline
+        2nd Solution & local (HDFS) & CMSSW Git HTTP & shell script \\ \hline
+        3rd Solution & independent package & independent package & shell script + packaging utility \\ \hline
+        4th Solution & independent package & independent package & shell script + packaging utility \\ \hline
+    \end{tabular}
+    \caption{The relationship of different solutions}
+    \label{table:relationship}
+\end{table}
 
@@
 
-potential risk: different analysis programs share some common file names, but with different file contents. we should analyze the possibility of conflict: data.\\
+*****hmeng-doubt: potential risk: different analysis programs share some common file names, but with different file contents. we should analyze the possibility of conflict: data.\\
 
-in the fourth version, let user to mark whether they change the data and software.
+*****hmeng-doubt: in the fourth version, let user to mark whether they change the data and software.
 if changed, one new package is generated to avoid data overlap and pollution.
@@
 \subsection{the breakdown of execution time of the second solution: }
-according to the table, about half of the total execution time is consumed to prepare relevant data and software.
+\indent according to the Table~\ref{table:time-2nd}, about half of the total execution time is consumed to prepare relevant data and software.\\
+
+\begin{table}
+    \centering
+    \begin{tabular}{|l|r|r|}
+    \hline
+    Sub-Task & Time & Percentage \\ \hline
+    Software preparation from CMSSW & 15min 30s & 25.27\% \\ \hline
+    Software preparation from Git & 9s & 0.24\% \\ \hline
+    Software preparation from Wget & 36s & 0.98\% \\ \hline
+    Environment Build - SCRAM & 13min 20s & 21.74\% \\ \hline
+    Environment Build - Python & 1s & 0.03\% \\ \hline
+    Data analysis & 31min 44s & 51.74\% \\ \hline
+    Total & 61min 20s & 100.00\% \\ \hline
+    \end{tabular}
+    \caption{The breakdown of execution time of the 2nd solution}
+    \label{table:time-2nd}
+\end{table}
 
 \subsection{the data size of the second solution:}
-according to the data and software resources involved in this example, the size of each category is shown in this table.
+\indent according to the data and software resources involved in this example, the size of each category is shown in Table~\ref{table:datasize-2nd}.\\
 
-the size of hadoop need to reconsidered. how to correctly illustrate the data size of this example?\\
+\begin{table}
+    \centering
+    \begin{tabular}{|l|r|}
+    \hline
+    Data Category & Data Size \\ \hline
+    Software from CMSSW & 449MB \\ \hline
+    Software from Git & 61MB \\ \hline
+    Software from Wget & 52MB \\ \hline
+    Hadoop & 33TB \\ \hline
+    Total & 33792.562GB \\ \hline
+    \end{tabular}
+    \caption{The data size of the 2nd solution}
+    \label{table:datasize-2nd}
+\end{table}
+
+*****hmeng-doult: the size of hadoop need to reconsidered. how to correctly illustrate the data size of this example?\\
 
 \subsection{the breakdown of execution time of the third solution: }
-the breakdown of execution time of the third solution is illustrated in this table.
+\indent the breakdown of execution time of the third solution is illustrated in Table~\ref{table:time-3rd}.
 the time used to obtain file namelist and generate p1 is greatly longer than the execution time within the new package.
 however, the time consumption of file namelist obtainance and package generation is one-time.
-that is, once the package is generated, many users can directly obtain the package and re-execute it separately.
+that is, once the package is generated, many users can directly obtain the package and re-execute it separately.\\
+
+\begin{table}
+    \centering
+    \begin{tabular}{|l|r|}
+    \hline
+    Sub-Task & Time \\ \hline
+    Obtain file namelist & 37min 51s \\ \hline
+    Generate P1 & 13min 37s \\ \hline
+    Re-run the program within P1 & 13min 5s \\ \hline
+    \end{tabular}
+    \caption{The time breakdown of the 3rd solution}
+    \label{table:time-3rd}
+\end{table}
 
 \subsection{ the data size of the third solution}
+\indent The data size of the 3rd solution is shown in Table~\ref{table:datasize-3rd}.
 The data categories is more complex than our imagination.
@@
 
+\begin{table}
+    \centering
+    \begin{tabular}{|l|r|}
+    \hline
+    Data Category & Data size \\ \hline
+    Hadoop & 20GB \\ \hline
+    CMSSW\_5\_3\_11\_patch3 & 5.2MB \\ \hline
+    pscratch & 119MB \\ \hline
+    usr & 60MB \\ \hline
+    Others (/sbin + /tmp / + /lib + /lib64 + /var + /opt + /bin + /etc) & 28.4MB \\ \hline
+    Total & 20.213GB \\ \hline
+    \end{tabular}
+    \caption{The data size of the 3rd solution}
+    \label{table:datasize-3rd}
+\end{table}
+
 \subsection{ Data size comparison of 2nd and 3rd solution}
-The packaging utility checks the system call of each file within the namelist, and maintains the minimum dataset, which makes the size of the final package is as small as possible.
+\indent The packaging utility checks the system call of each file within the namelist, and maintains the minimum dataset, which makes the size of the final package is as small as possible.
 The total size of Hadoop under the second solution is astonished, while the size of Hadoop under the package is decreased to 20GB.
 The same trend applies to the size of CMSSW\_5\_3\_11\_patch3.
-Because the packaging utility tries to construct one independent and self-contained package, necessary files  from /usr, /bin, /lib are also copied into the package and denoted as “Data necessary for Package” in the table.\\
+Because the packaging utility tries to construct one independent and self-contained package, necessary files  from /usr, /bin, /lib are also copied into the package and denoted as “Data necessary for Package” in the Table~\ref{table:datasize-2nd3rd}.\\
+
+\begin{table}
+    \centering
+    \begin{tabular}{|l|r|r|}
+    \hline
+     Data Category & Data size of 2nd solution & Data size of 3rd solution \\ \hline
+     Hadoop & 33TB = 33792GB & 20GB \\ \hline
+     CMSSW\_5\_3\_11\_patch3 & 562MB & 5.2MB \\ \hline
+     Data necessary for Package & 207.4MB & N/A \\ \hline
+     Total & 33792.562GB & 20.213GB \\ \hline
+    \end{tabular}
+    \caption{Data size comparison beweeen second solution and third solution}
+    \label{table:datasize-2nd3rd}
+\end{table}
 
 \subsection{Execution time comparison of 2nd and 3rd solution}
+\indent Table~\ref{table:time-2nd3rd} shows the execution time comparison between the 2nd solution and the 3rd solution.
 The time consumption of the repeat of one program from different scholars kept the same under the second solution, including software and data preparation.
@@
 
-make use of shell packaging utility to regenerate the package to test our the packaging time and package size.\\
+\begin{table}
+    \centering
+    \begin{tabular}{|l|r|r|}
+    \hline
+    Task Category & execution time of 2nd solution & execution time of 3rd solution \\ \hline
+    Software Acquisition & 16min 15s & N/A \\ \hline
+    Environment Building & 13min 21s  & 4s \\ \hline
+    Obtain file namelist & N/A & 37min 51s \\ \hline
+    Generate the package & N/A & 13min 37s \\ \hline
+    Actual Experimental Analysis & 31min 44s & 13min 1s \\ \hline
+    Total & 61min 20s & N/A \\ \hline
+    \end{tabular}
+    \caption{Execution time comparison between second and third solution}
+    \label{table:time-2nd3rd}
+\end{table}
 
-Another reason for the packaging utility is that not all the data and software generated by Peter’s script is used during the the actual data analysis.
+*****hmeng-doubt:Another reason for the packaging utility is that not all the data and software generated by Peter’s script is used during the the actual data analysis.
 The packaging utility can help us find out the optimal subset of data and software involved in one actual data analysis.
 \\
-
 this point is not the motivation. but one achievement comes together. out of imagination.\\

### 2014-01-08 paper.tex
adjust the format:margin indent

@@
 \documentclass{article}
+\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}
 \usepackage{indentfirst, multicol}
@@
 
-The remaining parts of the paper is organized as follows. \\
+The remaining parts of the paper is organized as follows.
 
@@
 
-actual data analysis.\\
+actual data analysis.
 
@@
 
-what’s more, step 3 of this tau analysis requires the new user owning the access authority for grid, however, granting  everyone who wants to repeat the analysis the access authority for grid (grid certificate) is too wasteful and unsafe.
+What’s more, step 3 of this tau analysis requires the new user owning the access authority for grid, however, granting  everyone who wants to repeat the analysis the access authority for grid (grid certificate) is too wasteful and unsafe.
 \\
 
-*****lack: the email content\\
+*****lack: the email content
 
@@
 during the integration process of all the data and software dependencies, we notice that the data and software sources are rich, including cmssw, hadoop, grid, git, http and one personal main page. \\
-wget -r http://nd.edu/~abrinke1/electroneffectivearea.h -o electroneffectivearea.h\\
+\indent wget -r http://nd.edu/~abrinke1/electroneffectivearea.h -o electroneffectivearea.h\\
 
 the source and size of data and software involved in the program is as follows:\\
-data source: mathias makes use of grid to copy the subset of t3 to hadoop file system, which is mounted as one local file system.\\
-data size: the size of mathias’s sub-directory under hdfs.\\
-the total size of data stored in hdfs is 33tb\\
-software source: git http cmssw\\
-software size: the size of data from different software sources.\\
-cmssw\_5\_3\_11\_patch3          1.16 tb\\
-git https://github.com/cms-tth (7 public repos)   only use 3 repos: 16mb + 39mb + 6mb\\
-http (wget command)\\
-(http://cmsdoc.cern.ch/cms/data/cmssw/recoegamma/electronidentification/data/*xml  12 xml files)  52mb\\
-http://pyyaml.org/download/pyyaml/pyyaml-3.10.tar.gz    236kb\\
-http://nd.edu/~abrinke1/electroneffectivearea.h      41kb\\
+\indent data source: mathias makes use of grid to copy the subset of t3 to hadoop file system, which is mounted as one local file system.\\
+\indent data size: the size of mathias’s sub-directory under hdfs.\\
+\indent \indent the total size of data stored in hdfs is 33tb\\
+\indent software source: git http cmssw\\
+\indent software size: the size of data from different software sources.\\
+\indent \indent cmssw\_5\_3\_11\_patch3          1.16 tb\\
+\indent \indent git https://github.com/cms-tth (7 public repos)   only use 3 repos: 16mb + 39mb + 6mb\\
+\indent \indent http (wget command)\\
+\indent \indent (http://cmsdoc.cern.ch/cms/data/cmssw/recoegamma/electronidentification/data/*xml  12 xml files)  52mb\\
+\indent \indent http://pyyaml.org/download/pyyaml/pyyaml-3.10.tar.gz    236kb\\
+\indent \indent http://nd.edu/~abrinke1/electroneffectivearea.h      41kb\\
+
 the benefits of the solution: the script includes all the necessary procedures for the repeat of one analysis program.
@@
 
-the drawbacks of this solution: using the data copy stored in the machine where mathias executed the experiment requires the new user have the authority to access the machine, which complicates the management of the original machine, even is impossible if the original machine executes rigid user access control.\\
+the drawbacks of this solution: using the data copy stored in the machine where mathias executed the experiment requires the new user have the authority to access the machine, which complicates the management of the original machine, even is impossible if the original machine executes rigid user access control.
 
 \section{third solution to repeat the program}
-\indent the difficulty of data access authority obtainance enforces us to find out one independent solution, in which the repeat of the original analysis can be done without any external dependency.
+\indent The difficulty of data access authority obtainance enforces us to find out one independent solution, in which the repeat of the original analysis can be done without any external dependency.
 that is, one independent and self-contained package containing all the data and software dependencies is necessary.\\
 
-parrot is a virtual filesystem access tool which attaching existing programs to a variety of remote I/O systems including http, ftp, gridftp, irods, hdfs, xrootd, grow and chirp.
+Parrot is a virtual filesystem access tool which attaching existing programs to a variety of remote I/O systems including http, ftp, gridftp, irods, hdfs, xrootd, grow and chirp.
 it traps all system calls of one program through ptrace debugging interface, and replaces them with remote I/O operations as desired.
@@
 
-with the help of parrot, one packaging utility which generates one independent package for one program to make the repeat of the program convenient can be deployed.
+With the help of parrot, one packaging utility which generates one independent package for one program to make the repeat of the program convenient can be deployed.
 the basis of the packaging utility is one successful execution sandbox (the data from grid has been preserved in hdfs and the software from cmssw, git and http has been on the local machine.).
@@
 
-the shell script of the second solution is simplified into one new version, which only contains the necessary environment variables, access authority and the actual analysis command.\\
+The shell script of the second solution is simplified into one new version, which only contains the necessary environment variables, access authority and the actual analysis command.\\
 
@@
 the workflow of generating one package for one analysis program  is as follows: \\
-(1) execute one analysis program under parrot and obtain filename list (l1) of it\\
-parrot is one virtual file system that can support user access to multiple underlying file systems.
+\indent (1) execute one analysis program under parrot and obtain filename list (L1) of it\\
+\indent Parrot is one virtual file system that can support user access to multiple underlying file systems.
 parrot traps each system call involved in the process of data access, figures out the type of file system and redirects it into corresponding operations to the accessed file system.
 during this process, each accessed file is recorded into one file with the access type of it, such as open, stat, read and write.\\
-command:\\
-parrot\_run –l namelist /bin/tcsh parrot\_cms.sh (installcms.sh)\\
-namelist size: 5.7mb     128711 lines\\
-de-duplicated namelist size: 2.2mb   42385 lines\\
+\indent command:\\
+\indent parrot\_run –l namelist /bin/tcsh parrot\_cms.sh (installcms.sh)\\
+\indent namelist size: 5.7mb     128711 lines\\
+\indent de-duplicated namelist size: 2.2mb   42385 lines\\
 
-(2) generate one package containing the files of l1 \\
-the packaging utility iterates each filename inside l1 and copies it into the target package.
+(2) generate one package containing the files of L1 \\
+\indent The packaging utility iterates each filename inside L1 and copies it into the target package.
 after completing the packaging process, the target package together with its information, and one mountlist, which redirects the access of data from different file systems into the target package, will be provided to users.\\
-the packaging process also runs within parrot environment to access data from different file systems.\\
-command:\\
-/bin/bash ~/package1-4.sh –l ~/namelist\\
-– the path of pacakge is: /tmp/package1-4\\
-– the total size of package is: 21g\\
-– the total number of files is: 1204\\
-– the total number of directory is: 473\\
-– the total number of symbolic link files is: 195\\
-– the mountlist path is: /tmp/mountlist\\
+
+The packaging process also runs within parrot environment to access data from different file systems.\\
+\indent command:\\
+\indent /bin/bash ~/package1-4.sh –l ~/namelist\\
+\indent the path of pacakge is: /tmp/package1-4\\
+\indent the total size of package is: 21g\\
+\indent the total number of files is: 1204\\
+\indent the total number of directory is: 473\\
+\indent the total number of symbolic link files is: 195\\
+\indent the mountlist path is: /tmp/mountlist\\
 
@@
 each file inside l1 is copied into the package, the final file path becomes the path of the package, followed by the original file path.
-in this program, the path of the package is /tmp/package1-4, so the final path of one file with the original path path1 is /tmp/package1-4/path1.
-to ensure the successful reproductivity, the filesystem structure of the original execution environment should be preserved as completely as possible.
+in this program, the path of the package is /tmp/package1-4, so the final path of one file with the original path path1 is /tmp/package1-4/path1.\\
+
+To ensure the successful reproductivity, the filesystem structure of the original execution environment should be preserved as completely as possible.
 however, attempting to copy the whole content of one directory or one file is space-consuming and time-consuming, because the original program may only access the metadata of one directory with the size of 200gb.
@@
 
-the map relationship between the file access path inside the actual analysis program and the actual file location is kept inside the mountlist file. the structure of the mountlist is as follows:\\
-
-/ /tmp/package1-4
-/tmp/package1-4 /tmp/package1-4
-/dev /dev
-/misc /misc
-/net /net
-/proc /proc
-/sys /sys
-/var /var
-/selinux /selinux\\
+The map relationship between the file access path inside the actual analysis program and the actual file location is kept inside the mountlist file. the structure of the mountlist is as follows:\\
+\indent / /tmp/package1-4 \\
+\indent /tmp/package1-4 /tmp/package1-4 \\
+\indent /dev /dev \\
+\indent /misc /misc \\
+\indent /net /net \\
+\indent /proc /proc \\
+\indent /sys /sys \\
+\indent /var /var \\
+\indent /selinux /selinux\\
 
@@
 (3) rerun the analysis program using the package\\
-when another scholar wants to repeat one analysis program, the accessed data field is limited into the target package with the help of the mountlist generated in step 2. \\
+\indent When another scholar wants to repeat one analysis program, the accessed data field is limited into the target package with the help of the mountlist generated in step 2. \\
 
 command:\\
-parrot\_run –m /tmp/mountlist /bin/tcsh parrot\_cms.sh\\
+\indent parrot\_run –m /tmp/mountlist /bin/tcsh parrot\_cms.sh\\
 
@@
 generating one new package for each analysis program from scratch is time-consuming and space-consuming, which makes one data and software preservation mechanism, which can integrate the preservation requirements of different analysis programs, become necessary.
-\\
 
@@
 
-*****lack: the 4th version of script (how to design the new script still needs consideration):\\
+*****lack: the 4th version of script (how to design the new script still needs consideration)
 
@@
 
-the fourth solution should be based on the third solution.
+The fourth solution should be based on the third solution.
 during the packaging process, packaging utility first checks whether the file has been inside the target package, (if exists, whether it is the latest version).
@@
 otherwise, directly starts packaging process based on the current target package.
-\\
 
@@
 \subsection{the breakdown of execution time of the second solution: }
-\indent according to the Table~\ref{table:time-2nd}, about half of the total execution time is consumed to prepare relevant data and software.\\
+\indent according to the Table~\ref{table:time-2nd}, about half of the total execution time is consumed to prepare relevant data and software.
 
@@
 \subsection{the data size of the second solution:}
-\indent according to the data and software resources involved in this example, the size of each category is shown in Table~\ref{table:datasize-2nd}.\\
+\indent according to the data and software resources involved in this example, the size of each category is shown in Table~\ref{table:datasize-2nd}.
 
@@
 
-*****hmeng-doult: the size of hadoop need to reconsidered. how to correctly illustrate the data size of this example?\\
+*****hmeng-doult: the size of hadoop need to reconsidered. how to correctly illustrate the data size of this example?
 
 \subsection{the breakdown of execution time of the third solution: }
-\indent the breakdown of execution time of the third solution is illustrated in Table~\ref{table:time-3rd}.
+\indent The breakdown of execution time of the third solution is illustrated in Table~\ref{table:time-3rd}.
 the time used to obtain file namelist and generate p1 is greatly longer than the execution time within the new package.
 however, the time consumption of file namelist obtainance and package generation is one-time.
-that is, once the package is generated, many users can directly obtain the package and re-execute it separately.\\
+that is, once the package is generated, many users can directly obtain the package and re-execute it separately.
 
@@
 The data categories is more complex than our imagination.
-Except the experimental data stored in Hadoop and the software stored in CMSSW\_5\_3\_11\_patch3, files from /usr /lib /bin and other paths are also necessary for the execution of the program.\\
+Except the experimental data stored in Hadoop and the software stored in CMSSW\_5\_3\_11\_patch3, files from /usr /lib /bin and other paths are also necessary for the execution of the program.
 
@@
 The same trend applies to the size of CMSSW\_5\_3\_11\_patch3.
-Because the packaging utility tries to construct one independent and self-contained package, necessary files  from /usr, /bin, /lib are also copied into the package and denoted as “Data necessary for Package” in the Table~\ref{table:datasize-2nd3rd}.\\
+Because the packaging utility tries to construct one independent and self-contained package, necessary files  from /usr, /bin, /lib are also copied into the package and denoted as “Data necessary for Package” in the Table~\ref{table:datasize-2nd3rd}.
 
@@
 However, under the third solution, the data and software preparation is one-time.
-All the following repeat of the same program only need to obtain one copy of the package and execute the actual experimental analysis directly.\\
+All the following repeat of the same program only need to obtain one copy of the package and execute the actual experimental analysis directly.
 
@@
 \\
-this point is not the motivation. but one achievement comes together. out of imagination.\\
+\indent *****hmeng-doubt: this point is not the motivation. but one achievement comes together. out of imagination.\\
 
@@
 \section{Future Work}
-
-dfdk\cite{Laboratories79make}lications in the fields of biology, physics, and many others involve a large amount of data and computation, and the size is continuing to grow.
-Ways of handling the execution of such applications has become a hot topic both in industry and academia.
-One answer is the use of distributed computing, which integrates the computational resources of many computers into one system.
-Distributed computing has been widely adopted to implement execution engines for large scale applications, examples of these engines include Condor\\
+\indent this is an example of citing \cite{Laboratories79make}. \\
 

### 2014-01-14 paper.tex
add motivation (challenger + answer)

@@
 
-\section{This workflow of the example}
+\section{Introduction of the exmaple}
+\subsection{This workflow of the example}
 \indent declare environment variables\\
 
-create a CMS release\\
+Obtain software from CMSSW\\
 
-set up CMSSW environment\\
+Obtain software from Git\\
 
-install the Boson Exploration Analysis Ntuple (BEAN) packages\\
+Obtain software from some public HTTP web links\\
+
+Obtain software from one private home page\\
+
+Build software enviroment using SCRAM and Python\\
 
@@
 
-install the TauAnalysis package\\
-
-perform the instruction steps on a ttH-TT Ntuple analyzing package.\\
-
 actual data analysis.
 
+\subsection{the source and size of experiment data and software}
+We notice that the software sources are rich, including cmssw, hadoop, grid, git, http and one personal main page. The size of experiment data and software is large.\\
+
+*****hmeng: wget -r http://nd.edu/~abrinke1/electroneffectivearea.h -o electroneffectivearea.h\\
+
+As for the experiment data, Matthias copies the subset of T3 data from grid and stores the data into HDFS mounted as one local file system. The total size of data stored in HDFS is 33TB.\\
+
+The source and size of software are shown in Table~\ref{table:software-source-size}.\\
+
+\begin{table}
+    \centering
+    \begin{tabular}{|l|r|}
+        \hline
+        Source of Software & Size of Software \\ \hline
+        cmssw\_5\_3\_11\_patch3 & 1.16TB \\ \hline
+        Git & 51MB \\ \hline
+        Public HTTP & 52MB \\ \hline
+        Private home page & 41KB \\ \hline
+    \end{tabular}
+    \caption{Source and size of software}
+    \label{table:software-source-size}
+\end{table}
+
+\begin{table}
+    \centering
+    \begin{tabular}{|l|l|}
+        \hline
+        First version & Second version \\ \hline
+        1. Create a CMS release, e.g. cmsrel CMSSW\_5\_3\_11\_patch3 \\
+        2. Install the BEAN packages follow the instructions on github:\\
+            https://github.com/cms-ttH/BEAN/blob/master/README.md\\
+        3. Install git-control: svn co https://ekptrack ... grid-control\\
+        4. INstall the TauAnalysis package: \\
+            git clone https://github.com/matz-e/.../TauAnalysis\\
+            scram b -j32 \\
+        5. Perform actual analysis & second88 \\ \hline
+        Third version & Fourth version \\ \hline
+    \end{tabular}
+    \caption{Scripts of each Solution}
+    \label{table:scripts}
+\end{table}
 \section{First solution to repeat the program}
-\indent First, Matthias introduced the general workflow of his tau analysis through one long email including notes, linux shell commands, web links.\\
+\indent In order to repeat Matthais's example, the new user consulted the original author by email about the necessary work for the experiment.
+In response, Matthias introduced the general workflow of his tau analysis through one long email including notes, linux shell commands, web links.
+The First version of Table~\ref{table:scripts} illstrates Matthias's example.\\
 
-The drawbacks of this solution: The experience of repeating one tau analysis through emails is chaotic.
+However, this solution to repeat one experiment has three potential drawbacks.
+Firstly, the experience of repeating one tau analysis through emails is chaotic.
 You need constant jumps around multiple web links.
@@
 Multiple communication through emails is necessary to ensure the successful repeat of the whole analysis.
-For example, the original email refers to one environment variable called CMSSW\_base without clear declaration, the new user needs to send one email to the original writer to obtain its accurate value.\\
-
-What’s more, step 3 of this tau analysis requires the new user owning the access authority for grid, however, granting  everyone who wants to repeat the analysis the access authority for grid (grid certificate) is too wasteful and unsafe.
+For example, the original email refers to one environment variable called CMSSW\_base without clear declaration, the new user needs to send one email to the original writer to obtain its accurate value.
+Secondly, the necessary procedure to repeat the experiment, including softwares from different sources, is complex for the new user.
+In Matthias's example, the sources of software includes CMSSW, GIT, HTTP.
+The access of CMSSW requires the new user be an authorized user of CMSSW.
+What’s more, some parts of the workflow is unrepeatible.
+The third step of this experiment requires the new user owning the access authority for grid.
 \\
 
-*****lack: the email content
+Implication:  Directly repeating the experiment using the published workflow and results by the original author is complex and even difficulty.
+Some extra work must be done to make the repeating process easier.
 
 \section{second solution to repeat the program}
-\indent To make the repeat of one analysis convenient and feasible, we integrate the content of all the notes, commands and web links involved in the emails into one neat, complete shell script, which begins with the definition of environment variables, then data obtainance from grid, software obtainance from cmssw, git and other web resources, and software installation, ends with the execution of the actual analysis program.\\
+\indent One possible solution for the access authority problem of grid data is to grant the new user the authority to access gird data directly.
+Another possible solution is let the new user directly operate on the machine the original author used.
+As for the complexity of jumping between multiple web links, people may suggest that letting the original author generate one clear script including all the contents from different web links.\\
 
-*****lack: the script of 2nd solution \\
+To test out these possible solutions, we integrate the content of all the notes, commands and web links involved in the emails into one neat, complete shell script, which begins with the definition of environment variables, then data obtainance from grid, software obtainance from cmssw, git and other web resources, and software installation, ends with the execution of the actual analysis program.
+The Second version of Table~\ref{table:scripts} illstrates the merged script.
+As for the data obtainance from grid, we directly use the local copy in hdfs to avoid the new user to obtain the grid certification.\\
 
-as for the data obtainance from grid, we directly use the local copy in hdfs to avoid the new user to obtain the grid certification.\\
+*****hmeng: add the time and data analysis of the second solution.\\
 
-during the integration process of all the data and software dependencies, we notice that the data and software sources are rich, including cmssw, hadoop, grid, git, http and one personal main page. \\
-\indent wget -r http://nd.edu/~abrinke1/electroneffectivearea.h -o electroneffectivearea.h\\
+Because the script includes all the necessary procedures for the repeat of one analysis program, the readability and friendliness of this solution is higher than that of the email format.
+However, each execution of the script will involve the obtainance of software from different sources and the building of software environment.
+As for the access problem of grid data, using the data copy stored in the machine where mathias executed the experiment requires the new user have the authority to access the machine, which complicates the management of the original machine, even is impossible if the original machine executes rigid user access control.
+Granting everyone who wants to repeat the analysis the access authority for grid (grid certificate) is wasteful and unsafe.
+\\
 
-the source and size of data and software involved in the program is as follows:\\
-\indent data source: mathias makes use of grid to copy the subset of t3 to hadoop file system, which is mounted as one local file system.\\
-\indent data size: the size of mathias’s sub-directory under hdfs.\\
-\indent \indent the total size of data stored in hdfs is 33tb\\
-\indent software source: git http cmssw\\
-\indent software size: the size of data from different software sources.\\
-\indent \indent cmssw\_5\_3\_11\_patch3          1.16 tb\\
-\indent \indent git https://github.com/cms-tth (7 public repos)   only use 3 repos: 16mb + 39mb + 6mb\\
-\indent \indent http (wget command)\\
-\indent \indent (http://cmsdoc.cern.ch/cms/data/cmssw/recoegamma/electronidentification/data/*xml  12 xml files)  52mb\\
-\indent \indent http://pyyaml.org/download/pyyaml/pyyaml-3.10.tar.gz    236kb\\
-\indent \indent http://nd.edu/~abrinke1/electroneffectivearea.h      41kb\\
-
-the benefits of the solution: the script includes all the necessary procedures for the repeat of one analysis program.
-the readability and friendliness of the script is higher than that of the email format.\\
-
-the drawbacks of this solution: using the data copy stored in the machine where mathias executed the experiment requires the new user have the authority to access the machine, which complicates the management of the original machine, even is impossible if the original machine executes rigid user access control.
+Implication: All the data and software involved in the experiment should be provide to the new user in the format of one static package so that the multiple execution of the experiment from the same user only involve one time of data obtainance and software obtainance and compiling.
+In addition, the requirement of the underlying OS and hardware should also be provided to the new users.
 
@@
 \indent The difficulty of data access authority obtainance enforces us to find out one independent solution, in which the repeat of the original analysis can be done without any external dependency.
-that is, one independent and self-contained package containing all the data and software dependencies is necessary.\\
+that is, one independent and self-contained package containing all the data and software dependencies is necessary.
+Someone may suggest that it should be the responsibility of the original author to generate the required package.
+However, letting the original author to provide the package which can be used by other scholars to repeat the original experiment is unrealistic.
+One reason for this is that figuring out the underlying dependency of each software is complex and time-consumpting and even impossible for the original author.
+In this experiment, the machine used for the experiment is one public machine of physics department, and Matthias is one common user without root authority.
+All the underlying OS and supporting softwares are installed and maintained by the IT department of the university.
+On the other hand, the architecture design of the required package including all the data and software dependencies is not under the research range of physists.\\
 
@@
 
-The shell script of the second solution is simplified into one new version, which only contains the necessary environment variables, access authority and the actual analysis command.\\
-
-*****lack:script of 3rd solution\\
+The shell script of the second solution is simplified into one new version, which only contains the necessary environment variables, access authority and the actual analysis command.
+The Third version of Table~\ref{table:scripts} illustrates the simplified script.\\
 
@@
 
-*****lack: explain the dir structure of the package:  directory ; file content + metadata; only file metadata; different process solutions\\
+*****lack: file content + metadata; only file metadata; different process solutions\\
 
@@
 \indent parrot\_run –m /tmp/mountlist /bin/tcsh parrot\_cms.sh\\
+
+*****hmeng: add the evaluation of this solution\\
 

### 2014-01-14 paper.tex
the first acm version

@@
 
-\documentclass{article}
-\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}
-\usepackage{indentfirst, multicol}
-\onecolumn
+\documentclass{acm_proc_article-sp}
+\usepackage{url}
 \begin{document}
+
 \title{A Case Study in Preserving a High Energy Physics Application}
-\author{Haiyan Meng\\ Department of Computer Science and Engineering\\ University of Notre Dame}
-\date{January 2014}
+%
+% You need the command \numberofauthors to handle the 'placement
+% and alignment' of the authors beneath the title.
+%
+% For aesthetic reasons, we recommend 'three authors at a time'
+% i.e. three 'name/affiliation blocks' be placed beneath the title.
+%
+% NOTE: You are NOT restricted in how many 'rows' of
+% "name/affiliations" may appear. We just ask that you restrict
+% the number of 'columns' to three.
+%
+% Because of the available 'opening page real-estate'
+% we ask you to refrain from putting more than six authors
+% (two rows with three columns) beneath the article title.
+% More than six makes the first-page appear very cluttered indeed.
+%
+% Use the \alignauthor commands to handle the names
+% and affiliations for an 'aesthetic maximum' of six authors.
+% Add names, affiliations, addresses for
+% the seventh etc. author(s) as the argument for the
+% \additionalauthors command.
+% These 'additional authors' will be output/set for you
+% without further effort on your part as the last section in
+% the body of your article BEFORE References or any Appendices.
+
+\numberofauthors{6} %  in this sample file, there are a *total*
+% of EIGHT authors. SIX appear on the 'first-page' (for formatting
+% reasons) and the remaining two appear in the \additionalauthors section.
+%
+\author{
+% You can go ahead and credit any number of authors here,
+% e.g. one 'row of three' or two rows (consisting of one row of three
+% and a second row of one, two or three).
+%
+% The command \alignauthor (no curly braces needed) should
+% precede each author name, affiliation/snail-mail address and
+% e-mail address. Additionally, tag each line of
+% affiliation/address with \affaddr, and tag the
+% e-mail address with \email.
+%
+% 1st. author
+\alignauthor
+Haiyan Meng\\
+    \affaddr{Department of Computer Science and Engineering}\\
+    \affaddr{University of Notre Dame}\\
+    \affaddr{Notre Dame, Indiana}\\
+    \email{hmeng@nd.edu}
+% 2nd. author
+\alignauthor
+Matthias Wolf\\
+    \affaddr{Department of Physics}\\
+    \affaddr{University of Notre Dame}\\
+    \affaddr{Notre Dame, Indiana}\\
+    \email{mwolf3@nd.edu}
+% 3rd. author
+\alignauthor
+Anna Woodard\\
+    \affaddr{Department of Physics}\\
+    \affaddr{University of Notre Dame}\\
+    \affaddr{Notre Dame, Indiana}\\
+    \email{awoodard@nd.edu}
+\and  % use '\and' if you need 'another row' of author names
+% 4th. author
+\alignauthor 
+Peter Ivie\\
+    \affaddr{Department of Computer Science and Engineering}\\
+    \affaddr{University of Notre Dame}\\
+    \affaddr{Notre Dame, Indiana}\\
+    \email{pivie@nd.edu}
+% 5th. author
+\alignauthor 
+Michael Hildreth\\
+    \affaddr{Department of Physics}\\
+    \affaddr{University of Notre Dame}\\
+    \affaddr{Notre Dame, Indiana}\\
+    \email{Michael.D.Hildreth.2@nd.edu}
+% 6th. author
+\alignauthor 
+Douglas Thain\\
+    \affaddr{Department of Computer Science and Engineering}\\
+    \affaddr{University of Notre Dame}\\
+    \affaddr{Notre Dame, Indiana}\\
+    \email{dthain@nd.edu}
+}
+\date{15 January 2014}
 \maketitle
+\begin{abstract}
+...
+\end{abstract}
+
+% A category with the (minimum) three required fields
+\category{H.4}{Information Systems Applications}{Miscellaneous}
+%A category including the fourth, optional field follows...
+\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]
+
+\terms{Theory}
+
+\keywords{ACM proceedings, \LaTeX, text tagging} % NOT required for Proceedings
 
 \section{Introduction}
+...
+\section{Introduction of the exmaple}
+\subsection{Background}
+Matthias, one guy from physics department, finished one interesting tau analysis. We want to understand how the tau analysis works and repeat it.
 
-\indent The longevity of high Energy physics (HEP) experiments makes it become important to preserve data and software in HEP.
-The Tevatron, the second most powerful proton-antiproton collider, serviced until 2011 since its completion in 1883.
-The CDF experiment, which belongs to the Tevatron, involved three levels triggers.
-The output rates of Level-1 and Level-2 are about 30kHz and 350Hz respectively.
-Even if the event rate (with an average event size of 150KB) of the Level-3 trigger is reduced to about 100Hz, the total size of data needed to be preserved is still very large---about 15MB/s.It is necessary to preserve all these event data to to ensure the smooth progress of the whole experiment.\\
+\subsection{This workflow of the example}
+Declare environment variables
 
-The development of theory and experimental analysis technology in the physics field makes it become possible to re-evaluate the dataset of current HEP experiments several decades later.
-The software and hardware environment of current HEP experiments is also needed to be preserved to repeat the whole experimental process from scratch.
-\\
+Obtain software from CMSSW
 
-The complexity of HEP experiments makes the collaboration of physicists from different countries and projects, become necessary.
-For example, the CDF collaboration consists of about 600 researchers from about 60 institutions in 15 countries.
-One efficient data preservation and sharing mechanism is necessary for the progress of the whole project.
-One ATLAS physicist might want to access the preserved CMS data and perform an analysis on it.
-How to preserve CMS data so that it can be accessed and utilized by physicists from different projects efficiently and flexibly becomes urgent.\\
+Obtain software from Git
 
-Facing with the huge amounts of original data and different upper-layer data analysis software environments, one preservation mechanism, which decides the minimal and essential set of data and software need to be stored, what sorts of metadata is necessary to be preserved, how to organize metadata to guarantee fast indexing and retrieval of data and software, is needed.\\
+Obtain software from some public HTTP web links
 
-To have a clear understanding of the core components of such a preservation mechanism, case study research can verify and supplement our origin design thought.
-Through detailed analysis of one case, which aims to preserve the data and software involved in one HEP application, data sources, software sources and the main analysis workflow of one HEP application can be obtained.
-The difficult points of designing one preservation scheme will become explicit.
-One tentative preservation mechanism considering all these factors will be deployed and verified, and the verification process will in turn help us figure out the points need to be modified and optimized.\\
+Obtain software from one private home page
 
-The remaining parts of the paper is organized as follows.
+Build software enviroment using SCRAM and Python
 
-\section{Motivation}
+Install grid control, obtain CMS data from grid and store the data into HDFS mounted as one local file system.
 
-\indent Matthias, one guy from physics department, finished one interesting tau analysis. We want to understand how the tau analysis works and repeat it.
-
-\section{Introduction of the exmaple}
-\subsection{This workflow of the example}
-\indent declare environment variables\\
-
-Obtain software from CMSSW\\
-
-Obtain software from Git\\
-
-Obtain software from some public HTTP web links\\
-
-Obtain software from one private home page\\
-
-Build software enviroment using SCRAM and Python\\
-
-install grid control, obtain CMS data from grid and store the data into HDFS mounted as one local file system.\\
-
-actual data analysis.
+Actual data analysis.
 
 \subsection{the source and size of experiment data and software}
-We notice that the software sources are rich, including cmssw, hadoop, grid, git, http and one personal main page. The size of experiment data and software is large.\\
+We notice that the software sources are rich, including cmssw, hadoop, grid, git, http and one personal main page. The size of experiment data and software is large.
 
-*****hmeng: wget -r http://nd.edu/~abrinke1/electroneffectivearea.h -o electroneffectivearea.h\\
+As for the experiment data, Matthias copies the subset of T3 data from grid and stores the data into HDFS mounted as one local file system. The total size of data stored in HDFS is 33TB.
 
-As for the experiment data, Matthias copies the subset of T3 data from grid and stores the data into HDFS mounted as one local file system. The total size of data stored in HDFS is 33TB.\\
-
-The source and size of software are shown in Table~\ref{table:software-source-size}.\\
+The source and size of software are shown in Table~\ref{table:software-source-size}.
 
@@
     \centering
-    \begin{tabular}{|l|l|}
+    \begin{tabular}{|l|}
         \hline
-        First version & Second version \\ \hline
-        1. Create a CMS release, e.g. cmsrel CMSSW\_5\_3\_11\_patch3 \\
-        2. Install the BEAN packages follow the instructions on github:\\
-            https://github.com/cms-ttH/BEAN/blob/master/README.md\\
-        3. Install git-control: svn co https://ekptrack ... grid-control\\
+        First version \\ \hline
+        \\
+        1. Create CMS release,\\
+            \hspace{9pt} e.g. cmsrel CMSSW\_5\_3... \\
+        2. Install BEAN packages: \\
+            \hspace{9pt} https://github.com/cms-ttH/...\\
+        3. Install grid-control: \\ 
+            \hspace{9pt} svn co https://dwekptrack... \\
         4. INstall the TauAnalysis package: \\
-            git clone https://github.com/matz-e/.../TauAnalysis\\
+           \hspace{9pt} git clone https://github.com/matz-e/... \\
+           \hspace{9pt} scram b -j32 \\
+        5. fix grid\_control.cfg and run it. \\
+        6. Perform actual analysis \\ 
+        \\ \hline
+        Second version \\ \hline
+        \\
+        set CMSSW\_BASE = (CMSSW\_5\_3...) \\
+        module load git \\        
+        cmsenv \\ 
+        cvs login \\
+        cvs co UserCode/Bicocca/... \\
+        git clone... \\
         scram b -j32 \\
-        5. Perform actual analysis & second88 \\ \hline
-        Third version & Fourth version \\ \hline
+        wget http://pyyaml.org/... \\
+        python setup.py install... \\
+        \#the experiment data is from HDFS \\
+        roaster data/generic\_ttl.yaml \\ 
+        \\ \hline
+        Third version \\ \hline
+        \\
+        \#the description of OS version and hardware architecture \\
+        set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3) \\ 
+        cmsenv \\
+        wget http://pyyaml.org/... \\
+        python setup.py install... \\
+        roaster data/generic\_ttl.yaml \\
+        \\ \hline
+        Fourth version \\ \hline
+        \\
+        \#the description of OS version and hardware architecture \\
+        \#declaration of environment variables\\
+        \#clear data dependency\\
+        \#clear software dependency\\
+        \#software build and install command\\
+        \#actual analysis program\\ 
+        \\ \hline
     \end{tabular}
@@
 \end{table}
+
 \section{First solution to repeat the program}
-\indent In order to repeat Matthais's example, the new user consulted the original author by email about the necessary work for the experiment.
+In order to repeat Matthais's example, the new user consulted the original author by email about the necessary work for the experiment.
 In response, Matthias introduced the general workflow of his tau analysis through one long email including notes, linux shell commands, web links.
-The First version of Table~\ref{table:scripts} illstrates Matthias's example.\\
+The First version of Table~\ref{table:scripts} illstrates Matthias's example.
 
@@
 The access of CMSSW requires the new user be an authorized user of CMSSW.
-What’s more, some parts of the workflow is unrepeatible.
+What's more, some parts of the workflow is unrepeatible.
 The third step of this experiment requires the new user owning the access authority for grid.
-\\
 
@@
 \section{second solution to repeat the program}
-\indent One possible solution for the access authority problem of grid data is to grant the new user the authority to access gird data directly.
+One possible solution for the access authority problem of grid data is to grant the new user the authority to access gird data directly.
 Another possible solution is let the new user directly operate on the machine the original author used.
-As for the complexity of jumping between multiple web links, people may suggest that letting the original author generate one clear script including all the contents from different web links.\\
+As for the complexity of jumping between multiple web links, people may suggest that letting the original author generate one clear script including all the contents from different web links.
 
@@
 The Second version of Table~\ref{table:scripts} illstrates the merged script.
-As for the data obtainance from grid, we directly use the local copy in hdfs to avoid the new user to obtain the grid certification.\\
+As for the data obtainance from grid, we directly use the local copy in hdfs to avoid the new user to obtain the grid certification.
 
-*****hmeng: add the time and data analysis of the second solution.\\
-
-Because the script includes all the necessary procedures for the repeat of one analysis program, the readability and friendliness of this solution is higher than that of the email format.
-However, each execution of the script will involve the obtainance of software from different sources and the building of software environment.
-As for the access problem of grid data, using the data copy stored in the machine where mathias executed the experiment requires the new user have the authority to access the machine, which complicates the management of the original machine, even is impossible if the original machine executes rigid user access control.
-Granting everyone who wants to repeat the analysis the access authority for grid (grid certificate) is wasteful and unsafe.
-\\
-
-Implication: All the data and software involved in the experiment should be provide to the new user in the format of one static package so that the multiple execution of the experiment from the same user only involve one time of data obtainance and software obtainance and compiling.
-In addition, the requirement of the underlying OS and hardware should also be provided to the new users.
-
-\section{third solution to repeat the program}
-\indent The difficulty of data access authority obtainance enforces us to find out one independent solution, in which the repeat of the original analysis can be done without any external dependency.
-that is, one independent and self-contained package containing all the data and software dependencies is necessary.
-Someone may suggest that it should be the responsibility of the original author to generate the required package.
-However, letting the original author to provide the package which can be used by other scholars to repeat the original experiment is unrealistic.
-One reason for this is that figuring out the underlying dependency of each software is complex and time-consumpting and even impossible for the original author.
-In this experiment, the machine used for the experiment is one public machine of physics department, and Matthias is one common user without root authority.
-All the underlying OS and supporting softwares are installed and maintained by the IT department of the university.
-On the other hand, the architecture design of the required package including all the data and software dependencies is not under the research range of physists.\\
-
-Parrot is a virtual filesystem access tool which attaching existing programs to a variety of remote I/O systems including http, ftp, gridftp, irods, hdfs, xrootd, grow and chirp.
-it traps all system calls of one program through ptrace debugging interface, and replaces them with remote I/O operations as desired.
-through executing one program under parrot, all the paths of files involved in this program can be recorded.\\
-
-With the help of parrot, one packaging utility which generates one independent package for one program to make the repeat of the program convenient can be deployed.
-the basis of the packaging utility is one successful execution sandbox (the data from grid has been preserved in hdfs and the software from cmssw, git and http has been on the local machine.).
-we re-execute the actual data analysis code (shown in “the script of the third solution”) under parrot and get the name list of all the files actually accessed during the execution process of the actual data analysis.
-then, according to the file name list, one package containing all the necessary data and software for one analysis program is generated.
-next time, when another scholar wants to repeat the program, he only needs to obtain the package and directly execute the actual analysis program inside the package.\\
-
-The shell script of the second solution is simplified into one new version, which only contains the necessary environment variables, access authority and the actual analysis command.
-The Third version of Table~\ref{table:scripts} illustrates the simplified script.\\
-
-the workflow of generating one package for one analysis program  is as follows: \\
-\indent (1) execute one analysis program under parrot and obtain filename list (L1) of it\\
-\indent Parrot is one virtual file system that can support user access to multiple underlying file systems.
-parrot traps each system call involved in the process of data access, figures out the type of file system and redirects it into corresponding operations to the accessed file system.
-during this process, each accessed file is recorded into one file with the access type of it, such as open, stat, read and write.\\
-\indent command:\\
-\indent parrot\_run –l namelist /bin/tcsh parrot\_cms.sh (installcms.sh)\\
-\indent namelist size: 5.7mb     128711 lines\\
-\indent de-duplicated namelist size: 2.2mb   42385 lines\\
-
-(2) generate one package containing the files of L1 \\
-\indent The packaging utility iterates each filename inside L1 and copies it into the target package.
-after completing the packaging process, the target package together with its information, and one mountlist, which redirects the access of data from different file systems into the target package, will be provided to users.\\
-
-The packaging process also runs within parrot environment to access data from different file systems.\\
-\indent command:\\
-\indent /bin/bash ~/package1-4.sh –l ~/namelist\\
-\indent the path of pacakge is: /tmp/package1-4\\
-\indent the total size of package is: 21g\\
-\indent the total number of files is: 1204\\
-\indent the total number of directory is: 473\\
-\indent the total number of symbolic link files is: 195\\
-\indent the mountlist path is: /tmp/mountlist\\
-
-*****lack: file content + metadata; only file metadata; different process solutions\\
-
-the structure of the generated package is as follows.
-each file inside l1 is copied into the package, the final file path becomes the path of the package, followed by the original file path.
-in this program, the path of the package is /tmp/package1-4, so the final path of one file with the original path path1 is /tmp/package1-4/path1.\\
-
-To ensure the successful reproductivity, the filesystem structure of the original execution environment should be preserved as completely as possible.
-however, attempting to copy the whole content of one directory or one file is space-consuming and time-consuming, because the original program may only access the metadata of one directory with the size of 200gb.
-our solution is to determine the copy degree of one directory or one common file according to the system call type for each file.\\
-
-The map relationship between the file access path inside the actual analysis program and the actual file location is kept inside the mountlist file. the structure of the mountlist is as follows:\\
-\indent / /tmp/package1-4 \\
-\indent /tmp/package1-4 /tmp/package1-4 \\
-\indent /dev /dev \\
-\indent /misc /misc \\
-\indent /net /net \\
-\indent /proc /proc \\
-\indent /sys /sys \\
-\indent /var /var \\
-\indent /selinux /selinux\\
-
-*****lack: re-execute process: re-execution process will redirect all the data access into the package except for data under proc sys dev selinux\\
-
-(3) rerun the analysis program using the package\\
-\indent When another scholar wants to repeat one analysis program, the accessed data field is limited into the target package with the help of the mountlist generated in step 2. \\
-
-command:\\
-\indent parrot\_run –m /tmp/mountlist /bin/tcsh parrot\_cms.sh\\
-
-*****hmeng: add the evaluation of this solution\\
-
-benefits of this solution: the repeat of one analysis program becomes easier, which would be executed in one independent package containing all the data and software dependencies of one analysis program.
-\\
-
-rethink mathias’s example, under this solution, the repeat of it only needs the necessary environment variables, svn login,  the last command (scripts/roaster -atfpvy data/generic\_ttl.yam) and the package.
-if different scholars want to repeat one analysis program, what they need to do is to obtain the package and rerun the actual analysis program.
-under the second solution, each scholar needs to get the necessary data and software, and then prepare software environment, which is time-consuming.
-\\
-
-drawbacks of this solution: however, different experimenters may execute different analysis programs on the same dataset using the same or overlapping sets of software.
-generating one new package for each analysis program from scratch is time-consuming and space-consuming, which makes one data and software preservation mechanism, which can integrate the preservation requirements of different analysis programs, become necessary.
-
-\section{fourth solution to repeat the program}
-\indent To integrate the data and software from multiple analysis programs into one package, the concrete information of data and software, such as size, version, source and the number of files, need to be recorded.
-we also need to design one more instructive shell script format, in which the data dependencies and software dependencies can be clearly expressed and recognized.
-the packaging process needs to be re-organized.
-packaging utility needs to maintain one list of current software and data subset already stored in the package.
-when one user wants to generate one package, it will fork the packaging utility, the packaging utility will scan the script, get the data dependency part and software dependency part, judge whether each dependency has been inside the package, and only add the new data and software into the package, and update the package information and package retrieval information.\\
-
-as for data and software, need to ensure its identity. the software version.\\
-
-benefits of this solution: time saving (there are some overlap parts between different analysis programs, especially different analysis programs of one physicist); storage space saving (overlap parts between different analysis programs).
-the fourth-version script is very instructive so that physicists can repeat one analysis program or create one new analysis program more easily and efficiently.
-this is more manageable (data software sharing)\\
-
-*****hmeng-doubt: maybe one lightweight database like sqlite, can be used to manage the metadata of data and software. \\
-
-*****hmeng-doubt: difficulties: for parrot, how to recognize the start and end points of one dataset or one software.
-because up till now, the process unit of parrot is one single file, rather one single package.\\
-
-*****hmeng-doubt: questions: how to set the unit of parrot: file or package\\
-
-*****lack: the 4th version of script (how to design the new script still needs consideration)
-
-\section{the relationship of different solutions}
-\indent The relationship of these four solutions to repeat one program is shown in Table~\ref{table:relationship}.\\
-
-\begin{table}
-    \centering
-    \begin{tabular}{|l|r|r|r|}
-        \hline
-        Solution ID & Data Resources & Software Resources & Operation Manual \\ \hline
-        1st Solution & grid & CMSSW Git HTTP & email \\ \hline
-        2nd Solution & local (HDFS) & CMSSW Git HTTP & shell script \\ \hline
-        3rd Solution & independent package & independent package & shell script + packaging utility \\ \hline
-        4th Solution & independent package & independent package & shell script + packaging utility \\ \hline
-    \end{tabular}
-    \caption{The relationship of different solutions}
-    \label{table:relationship}
-\end{table}
-
-The fourth solution should be based on the third solution.
-during the packaging process, packaging utility first checks whether the file has been inside the target package, (if exists, whether it is the latest version).
-only if the file does not exist in the target package or the file in the target package is not the latest version, the packaging utility copies the file into the target package.\\
-
-*****hmeng-doubt: potential risk: different analysis programs share some common file names, but with different file contents. we should analyze the possibility of conflict: data.\\
-
-*****hmeng-doubt: in the fourth version, let user to mark whether they change the data and software.
-if changed, one new package is generated to avoid data overlap and pollution.
-otherwise, directly starts packaging process based on the current target package.
-
-\section{comparison of the 2nd solution and the 3rd solution}
-\subsection{the breakdown of execution time of the second solution: }
-\indent according to the Table~\ref{table:time-2nd}, about half of the total execution time is consumed to prepare relevant data and software.
+The breakdown of execution time of the second solution is shown in Table~\ref{table:time-2nd}.
+According to Table~\ref{table:time-2nd}, about half of the total execution time is consumed to prepare relevant data and software.
 
@@
 
-\subsection{the data size of the second solution:}
-\indent according to the data and software resources involved in this example, the size of each category is shown in Table~\ref{table:datasize-2nd}.
+According to the data and software resources involved in this example, the size of each category is shown in Table~\ref{table:datasize-2nd}.
 
@@
 
-\subsection{the breakdown of execution time of the third solution: }
-\indent The breakdown of execution time of the third solution is illustrated in Table~\ref{table:time-3rd}.
+Because the script includes all the necessary procedures for the repeat of one analysis program, the readability and friendliness of this solution is higher than that of the email format.
+However, each execution of the script will involve the obtainance of software from different sources and the building of software environment.
+As for the access problem of grid data, using the data copy stored in the machine where mathias executed the experiment requires the new user have the authority to access the machine, which complicates the management of the original machine, even is impossible if the original machine executes rigid user access control.
+Granting everyone who wants to repeat the analysis the access authority for grid (grid certificate) is wasteful and unsafe.
+
+Implication: All the data and software involved in the experiment should be provide to the new user in the format of one static package so that the multiple execution of the experiment from the same user only involve one time of data obtainance and software obtainance and compiling.
+In addition, the requirement of the underlying OS and hardware should also be provided to the new users.
+
+\section{third solution to repeat the program}
+\subsection{Working principle of packaging utility}
+The difficulty of data access authority obtainance enforces us to find out one independent solution, in which the repeat of the original analysis can be done without any external dependency.
+that is, one independent and self-contained package containing all the data and software dependencies is necessary.
+Someone may suggest that it should be the responsibility of the original author to generate the required package.
+However, letting the original author to provide the package which can be used by other scholars to repeat the original experiment is unrealistic.
+One reason for this is that figuring out the underlying dependency of each software is complex and time-consumpting and even impossible for the original author.
+In this experiment, the machine used for the experiment is one public machine of physics department, and Matthias is one common user without root authority.
+All the underlying OS and supporting softwares are installed and maintained by the IT department of the university.
+On the other hand, the architecture design of the required package including all the data and software dependencies is not under the research range of physists.
+
+Parrot is a virtual filesystem access tool which attaching existing programs to a variety of remote I/O systems including http, ftp, gridftp, irods, hdfs, xrootd, grow and chirp.
+it traps all system calls of one program through ptrace debugging interface, and replaces them with remote I/O operations as desired.
+through executing one program under parrot, all the paths of files involved in this program can be recorded.
+
+With the help of parrot, one packaging utility which generates one independent package for one program to make the repeat of the program convenient can be deployed.
+the basis of the packaging utility is one successful execution sandbox (the data from grid has been preserved in hdfs and the software from cmssw, git and http has been on the local machine.).
+we re-execute the actual data analysis code (shown in "the script of the third solution") under parrot and get the name list of all the files actually accessed during the execution process of the actual data analysis.
+then, according to the file name list, one package containing all the necessary data and software for one analysis program is generated.
+next time, when another scholar wants to repeat the program, he only needs to obtain the package and directly execute the actual analysis program inside the package.\\
+
+The shell script of the second solution is simplified into one new version, which only contains the necessary environment variables, access authority and the actual analysis command.
+The Third version of Table~\ref{table:scripts} illustrates the simplified script.
+
+\subsection{Workflow of packaging utility}
+The workflow of generating one package for one analysis program  is as follows:
+
+(1) execute one analysis program under parrot and obtain filename list (L1) of it
+
+Parrot is one virtual file system that can support user access to multiple underlying file systems.
+parrot traps each system call involved in the process of data access, figures out the type of file system and redirects it into corresponding operations to the accessed file system.
+during this process, each accessed file is recorded into one file with the access type of it, such as open, stat, read and write.
+
+command:
+
+parrot\_run -l namelist /bin/tcsh parrot\_cms.sh
+
+namelist size: 5.7mb     128711 lines
+
+de-duplicated namelist size: 2.2mb   42385 lines
+
+(2) generate one package containing the files of L1
+
+The packaging utility iterates each filename inside L1 and copies it into the target package.
+after completing the packaging process, the target package together with its information, and one mountlist, which redirects the access of data from different file systems into the target package, will be provided to users.
+
+The packaging process also runs within parrot environment to access data from different file systems.
+
+command:
+
+/bin/bash package1-4.sh -l ~/namelist
+
+the path of pacakge is: /tmp/package1-4
+
+the total size of package is: 21g
+
+the total number of files is: 1204
+
+the total number of directory is: 473
+
+the total number of symbolic link files is: 195
+
+the mountlist path is: /tmp/mountlist
+
+*****lack: file content + metadata; only file metadata; different process solutions
+
+The structure of the generated package is as follows.
+each file inside l1 is copied into the package, the final file path becomes the path of the package, followed by the original file path.
+in this program, the path of the package is /tmp/package1-4, so the final path of one file with the original path path1 is /tmp/package1-4/path1.
+
+To ensure the successful reproductivity, the filesystem structure of the original execution environment should be preserved as completely as possible.
+however, attempting to copy the whole content of one directory or one file is space-consuming and time-consuming, because the original program may only access the metadata of one directory with the size of 200gb.
+our solution is to determine the copy degree of one directory or one common file according to the system call type for each file.
+
+The map relationship between the file access path inside the actual analysis program and the actual file location is kept inside the mountlist file. the structure of the mountlist is as follows:
+
+/ /tmp/package1-4
+
+/tmp/package1-4 /tmp/package1-4
+
+/dev /dev
+
+/misc /misc
+
+/net /net
+
+/proc /proc
+
+/sys /sys
+
+/var /var
+
+/selinux /selinux
+
+*****lack: re-execute process: re-execution process will redirect all the data access into the package except for data under proc sys dev selinux
+
+(3) rerun the analysis program using the package
+
+When another scholar wants to repeat one analysis program, the accessed data field is limited into the target package with the help of the mountlist generated in step 2.
+
+command:
+
+parrot\_run -m /tmp/mountlist /bin/tcsh parrot\_cms.sh
+
+\subsection{Evaluation of the third solution}
+The breakdown of execution time of the third solution is illustrated in Table~\ref{table:time-3rd}.
 the time used to obtain file namelist and generate p1 is greatly longer than the execution time within the new package.
@@
 
-\subsection{ the data size of the third solution}
-\indent The data size of the 3rd solution is shown in Table~\ref{table:datasize-3rd}.
+The data size of the 3rd solution is shown in Table~\ref{table:datasize-3rd}.
 The data categories is more complex than our imagination.
@@
     usr & 60MB \\ \hline
-    Others (/sbin + /tmp / + /lib + /lib64 + /var + /opt + /bin + /etc) & 28.4MB \\ \hline
+    Others (/sbin + ... + /lib) & 28.4MB \\ \hline
     Total & 20.213GB \\ \hline
@@
 
+\subsection{Discussion of the third solution}
+benefits of this solution: the repeat of one analysis program becomes easier, which would be executed in one independent package containing all the data and software dependencies of one analysis program.
+
+rethink mathias's example, under this solution, the repeat of it only needs the necessary environment variables, svn login,  the last command (actual analysis command) and the package.
+if different scholars want to repeat one analysis program, what they need to do is to obtain the package and rerun the actual analysis program.
+under the second solution, each scholar needs to get the necessary data and software, and then prepare software environment, which is time-consuming.
+
+\section{the relationship of different solutions}
+The relationship of these four solutions to repeat one program is shown in Table~\ref{table:relationship}.
+
+\begin{table*}
+    \centering
+    \begin{tabular}{|l|r|r|r|}
+        \hline
+        Solution ID & Data Resources & Software Resources & Operation Manual \\ \hline
+        1st Solution & grid & CMSSW Git HTTP & email \\ \hline
+        2nd Solution & local (HDFS) & CMSSW Git HTTP & shell script \\ \hline
+        3rd Solution & package & package & shell script + packaging utility \\ \hline
+    \end{tabular}
+    \caption{The relationship of different solutions}
+    \label{table:relationship}
+\end{table*}
+
+The fourth solution should be based on the third solution.
+during the packaging process, packaging utility first checks whether the file has been inside the target package, (if exists, whether it is the latest version).
+only if the file does not exist in the target package or the file in the target package is not the latest version, the packaging utility copies the file into the target package.
+
+*****hmeng-doubt: potential risk: different analysis programs share some common file names, but with different file contents. we should analyze the possibility of conflict: data.
+
+*****hmeng-doubt: in the fourth version, let user to mark whether they change the data and software.
+if changed, one new package is generated to avoid data overlap and pollution.
+otherwise, directly starts packaging process based on the current target package.
+
+\section{comparison of the 2nd solution and the 3rd solution}
 \subsection{ Data size comparison of 2nd and 3rd solution}
-\indent The packaging utility checks the system call of each file within the namelist, and maintains the minimum dataset, which makes the size of the final package is as small as possible.
+The packaging utility checks the system call of each file within the namelist, and maintains the minimum dataset, which makes the size of the final package is as small as possible.
 The total size of Hadoop under the second solution is astonished, while the size of Hadoop under the package is decreased to 20GB.
 The same trend applies to the size of CMSSW\_5\_3\_11\_patch3.
-Because the packaging utility tries to construct one independent and self-contained package, necessary files  from /usr, /bin, /lib are also copied into the package and denoted as “Data necessary for Package” in the Table~\ref{table:datasize-2nd3rd}.
+Because the packaging utility tries to construct one independent and self-contained package, necessary files  from /usr, /bin, /lib are also copied into the package and denoted as "Data necessary for Package" in the Table~\ref{table:datasize-2nd3rd}.
 
@@
     \hline
-     Data Category & Data size of 2nd solution & Data size of 3rd solution \\ \hline
+     Data Category & Data size & Data size \\
+    & 2nd solution & 3nd solution \\ \hline
     Hadoop & 33TB = 33792GB & 20GB \\ \hline
      CMSSW\_5\_3\_11\_patch3 & 562MB & 5.2MB \\ \hline
-     Data necessary for Package & 207.4MB & N/A \\ \hline
+     Other data for Package & 207.4MB & N/A \\ \hline
      Total & 33792.562GB & 20.213GB \\ \hline
@@
 \subsection{Execution time comparison of 2nd and 3rd solution}
-\indent Table~\ref{table:time-2nd3rd} shows the execution time comparison between the 2nd solution and the 3rd solution.
+Table~\ref{table:time-2nd3rd} shows the execution time comparison between the 2nd solution and the 3rd solution.
 The time consumption of the repeat of one program from different scholars kept the same under the second solution, including software and data preparation.
@@
     \hline
-    Task Category & execution time of 2nd solution & execution time of 3rd solution \\ \hline
+    Task Category & execution time & execution time \\
+    & 2nd solution & 3rd solution \\ \hline
     Software Acquisition & 16min 15s & N/A \\ \hline
@@
     Generate the package & N/A & 13min 37s \\ \hline
-    Actual Experimental Analysis & 31min 44s & 13min 1s \\ \hline
+    Actual Analysis & 31min 44s & 13min 1s \\ \hline
     Total & 61min 20s & N/A \\ \hline
@@
 
-*****hmeng-doubt:Another reason for the packaging utility is that not all the data and software generated by Peter’s script is used during the the actual data analysis.
+*****hmeng-doubt:Another reason for the packaging utility is that not all the data and software generated by the second version script is used during the the actual data analysis.
 The packaging utility can help us find out the optimal subset of data and software involved in one actual data analysis.
-\\
-\indent *****hmeng-doubt: this point is not the motivation. but one achievement comes together. out of imagination.\\
+
+*****hmeng-doubt: this point is not the motivation. but one achievement comes together. out of imagination.
+
+\section{Discussion of data and software preservation}
+\subsection{Preservation integration of multiple programs}
+The third solution can work well for the preservation and repeat of one single program.
+However, different experimenters may execute different analysis programs on the same dataset using the same or overlapping sets of software.
+Generating one new package for each analysis program from scratch is time-consuming and space-consuming, which makes one data and software preservation mechanism, that can integrate the preservation requirements of different analysis programs, become necessary.
+
+To integrate the data and software from multiple analysis programs into one package, the concrete information of data and software, such as size, version, source and the number of files, need to be recorded.
+we also need to design one more instructive shell script format, in which the data dependencies and software dependencies can be clearly expressed and recognized.
+the packaging process needs to be re-organized.
+packaging utility needs to maintain one list of current software and data subset already stored in the package.
+when one user wants to generate one package, it will fork the packaging utility, the packaging utility will scan the script, get the data dependency part and software dependency part, judge whether each dependency has been inside the package, and only add the new data and software into the package, and update the package information and package retrieval information.
+
+\subsection{Preservation granularity}
+Another important factor of data and software preservation is the choice of preservation of preservation granularity.
+In the third solution, the preservation granularity is one file ,because Parrot virtual filesystem traps each system call and redirects the access path to each file.
+As a result, during the packaging process, each time only one file can be copied into the target package, which is low-efficient.
+However, there are other options of preservation granularity.
+The software is generally preserved in the unit of package inside the remote repository, the packaging process of one experiment can adopt one package as the unit.
+In addition, if the size of one whole software repository is reasonable and the access frequency of each package of it is high, the granularity can be set to the whole repository.
+
+\subsection{The user access model of data and software}
+Through this case study, we notice that the user access module of remote data and software has a great impact of the preservation mechanism, especially when we try to integrate the preservation of multiple programs.
+If all the programs only refer the original data and software and refuse to modify it, the preservation is easy and can ignore the data version problem.
+However, if each program tries to modify the original data and software to accustom to its own requirement, the preservation mechanism must provide one way to differentiate the original data version and the special data version of one certain program.
+To have a clear understanding of the data access model, more examples need to be investigated.
 
@@
 
-\section{Future Work}
-\indent this is an example of citing \cite{Laboratories79make}. \\
+this is an example of citing \cite{Laboratories79make}.
 

### 2014-01-14 paper1.tex
the first acm version

--- 2014-01-14 paper.tex
@@
 \title{A Case Study in Preserving a High Energy Physics Application}
-\author{Haiyan Meng\\ Department of Computer Science and Engineering\\ University of Notre Dame}
+\author{Haiyan Meng, Matthias Wolf, Anna Woodard, Peter Ivie, Michael Hildreth, Douglas Thain\\ University of Notre Dame}
 \date{January 2014}
@@
 \section{Introduction}
-
 \indent The longevity of high Energy physics (HEP) experiments makes it become important to preserve data and software in HEP.
@@
 
-\section{Motivation}
-
+\section{Introduction of the exmaple}
+\subsection{Background}
 \indent Matthias, one guy from physics department, finished one interesting tau analysis. We want to understand how the tau analysis works and repeat it.
 
-\section{Introduction of the exmaple}
 \subsection{This workflow of the example}
@@
 
-Implication:  Directly repeating the experiment using the published workflow and results by the original author is complex and even difficulty.
+:Implication:  Directly repeating the experiment using the published workflow and results by the original author is complex and even difficulty.
 Some extra work must be done to make the repeating process easier.
@@
 
-*****hmeng: add the time and data analysis of the second solution.\\
+The breakdown of execution time of the second solution is shown in Table~\ref{table:time-2nd}.
+According to Table~\ref{table:time-2nd}, about half of the total execution time is consumed to prepare relevant data and software.\\
+
+\begin{table}
+    \centering
+    \begin{tabular}{|l|r|r|}
+    \hline
+    Sub-Task & Time & Percentage \\ \hline
+    Software preparation from CMSSW & 15min 30s & 25.27\% \\ \hline
+    Software preparation from Git & 9s & 0.24\% \\ \hline
+    Software preparation from Wget & 36s & 0.98\% \\ \hline
+    Environment Build - SCRAM & 13min 20s & 21.74\% \\ \hline
+    Environment Build - Python & 1s & 0.03\% \\ \hline
+    Data analysis & 31min 44s & 51.74\% \\ \hline
+    Total & 61min 20s & 100.00\% \\ \hline
+    \end{tabular}
+    \caption{The breakdown of execution time of the 2nd solution}
+    \label{table:time-2nd}
+\end{table}
+According to the data and software resources involved in this example, the size of each category is shown in Table~\ref{table:datasize-2nd}.\\
+
+\begin{table}
+    \centering
+    \begin{tabular}{|l|r|}
+    \hline
+    Data Category & Data Size \\ \hline
+    Software from CMSSW & 449MB \\ \hline
+    Software from Git & 61MB \\ \hline
+    Software from Wget & 52MB \\ \hline
+    Hadoop & 33TB \\ \hline
+    Total & 33792.562GB \\ \hline
+    \end{tabular}
+    \caption{The data size of the 2nd solution}
+    \label{table:datasize-2nd}
+\end{table}
+*****hmeng-doult: the size of hadoop need to reconsidered. how to correctly illustrate the data size of this example?
 
@@
 \section{third solution to repeat the program}
+\subsection{Working principle of packaging utility}
 \indent The difficulty of data access authority obtainance enforces us to find out one independent solution, in which the repeat of the original analysis can be done without any external dependency.
@@
 The shell script of the second solution is simplified into one new version, which only contains the necessary environment variables, access authority and the actual analysis command.
-The Third version of Table~\ref{table:scripts} illustrates the simplified script.\\
+The Third version of Table~\ref{table:scripts} illustrates the simplified script.
 
-the workflow of generating one package for one analysis program  is as follows: \\
+\subsection{Workflow of packaging utility}
+\indent The workflow of generating one package for one analysis program  is as follows: \\
 \indent (1) execute one analysis program under parrot and obtain filename list (L1) of it\\
@@
 command:\\
-\indent parrot\_run –m /tmp/mountlist /bin/tcsh parrot\_cms.sh\\
+\indent parrot\_run –m /tmp/mountlist /bin/tcsh parrot\_cms.sh
 
-*****hmeng: add the evaluation of this solution\\
-
-benefits of this solution: the repeat of one analysis program becomes easier, which would be executed in one independent package containing all the data and software dependencies of one analysis program.
-\\
-
-rethink mathias’s example, under this solution, the repeat of it only needs the necessary environment variables, svn login,  the last command (scripts/roaster -atfpvy data/generic\_ttl.yam) and the package.
-if different scholars want to repeat one analysis program, what they need to do is to obtain the package and rerun the actual analysis program.
-under the second solution, each scholar needs to get the necessary data and software, and then prepare software environment, which is time-consuming.
-\\
-
-drawbacks of this solution: however, different experimenters may execute different analysis programs on the same dataset using the same or overlapping sets of software.
-generating one new package for each analysis program from scratch is time-consuming and space-consuming, which makes one data and software preservation mechanism, which can integrate the preservation requirements of different analysis programs, become necessary.
-
-\section{fourth solution to repeat the program}
-\indent To integrate the data and software from multiple analysis programs into one package, the concrete information of data and software, such as size, version, source and the number of files, need to be recorded.
-we also need to design one more instructive shell script format, in which the data dependencies and software dependencies can be clearly expressed and recognized.
-the packaging process needs to be re-organized.
-packaging utility needs to maintain one list of current software and data subset already stored in the package.
-when one user wants to generate one package, it will fork the packaging utility, the packaging utility will scan the script, get the data dependency part and software dependency part, judge whether each dependency has been inside the package, and only add the new data and software into the package, and update the package information and package retrieval information.\\
-
-as for data and software, need to ensure its identity. the software version.\\
-
-benefits of this solution: time saving (there are some overlap parts between different analysis programs, especially different analysis programs of one physicist); storage space saving (overlap parts between different analysis programs).
-the fourth-version script is very instructive so that physicists can repeat one analysis program or create one new analysis program more easily and efficiently.
-this is more manageable (data software sharing)\\
-
-*****hmeng-doubt: maybe one lightweight database like sqlite, can be used to manage the metadata of data and software. \\
-
-*****hmeng-doubt: difficulties: for parrot, how to recognize the start and end points of one dataset or one software.
-because up till now, the process unit of parrot is one single file, rather one single package.\\
-
-*****hmeng-doubt: questions: how to set the unit of parrot: file or package\\
-
-*****lack: the 4th version of script (how to design the new script still needs consideration)
-
-\section{the relationship of different solutions}
-\indent The relationship of these four solutions to repeat one program is shown in Table~\ref{table:relationship}.\\
-
-\begin{table}
-    \centering
-    \begin{tabular}{|l|r|r|r|}
-        \hline
-        Solution ID & Data Resources & Software Resources & Operation Manual \\ \hline
-        1st Solution & grid & CMSSW Git HTTP & email \\ \hline
-        2nd Solution & local (HDFS) & CMSSW Git HTTP & shell script \\ \hline
-        3rd Solution & independent package & independent package & shell script + packaging utility \\ \hline
-        4th Solution & independent package & independent package & shell script + packaging utility \\ \hline
-    \end{tabular}
-    \caption{The relationship of different solutions}
-    \label{table:relationship}
-\end{table}
-
-The fourth solution should be based on the third solution.
-during the packaging process, packaging utility first checks whether the file has been inside the target package, (if exists, whether it is the latest version).
-only if the file does not exist in the target package or the file in the target package is not the latest version, the packaging utility copies the file into the target package.\\
-
-*****hmeng-doubt: potential risk: different analysis programs share some common file names, but with different file contents. we should analyze the possibility of conflict: data.\\
-
-*****hmeng-doubt: in the fourth version, let user to mark whether they change the data and software.
-if changed, one new package is generated to avoid data overlap and pollution.
-otherwise, directly starts packaging process based on the current target package.
-
-\section{comparison of the 2nd solution and the 3rd solution}
-\subsection{the breakdown of execution time of the second solution: }
-\indent according to the Table~\ref{table:time-2nd}, about half of the total execution time is consumed to prepare relevant data and software.
-
-\begin{table}
-    \centering
-    \begin{tabular}{|l|r|r|}
-    \hline
-    Sub-Task & Time & Percentage \\ \hline
-    Software preparation from CMSSW & 15min 30s & 25.27\% \\ \hline
-    Software preparation from Git & 9s & 0.24\% \\ \hline
-    Software preparation from Wget & 36s & 0.98\% \\ \hline
-    Environment Build - SCRAM & 13min 20s & 21.74\% \\ \hline
-    Environment Build - Python & 1s & 0.03\% \\ \hline
-    Data analysis & 31min 44s & 51.74\% \\ \hline
-    Total & 61min 20s & 100.00\% \\ \hline
-    \end{tabular}
-    \caption{The breakdown of execution time of the 2nd solution}
-    \label{table:time-2nd}
-\end{table}
-
-\subsection{the data size of the second solution:}
-\indent according to the data and software resources involved in this example, the size of each category is shown in Table~\ref{table:datasize-2nd}.
-
-\begin{table}
-    \centering
-    \begin{tabular}{|l|r|}
-    \hline
-    Data Category & Data Size \\ \hline
-    Software from CMSSW & 449MB \\ \hline
-    Software from Git & 61MB \\ \hline
-    Software from Wget & 52MB \\ \hline
-    Hadoop & 33TB \\ \hline
-    Total & 33792.562GB \\ \hline
-    \end{tabular}
-    \caption{The data size of the 2nd solution}
-    \label{table:datasize-2nd}
-\end{table}
-
-*****hmeng-doult: the size of hadoop need to reconsidered. how to correctly illustrate the data size of this example?
-
-\subsection{the breakdown of execution time of the third solution: }
+\subsection{Evaluation of the third solution}
 \indent The breakdown of execution time of the third solution is illustrated in Table~\ref{table:time-3rd}.
@@
 that is, once the package is generated, many users can directly obtain the package and re-execute it separately.
+\\
 
@@
 \end{table}
-
-\subsection{ the data size of the third solution}
-\indent The data size of the 3rd solution is shown in Table~\ref{table:datasize-3rd}.
+The data size of the 3rd solution is shown in Table~\ref{table:datasize-3rd}.
 The data categories is more complex than our imagination.
@@
 \end{table}
+
+\subsection{Discussion of the third solution}
+\indent benefits of this solution: the repeat of one analysis program becomes easier, which would be executed in one independent package containing all the data and software dependencies of one analysis program.
+\\
+
+rethink mathias’s example, under this solution, the repeat of it only needs the necessary environment variables, svn login,  the last command (scripts/roaster -atfpvy data/generic\_ttl.yam) and the package.
+if different scholars want to repeat one analysis program, what they need to do is to obtain the package and rerun the actual analysis program.
+under the second solution, each scholar needs to get the necessary data and software, and then prepare software environment, which is time-consuming.
+\\
+
+\section{the relationship of different solutions}
+\indent The relationship of these four solutions to repeat one program is shown in Table~\ref{table:relationship}.\\
+
+\begin{table}
+    \centering
+    \begin{tabular}{|l|r|r|r|}
+        \hline
+        Solution ID & Data Resources & Software Resources & Operation Manual \\ \hline
+        1st Solution & grid & CMSSW Git HTTP & email \\ \hline
+        2nd Solution & local (HDFS) & CMSSW Git HTTP & shell script \\ \hline
+        3rd Solution & independent package & independent package & shell script + packaging utility \\ \hline
+    \end{tabular}
+    \caption{The relationship of different solutions}
+    \label{table:relationship}
+\end{table}
+
+The fourth solution should be based on the third solution.
+during the packaging process, packaging utility first checks whether the file has been inside the target package, (if exists, whether it is the latest version).
+only if the file does not exist in the target package or the file in the target package is not the latest version, the packaging utility copies the file into the target package.\\
+
+*****hmeng-doubt: potential risk: different analysis programs share some common file names, but with different file contents. we should analyze the possibility of conflict: data.\\
+
+*****hmeng-doubt: in the fourth version, let user to mark whether they change the data and software.
+if changed, one new package is generated to avoid data overlap and pollution.
+otherwise, directly starts packaging process based on the current target package.
+
+\section{comparison of the 2nd solution and the 3rd solution}
 
@@
 \\
-\indent *****hmeng-doubt: this point is not the motivation. but one achievement comes together. out of imagination.\\
+\indent *****hmeng-doubt: this point is not the motivation. but one achievement comes together. out of imagination.
+
+\section{Discussion of data and software preservation}
+\subsection{Preservation integration of multiple programs}
+\indent The third solution can work well for the preservation and repeat of one single program.
+However, different experimenters may execute different analysis programs on the same dataset using the same or overlapping sets of software.
+Generating one new package for each analysis program from scratch is time-consuming and space-consuming, which makes one data and software preservation mechanism, that can integrate the preservation requirements of different analysis programs, become necessary.
+\\
+
+To integrate the data and software from multiple analysis programs into one package, the concrete information of data and software, such as size, version, source and the number of files, need to be recorded.
+we also need to design one more instructive shell script format, in which the data dependencies and software dependencies can be clearly expressed and recognized.
+the packaging process needs to be re-organized.
+packaging utility needs to maintain one list of current software and data subset already stored in the package.
+when one user wants to generate one package, it will fork the packaging utility, the packaging utility will scan the script, get the data dependency part and software dependency part, judge whether each dependency has been inside the package, and only add the new data and software into the package, and update the package information and package retrieval information.
+
+\subsection{Preservation granularity}
+\indent Another important factor of data and software preservation is the choice of preservation of preservation granularity.
+In the third solution, the preservation granularity is one file ,because Parrot virtual filesystem traps each system call and redirects the access path to each file.
+As a result, during the packaging process, each time only one file can be copied into the target package, which is low-efficient.
+However, there are other options of preservation granularity.
+The software is generally preserved in the unit of package inside the remote repository, the packaging process of one experiment can adopt one package as the unit.
+In addition, if the size of one whole software repository is reasonable and the access frequency of each package of it is high, the granularity can be set to the whole repository.
+
+\subsection{The user access model of data and software}
+\indent Through this case study, we notice that the user access module of remote data and software has a great impact of the preservation mechanism, especially when we try to integrate the preservation of multiple programs.
+If all the programs only refer the original data and software and refuse to modify it, the preservation is easy and can ignore the data version problem.
+However, if each program tries to modify the original data and software to accustom to its own requirement, the preservation mechanism must provide one way to differentiate the original data version and the special data version of one certain program.
+To have a clear understanding of the data access model, more examples need to be investigated.
 

### 2014-01-16 paper.tex
First HEP meeting

@@
 \subsection{Background}
-Matthias, one guy from physics department, finished one interesting tau analysis. We want to understand how the tau analysis works and repeat it.
+Matthias, one graduate student from Physics Department of University of Notre Dame, finished one interesting tau analysis. We want to understand how the tau analysis works and repeat it.
 
-\subsection{This workflow of the example}
+\subsection{Workflow of Matthias's Example}
 Declare environment variables
@@
 
-\subsection{the source and size of experiment data and software}
-We notice that the software sources are rich, including cmssw, hadoop, grid, git, http and one personal main page. The size of experiment data and software is large.
+\subsection{Source and Size of Data and Software}
+We notice that the software sources are rich, including CMSSW, Git, HTTP and one personal main page. The size of software from each source is shown in Table~\ref{table:software-source-size}.
 
-As for the experiment data, Matthias copies the subset of T3 data from grid and stores the data into HDFS mounted as one local file system. The total size of data stored in HDFS is 33TB.
-
-The source and size of software are shown in Table~\ref{table:software-source-size}.
+As for the experiment data, Matthias copies the subset of T3 data from grid and stores the data into HDFS mounted as one local file system.
+The total size of data stored in HDFS is 33TB (*need to rethink).
 
@@
     \end{tabular}
-    \caption{Source and size of software}
+    \caption{Source and Size of Software}
     \label{table:software-source-size}
@@
         \hline
-        First version \\ \hline
+        Version 1\\ \hline
         \\
@@
         \\ \hline
-        Second version \\ \hline
+        Version 2\\ \hline
         \\
@@
         \\ \hline
-        Third version \\ \hline
+        Version 3\\ \hline
         \\
@@
         \\ \hline
-        Fourth version \\ \hline
+        Version 4\\ \hline
         \\
@@
 
-\section{First solution to repeat the program}
+\section{Solution 1 to Repeat the Program}
 In order to repeat Matthais's example, the new user consulted the original author by email about the necessary work for the experiment.
 In response, Matthias introduced the general workflow of his tau analysis through one long email including notes, linux shell commands, web links.
-The First version of Table~\ref{table:scripts} illstrates Matthias's example.
+The First version of Table~\ref{table:scripts} illstrates his email.
 
@@
 For example, the original email refers to one environment variable called CMSSW\_base without clear declaration, the new user needs to send one email to the original writer to obtain its accurate value.
-Secondly, the necessary procedure to repeat the experiment, including softwares from different sources, is complex for the new user.
-In Matthias's example, the sources of software includes CMSSW, GIT, HTTP.
+Secondly, the necessary procedure to repeat the experiment, including software acquisition from different sources, is complex for the new user.
+In Matthias's example, the sources of software includes CMSSW, Git, HTTP.
 The access of CMSSW requires the new user be an authorized user of CMSSW.
-What's more, some parts of the workflow is unrepeatible.
-The third step of this experiment requires the new user owning the access authority for grid.
+What's more, some parts of the workflow are unrepeatible.
+The third step of this experiment requires the new user owning the access authority to the Grid.
 
-Implication: Directly repeating the experiment using the published workflow and results by the original author is complex and even difficulty.
-Some extra work must be done to make the repeating process easier.
+Implication: Directly repeating the experiment using the workflow and results by the original author is complex and difficult. Some extra work must be done to make the reproduction process easier.
 
-\section{second solution to repeat the program}
+\section{Solution 2 to Repeat the Program}
 One possible solution for the access authority problem of grid data is to grant the new user the authority to access gird data directly.
@@
 
-To test out these possible solutions, we integrate the content of all the notes, commands and web links involved in the emails into one neat, complete shell script, which begins with the definition of environment variables, then data obtainance from grid, software obtainance from cmssw, git and other web resources, and software installation, ends with the execution of the actual analysis program.
-The Second version of Table~\ref{table:scripts} illstrates the merged script.
-As for the data obtainance from grid, we directly use the local copy in hdfs to avoid the new user to obtain the grid certification.
+To test out these possible solutions, we integrate the content of all the notes, commands and web links involved in the emails into one neat, complete shell script, which begins with the definition of environment variables, software acquisition from CMSSW, Git and other web resources, and software installation, ends with the execution of the actual analysis program.
+Version 2 of Table~\ref{table:scripts} illstrates the merged script.
+As for the data acquisition from the Grid, we directly use the local copy in HDFS to avoidrequiring the new user to obtain a grid certification.
 
-The breakdown of execution time of the second solution is shown in Table~\ref{table:time-2nd}.
-According to Table~\ref{table:time-2nd}, about half of the total execution time is consumed to prepare relevant data and software.
+The breakdown of execution time of Solution 2 is shown in Table~\ref{table:time-2nd}.
+According to Table~\ref{table:time-2nd}, about half of the total execution time is consumed to prepare relevant software environment.
 
@@
     \end{tabular}
-    \caption{The breakdown of execution time of the 2nd solution}
+    \caption{Breakdown of Execution Time of Solution 2}
     \label{table:time-2nd}
@@
 
-According to the data and software resources involved in this example, the size of each category is shown in Table~\ref{table:datasize-2nd}.
+The size of data and software from each category is shown in table~\ref{table:datasize-2nd}.
 
@@
     \end{tabular}
-    \caption{The data size of the 2nd solution}
+    \caption{Data Size of Solution 2}
     \label{table:datasize-2nd}
@@
 
-*****hmeng-doult: the size of hadoop need to reconsidered. how to correctly illustrate the data size of this example?
+%*****hmeng-doult: the size of hadoop need to reconsidered. how to correctly illustrate the data size of this example?
+Because the script includes all the necessary procedures for the reproduction of one analysis program, the readability and friendliness of this solution is higher than that of the email format.
+However, each execution of the script will involve the acquisition of software from different sources and the building of software environment.
+As for accessing grid data, using the data copy stored in the machine where Matthias executed the experiment requires the new user to have the authority to access the machine, which complicates the management of the original machine, even is impossible if the original machine executes rigid user access control.
+Granting everyone who wants to repeat the analysis the access authority for grid is unacceptable to system administrator.
 
-Because the script includes all the necessary procedures for the repeat of one analysis program, the readability and friendliness of this solution is higher than that of the email format.
-However, each execution of the script will involve the obtainance of software from different sources and the building of software environment.
-As for the access problem of grid data, using the data copy stored in the machine where mathias executed the experiment requires the new user have the authority to access the machine, which complicates the management of the original machine, even is impossible if the original machine executes rigid user access control.
-Granting everyone who wants to repeat the analysis the access authority for grid (grid certificate) is wasteful and unsafe.
+Implication: All the data and software involved in the experiment should be provided to the new user in the format of one self-contained package so that the multiple execution of the experiment from the same user only involve one time of data and software acquisition and environment building process.
+In addition, the requirement of the underlying OS and hardware should also be provided to the new user.
 
-Implication: All the data and software involved in the experiment should be provide to the new user in the format of one static package so that the multiple execution of the experiment from the same user only involve one time of data obtainance and software obtainance and compiling.
-In addition, the requirement of the underlying OS and hardware should also be provided to the new users.
+\section{Solution 3 to Repeat the Program}
+\subsection{Working principle of Packaging Utility}
+The difficulty of data access authority acquisition enforces us to find out one solution, in which the reproduction of the original analysis can be done without any external dependency.
+That is, one independent and self-contained package containing all the data and software dependencies is necessary.
+Someone may suggest that it should be the responsibility of the original author to generate the required package.
+However, letting the original author to provide the package which can be used by others to repeat the original experiment is unrealistic.
+One reason is that figuring out the underlying dependency of each software is complex and time-consumpting and even impossible for the original author.
+In this experiment, the machine used for the experiment is one public machine of physics department, and Matthias is one common user without root authority.
+The underlying OS and supporting softwares are installed and maintained by the IT department of the university.
+On the other hand, the architecture design of the required package including all the data and software dependencies is not under the research field of physists.
 
-\section{third solution to repeat the program}
-\subsection{Working principle of packaging utility}
-The difficulty of data access authority obtainance enforces us to find out one independent solution, in which the repeat of the original analysis can be done without any external dependency.
-that is, one independent and self-contained package containing all the data and software dependencies is necessary.
-Someone may suggest that it should be the responsibility of the original author to generate the required package.
-However, letting the original author to provide the package which can be used by other scholars to repeat the original experiment is unrealistic.
-One reason for this is that figuring out the underlying dependency of each software is complex and time-consumpting and even impossible for the original author.
-In this experiment, the machine used for the experiment is one public machine of physics department, and Matthias is one common user without root authority.
-All the underlying OS and supporting softwares are installed and maintained by the IT department of the university.
-On the other hand, the architecture design of the required package including all the data and software dependencies is not under the research range of physists.
-
-Parrot is a virtual filesystem access tool which attaching existing programs to a variety of remote I/O systems including http, ftp, gridftp, irods, hdfs, xrootd, grow and chirp.
+Parrot is a virtual filesystem access tool which attaching existing programs to a variety of remote I/O systems including http, ftp, gridftp, irods, HDFS, xrootd, grow and chirp.
 it traps all system calls of one program through ptrace debugging interface, and replaces them with remote I/O operations as desired.
@@
 
-With the help of parrot, one packaging utility which generates one independent package for one program to make the repeat of the program convenient can be deployed.
-the basis of the packaging utility is one successful execution sandbox (the data from grid has been preserved in hdfs and the software from cmssw, git and http has been on the local machine.).
-we re-execute the actual data analysis code (shown in "the script of the third solution") under parrot and get the name list of all the files actually accessed during the execution process of the actual data analysis.
-then, according to the file name list, one package containing all the necessary data and software for one analysis program is generated.
-next time, when another scholar wants to repeat the program, he only needs to obtain the package and directly execute the actual analysis program inside the package.\\
+With the help of parrot, one packaging utility which generates one independent package for one program to make the reproduction of the program convenient can be deployed.
+The basis of the packaging utility is one successful execution sandbox (the data from grid has been preserved in HDFS and the software from CMSSW, Git and HTTP has been on the local machine.).
+We re-execute the actual data analysis code under Parrot and get the name list of all the files actually accessed during the execution process of the actual data analysis.
+Then, according to the file name list, one package containing all the necessary data and software for one analysis program is generated.
+Next time, when another scholar wants to repeat the program, he only needs to obtain the package and directly execute the actual analysis program inside the package.
 
-The shell script of the second solution is simplified into one new version, which only contains the necessary environment variables, access authority and the actual analysis command.
-The Third version of Table~\ref{table:scripts} illustrates the simplified script.
+The shell script of the Solution 2 is simplified into one new version, which only contains the necessary environment variables, access authority and the actual analysis command.
+The Version 2 of Table~\ref{table:scripts} illustrates the simplified script.
 
-\subsection{Workflow of packaging utility}
+\subsection{Workflow of Packaging Utility}
 The workflow of generating one package for one analysis program is as follows:
 
-(1) execute one analysis program under parrot and obtain filename list (L1) of it
+(1) execute one analysis program under Parrot and obtain filename list (L1) of it
 
 Parrot is one virtual file system that can support user access to multiple underlying file systems.
-parrot traps each system call involved in the process of data access, figures out the type of file system and redirects it into corresponding operations to the accessed file system.
-during this process, each accessed file is recorded into one file with the access type of it, such as open, stat, read and write.
+Parrot traps each system call involved in the process of data access, figures out the type of file system and redirects it into corresponding operations to the accessed file system.
+During this process, each accessed file is recorded into one file with the access type of it, such as open, stat, read and write.
 
-command:
+Command:
 
@@
 
-namelist size: 5.7mb     128711 lines
+Output:
+namelist size: 5.7MB     128711 lines
 
-de-duplicated namelist size: 2.2mb   42385 lines
+de-duplicated namelist size: 2.2MB   42385 lines
 
@@
 The packaging utility iterates each filename inside L1 and copies it into the target package.
-after completing the packaging process, the target package together with its information, and one mountlist, which redirects the access of data from different file systems into the target package, will be provided to users.
+After completing the packaging process, the target package together with its description information, and one mountlist, which redirects the access of data from different file systems into the target package, will be provided to users.
+The packaging process also runs within Parrot environment to access data from different file systems.
 
-The packaging process also runs within parrot environment to access data from different file systems.
+Command:
 
-command:
-
-/bin/bash package1-4.sh -l ~/namelist
+parrot\_run /bin/bash package1-4.sh -l ~/namelist
 
@@
 
-the total size of package is: 21g
+the total size of package is: 21GB
 
@@
 
-*****lack: file content + metadata; only file metadata; different process solutions
+%*****lack: file content + metadata; only file metadata; different process solutions
+Each file inside L1 is copied into the package, the final path of the file becomes the path of the package, followed by the original file path.
+In this program, the path of the package is /tmp/package1-4, so the final path of one file with the original path path1 is /tmp/package1-4/path1.
 
-The structure of the generated package is as follows.
-each file inside l1 is copied into the package, the final file path becomes the path of the package, followed by the original file path.
-in this program, the path of the package is /tmp/package1-4, so the final path of one file with the original path path1 is /tmp/package1-4/path1.
+To ensure the successful reproduction, the filesystem structure of the original execution environment should be preserved as completely as possible.
+However, attempting to copy the whole content of one directory or one file is space-consuming and time-consuming, because the original program may only access the metadata of one directory with the size of 200GB.
+our solution is to determine the copy degree of one directory or one common file according to the system call type for its path.
 
-To ensure the successful reproductivity, the filesystem structure of the original execution environment should be preserved as completely as possible.
-however, attempting to copy the whole content of one directory or one file is space-consuming and time-consuming, because the original program may only access the metadata of one directory with the size of 200gb.
-our solution is to determine the copy degree of one directory or one common file according to the system call type for each file.
-
-The map relationship between the file access path inside the actual analysis program and the actual file location is kept inside the mountlist file. the structure of the mountlist is as follows:
+The map relationship between the file access path used in the actual analysis program and the actual file location used during the reproduction process is kept inside the mountlist file.
+the structure of the mountlist is as follows:
 
@@
 
-*****lack: re-execute process: re-execution process will redirect all the data access into the package except for data under proc sys dev selinux
-
+%*****lack: re-execute process: re-execution process will redirect all the data access into the package except for data under proc sys dev selinux
 (3) rerun the analysis program using the package
@@
 
-command:
+Command:
 
@@
 
-\subsection{Evaluation of the third solution}
-The breakdown of execution time of the third solution is illustrated in Table~\ref{table:time-3rd}.
-the time used to obtain file namelist and generate p1 is greatly longer than the execution time within the new package.
-however, the time consumption of file namelist obtainance and package generation is one-time.
-that is, once the package is generated, many users can directly obtain the package and re-execute it separately.
+\subsection{Evaluation of Solution 3}
+The breakdown of execution time of the Solution 3 is illustrated in Table~\ref{table:time-3rd}.
+The time used to obtain file namelist and generate P1 is greatly longer than the execution time within the new package.
+however, the time consumption of file namelist acquisition and package generation is one-time.
+That is, once the package is generated, many users can directly obtain the package and repeat the experiment separately.
 
@@
     \end{tabular}
-    \caption{The time breakdown of the 3rd solution}
+    \caption{Time Breakdown of Solution 3}
     \label{table:time-3rd}
@@
 
-The data size of the 3rd solution is shown in Table~\ref{table:datasize-3rd}.
+The data size of Solution 3 is shown in Table~\ref{table:datasize-3rd}.
 The data categories is more complex than our imagination.
-Except the experimental data stored in Hadoop and the software stored in CMSSW\_5\_3\_11\_patch3, files from /usr /lib /bin and other paths are also necessary for the execution of the program.
+Except the data stored in Hadoop and the necessary set of software, files from /sbin, /bin and other paths are also necessary for the reproduction of the program.
 
@@
     \hline
-    Data Category & Data size \\ \hline
+    Data Category & Data Size \\ \hline
     Hadoop & 20GB \\ \hline
@@
     \end{tabular}
-    \caption{The data size of the 3rd solution}
+    \caption{Data Size of Solution 3}
     \label{table:datasize-3rd}
@@
 
-\subsection{Discussion of the third solution}
-benefits of this solution: the repeat of one analysis program becomes easier, which would be executed in one independent package containing all the data and software dependencies of one analysis program.
+\subsection{Discussion of Solution 3}
+Under Solution 3, the reproduction of one analysis program becomes easier.The namespace of repeating one experiment will be limited into one independent package containing all the data and software dependencies of one analysis program.
 
-rethink mathias's example, under this solution, the repeat of it only needs the necessary environment variables, svn login,  the last command (actual analysis command) and the package.
-if different scholars want to repeat one analysis program, what they need to do is to obtain the package and rerun the actual analysis program.
-under the second solution, each scholar needs to get the necessary data and software, and then prepare software environment, which is time-consuming.
-
-\section{the relationship of different solutions}
-The relationship of these four solutions to repeat one program is shown in Table~\ref{table:relationship}.
+Rethink Matthias's example, under Solution 3, the reproduction of it only needs the necessary environment variables, svn login,  the actual analysis command and the package.
+If different scholars want to repeat one analysis program, what they need to do is to obtain the package and rerun the actual analysis program.
+Under Solution 2, each scholar needs to get the necessary data and software, and then prepare software environment.
 
@@
         Solution ID & Data Resources & Software Resources & Operation Manual \\ \hline
-        1st Solution & grid & CMSSW Git HTTP & email \\ \hline
-        2nd Solution & local (HDFS) & CMSSW Git HTTP & shell script \\ \hline
-        3rd Solution & package & package & shell script + packaging utility \\ \hline
+        Solution 3& grid & CMSSW Git HTTP & email \\ \hline
+        Solution 3& local (HDFS) & CMSSW Git HTTP & shell script \\ \hline
+        Solution 3& package & package & shell script + packaging utility \\ \hline
     \end{tabular}
@@
 
-The fourth solution should be based on the third solution.
+%The fourth solution should be based on the third solution.
 during the packaging process, packaging utility first checks whether the file has been inside the target package, (if exists, whether it is the latest version).
@@
 
-*****hmeng-doubt: potential risk: different analysis programs share some common file names, but with different file contents. we should analyze the possibility of conflict: data.
+%*****hmeng-doubt: potential risk: different analysis programs share some common file names, but with different file contents. we should analyze the possibility of conflict: data.
 
-*****hmeng-doubt: in the fourth version, let user to mark whether they change the data and software.
+%*****hmeng-doubt: in the fourth version, let user to mark whether they change the data and software.
 if changed, one new package is generated to avoid data overlap and pollution.
 otherwise, directly starts packaging process based on the current target package.
+\section{Comparison of different Solutions}
+\subsection{Relationship of Different Solutions}
+The relationship of these four solutions to repeat one program is shown in Table~\ref{table:relationship}.
 
-\section{comparison of the 2nd solution and the 3rd solution}
-\subsection{ Data size comparison of 2nd and 3rd solution}
+\subsection{ Data size Comparison of Solution 2 and 3}
 The packaging utility checks the system call of each file within the namelist, and maintains the minimum dataset, which makes the size of the final package is as small as possible.
-The total size of Hadoop under the second solution is astonished, while the size of Hadoop under the package is decreased to 20GB.
+The total size of Hadoop under Solution 2 is astonishing, while the size of Hadoop under the package is decreased to 20GB.
 The same trend applies to the size of CMSSW\_5\_3\_11\_patch3.
-Because the packaging utility tries to construct one independent and self-contained package, necessary files  from /usr, /bin, /lib are also copied into the package and denoted as "Data necessary for Package" in the Table~\ref{table:datasize-2nd3rd}.
+Because the packaging utility tries to construct one independent and self-contained package, necessary files  from /sbin, /lib and other directories are also copied into the package and denoted as "Other data for Package" in the Table~\ref{table:datasize-2nd3rd}.
 
@@
     \hline
-     Data Category & Data size & Data size \\
-    & 2nd solution & 3nd solution \\ \hline
+     Data Category & Data Size & Data Size \\
+    & Solution 2 & Solution 3\\ \hline
     Hadoop & 33TB = 33792GB & 20GB \\ \hline
@@
     \end{tabular}
-    \caption{Data size comparison beweeen second solution and third solution}
+    \caption{Data Size Comparison beweeen Solution 2 and 3}
     \label{table:datasize-2nd3rd}
@@
 
-\subsection{Execution time comparison of 2nd and 3rd solution}
-Table~\ref{table:time-2nd3rd} shows the execution time comparison between the 2nd solution and the 3rd solution.
-The time consumption of the repeat of one program from different scholars kept the same under the second solution, including software and data preparation.
-However, under the third solution, the data and software preparation is one-time.
-All the following repeat of the same program only need to obtain one copy of the package and execute the actual experimental analysis directly.
+\subsection{Execution Time Comparison of Solution 2 and 3}
+Table~\ref{table:time-2nd3rd} shows the execution time comparison between Solution 2 and 3.
+The time consumption of the reproduction of one program from different scholars kept the same under Solution 2, including software and data preparation.
+However, under Solution 3, the data and software preparation is one-time.
+The following reproduction of the same program only needs to obtain one copy of the package and execute the actual experimental analysis directly.
 
@@
     \hline
-    Task Category & execution time & execution time \\
-    & 2nd solution & 3rd solution \\ \hline
+    Task Category & Execution Time & Execution Time \\
+    & Solution 2 & Solution 3\\ \hline
     Software Acquisition & 16min 15s & N/A \\ \hline
@@
     \end{tabular}
-    \caption{Execution time comparison between second and third solution}
+    \caption{Execution Time Comparison between Solution 2 and 3}
     \label{table:time-2nd3rd}
@@
 
-*****hmeng-doubt:Another reason for the packaging utility is that not all the data and software generated by the second version script is used during the the actual data analysis.
+%*****hmeng-doubt:Another reason for the packaging utility is that not all the data and software generated by the second version script is used during the the actual data analysis.
 The packaging utility can help us find out the optimal subset of data and software involved in one actual data analysis.
-
-*****hmeng-doubt: this point is not the motivation. but one achievement comes together. out of imagination.
-
-\section{Discussion of data and software preservation}
-\subsection{Preservation integration of multiple programs}
-The third solution can work well for the preservation and repeat of one single program.
+%*****hmeng-doubt: this point is not the motivation. but one achievement comes together. out of imagination.
+\section{Discussion of Data and Software Preservation}
+\subsection{Preservation Integration of Multiple Programs}
+The Solution 3 can work well for the preservation and reproduction of one single program.
 However, different experimenters may execute different analysis programs on the same dataset using the same or overlapping sets of software.
@@
 we also need to design one more instructive shell script format, in which the data dependencies and software dependencies can be clearly expressed and recognized.
-the packaging process needs to be re-organized.
+The packaging process needs to be re-organized.
 packaging utility needs to maintain one list of current software and data subset already stored in the package.
-when one user wants to generate one package, it will fork the packaging utility, the packaging utility will scan the script, get the data dependency part and software dependency part, judge whether each dependency has been inside the package, and only add the new data and software into the package, and update the package information and package retrieval information.
+When one user wants to generate one package, it will fork the packaging utility, the packaging utility will scan the script, get the data and software dependency part, judge whether each dependency has been inside the package, and only add the new data and software into the package, and update the package information and relavant retrieval information.
 
-\subsection{Preservation granularity}
-Another important factor of data and software preservation is the choice of preservation of preservation granularity.
-In the third solution, the preservation granularity is one file ,because Parrot virtual filesystem traps each system call and redirects the access path to each file.
+\subsection{Preservation Granularity}
+Another important factor of data and software preservation is the choice of preservation granularity.
+In Solution 3, the preservation granularity is one file, because Parrot virtual filesystem traps each system call and redirects the access path to each file.
 As a result, during the packaging process, each time only one file can be copied into the target package, which is low-efficient.
@@
 The software is generally preserved in the unit of package inside the remote repository, the packaging process of one experiment can adopt one package as the unit.
-In addition, if the size of one whole software repository is reasonable and the access frequency of each package of it is high, the granularity can be set to the whole repository.
+In addition, if the size of one whole software repository is small and the access frequency of each package inside it is high, the granularity can be set to the whole repository.
 
-\subsection{The user access model of data and software}
+\subsection{User Access Model of Data and Software}
 Through this case study, we notice that the user access module of remote data and software has a great impact of the preservation mechanism, especially when we try to integrate the preservation of multiple programs.
-If all the programs only refer the original data and software and refuse to modify it, the preservation is easy and can ignore the data version problem.
-However, if each program tries to modify the original data and software to accustom to its own requirement, the preservation mechanism must provide one way to differentiate the original data version and the special data version of one certain program.
+If all the programs only refer the original data and software and refuse to modify them, the preservation is easy and can ignore the data version problem.
+However, if each program tries to modify the original data and software to accustom to its own requirement, the preservation mechanism must provide one way to differentiate the original data version and the special data version used in one certain program.
 To have a clear understanding of the data access model, more examples need to be investigated.

### 2014-01-16 paper.tex
Removed junk at top.
Reworked the first page.

@@
-% THIS IS SIGPROC-SP.TEX - VERSION 3.1
-% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
-% APRIL 2009
-%
-% It is an example file showing how to use the 'acm_proc_article-sp.cls' V3.2SP
-% LaTeX2e document class file for Conference Proceedings submissions.
-% ----------------------------------------------------------------------------------------------------------------
-% This .tex file (and associated .cls V3.2SP) *DOES NOT* produce:
-%       1) The Permission Statement
-%       2) The Conference (location) Info information
-%       3) The Copyright Line with ACM data
-%       4) Page numbering
-% ---------------------------------------------------------------------------------------------------------------
-% It is an example which *does* use the .bib file (from which the .bbl file
-% is produced).
-% REMEMBER HOWEVER: After having produced the .bbl file,
-% and prior to final submission,
-% you need to 'insert'  your .bbl file into your source .tex file so as to provide
-% ONE 'self-contained' source file.
-%
-% Questions regarding SIGS should be sent to
-% Adrienne Griscti ---> griscti@acm.org
-%
-% Questions/suggestions regarding the guidelines, .tex and .cls files, etc. to
-% Gerald Murray ---> murray@hq.acm.org
-%
-% For tracking purposes - this is V3.1SP - APRIL 2009
-
 \documentclass{acm_proc_article-sp}
@@
 \title{A Case Study in Preserving a High Energy Physics Application}
-%
-% You need the command \numberofauthors to handle the 'placement
-% and alignment' of the authors beneath the title.
-%
-% For aesthetic reasons, we recommend 'three authors at a time'
-% i.e. three 'name/affiliation blocks' be placed beneath the title.
-%
-% NOTE: You are NOT restricted in how many 'rows' of
-% "name/affiliations" may appear. We just ask that you restrict
-% the number of 'columns' to three.
-%
-% Because of the available 'opening page real-estate'
-% we ask you to refrain from putting more than six authors
-% (two rows with three columns) beneath the article title.
-% More than six makes the first-page appear very cluttered indeed.
-%
-% Use the \alignauthor commands to handle the names
-% and affiliations for an 'aesthetic maximum' of six authors.
-% Add names, affiliations, addresses for
-% the seventh etc. author(s) as the argument for the
-% \additionalauthors command.
-% These 'additional authors' will be output/set for you
-% without further effort on your part as the last section in
-% the body of your article BEFORE References or any Appendices.
-
-\numberofauthors{6} %  in this sample file, there are a *total*
-% of EIGHT authors. SIX appear on the 'first-page' (for formatting
-% reasons) and the remaining two appear in the \additionalauthors section.
-%
 \author{
-% You can go ahead and credit any number of authors here,
-% e.g. one 'row of three' or two rows (consisting of one row of three
-% and a second row of one, two or three).
-%
-% The command \alignauthor (no curly braces needed) should
-% precede each author name, affiliation/snail-mail address and
-% e-mail address. Additionally, tag each line of
-% affiliation/address with \affaddr, and tag the
-% e-mail address with \email.
-%
-% 1st. author
-\alignauthor
-Haiyan Meng\\
-    \affaddr{Department of Computer Science and Engineering}\\
+Haiyan Meng, Matthias Wolf, Peter Ivie, Anna Woodard, Michael Hildreth, and Douglas Thain\\
+\affaddr{Department of Physics and Department of Computer Science and Engineering}\\
 \affaddr{University of Notre Dame}\\
-    \affaddr{Notre Dame, Indiana}\\
-    \email{hmeng@nd.edu}
-% 2nd. author
-\alignauthor
-Matthias Wolf\\
-    \affaddr{Department of Physics}\\
-    \affaddr{University of Notre Dame}\\
-    \affaddr{Notre Dame, Indiana}\\
-    \email{mwolf3@nd.edu}
-% 3rd. author
-\alignauthor
-Anna Woodard\\
-    \affaddr{Department of Physics}\\
-    \affaddr{University of Notre Dame}\\
-    \affaddr{Notre Dame, Indiana}\\
-    \email{awoodard@nd.edu}
-\and  % use '\and' if you need 'another row' of author names
-% 4th. author
-\alignauthor 
-Peter Ivie\\
-    \affaddr{Department of Computer Science and Engineering}\\
-    \affaddr{University of Notre Dame}\\
-    \affaddr{Notre Dame, Indiana}\\
-    \email{pivie@nd.edu}
-% 5th. author
-\alignauthor 
-Michael Hildreth\\
-    \affaddr{Department of Physics}\\
-    \affaddr{University of Notre Dame}\\
-    \affaddr{Notre Dame, Indiana}\\
-    \email{Michael.D.Hildreth.2@nd.edu}
-% 6th. author
-\alignauthor 
-Douglas Thain\\
-    \affaddr{Department of Computer Science and Engineering}\\
-    \affaddr{University of Notre Dame}\\
-    \affaddr{Notre Dame, Indiana}\\
-    \email{dthain@nd.edu}
+\affaddr{\{hmeng|mwolf3|awoodard|pivie|mhildreth|dthain\}@nd.edu}
 }
@@
 \maketitle
+
 \begin{abstract}
@@
 % A category with the (minimum) three required fields
-\category{H.4}{Information Systems Applications}{Miscellaneous}
+%\category{H.4}{Information Systems Applications}{Miscellaneous}
 %A category including the fourth, optional field follows...
-\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]
+%\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]
 
-\terms{Theory}
-
-\keywords{ACM proceedings, \LaTeX, text tagging} % NOT required for Proceedings
+%\terms{Theory}
 
 \section{Introduction}
-...
+
+Reproducibility is a cornerstone of the scientific process.
+In order to understand, verify, and build upon previous work,
+one must be able to first recreate previous results by applying
+the same methods. Historically, reproducibility this has been
+accomplished through painstaking detailed documentation recorded
+in lab notebooks, which are then summarized in peer-reviewed publications.
+But as science increasingly depends on computation,
+reproducibility must also encompass the environments, data, and software
+involved in each result. It is widely recognized that informal
+descriptions of software and systems -- although common -- are insufficient
+for reproducing a computational result accurately.
+A more automated and comprehensive approach is required.
+
+The overall reproduction of a computation has three broad components,
+each of which suggests somewhat different approaches:
+
+\begin{itemize}
+\item The {\bf computing environment}, consisting of the basic hardware and the operating system can be preserved as physical artifacts or as a combination of virtual machine monitor (hardware) and virtual machine image (operating system).
+\item The {\bf scientific data} to be analyzed has historically received the most attention for curation.
+In a large, well-organized project, it may be stored in a  data repository or database management system, with associated documentation and a curation strategy.
+In a small effort, it could simply be a handful of files.
+\item The {\bf software environment} includes the source code, binaries, scripts, configuration files, and everything else needed to execute the desired code.
+As with data, the software could be drawn from a well-managed software repository, or it could be a handful custom scripts that exist in the user's home directory.
+\end{itemize}
+
+In a very abstract sense, reproducing a computation is trivial.
+Assuming a computation is deterministic, one must simply
+preserve all of the inputs to a computation, then re-run
+the same code in an equivalent environment, and the same result
+will be produced.  For a small custom application on a modest
+amount of data, this could be accomplished by capturing the environment,
+data, and software within a single virtual machine image,
+and then depositing the virtual
+it into a curated environment.  The publication could
+then simply refer to the identifier of the image, which the
+interested reader can obtain and re-use.  This approach has
+been used to some success with systems X, Y, and Z.
+\footnote{Of course, we are glossing over the problem that hardware
+architectures and virtual machines also change, so one must also
+preserve the VMM software necessary to run the image.  The VMM itself
+depends on a software environment which must also be preserved.
+A long-term preservation system might end up running a whole
+stack of nested virtual machines in order to provide the desired
+environment! }
+
+However, this simple approach is not sufficient for large applications
+that are run in complex social environments.
+
+\begin{itemize}
+\item There may be {\bf implicit dependencies} on items that are
+not apparent to the end user.  For example, they may understand that
+they rely on a particular data analysis package, but would have
+no reason to know that the package has further dependencies on
+other libraries and configuration files.  Or, they may know that
+the computation only runs correctly on a particular machine, but
+not know this is because it relies on data in a filesystem that
+is mounted only on that machine.
+
+\item The {\bf granularity} of the dependencies may not be well understood.
+For example, the user may understand that a computation depends upon
+a data collection that is 1TB in overall size, but not have detailed
+knowledge that it only requires three files totalling 300MB out of that
+whole collection
+
+\item There may be dependencies upon {\bf networked resources} that
+are inherently external to the system, such as a database, a code
+repository, or a scalable filesystem.  For such resources, it
+must be decided whether the dependency will simply be noted, or if it
+must be incorporated whole or in part.
+
+\item Where {\bf common dependencies} are widely used, it may be ineffecient or
+impossible to store one copy of each dependency for each archived object.
+Some form of sharing or de-duplication is necessary in order to keep
+the archive to a reasonable size.
+\end{itemize}
+
+In this paper, we demonstrate many of these difficulties by presenting
+a case study of a high energy physics application, considered from
+the perspective of preservation.  The application is presented to us
+first in the form of an email that describes in prose how to install
+the software and run the analysis.  We perform several successive
+refinements to convert it into an executable and preservable object.
+Then, we develop three techniques for observing and capturing the
+dependencies associated with the system, comparing the cost of capture,
+the size of the preserved object, and the flexibility of the resulting
+object.  We conclude with some reflections on the challenges of preservation
+and advice for future efforts.
+
 \section{Introduction of the exmaple}

### 2014-01-17 paper.tex
Give an introduction to the tau analysis.
A high-level, more abstract view of our concept of data analysis.  May need
more refinement.

@@
 \usepackage{url}
+\usepackage{siunitx}
 \begin{document}
@@
 Matthias, one graduate student from Physics Department of University of Notre Dame, finished one interesting tau analysis. We want to understand how the tau analysis works and repeat it.
+
+Within the ongoing investigation of the Higgs boson at the CMS
+detector, part of the LHC at CERN, the Higgs production in association
+with two top quarks allows to measure the Higgs coupling strength to
+top quarks.  As the Higgs boson cannot be detected itself, it has to
+be reconstructed from its decay products.  The analysis discussed in
+this section focuses on the Higgs decaying to two tau leptons, which
+are reconstructed from particle showers.
+
+The CMS collaboration provides analysis end-users with a pre-processed
+and reduced data format, AOD, containing information for events, i.e.,
+proton-proton collisions with a signature of interest, in the form of
+reconstructed particles.  This format is based on the RAW output of
+the CMS detector readout electronics and reconstructed world-wide.
+Both real and simulated data are available for examination.
+
+As AOD data are too large to be iteratively processed repetitively in
+an physics analysis workflow, it is normally reduced further in
+structural complexity and content.  For the analysis under
+investigation here, this is a two-step process.  First, the AOD data
+are processed at the Notre Dame working group cluster to BEAN events,
+containing only trivial data containers packed in vectors.  This step
+is time and CPU intensive and contains data of \SI{11.6}{TB} to be
+analyzed by the tau analysis.  The BEAN format and data is shared
+within the analysis group looking at Higgs production in association
+with top quarks, which is formed by groups from a few American and
+European universities.
+
+In the second step, which is the beginning of the actual tau analysis,
+the data are reduced to variables relevant to the tau analysis, while
+only events matching basic quality criteria are kept.  This results in
+a dataset of \SI{43.3}{GB}.  Again, the Notre Dame CMS groups cluster
+resources are used to perform this reduction and selection, with
+highly customized software.
+
+The final data analysis, investigated below, can be run as a single
+process, and contains a stringent event selection to keep only high
+quality candidate events for the underlying physical process (using
+\SI{122}{MiB} of space).  Quantities from the selected events can be
+both plotted and used in multivariate analysis to determine the level
+of expected signal in real data.
+
+% FWIW, units are TB, GB, not TiB, GiB!
 

### 2014-01-17 paper.tex
Expand a bit on the analysis purpose.

@@
 with two top quarks allows to measure the Higgs coupling strength to
-top quarks.  As the Higgs boson cannot be detected itself, it has to
-be reconstructed from its decay products.  The analysis discussed in
-this section focuses on the Higgs decaying to two tau leptons, which
-are reconstructed from particle showers.
+top quarks.  As the Higgs boson is to short-lived to be detected
+itself, it has to be reconstructed from its decay products.  The
+analysis discussed in this section focuses on the Higgs decaying to
+two tau leptons, which are themselves reconstructed from particle
+showers.  Within the analysis, events are identified that show a
+signature of decay products compatible with both hadronic tau and top
+decays.  Properties of such events are used to distinguish signal-like
+(matching simulated Higgs decays) and background-like events and are
+also used in further statistical analysis.
 

### 2014-01-17 paper.tex
Remove SIunitx dependency.

@@
 \usepackage{url}
-\usepackage{siunitx}
 \begin{document}
@@
 containing only trivial data containers packed in vectors.  This step
-is time and CPU intensive and contains data of \SI{11.6}{TB} to be
+is time and CPU intensive and contains data of 11.6$\,$TB to be
 analyzed by the tau analysis.  The BEAN format and data is shared
@@
 only events matching basic quality criteria are kept.  This results in
-a dataset of \SI{43.3}{GB}.  Again, the Notre Dame CMS groups cluster
+a dataset of 43.3$\,$GB.  Again, the Notre Dame CMS groups cluster
 resources are used to perform this reduction and selection, with
@@
 quality candidate events for the underlying physical process (using
-\SI{122}{MiB} of space).  Quantities from the selected events can be
+122$\,$MiB of space).  Quantities from the selected events can be
 both plotted and used in multivariate analysis to determine the level

### 2014-01-18 paper.tex
Add process of .svg into Makefile &two pics

@@
 
+\begin{figure*}
+\centering
+\epsfig{file=overview-of-architecture.eps, height=6in, width=7in}
+\caption{Overview of Architecture}
+\label{fig:Overview of architecture}
+\end{figure*}
+
 \begin{table}
@@
 \section{Solution 3 to Repeat the Program}
+The overview of the architecture is shown in ~\ref{fig:Overview of architecture}.
+
 \subsection{Working principle of Packaging Utility}
@@
 
+\begin{figure*}
+\centering
+\epsfig{file=preservation-integration.eps, height=4in, width=6in}
+\caption{Preservation Integration of Multiple Programs}
+\label{fig:Preservation integration}
+\end{figure*}
+
 To integrate the data and software from multiple analysis programs into one package, the concrete information of data and software, such as size, version, source and the number of files, need to be recorded.
@@
 When one user wants to generate one package, it will fork the packaging utility, the packaging utility will scan the script, get the data and software dependency part, judge whether each dependency has been inside the package, and only add the new data and software into the package, and update the package information and relavant retrieval information.
+
+The architecture of preservation integration of multiple programs is shown in ~\ref{fig:Preservation intergration}.
 

### 2014-01-20 paper.tex
add pics

@@
 \section{Introduction of the exmaple}
+
+Matthias, one graduate student from Physics Department of University of Notre
+Dame, finished one interesting tau analysis. Others want to understand how the tau
+analysis works and repeat it.
+
 \subsection{Background}
-Matthias, one graduate student from Physics Department of University of Notre Dame, finished one interesting tau analysis. We want to understand how the tau analysis works and repeat it.
 
@@
 of expected signal in real data.
+
+\begin{figure}
+\centering
+\epsfig{file=data-process.eps, height=3in, width=3in}
+\caption{Data Process}
+\label{fig:data-process}
+\end{figure}
+
+The data process is shown in Figure~\ref{fig:data-process}.
 
@@
 \section{Solution 3 to Repeat the Program}
-The overview of the architecture is shown in ~\ref{fig:Overview of architecture}.
+\subsection{Dependencies of the Program}
+
+Figure~\ref{fig:Overview of architecture} illustrates all the dependencies involved in the program, which can be divided into two categories: clear dependencies and implicit dependencies.
+Clear dependencies include data dependencies and direct software dependencies which can be extracted directly from the analysis program.
+Implicit dependencies include indirect software dependencies which is necessary for the successful execution of direct software dependencies and other implicit dependencies.
+For example, we know Git is one direct software dependency from the analysis program, which further depends on perl, python, rsync, openssh-clients and other packages.
+The analysis program accesses one file File1, which is one soft link file further referring to File2.
+
+Implication: One mechanism which can mine all the dependencies of the program is necessary.
 
@@
 
+\begin{figure}
+\centering
+\epsfig{file=solution3.eps, height=3in, width=3in}
+\caption{Relationship of Roles}
+\label{fig:solution3}
+\end{figure}
+
+The relationship of different roles involved experiment preservation and reproduction is shown in Figure~\ref{fig:solution3}.
+The original author is responsible for generating one package based on the successful execution sandbox with the help of the packaging utility.
+Then the package, together with the map file and description file will be uploaded into the archive.
+When another scholar wants to repeat the experiment, one copy of the package and its corresponding map file will be downloaded into the new machine.
+
+\subsection{Structure of Map File}
+
+The map file of one package supports pattern matching semantics,
+which greatly reduces the scale of the map file and improves the efficiency of file path redirection. 
+For example,
+one item inside the map file is "/dir1 /package-dir1" means that the access to each file and
+subdirectory under /dir1 will be redirected into /package-dir1.
+If the semantics of the map file do not support pattern matching, the size of the map file will become astonishing. 
+/dir1 may contain thousands of files, which will generates thousands of map items and will take more time to redirect file paths.
+
+In the map relationship shown above, During the packaging process, we noticed
+that it is impossible to copy the files under certain directories like /dev.
+For example, during namelist acquisition process, three special files under /dev directory were recorded into the namelist: tty, null and urandom, which are used for input and output.
+We tried to copy these files into the new package, but the packaging utility halted.
+We also noticed that copying the files under directories like /proc is
+meaningless. Because the process id of one program is random and depends on the
+current allocation of process ID. As for these two file categories, letting
+the program directly utilize the files on the machine, where the new user
+repeats the program, is a better choice. The semantics is implemented by
+setting the target path of one file equal to the origin file path inside the
+map file. For example, "/dev /dev" means that when the program needs to access
+files under /dev directory, it will directly use the file under /dev, which is
+independent from the namespace of the package. This semantics also makes the
+reference of files outside the package possible. If the new user wants to
+expand the analysis of one program to his own data with the path of /A, he can add the analysis
+code into the analysis script and add one item "/A /A" into the map file.
+
 \subsection{Evaluation of Solution 3}
@@
 \subsection{Discussion of Solution 3}
-Under Solution 3, the reproduction of one analysis program becomes easier.The namespace of repeating one experiment will be limited into one independent package containing all the data and software dependencies of one analysis program.
 
-Rethink Matthias's example, under Solution 3, the reproduction of it only needs the necessary environment variables, svn login,  the actual analysis command and the package.
-If different scholars want to repeat one analysis program, what they need to do is to obtain the package and rerun the actual analysis program.
-Under Solution 2, each scholar needs to get the necessary data and software, and then prepare software environment.
+Under Solution 3, the reproduction of one analysis program becomes easier.
+Rethink Matthias's example, the reproduction of it only needs
+the necessary environment variables, svn login, the actual analysis command
+and the package. If different scholars want to repeat one analysis program,
+what they need to do is to obtain the package and rerun the actual analysis
+program. Under Solution 2, each scholar needs to get the necessary data and
+software, and then prepare software environment.
+
+%here is the new content-hmeng
+The starting point of Solution 3 is one successful execution sandbox on the original machine. 
+Parrot traps all the system calls and copies each accessed file (except for common dependencies) into one new package.
+The necessary scientific data will be copied into the target package.
+The software dependencies can be divided into two categories: clear dependencies, which can be observed directly through reading the analysis script and implicit dependencies,
+which can not be obtained through reading the analysis script. 
+Parrot can obtain every dependency through trapping each system call.
+Strictly speaking, the software concept and the scientific data concept are lost in Solution 3, because
+the granularity of parrot is file.
+The same thing happens to network resources.
+Packaging utlity maintains one list of common dependencies and first judges whether the file belongs to this list before trying to copy one file into the package.
+As for the computing environment, Solution 3 notices the new user through the description information at the beginning of the script.
+%the following subsection belongs to the "discussion of data and software
+%preservation" section
 
@@
 
-The architecture of preservation integration of multiple programs is shown in ~\ref{fig:Preservation intergration}.
+The architecture of preservation integration of multiple programs is shown in ~\ref{fig:Preservation integration}.
+Script 1 and Script 2, sharing one same dependency B, belongs two different programs.
+Without preservation integration, B will be preserved twice in the archive, which is space-consuming.
+To improve the utilization efficiency of storage resources, preservation integration of multiple programs is necessary.
+In the archive, only one copy of B is stored, which is referred by both scripts 1 and script 2.
 
@@
 In addition, if the size of one whole software repository is small and the access frequency of each package inside it is high, the granularity can be set to the whole repository.
+
+\subsection{Preservation of Large Data}
+
+The preservation policy must concern about the size of data. If its size is
+small, copying it into one pacakge and transferring it between different
+machines is not a bad idea.Howerver, when the size becomes large, copying it
+into one package will make the size of the package uncontrollable.  In
+Figure~\ref{fig:Preservation integration}, the size of C is very large and
+easily to be obtained through Internet by different users. Directly referring C
+as network resources is more efficient than preserving it into one package.
+
+\subsection{Mining of Dependencies}
+
+The mining degree of data and software dependencies greatly determines the
+repeatability of one experiment. Data dependencies is easy to figured out.
+However, the situation of software dependencies is complex. The software
+dependencies include OS, hardware platform, software directly forked inside the
+progam and software indirectly forked by directly forked software. The first
+three categories are easy to deal with. The description of indirect software
+dependencies needs more efforts. One solution is to utlize package management
+tools, like rpm, pacman, apt, to recursively trace each direct software
+dependency and generate one clear dependency graph. With the dependency graph,
+the new user can configure the software environment and repeat the experiment.
+Solution 3 odopts this solution, which is easy to implement, but leaves the
+complex environment configuration to the new users.
+
+Another solution is to treat the computing environment, software environment
+and scientific data as one integral entirety and preserve the entirety
+completely. The reproduction of one experiment using this solution is easier.
+However, the original machine is not only for one special experiment and may
+concern a large amount of software and data unrelevant to the experiment. The
+time and space overhead of this solution must be considered.
+
+%\subsection{The preservation} When the authors and the programs becomes more
+%and more, the whole pool of one repo may be nearly to be preserved. why not
+%directly copy the whole repo and preserve it at the begining directly?  Answer:
+%we must concern the efficiency of repeating one small and simple program.
+\subsection{Preservation Degree of Directory Structure}
+
+Data and software preservation of physics experiments must concern the
+preservation degree of the original filesystem.  The three core components of
+one filesytem are file, directory and metadata.  The access of files can be
+divided into two categories: only access file metadata, like size, ownership,
+access authority list, and access both the file content and metadata.  If both
+the content and metadata need to be accessed, the whole file must be copies
+into the package.  However, if only the metadata of one file is accessed, how
+to preserve the file needs to be considered carefully. If the size of the file
+is 1KB or 1MB, preserving the content is acceptable. If the size of one file is
+1GB, preserving the whole file just for the access of its metadata is
+inefficient.
+
+Directory is one list of files and subdirectories under it. At first, we only
+copied the accessed items under one directory and ignored the unaccessed items.
+However, some operations on one directory depends on each item under it. For
+example, `ls /dirA` is one linux command to list the name of each item under
+/dirA. Because the directory itself has the name list of items under it, only
+the path of the directory was recorded into the namelist in the first phrase of
+Solution 3. However, when we repeated the command `ls /dirA` using the
+preserved package, it returned NULL because none of items under it existed in
+the package. If one routine within the original program depends on the return
+value of `ls /dirA`, the behavior of the whole program will become incorrect
+and unpredictable. Lessons: all the items under one directory must be copied
+into the package to ensure the semantics of the original program. However, the
+time and space overhead appears again. Currently, Solution 3 creates one item
+with the same name but the size of zero for each item under /dirA. Another
+solution is to introduce one database to preserve the metadata of each file and
+directory and record the origial metadata into the database.
+
+\subsection{Here is the Useful Package}
+
+At the beginnig of our case study, we generated one package for Matthias's
+example based on Solution 3. Several months later, the original machine meets
+some problems and the access model of CMSSW was also modified. In this case, if
+you want to repeat Matthias's example on the original machine, different 
+configurations, including CMSSW\_ARCH, environment variables and CVS access
+authority need to be modified. However, with the generated package and map file, we can repeat the experiment directly on the same machine.
+%here is the new content-hmeng
 

### 2014-01-20 paper.tex
format modification

@@
 \centering
-\epsfig{file=data-process.eps, height=3in, width=3in}
-\caption{Data Process}
+\epsfig{file=data-process.eps, height=2.8in, width=3in}
+\caption{Data Processing Procedures}
 \label{fig:data-process}
@@
 
-The data process is shown in Figure~\ref{fig:data-process}.
+The data processing procedures are shown in Figure~\ref{fig:data-process}.
 
@@
 \subsection{Workflow of Matthias's Example}
-Declare environment variables
 
-Obtain software from CMSSW
+The workflow of Matthias's exmaple can be divided into eight procedures.
 
-Obtain software from Git
+(a) Declare environment variables
 
-Obtain software from some public HTTP web links
+(b) Obtain software from CMSSW
 
-Obtain software from one private home page
+(c) Obtain software from Git
 
-Build software enviroment using SCRAM and Python
+(d) Obtain software from some public HTTP web links
 
-Install grid control, obtain CMS data from grid and store the data into HDFS mounted as one local file system.
+(e) Obtain software from one private home page
 
-Actual data analysis.
+(f) Build software enviroment using SCRAM and Python
+
+(g) Install grid control, obtain CMS data from grid and store the data into HDFS mounted as one local file system.
+
+(h) Actual data analysis.
 
 \subsection{Source and Size of Data and Software}
-We notice that the software sources are rich, including CMSSW, Git, HTTP and one personal main page. The size of software from each source is shown in Table~\ref{table:software-source-size}.
+
+The software sources are rich, including CMSSW, Git, HTTP and one personal main page. The size of software from each source is shown in Table~\ref{table:software-source-size}.
 
@@
 
-\begin{figure*}
-\centering
-\epsfig{file=overview-of-architecture.eps, height=6in, width=7in}
-\caption{Overview of Architecture}
-\label{fig:Overview of architecture}
-\end{figure*}
-
 \begin{table}
@@
            \hspace{9pt} scram b -j32 \\
-        5. fix grid\_control.cfg and run it. \\
+        5. Fix grid\_control.cfg and run it. \\
         6. Perform actual analysis \\ 
@@
         \#the description of OS version and hardware architecture \\
+        \# list of indirect software dependencies \\
         set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3) \\ 
@@
         \#declaration of environment variables\\
-        \#clear data dependency\\
-        \#clear software dependency\\
-        \#software build and install command\\
+        \#data dependencies\\
+        \#direct and indirect software dependencies\\
+        \#software build and install commands\\
         \#actual analysis program\\ 
@@
 In response, Matthias introduced the general workflow of his tau analysis through one long email including notes, linux shell commands, web links.
-The First version of Table~\ref{table:scripts} illstrates his email.
+The Version 1 of Table~\ref{table:scripts} illstrates his email.
 
 However, this solution to repeat one experiment has three potential drawbacks.
-Firstly, the experience of repeating one tau analysis through emails is chaotic.
-You need constant jumps around multiple web links.
-There are overlap between the content of the email and the content of web links, which needs the new user to merge them.
-Multiple communication through emails is necessary to ensure the successful repeat of the whole analysis.
-For example, the original email refers to one environment variable called CMSSW\_base without clear declaration, the new user needs to send one email to the original writer to obtain its accurate value.
-Secondly, the necessary procedure to repeat the experiment, including software acquisition from different sources, is complex for the new user.
-In Matthias's example, the sources of software includes CMSSW, Git, HTTP.
-The access of CMSSW requires the new user be an authorized user of CMSSW.
-What's more, some parts of the workflow are unrepeatible.
-The third step of this experiment requires the new user owning the access authority to the Grid.
+Firstly, the experience of repeating one tau analysis through emails is
+chaotic. You need to constantly jump around multiple web links. There are overlap
+between the content of the email and the content of web links, which needs the
+new user to merge them. Multiple communication through emails is necessary to
+ensure the successful reproduction of the whole analysis. For example, the original
+email refers to one environment variable called CMSSW\_base without clear
+declaration, the new user needs to send one email to the original writer to
+obtain its accurate value. Secondly, the necessary procedures to repeat the
+experiment, including software acquisition from different sources, is complex
+for the new user. In Matthias's example, the sources of software includes
+CMSSW, Git, HTTP. The access of CMSSW requires the new user to be an authorized
+user of CMSSW. What's more, some parts of the workflow are unrepeatable. The
+third step of this experiment requires the new user to own the access authority
+of the Grid.
 
-Implication: Directly repeating the experiment using the workflow and results by the original author is complex and difficult. Some extra work must be done to make the reproduction process easier.
+Implication: Directly repeating the experiment using the workflow description and results provided by the original author is complex and difficult.
+Some extra work must be done to make the reproduction process easier.
 
@@
 Version 2 of Table~\ref{table:scripts} illstrates the merged script.
-As for the data acquisition from the Grid, we directly use the local copy in HDFS to avoidrequiring the new user to obtain a grid certification.
+As for the data acquisition from the Grid, we directly use the local copy in HDFS to avoid requiring the new user to obtain a grid certification.
 
 The breakdown of execution time of Solution 2 is shown in Table~\ref{table:time-2nd}.
-According to Table~\ref{table:time-2nd}, about half of the total execution time is consumed to prepare relevant software environment.
+About half of the total execution time is consumed to prepare relevant software environment.
+The cvs command is forked to check out 23 packages from CMSSW and three git repositories are cloned.
 
@@
     Sub-Task & Time & Percentage \\ \hline
-    Software preparation from CMSSW & 15min 30s & 25.27\% \\ \hline
-    Software preparation from Git & 9s & 0.24\% \\ \hline
-    Software preparation from Wget & 36s & 0.98\% \\ \hline
+    Software acquisition from CMSSW & 15min 30s & 25.27\% \\ \hline
+    Software acquisition from Git & 9s & 0.24\% \\ \hline
+    Software acquisition from Wget & 36s & 0.98\% \\ \hline
     Environment Build - SCRAM & 13min 20s & 21.74\% \\ \hline
@@
 
-Implication: All the data and software involved in the experiment should be provided to the new user in the format of one self-contained package so that the multiple execution of the experiment from the same user only involve one time of data and software acquisition and environment building process.
-In addition, the requirement of the underlying OS and hardware should also be provided to the new user.
+Implication: All the data and software involved in the experiment should be
+provided to the new user in the format of one self-contained package so that
+the new user can avoid complex data and software acquisition and software
+environment building process. In addition, the requirements of the underlying
+OS and hardware should also be provided to the new user.
 
@@
 
-Figure~\ref{fig:Overview of architecture} illustrates all the dependencies involved in the program, which can be divided into two categories: clear dependencies and implicit dependencies.
-Clear dependencies include data dependencies and direct software dependencies which can be extracted directly from the analysis program.
-Implicit dependencies include indirect software dependencies which is necessary for the successful execution of direct software dependencies and other implicit dependencies.
-For example, we know Git is one direct software dependency from the analysis program, which further depends on perl, python, rsync, openssh-clients and other packages.
-The analysis program accesses one file File1, which is one soft link file further referring to File2.
+\begin{figure*}
+\centering
+\epsfig{file=overview-of-architecture.eps, height=4in, width=6.5in}
+\caption{Overview of Architecture}
+\label{fig:Overview of architecture}
+\end{figure*}
+
+Figure~\ref{fig:Overview of architecture} illustrates all the dependencies
+involved in the program, which can be divided into two categories: clear
+dependencies and implicit dependencies. Clear dependencies include data
+dependencies and direct software dependencies which can be extracted directly
+from the analysis program. Implicit dependencies include indirect software
+dependencies which is necessary for the successful execution of direct software
+dependencies and other implicit dependencies. For example, we know Git is one
+direct software dependency from the analysis program, which further depends on
+perl, python, rsync, openssh-clients and other packages. The analysis program
+accesses one file called File1, which is one soft link file further referring to
+another name named File2. 
+The implicit dependencies also refers to some files under /pscratch, which is one local mount point of one PanFS clustered file system with the size of 206TB.
 
@@
 \subsection{Working principle of Packaging Utility}
-The difficulty of data access authority acquisition enforces us to find out one solution, in which the reproduction of the original analysis can be done without any external dependency.
-That is, one independent and self-contained package containing all the data and software dependencies is necessary.
-Someone may suggest that it should be the responsibility of the original author to generate the required package.
-However, letting the original author to provide the package which can be used by others to repeat the original experiment is unrealistic.
-One reason is that figuring out the underlying dependency of each software is complex and time-consumpting and even impossible for the original author.
-In this experiment, the machine used for the experiment is one public machine of physics department, and Matthias is one common user without root authority.
-The underlying OS and supporting softwares are installed and maintained by the IT department of the university.
-On the other hand, the architecture design of the required package including all the data and software dependencies is not under the research field of physists.
 
-Parrot is a virtual filesystem access tool which attaching existing programs to a variety of remote I/O systems including http, ftp, gridftp, irods, HDFS, xrootd, grow and chirp.
-it traps all system calls of one program through ptrace debugging interface, and replaces them with remote I/O operations as desired.
-through executing one program under parrot, all the paths of files involved in this program can be recorded.
+The difficulty of data access authority acquisition enforces us to find out one
+solution, in which the reproduction of the original analysis can be done
+without any external dependency. That is, one independent and self-contained
+package containing all the data and software dependencies is necessary.
 
-With the help of parrot, one packaging utility which generates one independent package for one program to make the reproduction of the program convenient can be deployed.
-The basis of the packaging utility is one successful execution sandbox (the data from grid has been preserved in HDFS and the software from CMSSW, Git and HTTP has been on the local machine.).
-We re-execute the actual data analysis code under Parrot and get the name list of all the files actually accessed during the execution process of the actual data analysis.
-Then, according to the file name list, one package containing all the necessary data and software for one analysis program is generated.
-Next time, when another scholar wants to repeat the program, he only needs to obtain the package and directly execute the actual analysis program inside the package.
+Someone may suggest that it should be the responsibility of the original author
+to generate the required package. However, letting the original author provide
+the package which can be used by others to repeat the original experiment is
+unrealistic. One reason is that figuring out the underlying dependencies of
+each software is complex and time-consumpting and even impossible for the
+original author. In this experiment, the machine used for the experiment is one
+public machine of physics department, and Matthias is one common user without
+root authority. The underlying OS and supporting softwares are installed and
+maintained by the IT department of the university. On the other hand, the
+architecture design of the required package including all the data and software
+dependencies is not under the research field of physists.
 
-The shell script of the Solution 2 is simplified into one new version, which only contains the necessary environment variables, access authority and the actual analysis command.
-The Version 2 of Table~\ref{table:scripts} illustrates the simplified script.
+Parrot is a virtual filesystem access tool which attaching existing programs to
+a variety of remote I/O systems including http, ftp, gridftp, irods, HDFS,
+xrootd, grow and chirp. It traps all system calls of one program through ptrace
+debugging interface, and replaces them with remote I/O operations as desired.
+Through executing one program under Parrot, all the paths of files involved in
+this program can be recorded.
+
+With the help of Parrot, one packaging utility which generates one independent
+package for one program to make the reproduction of the program convenient can
+be deployed. The starting point of the packaging utility is one successful execution
+sandbox (the data from grid has been preserved in HDFS and the software from
+CMSSW, Git and HTTP has been on the local machine.). We re-execute the actual
+data analysis code under Parrot and get the name list of all the files actually
+accessed during the execution process of the actual data analysis. Then,
+according to the file name list, one package containing all the necessary data
+and software for one analysis program is generated. Next time, when another
+scholar wants to repeat the program, he only needs to obtain the package and
+directly execute the actual analysis program inside the package.
+
+The shell script of the Solution 2 is simplified into one new version, which
+only contains the necessary environment variables, access authority and the
+actual analysis command. The Version 3 of Table~\ref{table:scripts} illustrates
+the simplified script.
 
 \subsection{Workflow of Packaging Utility}
-The workflow of generating one package for one analysis program is as follows:
+The workflow of generating one package for one analysis program is as follows.
 
@@
 
-Command:
+The command used to generate the file name list is as follows. The `-L` parameter refers to the path of the file containing all the accessed file name of the experiment.
 
-parrot\_run -l namelist /bin/tcsh parrot\_cms.sh
+parrot\_run -L namelist /bin/tcsh parrot\_cms.sh
 
-Output:
-namelist size: 5.7MB     128711 lines
-
-de-duplicated namelist size: 2.2MB   42385 lines
+The original ouput of this command is one namelist file with the size of 5.7MB
+and 128,711 lines, each of which corresponds to one one accessed file of the
+program. We noticed that some items appeared multiple times. To reduce the
+packaging time, de-duplication and sorting techoniques are used for the
+namelist file, generating one smaller file with the size of 5.7MB and 42,385
+lines.
 
@@
 
-The packaging utility iterates each filename inside L1 and copies it into the target package.
-After completing the packaging process, the target package together with its description information, and one mountlist, which redirects the access of data from different file systems into the target package, will be provided to users.
-The packaging process also runs within Parrot environment to access data from different file systems.
+The packaging utility iterates each filename inside L1 and copies it into the
+target package. After finishing the packaging process, the target package
+together with its description information, and one map file, which redirects
+the access of files from different file systems into the files inside the target package, will be
+provided to users. The packaging process also runs within Parrot environment to
+access data from different file systems.
 
-Command:
+\begin{figure}
+\centering
+\epsfig{file=package-info.eps, height=1.5in, width=2.5in}
+\caption{Package Description Infomation}
+\label{fig:package-info}
+\end{figure}
+The command used to generate the package containing all the files of L1 is as follows. 
+`package1-4.sh` is a bash script which iterates each line of L1 and
+determines the behavior according to the file type (common files, directories,
+linked files) and the system call type.
+The package description information is shown in Figure~\ref{fig:package-info}.
 
-parrot\_run /bin/bash package1-4.sh -l ~/namelist
-
-the path of pacakge is: /tmp/package1-4
-
-the total size of package is: 21GB
-
-the total number of files is: 1204
-
-the total number of directory is: 473
-
-the total number of symbolic link files is: 195
-
-the mountlist path is: /tmp/mountlist
+parrot\_run /bin/bash package1-4.sh -L ~/namelist
 
@@
 
-To ensure the successful reproduction, the filesystem structure of the original execution environment should be preserved as completely as possible.
-However, attempting to copy the whole content of one directory or one file is space-consuming and time-consuming, because the original program may only access the metadata of one directory with the size of 200GB.
-our solution is to determine the copy degree of one directory or one common file according to the system call type for its path.
+To ensure the successful reproduction, the filesystem structure of the original
+execution environment should be preserved as completely as possible. However,
+attempting to copy the whole content of one directory or one file is
+space-consuming and time-consuming, because the original program may only
+access the metadata of one file with the size of 200GB. Our solution is to
+determine the copy degree of one directory or one common file according to the
+system call type for its path.
 
-The map relationship between the file access path used in the actual analysis program and the actual file location used during the reproduction process is kept inside the mountlist file.
-the structure of the mountlist is as follows:
+The map relationship between the file access path used in the actual analysis
+program and the actual file location used during the reproduction process is
+kept inside the map file. The structure of the map file is shown in Table~\ref{table:map-file}.
 
-/ /tmp/package1-4
-
-/tmp/package1-4 /tmp/package1-4
-
-/dev /dev
-
-/misc /misc
-
-/net /net
-
-/proc /proc
-
-/sys /sys
-
-/var /var
-
-/selinux /selinux
+\begin{table}
+    \centering
+    \begin{tabular}{|l|l|}
+    \hline
+    Path used in Program & Actual Location \\ \hline
+    / & /tmp/package1-4 \\ \hline
+    /tmp/package1-4 & /tmp/package1-4 \\ \hline
+    /dev & /dev \\ \hline
+    /misc & /misc\\ \hline
+    /net & /net\\ \hline
+    /proc & /proc\\ \hline
+    /sys & /sys\\ \hline
+    /var & /var\\ \hline
+    /selinux & /selinux\\ \hline
+    \end{tabular}
+    \caption{Structure of Map File}
+    \label{table:map-file}
+\end{table}
 
@@
 
-When another scholar wants to repeat one analysis program, the accessed data field is limited into the target package with the help of the mountlist generated in step 2.
+When another scholar wants to repeat one analysis program, the accessed data
+field is limited into the target package with the help of the map file 
+generated in step 2.
 
@@
 \centering
-\epsfig{file=solution3.eps, height=3in, width=3in}
+\epsfig{file=solution3.eps, height=2in, width=3in}
 \caption{Relationship of Roles}
@@
 
-The relationship of different roles involved experiment preservation and reproduction is shown in Figure~\ref{fig:solution3}.
-The original author is responsible for generating one package based on the successful execution sandbox with the help of the packaging utility.
-Then the package, together with the map file and description file will be uploaded into the archive.
-When another scholar wants to repeat the experiment, one copy of the package and its corresponding map file will be downloaded into the new machine.
+The relationship of different roles involved experiment preservation and
+reproduction is shown in Figure~\ref{fig:solution3}.  The original author is
+responsible for generating one package based on the successful execution
+sandbox with the help of the packaging utility. Then the package, together with
+its map file and description file will be uploaded into the archive. When
+another scholar wants to repeat the experiment, one copy of the package and its
+corresponding map file will be downloaded into the new machine.
 
@@
 
-In the map relationship shown above, During the packaging process, we noticed
-that it is impossible to copy the files under certain directories like /dev.
+During the packaging process, we noticed
+that it is impossible to copy the files under certain directories.
 For example, during namelist acquisition process, three special files under /dev directory were recorded into the namelist: tty, null and urandom, which are used for input and output.
@@
 meaningless. Because the process id of one program is random and depends on the
-current allocation of process ID. As for these two file categories, letting
+current allocation of process ID.
+
+As for these two file categories, letting
 the program directly utilize the files on the machine, where the new user
@@
 
-The data size of Solution 3 is shown in Table~\ref{table:datasize-3rd}.
-The data categories is more complex than our imagination.
-Except the data stored in Hadoop and the necessary set of software, files from /sbin, /bin and other paths are also necessary for the reproduction of the program.
+The data size of Solution 3 is shown in Table~\ref{table:datasize-3rd}. The
+data categories is more complex than our imagination. Except the data stored in
+Hadoop and the necessary set of software, files from /pscratch, /sbin, /lib and other
+paths are also necessary for the reproduction of the program.
 
@@
 Rethink Matthias's example, the reproduction of it only needs
-the necessary environment variables, svn login, the actual analysis command
+the necessary environment variables, the actual analysis command
 and the package. If different scholars want to repeat one analysis program,
@@
 The starting point of Solution 3 is one successful execution sandbox on the original machine. 
-Parrot traps all the system calls and copies each accessed file (except for common dependencies) into one new package.
+Parrot traps all the system calls and copies each accessed file (except for common dependencies) into one package.
 The necessary scientific data will be copied into the target package.
@@
 the granularity of parrot is file.
-The same thing happens to network resources.
+The same thing happens to networked resources.
 Packaging utlity maintains one list of common dependencies and first judges whether the file belongs to this list before trying to copy one file into the package.
@@
 \subsection{Relationship of Different Solutions}
-The relationship of these four solutions to repeat one program is shown in Table~\ref{table:relationship}.
+The relationship of these three solutions to repeat one program is shown in Table~\ref{table:relationship}.
+The aim is to make it easier to repeat one program through making the data and software preparation easier.
 
 \subsection{ Data size Comparison of Solution 2 and 3}
-The packaging utility checks the system call of each file within the namelist, and maintains the minimum dataset, which makes the size of the final package is as small as possible.
-The total size of Hadoop under Solution 2 is astonishing, while the size of Hadoop under the package is decreased to 20GB.
-The same trend applies to the size of CMSSW\_5\_3\_11\_patch3.
-Because the packaging utility tries to construct one independent and self-contained package, necessary files  from /sbin, /lib and other directories are also copied into the package and denoted as "Other data for Package" in the Table~\ref{table:datasize-2nd3rd}.
+
+The packaging utility checks the system call of each file within the namelist,
+and maintains the minimum dataset, which makes the size of the final package 
+as small as possible. The total size of Hadoop under Solution 2 is astonishing,
+while the size of Hadoop under the package is decreased to 20GB. The same trend
+applies to the size of CMSSW\_5\_3\_11\_patch3. Because the packaging utility
+tries to construct one independent and self-contained package, necessary files
+from /sbin, /lib and other directories are also copied into the package and
+denoted as "Other data for Package" in Table~\ref{table:datasize-2nd3rd}.
 
@@
 \subsection{Execution Time Comparison of Solution 2 and 3}
-Table~\ref{table:time-2nd3rd} shows the execution time comparison between Solution 2 and 3.
-The time consumption of the reproduction of one program from different scholars kept the same under Solution 2, including software and data preparation.
-However, under Solution 3, the data and software preparation is one-time.
-The following reproduction of the same program only needs to obtain one copy of the package and execute the actual experimental analysis directly.
+
+Table~\ref{table:time-2nd3rd} shows the execution time comparison between
+Solution 2 and 3. The time consumption of the reproduction of one program from
+different scholars kept the same under Solution 2, including software and data
+preparation. However, under Solution 3, the data and software preparation is
+one-time. The following reproduction of the same program only needs to obtain
+one copy of the package and execute the actual experimental analysis directly.
+Data is obtained through accessing Hadoop Distributed File System in Solution 2, but is copied into the package in Solution 3.
+This localization of data speeds up the data analysis process, resulting the actual analysis time reducing from 31 minutes to 13 minutes.
 
@@
 
-\begin{figure*}
+\begin{figure}
 \centering
-\epsfig{file=preservation-integration.eps, height=4in, width=6in}
+\epsfig{file=preservation-integration.eps, height=2.2in, width=3.3in}
 \caption{Preservation Integration of Multiple Programs}
 \label{fig:Preservation integration}
-\end{figure*}
+\end{figure}
 
-To integrate the data and software from multiple analysis programs into one package, the concrete information of data and software, such as size, version, source and the number of files, need to be recorded.
-we also need to design one more instructive shell script format, in which the data dependencies and software dependencies can be clearly expressed and recognized.
-The packaging process needs to be re-organized.
-packaging utility needs to maintain one list of current software and data subset already stored in the package.
-When one user wants to generate one package, it will fork the packaging utility, the packaging utility will scan the script, get the data and software dependency part, judge whether each dependency has been inside the package, and only add the new data and software into the package, and update the package information and relavant retrieval information.
+To integrate the data and software from multiple analysis programs into one
+package, the concrete information of data and software, such as size, version,
+source and the number of files, need to be recorded. we also need to design one
+more instructive shell script format, in which the data dependencies and
+software dependencies can be clearly expressed and recognized. The packaging
+process needs to be re-organized. Packaging utility needs to maintain one list
+of current software and data subset already stored in the package. When one
+user fork the packaging utility to preserve one program, the
+packaging utility will scan the script, get the data and software dependency
+part, judge whether each dependency has been inside the package, and only add
+the new data and software into the package, and update the package information
+and relavant retrieval information.
 
-The architecture of preservation integration of multiple programs is shown in ~\ref{fig:Preservation integration}.
-Script 1 and Script 2, sharing one same dependency B, belongs two different programs.
-Without preservation integration, B will be preserved twice in the archive, which is space-consuming.
-To improve the utilization efficiency of storage resources, preservation integration of multiple programs is necessary.
-In the archive, only one copy of B is stored, which is referred by both scripts 1 and script 2.
+The architecture of preservation integration of multiple programs is shown in
+Figure~\ref{fig:Preservation integration}. Script 1 and Script 2, sharing one
+dependency B, belongs two different programs. Without preservation
+integration, B will be preserved twice in the archive, which is
+space-consuming. To improve the utilization efficiency of storage resources,
+preservation integration of multiple programs is necessary. In the archive,
+only one copy of B is stored, which is referred by both scripts and script 2.
 
 \subsection{Preservation Granularity}
-Another important factor of data and software preservation is the choice of preservation granularity.
-In Solution 3, the preservation granularity is one file, because Parrot virtual filesystem traps each system call and redirects the access path to each file.
-As a result, during the packaging process, each time only one file can be copied into the target package, which is low-efficient.
-However, there are other options of preservation granularity.
-The software is generally preserved in the unit of package inside the remote repository, the packaging process of one experiment can adopt one package as the unit.
-In addition, if the size of one whole software repository is small and the access frequency of each package inside it is high, the granularity can be set to the whole repository.
+
+Another important factor of data and software preservation is the choice of
+preservation granularity. In Solution 3, the preservation granularity is one
+file, because Parrot virtual filesystem traps each system call and redirects
+the access path of each file. As a result, during the packaging process, each
+time only one file can be copied into the target package, which is
+low-efficient. However, there are other options of preservation granularity.
+The software is generally preserved in the unit of package inside the remote
+repository, the packaging process of one experiment can adopt one package as
+the unit. In addition, if the size of one whole software repository is small
+and the access frequency of each package inside it is high, the granularity can
+be set to the whole repository.
 
@@
 small, copying it into one pacakge and transferring it between different
-machines is not a bad idea.Howerver, when the size becomes large, copying it
+machines is not a bad idea. Howerver, when the size becomes large, copying it
 into one package will make the size of the package uncontrollable. In
@@
 easily to be obtained through Internet by different users. Directly referring C
-as network resources is more efficient than preserving it into one package.
+as networked resources is more efficient than preserving it into one package.
 
@@
 The mining degree of data and software dependencies greatly determines the
-repeatability of one experiment. Data dependencies is easy to figured out.
-However, the situation of software dependencies is complex. The software
-dependencies include OS, hardware platform, software directly forked inside the
-progam and software indirectly forked by directly forked software. The first
+repeatability of one experiment. Data dependencies is easy to figured out. However, the situation of software dependencies is complex. The software
+dependencies include OS, hardware platform, 
+direct software dependencies and indirect software dependency which is dependent upon direct software dependencies.
+The first
 three categories are easy to deal with. The description of indirect software
@@
 into the package.  However, if only the metadata of one file is accessed, how
-to preserve the file needs to be considered carefully. If the size of the file
+to preserve the file needs to be considered carefully. If the file size
 is 1KB or 1MB, preserving the content is acceptable. If the size of one file is
-1GB, preserving the whole file just for the access of its metadata is
+1GB, preserving the whole file just for accessing its metadata is
 inefficient.
@@
 value of `ls /dirA`, the behavior of the whole program will become incorrect
-and unpredictable. Lessons: all the items under one directory must be copied
-into the package to ensure the semantics of the original program. However, the
+and unpredictable.
+
+To ensure the semantics of the original program, all the items under one directory must be copied
+into the package. However, the
 time and space overhead appears again. Currently, Solution 3 creates one item
@@
 solution is to introduce one database to preserve the metadata of each file and
-directory and record the origial metadata into the database.
+directory.
+
+\subsection{User Access Model of Data and Software}
+
+Through this case study, we noticed that the user access module of remote data
+and software has a great impact of the preservation mechanism, especially when
+we try to integrate the preservation of multiple programs. If all the programs
+only refer the original data and software and refuse to modify them, the
+preservation is easy and can ignore the data version problem. However, if some
+programs try to modify the original data and software to accustom to its own
+requirement, the preservation mechanism must provide one way to differentiate
+the original data and the special data used in one certain
+program. To have a clear understanding of the data access model, more examples
+need to be investigated.
 
@@
 configurations, including CMSSW\_ARCH, environment variables and CVS access
-authority need to be modified. However, with the generated package and map file, we can repeat the experiment directly on the same machine.
+authority need to be modified. However, with the generated package and its map file, we can repeat the experiment directly on the same machine without any modification.
 %here is the new content-hmeng
-
-\subsection{User Access Model of Data and Software}
-Through this case study, we notice that the user access module of remote data and software has a great impact of the preservation mechanism, especially when we try to integrate the preservation of multiple programs.
-If all the programs only refer the original data and software and refuse to modify them, the preservation is easy and can ignore the data version problem.
-However, if each program tries to modify the original data and software to accustom to its own requirement, the preservation mechanism must provide one way to differentiate the original data version and the special data version used in one certain program.
-To have a clear understanding of the data access model, more examples need to be investigated.
 

### 2014-01-23 paper.tex
Added outline to follow.

@@
 refinements to convert it into an executable and preservable object.
-Then, we develop three techniques for observing and capturing the
+Then, we develop two techniques for observing and capturing the
 dependencies associated with the system, comparing the cost of capture,
 the size of the preserved object, and the flexibility of the resulting
-object.  We conclude with some reflections on the challenges of preservation
-and advice for future efforts.
+object.  We describe how each of these techniques may interact with
+a future archive of preserved software artifacts, and conclude with
+some reflections on the challenges of preservation and advice for future efforts.
+
+\if 0
+Section 2: Overview of Application
+    CMS/LHC introduction.
+    Data sources and reduction of size.
+    Code sources and reduction of size.
+    Prose observations about the script.
+        Uses multiple repos that change over time, with varying level of stability.
+        Low selectivity from the larger repos
+        Significant initialization time to collect everything.
+        Incidental infrastructure tools versus essential objects.
+        Some dependencies were surprising.
+    Figure: Diagram of app with both code and data sources.
+    Table: Show all code and data sources and size within one table.
+
+Section 3: Preservation Strategies
+    Figure: Show app in four stages:
+        Single email.
+        Script with embedded references to dependencies.
+        Script with map file that refers to external dependencies.
+        Script with map file that refers to preserved dependencies.
+
+    Transform to more suitable format that expresses dependencies.
+
+    Incorporate into archive, saving deps and map file.
+
+    But, how to get the dependencies?
+
+    Three strategies:
+        Original - Unmodified application run in original environment.
+        Coarse-Grained - Capture deps at large granularity -- whole filesystems and repositories.
+        Fine-Grained - Capture deps at a fine granularity -- individual files actually used.
+
+    Coarse-Grained Method (Copy Repositories)
+        First, determine dependencies
+        Express app as script + map file
+        Packaging tool downloads deps, rewrites map file.
+        To run packaged application, obtain map, download
+
+    Fine-Trained Toolkit (Parrot)
+        Tool to detect dependencies (Parrot)
+        Express app as script + map file
+        Packaging tool downloads deps, rewrites map file.
+        To run package application, run again with Parrot.
+
+Section 4: Evaluation
+
+    Table: Time and size of preserving using each of the two techniques.
+
+    Explain why the techniques show different performance.
+
+    Is one technique more effective than the other?  Why?
+\fi
 

### 2014-01-24 paper.tex
new pics and new sequence

@@
 
-\section{Introduction of the exmaple}
+\section{Overview of Application}
 
@@
 
-\begin{figure}
-\centering
-\epsfig{file=data-process.eps, height=2.8in, width=3in}
-\caption{Data Processing Procedures}
-\label{fig:data-process}
-\end{figure}
-
-The data processing procedures are shown in Figure~\ref{fig:data-process}.
-
 % FWIW, units are TB, GB, not TiB, GiB!
@@
 
-\subsection{Source and Size of Data and Software}
+\subsection{Key Observations of the Example}
 
-The software sources are rich, including CMSSW, Git, HTTP and one personal main page. The size of software from each source is shown in Table~\ref{table:software-source-size}.
+\subsubsection{Complexity of Data and Software Dependencies}
 
-As for the experiment data, Matthias copies the subset of T3 data from grid and stores the data into HDFS mounted as one local file system.
-The total size of data stored in HDFS is 33TB (*need to rethink).
+\begin{figure}
+\centering
+\epsfig{file=dependencies.eps, height=3in, width=3.5in}
+\caption{Dependencies}
+\label{fig:dependencies}
+\end{figure}
+
+Figure~\ref{fig:dependencies} illustrates all the dependencies
+involved in the program, which can be divided into two categories: clear
+dependencies and implicit dependencies. Clear dependencies include data
+dependencies and direct software dependencies which can be extracted directly
+from the analysis program. The scientific data of this example comes from Grid. Direct software dependencies includes CMSSW, Git, HTTP and one personal main page.
+
+Implicit dependencies include indirect software
+dependencies which is necessary for the successful execution of direct software
+dependencies and other implicit dependencies. For example, we know Git is one
+direct software dependency from the analysis program, which further depends on
+perl, python, rsync, openssh-clients and other packages. The analysis program
+accesses one file called File1, which is one soft link file further referring to
+another name named File2.
+The implicit dependencies also refers to some files under /pscratch, which is one local mount point of one PanFS clustered file system with the size of 206TB.
+And more importantly, the successful execution of this program greatly depends on the underlying OS and hardware platform.
+
+\subsubsection{Size of Data and Software Dependencies}
+The size of data and software dependencies is astonishing.
+The size of the BEAN is 11.6TB, which is too large to be analyzed directly by the Tau Analysis program.
+However, after one preprocessing which only collects the events matching basic quality criteria, the data size is still very large, 43.3GB.
+
+The size of software from each source is shown in Table~\ref{table:software-source-size}.
 
@@
 
+\subsubsection{Complexity of the Program}
+Complex data and software dependencies, complex environment building process, the large size of data and software involved in the Tau analysis, together with the access authority problem, determine the complexity of the program.
+In order to obtain the experimental data from the Grid, the author needs to install and config grid-control software. 
+The access authority of the Grid is also necessary for the data acquisition.
+The software acquisition from CMSSW, Git and HTTP and environment building process is time-consuming.
+The execution time of actual data analysis is about 30 minutes.
+However, the software acquisition and environment building time is about 30 minutes, which is very close to the execution time of actual data analysis.
+If the acquisition of experimental data is considered, the percentage of actual data analysis only occupies one small pertentage of the whole time consumption.
+The size of data and software dependencies further complicate the program.
+
+\subsubsection{Real Used Data and Software Size}
+
+Even if the orginal data size referred by the program is astonishing, the size
+of really used data and software is greatly smaller.
+Figure~\ref{fig:data-code-size} illustrates the procedures of the Tau analysis.
+After SBEAN, the data size is 43.3GB, however, the atual size of really used
+data in the program is 20GB.  The same thend occurs to the size of software and
+other dependencies. The size of CMSSW repository is 1.16TB, the size of
+packages checked out from CMSSW is 449MB, and the size of actually used CMSSW
+files is only 5.2MB. 
+The total size of PanFS mounted as /pscratch is 206TB, however, the really used data from /pscratch is only 119MB.
+We compared the original size and actually used size of data and software in Table~\ref{table:size-original-real}.
+
+\begin{table}
+    \centering
+    \begin{tabular}{|l|r|r|r|}
+        \hline
+        Source & Original & Referred & Really Used \\ 
+        & Size & Size & Size \\ \hline
+        CMSSW & 1.16TB & 449MB & 5.2MB\\ \hline
+        Git & 51MB & & \\ \hline
+        Public HTTP & 52MB & & \\ \hline
+        Private home page & 41KB & & \\ \hline
+        HDFS & 33TB & 43.3GB & 20GB \\ \hline
+        pscratch & 206TB & & 119MB \\ \hline
+        Local Disk & & & 88.4MB \\ \hline     
+    \end{tabular}
+    \caption{Really Used Data and Software Size}
+    \label{table:size-original-real}
+\end{table}
+
+\begin{figure}
+\centering
+\epsfig{file=data-code-size.eps, height=3in, width=3.5in}
+\caption{Workflow of Tau Analysis}
+\label{fig:data-code-size}
+\end{figure}
+
+\subsubsection{Stability of Dependencies}
+
+The program involves obtaining software from the home page of another graduate
+student from University of Notre Dame. However, the access authority of this
+home page will termi nate after the graduation of the student. We need one
+mechanism to 
+evaluate the stability of each dependency must be evaluated to ensure the program can be 
+repeated by others.
+
+The stability of Grid is relatively higher. However, the
+public web resources and personal home page is not stable. Too many factors
+like the termination of one web site, the graduation of the home page's author,
+would result in the failure of resource access. CMSSW, which seems to be
+stable, in fact, also involves stability problems. CMSSW provides different
+collections of accessible versions to different architectures. Transformation
+from one architecture to another may result in the failure of accessing one
+certain CMSSW version. At the beginning of our reseach, cvs supported
+anonymous access of CMSSW outside of Cern. However, this anonymous access has
+been cancelled now.
+
 \begin{table}
@@
         \hline
-        Version 1\\ \hline
+        Version 1: Email\\ \hline
         \\
@@
         \\ \hline
-        Version 2\\ \hline
+        Version 2: Script\\ \hline
         \\
@@
         \\ \hline
-        Version 3\\ \hline
+        Version 3: Fine-Grained Toolkit\\ \hline
         \\
@@
 
-\section{Solution 1 to Repeat the Program}
+\section{Preservation Strategies}
+
+\begin{figure*}
+\centering
+\epsfig{file=version-evolution.eps, height=4in, width=6.5in}
+\caption{Version Evolution}
+\label{fig:version-evolution}
+\end{figure*}
+
+Figure~\ref{fig:version-evolution} illustrates the evolution history of different preservation strategies.
+
+\subsection{Solution 1: Email}
 In order to repeat Matthais's example, the new user consulted the original author by email about the necessary work for the experiment.
@@
 
-\section{Solution 2 to Repeat the Program}
+\subsection{Solution 2: Script}
 One possible solution for the access authority problem of grid data is to grant the new user the authority to access gird data directly.
@@
 As for the data acquisition from the Grid, we directly use the local copy in HDFS to avoid requiring the new user to obtain a grid certification.
-
-The breakdown of execution time of Solution 2 is shown in Table~\ref{table:time-2nd}.
-About half of the total execution time is consumed to prepare relevant software environment.
-The cvs command is forked to check out 23 packages from CMSSW and three git repositories are cloned.
-
-\begin{table}
-    \centering
-    \begin{tabular}{|l|r|r|}
-    \hline
-    Sub-Task & Time & Percentage \\ \hline
-    Software acquisition from CMSSW & 15min 30s & 25.27\% \\ \hline
-    Software acquisition from Git & 9s & 0.24\% \\ \hline
-    Software acquisition from Wget & 36s & 0.98\% \\ \hline
-    Environment Build - SCRAM & 13min 20s & 21.74\% \\ \hline
-    Environment Build - Python & 1s & 0.03\% \\ \hline
-    Data analysis & 31min 44s & 51.74\% \\ \hline
-    Total & 61min 20s & 100.00\% \\ \hline
-    \end{tabular}
-    \caption{Breakdown of Execution Time of Solution 2}
-    \label{table:time-2nd}
-\end{table}
-
-The size of data and software from each category is shown in table~\ref{table:datasize-2nd}.
-
-\begin{table}
-    \centering
-    \begin{tabular}{|l|r|}
-    \hline
-    Data Category & Data Size \\ \hline
-    Software from CMSSW & 449MB \\ \hline
-    Software from Git & 61MB \\ \hline
-    Software from Wget & 52MB \\ \hline
-    Hadoop & 33TB \\ \hline
-    Total & 33792.562GB \\ \hline
-    \end{tabular}
-    \caption{Data Size of Solution 2}
-    \label{table:datasize-2nd}
-\end{table}
 
@@
 
-\section{Solution 3 to Repeat the Program}
-\subsection{Dependencies of the Program}
+\subsection{Solution 3: Coarse-Grained Method}
+%%
 
-\begin{figure*}
-\centering
-\epsfig{file=overview-of-architecture.eps, height=4in, width=6.5in}
-\caption{Overview of Architecture}
-\label{fig:Overview of architecture}
-\end{figure*}
+\subsection{Solution 4: Fine-Grained Toolkit}
 
-Figure~\ref{fig:Overview of architecture} illustrates all the dependencies
-involved in the program, which can be divided into two categories: clear
-dependencies and implicit dependencies. Clear dependencies include data
-dependencies and direct software dependencies which can be extracted directly
-from the analysis program. Implicit dependencies include indirect software
-dependencies which is necessary for the successful execution of direct software
-dependencies and other implicit dependencies. For example, we know Git is one
-direct software dependency from the analysis program, which further depends on
-perl, python, rsync, openssh-clients and other packages. The analysis program
-accesses one file called File1, which is one soft link file further referring to
-another name named File2. 
-The implicit dependencies also refers to some files under /pscratch, which is one local mount point of one PanFS clustered file system with the size of 206TB.
-
-Implication: One mechanism which can mine all the dependencies of the program is necessary.
-
-\subsection{Working principle of Packaging Utility}
+\subsubsection{Working principle of Packaging Utility}
 
@@
 
-\subsection{Workflow of Packaging Utility}
+\subsubsection{Workflow of Packaging Utility}
+\begin{figure*}
+\centering
+\epsfig{file=workflow-parrot.eps, height=4in, width=6.5in}
+\caption{Workflow of Solution 4}
+\label{fig:workflow-parrot}
+\end{figure*}
+
+Figure~\ref{fig:workflow-parrot} illustrates the workflow of this solution.
+
 The workflow of generating one package for one analysis program is as follows.
@@
 
-\subsection{Structure of Map File}
+\subsubsection{Structure of Map File}
 
@@
 
-\subsection{Evaluation of Solution 3}
-The breakdown of execution time of the Solution 3 is illustrated in Table~\ref{table:time-3rd}.
+\subsubsection{Discussion of Solution 4}
+
+Under Solution 4, the reproduction of one analysis program becomes easier.
+Rethink Matthias's example, the reproduction of it only needs
+the necessary environment variables, the actual analysis command
+and the package. If different scholars want to repeat one analysis program,
+what they need to do is to obtain the package and rerun the actual analysis
+program. Under Solution 2, each scholar needs to get the necessary data and
+software, and then prepare software environment.
+
+%here is the new content-hmeng
+The starting point of Solution 4 is one successful execution sandbox on the original machine. 
+Parrot traps all the system calls and copies each accessed file (except for common dependencies) into one package.
+The necessary scientific data will be copied into the target package.
+The software dependencies can be divided into two categories: clear dependencies, which can be observed directly through reading the analysis script and implicit dependencies,
+which can not be obtained through reading the analysis script. 
+Parrot can obtain every dependency through trapping each system call.
+Strictly speaking, the software concept and the scientific data concept are lost in Solution 4, because
+the granularity of parrot is file.
+The same thing happens to networked resources.
+Packaging utlity maintains one list of common dependencies and first judges whether the file belongs to this list before trying to copy one file into the package.
+As for the computing environment, Solution 4 notices the new user through the description information at the beginning of the script.
+%the following subsection belongs to the "discussion of data and software
+%preservation" section
+
+\begin{table*}
+    \centering
+    \begin{tabular}{|l|r|r|r|}
+        \hline
+        Solution ID & Data Resources & Software Resources & Operation Manual \\ \hline
+        Solution 1& grid & CMSSW Git HTTP & email \\ \hline
+        Solution 2& local (HDFS) & CMSSW Git HTTP & shell script \\ \hline
+        Solution 4& package & package & shell script + packaging utility \\ \hline
+    \end{tabular}
+    \caption{The relationship of different solutions}
+    \label{table:relationship}
+\end{table*}
+
+%The fourth solution should be based on the third solution.
+during the packaging process, packaging utility first checks whether the file has been inside the target package, (if exists, whether it is the latest version).
+only if the file does not exist in the target package or the file in the target package is not the latest version, the packaging utility copies the file into the target package.
+
+%*****hmeng-doubt: potential risk: different analysis programs share some common file names, but with different file contents. we should analyze the possibility of conflict: data.
+
+%*****hmeng-doubt: in the fourth version, let user to mark whether they change the data and software.
+if changed, one new package is generated to avoid data overlap and pollution.
+otherwise, directly starts packaging process based on the current target package.
+\section{Evaluation}
+\subsection{Relationship of Different Solutions}
+The relationship of these three solutions to repeat one program is shown in Table~\ref{table:relationship}.
+The aim is to make it easier to repeat one program through making the data and software preparation easier.
+
+\subsection{Evaluation of Solution 2}
+The breakdown of execution time of Solution 2 is shown in Table~\ref{table:time-2nd}.
+About half of the total execution time is consumed to prepare relevant software environment.
+The cvs command is forked to check out 23 packages from CMSSW and three git repositories are cloned.
+
+\begin{table}
+    \centering
+    \begin{tabular}{|l|r|r|}
+    \hline
+    Sub-Task & Time & Percentage \\ \hline
+    Software acquisition from CMSSW & 15min 30s & 25.27\% \\ \hline
+    Software acquisition from Git & 9s & 0.24\% \\ \hline
+    Software acquisition from Wget & 36s & 0.98\% \\ \hline
+    Environment Build - SCRAM & 13min 20s & 21.74\% \\ \hline
+    Environment Build - Python & 1s & 0.03\% \\ \hline
+    Data analysis & 31min 44s & 51.74\% \\ \hline
+    Total & 61min 20s & 100.00\% \\ \hline
+    \end{tabular}
+    \caption{Breakdown of Execution Time of Solution 2}
+    \label{table:time-2nd}
+\end{table}
+
+The size of data and software from each category is shown in table~\ref{table:datasize-2nd}.
+
+\begin{table}
+    \centering
+    \begin{tabular}{|l|r|}
+    \hline
+    Data Category & Data Size \\ \hline
+    Software from CMSSW & 449MB \\ \hline
+    Software from Git & 61MB \\ \hline
+    Software from Wget & 52MB \\ \hline
+    Hadoop & 33TB \\ \hline
+    Total & 33792.562GB \\ \hline
+    \end{tabular}
+    \caption{Data Size of Solution 2}
+    \label{table:datasize-2nd}
+\end{table}
+
+\subsection{Evaluation of Solution 4}
+The breakdown of execution time of the Solution 4 is illustrated in Table~\ref{table:time-3rd}.
 The time used to obtain file namelist and generate P1 is greatly longer than the execution time within the new package.
@@
     \end{tabular}
-    \caption{Time Breakdown of Solution 3}
+    \caption{Time Breakdown of Solution 4}
     \label{table:time-3rd}
@@
 
-The data size of Solution 3 is shown in Table~\ref{table:datasize-3rd}. The
+The data size of Solution 4 is shown in Table~\ref{table:datasize-3rd}. The
 data categories is more complex than our imagination. Except the data stored in
@@
     \end{tabular}
-    \caption{Data Size of Solution 3}
+    \caption{Data Size of Solution 4}
     \label{table:datasize-3rd}
@@
 
-\subsection{Discussion of Solution 3}
-
-Under Solution 3, the reproduction of one analysis program becomes easier.
-Rethink Matthias's example, the reproduction of it only needs
-the necessary environment variables, the actual analysis command
-and the package. If different scholars want to repeat one analysis program,
-what they need to do is to obtain the package and rerun the actual analysis
-program. Under Solution 2, each scholar needs to get the necessary data and
-software, and then prepare software environment.
-
-%here is the new content-hmeng
-The starting point of Solution 3 is one successful execution sandbox on the original machine. 
-Parrot traps all the system calls and copies each accessed file (except for common dependencies) into one package.
-The necessary scientific data will be copied into the target package.
-The software dependencies can be divided into two categories: clear dependencies, which can be observed directly through reading the analysis script and implicit dependencies,
-which can not be obtained through reading the analysis script. 
-Parrot can obtain every dependency through trapping each system call.
-Strictly speaking, the software concept and the scientific data concept are lost in Solution 3, because
-the granularity of parrot is file.
-The same thing happens to networked resources.
-Packaging utlity maintains one list of common dependencies and first judges whether the file belongs to this list before trying to copy one file into the package.
-As for the computing environment, Solution 3 notices the new user through the description information at the beginning of the script.
-%the following subsection belongs to the "discussion of data and software
-%preservation" section
-
-\begin{table*}
-    \centering
-    \begin{tabular}{|l|r|r|r|}
-        \hline
-        Solution ID & Data Resources & Software Resources & Operation Manual \\ \hline
-        Solution 3& grid & CMSSW Git HTTP & email \\ \hline
-        Solution 3& local (HDFS) & CMSSW Git HTTP & shell script \\ \hline
-        Solution 3& package & package & shell script + packaging utility \\ \hline
-    \end{tabular}
-    \caption{The relationship of different solutions}
-    \label{table:relationship}
-\end{table*}
-
-%The fourth solution should be based on the third solution.
-during the packaging process, packaging utility first checks whether the file has been inside the target package, (if exists, whether it is the latest version).
-only if the file does not exist in the target package or the file in the target package is not the latest version, the packaging utility copies the file into the target package.
-
-%*****hmeng-doubt: potential risk: different analysis programs share some common file names, but with different file contents. we should analyze the possibility of conflict: data.
-
-%*****hmeng-doubt: in the fourth version, let user to mark whether they change the data and software.
-if changed, one new package is generated to avoid data overlap and pollution.
-otherwise, directly starts packaging process based on the current target package.
-\section{Comparison of different Solutions}
-\subsection{Relationship of Different Solutions}
-The relationship of these three solutions to repeat one program is shown in Table~\ref{table:relationship}.
-The aim is to make it easier to repeat one program through making the data and software preparation easier.
-
-\subsection{ Data size Comparison of Solution 2 and 3}
+\subsection{ Data size Comparison of Solution 2 and 4}
 
@@
      Data Category & Data Size & Data Size \\
-    & Solution 2 & Solution 3\\ \hline
+    & Solution 2 & Solution 4\\ \hline
     Hadoop & 33TB = 33792GB & 20GB \\ \hline
@@
     \end{tabular}
-    \caption{Data Size Comparison beweeen Solution 2 and 3}
+    \caption{Data Size Comparison beweeen Solution 2 and 4}
     \label{table:datasize-2nd3rd}
@@
 
-\subsection{Execution Time Comparison of Solution 2 and 3}
+\subsection{Execution Time Comparison of Solution 2 and 4}
 
@@
 different scholars kept the same under Solution 2, including software and data
-preparation. However, under Solution 3, the data and software preparation is
+preparation. However, under Solution 4, the data and software preparation is
 one-time. The following reproduction of the same program only needs to obtain
 one copy of the package and execute the actual experimental analysis directly.
-Data is obtained through accessing Hadoop Distributed File System in Solution 2, but is copied into the package in Solution 3.
+Data is obtained through accessing Hadoop Distributed File System in Solution 2, but is copied into the package in Solution 4.
 This localization of data speeds up the data analysis process, resulting the actual analysis time reducing from 31 minutes to 13 minutes.
@@
     Task Category & Execution Time & Execution Time \\
-    & Solution 2 & Solution 3\\ \hline
+    & Solution 2 & Solution 4\\ \hline
     Software Acquisition & 16min 15s & N/A \\ \hline
@@
     \end{tabular}
-    \caption{Execution Time Comparison between Solution 2 and 3}
+    \caption{Execution Time Comparison between Solution 2 and 4}
     \label{table:time-2nd3rd}
@@
 \subsection{Preservation Integration of Multiple Programs}
-The Solution 3 can work well for the preservation and reproduction of one single program.
+The Solution 4 can work well for the preservation and reproduction of one single program.
 However, different experimenters may execute different analysis programs on the same dataset using the same or overlapping sets of software.
@@
 Another important factor of data and software preservation is the choice of
-preservation granularity. In Solution 3, the preservation granularity is one
+preservation granularity. In Solution 4, the preservation granularity is one
 file, because Parrot virtual filesystem traps each system call and redirects
@@
 the new user can configure the software environment and repeat the experiment.
-Solution 3 odopts this solution, which is easy to implement, but leaves the
+Solution 4 odopts this solution, which is easy to implement, but leaves the
 complex environment configuration to the new users.
@@
 the path of the directory was recorded into the namelist in the first phrase of
-Solution 3. However, when we repeated the command `ls /dirA` using the
-preserved package, it returned NULL because none of items under it existed in
-the package. If one routine within the original program depends on the return
+Solution 4. However, when we repeated the command `ls /dirA` using the preserved package, it returned NULL because none of items under it existed in
 value of `ls /dirA`, the behavior of the whole program will become incorrect
@@
 into the package. However, the
-time and space overhead appears again. Currently, Solution 3 creates one item
+time and space overhead appears again. Currently, Solution 4 creates one item
 with the same name but the size of zero for each item under /dirA. Another
@@
 At the beginnig of our case study, we generated one package for Matthias's
-example based on Solution 3. Several months later, the original machine meets
+example based on Solution 4. Several months later, the original machine meets
 some problems and the access model of CMSSW was also modified. In this case, if

### 2014-01-24 paper.tex
Added abstract and placed figures at beginning of paper.

@@
 \begin{abstract}
-...
+\it The reproducibility of scientific results increasingly
+depends upon the preservation of computational artifacts.
+Although preserving a computation to be used later sounds
+easy, it is surprisingly difficult due to the complexity
+of existing software and systems.  Implicit dependencies,
+networked resources, and shifting compatibility all conspire
+to break applications that appear to work well.  To investigate
+these issues, we present a case study of a complex high energy
+physics application.  We analyze the application and attempt
+several methods at extracting its dependencies for the purposes
+of preservation.  We report on the completeness, performance,
+and efficiency of each technique, and offer some guidance for
+future work in application preservation.
 \end{abstract}
@@
 
-In this paper, we demonstrate many of these difficulties by presenting
-a case study of a high energy physics application, considered from
-the perspective of preservation.  The application is presented to us
+We do not claim to have solved these problems in any comprehensive
+way.  Rather, our aim in this paper is to highlight the scope
+of the problems by presenting a case study of one complex application.
+The application is presented to us
 first in the form of an email that describes in prose how to install
@@
 
+\begin{figure}[t]
+\centering
+\includegraphics[width=.8\columnwidth]{data-code-size.eps}
+\caption{Inputs to Tau Analysis}
+\label{fig:data-code-size}
+\end{figure}
+
 \section{Overview of Application}
@@
 Both real and simulated data are available for examination.
+
+\begin{table}[t]
+    \centering
+    \small
+    \begin{tabular}{|l|l|r|r|r|}
+        \hline
+        \bf Name & \bf Location & \bf Total & \bf Named & \bf Used \\ 
+        \hline
+        SBEAN data    & hdfs & 33TB & 43.3GB & 20GB \\ \hline
+        CMSSW binaries     & local & 1.16TB & 449MB & 5.2MB\\ \hline
+        Tau source       & git & 51MB & 51MB & 51MB \\ \hline
+        PyYAML binaries    & http & 52MB & 51MB & 51MB \\ \hline
+        .h file       & http & 41KB & 41KB & 41KB \\ \hline
+        Misc commands & hpc fs & 206TB & ??? & 119MB \\ \hline
+        Linux commands & local fs & ??? & ??? & 88.4MB \\ \hline     
+        Total          &          & ??? & ??? & ??? \\ \hline
+    \end{tabular}
+    \caption{Data and Code Used by Tau Analysis}
+    \label{table:size-original-real}
+\end{table}
 
@@
 
+\begin{figure*}
+\centering
+\includegraphics[width=1.6\columnwidth]{version-evolution.eps}
+\caption{Version Evolution}
+\label{fig:version-evolution}
+\end{figure*}
+
 \subsection{Workflow of Matthias's Example}
@@
 
-\begin{figure}
-\centering
-\epsfig{file=dependencies.eps, height=3in, width=3.5in}
-\caption{Dependencies}
-\label{fig:dependencies}
-\end{figure}
-
 Figure~\ref{fig:dependencies} illustrates all the dependencies
@@
 
-\begin{table}
-    \centering
-    \begin{tabular}{|l|r|}
-        \hline
-        Source of Software & Size of Software \\ \hline
-        cmssw\_5\_3\_11\_patch3 & 1.16TB \\ \hline
-        Git & 51MB \\ \hline
-        Public HTTP & 52MB \\ \hline
-        Private home page & 41KB \\ \hline
-    \end{tabular}
-    \caption{Source and Size of Software}
-    \label{table:software-source-size}
-\end{table}
-
 \subsubsection{Complexity of the Program}
@@
 We compared the original size and actually used size of data and software in Table~\ref{table:size-original-real}.
-
-\begin{table}
-    \centering
-    \begin{tabular}{|l|r|r|r|}
-        \hline
-        Source & Original & Referred & Really Used \\ 
-        & Size & Size & Size \\ \hline
-        CMSSW & 1.16TB & 449MB & 5.2MB\\ \hline
-        Git & 51MB & & \\ \hline
-        Public HTTP & 52MB & & \\ \hline
-        Private home page & 41KB & & \\ \hline
-        HDFS & 33TB & 43.3GB & 20GB \\ \hline
-        pscratch & 206TB & & 119MB \\ \hline
-        Local Disk & & & 88.4MB \\ \hline     
-    \end{tabular}
-    \caption{Really Used Data and Software Size}
-    \label{table:size-original-real}
-\end{table}
-
-\begin{figure}
-\centering
-\epsfig{file=data-code-size.eps, height=3in, width=3.5in}
-\caption{Workflow of Tau Analysis}
-\label{fig:data-code-size}
-\end{figure}
 
@@
 \section{Preservation Strategies}
-
-\begin{figure*}
-\centering
-\epsfig{file=version-evolution.eps, height=4in, width=6.5in}
-\caption{Version Evolution}
-\label{fig:version-evolution}
-\end{figure*}
 

### 2014-01-28 paper.tex
add Coarse-Grained Method

--- 2014-01-24 paper.tex
@@
 
+Understanding all the remote and local dependencies of one program, one self-contained package can be built from scratch by copying all the dependencies directly using coarse-grained method,
+which means copying the whole local filesystem, HDFS, PanFS, together with each complete remote repository without selection, into the new package.
+However, the whole OS and local filesystem do not exist only for this special program, and contain a lot of files and software unrelevant to this special program. 
+The size of HDFS, PanFS, remote CMSSW repository all reaches TB level. 
+This solution is easy to implement, but time-consuming and space-consuming.
+Through observation, we noticed that the size of really used data and software is greatly less than the original total size. 
+Therefore, one fine-grained toolkit generating the target package is necessary.
+
 \subsection{Solution 4: Fine-Grained Toolkit}

### 2014-01-29 paper.tex
modify the section 2

@@
 involved in the program, which can be divided into two categories: clear
-dependencies and implicit dependencies. Clear dependencies include data
+dependencies and implicit dependencies. Clear dependencies include scientific data
 dependencies and direct software dependencies which can be extracted directly
-from the analysis program. The scientific data of this example comes from Grid. Direct software dependencies includes CMSSW, Git, HTTP and one personal main page.
+from the analysis program. The scientific data of this example comes from the Grid. Direct software dependencies include CMSSW, Git, HTTP and one personal home page.
 
@@
 perl, python, rsync, openssh-clients and other packages. The analysis program
-accesses one file called File1, which is one soft link file further referring to
-another name named File2.
-The implicit dependencies also refers to some files under /pscratch, which is one local mount point of one PanFS clustered file system with the size of 206TB.
+accesses one file called File1, which is one symbolic link file further referring to
+another file named File2.
+The implicit dependencies also refers to some files under /pscratch, which is a local mount point of one PanFS with the size of 206TB.
 And more importantly, the successful execution of this program greatly depends on the underlying OS and hardware platform.
@@
 The size of data and software dependencies is astonishing.
-The size of the BEAN is 11.6TB, which is too large to be analyzed directly by the Tau Analysis program.
-However, after one preprocessing which only collects the events matching basic quality criteria, the data size is still very large, 43.3GB.
+The size of BEAN is 11.6TB, which is too large to be analyzed directly by the tau analysis program.
+After one preprocessing which only collects the events matching basic quality criteria, the data size is still very large, 43.3GB.
 
@@
 \subsubsection{Complexity of the Program}
-Complex data and software dependencies, complex environment building process, the large size of data and software involved in the Tau analysis, together with the access authority problem, determine the complexity of the program.
+Complex data and software dependencies, complex environment building process, the large size of data and software involved in the tau analysis, together with the access authority problem, determine the complexity of the program.
 In order to obtain the experimental data from the Grid, the author needs to install and config grid-control software. 
@@
 The execution time of actual data analysis is about 30 minutes.
-However, the software acquisition and environment building time is about 30 minutes, which is very close to the execution time of actual data analysis.
-If the acquisition of experimental data is considered, the percentage of actual data analysis only occupies one small pertentage of the whole time consumption.
+However, the software acquisition and environment building time, excluding data acquisition time, is about 30 minutes, which is very close to the execution time of actual data analysis.
+If the acquisition of experimental data is considered, actual data analysis only occupies one small percentage of the whole time consumption.
 The size of data and software dependencies further complicate the program.
 
-\subsubsection{Real Used Data and Software Size}
+\subsubsection{Really Used Data and Software Size}
 
@@
 of really used data and software is greatly smaller.
-Figure~\ref{fig:data-code-size} illustrates the procedures of the Tau analysis.
+Figure~\ref{fig:data-code-size} illustrates the procedures of the tau analysis.
 After SBEAN, the data size is 43.3GB, however, the atual size of really used
-data in the program is 20GB.  The same thend occurs to the size of software and
+data in the program is 20GB.  The same trend occurs to the size of software and
 other dependencies. The size of CMSSW repository is 1.16TB, the size of
@@
 The program involves obtaining software from the home page of another graduate
-student from University of Notre Dame. However, the access authority of this
-home page will termi nate after the graduation of the student. We need one
-mechanism to 
-evaluate the stability of each dependency must be evaluated to ensure the program can be 
+student from University of Notre Dame. However, the maintenance of this
+home page will terminate after the graduation of the student.
+The stability of each dependency must be evaluated to ensure the program can be 
 repeated by others.
 
-The stability of Grid is relatively higher. However, the
+The stability of the Grid is relatively higher. However, the
 public web resources and personal home page is not stable. Too many factors
@@
 certain CMSSW version. At the beginning of our reseach, cvs supported
-anonymous access of CMSSW outside of Cern. However, this anonymous access has
+anonymous access of CMSSW outside of CERN. However, this anonymous access has
 been cancelled now.
@@
 
-The relationship of different roles involved experiment preservation and
+The relationship of different roles involved in the experiment preservation and
 reproduction is shown in Figure~\ref{fig:solution3}.  The original author is
 responsible for generating one package based on the successful execution
-sandbox with the help of the packaging utility. Then the package, together with
+with the help of the packaging utility. Then the package, together with
 its map file and description file will be uploaded into the archive. When

### 2014-01-29 paper.tex
Add little bits about the software used.

@@
 with two top quarks allows to measure the Higgs coupling strength to
-top quarks.  As the Higgs boson is to short-lived to be detected
+top quarks.  As the Higgs boson is too short-lived to be detected
 itself, it has to be reconstructed from its decay products.  The
@@
 containing only trivial data containers packed in vectors.  This step
-is time and CPU intensive and contains data of 11.6$\,$TB to be
-analyzed by the tau analysis.  The BEAN format and data is shared
-within the analysis group looking at Higgs production in association
-with top quarks, which is formed by groups from a few American and
-European universities.
+is time and CPU intensive and its output contains data of 11.6$\,$TB to be
+analyzed by the tau analysis.
+It is performed by a small custom code framework,
+which is built on top of the CMS software stack, CMSSW,
+and uses packages provided by several other special interest groups within CMS.
+While the CMSSW framework is installed locally,
+the various packages used are checked out from CVS,
+and the BEAN framework is stored in git.
+This is scheduled to change,
+as the CMSSW distribution model switches to a virtual filesystem mounted via FUSE,
+and special interest groups move their code to git.
+The BEAN format, production code, and
+data are shared within the analysis group looking at Higgs production
+in association with top quarks, which is formed by groups from a few
+American and European universities,
+consisting of up to a few dozen contributors.
 
@@
 a dataset of 43.3$\,$GB.  Again, the Notre Dame CMS groups cluster
-resources are used to perform this reduction and selection, with
-highly customized software.
+resources are used to perform this reduction and selection,
+running highly customized software,
+built on CMSSW and the BEAN framework,
+but with output code written and maintained by a few people only.
+Again, the code is stored in a git repository.
 
@@
 of expected signal in real data.
+This package is written using the CMSSW build framework,
+but only utilizes code from ROOT,
+a particle physics toolkit underlying CMSSW,
+and a few external python dependencies for convenience.
+The latter have to be manually fetched and installed,
+while the analysis program is built by CMSSW after being checked out of git.
 

### 2014-01-29 paper.tex
Cleaned up introduction.

--- 2014-01-28 paper.tex
@@
 
-\section{Overview of Application}
-
-Matthias, one graduate student from Physics Department of University of Notre
-Dame, finished one interesting tau analysis. Others want to understand how the tau
-analysis works and repeat it.
-
-\subsection{Background}
+\begin{figure}[t]
+\centering
+\includegraphics[width=.8\columnwidth]{data-code-size.eps}
+\caption{Inputs to Tau Analysis}
+\label{fig:data-code-size}
+\end{figure}
+
+\begin{table}[t]
+    \centering
+    \small
+    \begin{tabular}{|l|l|r|r|r|}
+        \hline
+        \bf Name & \bf Location & \bf Total & \bf Named & \bf Used \\ 
+        \hline
+        SBEAN data    & hdfs & 33TB & 43.3GB & 20GB \\ \hline
+        CMSSW binaries     & local & 1.16TB & 449MB & 5.2MB\\ \hline
+        Tau source       & git & 51MB & 51MB & 51MB \\ \hline
+        PyYAML binaries    & http & 52MB & 51MB & 51MB \\ \hline
+        .h file       & http & 41KB & 41KB & 41KB \\ \hline
+        Misc commands & hpc fs & 206TB & ??? & 119MB \\ \hline
+        Linux commands & local fs & ??? & ??? & 88.4MB \\ \hline     
+        Total          &          & ??? & ??? & ??? \\ \hline
+    \end{tabular}
+    \caption{Data and Code Used by Tau Analysis}
+    \label{table:size-original-real}
+\end{table}
+
+\section{Overview of Tau Analysis}
 
@@
 top quarks.  As the Higgs boson is to short-lived to be detected
-itself, it has to be reconstructed from its decay products.  The
-analysis discussed in this section focuses on the Higgs decaying to
-two tau leptons, which are themselves reconstructed from particle
-showers.  Within the analysis, events are identified that show a
-signature of decay products compatible with both hadronic tau and top
-decays.  Properties of such events are used to distinguish signal-like
-(matching simulated Higgs decays) and background-like events and are
-also used in further statistical analysis.
-
+itself, it has to be reconstructed from its decay products.
+
+The application which is the study of this paper is called \emph{TauAnalysis}
+It searches for cases where the the Higgs boson decays to two tau leptons.
+The leptons are not observed directly, but by the particle showers
+that they generate.  So, the analysis must search for detector
+events that show a signature of decay products compatible with both hadronic tau and top decays.  Properties of such events are used to distinguish
+the events of interest (Higgs decays) from all other events and
+are also used in further statistical analysis.
+
+Figure~\ref{fig:data-code-size} shows that both the code and data
+that form \emph{TauAnalysis} are drawn from large repositories through
+multiple steps of reduction.
+
+{\bf Data Sources.}
 The CMS collaboration provides analysis end-users with a pre-processed
@@
 
-% FWIW, units are TB, GB, not TiB, GiB!
+{\bf Code Sources.} Like many scientific codes, the central algorithm
+of \emph{TauAnalysis} is expressed in a relatively small amount of
+custom code developed by the primary author.  But, the code cannot
+run at all without making use of an enormous collection of software
+dependencies.  Some of these dependencies are standard to operating
+systems worldwide, some are standardized across the entire high-energy
+physics field, some are particular to small collaborative groups,
+and a few are very specific to a single researcher.
+
+The largest of these repositories is the CMS Software Distribution (CMSSW),
+a carefully-curated selection of software packages which is distributed
+in binary form.  Historically, CMSSW was downloaded and installed on shared
+filesystems within HPC centers.  In recent years, distribution has moved to
+an on-demand delivery system known as CVMFS~\cite{cvmfs}.  The content
+of CMSSW is managed very carefully by a centralized team whose main goal
+is to ensure that the current version of the software operates correctly
+on the operating systems and architectures currently in use.  However,
+preservation per se is not an objective of the group, and so there is
+no guarantee that old versions of CMSSW operate in new environments,
+or vice versa.
+
+\begin{figure*}
+\centering
+\includegraphics[width=1.6\columnwidth]{version-evolution.eps}
+\caption{Version Evolution}
+\label{fig:version-evolution}
+\end{figure*}
+
+\emph{TauAnalysis} was provided to us in the form of an
+email which described, in prose, how to obtain the source,
+build the program, and run it correctly on one specific
+machine at Notre Dame, with no particularly guarantee that
+it will run anywhere else in the world.
+Although this starting point may seem extreme, it is
+perfectly natural for collaborators to share configurations
+with each other in this form, and to rely on the presence
+of a working environment with appropriate dependencies already
+installed.
+
+The authors played the role of curators, whose job it is to prepare the application for permanent archival by determining and packaging the dependencies.
 
@@
 \subsubsection{Complexity of Data and Software Dependencies}
-
-\begin{figure}
-\centering
-\epsfig{file=dependencies.eps, height=3in, width=3.5in}
-\caption{Dependencies}
-\label{fig:dependencies}
-\end{figure}
 
@@
 The size of software from each source is shown in Table~\ref{table:software-source-size}.
-
-\begin{table}
-    \centering
-    \begin{tabular}{|l|r|}
-        \hline
-        Source of Software & Size of Software \\ \hline
-        cmssw\_5\_3\_11\_patch3 & 1.16TB \\ \hline
-        Git & 51MB \\ \hline
-        Public HTTP & 52MB \\ \hline
-        Private home page & 41KB \\ \hline
-    \end{tabular}
-    \caption{Source and Size of Software}
-    \label{table:software-source-size}
-\end{table}
 
@@
 
-\begin{figure*}
-\centering
-\epsfig{file=version-evolution.eps, height=4in, width=6.5in}
-\caption{Version Evolution}
-\label{fig:version-evolution}
-\end{figure*}
-
 Figure~\ref{fig:version-evolution} illustrates the evolution history of different preservation strategies.
@@
 %%
-
-Understanding all the remote and local dependencies of one program, one self-contained package can be built from scratch by copying all the dependencies directly using coarse-grained method,
-which means copying the whole local filesystem, HDFS, PanFS, together with each complete remote repository without selection, into the new package.
-However, the whole OS and local filesystem do not exist only for this special program, and contain a lot of files and software unrelevant to this special program. 
-The size of HDFS, PanFS, remote CMSSW repository all reaches TB level. 
-This solution is easy to implement, but time-consuming and space-consuming.
-Through observation, we noticed that the size of really used data and software is greatly less than the original total size. 
-Therefore, one fine-grained toolkit generating the target package is necessary.
 

### 2014-01-29 paper.tex

--- 2014-01-29 paper.tex
@@
 with two top quarks allows to measure the Higgs coupling strength to
-top quarks.  As the Higgs boson is too short-lived to be detected
-itself, it has to be reconstructed from its decay products.  The
-analysis discussed in this section focuses on the Higgs decaying to
-two tau leptons, which are themselves reconstructed from particle
-showers.  Within the analysis, events are identified that show a
-signature of decay products compatible with both hadronic tau and top
-decays.  Properties of such events are used to distinguish signal-like
-(matching simulated Higgs decays) and background-like events and are
-also used in further statistical analysis.
-
+top quarks.  As the Higgs boson is to short-lived to be detected
+itself, it has to be reconstructed from its decay products.
+
+The application which is the study of this paper is called \emph{TauAnalysis}
+It searches for cases where the the Higgs boson decays to two tau leptons.
+The leptons are not observed directly, but by the particle showers
+that they generate.  So, the analysis must search for detector
+events that show a signature of decay products compatible with both hadronic tau and top decays.  Properties of such events are used to distinguish
+the events of interest (Higgs decays) from all other events and
+are also used in further statistical analysis.
+
+Figure~\ref{fig:data-code-size} shows that both the code and data
+that form \emph{TauAnalysis} are drawn from large repositories through
+multiple steps of reduction.
+
+{\bf Data Sources.}
 The CMS collaboration provides analysis end-users with a pre-processed

### 2014-02-04 paper.tex
modify version-evolution pic
add related work part

@@
 \affaddr{University of Notre Dame}\\
-\affaddr{\{hmeng|mwolf3|awoodard|pivie|mhildreth|dthain\}@nd.edu}
+\affaddr{\{hmeng|mwolf3|pivie|awoodard|mhildreth|dthain\}@nd.edu}
 }
@@
 \includegraphics[width=.8\columnwidth]{data-code-size.eps}
-\caption{Inputs to Tau Analysis}
+\caption{Inputs to Tau Roast}
 \label{fig:data-code-size}
@@
         \hline
-        SBEAN data    & hdfs & 33TB & 43.3GB & 20GB \\ \hline
+        Ntuples data    & hdfs & 33TB & 43.3GB & 20GB \\ \hline
         CMSSW binaries     & local & 1.16TB & 449MB & 5.2MB\\ \hline
@@
     \end{tabular}
-    \caption{Data and Code Used by Tau Analysis}
+    \caption{Data and Code Used by Tau Roast}
     \label{table:size-original-real}
@@
 
-The application which is the study of this paper is called \emph{TauAnalysis}
+The application which is the study of this paper is called \emph{TauRoast}
 It searches for cases where the the Higgs boson decays to two tau leptons.
@@
 Figure~\ref{fig:data-code-size} shows that both the code and data
-that form \emph{TauAnalysis} are drawn from large repositories through
+that form \emph{TauRoast} are drawn from large repositories through
 multiple steps of reduction.
@@
 In the second step, which is the beginning of the actual tau analysis,
-the data are reduced to variables relevant to the tau analysis, while
+the data are reduced to variables relevant to the tau roast procedure, while
 only events matching basic quality criteria are kept.  This results in
@@
 quality candidate events for the underlying physical process (using
-122$\,$MiB of space).  Quantities from the selected events can be
+about 20$\,$MiB of space).  Quantities from the selected events can be
 both plotted and used in multivariate analysis to determine the level
@@
 {\bf Code Sources.} Like many scientific codes, the central algorithm
-of \emph{TauAnalysis} is expressed in a relatively small amount of
+of \emph{TauRoast} is expressed in a relatively small amount of
 custom code developed by the primary author.  But, the code cannot
@@
 
-\begin{figure*}
-\centering
-\includegraphics[width=1.6\columnwidth]{version-evolution.eps}
-\caption{Version Evolution}
-\label{fig:version-evolution}
-\end{figure*}
-
-\emph{TauAnalysis} was provided to us in the form of an
+\emph{TauRoast} was provided to us in the form of an
 email which described, in prose, how to obtain the source,
@@
 
+\begin{figure}[t]
+\centering
+\includegraphics[width=.8\columnwidth]{dependencies.eps}
+\caption{Dependencies}
+\label{fig:dependencies}
+\end{figure}
+
 Figure~\ref{fig:dependencies} illustrates all the dependencies
@@
 The size of data and software dependencies is astonishing.
-The size of BEAN is 11.6TB, which is too large to be analyzed directly by the tau analysis program.
+The size of BEAN is 11.6TB, which is too large to be analyzed directly by the tau roast program.
 After one preprocessing which only collects the events matching basic quality criteria, the data size is still very large, 43.3GB.
@@
 \subsubsection{Complexity of the Program}
-Complex data and software dependencies, complex environment building process, the large size of data and software involved in the tau analysis, together with the access authority problem, determine the complexity of the program.
+Complex data and software dependencies, complex environment building process, the large size of data and software involved in the tau roast program, together with the access authority problem, determine the complexity of the program.
 In order to obtain the experimental data from the Grid, the author needs to install and config grid-control software. 
@@
 of really used data and software is greatly smaller.
-Figure~\ref{fig:data-code-size} illustrates the procedures of the tau analysis.
-After SBEAN, the data size is 43.3GB, however, the atual size of really used
+Figure~\ref{fig:data-code-size} illustrates the inputs of the tau roast program.
+After the TauAnalysis procedure, the data size of Ntuples is 43.3GB, however, the atual size of really used
 data in the program is 20GB.  The same trend occurs to the size of software and
@@
         5. Fix grid\_control.cfg and run it. \\
-        6. Perform actual analysis \\ 
+        6. Perform actual tau roast program \\ 
         \\ \hline
@@
 
+\begin{figure*}
+\centering
+\includegraphics[width=1.6\columnwidth]{version-evolution.eps}
+\caption{Version Evolution}
+\label{fig:version-evolution}
+\end{figure*}
+
 \section{Preservation Strategies}
@@
 \subsection{Solution 1: Email}
-In order to repeat Matthais's example, the new user consulted the original author by email about the necessary work for the experiment.
-In response, Matthias introduced the general workflow of his tau analysis through one long email including notes, linux shell commands, web links.
-The Version 1 of Table~\ref{table:scripts} illstrates his email.
+
+In order to repeat Matthais's example, the new user consulted the original
+author by email about the necessary work for the experiment. In response,
+Matthias introduced the general workflow of his tau roast program through one long
+email including notes, linux shell commands, web links. The Version 1 of
+Table~\ref{table:scripts} illstrates his email.
 
 However, this solution to repeat one experiment has three potential drawbacks.
-Firstly, the experience of repeating one tau analysis through emails is
+Firstly, the experience of repeating one tau roast program through emails is
 chaotic. You need to constantly jump around multiple web links. There are overlap
@@
 \section{Related Work }
+\subsection{Software Preservation Approaches}
+
+Generally, there are three approaches to preserve software environment:
+technical/hardware preservation, migration and emulation.  Hardware
+preservation preserves the original software and its original operating
+environment. \cite{cifuentes1996binary} presented techniques used to migrate
+legacy software running on register-based machines to modern RISC machines. \cite{mancl2001refactoring}
+utilized one method called refactoring to make software migration become
+easier. However, migration often involves the re-compiling and re-configuring
+the source code to accustom a new hardware platform and software environment.
+Emulation recreate the original software and hardware environment by
+programming future platforms and OSs. One common solution to implement this is
+virtual machine. According to the usage and emulation degree of the real
+machine, virtual machine can be divided into system virtual machine and process
+virtual machine. \cite{goldberg1974survey}\cite{smith2005architecture} introduced the working principle, design principle and
+performance evaluation of system virtual machine. \cite{barham2003xen}\cite{kivity2007kvm}\cite{rosenblum1999vmware} illustrated the
+functionality of  system VM to support different guest operating systems. \cite{esquembre2004easy} illustrated how JVM, one process virtual machine, can expedite the creation of
+scientific simulations in Java. \cite{matthews2009towards}\cite{phelps2005no}\cite{hong2010software} discussed the pros and cons of each
+approach.
+
+\subsection{Software Environment vs Computing Environment}
+
+\cite{matthews2009towards}\cite{phelps2005no}\cite{hong2010software} treated the preservation of computing environment and software environment as one entirety.
+However, frequently changing experiment software makes the maintenance of the preserved experimental environment very complex.
+
+\cite{buncic2010cernvm} treated them as two different categories.
+The preservation of computing environment is implemented with CernVM, and the preservation of software environment is based on a CernVM filesystem(CVMFS) specifically designed for efficient software distribution.
+
+\subsection{Software Preservation Format}
+
+\cite{zabolitzky2002preserving}\cite{castagne2013consider} emphasized the importance of preserving software in source code format.
+
+\cite{buncic2010cernvm} published pre-built and configured experiment software releases to avoid repeating the time-consuming software building procedure.
+
+\subsection{facilitate the reproduction of scientific experiments}
+
+Attempts from different perspectives to facilitate the reproduction of scientific experiments utilizing preserved software library has been made. 
+\cite{compostella2010cdf} discussed software distribution mechanism over the Grid using Parrot. 
+\cite{blomer2011cernvm} proposed CVMFS to facilitate the software distribution over the network to CernVM. 
+\cite{rice1996scientific} made the reproduction process easier through the integration of user interface, scientific software libraries, knowledge base into problem-solving environment.
+\cite{kohn2001divorcing} tried to enable the creation and distribution of language-independent software library by addressing language interoperability.
+
+\subsection{figure out the absolutely relevant data and software }
+
+Current mechanisms of preserving scientific experiments assume that all the data and software mentioned in the experiments are necessary for the reproduction of the experiments.
+However, this is not always right.
+In some cases, the original author may leave additional code referring to irrelative data and software in the experiment programs.
+One mechanism, which can figure out the absolutely relevant data and software of one experiment, is important for both the preservation and reproduction of scientific experiments.
+
+\subsection{the importance of case study}
+\cite{matthews2008significant} introduced one conceptual framework for software preservation from several case studies of software preservation
+\cite{matthews2010framework} designed a tool to capture software preservation properties within a software environment through a series of case studies conducted to evaluate the software preservation framework.
+\cite{johnston2014workflow} proposed one overall data curation workflow for 3-5 case studies of preserving research data.
+To figure out how to preserve HEP applications, this paper studies one case of preserving one representative HEP application.
 
 \section{Conclusion}
-
-this is an example of citing \cite{Laboratories79make}.
 

### 2014-02-04 paper.tex
add the table "Script of each Solution"

@@
         \\
-        1. Create CMS release,\\
-            \hspace{9pt} e.g. cmsrel CMSSW\_5\_3... \\
-        2. Install BEAN packages: \\
-            \hspace{9pt} https://github.com/cms-ttH/...\\
+        1. Create a CMS release,\\
+            \hspace{9pt} e.g. cmsrel CMSSW\_5\_3\_11\_patch3 \\
+        2. Install the BEAN packages as the instructions: \\
+            \hspace{9pt} https://github.com/cms-ttH/BEAN/blob/...\\
         3. Install grid-control: \\ 
-            \hspace{9pt} svn co https://dwekptrack... \\
+            \hspace{9pt} svn co https://ekptrac.physik.uni-ka/... \\
         4. INstall the TauAnalysis package: \\
@@
         5. Fix grid\_control.cfg and run it. \\
-        6. Perform actual tau roast program \\ 
+        6. Perform the actual tau roast program. \\ 
         \\ \hline
@@
         \\
-        set CMSSW\_BASE = (CMSSW\_5\_3...) \\
-        module load git \\        
+        set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3) \\
+        cmsrel \$HOME/\$CMSSW\_BASE \\
+        cvs co -r V03-09-23 PhysicsTools/PatUtils \\
+        git clone https://github.com/cms-ttH/BEAN.git \\
+        wget -r http://nd.edu/~abrinke1/ElectronEffectiveArea.h \\
+        scram b -j32 \\
+        wget http://pyyaml.org/download/pyyaml/PyYAML...\\
+        \#the experiment data is from HDFS \\
+        cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10\\
         cmsenv \\
-        cvs login \\
-        cvs co UserCode/Bicocca/... \\
-        git clone... \\
+        python setup.py install --user \\
+        cd \$HOME/\$CMSSW\_BASE/src/ttH/TauRoast\\
+        scripts/roaster data/generic\_ttl.yaml \\ 
+        \\ \hline
+        version 3: Formulated Script \\ \hline
+        \\
+        set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3) \\
+        set {\bf GIT} = (https://github.com) \\
+        set {\bf PYYAML} = (http://pyyaml.org) \\
+        set {\bf ND} = (http://nd.edu) \\
+        cmsrel \$HOME/\$CMSSW\_BASE \\
+        cvs co -r V03-09-23 PhysicsTools/PatUtils \\
+        git clone \${\bf GIT}/cms-ttH/BEAN.git \\
+        wget -r \${\bf ND}/~abrinke1/ElectronEffectiveArea.h \\
         scram b -j32 \\
-        wget http://pyyaml.org/... \\
-        python setup.py install... \\
+        wget \${\bf PYYAML}/download/pyyaml/PyYAML...\\
         \#the experiment data is from HDFS \\
-        roaster data/generic\_ttl.yaml \\ 
+        cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10\\
+        cmsenv \\
+        python setup.py install --user \\
+        cd \$HOME/\$CMSSW\_BASE/src/ttH/TauRoast\\
+        scripts/roaster data/generic\_ttl.yaml \\ 
         \\ \hline
-        Version 3: Fine-Grained Toolkit\\ \hline
+        Version 4: Fine-Grained Toolkit\\ \hline
         \\
-        \#the description of OS version and hardware architecture \\
-        \# list of indirect software dependencies \\
+        \#description of OS version and hardware architecture \\
+        \#list of indirect software dependencies \\
+        \# set all environment variables\\
         set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3) \\ 
+        cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10\\
         cmsenv \\
-        wget http://pyyaml.org/... \\
-        python setup.py install... \\
-        roaster data/generic\_ttl.yaml \\
-        \\ \hline
-        Version 4\\ \hline
-        \\
-        \#the description of OS version and hardware architecture \\
-        \#declaration of environment variables\\
-        \#data dependencies\\
-        \#direct and indirect software dependencies\\
-        \#software build and install commands\\
-        \#actual analysis program\\ 
+        python setup.py install --user \\
+        cd \$HOME/\$CMSSW\_BASE/src/ttH/TauRoast\\
+        scripts/roaster data/generic\_ttl.yaml \\
         \\ \hline

### 2014-02-10 paper.tex
modify scripts

@@
         \hline
-        Version 1: Email\\ \hline
-        \\
+        {\bf Version 1: Email}\\ \hline
         1. Create a CMS release,\\
@@
         6. Perform the actual tau roast program. \\ 
-        \\ \hline
-        Version 2: Script\\ \hline
-        \\
+        \hline
+        {\bf Version 2: Script}\\ \hline
         set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3) \\
@@
         cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10\\
-        cmsenv \\
+        cmsenv\\
         python setup.py install --user \\
-        cd \$HOME/\$CMSSW\_BASE/src/ttH/TauRoast\\
         scripts/roaster data/generic\_ttl.yaml \\ 
-        \\ \hline
-        version 3: Formulated Script \\ \hline
-        \\
+        \hline
+        {\bf version 3: Formulated Script} \\ \hline
         set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3) \\
@@
         cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10\\
-        cmsenv \\
+        cmsenv\\
         python setup.py install --user \\
-        cd \$HOME/\$CMSSW\_BASE/src/ttH/TauRoast\\
         scripts/roaster data/generic\_ttl.yaml \\ 
-        \\ \hline
-        Version 4: Fine-Grained Toolkit\\ \hline
+        \hline
+        {\bf Version 4: Fine-Grained Toolkit}\\ \hline
+        \#deploy software environment using /archive \\
+        set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3) \\
+        set {\bf GIT} = /archive/git \\
+        set {\bf CMSSW} = /archive/CMSSW \\
+        set {\bf HTTP} = /archive/http \\
+        set {\bf EXP} = /archive/experiment\\
+        set {\bf GRID} = /archive/grid-data \\
+        cmsrel \$HOME/\$CMSSW\_BASE \\
+        archive\_get \${\bf CMSSW}/...\\
+        archive\_get \${\bf GIT}/cms-ttH/BEAN.git \\
+        archive\_get \${\bf EXP}/nd.edu/~abrinke1/... \\        
+        archive\_get \${\bf HTTP}/PyYAML/...\\
+        archive\_get \${\bf GRID}/...\\
+        scram b -j32 \\
+        cmsenv\\
+        python setup.py install --user \\
+        scripts/roaster data/generic\_ttl.yaml \\
+        \hline
+    \end{tabular}
+    \caption{Scripts of each Solution}
+    \label{table:scripts}
+\end{table}
+
+\begin{table}
+    \centering
+    \begin{tabular}{|l|}
+        \hline
         \\
@@
     \end{tabular}
-    \caption{Scripts of each Solution}
-    \label{table:scripts}
+    \caption{Script of Fine-Grained Toolkit using Parrot}
+    \label{table:parrot-script}
 \end{table}
@@
 
-\subsubsection{Working principle of Packaging Utility}
+\section{One Implemention of Fine-Grained Toolkit Using Parrot}
+\subsection{Working principle of Packaging Utility}
 
@@
 The shell script of the Solution 2 is simplified into one new version, which
-only contains the necessary environment variables, access authority and the
-actual analysis command. The Version 3 of Table~\ref{table:scripts} illustrates
+only contains the necessary environment variables and the
+actual analysis command. Table~\ref{table:parrot-script} illustrates
 the simplified script.
 
-\subsubsection{Workflow of Packaging Utility}
+\subsection{Workflow of Packaging Utility}
 \begin{figure*}
@@
 
-\subsubsection{Structure of Map File}
+\subsection{Structure of Map File}
 
@@
 
-\subsubsection{Discussion of Solution 4}
+\subsection{Discussion of Solution 4}
 

### 2014-02-10 paper.tex
section 3 and section 4 modification

@@
 
-\begin{table}
-    \centering
-    \begin{tabular}{|l|}
-        \hline
-        \\
-        \#description of OS version and hardware architecture \\
-        \#list of indirect software dependencies \\
-        \# set all environment variables\\
-        set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3) \\
-        cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10\\
-        cmsenv \\
-        python setup.py install --user \\
-        cd \$HOME/\$CMSSW\_BASE/src/ttH/TauRoast\\
-        scripts/roaster data/generic\_ttl.yaml \\
-        \\ \hline
-    \end{tabular}
-    \caption{Script of Fine-Grained Toolkit using Parrot}
-    \label{table:parrot-script}
-\end{table}
-
 \begin{figure*}
@@
 %*****hmeng-doult: the size of hadoop need to reconsidered. how to correctly illustrate the data size of this example?
-Because the script includes all the necessary procedures for the reproduction of one analysis program, the readability and friendliness of this solution is higher than that of the email format.
-However, each execution of the script will involve the acquisition of software from different sources and the building of software environment.
-As for accessing grid data, using the data copy stored in the machine where Matthias executed the experiment requires the new user to have the authority to access the machine, which complicates the management of the original machine, even is impossible if the original machine executes rigid user access control.
-Granting everyone who wants to repeat the analysis the access authority for grid is unacceptable to system administrator.
+
+Because the script includes all the necessary procedures for the reproduction
+of one analysis program, the readability and friendliness of this solution is
+higher than that of the email format.
+
+\subsection{Solution 3: Formulated Script}
+%%
+
+The script can reduce the complexity of repeating one experiment through the integration of all the necessary procedures.
+However, the data and software dependencies are still randomly distributed across the whole script, which requires one complete scan of the script to obtain the  dependency list.
+
+To further separate the data and software dependencies from the actual analysis
+script, we formulate the Version 2 of Table~\ref{table:scripts}  into one new version, as shown in
+the Version 3 of Table~\ref{table:scripts}. Each new environment variable at the beginning part of
+the script is corresponding to one dependency. All the following access to data
+or software dependency will refer to its corresponding environment variable.
+All the environment variables of dependencies form one map, which maintains the
+target address of each dependency.
+
+This script style may function as one new guideline to the original author of one experiment, which expresses the dependencies more clearly and expedites the preparation process to 
+repeat one experiment.
+The introduction of the map file also reduces the workload of changing one dependency.
+For example, if we want to utilize one new git package to analyze the same dataset, only the change of environment variable corresponding to the original git package is necessary.
+Without the map file, the whole script needs to be scanned to figure out and replace all the references of the original git package.
+
+However, each execution of the script
+will involve the acquisition of software from different sources and the
+building of software environment. As for accessing grid data, using the data
+copy stored in the machine where Matthias executed the experiment requires the
+new user to have the authority to access the machine, which complicates the
+management of the original machine, even is impossible if the original machine
+executes rigid user access control. Granting everyone who wants to repeat the
+analysis the access authority for grid is unacceptable to system administrator.
 
@@
 
-\subsection{Solution 3: Coarse-Grained Method}
-%%
-
-Understanding all the remote and local dependencies of one program, one self-contained package can be built from scratch by copying all the dependencies directly using coarse-grained method,
-which means copying the whole local filesystem, HDFS, PanFS, together with each complete remote repository without selection, into the new package.
-However, the whole OS and local filesystem do not exist only for this special program, and contain a lot of files and software unrelevant to this special program. 
-The size of HDFS, PanFS, remote CMSSW repository all reaches TB level. 
-This solution is easy to implement, but time-consuming and space-consuming.
-Through observation, we noticed that the size of really used data and software is greatly less than the original total size. 
-Therefore, one fine-grained toolkit generating the target package is necessary.
-
-\subsection{Solution 4: Fine-Grained Toolkit}
-
-\section{One Implemention of Fine-Grained Toolkit Using Parrot}
-\subsection{Working principle of Packaging Utility}
-
+\subsection{Solution 4: Package}
 The difficulty of data access authority acquisition enforces us to find out one
@@
 
+To generate one self-contained and independent package for one experiment, all
+the clear and implicit dependencies must be figured out firstly. The map file
+of Solution 3 can provide clear data and software dependencies. As for the
+implicit dependencies, directly preserving the whole OS together with the data
+stored on the disk of the original machine or the data from other filesystems
+mounted as local filesystems, such as HDFS and PanFS,  is not feasible. One
+efficient mechanism which can figure out the really used parts of all these
+filesystems is necessary. The requirements of the underlying OS and hardware
+architecture can be easily found with system tools such as uname or
+lsb\_release.
+
+Then one new package including all the data and software dependencies can be generated and published. 
+One packaging utility is necessary for the original author to generate the package. 
+To multiplex the common data which is involved in different experiments, such as OS images and common software library, the data of different packages will be rearranged and categorized in the archive.
+One description file, which includes the experiment aim, dependency list,  package size and relevant information, will be generated for each package.
+
+\begin{table}
+    \centering
+    \begin{tabular}{|l|l|}
+        \hline
+        Archive Path & Service Description \\ \hline
+        /archive/OS/path & OS Image \\ \hline
+        /archive/software/path & Common Software Library \\ \hline
+        /archive/CMSSW/path & CMS Software Library \\ \hline
+        /archive/git/path & Git Software Library \\ \hline
+        /archive/http/path & http resources \\ \hline
+        /archive/experiment/path & experiment private files \\ \hline
+        /archive/grid-data/path & data from the Grid \\ \hline
+    \end{tabular}
+    \caption{Structure Organization of the Archive}
+    \label{table:archive-map}
+\end{table}
+
+One new version of the analysis script will be generated for the reproduction
+of the original experiment. The Version 4 of Table~\ref{table:scripts} illustrates the format of
+this new version. The environment variables of dependencies refer to the
+storage path inside the archive.  One utility, archive\_get,  is created to
+help the new user to obtain data from the remote archive.
+Table~\ref{table:archive-map} illustrates the structure of the remote archive.
+/archive/OS includes the images of different Operating Systems.
+/archive/software integrates all the commonly used software, such as git,
+python, perl. The archive also organizes the data from CMSSW, Git, HTTP and the
+Grid. /archive/experiment includes the all the experiments submitted into the
+archive. The private files and description files of each experiment will be
+organized together.
+
+The archive supports two different data preservation model: Internal and External.
+Internal method will preserve the data in the archive.
+External method refuses to preserve the content of data, but only preserve the reference to the actual storage place of data.
+For example, the size of experiment data from the Grid is extremely large, and storing the same data in the archive is time-consuming and space-consuming.
+Through External method, the archive only preserves one reference to the data inside the remote Grid.
+
+This solution tries to create one self-contained and independent package for each experiment and integrate different packages for different experiments into one archive to multiplex common data.
+One packaging utility  will be provided to help the original author to generate the package.
+The archive can maintain the experiment dependencies through Internal or External method.
+The archive itself will be responsible for the data maintenance and relevant authority access problem.
+All the new user can repeat one experiment through the interaction with the archive.
+
+\section{One Implemention of Fine-Grained Toolkit Using Parrot}
+\subsection{Working principle of Packaging Utility}
+
 Parrot is a virtual filesystem access tool which attaching existing programs to
@@
 directly execute the actual analysis program inside the package.
+
+\begin{table}
+    \centering
+    \begin{tabular}{|l|}
+        \hline
+        \#description of OS version and hardware architecture \\
+        \#list of indirect software dependencies \\
+        \# set all environment variables\\
+        set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3) \\
+        cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10\\
+        cmsenv \\
+        python setup.py install --user \\
+        cd \$HOME/\$CMSSW\_BASE/src/ttH/TauRoast\\
+        scripts/roaster data/generic\_ttl.yaml \\
+        \hline
+    \end{tabular}
+    \caption{Script of Fine-Grained Toolkit using Parrot}
+    \label{table:parrot-script}
+\end{table}
 

### 2014-02-24 paper.tex
experiment data rearrangement

@@
         \hline
-        Ntuples data    & hdfs & 33TB & 43.3GB & 20GB \\ \hline
-        CMSSW binaries     & local & 1.16TB & 449MB & 5.2MB\\ \hline
-        Tau source       & git & 51MB & 51MB & 51MB \\ \hline
+        Ntuples data    & hdfs & 24TB & 43.3GB & 20GB \\ \hline
+        CMSSW binaries     & local & 1.16TB & 448.3MB & 6.3MB\\ \hline
+        Tau source       & git & 73.7MB & 73.7MB & 73.7MB \\ \hline
         PyYAML binaries    & http & 52MB & 51MB & 51MB \\ \hline
         .h file       & http & 41KB & 41KB & 41KB \\ \hline
-        Misc commands & hpc fs & 206TB & ??? & 119MB \\ \hline
-        Linux commands & local fs & ??? & ??? & 88.4MB \\ \hline     
-        Total          &          & ??? & ??? & ??? \\ \hline
+        Misc commands & PanFS & 155TB & N/A  & 1.6MB \\ \hline
+        Linux commands & localFS & 110GB &  N/A & 68.3MB \\ \hline     
+        CVMFS & CVMFS & 7.4GB & N/A & 103MB \\ \hline
+        NDCMS & optFS & 862GB & N/A & 53KB \\ \hline
+        AFS & AFS &10.2GB & N/A & 34MB\\ \hline
+        Total      &    & 181.1TB            & N/A & 21GB \\ \hline
     \end{tabular}
@@
 \centering
-\epsfig{file=package-info.eps, height=1.5in, width=2.5in}
+\epsfig{file=package-info.eps, height=1.2in, width=2.5in}
 \caption{Package Description Infomation}
@@
     Path used in Program & Actual Location \\ \hline
-    / & /tmp/package1-4 \\ \hline
-    /tmp/package1-4 & /tmp/package1-4 \\ \hline
+    / & /tmp/package-hep \\ \hline
+    /tmp/package-hep & /tmp/package-hep \\ \hline
     /dev & /dev \\ \hline
@@
         Solution 1& grid & CMSSW Git HTTP & email \\ \hline
-        Solution 2& local (HDFS) & CMSSW Git HTTP & shell script \\ \hline
+        Solution 2 and 3& local (HDFS) & CMSSW Git HTTP & shell script \\ \hline
         Solution 4& package & package & shell script + packaging utility \\ \hline
@@
     Sub-Task & Time & Percentage \\ \hline
-    Software acquisition from CMSSW & 15min 30s & 25.27\% \\ \hline
-    Software acquisition from Git & 9s & 0.24\% \\ \hline
-    Software acquisition from Wget & 36s & 0.98\% \\ \hline
-    Environment Build - SCRAM & 13min 20s & 21.74\% \\ \hline
-    Environment Build - Python & 1s & 0.03\% \\ \hline
-    Data analysis & 31min 44s & 51.74\% \\ \hline
-    Total & 61min 20s & 100.00\% \\ \hline
+    Software acquisition from CMSSW & 7min 24s & 21.44\% \\ \hline
+    Software acquisition from Git & 9s & 0.43\% \\ \hline
+    Software acquisition from Wget & 38s & 1.83\% \\ \hline
+    Environment Build - SCRAM & 5min 48s & 16.80\% \\ \hline
+    Environment Build - Python & 1s & 0.05\% \\ \hline
+    Data analysis & 20min 31s & 59.44\% \\ \hline
+    Total & 34min 31s & 100.00\% \\ \hline
     \end{tabular}
@@
     Data Category & Data Size \\ \hline
-    Software from CMSSW & 449MB \\ \hline
-    Software from Git & 61MB \\ \hline
+    Software from CMSSW & 448.3MB \\ \hline
+    Software from Git & 73.7MB \\ \hline
     Software from Wget & 52MB \\ \hline
-    Hadoop & 33TB \\ \hline
-    Total & 33792.562GB \\ \hline
+    HDFS & 43.3GB \\ \hline
+    Total & 43.86GB \\ \hline
     \end{tabular}
@@
     Sub-Task & Time \\ \hline
-    Obtain file namelist & 37min 51s \\ \hline
-    Generate P1 & 13min 37s \\ \hline
-    Re-run the program within P1 & 13min 5s \\ \hline
+    Obtain file namelist & 28min 23s \\ \hline
+    Generate P1 & 85min 51s \\ \hline
+    Re-run the program within P1 & 13min 4s \\ \hline
     \end{tabular}
@@
     \centering
-    \begin{tabular}{|l|r|}
-    \hline
-    Data Category & Data Size \\ \hline
-    Hadoop & 20GB \\ \hline
-    CMSSW\_5\_3\_11\_patch3 & 5.2MB \\ \hline
-    pscratch & 119MB \\ \hline
-    usr & 60MB \\ \hline
-    Others (/sbin + ... + /lib) & 28.4MB \\ \hline
-    Total & 20.213GB \\ \hline
+    \begin{tabular}{|l|l|r|}
+    \hline
+    Data Category &Location & Data Size \\ \hline
+    HDFS & hadoop &20GB \\ \hline
+    PanFS & opt & 1.6MB \\ \hline
+    CVMFS & cvmfs &103MB \\ \hline 
+    NDCMS & opt &53KB \\ \hline
+    AFS & afs &34MB \\ \hline
+    Local FS& bin etc lib lib64 sbin tmp usr&68.3MB \\ \hline
+    Total & &21GB \\ \hline
     \end{tabular}
@@
     & Solution 2 & Solution 4\\ \hline
-    Hadoop & 33TB = 33792GB & 20GB \\ \hline
-     CMSSW\_5\_3\_11\_patch3 & 562MB & 5.2MB \\ \hline
-     Other data for Package & 207.4MB & N/A \\ \hline
-     Total & 33792.562GB & 20.213GB \\ \hline
+    HDFS & 43.3GB & 20GB \\ \hline
+    PanFS & 155TB & 1.6MB \\ \hline
+    CVMFS & 7.4GB &103MB \\ \hline
+    NDCMS & 862GB &53KB \\ \hline
+    AFS & 10.2GB &34MB \\ \hline
+    Local FS& 110GB&68.3MB \\ \hline
+    Total & 156TB &21GB \\ \hline
     \end{tabular}
@@
     & Solution 2 & Solution 4\\ \hline
-    Software Acquisition & 16min 15s & N/A \\ \hline
-    Environment Building & 13min 21s  & 4s \\ \hline
-    Obtain file namelist & N/A & 37min 51s \\ \hline
-    Generate the package & N/A & 13min 37s \\ \hline
-    Actual Analysis & 31min 44s & 13min 1s \\ \hline
-    Total & 61min 20s & N/A \\ \hline
+    Software Acquisition & 8min 11s & N/A \\ \hline
+    Environment Building & 5min 49s  & 3s \\ \hline
+    Obtain file namelist & N/A & 28min 23s \\ \hline
+    Generate the package & N/A & 85min 51s \\ \hline
+    Actual Analysis & 20min 31s & 13min 4s \\ \hline
     \end{tabular}

### 2014-02-26 paper.tex
modify script pic of version4;

@@
         1. Create a CMS release,\\
-            \hspace{9pt} e.g. cmsrel CMSSW\_5\_3\_11\_patch3 \\
+            \hspace{9pt} e.g. {\tt cmsrel CMSSW\_5\_3\_11\_patch3} \\
         2. Install the BEAN packages as the instructions: \\
-            \hspace{9pt} https://github.com/cms-ttH/BEAN/blob/...\\
+            \hspace{9pt} {\tt https://github.com/cms-ttH/BEAN/blob/...}\\
         3. Install grid-control: \\ 
-            \hspace{9pt} svn co https://ekptrac.physik.uni-ka/... \\
+            \hspace{9pt} {\tt svn co https://ekptrac.physik.uni-ka/...} \\
         4. INstall the TauAnalysis package: \\
-           \hspace{9pt} git clone https://github.com/matz-e/... \\
-           \hspace{9pt} scram b -j32 \\
+           \hspace{9pt} {\tt git clone https://github.com/matz-e/...} \\
+           \hspace{9pt} {\tt scram b -j32} \\
         5. Fix grid\_control.cfg and run it. \\
@@
         {\bf Version 2: Script}\\ \hline
-        set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3) \\
-        cmsrel \$HOME/\$CMSSW\_BASE \\
-        cvs co -r V03-09-23 PhysicsTools/PatUtils \\
-        git clone https://github.com/cms-ttH/BEAN.git \\
-        wget -r http://nd.edu/~abrinke1/ElectronEffectiveArea.h \\
-        scram b -j32 \\
-        wget http://pyyaml.org/download/pyyaml/PyYAML...\\
+        {\tt set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3)} \\
+        {\tt cmsrel \$HOME/\$CMSSW\_BASE} \\
+        {\tt cvs co -r V03-09-23 PhysicsTools/PatUtils} \\
+        {\tt git clone {\tt https://github.com/cms-ttH/BEAN.git}} \\
+        {\tt wget -r http://nd.edu/~abrinke1/ElectronEffectiveArea.h} \\
+        {\tt scram b -j32} \\
+        {\tt wget http://pyyaml.org/download/pyyaml/PyYAML...}\\
         \#the experiment data is from HDFS \\
-        cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10\\
-        cmsenv\\
-        python setup.py install --user \\
-        scripts/roaster data/generic\_ttl.yaml \\ 
+        {\tt cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10}\\
+        {\tt cmsenv}\\
+        {\tt python setup.py install --user} \\
+        {\tt scripts/roaster data/generic\_ttl.yaml} \\ 
         \hline
@@
         {\bf Version 4: Fine-Grained Toolkit}\\ \hline
-        \#deploy software environment using /archive \\
         set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3) \\
-        set {\bf GIT} = /archive/git \\
-        set {\bf CMSSW} = /archive/CMSSW \\
-        set {\bf HTTP} = /archive/http \\
-        set {\bf EXP} = /archive/experiment\\
-        set {\bf GRID} = /archive/grid-data \\
+        set {\bf GIT} = (https://github.com) \\
+        set {\bf PYYAML} = (http://pyyaml.org) \\
+        set {\bf ND} = (http://nd.edu) \\
         cmsrel \$HOME/\$CMSSW\_BASE \\
-        archive\_get \${\bf CMSSW}/...\\
-        archive\_get \${\bf GIT}/cms-ttH/BEAN.git \\
-        archive\_get \${\bf EXP}/nd.edu/~abrinke1/... \\        
-        archive\_get \${\bf HTTP}/PyYAML/...\\
-        archive\_get \${\bf GRID}/...\\
+        cvs co -r V03-09-23 PhysicsTools/PatUtils \\
+        git clone \${\bf GIT}/cms-ttH/BEAN.git \\
+        wget -r \${\bf ND}/~abrinke1/ElectronEffectiveArea.h \\
         scram b -j32 \\
+        wget \${\bf PYYAML}/download/pyyaml/PyYAML...\\
+        \#the experiment data is from HDFS \\
+        cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10\\ 
         cmsenv\\
@@
 
+\begin{figure}
+\centering
+\epsfig{file=solution3.eps, height=2in, width=3in}
+\caption{Relationship of Roles}
+\label{fig:solution3}
+\end{figure}
+
+The relationship of different roles involved in the experiment preservation and
+reproduction is shown in Figure~\ref{fig:solution3}.  The original author is
+responsible for generating one package based on the successful execution
+with the help of the packaging utility. Then the package, together with
+its map file and description file will be uploaded into the archive. When
+another scholar wants to repeat the experiment, one copy of the package and its
+corresponding map file will be downloaded into the new machine.
+
 \begin{table}
@@
 
-One new version of the analysis script will be generated for the reproduction
-of the original experiment. The Version 4 of Table~\ref{table:scripts} illustrates the format of
-this new version. The environment variables of dependencies refer to the
-storage path inside the archive.  One utility, archive\_get,  is created to
-help the new user to obtain data from the remote archive.
 Table~\ref{table:archive-map} illustrates the structure of the remote archive.
-/archive/OS includes the images of different Operating Systems.
+\path{/archive/OS} includes the images of different Operating Systems.
 /archive/software integrates all the commonly used software, such as git,
 python, perl. The archive also organizes the data from CMSSW, Git, HTTP and the
-Grid. /archive/experiment includes the all the experiments submitted into the
+Grid. \path{/archive/experiment} includes the all the experiments submitted into the
 archive. The private files and description files of each experiment will be
 organized together.
+
+The Version 4 of Table~\ref{table:scripts} illustrates the script used in
+Solution 4, which is the same as the one used in Solution 3. 
+However, one map file is necessary for the relocation of the data access targets, as
+show in Figure~\ref{fig:version-evolution}. 
+The map file redirects the git access path into /archive/git from the original path (http://github.com) referred in the script.
+This design decouples the experiment script and the actual data access targets, which minimizes the impact of the evolution of different data dependencies
+and ensures the transparent access.
+The modification of the archive only introduces the minimal changes of the map file.
 
@@
 parrot\_run -m /tmp/mountlist /bin/tcsh parrot\_cms.sh
-
-\begin{figure}
-\centering
-\epsfig{file=solution3.eps, height=2in, width=3in}
-\caption{Relationship of Roles}
-\label{fig:solution3}
-\end{figure}
-
-The relationship of different roles involved in the experiment preservation and
-reproduction is shown in Figure~\ref{fig:solution3}.  The original author is
-responsible for generating one package based on the successful execution
-with the help of the packaging utility. Then the package, together with
-its map file and description file will be uploaded into the archive. When
-another scholar wants to repeat the experiment, one copy of the package and its
-corresponding map file will be downloaded into the new machine.
 

### 2014-02-27 paper.tex
modify the format of path and code

@@
 another file named File2.
-The implicit dependencies also refers to some files under /pscratch, which is a local mount point of one PanFS with the size of 206TB.
+The implicit dependencies also refers to some files under {\tt /pscratch}, which is a local mount point of one PanFS with the size of 206TB.
 And more importantly, the successful execution of this program greatly depends on the underlying OS and hardware platform.
@@
 files is only 5.2MB. 
-The total size of PanFS mounted as /pscratch is 206TB, however, the really used data from /pscratch is only 119MB.
+The total size of PanFS mounted as {\tt /pscratch is 206TB}, however, the really used data from {\tt /pscratch} is only 119MB.
 We compared the original size and actually used size of data and software in Table~\ref{table:size-original-real}.
@@
         2. Install the BEAN packages as the instructions: \\
-            \hspace{9pt} {\tt https://github.com/cms-ttH/BEAN/blob/...}\\
+            \hspace{9pt} {\tt \url{https://github.com/cms-ttH/BEAN/blob/...}}\\
         3. Install grid-control: \\ 
-            \hspace{9pt} {\tt svn co https://ekptrac.physik.uni-ka/...} \\
+            \hspace{9pt} {\tt svn co \url{https://ekptrac.physik.uni-ka/...}} \\
         4. INstall the TauAnalysis package: \\
-           \hspace{9pt} {\tt git clone https://github.com/matz-e/...} \\
+           \hspace{9pt} {\tt git clone \url{https://github.com/matz-e/...}} \\
            \hspace{9pt} {\tt scram b -j32} \\
@@
         {\tt cvs co -r V03-09-23 PhysicsTools/PatUtils} \\
-        {\tt git clone {\tt https://github.com/cms-ttH/BEAN.git}} \\
-        {\tt wget -r http://nd.edu/~abrinke1/ElectronEffectiveArea.h} \\
+        {\tt git clone \url{https://github.com/cms-ttH/BEAN.git}} \\
+        {\tt wget -r \url{http://nd.edu/~abrinke1/...}} \\
         {\tt scram b -j32} \\
-        {\tt wget http://pyyaml.org/download/pyyaml/PyYAML...}\\
+        {\tt wget \url{http://pyyaml.org/download/pyyaml/PyYAML...}}\\
         \#the experiment data is from HDFS \\
@@
         {\bf version 3: Formulated Script} \\ \hline
-        set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3) \\
-        set {\bf GIT} = (https://github.com) \\
-        set {\bf PYYAML} = (http://pyyaml.org) \\
-        set {\bf ND} = (http://nd.edu) \\
-        cmsrel \$HOME/\$CMSSW\_BASE \\
-        cvs co -r V03-09-23 PhysicsTools/PatUtils \\
-        git clone \${\bf GIT}/cms-ttH/BEAN.git \\
-        wget -r \${\bf ND}/~abrinke1/ElectronEffectiveArea.h \\
-        scram b -j32 \\
-        wget \${\bf PYYAML}/download/pyyaml/PyYAML...\\
+        {\tt set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3)} \\
+        {\tt set {\bf GIT} = (\url{https://github.com})} \\
+        {\tt set {\bf PYYAML} = (\url{http://pyyaml.org})} \\
+        {\tt set {\bf ND} = (\url{http://nd.edu})} \\
+        {\tt cmsrel \$HOME/\$CMSSW\_BASE} \\
+        {\tt cvs co -r V03-09-23 PhysicsTools/PatUtils} \\
+        {\tt git clone \${\bf GIT}/cms-ttH/BEAN.git} \\
+        {\tt wget -r \${\bf ND}\url{/~abrinke1/ElectronEffectiveArea.h}} \\
+        {\tt scram b -j32} \\
+        {\tt wget \${\bf PYYAML}/download/pyyaml/PyYAML...}\\
         \#the experiment data is from HDFS \\
-        cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10\\
-        cmsenv\\
-        python setup.py install --user \\
-        scripts/roaster data/generic\_ttl.yaml \\ 
+        {\tt cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10}\\
+        {\tt cmsenv}\\
+        {\tt python setup.py install --user} \\
+        {\tt scripts/roaster data/generic\_ttl.yaml} \\ 
         \hline
        {\bf Version 4: Fine-Grained Toolkit}\\ \hline
-        set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3) \\
-        set {\bf GIT} = (https://github.com) \\
-        set {\bf PYYAML} = (http://pyyaml.org) \\
-        set {\bf ND} = (http://nd.edu) \\
-        cmsrel \$HOME/\$CMSSW\_BASE \\
-        cvs co -r V03-09-23 PhysicsTools/PatUtils \\
-        git clone \${\bf GIT}/cms-ttH/BEAN.git \\
-        wget -r \${\bf ND}/~abrinke1/ElectronEffectiveArea.h \\
-        scram b -j32 \\
-        wget \${\bf PYYAML}/download/pyyaml/PyYAML...\\
+        {\tt set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3)} \\
+        {\tt set {\bf GIT} = (\url{https://github.com})} \\
+        {\tt set {\bf PYYAML} = (\url{http://pyyaml.org})} \\
+        {\tt set {\bf ND} = (\url{http://nd.edu})} \\
+        {\tt cmsrel \$HOME/\$CMSSW\_BASE} \\
+        {\tt cvs co -r V03-09-23 PhysicsTools/PatUtils} \\
+        {\tt git clone \${\bf GIT}/cms-ttH/BEAN.git} \\
+        {\tt wget -r \${\bf ND}\url{/~abrinke1/ElectronEffectiveArea.h}} \\
+        {\tt scram b -j32} \\
+        {\tt wget \${\bf PYYAML}/download/pyyaml/PyYAML...}\\
         \#the experiment data is from HDFS \\
-        cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10\\ 
-        cmsenv\\
-        python setup.py install --user \\
-        scripts/roaster data/generic\_ttl.yaml \\
+        {\tt cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10}\\
+        {\tt cmsenv}\\
+        {\tt python setup.py install --user} \\
+        {\tt scripts/roaster data/generic\_ttl.yaml} \\ 
         \hline
@@
         Archive Path & Service Description \\ \hline
-        /archive/OS/path & OS Image \\ \hline
-        /archive/software/path & Common Software Library \\ \hline
-        /archive/CMSSW/path & CMS Software Library \\ \hline
-        /archive/git/path & Git Software Library \\ \hline
-        /archive/http/path & http resources \\ \hline
-        /archive/experiment/path & experiment private files \\ \hline
-        /archive/grid-data/path & data from the Grid \\ \hline
+        {\tt /archive/OS/path} & OS Image \\ \hline
+        {\tt /archive/software/path} & Common Software Library \\ \hline
+        {\tt /archive/CMSSW/path} & CMS Software Library \\ \hline
+        {\tt /archive/git/path} & Git Software Library \\ \hline
+        {\tt /archive/http/path} & http resources \\ \hline
+        {\tt /archive/experiment/path} & experiment private files \\ \hline
+        {\tt /archive/grid-data/path} & data from the Grid \\ \hline
     \end{tabular}
@@
 Table~\ref{table:archive-map} illustrates the structure of the remote archive.
-\path{/archive/OS} includes the images of different Operating Systems.
-/archive/software integrates all the commonly used software, such as git,
+{\tt /archive/OS} includes the images of different Operating Systems.
+{\tt /archive/software} integrates all the commonly used software, such as git,
 python, perl. The archive also organizes the data from CMSSW, Git, HTTP and the
-Grid. \path{/archive/experiment} includes the all the experiments submitted into the
+Grid. {\tt /archive/experiment} includes the all the experiments submitted into the
 archive. The private files and description files of each experiment will be
@@
 show in Figure~\ref{fig:version-evolution}. 
-The map file redirects the git access path into /archive/git from the original path (http://github.com) referred in the script.
+The map file redirects the git access path into {\tt /archive/git} from the original path (\path{http://github.com}) referred in the script.
 This design decouples the experiment script and the actual data access targets, which minimizes the impact of the evolution of different data dependencies
@@
 Parrot is a virtual filesystem access tool which attaching existing programs to
-a variety of remote I/O systems including http, ftp, gridftp, irods, HDFS,
+a variety of remote {\tt I/O} systems including http, ftp, gridftp, irods, HDFS,
 xrootd, grow and chirp. It traps all system calls of one program through ptrace
-debugging interface, and replaces them with remote I/O operations as desired.
+debugging interface, and replaces them with remote {\tt I/O} operations as desired.
 Through executing one program under Parrot, all the paths of files involved in
@@
         \hline
-        \#description of OS version and hardware architecture \\
-        \#list of indirect software dependencies \\
-        \# set all environment variables\\
-        set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3) \\
-        cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10\\
-        cmsenv \\
-        python setup.py install --user \\
-        cd \$HOME/\$CMSSW\_BASE/src/ttH/TauRoast\\
-        scripts/roaster data/generic\_ttl.yaml \\
+        {\tt set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3)} \\
+        {\tt cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10}\\
+        {\tt cmsenv} \\
+        {\tt python setup.py install --user} \\
+        {\tt cd \$HOME/\$CMSSW\_BASE/src/ttH/TauRoast}\\
+        {\tt scripts/roaster data/generic\_ttl.yaml} \\
         \hline
@@
 
-The command used to generate the file name list is as follows. The `-L` parameter refers to the path of the file containing all the accessed file name of the experiment.
-
-parrot\_run -L namelist /bin/tcsh parrot\_cms.sh
-
-The original ouput of this command is one namelist file with the size of 5.7MB
-and 128,711 lines, each of which corresponds to one one accessed file of the
+The command used to generate the file name list is as follows. The {\tt -L} parameter refers to the path of the file containing all the accessed file name of the experiment.
+
+{\tt parrot\_run -L namelist /bin/tcsh script\_v4.sh}
+
+The original ouput of this command is one namelist file with the size of 6.6MB
+and 132,058 lines, each of which corresponds to one one accessed file of the
 program. We noticed that some items appeared multiple times. To reduce the
 packaging time, de-duplication and sorting techoniques are used for the
-namelist file, generating one smaller file with the size of 5.7MB and 42,385
-lines.
+namelist file, generating one smaller file with the size of 3.2MB and 67,178 lines.
 
@@
 The command used to generate the package containing all the files of L1 is as follows. 
-`package1-4.sh` is a bash script which iterates each line of L1 and
+{\tt package-utility.sh} is a bash script which iterates each line of L1 and
 determines the behavior according to the file type (common files, directories,
@@
 
-parrot\_run /bin/bash package1-4.sh -L ~/namelist
-
-%*****lack: file content + metadata; only file metadata; different process solutions
-Each file inside L1 is copied into the package, the final path of the file becomes the path of the package, followed by the original file path.
-In this program, the path of the package is /tmp/package1-4, so the final path of one file with the original path path1 is /tmp/package1-4/path1.
+{\tt parrot\_run /bin/bash package-utility.sh -L namelist}
+
+%*****lack: file content + metadata; only file metadata; different process
+%solutions
+Each file inside L1 is copied into the package, the final path of the file
+becomes the path of the package, followed by the original file path. In this
+program, the path of the package is {\tt /tmp/package-hep}, so the final path of one
+file with the original path path1 is {\tt /tmp/package-hep/path1}.
 
@@
     Path used in Program & Actual Location \\ \hline
-    / & /tmp/package-hep \\ \hline
-    /tmp/package-hep & /tmp/package-hep \\ \hline
-    /dev & /dev \\ \hline
-    /misc & /misc\\ \hline
-    /net & /net\\ \hline
-    /proc & /proc\\ \hline
-    /sys & /sys\\ \hline
-    /var & /var\\ \hline
-    /selinux & /selinux\\ \hline
+    {\tt /} & {\tt /tmp/package-hep} \\ \hline
+    {\tt /tmp/package-hep} & {\tt /tmp/package-hep} \\ \hline
+    {\tt /dev} & {\tt /dev} \\ \hline
+    {\tt /misc} & {\tt /misc}\\ \hline
+    {\tt /net} & {\tt /net}\\ \hline
+    {\tt /proc} & {\tt /proc}\\ \hline
+    {\tt /sys} & {\tt /sys}\\ \hline
+    {\tt /var} & {\tt /var}\\ \hline
+    {\tt /selinux} & {\tt /selinux}\\ \hline
     \end{tabular}
@@
 
-parrot\_run -m /tmp/mountlist /bin/tcsh parrot\_cms.sh
+{\tt parrot\_run -m /tmp/mountlist /bin/tcsh script\_v4.sh}
 
@@
 For example,
-one item inside the map file is "/dir1 /package-dir1" means that the access to each file and
-subdirectory under /dir1 will be redirected into /package-dir1.
+one item inside the map file is {\tt /dir1 /package-dir1} means that the access to each file and
+subdirectory under {\tt /dir1} will be redirected into {\tt /package-dir1}.
 If the semantics of the map file do not support pattern matching, the size of the map file will become astonishing. 
-/dir1 may contain thousands of files, which will generates thousands of map items and will take more time to redirect file paths.
+{\tt /dir1} may contain thousands of files, which will generates thousands of map items and will take more time to redirect file paths.
 
@@
 that it is impossible to copy the files under certain directories.
-For example, during namelist acquisition process, three special files under /dev directory were recorded into the namelist: tty, null and urandom, which are used for input and output.
+For example, during namelist acquisition process, three special files under {\tt /dev} directory were recorded into the namelist: tty, null and urandom, which are used for input and output.
 We tried to copy these files into the new package, but the packaging utility halted.
-We also noticed that copying the files under directories like /proc is
+We also noticed that copying the files under directories like {\tt /proc} is
 meaningless. Because the process id of one program is random and depends on the
@@
 setting the target path of one file equal to the origin file path inside the
-map file. For example, "/dev /dev" means that when the program needs to access
-files under /dev directory, it will directly use the file under /dev, which is
+map file. For example, {\tt /dev /dev} means that when the program needs to access
+files under {\tt /dev} directory, it will directly use the file under {\tt /dev}, which is
 independent from the namespace of the package. This semantics also makes the
 reference of files outside the package possible. If the new user wants to
-expand the analysis of one program to his own data with the path of /A, he can add the analysis
-code into the analysis script and add one item "/A /A" into the map file.
+expand the analysis of one program to his own data with the path of {\tt /A}, he can add the analysis
+code into the analysis script and add one item {\tt /A /A} into the map file.
 
@@
 data categories is more complex than our imagination. Except the data stored in
-Hadoop and the necessary set of software, files from /pscratch, /sbin, /lib and other
+Hadoop and the necessary set of software, files from {\tt /pscratch, /sbin, /lib} and other
 paths are also necessary for the reproduction of the program.
@@
 tries to construct one independent and self-contained package, necessary files
-from /sbin, /lib and other directories are also copied into the package and
+from {\tt /sbin, /lib} and other directories are also copied into the package and
 denoted as "Other data for Package" in Table~\ref{table:datasize-2nd3rd}.
@@
 However, some operations on one directory depends on each item under it. For
-example, `ls /dirA` is one linux command to list the name of each item under
-/dirA. Because the directory itself has the name list of items under it, only
+example, {\tt ls /dirA} is one linux command to list the name of each item under
+{\tt /dirA}. Because the directory itself has the name list of items under it, only
 the path of the directory was recorded into the namelist in the first phrase of
-Solution 4. However, when we repeated the command `ls /dirA` using the preserved package, it returned NULL because none of items under it existed in
-value of `ls /dirA`, the behavior of the whole program will become incorrect
+Solution 4. However, when we repeated the command {\tt ls /dirA} using the preserved package, it returned NULL because none of items under it existed in
+value of {\tt ls /dirA}, the behavior of the whole program will become incorrect
 and unpredictable.
@@
 time and space overhead appears again. Currently, Solution 4 creates one item
-with the same name but the size of zero for each item under /dirA. Another
+with the same name but the size of zero for each item under {\tt /dirA}. Another
 solution is to introduce one database to preserve the metadata of each file and

### 2014-03-01 paper.tex
add JCDL references

@@
         Linux commands & localFS & 110GB &  N/A & 68.3MB \\ \hline     
-        CVMFS & CVMFS & 7.4GB & N/A & 103MB \\ \hline
-        NDCMS & optFS & 862GB & N/A & 53KB \\ \hline
-        AFS & AFS &10.2GB & N/A & 34MB\\ \hline
+        Cern files & CVMFS & 7.4GB & N/A & 103MB \\ \hline
+        NDCMS & NFS & 862GB & N/A & 53KB \\ \hline
+        Local store & AFS &10.2GB & N/A & 34MB\\ \hline
         Total      &    & 181.1TB            & N/A & 21GB \\ \hline
@@
     HDFS & hadoop &20GB \\ \hline
-    PanFS & opt & 1.6MB \\ \hline
+    PanFS & pscratch & 1.6MB \\ \hline
     CVMFS & cvmfs &103MB \\ \hline 
-    NDCMS & opt &53KB \\ \hline
+    NFS & opt &53KB \\ \hline
     AFS & afs &34MB \\ \hline
@@
     CVMFS & 7.4GB &103MB \\ \hline
-    NDCMS & 862GB &53KB \\ \hline
+    NFS & 862GB &53KB \\ \hline
     AFS & 10.2GB &34MB \\ \hline
@@
 \cite{kohn2001divorcing} tried to enable the creation and distribution of language-independent software library by addressing language interoperability.
-
+\cite{agosti2012envisage} aimed to help non-domain users to utilize the digital archive system developed for domain experts.
+\cite{schoneberg2013scalable} proposed a scalable, distributed and dynamic workflow system for digitization processes.
+\cite{subotic2013distributed} proposed a distributed archival network for process-oriented automatic long-term digital preservation.
 \subsection{figure out the absolutely relevant data and software }
@@
 \cite{johnston2014workflow} proposed one overall data curation workflow for 3-5 case studies of preserving research data.
+\cite{borgman2012data} tried to figure out what types of data are most likely to be used and reused, by whom, and for what purposes through two cases studies.
 To figure out how to preserve HEP applications, this paper studies one case of preserving one representative HEP application.

### 2014-03-02 paper.tex
content modification page 1-6

@@
 \usepackage{url}
+\usepackage[flushleft]{threeparttable}
 \begin{document}
@@
     \end{tabular}
+    \begin{tablenotes}
+      \small
+      \item The first column illustrates the total size of each data and software source; 
+            the second column illustrates the size of the named files from each source;
+            the third column illustrates the size of acutally used data from each source.
+            N/A denotes it is hard to figure out the named size of implicit dependencies directly.        
+    \end{tablenotes}
     \caption{Data and Code Used by Tau Roast}
@@
 filesystems within HPC centers.  In recent years, distribution has moved to
-an on-demand delivery system known as CVMFS~\cite{cvmfs}.  The content
+an on-demand delivery system known as CVMFS~\cite{blomer2011cernvm}.  The content
 of CMSSW is managed very carefully by a centralized team whose main goal
@@
 on the operating systems and architectures currently in use.  However,
-preservation per se is not an objective of the group, and so there is
+preservation is not an objective of the group, and so there is
 no guarantee that old versions of CMSSW operate in new environments,
@@
 another file named File2.
-The implicit dependencies also refers to some files under {\tt /pscratch}, which is a local mount point of one PanFS with the size of 206TB.
-And more importantly, the successful execution of this program greatly depends on the underlying OS and hardware platform.
+The implicit dependencies also include some remote file systems mounted as local file systems, such CVMFS, AFS, NFS, PanFS and HDFS.
+More importantly, the successful execution of this program greatly depends on the underlying OS and hardware platform.
 
@@
 
-The size of software from each source is shown in Table~\ref{table:software-source-size}.
+The first column of Table~\ref{table:size-original-real} illustrates the size of each source of data and software.
+The size of PanFS is as large as 155TB and the size of Ntuples data is 24TB.
+The total size of all the dependencies is about 181TB, which directly makes the idea of preserving the original execution environment completely impossible.
 
@@
 The software acquisition from CMSSW, Git and HTTP and environment building process is time-consuming.
-The execution time of actual data analysis is about 30 minutes.
-However, the software acquisition and environment building time, excluding data acquisition time, is about 30 minutes, which is very close to the execution time of actual data analysis.
+The execution time of actual data analysis is about 20 minutes.
+However, the software acquisition and environment building time, excluding data acquisition time, is about 14 minutes.
 If the acquisition of experimental data is considered, actual data analysis only occupies one small percentage of the whole time consumption.
-The size of data and software dependencies further complicate the program.
+The size of data and software dependencies further complicates the program.
 
@@
 other dependencies. The size of CMSSW repository is 1.16TB, the size of
-packages checked out from CMSSW is 449MB, and the size of actually used CMSSW
-files is only 5.2MB. 
-The total size of PanFS mounted as {\tt /pscratch is 206TB}, however, the really used data from {\tt /pscratch} is only 119MB.
-We compared the original size and actually used size of data and software in Table~\ref{table:size-original-real}.
+packages checked out from CMSSW is 448.3MB, and the size of actually used CMSSW
+files is only 6.3MB. 
+The total size of PanFS mounted as {\tt /pscratch} is 155TB, however, the really used data from {\tt /pscratch} is only 1.6MB.
+The third column of Table~\ref{table:size-original-real} illustrates the size of actually used data and software from each dependency.
 
@@
 from one architecture to another may result in the failure of accessing one
-certain CMSSW version. At the beginning of our reseach, cvs supported
-anonymous access of CMSSW outside of CERN. However, this anonymous access has
+certain CMSSW version. At the beginning of our reseach, we can use the cvs command to
+check out packages from CMSSW anonymously. However, this anonymous access has
 been cancelled now.
@@
         \hline
-       {\bf Version 4: Fine-Grained Toolkit}\\ \hline
+       {\bf Version 4: Fine-Grained Toolkit - Package}\\ \hline
         {\tt set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3)} \\
@@
 
-Figure~\ref{fig:version-evolution} illustrates the evolution history of different preservation strategies.
+Figure~\ref{fig:version-evolution} illustrates the evolution history of
+different preservation strategies. First, an email depicting how to repeat the
+experiment is used. Then, all the necessary steps to reproduce the experiment
+mentioned in the mail are collected into one shell script. In order to decouple
+data sources and data references, one formulated script is introduced
+to express all the dependencies at the beginning of the script in the form of
+environment variables. Finally, this decoupling idea is further extended into
+one map file which keeps the relationship between the data reference in the
+script and the actual storage location. One independent package containing all
+the data and software dependencies is generated to make the reproduction
+process more easier.
 
@@
 
-In order to repeat Matthais's example, the new user consulted the original
+In order to repeat Matthais's example, we consulted the original
 author by email about the necessary work for the experiment. In response,
 Matthias introduced the general workflow of his tau roast program through one long
-email including notes, linux shell commands, web links. The Version 1 of
-Table~\ref{table:scripts} illstrates his email.
+email including notes, linux shell commands, web linksi, as illustrated by the Version 1 of
+Table~\ref{table:scripts}.
 
@@
 third step of this experiment requires the new user to own the access authority
-of the Grid.
+of the Grid and involves the analysis of AOD data with the size of about 400TB.
 
@@
 
-\subsection{Solution 2: Script}
-One possible solution for the access authority problem of grid data is to grant the new user the authority to access gird data directly.
-Another possible solution is let the new user directly operate on the machine the original author used.
-As for the complexity of jumping between multiple web links, people may suggest that letting the original author generate one clear script including all the contents from different web links.
+\subsection{Solution 2: Script} One possible solution for the access authority
+problem of grid data is to grant the new user the authority to access gird data
+directly. Another possible solution is let the new user directly operate on the
+machine the original author used. As for the complexity of jumping between
+multiple web links, people may suggest that the original author
+should generate one script including all the contents from different web links.
 
@@
 
-To further separate the data and software dependencies from the actual analysis
-script, we formulate the Version 2 of Table~\ref{table:scripts}  into one new version, as shown in
+To decouple data sources and data references and make the data dependencies clear, Version 2 of Table~\ref{table:scripts} is formulated into one new version, as shown in
 the Version 3 of Table~\ref{table:scripts}. Each new environment variable at the beginning part of
@@
 
-This script style may function as one new guideline to the original author of one experiment, which expresses the dependencies more clearly and expedites the preparation process to 
-repeat one experiment.
-The introduction of the map file also reduces the workload of changing one dependency.
-For example, if we want to utilize one new git package to analyze the same dataset, only the change of environment variable corresponding to the original git package is necessary.
-Without the map file, the whole script needs to be scanned to figure out and replace all the references of the original git package.
-
-However, each execution of the script
-will involve the acquisition of software from different sources and the
-building of software environment. As for accessing grid data, using the data
+This script style may function as one new guideline to the original author of
+one experiment, which expresses the dependencies more clearly and expedites the
+preparation process to repeat one experiment. The introduction of the map file
+also reduces the workload of changing one dependency. For example, if we want
+to utilize one new git package to analyze the same dataset, only the modification of
+environment variable corresponding to the original git package is necessary.
+Without the map mechanism, the whole script needs to be scanned to figure out and
+replace all the references of the original git package.
+
+So far, the data access authority is ignored and
+the reproduction of the experiment is on the machine the original author used. 
+As for grid data, using the data
 copy stored in the machine where Matthias executed the experiment requires the
@@
 provided to the new user in the format of one self-contained package so that
-the new user can avoid complex data and software acquisition and software
-environment building process. In addition, the requirements of the underlying
-OS and hardware should also be provided to the new user.
-
-\subsection{Solution 4: Package}
+the new user can avoid 
+access authority problems.
+In addition, the requirements of the underlying
+OS and hardware should also be figured out and provided to the new user.
+
+\subsection{Solution 4: Fine-Grained Toolkit - Package}
 The difficulty of data access authority acquisition enforces us to find out one
@@
 to generate the required package. However, letting the original author provide
-the package which can be used by others to repeat the original experiment is
-unrealistic. One reason is that figuring out the underlying dependencies of
-each software is complex and time-consumpting and even impossible for the
+the package. 
+One reason is that figuring out the underlying dependencies of
+each software is complex and time-consuming and even impossible for the
 original author. In this experiment, the machine used for the experiment is one
@@
 To generate one self-contained and independent package for one experiment, all
-the clear and implicit dependencies must be figured out firstly. The map file
+the clear and implicit dependencies must be figured out firstly. The map mechanism
 of Solution 3 can provide clear data and software dependencies. As for the
@@
 One packaging utility is necessary for the original author to generate the package. 
-To multiplex the common data which is involved in different experiments, such as OS images and common software library, the data of different packages will be rearranged and categorized in the archive.
+To multiplex the common data which is involved in different experiments, such as OS images and common software libraries, the data of different packages will be rearranged and categorized in the archive.
 One description file, which includes the experiment aim, dependency list,  package size and relevant information, will be generated for each package.
@@
 reproduction is shown in Figure~\ref{fig:solution3}.  The original author is
-responsible for generating one package based on the successful execution
-with the help of the packaging utility. Then the package, together with
+responsible for generating one package with the help of the packaging utility. Then the package, together with
 its map file and description file will be uploaded into the archive. When

### 2014-03-02 paper.tex
modify section 4: one implementation using parrot

@@
 Table~\ref{table:archive-map} illustrates the structure of the remote archive.
-{\tt /archive/OS} includes the images of different Operating Systems.
-{\tt /archive/software} integrates all the commonly used software, such as git,
+Item {\tt /archive/OS} includes the images of different Operating Systems.
+Item {\tt /archive/software} integrates all the commonly used software, such as git,
 python, perl. The archive also organizes the data from CMSSW, Git, HTTP and the
-Grid. {\tt /archive/experiment} includes the all the experiments submitted into the
+Grid. Item {\tt /archive/experiment} includes the all the experiments submitted into the
 archive. The private files and description files of each experiment will be
@@
 and ensures the transparent access.
-The modification of the archive only introduces the minimal changes of the map file.
-
-The archive supports two different data preservation model: Internal and External.
+The modification of the archive only introduces the minimal changes of the map file on the client side.
+
+The archive supports two different data preservation models: Internal and External.
 Internal method will preserve the data in the archive.
@@
 
-This solution tries to create one self-contained and independent package for each experiment and integrate different packages for different experiments into one archive to multiplex common data.
-One packaging utility  will be provided to help the original author to generate the package.
-The archive can maintain the experiment dependencies through Internal or External method.
-The archive itself will be responsible for the data maintenance and relevant authority access problem.
-All the new user can repeat one experiment through the interaction with the archive.
+This solution tries to create one self-contained and independent package for
+each experiment and integrate different packages for different experiments into
+one archive to multiplex common data. One packaging utility, which can figure out all the really used data of one program  will be provided
+to help the original author to generate the package. The archive can maintain
+the experiment dependencies through Internal or External method. The archive
+itself will be responsible for the data maintenance and relevant authority
+access problem. The new user can repeat one experiment through the
+interaction with the archive.
 
@@
 accessed during the execution process of the actual data analysis. Then,
-according to the file name list, one package containing all the necessary data
+according to the filename list, one package containing all the necessary data
 and software for one analysis program is generated. Next time, when another
@@
 directly execute the actual analysis program inside the package. 
+Figure~\ref{fig:solution3} illustrates the working principle of the packaging utility.
 
@@
 
-The shell script of the Solution 2 is simplified into one new version, which
+Table~\ref{table:parrot-script} illustrates
+the simplified script, which
 only contains the necessary environment variables and the
-actual analysis command. Table~\ref{table:parrot-script} illustrates
-the simplified script.
+actual analysis command.
 
@@
 Figure~\ref{fig:workflow-parrot} illustrates the workflow of this solution.
-
-The workflow of generating one package for one analysis program is as follows.
+Firstly, execute the analysis program under Parrot and obtain one filename list containing all the accessed files.
+Then generate one package containing all the files included in the filename list.
+Finally, rerun the program with the help of the package.
+Each step will be examined in details.
 
@@
 
-Parrot is one virtual file system that can support user access to multiple underlying file systems.
-Parrot traps each system call involved in the process of data access, figures out the type of file system and redirects it into corresponding operations to the accessed file system.
-During this process, each accessed file is recorded into one file with the access type of it, such as open, stat, read and write.
-
-The command used to generate the file name list is as follows. The {\tt -L} parameter refers to the path of the file containing all the accessed file name of the experiment.
+Parrot is one virtual file system that can support user access to multiple
+underlying file systems. Parrot traps each system call involved in the process
+of data access, figures out the type of file system and redirects it into
+corresponding operations to the accessed file system. During this process, each
+accessed file, together with the access type, such as
+open, stat, read and write, is recorded into one file.
+
+The command used to generate the filename list is as follows. The {\tt -L} parameter refers to the path of the file containing all the accessed file name of the experiment.
 
@@
 and 132,058 lines, each of which corresponds to one one accessed file of the
-program. We noticed that some items appeared multiple times. To reduce the
+program. We noticed that some items appeared multiple times in the filename list. To reduce the
 packaging time, de-duplication and sorting techoniques are used for the
@@
 The packaging utility iterates each filename inside L1 and copies it into the
-target package. After finishing the packaging process, the target package
+target package. Finally, the target package
 together with its description information, and one map file, which redirects
 the access of files from different file systems into the files inside the target package, will be
-provided to users. The packaging process also runs within Parrot environment to
+generated as the output of this step. The packaging process also runs within Parrot environment to
 access data from different file systems.
@@
 \end{figure}
-The command used to generate the package containing all the files of L1 is as follows. 
+The command used to generate the package is as follows. 
 {\tt package-utility.sh} is a bash script which iterates each line of L1 and
 determines the behavior according to the file type (common files, directories,
-linked files) and the system call type.
+symbolic link files) and the system call type.
 The package description information is shown in Figure~\ref{fig:package-info}.
@@
 %solutions
-Each file inside L1 is copied into the package, the final path of the file
+Each file inside L1 except for common dependencies is copied into the package, the final path of the file
 becomes the path of the package, followed by the original file path. In this
@@
 file with the original path path1 is {\tt /tmp/package-hep/path1}.
+
+The map relationship between the file access path used in the actual analysis
+program and the actual file location used during the reproduction process is
+kept inside the map file, as illustrated in Table~\ref{table:map-file}.
 
@@
 determine the copy degree of one directory or one common file according to the
-system call type for its path.
-
-The map relationship between the file access path used in the actual analysis
-program and the actual file location used during the reproduction process is
-kept inside the map file. The structure of the map file is shown in Table~\ref{table:map-file}.
+type of the system call.
 
@@
 
-When another scholar wants to repeat one analysis program, the accessed data
-field is limited into the target package with the help of the map file 
-generated in step 2.
-
-Command:
+When another scholar wants to repeat the analysis program, 
+the description of the exepriment environment is firstly referred to build the underlying OS and basic software environment.
+In this example, the only necessary software basis is Parrot.
+Then the scholar can obtain one copy of the package and its map file, and rerun the program using the following command:
 
@@
 If the semantics of the map file do not support pattern matching, the size of the map file will become astonishing. 
-{\tt /dir1} may contain thousands of files, which will generates thousands of map items and will take more time to redirect file paths.
-
-During the packaging process, we noticed
+{\tt /dir1} may contain thousands of files, which will generate thousands of map items and take more time to redirect file paths.
+
+During the packaging process, we notice
 that it is impossible to copy the files under certain directories.
 For example, during namelist acquisition process, three special files under {\tt /dev} directory were recorded into the namelist: tty, null and urandom, which are used for input and output.
-We tried to copy these files into the new package, but the packaging utility halted.
-We also noticed that copying the files under directories like {\tt /proc} is
+Trying to copy these files into the new package would cause the packaging utility halt.
+We also notice that copying the files under directories like {\tt /proc} is
 meaningless. Because the process id of one program is random and depends on the
@@
 
-As for these two file categories, letting
-the program directly utilize the files on the machine, where the new user
+As for these special file paths, letting
+the program directly utilize the files on the new machine, where the new user
 repeats the program, is a better choice. The semantics is implemented by
@@
 map file. For example, {\tt /dev /dev} means that when the program needs to access
-files under {\tt /dev} directory, it will directly use the file under {\tt /dev}, which is
-independent from the namespace of the package. This semantics also makes the
+files under {\tt /dev} directory, it will directly use the file under {\tt /dev} on the new machine, which is
+independent from the namespace of the package. This semantics also make the
 reference of files outside the package possible. If the new user wants to
@@
 Under Solution 4, the reproduction of one analysis program becomes easier.
-Rethink Matthias's example, the reproduction of it only needs
-the necessary environment variables, the actual analysis command
+Rethink Matthias's example, the reproduction only needs
+to set necessary environment variables, the actual analysis command
 and the package. If different scholars want to repeat one analysis program,
@@
 %here is the new content-hmeng
-The starting point of Solution 4 is one successful execution sandbox on the original machine. 
+The starting point of Solution 4 is one successful execution on the original machine. 
 Parrot traps all the system calls and copies each accessed file (except for common dependencies) into one package.
-The necessary scientific data will be copied into the target package.
-The software dependencies can be divided into two categories: clear dependencies, which can be observed directly through reading the analysis script and implicit dependencies,
-which can not be obtained through reading the analysis script. 
-Parrot can obtain every dependency through trapping each system call.
-Strictly speaking, the software concept and the scientific data concept are lost in Solution 4, because
+The necessary scientific data and software dependencies will be copied into the target package.
+Strictly speaking, the concept of software and the concept of the scientific data are lost in Solution 4, because
 the granularity of parrot is file.
@@
 Packaging utlity maintains one list of common dependencies and first judges whether the file belongs to this list before trying to copy one file into the package.
-As for the computing environment, Solution 4 notices the new user through the description information at the beginning of the script.
 %the following subsection belongs to the "discussion of data and software

### 2014-03-03 paper.tex
evalution platform introduction

@@
 \section{Evaluation}
+The section first illustrates the relationship of different preservation and reproduction solutions, then the platform used to evaluate different solutions is introduced.
+The execution time and data size of Solution 2 and 4 are tested and compared.
+It is hard to accurately calculate the time consumption of Solution 1.
+Solution 3 shares the same time consumption and data size with Solution 3.
+
 \subsection{Relationship of Different Solutions}
@@
 The aim is to make it easier to repeat one program through making the data and software preparation easier.
+
+\subsection{Evaluation Platform}
+
+The first three solutions are all directly verified on the machine the original
+author used to execute the experiment, which is convenient but involves access
+authority problem. Solution 4 is verified on the original machine and on one virtual machine.
+To compare the execution time and data size of Solution 4
+with Solution 2, the package generated on the original machine is utilized to
+rerun the experiment on the original machine. This choice avoids the impact of
+different CPUs of the original machine and the new machine to repeat the
+experiment. To completely verify the correctness of Solution 4, one virtual
+machine sharing the same kernel version with the original machine is deployed.
+Then the necessary software environment is configured on the virtual machine,
+and the package together with the map file are copied onto it, and the
+experiment is repeated on the virtual machine.
 

### 2014-03-03 paper.tex
content modification: section 5

@@
         Solution 2 and 3& local (HDFS) & CMSSW Git HTTP & shell script \\ \hline
-        Solution 4& package & package & shell script + packaging utility \\ \hline
+        Solution 4& package & package & user manual of package \\ \hline
     \end{tabular}
@@
 \subsection{Relationship of Different Solutions}
-The relationship of these three solutions to repeat one program is shown in Table~\ref{table:relationship}.
-The aim is to make it easier to repeat one program through making the data and software preparation easier.
+The relationship of these four solutions to repeat one program is shown in Table~\ref{table:relationship}.
+Each new solution tries to make it easier to repeat one program through making the data and software preparation easier.
 
@@
 The breakdown of execution time of Solution 2 is shown in Table~\ref{table:time-2nd}.
-About half of the total execution time is consumed to prepare relevant software environment.
-The cvs command is forked to check out 23 packages from CMSSW and three git repositories are cloned.
+About 40\%  of the total execution time is consumed to prepare relevant software environment.
+The cvs command is called to check out 23 packages from CMSSW and three git repositories are cloned.
 
@@
 
-The size of data and software from each category is shown in table~\ref{table:datasize-2nd}.
+This solution does not support mining of implicit dependencies.
+The size of data and software from each category is shown in table~\ref{table:datasize-2nd}, which only lists the size of each clear dependency.
 
@@
 \subsection{Evaluation of Solution 4}
-The breakdown of execution time of the Solution 4 is illustrated in Table~\ref{table:time-3rd}.
-The time used to obtain file namelist and generate P1 is greatly longer than the execution time within the new package.
-however, the time consumption of file namelist acquisition and package generation is one-time.
-That is, once the package is generated, many users can directly obtain the package and repeat the experiment separately.
+
+The breakdown of execution time of the
+Solution 4 is illustrated in Table~\ref{table:time-3rd}. The time used to
+obtain filename list and generate P1 is greatly longer than the execution time
+within the new package. However, the time consumption of filename list
+acquisition and package generation is one-time. That is, once the package is
+generated, many users can directly obtain the package and repeat the experiment
+separately.
 
@@
 The data size of Solution 4 is shown in Table~\ref{table:datasize-3rd}. The
-data categories is more complex than our imagination. Except the data stored in
-Hadoop and the necessary set of software, files from {\tt /pscratch, /sbin, /lib} and other
-paths are also necessary for the reproduction of the program.
+data categories are more complex than our imagination. Except the data stored in
+Hadoop and the necessary set of software, files from local filesystem and several remote filesystems, such as PanFS, CVMFS, NFS, and AFS, are also necessary for the reproduction of the program.
 
@@
 as small as possible. The total size of Hadoop under Solution 2 is astonishing,
-while the size of Hadoop under the package is decreased to 20GB. The same trend
-applies to the size of CMSSW\_5\_3\_11\_patch3. Because the packaging utility
-tries to construct one independent and self-contained package, necessary files
-from {\tt /sbin, /lib} and other directories are also copied into the package and
-denoted as "Other data for Package" in Table~\ref{table:datasize-2nd3rd}.
+while the size of Hadoop under the package is decreased to 20GB. 
+The total size of PanFS is 155TB, however, the size of the really used data of PanFS is only 1.6MB.
+Table~\ref{table:datasize-2nd3rd} compares the original size and the really used size of each data source.
+Solution 4 reduces the total size of all data sources from 156TB to 21GB.
 
@@
     \hline
-     Data Category & Data Size & Data Size \\
-    & Solution 2 & Solution 4\\ \hline
+     Data Category & Solution2: Size & Solution4: Size \\ \hline
     HDFS & 43.3GB & 20GB \\ \hline
@@
 Table~\ref{table:time-2nd3rd} shows the execution time comparison between
-Solution 2 and 3. The time consumption of the reproduction of one program from
+Solution 2 and 4. The time consumption of the reproduction of one program from
 different scholars kept the same under Solution 2, including software and data
@@
 one copy of the package and execute the actual experimental analysis directly.
-Data is obtained through accessing Hadoop Distributed File System in Solution 2, but is copied into the package in Solution 4.
-This localization of data speeds up the data analysis process, resulting the actual analysis time reducing from 31 minutes to 13 minutes.
+Data is obtained through accessing HDFS in Solution 2, but is copied into the package in Solution 4.
+This localization of experimental data speeds up the data analysis process, resulting the actual analysis time reducing from 20 minutes to 13 minutes.
 
@@
     \hline
-    Task Category & Execution Time & Execution Time \\
-    & Solution 2 & Solution 4\\ \hline
+    Task Category & Solution 2: Time & Solution 4: Time\\ \hline
     Software Acquisition & 8min 11s & N/A \\ \hline
-    Environment Building & 5min 49s  & 3s \\ \hline
+    Environment Build & 5min 49s  & 3s \\ \hline
     Obtain file namelist & N/A & 28min 23s \\ \hline
-    Generate the package & N/A & 85min 51s \\ \hline
+    Generate package & N/A & 85min 51s \\ \hline
     Actual Analysis & 20min 31s & 13min 4s \\ \hline

### 2014-03-03 paper.tex
CMSSW size modification and verification

@@
         Ntuples data    & hdfs & 24TB & 43.3GB & 20GB \\ \hline
-        CMSSW binaries     & local & 1.16TB & 448.3MB & 6.3MB\\ \hline
+        CMSSW binaries     & local & 88.1GB & 448.3MB & 6.3MB\\ \hline
         Tau source       & git & 73.7MB & 73.7MB & 73.7MB \\ \hline
@@
         Local store & AFS &10.2GB & N/A & 34MB\\ \hline
-        Total      &    & 181.1TB            & N/A & 21GB \\ \hline
+        Total      &    & 180.1TB            & N/A & 21GB \\ \hline
     \end{tabular}
@@
 data in the program is 20GB.  The same trend occurs to the size of software and
-other dependencies. The size of CMSSW repository is 1.16TB, the size of
+other dependencies. The size of CMSSW repository is 13.1GB, the size of
 packages checked out from CMSSW is 448.3MB, and the size of actually used CMSSW

### 2014-03-03 paper.tex
content modification: section 6

@@
 \subsection{Preservation Integration of Multiple Programs}
-The Solution 4 can work well for the preservation and reproduction of one single program.
-However, different experimenters may execute different analysis programs on the same dataset using the same or overlapping sets of software.
-Generating one new package for each analysis program from scratch is time-consuming and space-consuming, which makes one data and software preservation mechanism, that can integrate the preservation requirements of different analysis programs, become necessary.
+
+Different experimenters may execute different analysis
+programs on the same dataset using the same or overlapping sets of software.
+Generating one new package for each analysis program from scratch is
+time-consuming and space-consuming, which makes one data and software
+preservation mechanism, that can integrate the preservation requirements of
+different analysis programs, become necessary.
 
@@
 To integrate the data and software from multiple analysis programs into one
-package, the concrete information of data and software, such as size, version,
-source and the number of files, need to be recorded. we also need to design one
-more instructive shell script format, in which the data dependencies and
-software dependencies can be clearly expressed and recognized. The packaging
+archive, the concrete information of data and software, such as size, version,
+source and the number of files, need to be recorded. 
+The packaging
 process needs to be re-organized. Packaging utility needs to maintain one list
-of current software and data subset already stored in the package. When one
-user fork the packaging utility to preserve one program, the
-packaging utility will scan the script, get the data and software dependency
-part, judge whether each dependency has been inside the package, and only add
-the new data and software into the package, and update the package information
+of current software and data subset already stored in the archive. When one
+user utilizes the packaging utility to preserve one program, the
+packaging utility scans the script, gets the data and software dependency
+part, judges whether each dependency has been inside the package, and only adds
+the new data and software into the archive, and updates the package information
 and relavant retrieval information.
@@
 dependency B, belongs two different programs. Without preservation
-integration, B will be preserved twice in the archive, which is
-space-consuming. To improve the utilization efficiency of storage resources,
+integration, B will be preserved twice in the archive. To improve the utilization efficiency of storage resources,
 preservation integration of multiple programs is necessary. In the archive,
-only one copy of B is stored, which is referred by both scripts and script 2.
+only one copy of B is stored, which is referred by both scripts.
 
@@
 Another important factor of data and software preservation is the choice of
-preservation granularity. In Solution 4, the preservation granularity is one
+preservation granularity. In our implementation of Solution 4, the preservation granularity is one
 file, because Parrot virtual filesystem traps each system call and redirects
@@
 
-The preservation policy must concern about the size of data. If its size is
+The preservation policy must concern about the size of data. If data size is
 small, copying it into one pacakge and transferring it between different
@@
 The mining degree of data and software dependencies greatly determines the
-repeatability of one experiment. Data dependencies is easy to figured out. However, the situation of software dependencies is complex. The software
-dependencies include OS, hardware platform, 
-direct software dependencies and indirect software dependency which is dependent upon direct software dependencies.
+repeatability of one experiment. Clear data dependencies is easy to figure
+out, but how to figure out implicit data dependencies is complex. The situation
+of software dependencies is more complex. The software dependencies include OS,
+hardware platform, direct software dependencies and indirect software
+dependencies.
 The first
-three categories are easy to deal with. The description of indirect software
-dependencies needs more efforts. One solution is to utlize package management
-tools, like rpm, pacman, apt, to recursively trace each direct software
-dependency and generate one clear dependency graph. With the dependency graph,
-the new user can configure the software environment and repeat the experiment.
-Solution 4 odopts this solution, which is easy to implement, but leaves the
-complex environment configuration to the new users.
-
-Another solution is to treat the computing environment, software environment
+three categories are easy to deal with. The acquisition of indirect software
+dependencies needs more efforts.
+
+One solution is to treat the computing environment, software environment
 and scientific data as one integral entirety and preserve the entirety
@@
 time and space overhead of this solution must be considered.
+
+Another solution is to utlize package management
+tools, like rpm, pacman, apt, to recursively trace each direct software
+dependency and generate one clear dependency graph. With the dependency graph,
+the new user can configure the software environment and repeat the experiment.
+
+The third solution is to trace the system calls of the experiment execution process
+and record the paths of accessed files, which including the files of software dependencies.
+Parrot adopts this solution. Even if git is one software dependency, there is no necessary to install git on the new machine.
+All the files to guarantee the accurate execution of git has been copied into the package.
 
@@
 Directory is one list of files and subdirectories under it. At first, we only
-copied the accessed items under one directory and ignored the unaccessed items.
+copy the accessed items under one directory and ignored the unaccessed items.
 However, some operations on one directory depends on each item under it. For
@@
 {\tt /dirA}. Because the directory itself has the name list of items under it, only
-the path of the directory was recorded into the namelist in the first phrase of
-Solution 4. However, when we repeated the command {\tt ls /dirA} using the preserved package, it returned NULL because none of items under it existed in
-value of {\tt ls /dirA}, the behavior of the whole program will become incorrect
+the path of the directory is recorded into the namelist in the first phrase of
+Solution 4. However, when we repeat the command {\tt ls /dirA} using the preserved package, it returns NULL because none of items under it exists in
+the package, the behavior of the whole program will become incorrect
 and unpredictable.
@@
 
-Through this case study, we noticed that the user access module of remote data
+The user access module of remote data
 and software has a great impact of the preservation mechanism, especially when
@@
 At the beginnig of our case study, we generated one package for Matthias's
-example based on Solution 4. Several months later, the original machine meets
+example based on Solution 4. Several months later, the original machine met
 some problems and the access model of CMSSW was also modified. In this case, if

### 2014-03-07 paper.tex
add introduction to section 4 and 6

@@
 \section{One Implemention of Fine-Grained Toolkit Using Parrot}
+
+The section introduces our implementation of one fine-grained packaging utility based on Solution 4. With the help of one
+virtual filesystem access tool, Parrot, we trap all system calls of one
+program through ptrace debugging interface, and collect all the names of accessed files. 
+Then one self-contained package containing all the accessed files is generated to help others repeat the experiment.
+
 \subsection{Working principle of Packaging Utility}
@@
 \section{Discussion of Data and Software Preservation}
+
+This section concludes the important lessons of data and software preservation and experiment reproduction learnt from this case study. 
+The necessity of preservation integration of multiple programs, preservation granularity, how to preserve large data, how to mine data and software dependencies,
+the presrvation degree of the original filesystems, the importance of investigating user access model of data and software, will be discussed.
+
 \subsection{Preservation Integration of Multiple Programs}

### 2014-03-07 paper.tex
modify related work part

@@
 \section{Related Work }
-\subsection{Software Preservation Approaches}
 
 Generally, there are three approaches to preserve software environment:
-technical/hardware preservation, migration and emulation.  Hardware
+hardware preservation, migration and emulation.  Hardware
 preservation preserves the original software and its original operating
-environment. \cite{cifuentes1996binary} presented techniques used to migrate
-legacy software running on register-based machines to modern RISC machines. \cite{mancl2001refactoring}
-utilized one method called refactoring to make software migration become
-easier. However, migration often involves the re-compiling and re-configuring
+environment. 
+Software migration technique \cite{cifuentes1996binary,mancl2001refactoring} was used to facilitate running software on new machines.
+However, migration often involves the re-compiling and re-configuring
 the source code to accustom a new hardware platform and software environment.
-Emulation recreate the original software and hardware environment by
+Emulation recreates the original software and hardware environment by
 programming future platforms and OSs. One common solution to implement this is
@@
 machine, virtual machine can be divided into system virtual machine and process
-virtual machine. \cite{goldberg1974survey}\cite{smith2005architecture} introduced the working principle, design principle and
-performance evaluation of system virtual machine. \cite{barham2003xen}\cite{kivity2007kvm}\cite{rosenblum1999vmware} illustrated the
-functionality of  system VM to support different guest operating systems. \cite{esquembre2004easy} illustrated how JVM, one process virtual machine, can expedite the creation of
-scientific simulations in Java. \cite{matthews2009towards}\cite{phelps2005no}\cite{hong2010software} discussed the pros and cons of each
-approach.
-
-\subsection{Software Environment vs Computing Environment}
-
-\cite{matthews2009towards}\cite{phelps2005no}\cite{hong2010software} treated the preservation of computing environment and software environment as one entirety.
+virtual machine. 
+The working principle, design principle and
+performance evaluation of system virtual machine were illustrated in \cite{goldberg1974survey, smith2005architecture}. 
+The
+functionality of system VM to support different guest operating systems was illustrated in \cite{barham2003xen,kivity2007kvm,rosenblum1999vmware}.
+F. Esquembre \cite{esquembre2004easy} illustrated how JVM, one process virtual machine, can expedite the creation of
+scientific simulations in Java. 
+The pros and cons of these three approaches were discussed in \cite{matthews2009towards,phelps2005no,hong2010software}.
+
+The preservation of computing environment and software environment was treated as one entirety in \cite{matthews2009towards,phelps2005no,hong2010software}.
 However, frequently changing experiment software makes the maintenance of the preserved experimental environment very complex.
-
-\cite{buncic2010cernvm} treated them as two different categories.
+CernVM \cite{buncic2010cernvm} treated them as two different categories.
 The preservation of computing environment is implemented with CernVM, and the preservation of software environment is based on a CernVM filesystem(CVMFS) specifically designed for efficient software distribution.
 
-\subsection{Software Preservation Format}
-
-\cite{zabolitzky2002preserving}\cite{castagne2013consider} emphasized the importance of preserving software in source code format.
-
-\cite{buncic2010cernvm} published pre-built and configured experiment software releases to avoid repeating the time-consuming software building procedure.
-
-\subsection{facilitate the reproduction of scientific experiments}
+The importance of preserving software in source code format was emphasized in \cite{zabolitzky2002preserving,castagne2013consider}. 
+However, CVMFS \cite{buncic2010cernvm} published pre-built and configured experiment software releases to avoid repeating the time-consuming software building procedure.
 
 Attempts from different perspectives to facilitate the reproduction of scientific experiments utilizing preserved software library has been made. 
-\cite{compostella2010cdf} discussed software distribution mechanism over the Grid using Parrot. 
-\cite{blomer2011cernvm} proposed CVMFS to facilitate the software distribution over the network to CernVM. 
+The software distribution mechanism over network was discussed in \cite{compostella2010cdf, blomer2011cernvm}.
+J.
+R.
+Rice et al.
 \cite{rice1996scientific} made the reproduction process easier through the integration of user interface, scientific software libraries, knowledge base into problem-solving environment.
-\cite{kohn2001divorcing} tried to enable the creation and distribution of language-independent software library by addressing language interoperability.
-\cite{agosti2012envisage} aimed to help non-domain users to utilize the digital archive system developed for domain experts.
-\cite{schoneberg2013scalable} proposed a scalable, distributed and dynamic workflow system for digitization processes.
-\cite{subotic2013distributed} proposed a distributed archival network for process-oriented automatic long-term digital preservation.
-\subsection{figure out the absolutely relevant data and software }
+S. R. Kohn et al. \cite{kohn2001divorcing} tried to enable the creation and distribution of language-independent software library by addressing language interoperability.
+a scalable, distributed and dynamic workflow system for digitization processes was proposed in \cite{schoneberg2013scalable}.
+A distributed archival network was designed in \cite{subotic2013distributed} to facilitate process-oriented automatic long-term digital preservation.
+M. Agosti et al. \cite{agosti2012envisage} aimed to help non-domain users to utilize the digital archive system developed for domain experts.
 
@@
 
-\subsection{the importance of case study}
-\cite{matthews2008significant} introduced one conceptual framework for software preservation from several case studies of software preservation
-\cite{matthews2010framework} designed a tool to capture software preservation properties within a software environment through a series of case studies conducted to evaluate the software preservation framework.
-\cite{johnston2014workflow} proposed one overall data curation workflow for 3-5 case studies of preserving research data.
-\cite{borgman2012data} tried to figure out what types of data are most likely to be used and reused, by whom, and for what purposes through two cases studies.
+B. Matthews et al. \cite{matthews2008significant} introduced one conceptual framework for software preservation from several case studies of software preservation.
+One tool to capture software preservation properties within a software environment was designed in \cite{matthews2010framework} through a series of case studies conducted to evaluate the software preservation framework.
+L. R. Johnston et al. \cite{johnston2014workflow} proposed one overall data curation workflow for 3-5 case studies of preserving research data.
+Two case studies \cite{borgman2012data} were conducted to figure out the properties of data to be reused in the future, including type, purpose, new users.
 To figure out how to preserve HEP applications, this paper studies one case of preserving one representative HEP application.

### 2014-03-11 paper.tex
add conclusion

@@
 
+In this paper, we tries to illustrate the challenges involved in data and software preservation and reproduction through one case study in preserving one High Energy Physics application.
+Four different solutions to repeat the original application, together with the pros and cons of each one, are proposed and analyzed.
+Each new solution aims to improve the reproductivity of the application and reduce the complexity of reproduction.
+Finally, we propose one fine-grained packaging toolkit to help the original author to generate one independent package containing all the necessary dependencies
+
 \bibliographystyle{abbrv}

### 2014-03-13 paper.tex
add conclusion

@@
 Each new solution aims to improve the reproductivity of the application and reduce the complexity of reproduction.
-Finally, we propose one fine-grained packaging toolkit to help the original author to generate one independent package containing all the necessary dependencies
+Finally, we propose one fine-grained packaging toolkit to help the original author to generate one independent package containing all the necessary dependencies except for common dependencies, and repeat the experiment from scratch on two Amazon EC2 virtual machines successfully.
+
+In the future, more case studies will be investigated to verify the correctness of our packaging toolkit. The challenges we propose in this paper will also be investigated.
 

### 2014-03-13 paper.tex
add the execution time on virtual machines

@@
 different CPUs of the original machine and the new machine to repeat the
-experiment. To completely verify the correctness of Solution 4, one virtual
+experiment.
+
+To completely verify the correctness of Solution 4, one virtual
 machine sharing the same kernel version with the original machine is deployed.
 Then the necessary software environment is configured on the virtual machine,
-and the package together with the map file are copied onto it, and the
+and the package is copied onto it, and the
 experiment is repeated on the virtual machine.
+
+One virtual machine from amazon EC2 is used to verify the reproducibility of the experiment.
+Table~\ref{table:config-vm} illustrates the configuration of the original machine and each virtual machine.
+All the machines adopt x86\_64 hardware platform and linux OS.
+Both the local VM and EC2 VM repeat the experiment with the help of the package generated on the original machine successfully.
+
+\begin{table}
+    \centering
+    \begin{tabular}{|l|r|r|r|r|}
+    \hline
+    Machine & Kernel & Distro & CPU & Mem\\ 
+    Type & Version & Version & Cores & (GB)\\ \hline
+    earth  & 2.6.18-371.4.1.el5 & RedHat 5.10 & 64 & 125 \\ \hline 
+    local VM& 2.6.18-371.4.1.el5 & CentOS 5.10 & 4 & 2 \\ \hline
+    EC2 VM& 2.6.18-348.el5xen & RedHat 5.9 & 16 & 60.5 \\ \hline
+    \end{tabular}
+    \caption{Configuration of Different Machines}
+    \label{table:config-vm}
+\end{table}
+
+The configuration of earth machine. The configuration of our virtual machine. The configuration of amazon ec2.
+each vm: data download time; untar time; script execution time;
 
@@
     \label{table:time-2nd3rd}
+\end{table}
+
+\subsection{Excution Time on Different Machines}
+Table~\ref{table:time-vm} shows the execution time of the experiment on different machines - the original machine, local VM and EC2 VM. 
+Each machine utilizes the package generated on the original machine (i.e. earth) to repeat the experiment.
+The execution time on one machine greatly depends on its hardware configuration, which is shown in Table~\ref{table:config-vm}.
+
+\begin{table}
+    \centering
+    \begin{tabular}{|l|r|}
+    \hline
+    Machine Type & Execution Time \\ \hline
+    earth & 13min 4s \\ \hline
+    EC2 VM & 13min 30s\\ \hline
+    local VM & 21min 38s \\ \hline
+    \end{tabular}
+    \caption{Execution Time on Different Machines}
+    \label{table:time-vm}
 \end{table}

### 2014-03-13 paper.tex
figure size modify

@@
 \centering
-\epsfig{file=solution3.eps, height=2in, width=3in}
+\includegraphics[width=.8\columnwidth]{solution3.eps}
 \caption{Relationship of Roles}
@@
 \centering
-\epsfig{file=workflow-parrot.eps, height=4in, width=6.5in}
+\includegraphics[width=1.6\columnwidth]{workflow-parrot.eps}
 \caption{Workflow of Solution 4}
@@
 
-\begin{figure}
-\centering
-\epsfig{file=package-info.eps, height=1.2in, width=2.5in}
-\caption{Package Description Infomation}
-\label{fig:package-info}
-\end{figure}
 The command used to generate the package is as follows. 
@@
 symbolic link files) and the system call type.
-The package description information is shown in Figure~\ref{fig:package-info}.
+The package description information is shown in Table~\ref{table:package-info}.
+
+\begin{table}
+    \centering
+    \begin{tabular}{|l|l|}
+    \hline
+     the total size of package&21GB \\ \hline
+    the total number of files&15905\\ \hline
+    the total number of directory&1549\\ \hline
+    the total number of symbolic link&4614 \\ \hline
+    \end{tabular}
+    \caption{Structure of Map File}
+    \label{table:map-file}
+\end{table}
 
@@
 \centering
-\epsfig{file=preservation-integration.eps, height=2.2in, width=3.3in}
+\includegraphics[width=.8\columnwidth]{preservation-integration.eps}
 \caption{Preservation Integration of Multiple Programs}

### 2014-03-13 paper.tex
add reference

@@
 
-Reproducibility is a cornerstone of the scientific process.
+Reproducibility is a cornerstone of the scientific process ~\cite{borgman2012data}.
 In order to understand, verify, and build upon previous work,
@@
 reproducibility must also encompass the environments, data, and software
-involved in each result. It is widely recognized that informal
+involved in each result ~\cite{zabolitzky2002preserving}. It is widely recognized that informal
 descriptions of software and systems -- although common -- are insufficient
@@
 \begin{itemize}
-\item The {\bf computing environment}, consisting of the basic hardware and the operating system can be preserved as physical artifacts or as a combination of virtual machine monitor (hardware) and virtual machine image (operating system).
+\item The {\bf computing environment}, consisting of the basic hardware and the operating system can be preserved as physical artifacts or as a combination of virtual machine monitor (hardware) and virtual machine image (operating system) ~\cite{matthews2009towards}.
 \item The {\bf scientific data} to be analyzed has historically received the most attention for curation.
@@
 interested reader can obtain and re-use. This approach has
-been used to some success with systems X, Y, and Z.
+been used to some success with systems like JVM ~\cite{barthe2008preservation}.
 \footnote{Of course, we are glossing over the problem that hardware
@@
 are inherently external to the system, such as a database, a code
-repository, or a scalable filesystem.  For such resources, it
+repository ~\cite{cms2006cmssw}, or a scalable filesystem ~\cite{blomer2011cernvm}.  For such resources, it
 must be decided whether the dependency will simply be noted, or if it
@@
 Within the ongoing investigation of the Higgs boson at the CMS
-detector, part of the LHC at CERN, the Higgs production in association
+detector, part of the LHC at CERN ~\cite{collaboration2008cms}, the Higgs production in association
 with two top quarks allows to measure the Higgs coupling strength to
@@
 The CMS collaboration provides analysis end-users with a pre-processed
-and reduced data format, AOD, containing information for events, i.e.,
+and reduced data format, AOD ~\cite{holtman2001cms}, containing information for events, i.e.,
 proton-proton collisions with a signature of interest, in the form of
@@
 It is performed by a small custom code framework,
-which is built on top of the CMS software stack, CMSSW,
+which is built on top of the CMS software stack, CMSSW ~\cite{cms2006cmssw},
 and uses packages provided by several other special interest groups within CMS.
@@
 
-(f) Build software enviroment using SCRAM and Python
-
-(g) Install grid control, obtain CMS data from grid and store the data into HDFS mounted as one local file system.
+(f) Build software enviroment using SCRAM ~\cite{rabbertz2004cms} and Python
+
+(g) Install grid control ~\cite{holtman2001cms}, obtain CMS data from grid and store the data into HDFS ~\cite{borthakur2008hdfs} mounted as one local file system.
 
@@
 another file named File2.
-The implicit dependencies also include some remote file systems mounted as local file systems, such CVMFS, AFS, NFS, PanFS and HDFS.
+The implicit dependencies also include some remote file systems mounted as local file systems, such CVMFS, AFS ~\cite{howard1988scale}, NFS ~\cite{sandberg1985design}, PanFS ~\cite{welch2008scalable} and HDFS.
 More importantly, the successful execution of this program greatly depends on the underlying OS and hardware platform.
@@
 To completely verify the correctness of Solution 4, one virtual
-machine sharing the same kernel version with the original machine is deployed.
+machine ~\cite{goldberg1974survey} sharing the same kernel version with the original machine is deployed.
 Then the necessary software environment is configured on the virtual machine,
@@
 
-One virtual machine from amazon EC2 is used to verify the reproducibility of the experiment.
+One virtual machine from amazon EC2 ~\cite{amazon2010amazon} is used to verify the reproducibility of the experiment.
 Table~\ref{table:config-vm} illustrates the configuration of the original machine and each virtual machine.
@@
 \centering
-\includegraphics[width=.8\columnwidth]{preservation-integration.eps}
+\includegraphics[width=1\columnwidth]{preservation-integration.eps}
 \caption{Preservation Integration of Multiple Programs}

### 2014-03-13 paper.tex
table bold format + capatilization

@@
         \hline
-        Ntuples data    & hdfs & 24TB & 43.3GB & 20GB \\ \hline
+        Ntuples data    & HDFS& 24TB & 43.3GB & 20GB \\ \hline
         CMSSW binaries     & local & 88.1GB & 448.3MB & 6.3MB\\ \hline
-        Tau source       & git & 73.7MB & 73.7MB & 73.7MB \\ \hline
-        PyYAML binaries    & http & 52MB & 51MB & 51MB \\ \hline
-        .h file       & http & 41KB & 41KB & 41KB \\ \hline
+        Tau source       & Git & 73.7MB & 73.7MB & 73.7MB \\ \hline
+        PyYAML binaries    & HTTP & 52MB & 51MB & 51MB \\ \hline
+        .h file       & HTTP& 41KB & 41KB & 41KB \\ \hline
         Misc commands & PanFS & 155TB & N/A  & 1.6MB \\ \hline
@@
 quality candidate events for the underlying physical process (using
-about 20$\,$MiB of space).  Quantities from the selected events can be
+about 20$\,$MB of space).  Quantities from the selected events can be
 both plotted and used in multivariate analysis to determine the level
@@
 
-\subsection{Workflow of Matthias's Example}
-
-The workflow of Matthias's exmaple can be divided into eight procedures.
+\subsection{Workflow of the Example}
+
+The workflow of the exmaple can be divided into eight procedures.
 
@@
 
-(g) Install grid control ~\cite{holtman2001cms}, obtain CMS data from grid and store the data into HDFS ~\cite{borthakur2008hdfs} mounted as one local file system.
+(g) Install grid control ~\cite{holtman2001cms}, obtain CMS data from Grid and store the data into HDFS ~\cite{borthakur2008hdfs} mounted as one local file system.
 
@@
 dependencies and direct software dependencies which can be extracted directly
-from the analysis program. The scientific data of this example comes from the Grid. Direct software dependencies include CMSSW, Git, HTTP and one personal home page.
+from the analysis program. The scientific data of this example comes from the Grid ~\cite{holtman2001cms}. Direct software dependencies include CMSSW, Git, HTTP and one personal home page.
 
@@
         {\bf Version 2: Script}\\ \hline
-        {\tt set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3)} \\
+        {\tt setenv CMSSW\_BASE CMSSW\_5\_3\_11\_patch3} \\
         {\tt cmsrel \$HOME/\$CMSSW\_BASE} \\
@@
         {\bf version 3: Formulated Script} \\ \hline
-        {\tt set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3)} \\
-        {\tt set {\bf GIT} = (\url{https://github.com})} \\
-        {\tt set {\bf PYYAML} = (\url{http://pyyaml.org})} \\
-        {\tt set {\bf ND} = (\url{http://nd.edu})} \\
+        {\tt setenv CMSSW\_BASE CMSSW\_5\_3\_11\_patch3} \\
+        {\tt setenv {\bf GIT} \url{https://github.com}} \\
+        {\tt setenv {\bf PYYAML} \url{http://pyyaml.org}} \\
+        {\tt setenv {\bf ND} \url{http://nd.edu}} \\
         {\tt cmsrel \$HOME/\$CMSSW\_BASE} \\
@@
        {\bf Version 4: Fine-Grained Toolkit - Package}\\ \hline
-        {\tt set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3)} \\
-        {\tt set {\bf GIT} = (\url{https://github.com})} \\
-        {\tt set {\bf PYYAML} = (\url{http://pyyaml.org})} \\
-        {\tt set {\bf ND} = (\url{http://nd.edu})} \\
+        {\tt setenv CMSSW\_BASE CMSSW\_5\_3\_11\_patch3} \\
+        {\tt setenv {\bf GIT} \url{https://github.com}} \\
+        {\tt setenv {\bf PYYAML} \url{http://pyyaml.org}} \\
+        {\tt setenv {\bf ND} \url{http://nd.edu}} \\
         {\tt cmsrel \$HOME/\$CMSSW\_BASE} \\
@@
 author by email about the necessary work for the experiment. In response,
-Matthias introduced the general workflow of his tau roast program through one long
+the original author introduced the general workflow of his tau roast program through one long
 email including notes, linux shell commands, web linksi, as illustrated by the Version 1 of
@@
 experiment, including software acquisition from different sources, is complex
-for the new user. In Matthias's example, the sources of software includes
+for the new user. In the example, the sources of software includes
 CMSSW, Git, HTTP. The access of CMSSW requires the new user to be an authorized
@@
 \subsection{Solution 2: Script} One possible solution for the access authority
-problem of grid data is to grant the new user the authority to access gird data
+problem of Grid data is to grant the new user the authority to access gird data
 directly. Another possible solution is let the new user directly operate on the
@@
 Version 2 of Table~\ref{table:scripts} illstrates the merged script.
-As for the data acquisition from the Grid, we directly use the local copy in HDFS to avoid requiring the new user to obtain a grid certification.
+As for the data acquisition from the Grid, we directly use the local copy in HDFS to avoid requiring the new user to obtain a Grid certification.
 
@@
 the reproduction of the experiment is on the machine the original author used. 
-As for grid data, using the data
-copy stored in the machine where Matthias executed the experiment requires the
+As for Grid data, using the data
+copy stored in the machine where the original author executed the experiment requires the
 new user to have the authority to access the machine, which complicates the
@@
 executes rigid user access control. Granting everyone who wants to repeat the
-analysis the access authority for grid is unacceptable to system administrator.
+analysis the access authority for Grid is unacceptable to system administrator.
 
@@
 original author. In this experiment, the machine used for the experiment is one
-public machine of physics department, and Matthias is one common user without
+public machine of physics department, and the original author is one common user without
 root authority. The underlying OS and supporting softwares are installed and
@@
         \hline
-        Archive Path & Service Description \\ \hline
+        \bf Archive Path & \bf Service Description \\ \hline
         {\tt /archive/OS/path} & OS Image \\ \hline
@@
         {\tt /archive/git/path} & Git Software Library \\ \hline
-        {\tt /archive/http/path} & http resources \\ \hline
+        {\tt /archive/http/path} & HTTP resources \\ \hline
         {\tt /archive/experiment/path} & experiment private files \\ \hline
@@
 The section introduces our implementation of one fine-grained packaging utility based on Solution 4. With the help of one
-virtual filesystem access tool, Parrot, we trap all system calls of one
+virtual filesystem access tool, Parrot ~\cite{thain2005parrot}, we trap all system calls of one
 program through ptrace debugging interface, and collect all the names of accessed files. 
@@
 Parrot is a virtual filesystem access tool which attaching existing programs to
-a variety of remote {\tt I/O} systems including http, ftp, gridftp, irods, HDFS,
-xrootd, grow and chirp. It traps all system calls of one program through ptrace
+a variety of remote {\tt I/O} systems including 
+HTTP, FTP, GridFTP, iRODS, HDFS, XRootD, GROW, and Chirp. It traps all system calls of one program through ptrace
 debugging interface, and replaces them with remote {\tt I/O} operations as desired.
@@
 be deployed. The starting point of the packaging utility is one successful execution
-sandbox (the data from grid has been preserved in HDFS and the software from
+sandbox (the data from Grid has been preserved in HDFS and the software from
 CMSSW, Git and HTTP has been on the local machine.). We re-execute the actual
@@
 
-(1) execute one analysis program under Parrot and obtain filename list (L1) of it
+{\bf(1)} Execute one analysis program under Parrot and obtain filename list (L1) of it
 
@@
 
-The command used to generate the filename list is as follows. The {\tt -L} parameter refers to the path of the file containing all the accessed file name of the experiment.
-
-{\tt parrot\_run -L namelist /bin/tcsh script\_v4.sh}
+The command used to generate the filename list is as follows. The {\tt name-list} parameter refers to the path of the file containing all the accessed file name of the experiment.
+
+{\tt parrot\_run \texttt{-{}-}name-list namelist /bin/tcsh script\_v4.sh}
 
 The original ouput of this command is one namelist file with the size of 6.6MB
-and 132,058 lines, each of which corresponds to one one accessed file of the
+and 132,047 lines, each of which corresponds to one one accessed file of the
 program. We noticed that some items appeared multiple times in the filename list. To reduce the
 packaging time, de-duplication and sorting techoniques are used for the
-namelist file, generating one smaller file with the size of 3.2MB and 67,178 lines.
-
-(2) generate one package containing the files of L1
+namelist file, generating one smaller file with the size of 3.2MB and 67,168 lines.
+
+{\bf (2)} Generate one package containing the files of L1
 
@@
     \centering
-    \begin{tabular}{|l|l|}
-    \hline
-     the total size of package&21GB \\ \hline
-    the total number of files&15905\\ \hline
-    the total number of directory&1549\\ \hline
-    the total number of symbolic link&4614 \\ \hline
-    \end{tabular}
-    \caption{Structure of Map File}
-    \label{table:map-file}
+    \begin{tabular}{|l|}
+    \hline
+     the total size of package: 21GB \\ 
+    the total number of files: 15905\\ 
+    the total number of directory: 1549\\ 
+    the total number of symbolic link: 4614 \\ \hline 
+    \end{tabular}
+    \caption{Package Infomation}
+    \label{table:package-info}
 \end{table}
@@
     \hline
-    Path used in Program & Actual Location \\ \hline
+    \bf Path used in Program & \bf Actual Location \\ \hline
     {\tt /} & {\tt /tmp/package-hep} \\ \hline
@@
     {\tt /dev} & {\tt /dev} \\ \hline
-    {\tt /misc} & {\tt /misc}\\ \hline
-    {\tt /net} & {\tt /net}\\ \hline
-    {\tt /proc} & {\tt /proc}\\ \hline
-    {\tt /sys} & {\tt /sys}\\ \hline
-    {\tt /var} & {\tt /var}\\ \hline
-    {\tt /selinux} & {\tt /selinux}\\ \hline
+    {\tt ...} & {\tt ...}\\ \hline
     \end{tabular}
@@
 %*****lack: re-execute process: re-execution process will redirect all the data access into the package except for data under proc sys dev selinux
-(3) rerun the analysis program using the package
+{\bf (3)} Repeat the analysis program using the package
 
@@
 In this example, the only necessary software basis is Parrot.
-Then the scholar can obtain one copy of the package and its map file, and rerun the program using the following command:
+Then the scholar can obtain one copy of the package and its map file, and rerun the program using the following command.
+The {\tt m} parameter can be used to refer to the path of map file, which will be explained in the next part.
 
@@
 Under Solution 4, the reproduction of one analysis program becomes easier.
-Rethink Matthias's example, the reproduction only needs
+Rethink the example, the reproduction only needs
 to set necessary environment variables, the actual analysis command
@@
         \hline
-        Solution ID & Data Resources & Software Resources & Operation Manual \\ \hline
-        Solution 1& grid & CMSSW Git HTTP & email \\ \hline
+        \bf Solution ID & \bf Data Resources &\bf Software Resources & \bf Operation Manual \\ \hline
+        Solution 1& Grid & CMSSW Git HTTP & email \\ \hline
         Solution 2 and 3& local (HDFS) & CMSSW Git HTTP & shell script \\ \hline
@@
     \end{tabular}
-    \caption{The relationship of different solutions}
+    \caption{Relationship of Different Solutions}
     \label{table:relationship}
@@
     \hline
-    Machine & Kernel & Distro & CPU & Mem\\ 
-    Type & Version & Version & Cores & (GB)\\ \hline
+    \bf Machine & \bf Kernel Version & \bf Distro & \bf CPU & \bf Mem\\ 
+    \bf Type &  & \bf Version & \bf Cores & (\bf GB)\\ \hline
     earth  & 2.6.18-371.4.1.el5 & RedHat 5.10 & 64 & 125 \\ \hline 
@@
     \hline
-    Sub-Task & Time & Percentage \\ \hline
-    Software acquisition from CMSSW & 7min 24s & 21.44\% \\ \hline
-    Software acquisition from Git & 9s & 0.43\% \\ \hline
-    Software acquisition from Wget & 38s & 1.83\% \\ \hline
-    Environment Build - SCRAM & 5min 48s & 16.80\% \\ \hline
-    Environment Build - Python & 1s & 0.05\% \\ \hline
+    \bf Sub-Task & \bf Time & \bf Percentage \\ \hline
+    Obtain software from CMSSW & 7min 24s & 21.44\% \\ \hline
+    Obtain software from Git & 9s & 0.43\% \\ \hline
+    Obtain software from Wget & 38s & 1.83\% \\ \hline
+    Environment build - SCRAM & 5min 48s & 16.80\% \\ \hline
+    Environment build - Python & 1s & 0.05\% \\ \hline
     Data analysis & 20min 31s & 59.44\% \\ \hline
@@
     \hline
-    Data Category & Data Size \\ \hline
+    \bf Data Category & \bf Data Size \\ \hline
     Software from CMSSW & 448.3MB \\ \hline
@@
     \hline
-    Sub-Task & Time \\ \hline
+    \bf Sub-Task &\bf Time \\ \hline
     Obtain file namelist & 28min 23s \\ \hline
@@
     \hline
-    Data Category &Location & Data Size \\ \hline
+    \bf Data &\bf Location & \bf Data \\ 
+    \bf Category & & \bf Size\\ \hline
     HDFS & hadoop &20GB \\ \hline
@@
     \hline
-     Data Category & Solution2: Size & Solution4: Size \\ \hline
+    \bf Data Category & \bf Solution2: Size & \bf Solution4: Size \\ \hline
     HDFS & 43.3GB & 20GB \\ \hline
@@
     \hline
-    Task Category & Solution 2: Time & Solution 4: Time\\ \hline
+    \bf Task & \bf Solution 2& \bf Solution 4\\ 
+    \bf Category & \bf Time & \bf Time \\ \hline
     Software Acquisition & 8min 11s & N/A \\ \hline
@@
     \hline
-    Machine Type & Execution Time \\ \hline
+    \bf Machine Type & \bf Execution Time \\ \hline
     earth & 13min 4s \\ \hline
@@
 
-At the beginnig of our case study, we generated one package for Matthias's
+At the beginnig of our case study, we generated one package for the
 example based on Solution 4. Several months later, the original machine met
 some problems and the access model of CMSSW was also modified. In this case, if
-you want to repeat Matthias's example on the original machine, different 
+you want to repeat the example on the original machine, different 
 configurations, including CMSSW\_ARCH, environment variables and CVS access

### 2014-03-14 paper.tex
modify figure 1 and table 1

@@
         \hline
-        Ntuples data    & HDFS& 24TB & 43.3GB & 20GB \\ \hline
-        CMSSW binaries     & local & 88.1GB & 448.3MB & 6.3MB\\ \hline
+        Ntuples data    & HDFS& 11.6TB & 43.3GB & 20GB \\ \hline
+        CMSSW code     & CVS & 88.1GB & 448.3MB & 6.3MB\\ \hline
         Tau source       & Git & 73.7MB & 73.7MB & 73.7MB \\ \hline
@@
         Linux commands & localFS & 110GB &  N/A & 68.3MB \\ \hline     
-        Cern files & CVMFS & 7.4GB & N/A & 103MB \\ \hline
-        NDCMS & NFS & 862GB & N/A & 53KB \\ \hline
-        Local store & AFS &10.2GB & N/A & 34MB\\ \hline
+        Configuration & CVMFS & 7.4GB & N/A & 103MB \\ \hline
+        HOME dir& AFS &10.2GB & N/A & 34MB\\ \hline
         Total      &    & 180.1TB            & N/A & 21GB \\ \hline

### 2014-03-14 paper.tex
Rewrote section 3.

@@
-\documentclass{acm_proc_article-sp}
+\documentclass{sig-alternate}
 \usepackage{url}
@@
 a carefully-curated selection of software packages which is distributed
-in binary form.  Historically, CMSSW was downloaded and installed on shared
-filesystems within HPC centers.  In recent years, distribution has moved to
+in several forms.  Historically, components of CMSSW were obtained by checking components
+of the source out of CVS, or by installing a complete binary package on a shared
+filesystem within an HPC center.  In recent years, distribution has moved to
 an on-demand delivery system known as CVMFS~\cite{blomer2011cernvm}.  The content
@@
 
+\section{Observations}
+
 \emph{TauRoast} was provided to us in the form of an
@@
 build the program, and run it correctly on one specific
-machine at Notre Dame, with no particularly guarantee that
+machine at our home institution, with no particular guarantee that
 it will run anywhere else in the world.
@@
 of a working environment with appropriate dependencies already
-installed.
-
-The authors played the role of curators, whose job it is to prepare the application for permanent archival by determining and packaging the dependencies.
-
-\subsection{Workflow of the Example}
-
-The workflow of the exmaple can be divided into eight procedures.
-
-(a) Declare environment variables
-
-(b) Obtain software from CMSSW
-
-(c) Obtain software from Git
-
-(d) Obtain software from some public HTTP web links
-
-(e) Obtain software from one private home page
-
-(f) Build software enviroment using SCRAM ~\cite{rabbertz2004cms} and Python
-
-(g) Install grid control ~\cite{holtman2001cms}, obtain CMS data from Grid and store the data into HDFS ~\cite{borthakur2008hdfs} mounted as one local file system.
-
-(h) Actual data analysis.
-
-\subsection{Key Observations of the Example}
-
-\subsubsection{Complexity of Data and Software Dependencies}
-
-\begin{figure}[t]
-\centering
-\includegraphics[width=.8\columnwidth]{dependencies.eps}
-\caption{Dependencies}
-\label{fig:dependencies}
-\end{figure}
-
-Figure~\ref{fig:dependencies} illustrates all the dependencies
-involved in the program, which can be divided into two categories: clear
-dependencies and implicit dependencies. Clear dependencies include scientific data
-dependencies and direct software dependencies which can be extracted directly
-from the analysis program. The scientific data of this example comes from the Grid ~\cite{holtman2001cms}. Direct software dependencies include CMSSW, Git, HTTP and one personal home page.
-
-Implicit dependencies include indirect software
-dependencies which is necessary for the successful execution of direct software
-dependencies and other implicit dependencies. For example, we know Git is one
-direct software dependency from the analysis program, which further depends on
-perl, python, rsync, openssh-clients and other packages. The analysis program
-accesses one file called File1, which is one symbolic link file further referring to
-another file named File2.
-The implicit dependencies also include some remote file systems mounted as local file systems, such CVMFS, AFS ~\cite{howard1988scale}, NFS ~\cite{sandberg1985design}, PanFS ~\cite{welch2008scalable} and HDFS.
-More importantly, the successful execution of this program greatly depends on the underlying OS and hardware platform.
-
-\subsubsection{Size of Data and Software Dependencies}
-The size of data and software dependencies is astonishing.
-The size of BEAN is 11.6TB, which is too large to be analyzed directly by the tau roast program.
-After one preprocessing which only collects the events matching basic quality criteria, the data size is still very large, 43.3GB.
-
-The first column of Table~\ref{table:size-original-real} illustrates the size of each source of data and software.
-The size of PanFS is as large as 155TB and the size of Ntuples data is 24TB.
-The total size of all the dependencies is about 181TB, which directly makes the idea of preserving the original execution environment completely impossible.
-
-\subsubsection{Complexity of the Program}
-Complex data and software dependencies, complex environment building process, the large size of data and software involved in the tau roast program, together with the access authority problem, determine the complexity of the program.
-In order to obtain the experimental data from the Grid, the author needs to install and config grid-control software. 
-The access authority of the Grid is also necessary for the data acquisition.
-The software acquisition from CMSSW, Git and HTTP and environment building process is time-consuming.
-The execution time of actual data analysis is about 20 minutes.
-However, the software acquisition and environment building time, excluding data acquisition time, is about 14 minutes.
-If the acquisition of experimental data is considered, actual data analysis only occupies one small percentage of the whole time consumption.
-The size of data and software dependencies further complicates the program.
-
-\subsubsection{Really Used Data and Software Size}
-
-Even if the orginal data size referred by the program is astonishing, the size
-of really used data and software is greatly smaller.
-Figure~\ref{fig:data-code-size} illustrates the inputs of the tau roast program.
-After the TauAnalysis procedure, the data size of Ntuples is 43.3GB, however, the atual size of really used
-data in the program is 20GB.  The same trend occurs to the size of software and
-other dependencies. The size of CMSSW repository is 13.1GB, the size of
-packages checked out from CMSSW is 448.3MB, and the size of actually used CMSSW
-files is only 6.3MB. 
-The total size of PanFS mounted as {\tt /pscratch} is 155TB, however, the really used data from {\tt /pscratch} is only 1.6MB.
-The third column of Table~\ref{table:size-original-real} illustrates the size of actually used data and software from each dependency.
-
-\subsubsection{Stability of Dependencies}
-
-The program involves obtaining software from the home page of another graduate
-student from University of Notre Dame. However, the maintenance of this
-home page will terminate after the graduation of the student.
-The stability of each dependency must be evaluated to ensure the program can be 
-repeated by others.
-
-The stability of the Grid is relatively higher. However, the
-public web resources and personal home page is not stable. Too many factors
-like the termination of one web site, the graduation of the home page's author,
-would result in the failure of resource access. CMSSW, which seems to be
-stable, in fact, also involves stability problems. CMSSW provides different
-collections of accessible versions to different architectures. Transformation
-from one architecture to another may result in the failure of accessing one
-certain CMSSW version. At the beginning of our reseach, we can use the cvs command to
-check out packages from CMSSW anonymously. However, this anonymous access has
-been cancelled now.
+installed.  From this starting point, the authors played the
+role of curators, whose job it is to prepare the application
+for permanent archival.
+
+First, we elaborated the email instructions into an
+executable script that obtains the dependencies and then
+executes the analysis.  The script declares the necessary
+environment variables, downloads and checks out the necessary source code,
+builds it appropriately, calls initialization scripts in
+the dependent software, and then runs the analysis.
+A few rounds of correction with the original author were necessary
+to obtain all the dependencies and run the artifact correctly.
+(The original email also indicated how to run the application
+within a production batch system.  For the purposes of preservation,
+we consider the execution infrastructure to be distinct from the application,
+and leave it out of consideration for now.)
+
+The process of elaborating the program into a script revealed
+several observations about this type of application:
+
+\begin{itemize}
+
+\item {\bf Many Explicit External Dependencies.}  TauRoast depends on a large number of
+external dependencies, each with a different access method and data source.
+While we knew in advance that it depended upon the large CMSSW distribution,
+it was not apparent until elaborating the script that it depended upon
+two different Github repositories for the Tau source,
+a CVS server at CERN for some configuration information, a public web page
+for the PyYAML library, and the public home page of a Notre Dame student
+for one missing header file.  (The latter is particularly troubling!)
+While, at some level, the authors and users of these software know of these dependencies, they are often missing in
+informal communications or forgotten once the dependency is install.
+However, once known, they are at least expressed explicitly within the script.
+
+{\bf Many Implicit Local Dependencies.} A much harder problem is that the
+application assumed the presence of many different components in the local
+filesystem view.  It would be tempting to capture all of these by simply
+storing a virtual machine image containing the local filesystem.  However,
+the application dependend on no less than {\bf six} networked filesystems
+available on a particular machine available to the author:
+the data to be analyzed was stored on an HDFS~\cite{hadoop} cluster,
+some configuration data was stored on a CVMFS~\cite{cvmfs} filesystem,
+and a variety of software tools were on an NFS~\cite{howard1988scale},
+pNFS~\cite{welch2008scalable} and AFS~\cite{sandberg1985design} systems.
+The original authors were not aware of many of these dependencies,
+because they simply relied on local administrators to configure the
+software and make it available.
+
+\item {\bf Configuration Complexity.}  As a means of controlling the complexity
+of dependent software packages, the high energy physics community has developed
+a number of tools that perform run-time configuration and consistency checks
+of the available software.  {\tt scram} is the software management tool used
+by the CMS experiment.  Before running any code, {\tt scram} is used to locate
+the appropriate version software,  set environment variables such as the PATH, run any
+tool-specific configuration, and do the same for all software on which it depends.
+If the correct versions are not available, {\tt scram} halts and emits an error.
+While this procedure has great value for consistency, it also introduces a significant cost
+because it involves a large number of nested scripts traversing a filesystem,
+repeatedly looking up metadata.  In our example, the time to perform this configuration
+with a cold cache is about 14 minutes, which is almost as large as the actual analysis
+run, which takes 20 minutes.
+
+{\bf High Selectivity.}  Although the total size of the resources accessed by this
+program is very large, the size of the data and software actually used are much smaller.
+Often, an entire repository or data source is named within the script, but the program
+only needs a handful of items from that source.  For example, the data is stored on an
+HDFS filesystem with 24TB of data, but only 43GB of that are the input Ntuples,
+and of those only 20GB are actually consumed by the program. The CMSSW repository is 88GB in total
+but only 448MB in source are checked out, and the software actually used only
+measured 6.3MB.  In a few cases, a source of software is named but never actually accessed.
+(For example, our original script includes the Open Science Grid software stack in the PATH, but does not actually use it.)
+We suspect that end users are accustomed to missing dependencies and thus get in the habit of adding commonly used software,
+whether it is needed or not.
+
+\item {\bf Rapid Changes in Dependencies.}  Over the course of three months
+between collecting the initial email, analyzing the program, and writing this
+paper, the computing environment was under continuous change.  The CMSSW software
+distribution released a new version, the target execution environment was upgraded
+to a new operating system, and the experiment deprecated the use of CVS for obtaining
+the software.  While the users of this software seem be accustomed to constant change,
+any preservation technique will have to be very cautious about relying upon an
+external service, even one that may appear to be highly stable.
+
+\end{itemize}
+
+\if 0
 
@@
 \end{figure*}
+\fi
 

### 2014-03-14 paper.tex
Moved paper back into place.

@@
 
-{\bf Many Implicit Local Dependencies.} A much harder problem is that the
+\item {\bf Many Implicit Local Dependencies.} A much harder problem is that the
 application assumed the presence of many different components in the local
@@
 
-{\bf High Selectivity.}  Although the total size of the resources accessed by this
+\begin{figure*}[t]
+\centering
+\includegraphics[width=1.6\columnwidth]{version-evolution.eps}
+\caption{Version Evolution}
+\label{fig:version-evolution}
+\end{figure*}
+
+\item {\bf High Selectivity.}  Although the total size of the resources accessed by this
 program is very large, the size of the data and software actually used are much smaller.
@@
 
-\begin{figure*}
-\centering
-\includegraphics[width=1.6\columnwidth]{version-evolution.eps}
-\caption{Version Evolution}
-\label{fig:version-evolution}
-\end{figure*}
 \fi

### 2014-03-14 paper.tex
modify figure 1

@@
         CMSSW code     & CVS & 88.1GB & 448.3MB & 6.3MB\\ \hline
-        Tau source       & Git & 73.7MB & 73.7MB & 73.7MB \\ \hline
-        PyYAML binaries    & HTTP & 52MB & 51MB & 51MB \\ \hline
-        .h file       & HTTP& 41KB & 41KB & 41KB \\ \hline
+        Tau source       & Git & 73.7MB & 73.7MB & 6.7MB \\ \hline
+        PyYAML binaries    & HTTP & 52MB & 52MB & 0KB \\ \hline
+        .h file       & HTTP& 41KB & 41KB & 0KB \\ \hline
         Misc commands & PanFS & 155TB & N/A  & 1.6MB \\ \hline
-        Linux commands & localFS & 110GB &  N/A & 68.3MB \\ \hline     
+        Linux commands & localFS & 110GB &  N/A & 68.4MB \\ \hline     
         Configuration & CVMFS & 7.4GB & N/A & 103MB \\ \hline
-        HOME dir& AFS &10.2GB & N/A & 34MB\\ \hline
-        Total      &    & 180.1TB            & N/A & 21GB \\ \hline
+        HOME dir& AFS &10.2GB & N/A & 32MB\\ \hline
+        Total      &    & 166.8TB            & N/A & 21GB \\ \hline
     \end{tabular}

### 2014-03-14 paper.tex
adjust the sequence of table 1

@@
         \hline
-        Ntuples data    & HDFS& 11.6TB & 43.3GB & 20GB \\ \hline
         CMSSW code     & CVS & 88.1GB & 448.3MB & 6.3MB\\ \hline
@@
         PyYAML binaries    & HTTP & 52MB & 52MB & 0KB \\ \hline
-        .h file       & HTTP& 41KB & 41KB & 0KB \\ \hline
+        .h file       & HTTP& 41KB & 41KB & 0KB \\ \hline \hline
+        Ntuples data    & HDFS& 11.6TB & 43.3GB & 20GB \\ \hline
+        Configuration & CVMFS & 7.4GB & N/A & 103MB \\ \hline
+        Linux commands & localFS & 110GB &  N/A & 68.4MB \\ \hline     
+        HOME dir& AFS &10.2GB & N/A & 32MB\\ \hline
         Misc commands & PanFS & 155TB & N/A  & 1.6MB \\ \hline
-        Linux commands & localFS & 110GB &  N/A & 68.4MB \\ \hline     
-        Configuration & CVMFS & 7.4GB & N/A & 103MB \\ \hline
-        HOME dir& AFS &10.2GB & N/A & 32MB\\ \hline
         Total      &    & 166.8TB            & N/A & 21GB \\ \hline
@@
 
-\begin{table*}
-    \centering
-    \begin{tabular}{|l|r|r|r|}
-        \hline
-        \bf Solution ID & \bf Data Resources &\bf Software Resources & \bf Operation Manual \\ \hline
-        Solution 1& Grid & CMSSW Git HTTP & email \\ \hline
-        Solution 2 and 3& local (HDFS) & CMSSW Git HTTP & shell script \\ \hline
-        Solution 4& package & package & user manual of package \\ \hline
-    \end{tabular}
-    \caption{Relationship of Different Solutions}
-    \label{table:relationship}
-\end{table*}
-
 %The fourth solution should be based on the third solution.
@@
 \section{Evaluation}
-The section first illustrates the relationship of different preservation and reproduction solutions, then the platform used to evaluate different solutions is introduced.
+The section first introduces the platform used to evaluate different solutions is introduced.
 The execution time and data size of Solution 2 and 4 are tested and compared.
@@
 Solution 3 shares the same time consumption and data size with Solution 3.
-
-\subsection{Relationship of Different Solutions}
-The relationship of these four solutions to repeat one program is shown in Table~\ref{table:relationship}.
-Each new solution tries to make it easier to repeat one program through making the data and software preparation easier.
 
@@
 This solution does not support mining of implicit dependencies.
-The size of data and software from each category is shown in table~\ref{table:datasize-2nd}, which only lists the size of each clear dependency.
-
-\begin{table}
-    \centering
-    \begin{tabular}{|l|r|}
-    \hline
-    \bf Data Category & \bf Data Size \\ \hline
-    Software from CMSSW & 448.3MB \\ \hline
-    Software from Git & 73.7MB \\ \hline
-    Software from Wget & 52MB \\ \hline
-    HDFS & 43.3GB \\ \hline
-    Total & 43.86GB \\ \hline
-    \end{tabular}
-    \caption{Data Size of Solution 2}
-    \label{table:datasize-2nd}
-\end{table}
 
@@
 
-\begin{table}
-    \centering
-    \begin{tabular}{|l|l|r|}
-    \hline
-    \bf Data &\bf Location & \bf Data \\ 
-    \bf Category & & \bf Size\\ \hline
-    HDFS & hadoop &20GB \\ \hline
-    PanFS & pscratch & 1.6MB \\ \hline
-    CVMFS & cvmfs &103MB \\ \hline 
-    NFS & opt &53KB \\ \hline
-    AFS & afs &34MB \\ \hline
-    Local FS& bin etc lib lib64 sbin tmp usr&68.3MB \\ \hline
-    Total & &21GB \\ \hline
-    \end{tabular}
-    \caption{Data Size of Solution 4}
-    \label{table:datasize-3rd}
-\end{table}
-
 \subsection{ Data size Comparison of Solution 2 and 4}
@@
 Solution 4 reduces the total size of all data sources from 156TB to 21GB.
-
-\begin{table}
-    \centering
-    \begin{tabular}{|l|r|r|}
-    \hline
-    \bf Data Category & \bf Solution2: Size & \bf Solution4: Size \\ \hline
-    HDFS & 43.3GB & 20GB \\ \hline
-    PanFS & 155TB & 1.6MB \\ \hline
-    CVMFS & 7.4GB &103MB \\ \hline
-    NFS & 862GB &53KB \\ \hline
-    AFS & 10.2GB &34MB \\ \hline
-    Local FS& 110GB&68.3MB \\ \hline
-    Total & 156TB &21GB \\ \hline
-    \end{tabular}
-    \caption{Data Size Comparison beweeen Solution 2 and 4}
-    \label{table:datasize-2nd3rd}
-\end{table}
 
@@
     Environment Build & 5min 49s  & 3s \\ \hline
-    Obtain file namelist & N/A & 28min 23s \\ \hline
-    Generate package & N/A & 85min 51s \\ \hline
     Actual Analysis & 20min 31s & 13min 4s \\ \hline

### 2014-03-14 paper.tex
modify the evaluation part

@@
 
-The configuration of earth machine. The configuration of our virtual machine. The configuration of amazon ec2.
-each vm: data download time; untar time; script execution time;
-
-\subsection{Evaluation of Solution 2}
+\subsection{Execution Time Comparison of Solution 2 and 4 on the Original Machine}
+
 The breakdown of execution time of Solution 2 is shown in Table~\ref{table:time-2nd}.
@@
 
-This solution does not support mining of implicit dependencies.
-
-\subsection{Evaluation of Solution 4}
-
 The breakdown of execution time of the
@@
 \end{table}
-
-The data size of Solution 4 is shown in Table~\ref{table:datasize-3rd}. The
-data categories are more complex than our imagination. Except the data stored in
-Hadoop and the necessary set of software, files from local filesystem and several remote filesystems, such as PanFS, CVMFS, NFS, and AFS, are also necessary for the reproduction of the program.
-
-\subsection{ Data size Comparison of Solution 2 and 4}
-
-The packaging utility checks the system call of each file within the namelist,
-and maintains the minimum dataset, which makes the size of the final package 
-as small as possible. The total size of Hadoop under Solution 2 is astonishing,
-while the size of Hadoop under the package is decreased to 20GB. 
-The total size of PanFS is 155TB, however, the size of the really used data of PanFS is only 1.6MB.
-Table~\ref{table:datasize-2nd3rd} compares the original size and the really used size of each data source.
-Solution 4 reduces the total size of all data sources from 156TB to 21GB.
-
-\subsection{Execution Time Comparison of Solution 2 and 4}
 
@@
 \end{table}
+
+\subsection{Data Size Comparison of Solution 2 and 4 on the Original Machine}
+
+Table~\ref{table:size-original-real} illustrates the total size, named size in the example and actually used size of each remote source (the first 4 items) and local source (the remaining 5 items).
+The third column is corresponding to the data size of Solution 4. 
+Solution 2 does not support mining of implicit dependencies.
+As for remote sources, we can figure out the named size through the analysis script.
+Howerver, it is hard to figure out the named size of each local source.
+
+The packaging utility checks the system call of each file within the namelist,
+and maintains the minimum dataset, which makes the size of the final package 
+as small as possible. The total size of Hadoop under Solution 2 is astonishing,
+while the size of Hadoop under the package is decreased to 20GB. 
+The total size of PanFS is 155TB, however, the size of the really used data of PanFS is only 1.6MB.
+Table~\ref{table:datasize-2nd3rd} compares the original size and the really used size of each data source.
+Solution 4 reduces the total size of all data sources from 156TB to 21GB.
 

### 2014-03-14 paper.tex
Edited the evolution section.

@@
 
-\title{A Case Study in Preserving a High Energy Physics Application}
+\title{A Case Study in Preserving a\\High Energy Physics Application}
 \author{
@@
 
-\section{Preservation Strategies}
-
-Figure~\ref{fig:version-evolution} illustrates the evolution history of
-different preservation strategies. First, an email depicting how to repeat the
-experiment is used. Then, all the necessary steps to reproduce the experiment
-mentioned in the mail are collected into one shell script. In order to decouple
-data sources and data references, one formulated script is introduced
-to express all the dependencies at the beginning of the script in the form of
-environment variables. Finally, this decoupling idea is further extended into
-one map file which keeps the relationship between the data reference in the
-script and the actual storage location. One independent package containing all
-the data and software dependencies is generated to make the reproduction
-process more easier.
-
-\subsection{Solution 1: Email}
-
-In order to repeat Matthais's example, we consulted the original
-author by email about the necessary work for the experiment. In response,
-the original author introduced the general workflow of his tau roast program through one long
-email including notes, linux shell commands, web linksi, as illustrated by the Version 1 of
-Table~\ref{table:scripts}.
-
-However, this solution to repeat one experiment has three potential drawbacks.
-Firstly, the experience of repeating one tau roast program through emails is
-chaotic. You need to constantly jump around multiple web links. There are overlap
-between the content of the email and the content of web links, which needs the
-new user to merge them. Multiple communication through emails is necessary to
-ensure the successful reproduction of the whole analysis. For example, the original
-email refers to one environment variable called CMSSW\_base without clear
-declaration, the new user needs to send one email to the original writer to
-obtain its accurate value. Secondly, the necessary procedures to repeat the
-experiment, including software acquisition from different sources, is complex
-for the new user. In the example, the sources of software includes
-CMSSW, Git, HTTP. The access of CMSSW requires the new user to be an authorized
-user of CMSSW. What's more, some parts of the workflow are unrepeatable. The
-third step of this experiment requires the new user to own the access authority
-of the Grid and involves the analysis of AOD data with the size of about 400TB.
-
-Implication: Directly repeating the experiment using the workflow description and results provided by the original author is complex and difficult.
-Some extra work must be done to make the reproduction process easier.
-
-\subsection{Solution 2: Script} One possible solution for the access authority
-problem of Grid data is to grant the new user the authority to access gird data
-directly. Another possible solution is let the new user directly operate on the
-machine the original author used. As for the complexity of jumping between
-multiple web links, people may suggest that the original author
-should generate one script including all the contents from different web links.
-
-To test out these possible solutions, we integrate the content of all the notes, commands and web links involved in the emails into one neat, complete shell script, which begins with the definition of environment variables, software acquisition from CMSSW, Git and other web resources, and software installation, ends with the execution of the actual analysis program.
-Version 2 of Table~\ref{table:scripts} illstrates the merged script.
-As for the data acquisition from the Grid, we directly use the local copy in HDFS to avoid requiring the new user to obtain a Grid certification.
-
-%*****hmeng-doult: the size of hadoop need to reconsidered. how to correctly illustrate the data size of this example?
-
-Because the script includes all the necessary procedures for the reproduction
-of one analysis program, the readability and friendliness of this solution is
-higher than that of the email format.
-
-\subsection{Solution 3: Formulated Script}
-%%
-
-The script can reduce the complexity of repeating one experiment through the integration of all the necessary procedures.
-However, the data and software dependencies are still randomly distributed across the whole script, which requires one complete scan of the script to obtain the  dependency list.
-
-To decouple data sources and data references and make the data dependencies clear, Version 2 of Table~\ref{table:scripts} is formulated into one new version, as shown in
-the Version 3 of Table~\ref{table:scripts}. Each new environment variable at the beginning part of
-the script is corresponding to one dependency. All the following access to data
-or software dependency will refer to its corresponding environment variable.
-All the environment variables of dependencies form one map, which maintains the
-target address of each dependency.
-
-This script style may function as one new guideline to the original author of
-one experiment, which expresses the dependencies more clearly and expedites the
-preparation process to repeat one experiment. The introduction of the map file
-also reduces the workload of changing one dependency. For example, if we want
-to utilize one new git package to analyze the same dataset, only the modification of
-environment variable corresponding to the original git package is necessary.
-Without the map mechanism, the whole script needs to be scanned to figure out and
-replace all the references of the original git package.
-
-So far, the data access authority is ignored and
-the reproduction of the experiment is on the machine the original author used. 
-As for Grid data, using the data
-copy stored in the machine where the original author executed the experiment requires the
-new user to have the authority to access the machine, which complicates the
-management of the original machine, even is impossible if the original machine
-executes rigid user access control. Granting everyone who wants to repeat the
-analysis the access authority for Grid is unacceptable to system administrator.
-
-Implication: All the data and software involved in the experiment should be
-provided to the new user in the format of one self-contained package so that
-the new user can avoid 
-access authority problems.
-In addition, the requirements of the underlying
-OS and hardware should also be figured out and provided to the new user.
+\section{Evolving the Artifact}
+
+It is clear that the artifact, as provided, is not in a suitable form
+for preservation.  While it might be technically possible to automatically
+capture the entire virtual machine and all of the connected filesystems,
+doing so would be wasteful and prohibitively expensive.  Further, if multiple
+similar applications are preserved, we would miss the opportunity to identify
+common dependencies and store them once for multiple artifacts.
+
+Figure~\ref{fig:version-evolution} shows how we have evolved this artifact
+through several stages which make it more suitable for preservation.
+In each step of evolution, we make the dependencies of the artifact
+more explicit and available for analysis and automated processing.
+As noted in the previous section, the original author provided us with
+prose instructions by email which we translated into an
+executable script.  The executable script has embedded in it
+a number of external identifiers such as URLs pointing to repositories
+and paths to networked filesystems.  As a general programming practice,
+embedding such constants into the middle of a program is unwise, and so
+we extract all of those identifiers and place them at the beginning
+of the script in the form of variable substitutions.  This makes
+it readily apparent to the reader what the dependencies are.
+
+Form 4 goes a step further and takes all of the dependencies \emph{out}
+of the script itself and places them in a \emph{dependency map}.
+The dependency map lists all of the external dependencies of the application, indicating
+the type, how they are accessed, and where they are currently located.
+The resulting script then simply refers to abstract file locations such
+as \verb!$CMSSW!, while the map file indicates where they are located.
+If properly constructed, the script should not refer to any external
+resource unless it is indicated in the dependency map.
+
+By extracting the dependencies into the external dependency map,
+we introduce great freedom for the curator to move, transform, and otherwise
+manipulate the dependencies of the artifact without damaging the artifact itself.
+For example, it is straightforward for an automated tool to examine
+all of the dependencies in the map, download those that are missing,
+and then modifiy the map to point to the local copies of the dependencies.
+
+\section{Fine Grained Dependency Management}
 

### 2014-03-14 paper.tex
modify the evaluation section

--- 2014-03-14 paper.tex
@@
 \section{Evaluation}
-The section first introduces the platform used to evaluate different solutions is introduced.
-The execution time and data size of Solution 2 and 4 are tested and compared.
-It is hard to accurately calculate the time consumption of Solution 1.
-Solution 3 shares the same time consumption and data size with Solution 3.
-
-\subsection{Evaluation Platform}
-
-The first three solutions are all directly verified on the machine the original
-author used to execute the experiment, which is convenient but involves access
-authority problem. Solution 4 is verified on the original machine and on one virtual machine.
-To compare the execution time and data size of Solution 4
-with Solution 2, the package generated on the original machine is utilized to
-rerun the experiment on the original machine. This choice avoids the impact of
-different CPUs of the original machine and the new machine to repeat the
-experiment.
-
-To completely verify the correctness of Solution 4, one virtual
-machine ~\cite{goldberg1974survey} sharing the same kernel version with the original machine is deployed.
-Then the necessary software environment is configured on the virtual machine,
-and the package is copied onto it, and the
-experiment is repeated on the virtual machine.
-
-One virtual machine from amazon EC2 ~\cite{amazon2010amazon} is used to verify the reproducibility of the experiment.
+The section evaluates the connectness of the packaging utility of Solution 4.
+To do it, the experiment is repeated using Solution 2 and 4 on the original machine.
+Then, two different virtual machines (VM) - one local VM and one amazon EC2 VM, are employed to further verify the reproductivity of Solution 4.
+
+\subsection{Evaluation on the Original Machine}
+
+This section evaluates the correctness of Solution 4 on the original machine and compares the time consumption and data size of Solution 2 and 4 on the original machine.
+
+To do this, we first repeat the example from scratch using Solution 2 on the the original machine and count the time consumption and data size. 
+Then based on the successful execution of Solution 2, Solution 4 is evaluated - one package containing necessary dependencies is generated, and then the time consumption and data size is analyzed.
+
+Table~\ref{table:time-2nd3rd} shows the execution time comparison between
+Solution 2 and 4. The time consumption of the reproduction of one program from
+different scholars kept the same under Solution 2, including software and data
+preparation. 
+However, under Solution 4, the Software Acquisition stage is not necessray, and all the environment building only takes 3s.
+Data is obtained through accessing HDFS in Solution 2, but is copied into the package in Solution 4.
+This localization of experimental data speeds up the data analysis process, resulting the actual analysis time reducing from 20 minutes to 13 minutes.
+
+\begin{table}
+    \centering
+    \begin{tabular}{|l|r|r|}
+    \hline
+    \bf Task & \bf Solution 2& \bf Solution 4\\ 
+    \bf Category & \bf Time & \bf Time \\ \hline
+    Software Acquisition & 8min 11s & N/A \\ \hline
+    Environment Build & 5min 49s  & 3s \\ \hline
+    Actual Analysis & 20min 31s & 13min 4s \\ \hline
+    \end{tabular}
+    \caption{Execution Time Comparison between Solution 2 and 4}
+    \label{table:time-2nd3rd}
+\end{table}
+
+Table~\ref{table:time-3rd} illustrates the time used to
+obtain filename list and generate the package. 
+The time used for these two steps is greatly longer than the execution time
+within the new package. However, the time consumption of filename list
+acquisition and package generation is one-time. That is, once the package is
+generated, many users can directly obtain the package and repeat the experiment
+separately.
+
+\begin{table}
+    \centering
+    \begin{tabular}{|l|r|}
+    \hline
+    \bf Sub-Task &\bf Time \\ \hline
+    Obtain file namelist & 28min 23s \\ \hline
+    Generate P1 & 85min 51s \\ \hline
+    Re-run the program within P1 & 13min 4s \\ \hline
+    \end{tabular}
+    \caption{File of Solution 4}
+    \label{table:time-3rd}
+\end{table}
+
+Table~\ref{table:size-original-real} illustrates the total size, named size in the example and actually used size of each remote source (the first 4 items) and local source (the remaining 5 items).
+The third column is corresponding to the data size of Solution 4. 
+Solution 2 does not support mining of implicit dependencies.
+As for remote sources, we can figure out the named size through the analysis script.
+Howerver, it is hard to figure out the named size of each local source.
+
+In conclusion, Solution 4 can repeat the whole experiment successfully and reduce the total size involved in the experiment to one reasonable size.
+
+\subsection{Evaluation on Different Machines}
+
+To further verify the reproductivity of Solution 4 on other machines, two different virtual machines are employed -
+one virtual
+machine ~\cite{goldberg1974survey} sharing the same kernel version with the original machine,
+and one virtual machine from amazon EC2 ~\cite{amazon2010amazon}.
+
 Table~\ref{table:config-vm} illustrates the configuration of the original machine and each virtual machine. 
@@
 
-\subsection{Execution Time Comparison of Solution 2 and 4 on the Original Machine}
-
-The breakdown of execution time of Solution 2 is shown in Table~\ref{table:time-2nd}.
-About 40\%  of the total execution time is consumed to prepare relevant software environment.
-The cvs command is called to check out 23 packages from CMSSW and three git repositories are cloned.
-
-\begin{table}
-    \centering
-    \begin{tabular}{|l|r|r|}
-    \hline
-    \bf Sub-Task & \bf Time & \bf Percentage \\ \hline
-    Obtain software from CMSSW & 7min 24s & 21.44\% \\ \hline
-    Obtain software from Git & 9s & 0.43\% \\ \hline
-    Obtain software from Wget & 38s & 1.83\% \\ \hline
-    Environment build - SCRAM & 5min 48s & 16.80\% \\ \hline
-    Environment build - Python & 1s & 0.05\% \\ \hline
-    Data analysis & 20min 31s & 59.44\% \\ \hline
-    Total & 34min 31s & 100.00\% \\ \hline
-    \end{tabular}
-    \caption{Breakdown of Execution Time of Solution 2}
-    \label{table:time-2nd}
-\end{table}
-
-The breakdown of execution time of the
-Solution 4 is illustrated in Table~\ref{table:time-3rd}. The time used to
-obtain filename list and generate P1 is greatly longer than the execution time
-within the new package. However, the time consumption of filename list
-acquisition and package generation is one-time. That is, once the package is
-generated, many users can directly obtain the package and repeat the experiment
-separately.
-
-\begin{table}
-    \centering
-    \begin{tabular}{|l|r|}
-    \hline
-    \bf Sub-Task &\bf Time \\ \hline
-    Obtain file namelist & 28min 23s \\ \hline
-    Generate P1 & 85min 51s \\ \hline
-    Re-run the program within P1 & 13min 4s \\ \hline
-    \end{tabular}
-    \caption{Time Breakdown of Solution 4}
-    \label{table:time-3rd}
-\end{table}
-
-Table~\ref{table:time-2nd3rd} shows the execution time comparison between
-Solution 2 and 4. The time consumption of the reproduction of one program from
-different scholars kept the same under Solution 2, including software and data
-preparation. However, under Solution 4, the data and software preparation is
-one-time. The following reproduction of the same program only needs to obtain
-one copy of the package and execute the actual experimental analysis directly.
-Data is obtained through accessing HDFS in Solution 2, but is copied into the package in Solution 4.
-This localization of experimental data speeds up the data analysis process, resulting the actual analysis time reducing from 20 minutes to 13 minutes.
-
-\begin{table}
-    \centering
-    \begin{tabular}{|l|r|r|}
-    \hline
-    \bf Task & \bf Solution 2& \bf Solution 4\\ 
-    \bf Category & \bf Time & \bf Time \\ \hline
-    Software Acquisition & 8min 11s & N/A \\ \hline
-    Environment Build & 5min 49s  & 3s \\ \hline
-    Actual Analysis & 20min 31s & 13min 4s \\ \hline
-    \end{tabular}
-    \caption{Execution Time Comparison between Solution 2 and 4}
-    \label{table:time-2nd3rd}
-\end{table}
-
-\subsection{Data Size Comparison of Solution 2 and 4 on the Original Machine}
-
-Table~\ref{table:size-original-real} illustrates the total size, named size in the example and actually used size of each remote source (the first 4 items) and local source (the remaining 5 items).
-The third column is corresponding to the data size of Solution 4. 
-Solution 2 does not support mining of implicit dependencies.
-As for remote sources, we can figure out the named size through the analysis script.
-Howerver, it is hard to figure out the named size of each local source.
-
-The packaging utility checks the system call of each file within the namelist,
-and maintains the minimum dataset, which makes the size of the final package 
-as small as possible. The total size of Hadoop under Solution 2 is astonishing,
-while the size of Hadoop under the package is decreased to 20GB. 
-The total size of PanFS is 155TB, however, the size of the really used data of PanFS is only 1.6MB.
-Table~\ref{table:datasize-2nd3rd} compares the original size and the really used size of each data source.
-Solution 4 reduces the total size of all data sources from 156TB to 21GB.
-
-\subsection{Excution Time on Different Machines}
 Table~\ref{table:time-vm} shows the execution time of the experiment on different machines - the original machine, local VM and EC2 VM. 
@@
     earth & 13min 4s \\ \hline
+    local VM & 21min 38s \\ \hline
     EC2 VM & 13min 30s\\ \hline
-    local VM & 21min 38s \\ \hline
     \end{tabular}

### 2014-03-14 paper.tex
modify the evaluation part

@@
 \section{Evaluation}
-The section evaluates the connectness of the packaging utility of Solution 4.
-To do it, the experiment is repeated using Solution 2 and 4 on the original machine.
-Then, two different virtual machines (VM) - one local VM and one amazon EC2 VM, are employed to further verify the reproductivity of Solution 4.
-
-\subsection{Evaluation on the Original Machine}
-
-This section evaluates the correctness of Solution 4 on the original machine and compares the time consumption and data size of Solution 2 and 4 on the original machine.
-
-To do this, we first repeat the example from scratch using Solution 2 on the the original machine and count the time consumption and data size. 
+The section evaluated the connectness and overhead of the packaging utility of Solution 4.
+To do it, the experiment was repeated using Solution 2 and 4 on the original machine.
+Then, two different virtual machines (VM) - one VM from Notre Dame Cloud Platform based on KVM and one VM from amazon EC2 Platform based on Xen, were employed to further verify the correctness of Solution 4.
+
+We first repeated the example from scratch using Solution 2 on the the original machine and counted the time consumption and data size. 
 Then based on the successful execution of Solution 2, Solution 4 is evaluated - one package containing necessary dependencies is generated, and then the time consumption and data size is analyzed.
 
+As for time consumption, we counted the time used to obtain remote software dependencies, build environment, and analyze the dataset respectively.
+Solution 4 also counted the time used to obtain the file namelist and generate the package.
+
+As for data size, we can easily figure out the size of each data and code source easily inside the package under Solution 4.
+Solution 2 does not support mining of implicit dependencies.
+As for remote sources, we can figure out the named size through the analysis script.
+Howerver, it is hard to figure out the named size of each local source.
+Instead, we only knew that total size of each file system is very large.
+
 Table~\ref{table:time-2nd3rd} shows the execution time comparison between
-Solution 2 and 4. The time consumption of the reproduction of one program from
-different scholars kept the same under Solution 2, including software and data
-preparation. 
-However, under Solution 4, the Software Acquisition stage is not necessray, and all the environment building only takes 3s.
-Data is obtained through accessing HDFS in Solution 2, but is copied into the package in Solution 4.
+Solution 2 and 4.
+Solution 4 is faster than Solution 2, because all the software copied into the pacakge has been compiled and the Software Acquisition stage is not necessray.
+and all the environment building only takes 3s.
+We were suprised that Solution 4 even reduces the actual analysis time. 
+The reason for this is that data is obtained through accessing HDFS in Solution 2, but is copied into the package in Solution 4.
 This localization of experimental data speeds up the data analysis process, resulting the actual analysis time reducing from 20 minutes to 13 minutes.
@@
     Environment Build & 5min 49s  & 3s \\ \hline
-    Actual Analysis & 20min 31s & 13min 4s \\ \hline
+    Actual Analysis & 20min 31s & 13min 04s \\ \hline
     \end{tabular}
@@
 Table~\ref{table:time-3rd} illustrates the time used to
-obtain filename list and generate the package. 
+obtain the filename list and generate the package. 
 The time used for these two steps is greatly longer than the execution time
-within the new package. However, the time consumption of filename list
-acquisition and package generation is one-time. That is, once the package is
+within the new package. 
+Because each filename of the list, together with its system call type, needs to be checked, and the structure of each directory item must be maintained.
+However, 
+this is only done once.
+That is, once the package is
 generated, many users can directly obtain the package and repeat the experiment
@@
     \bf Sub-Task &\bf Time \\ \hline
-    Obtain file namelist & 28min 23s \\ \hline
-    Generate P1 & 85min 51s \\ \hline
-    Re-run the program within P1 & 13min 4s \\ \hline
+    Obtain filename list & 28min 23s \\ \hline
+    Generate package & 85min 51s \\ \hline
     \end{tabular}
-    \caption{File of Solution 4}
+    \caption{Time Used to Obtain Filename List and Generate Package}
     \label{table:time-3rd}
@@
 Table~\ref{table:size-original-real} illustrates the total size, named size in the example and actually used size of each remote source (the first 4 items) and local source (the remaining 5 items).
-The third column is corresponding to the data size of Solution 4. 
+The third column is corresponding to the data size of Solution 4 and can be easily figured out, because all the necessary data has been copies into the package.
 Solution 2 does not support mining of implicit dependencies.
@@
 Howerver, it is hard to figure out the named size of each local source.
-
-In conclusion, Solution 4 can repeat the whole experiment successfully and reduce the total size involved in the experiment to one reasonable size.
-
-\subsection{Evaluation on Different Machines}
-
-To further verify the reproductivity of Solution 4 on other machines, two different virtual machines are employed -
+Instead, we only knew that total size of each file system is very large.
+
+To further verify the correctness of Solution 4 on other machines, two different virtual machines are employed -
 one virtual
-machine ~\cite{goldberg1974survey} sharing the same kernel version with the original machine,
-and one virtual machine from amazon EC2 ~\cite{amazon2010amazon}.
-
-Table~\ref{table:config-vm} illustrates the configuration of the original machine and each virtual machine. 
+machine ~\cite{goldberg1974survey} from Notre Dame Clou Platform based on KVM sharing the same kernel version with the original machine,
+and one virtual machine from amazon EC2 ~\cite{amazon2010amazon} based on Xen.
+
+Table~\ref{table:config-vm} illustrates the configuration of 
+each machine and the execution time of the experiment on each machine.
 All the machines adopt x86\_64 hardware platform and linux OS.
-Both the local VM and EC2 VM repeat the experiment with the help of the package generated on the original machine successfully.
+Both of the two VMs repeated the experiment with the help of the package generated on the original machine successfully.
+The execution time on one machine greatly depends on its hardware configuration.
 
@@
     \hline
-    \bf Machine & \bf Kernel Version & \bf Distro & \bf CPU & \bf Mem\\ 
-    \bf Type &  & \bf Version & \bf Cores & (\bf GB)\\ \hline
-    earth  & 2.6.18-371.4.1.el5 & RedHat 5.10 & 64 & 125 \\ \hline 
-    local VM& 2.6.18-371.4.1.el5 & CentOS 5.10 & 4 & 2 \\ \hline
-    EC2 VM& 2.6.18-348.el5xen & RedHat 5.9 & 16 & 60.5 \\ \hline
+    \bf Machine & \bf Distro & \bf CPU & \bf Mem & \bf Execution\\ 
+    \bf Type   &\bf Version&\bf Cores & (\bf GB) & \bf Time\\ \hline
+    Native &  RedHat  & 64 & 125 & 13min 04s\\  
+    Machine& 5.10 &&&\\ \hline
+    KVM & CentOS & 4 & 2 & 21min 38s\\
+    (Notre Dame)&5.10 &&&\\ \hline
+    Xen & RedHat & 16 & 60.5 & 13min 30s\\ 
+    (EC2) &5.9 &&&\\ \hline
     \end{tabular}
-    \caption{Configuration of Different Machines}
+    \caption{Evaluation of Different Machines}
     \label{table:config-vm}
-\end{table}
-
-Table~\ref{table:time-vm} shows the execution time of the experiment on different machines - the original machine, local VM and EC2 VM. 
-Each machine utilizes the package generated on the original machine (i.e. earth) to repeat the experiment.
-The execution time on one machine greatly depends on its hardware configuration, which is shown in Table~\ref{table:config-vm}.
-
-\begin{table}
-    \centering
-    \begin{tabular}{|l|r|}
-    \hline
-    \bf Machine Type & \bf Execution Time \\ \hline
-    earth & 13min 4s \\ \hline
-    local VM & 21min 38s \\ \hline
-    EC2 VM & 13min 30s\\ \hline
-    \end{tabular}
-    \caption{Execution Time on Different Machines}
-    \label{table:time-vm}
 \end{table}
@@
 need to be investigated.
-
-\subsection{Here is the Useful Package}
-
-At the beginnig of our case study, we generated one package for the
-example based on Solution 4. Several months later, the original machine met
-some problems and the access model of CMSSW was also modified. In this case, if
-you want to repeat the example on the original machine, different 
-configurations, including CMSSW\_ARCH, environment variables and CVS access
-authority need to be modified. However, with the generated package and its map file, we can repeat the experiment directly on the same machine without any modification.
-%here is the new content-hmeng
 
@@
 
-\section{Conclusion}
-
-In this paper, we tries to illustrate the challenges involved in data and software preservation and reproduction through one case study in preserving one High Energy Physics application.
-Four different solutions to repeat the original application, together with the pros and cons of each one, are proposed and analyzed.
-Each new solution aims to improve the reproductivity of the application and reduce the complexity of reproduction.
-Finally, we propose one fine-grained packaging toolkit to help the original author to generate one independent package containing all the necessary dependencies except for common dependencies, and repeat the experiment from scratch on two Amazon EC2 virtual machines successfully.
-
-In the future, more case studies will be investigated to verify the correctness of our packaging toolkit. The challenges we propose in this paper will also be investigated.
+\section{Postscript}
+By the way, at the beginnig of our case study, we generated one package for the
+example based on Solution 4. Several months later, the original machine met
+some problems and the access model of CMSSW was also modified. In this case, if
+you want to repeat the example on the original machine, different 
+configurations, including CMSSW\_ARCH, environment variables and CVS access
+authority need to be modified. However, with the generated package and its map file, we can repeat the experiment directly on the same machine without any modification.
 

### 2014-03-14 paper.tex
Updated section 8.

@@
 and then modifiy the map to point to the local copies of the dependencies.
+(Or, in the case of a dependency upon a reliable external archive,
+the map file could continue to point to the original source.)
 
@@
 %*****hmeng-doubt: this point is not the motivation. but one achievement comes together. out of imagination.
-\section{Discussion of Data and Software Preservation}
-
-This section concludes the important lessons of data and software preservation and experiment reproduction learnt from this case study. 
-The necessity of preservation integration of multiple programs, preservation granularity, how to preserve large data, how to mine data and software dependencies,
-the presrvation degree of the original filesystems, the importance of investigating user access model of data and software, will be discussed.
-
-\subsection{Preservation Integration of Multiple Programs}
-
-Different experimenters may execute different analysis
-programs on the same dataset using the same or overlapping sets of software.
-Generating one new package for each analysis program from scratch is
-time-consuming and space-consuming, which makes one data and software
-preservation mechanism, that can integrate the preservation requirements of
-different analysis programs, become necessary.
 
@@
 
-To integrate the data and software from multiple analysis programs into one
-archive, the concrete information of data and software, such as size, version,
-source and the number of files, need to be recorded. 
-The packaging
-process needs to be re-organized. Packaging utility needs to maintain one list
-of current software and data subset already stored in the archive. When one
-user utilizes the packaging utility to preserve one program, the
-packaging utility scans the script, gets the data and software dependency
-part, judges whether each dependency has been inside the package, and only adds
-the new data and software into the archive, and updates the package information
-and relavant retrieval information.
-
-The architecture of preservation integration of multiple programs is shown in
-Figure~\ref{fig:Preservation integration}. Script 1 and Script 2, sharing one
-dependency B, belongs two different programs. Without preservation
-integration, B will be preserved twice in the archive. To improve the utilization efficiency of storage resources,
-preservation integration of multiple programs is necessary. In the archive,
-only one copy of B is stored, which is referred by both scripts.
-
-\subsection{Preservation Granularity}
-
-Another important factor of data and software preservation is the choice of
-preservation granularity. In our implementation of Solution 4, the preservation granularity is one
-file, because Parrot virtual filesystem traps each system call and redirects
-the access path of each file. As a result, during the packaging process, each
-time only one file can be copied into the target package, which is
-low-efficient. However, there are other options of preservation granularity.
-The software is generally preserved in the unit of package inside the remote
-repository, the packaging process of one experiment can adopt one package as
-the unit. In addition, if the size of one whole software repository is small
-and the access frequency of each package inside it is high, the granularity can
-be set to the whole repository.
-
-\subsection{Preservation of Large Data}
-
-The preservation policy must concern about the size of data. If data size is
-small, copying it into one pacakge and transferring it between different
-machines is not a bad idea. Howerver, when the size becomes large, copying it
-into one package will make the size of the package uncontrollable. In
-Figure~\ref{fig:Preservation integration}, the size of C is very large and
-easily to be obtained through Internet by different users. Directly referring C
-as networked resources is more efficient than preserving it into one package.
-
-\subsection{Mining of Dependencies}
-
-The mining degree of data and software dependencies greatly determines the
-repeatability of one experiment. Clear data dependencies is easy to figure
-out, but how to figure out implicit data dependencies is complex. The situation
-of software dependencies is more complex. The software dependencies include OS,
-hardware platform, direct software dependencies and indirect software
-dependencies.
-The first
-three categories are easy to deal with. The acquisition of indirect software
-dependencies needs more efforts.
-
-One solution is to treat the computing environment, software environment
-and scientific data as one integral entirety and preserve the entirety
-completely. The reproduction of one experiment using this solution is easier.
-However, the original machine is not only for one special experiment and may
-concern a large amount of software and data unrelevant to the experiment. The
-time and space overhead of this solution must be considered.
-
-Another solution is to utlize package management
-tools, like rpm, pacman, apt, to recursively trace each direct software
-dependency and generate one clear dependency graph. With the dependency graph,
-the new user can configure the software environment and repeat the experiment.
-
-The third solution is to trace the system calls of the experiment execution process
-and record the paths of accessed files, which including the files of software dependencies.
-Parrot adopts this solution. Even if git is one software dependency, there is no necessary to install git on the new machine.
-All the files to guarantee the accurate execution of git has been copied into the package.
-
-%\subsection{The preservation} When the authors and the programs becomes more
-%and more, the whole pool of one repo may be nearly to be preserved. why not
-%directly copy the whole repo and preserve it at the begining directly?  Answer:
-%we must concern the efficiency of repeating one small and simple program.
-\subsection{Preservation Degree of Directory Structure}
-
-Data and software preservation of physics experiments must concern the
-preservation degree of the original filesystem.  The three core components of
-one filesytem are file, directory and metadata.  The access of files can be
-divided into two categories: only access file metadata, like size, ownership,
-access authority list, and access both the file content and metadata.  If both
-the content and metadata need to be accessed, the whole file must be copies
-into the package.  However, if only the metadata of one file is accessed, how
-to preserve the file needs to be considered carefully. If the file size
-is 1KB or 1MB, preserving the content is acceptable. If the size of one file is
-1GB, preserving the whole file just for accessing its metadata is
-inefficient.
-
-Directory is one list of files and subdirectories under it. At first, we only
-copy the accessed items under one directory and ignored the unaccessed items.
-However, some operations on one directory depends on each item under it. For
-example, {\tt ls /dirA} is one linux command to list the name of each item under
-{\tt /dirA}. Because the directory itself has the name list of items under it, only
-the path of the directory is recorded into the namelist in the first phrase of
-Solution 4. However, when we repeat the command {\tt ls /dirA} using the preserved package, it returns NULL because none of items under it exists in
-the package, the behavior of the whole program will become incorrect
-and unpredictable.
-
-To ensure the semantics of the original program, all the items under one directory must be copied
-into the package. However, the
-time and space overhead appears again. Currently, Solution 4 creates one item
-with the same name but the size of zero for each item under {\tt /dirA}. Another
-solution is to introduce one database to preserve the metadata of each file and
-directory.
-
-\subsection{User Access Model of Data and Software}
-
-The user access module of remote data
-and software has a great impact of the preservation mechanism, especially when
-we try to integrate the preservation of multiple programs. If all the programs
-only refer the original data and software and refuse to modify them, the
-preservation is easy and can ignore the data version problem. However, if some
-programs try to modify the original data and software to accustom to its own
-requirement, the preservation mechanism must provide one way to differentiate
-the original data and the special data used in one certain
-program. To have a clear understanding of the data access model, more examples
-need to be investigated.
+\section{Open Problems}
+
+Figure~\ref{fig:Preservation integration} shows the rough information
+architecture of the curation environment that we imagine for complex
+scientific software like TauRoast.
+Each artifact to be preserved is a package that consists of a top-level
+script to invoke the software, a dependency map, and the dependencies
+themselves, which may be external to the original program.  The artifacts
+are then ingested into the archive, where shared dependencies are stored
+only once.  In cases where an artifact has a dependency on a trusted
+(or very large) remote archive, the dependency may simply be tracked
+instead of ingested. A reearcher that wishes to reproduce a given
+result need only refer to the unique identifier of the artifact, and will
+be able to automatically extract all of the dependent components of
+that artifact.
+
+For example, in Figure~\ref{fig:Preservation integration} Script 1 depends on items A, B, and C.
+Items A and B are ingested into the archive, where B is shared with Script 2.
+Item C is stored in another trustworthy repository and is tracked rather than ingested.
+When Script 1 is exported from the repository, items A and B are exported along with it, while C can be copied or remain remote, according to the end user's choice.
+
+As simple as that picture appears, there are a number of problems that must be solved to get there:
+
+{\bf Measure the Mess or Force Cleanliness?}  Two radically different approachs to dependency tracking are possible.
+The first is to allow end users complete freedom to construct their environment as desired, then \emph{measure} what items were actually used.
+As we have shown, this is possible, but has significant overheads and does not fully preserve the structure or intent of the end user.
+The second approach is to \emph{force} users to work in a clean environment in which no resource can be used until a proper dependency has been declared.
+This ensures that all dependencies are known in advance (and made explicit to the end user) but places a variety of restrictions on the user's daily work, and may prevent creative approaches that do not fit within the curator's view of how programs should be structured.
+Whether end users will accept the inconvenience of forced cleanliness for the benefits of reproducibility can only be discovered through experiment.
+
+{\bf What is the Granularity of Dependencies?}  Dependencies could be handled
+at many different levels of granularity.  In this work, we have shown
+how they can be handled at the level of entire repositories or individual files.
+Other possible choices might include intermediate-sized software packages
+(like RPM) or in the case of experimental data, even portions of individual large files.  Clearly, a larger granularity will result in fewer packages,
+simpler dependency maps, and more wasted space; smaller granularity results
+in complex dependency maps and less wasted space.  A hybrid solution may
+be able to combine both by storing large granularity dependencies, but
+retain the ability to select sub-items out of objects when efficiency demands it.
+
+{\bf What is the Scope of Reuse?}  We have presented the data preservation
+problem as primarily one of accurate reproduction: if a result depends
+on running program X, we must be able to run exactly X again.  However,
+the goal of scientific reproducibility is rarely limited to running
+\emph{precisely} what a predecessor did. Often, the objective is to
+change a parameter or a data input in order to see how the result is affected.
+To that end, the preservation system must capture enough of the surrounding
+material to permit modifications to succeed.  From this perspective,
+a larger granularity of preservation is desirable.  A better understanding of
+how end users will consume preserved software will help to shape how
+software is preserved in the first place.
+
+{\bf How to Detect Dependencies?}  If we allow users to work in uncontrolled
+environments, then we must have better methods for understanding the dependencies  of existing programs.  At first, we relied on an expert reader to examine
+the user's script and extract the repository dependencies.  This is clearly
+not a scalable approach.  We then demonstrated an automated method of observing
+what individual files are accessed by a program. However, this does
+not cover all types of dependencies, particularly those that are networked.
+More sophisticated observation techniques could infer higher-level information,
+such as the RPM package names of the files accessed, the URLs of remote
+repositories named throughout the program, or even the addresses and names of networked dependencies like databases and filesystems.
+
+{\bf Keep Source, Binary, or Both?}
 

### 2014-03-14 paper.tex
Cleaned up section 8.

@@
 \includegraphics[width=1\columnwidth]{preservation-integration.eps}
-\caption{Preservation Integration of Multiple Programs}
+\caption{Preserving Multiple Artifacts}
 \label{fig:Preservation integration}
@@
 
-{\bf What is the Granularity of Dependencies?}  Dependencies could be handled
+{\bf Granularity of Dependencies.}  Dependencies could be handled
 at many different levels of granularity.  In this work, we have shown
@@
 
-{\bf What is the Scope of Reuse?}  We have presented the data preservation
+{\bf Scope of Reuse.}  We have presented the data preservation
 problem as primarily one of accurate reproduction: if a result depends
@@
 
-{\bf How to Detect Dependencies?}  If we allow users to work in uncontrolled
+{\bf Dependency Detection.}  If we allow users to work in uncontrolled
 environments, then we must have better methods for understanding the dependencies  of existing programs.  At first, we relied on an expert reader to examine
@@
 
-{\bf Keep Source, Binary, or Both?}
+{\bf Source, Binary, or Both?}  A science archive might choose to retain
+the source code of an artifact or the binary code that can actually run in a given environment.
+While conventional wisdom suggests that access to source code is critical for the long term
+survival and evolution of a piece of software, it also requires the maintenance of an enormous
+amount of supporting software in the form of compilers, linkers, and supporting libraries for
+the target platform.  Rebuilding all of these for every invocation of an artifact is
+likely to have excessive cost.  We suggest that a realistic repository will have to
+maintain \emph{both}: the source describes the ultimate meaning of the code, but
+the binary is an important performance cache, a backup if the compiler toolchain should
+fail to be preserved, and a checksum to ensure that a source artifact was rebuilt correctly.
 

### 2014-03-15 paper.tex
modify evaluation part

@@
 \section{Evaluation}
-The section evaluated the connectness and overhead of the packaging utility of Solution 4.
+We evaluated the connectness and overhead of the packaging utility of Solution 4.
 To do it, the experiment was repeated using Solution 2 and 4 on the original machine.
-Then, two different virtual machines (VM) - one VM from Notre Dame Cloud Platform based on KVM and one VM from amazon EC2 Platform based on Xen, were employed to further verify the correctness of Solution 4.
+Then, two different virtual machines (VM) - one VM from Notre Dame Cloud Platform based on KVM and one VM from Amazon EC2 Platform based on Xen, were employed to further verify the correctness of Solution 4.
 
@@
 
-As for time consumption, we counted the time used to obtain remote software dependencies, build environment, and analyze the dataset respectively.
+To measure time consumption, we counted the time used to obtain remote software dependencies, build environment, and analyze the dataset respectively.
 Solution 4 also counted the time used to obtain the file namelist and generate the package.
-
-As for data size, we can easily figure out the size of each data and code source easily inside the package under Solution 4.
+To measure data size, we can easily figure out the size of each data and code source easily inside the package under Solution 4.
 Solution 2 does not support mining of implicit dependencies.
 As for remote sources, we can figure out the named size through the analysis script.
-Howerver, it is hard to figure out the named size of each local source.
+However, it is hard to figure out the named size of each local source.
 Instead, we only knew that total size of each file system is very large.
@@
 Solution 2 and 4.
-Solution 4 is faster than Solution 2, because all the software copied into the pacakge has been compiled and the Software Acquisition stage is not necessray.
+Solution 4 is faster than Solution 2, because all the software copied into the package has been compiled and the Software Acquisition stage is not necessary.
 and all the environment building only takes 3s.
@@
 obtain the filename list and generate the package. 
-The time used for these two steps is greatly longer than the execution time
-within the new package. 
-Because each filename of the list, together with its system call type, needs to be checked, and the structure of each directory item must be maintained.
+The time used for these two steps is longer than the execution time,
+because each filename of the list, together with its system call type, needs to be checked, and the structure of each directory item must be maintained.
 However, 
 this is only done once.
-That is, once the package is
+Once the package is
 generated, many users can directly obtain the package and repeat the experiment
@@
 Table~\ref{table:size-original-real} illustrates the total size, named size in the example and actually used size of each remote source (the first 4 items) and local source (the remaining 5 items).
-The third column is corresponding to the data size of Solution 4 and can be easily figured out, because all the necessary data has been copies into the package.
-Solution 2 does not support mining of implicit dependencies.
+The third column corresponds to the data size of Solution 4 and can be easily figured out, because all the necessary data has been copied into the package.
+Solution 2 does not support measuring implicit dependencies.
 As for remote sources, we can figure out the named size through the analysis script.
-Howerver, it is hard to figure out the named size of each local source.
+However, it is hard to figure out the named size of each local source.
 Instead, we only knew that total size of each file system is very large.
 
-To further verify the correctness of Solution 4 on other machines, two different virtual machines are employed -
+To further verify the correctness of Solution 4 on other machines, two different machines are employed -
 one virtual
-machine ~\cite{goldberg1974survey} from Notre Dame Clou Platform based on KVM sharing the same kernel version with the original machine,
+machine ~\cite{goldberg1974survey} from Notre Dame Cloud Platform based on KVM sharing the same kernel version with the original machine,
 and one virtual machine from amazon EC2 ~\cite{amazon2010amazon} based on Xen.
@@
 
+Regardless, we demonstrate that the application runs correctly in a completely different environment.
 %*****hmeng-doubt:Another reason for the packaging utility is that not all the data and software generated by the second version script is used during the the actual data analysis.

### 2014-03-16 paper.tex
modify abstract and introduction: vm
modify parrot-implementation section

@@
 several methods at extracting its dependencies for the purposes
-of preservation.  We report on the completeness, performance,
+of preservation. 
+We propose one fine-grained dependency management toolkit to preserve the application and demonstrate its correctness in two different environments - one virtual machine from Notre Dame Cloud Platform and one virtual machine from Amazon EC2 Platform.
+We report on the completeness, performance,
 and efficiency of each technique, and offer some guidance for
@@
 the size of the preserved object, and the flexibility of the resulting
-object.  We describe how each of these techniques may interact with
+object.  
+We propose one fine-grained dependency management toolkit to preserve the application and demonstrate its correctness in two different environments - one virtual machine from Notre Dame Cloud Platform and one virtual machine from Amazon EC2 Platform.
+We describe how each of these techniques may interact with
 a future archive of preserved software artifacts, and conclude with
@@
 
-\subsection{Solution 4: Fine-Grained Toolkit - Package}
 The difficulty of data access authority acquisition enforces us to find out one
@@
 
-\section{One Implemention of Fine-Grained Toolkit Using Parrot}
-
-The section introduces our implementation of one fine-grained packaging utility based on Solution 4. With the help of one
+\section{One Implementation of Fine-Grained Toolkit Using Parrot}
+
+\begin{figure*}
+\centering
+\includegraphics[width=1.6\columnwidth]{workflow-parrot.eps}
+\caption{Workflow of The Fine-Grained Dependency Management Toolkit Based on Parrot}
+\label{fig:workflow-parrot}
+\end{figure*}
+
+With the help of one
 virtual filesystem access tool, Parrot ~\cite{thain2005parrot}, we trap all system calls of one
@@
 Then one self-contained package containing all the accessed files is generated to help others repeat the experiment.
-
-\subsection{Working principle of Packaging Utility}
 
@@
 debugging interface, and replaces them with remote {\tt I/O} operations as desired.
-Through executing one program under Parrot, all the paths of files involved in
-this program can be recorded.
-
-With the help of Parrot, one packaging utility which generates one independent
-package for one program to make the reproduction of the program convenient can
-be deployed. The starting point of the packaging utility is one successful execution
-sandbox (the data from Grid has been preserved in HDFS and the software from
-CMSSW, Git and HTTP has been on the local machine.). We re-execute the actual
-data analysis code under Parrot and get the name list of all the files actually
-accessed during the execution process of the actual data analysis. Then,
+
+Figure~\ref{fig:workflow-parrot} illustrates the workflow of the fine-grained dependency management toolkit based on Parrot.
+The starting point of this toolkit is one successful execution of the application on the native machine.
+First, re-execute the actual
+data analysis script under Parrot and get the name list of all the files actually
+accessed during the data analysis process. Then,
 according to the filename list, one package containing all the necessary data
-and software for one analysis program is generated. Next time, when another
+and software for one analysis program is generated. When another
 scholar wants to repeat the program, he only needs to obtain the package and
-directly execute the actual analysis program inside the package. 
-Figure~\ref{fig:solution3} illustrates the working principle of the packaging utility.
-
-\begin{table}
-    \centering
-    \begin{tabular}{|l|}
-        \hline
-        {\tt set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3)} \\
-        {\tt cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10}\\
-        {\tt cmsenv} \\
-        {\tt python setup.py install --user} \\
-        {\tt cd \$HOME/\$CMSSW\_BASE/src/ttH/TauRoast}\\
-        {\tt scripts/roaster data/generic\_ttl.yaml} \\
-        \hline
-    \end{tabular}
-    \caption{Script of Fine-Grained Toolkit using Parrot}
-    \label{table:parrot-script}
-\end{table}
-
-Table~\ref{table:parrot-script} illustrates
-the simplified script, which
-only contains the necessary environment variables and the
-actual analysis command.
-
-\subsection{Workflow of Packaging Utility}
-\begin{figure*}
-\centering
-\includegraphics[width=1.6\columnwidth]{workflow-parrot.eps}
-\caption{Workflow of Solution 4}
-\label{fig:workflow-parrot}
-\end{figure*}
-
-Figure~\ref{fig:workflow-parrot} illustrates the workflow of this solution.
-Firstly, execute the analysis program under Parrot and obtain one filename list containing all the accessed files.
-Then generate one package containing all the files included in the filename list.
-Finally, rerun the program with the help of the package.
-Each step will be examined in details.
-
-{\bf(1)} Execute one analysis program under Parrot and obtain filename list (L1) of it
-
-Parrot is one virtual file system that can support user access to multiple
-underlying file systems. Parrot traps each system call involved in the process
-of data access, figures out the type of file system and redirects it into
-corresponding operations to the accessed file system. During this process, each
-accessed file, together with the access type, such as
-open, stat, read and write, is recorded into one file.
-
-The command used to generate the filename list is as follows. The {\tt name-list} parameter refers to the path of the file containing all the accessed file name of the experiment.
-
-{\tt parrot\_run \texttt{-{}-}name-list namelist /bin/tcsh script\_v4.sh}
-
-The original ouput of this command is one namelist file with the size of 6.6MB
-and 132,047 lines, each of which corresponds to one one accessed file of the
-program. We noticed that some items appeared multiple times in the filename list. To reduce the
-packaging time, de-duplication and sorting techoniques are used for the
-namelist file, generating one smaller file with the size of 3.2MB and 67,168 lines.
-
-{\bf (2)} Generate one package containing the files of L1
-
-The packaging utility iterates each filename inside L1 and copies it into the
-target package. Finally, the target package
-together with its description information, and one map file, which redirects
-the access of files from different file systems into the files inside the target package, will be
-generated as the output of this step. The packaging process also runs within Parrot environment to
-access data from different file systems.
-
-The command used to generate the package is as follows. 
-{\tt package-utility.sh} is a bash script which iterates each line of L1 and
-determines the behavior according to the file type (common files, directories,
-symbolic link files) and the system call type.
-The package description information is shown in Table~\ref{table:package-info}.
+execute the actual analysis program inside the package.
+
+The filename list contains the names of 132,047 accessed file, together with the access type of each file, such as
+open, stat, read and write. 
+We noticed that some files appeared multiple times in the filename list. 
+De-duplication and sorting techoniques are used to deal with the original filename list, generating one smaller list containing 67,168 items.
+
+The toolkit iterates each item of the filename list, determines the process
+mode and replication degree according to the file type (common files,
+directories, symbolic links) and the system call type, generates one package
+containing all the necessray file dependnencies, and returns the description
+information of the package, as shown in Table~\ref{table:package-info}.  To
+ensure the successful reproduction, the filesystem structure of the original
+execution environment should be preserved as completely as possible. However,
+attempting to copy the whole content of one directory or one file is
+space-consuming and time-consuming, because the original program may only
+access the metadata of one file with the size of 200GB.  Our solution is to
+determine the replication degree of one directory or one file according to the
+system call type. The step also runs under Parrot to access data from
+different file systems.
 
@@
 
-{\tt parrot\_run /bin/bash package-utility.sh -L namelist}
-
-%*****lack: file content + metadata; only file metadata; different process
-%solutions
-Each file inside L1 except for common dependencies is copied into the package, the final path of the file
-becomes the path of the package, followed by the original file path. In this
-program, the path of the package is {\tt /tmp/package-hep}, so the final path of one
-file with the original path path1 is {\tt /tmp/package-hep/path1}.
-
-The map relationship between the file access path used in the actual analysis
-program and the actual file location used during the reproduction process is
-kept inside the map file, as illustrated in Table~\ref{table:map-file}.
-
-To ensure the successful reproduction, the filesystem structure of the original
-execution environment should be preserved as completely as possible. However,
-attempting to copy the whole content of one directory or one file is
-space-consuming and time-consuming, because the original program may only
-access the metadata of one file with the size of 200GB. Our solution is to
-determine the copy degree of one directory or one common file according to the
-type of the system call.
+The package, the Parrot executable program, together with the environment description information of the application, such as hardware platform, OS version and kernel version, will be published.
+
+When another scholar wants to repeat the analysis program,
+one map file, which maintains the relationship between the file access path referred in the program of the application and the actual file location 
+, will be generated, as shown in Table~\ref{table:map-file}.
+The path of the package is {\tt /tmp/package-hep}, so the actual location of one file with the original path {\tt path1} will be {\tt /tmp/package-hep/path1}.
+However, 
+it is impossible to copy the files under certain directories, such as  {\tt /dev}, which can halt the packaging process.
+It is meaningless to copy the file under the directory {\tt /proc}, because the process id of one program is random and depends on the
+current allocation of process ID.
+As for these special file paths, letting
+the program directly utilize the files on the new machine, where the new user
+repeats the program, is a better choice. 
+The item {\tt /dev /dev} of Table~\ref{table:map-file}
+illustrates this semantics.
+With the help of the map file and the package, the application can be repeated on one new machine.
 
@@
 
-%*****lack: re-execute process: re-execution process will redirect all the data access into the package except for data under proc sys dev selinux
-{\bf (3)} Repeat the analysis program using the package
-
-When another scholar wants to repeat the analysis program, 
-the description of the exepriment environment is firstly referred to build the underlying OS and basic software environment.
-In this example, the only necessary software basis is Parrot.
-Then the scholar can obtain one copy of the package and its map file, and rerun the program using the following command.
-The {\tt m} parameter can be used to refer to the path of map file, which will be explained in the next part.
-
-{\tt parrot\_run -m /tmp/mountlist /bin/tcsh script\_v4.sh}
-
-\subsection{Structure of Map File}
-
-The map file of one package supports pattern matching semantics,
-which greatly reduces the scale of the map file and improves the efficiency of file path redirection. 
-For example,
-one item inside the map file is {\tt /dir1 /package-dir1} means that the access to each file and
-subdirectory under {\tt /dir1} will be redirected into {\tt /package-dir1}.
-If the semantics of the map file do not support pattern matching, the size of the map file will become astonishing. 
-{\tt /dir1} may contain thousands of files, which will generate thousands of map items and take more time to redirect file paths.
-
-During the packaging process, we notice
-that it is impossible to copy the files under certain directories.
-For example, during namelist acquisition process, three special files under {\tt /dev} directory were recorded into the namelist: tty, null and urandom, which are used for input and output.
-Trying to copy these files into the new package would cause the packaging utility halt.
-We also notice that copying the files under directories like {\tt /proc} is
-meaningless. Because the process id of one program is random and depends on the
-current allocation of process ID.
-
-As for these special file paths, letting
-the program directly utilize the files on the new machine, where the new user
-repeats the program, is a better choice. The semantics is implemented by
-setting the target path of one file equal to the origin file path inside the
-map file. For example, {\tt /dev /dev} means that when the program needs to access
-files under {\tt /dev} directory, it will directly use the file under {\tt /dev} on the new machine, which is
-independent from the namespace of the package. This semantics also make the
-reference of files outside the package possible. If the new user wants to
-expand the analysis of one program to his own data with the path of {\tt /A}, he can add the analysis
-code into the analysis script and add one item {\tt /A /A} into the map file.
-
-\subsection{Discussion of Solution 4}
-
-Under Solution 4, the reproduction of one analysis program becomes easier.
-Rethink the example, the reproduction only needs
-to set necessary environment variables, the actual analysis command
-and the package. If different scholars want to repeat one analysis program,
-what they need to do is to obtain the package and rerun the actual analysis
-program. Under Solution 2, each scholar needs to get the necessary data and
-software, and then prepare software environment.
-
-%here is the new content-hmeng
-The starting point of Solution 4 is one successful execution on the original machine. 
-Parrot traps all the system calls and copies each accessed file (except for common dependencies) into one package.
-The necessary scientific data and software dependencies will be copied into the target package.
-Strictly speaking, the concept of software and the concept of the scientific data are lost in Solution 4, because
-the granularity of parrot is file.
-The same thing happens to networked resources.
-Packaging utlity maintains one list of common dependencies and first judges whether the file belongs to this list before trying to copy one file into the package.
-%the following subsection belongs to the "discussion of data and software
-%preservation" section
-
-%The fourth solution should be based on the third solution.
-during the packaging process, packaging utility first checks whether the file has been inside the target package, (if exists, whether it is the latest version).
-only if the file does not exist in the target package or the file in the target package is not the latest version, the packaging utility copies the file into the target package.
-
-%*****hmeng-doubt: potential risk: different analysis programs share some common file names, but with different file contents. we should analyze the possibility of conflict: data.
-
-%*****hmeng-doubt: in the fourth version, let user to mark whether they change the data and software.
-if changed, one new package is generated to avoid data overlap and pollution.
-otherwise, directly starts packaging process based on the current target package.
 \section{Evaluation}

### 2014-03-16 paper.tex
modify "fine grained dependency manamgement" section

@@
 solution, in which the reproduction of the original analysis can be done
-without any external dependency. That is, one independent and self-contained
+without any external dependency. One independent and self-contained
 package containing all the data and software dependencies is necessary. 
+Two questions must be answered for this aim.
 
+{\bf First, who should be responsible to generate the package?}
 Someone may suggest that it should be the responsibility of the original author
 to generate the required package. However, letting the original author provide
-the package. 
-One reason is that figuring out the underlying dependencies of
+the package is unrealistic. 
+Figuring out the underlying dependencies of
 each software is complex and time-consuming and even impossible for the
@@
 dependencies is not under the research field of physists.
+Therefore, one packaging utility is necessary to help the original author to generate the package.
 
-To generate one self-contained and independent package for one experiment, all
-the clear and implicit dependencies must be figured out firstly. The map mechanism
-of Solution 3 can provide clear data and software dependencies. As for the
-implicit dependencies, directly preserving the whole OS together with the data
+{\bf Second, how to figure out the implicit dependencies?}
+With the help of the formulated script, we can easily figure out the explicit dependencies.
+The requirements of the underlying OS and hardware
+architecture can be easily found with system tools such as uname or
+lsb\_release.
+However, how to figure out the implicit dependencies needs more concerns, because
+directly preserving the whole OS together with the data
 stored on the disk of the original machine or the data from other filesystems
@@
 efficient mechanism which can figure out the really used parts of all these
-filesystems is necessary. The requirements of the underlying OS and hardware
-architecture can be easily found with system tools such as uname or
-lsb\_release.
-
-Then one new package including all the data and software dependencies can be generated and published. 
-One packaging utility is necessary for the original author to generate the package. 
-To multiplex the common data which is involved in different experiments, such as OS images and common software libraries, the data of different packages will be rearranged and categorized in the archive.
-One description file, which includes the experiment aim, dependency list,  package size and relevant information, will be generated for each package.
+filesystems is necessary. 
+To do this, the file access details of the application should be tracked and utilized.
 
@@
 Table~\ref{table:archive-map} illustrates the structure of the remote archive.
+To multiplex the common data which is involved in different experiments, such as OS images and common software libraries, the data of different packages will be rearranged and categorized in the archive.
 Item {\tt /archive/OS} includes the images of different Operating Systems.
@@
 Grid. Item {\tt /archive/experiment} includes the all the experiments submitted into the
-archive. The private files and description files of each experiment will be
-organized together.
+archive, each sub-item should include the private files and description files of each experiment.
 
-The Version 4 of Table~\ref{table:scripts} illustrates the script used in
-Solution 4, which is the same as the one used in Solution 3. 
-However, one map file is necessary for the relocation of the data access targets, as
+One map file is necessary for the relocation of the data access targets, as
 show in Figure~\ref{fig:version-evolution}. 
@@
 
-\section{One Implementation of Fine-Grained Toolkit Using Parrot}
+\section{One Fine Grained Dependency Management Toolkit Based on Parrot}
 

### 2014-03-17 paper.tex
modify figure2,3 and section 5 and 6

@@
 The relationship of different roles involved in the experiment preservation and
-reproduction is shown in Figure~\ref{fig:solution3}.  The original author is
-responsible for generating one package with the help of the packaging utility. Then the package, together with
-its map file and description file will be uploaded into the archive. When
-another scholar wants to repeat the experiment, one copy of the package and its
-corresponding map file will be downloaded into the new machine.
+reproduction is shown in Figure~\ref{fig:solution3}.  The original author uses the packaging utility to generate the package for one application.
+Then the package, together with
+its map file and description file will be published. When
+another researcher wants to repeat the experiment, one copy of the package will be downloaded into the new machine and the application can be repeated.
 
-\begin{table}
-    \centering
-    \begin{tabular}{|l|l|}
-        \hline
-        \bf Archive Path & \bf Service Description \\ \hline
-        {\tt /archive/OS/path} & OS Image \\ \hline
-        {\tt /archive/software/path} & Common Software Library \\ \hline
-        {\tt /archive/CMSSW/path} & CMS Software Library \\ \hline
-        {\tt /archive/git/path} & Git Software Library \\ \hline
-        {\tt /archive/http/path} & HTTP resources \\ \hline
-        {\tt /archive/experiment/path} & experiment private files \\ \hline
-        {\tt /archive/grid-data/path} & data from the Grid \\ \hline
-    \end{tabular}
-    \caption{Structure Organization of the Archive}
-    \label{table:archive-map}
-\end{table}
-
-Table~\ref{table:archive-map} illustrates the structure of the remote archive.
-To multiplex the common data which is involved in different experiments, such as OS images and common software libraries, the data of different packages will be rearranged and categorized in the archive.
-Item {\tt /archive/OS} includes the images of different Operating Systems.
-Item {\tt /archive/software} integrates all the commonly used software, such as git,
-python, perl. The archive also organizes the data from CMSSW, Git, HTTP and the
-Grid. Item {\tt /archive/experiment} includes the all the experiments submitted into the
-archive, each sub-item should include the private files and description files of each experiment.
-
-One map file is necessary for the relocation of the data access targets, as
+When we try to repeat one application on one new machine, one map file is necessary for the relocation of the data access targets, as
 show in Figure~\ref{fig:version-evolution}. 
-The map file redirects the git access path into {\tt /archive/git} from the original path (\path{http://github.com}) referred in the script.
+The map file clearly defines the real location of each dependency in the format of dependency variables - the real location of dependency variable {\tt GIT} is \path{http://github.com} and the real location of dependency variable {\tt CVMFS}
+is {\tt /tmp/package-hep/cvmfs}.
+The script only refers to the dependency variables defined in the map file.
 This design decouples the experiment script and the actual data access targets, which minimizes the impact of the evolution of different data dependencies
 and ensures the transparent access.
-The modification of the archive only introduces the minimal changes of the map file on the client side.
-
-The archive supports two different data preservation models: Internal and External.
-Internal method will preserve the data in the archive.
-External method refuses to preserve the content of data, but only preserve the reference to the actual storage place of data.
-For example, the size of experiment data from the Grid is extremely large, and storing the same data in the archive is time-consuming and space-consuming.
-Through External method, the archive only preserves one reference to the data inside the remote Grid.
-
-This solution tries to create one self-contained and independent package for
-each experiment and integrate different packages for different experiments into
-one archive to multiplex common data. One packaging utility, which can figure out all the really used data of one program  will be provided
-to help the original author to generate the package. The archive can maintain
-the experiment dependencies through Internal or External method. The archive
-itself will be responsible for the data maintenance and relevant authority
-access problem. The new user can repeat one experiment through the
-interaction with the archive.
+The modification of the package only introduces the minimal changes of the map file on the client side.
 
@@
 directories, symbolic links) and the system call type, generates one package
-containing all the necessray file dependnencies, and returns the description
+containing all the necessary file dependencies, and returns the description
 information of the package, as shown in Table~\ref{table:package-info}.  To
@@
 attempting to copy the whole content of one directory or one file is
-space-consuming and time-consuming, because the original program may only
-access the metadata of one file with the size of 200GB.  Our solution is to
+space-consuming and time-consuming, because the original program may 
+only need to know how many items one directory contains and not need the content of the sub-dirctories or the sub-files.
+Our solution is to
 determine the replication degree of one directory or one file according to the
-system call type. The step also runs under Parrot to access data from
+system call type. 
+If one file is accessed through system calls like {\tt open}, {\tt read} and {\tt write}, the whole content of the file will be copied into the package.
+However, if the application only needs to check the existence of one file through {\tt stat} system call, we only create an empty file in the package.
+As for a directory item, the sub-items under it will be copied into the package if their contents are necessary.
+Otherwise, we only create empty sub-items in the package to maintain the directory structure.
+The step also runs under Parrot to access data from
 different file systems.
@@
 
-When another scholar wants to repeat the analysis program,
+When another researcher wants to repeat the analysis program,
 one map file, which maintains the relationship between the file access path referred in the program of the application and the actual file location 
@@
 However, 
-it is impossible to copy the files under certain directories, such as  {\tt /dev}, which can halt the packaging process.
-It is meaningless to copy the file under the directory {\tt /proc}, because the process id of one program is random and depends on the
-current allocation of process ID.
+it is impossible to copy the files under certain directories, such as  {\tt /dev}, which contains all the device files.
+Each device file is either a block file or a character file. 
+The new machine may not share the same device configuration with the original machine, so copying block files into the package is meaningless.
+Copying character files such as /dev/tty and /dev/urandom is also meaningless because of their dynamic nature.
+It is meaningless to copy the file under the directory {\tt /proc}, 
+because OS may allocate different process IDs for multiple executions of one application.
 As for these special file paths, letting
@@
     \bf Category & \bf Time & \bf Time \\ \hline
+    Obtain filename list & N/A & 28min 23s \\ \hline
+    Generate package & N/A & 85min 51s \\ \hline
     Software Acquisition & 8min 11s & N/A \\ \hline
@@
 
-Table~\ref{table:time-3rd} illustrates the time used to
+Table~\ref{table:time-2nd3rd} also illustrates the time used to
 obtain the filename list and generate the package. 
@@
 separately.
-
-\begin{table}
-    \centering
-    \begin{tabular}{|l|r|}
-    \hline
-    \bf Sub-Task &\bf Time \\ \hline
-    Obtain filename list & 28min 23s \\ \hline
-    Generate package & 85min 51s \\ \hline
-    \end{tabular}
-    \caption{Time Used to Obtain Filename List and Generate Package}
-    \label{table:time-3rd}
-\end{table}
 
@@
 Figure~\ref{fig:Preservation integration} shows the rough information
-architecture of the curation environment that we imagine for complex
+architecture of the archive that we imagine for complex
 scientific software like TauRoast.

### 2014-03-18 paper.tex
add total size of each item of the filename list
spelling check and experiment data recheck

@@
 
-Reproducibility is a cornerstone of the scientific process ~\cite{borgman2012data}.
+Reproducibility is a cornerstone of the scientific process~\cite{borgman2012data}.
 In order to understand, verify, and build upon previous work,
@@
 reproducibility must also encompass the environments, data, and software
-involved in each result ~\cite{zabolitzky2002preserving}. It is widely recognized that informal
+involved in each result~\cite{zabolitzky2002preserving}. It is widely recognized that informal
 descriptions of software and systems -- although common -- are insufficient
@@
 \begin{itemize}
-\item The {\bf computing environment}, consisting of the basic hardware and the operating system can be preserved as physical artifacts or as a combination of virtual machine monitor (hardware) and virtual machine image (operating system) ~\cite{matthews2009towards}.
+\item The {\bf computing environment}, consisting of the basic hardware and the operating system can be preserved as physical artifacts or as a combination of virtual machine monitor (hardware) and virtual machine image (operating system)~\cite{matthews2009towards}.
 \item The {\bf scientific data} to be analyzed has historically received the most attention for curation.
@@
 interested reader can obtain and re-use. This approach has
-been used to some success with systems like JVM ~\cite{barthe2008preservation}.
+been used to some success with systems like JVM~\cite{barthe2008preservation}.
 \footnote{Of course, we are glossing over the problem that hardware
@@
 are inherently external to the system, such as a database, a code
-repository ~\cite{cms2006cmssw}, or a scalable filesystem ~\cite{blomer2011cernvm}.  For such resources, it
+repository~\cite{cms2006cmssw}, or a scalable filesystem~\cite{blomer2011cernvm}.  For such resources, it
 must be decided whether the dependency will simply be noted, or if it
@@
 
-\item Where {\bf common dependencies} are widely used, it may be ineffecient or
+\item Where {\bf common dependencies} are widely used, it may be inefficient or
 impossible to store one copy of each dependency for each archived object.
@@
         Linux commands & localFS & 110GB &  N/A & 68.4MB \\ \hline     
-        HOME dir& AFS &10.2GB & N/A & 32MB\\ \hline
+        HOME dir& AFS &12GB & N/A & 32MB\\ \hline
         Misc commands & PanFS & 155TB & N/A  & 1.6MB \\ \hline
@@
             the second column illustrates the size of the named files from each source;
-            the third column illustrates the size of acutally used data from each source.
+            the third column illustrates the size of actually used data from each source.
             N/A denotes it is hard to figure out the named size of implicit dependencies directly.        
@@
 Within the ongoing investigation of the Higgs boson at the CMS
-detector, part of the LHC at CERN ~\cite{collaboration2008cms}, the Higgs production in association
+detector, part of the LHC at CERN~\cite{collaboration2008cms}, the Higgs production in association
 with two top quarks allows to measure the Higgs coupling strength to
@@
 The CMS collaboration provides analysis end-users with a pre-processed
-and reduced data format, AOD ~\cite{holtman2001cms}, containing information for events, i.e.,
+and reduced data format, AOD~\cite{holtman2001cms}, containing information for events, i.e.,
 proton-proton collisions with a signature of interest, in the form of
@@
 It is performed by a small custom code framework,
-which is built on top of the CMS software stack, CMSSW ~\cite{cms2006cmssw},
+which is built on top of the CMS software stack, CMSSW~\cite{cms2006cmssw},
 and uses packages provided by several other special interest groups within CMS.
@@
 storing a virtual machine image containing the local filesystem. However,
-the application dependend on no less than {\bf six} networked filesystems
+the application depended on no less than {\bf six} networked filesystems
 available on a particular machine available to the author:
@@
 and a variety of software tools were on an NFS~\cite{howard1988scale},
-pNFS~\cite{welch2008scalable} and AFS~\cite{sandberg1985design} systems.
+PanFS~\cite{welch2008scalable} and AFS~\cite{sandberg1985design} systems.
 The original authors were not aware of many of these dependencies,
@@
 all of the dependencies in the map, download those that are missing,
-and then modifiy the map to point to the local copies of the dependencies.
+and then modify the map to point to the local copies of the dependencies.
 (Or, in the case of a dependency upon a reliable external archive,
@@
 architecture design of the required package including all the data and software
-dependencies is not under the research field of physists.
+dependencies is not under the research field of physicists.
 Therefore, one packaging utility is necessary to help the original author to generate the package.
@@
 The requirements of the underlying OS and hardware
-architecture can be easily found with system tools such as uname or
-lsb\_release.
+architecture can be easily found with system tools such as {\tt uname} or
+{\tt lsb\_release}.
 However, how to figure out the implicit dependencies needs more concerns, because
@@
 With the help of one
-virtual filesystem access tool, Parrot ~\cite{thain2005parrot}, we trap all system calls of one
+virtual filesystem access tool, Parrot~\cite{thain2005parrot}, we trap all system calls of one
 program through ptrace debugging interface, and collect all the names of accessed files. 
@@
 We noticed that some files appeared multiple times in the filename list. 
-De-duplication and sorting techoniques are used to deal with the original filename list, generating one smaller list containing 67,168 items.
+De-duplication and sorting techniques are used to deal with the original filename list, generating one smaller list containing 67,168 items.
+The total size of each involved directory and file is 900.3GB.
 
@@
 space-consuming and time-consuming, because the original program may 
-only need to know how many items one directory contains and not need the content of the sub-dirctories or the sub-files.
+only need to know how many items one directory contains and not need the content of the sub-directories or the sub-files.
 Our solution is to
@@
     \end{tabular}
-    \caption{Package Infomation}
+    \caption{Package Information}
     \label{table:package-info}
@@
 \section{Evaluation}
-We evaluated the connectness and overhead of the packaging utility of Solution 4.
+We evaluated the correctness and overhead of the packaging utility of Solution 4.
 To do it, the experiment was repeated using Solution 2 and 4 on the original machine.
@@
 
-We first repeated the example from scratch using Solution 2 on the the original machine and counted the time consumption and data size. 
+We first repeated the example from scratch using Solution 2 on the original machine and counted the time consumption and data size. 
 Then based on the successful execution of Solution 2, Solution 4 is evaluated - one package containing necessary dependencies is generated, and then the time consumption and data size is analyzed.
@@
 To measure time consumption, we counted the time used to obtain remote software dependencies, build environment, and analyze the dataset respectively.
-Solution 4 also counted the time used to obtain the file namelist and generate the package.
+Solution 4 also counted the time used to obtain the filename list and generate the package.
 To measure data size, we can easily figure out the size of each data and code source easily inside the package under Solution 4.
@@
 Solution 4 is faster than Solution 2, because all the software copied into the package has been compiled and the Software Acquisition stage is not necessary.
-and all the environment building only takes 3s.
-We were suprised that Solution 4 even reduces the actual analysis time. 
+and all the environment building only takes 4 seconds.
+We were surprised that Solution 4 even reduces the actual analysis time. 
 The reason for this is that data is obtained through accessing HDFS in Solution 2, but is copied into the package in Solution 4.
@@
     \bf Category & \bf Time & \bf Time \\ \hline
-    Obtain filename list & N/A & 28min 23s \\ \hline
+    Obtain filename list & N/A & 28min 28s \\ \hline
     Generate package & N/A & 85min 51s \\ \hline
     Software Acquisition & 8min 11s & N/A \\ \hline
-    Environment Build & 5min 49s  & 3s \\ \hline
+    Environment Build & 5min 49s  & 4s \\ \hline
     Actual Analysis & 20min 31s & 13min 04s \\ \hline
@@
 one virtual
-machine ~\cite{goldberg1974survey} from Notre Dame Cloud Platform based on KVM sharing the same kernel version with the original machine,
-and one virtual machine from amazon EC2 ~\cite{amazon2010amazon} based on Xen.
+machine~\cite{goldberg1974survey} from Notre Dame Cloud Platform based on KVM sharing the same kernel version with the original machine,
+and one virtual machine from amazon EC2~\cite{amazon2010amazon} based on Xen.
 
@@
 each machine and the execution time of the experiment on each machine.
-All the machines adopt x86\_64 hardware platform and linux OS.
+All the machines adopt x86\_64 hardware platform and Linux OS.
 Both of the two VMs repeated the experiment with the help of the package generated on the original machine successfully.
@@
     \bf Type   &\bf Version&\bf Cores & (\bf GB) & \bf Time\\ \hline
-    Native &  RedHat  & 64 & 125 & 13min 04s\\  
+    Native &  Red Hat  & 64 & 125 & 13min 04s\\  
     Machine& 5.10 &&&\\ \hline
@@
     (Notre Dame)&5.10 &&&\\ \hline
-    Xen & RedHat & 16 & 60.5 & 13min 30s\\ 
+    Xen & Red Hat & 16 & 60.5 & 13min 30s\\ 
     (EC2) &5.9 &&&\\ \hline
@@
 (or very large) remote archive, the dependency may simply be tracked
-instead of ingested. A reearcher that wishes to reproduce a given
+instead of ingested. A researcher that wishes to reproduce a given
 result need only refer to the unique identifier of the artifact, and will
@@
 
-{\bf Measure the Mess or Force Cleanliness?}  Two radically different approachs to dependency tracking are possible.
+{\bf Measure the Mess or Force Cleanliness?}  Two radically different approaches to dependency tracking are possible.
 The first is to allow end users complete freedom to construct their environment as desired, then \emph{measure} what items were actually used.
@@
 environment. 
-Software migration technique \cite{cifuentes1996binary,mancl2001refactoring} was used to facilitate running software on new machines.
+Software migration technique~\cite{cifuentes1996binary,mancl2001refactoring} was used to facilitate running software on new machines.
 However, migration often involves the re-compiling and re-configuring
@@
 The working principle, design principle and
-performance evaluation of system virtual machine were illustrated in \cite{goldberg1974survey, smith2005architecture}. 
+performance evaluation of system virtual machine were illustrated in~\cite{goldberg1974survey, smith2005architecture}. 
 The
-functionality of system VM to support different guest operating systems was illustrated in \cite{barham2003xen,kivity2007kvm,rosenblum1999vmware}.
-F. Esquembre \cite{esquembre2004easy} illustrated how JVM, one process virtual machine, can expedite the creation of
+functionality of system VM to support different guest operating systems was illustrated in~\cite{barham2003xen,kivity2007kvm,rosenblum1999vmware}.
+F. Esquembre~\cite{esquembre2004easy} illustrated how JVM, one process virtual machine, can expedite the creation of
 scientific simulations in Java. 
-The pros and cons of these three approaches were discussed in \cite{matthews2009towards,phelps2005no,hong2010software}.
+The pros and cons of these three approaches were discussed in~\cite{matthews2009towards,phelps2005no,hong2010software}.
 
-The preservation of computing environment and software environment was treated as one entirety in \cite{matthews2009towards,phelps2005no,hong2010software}.
+The preservation of computing environment and software environment was treated as one entirety in~\cite{matthews2009towards,phelps2005no,hong2010software}.
 However, frequently changing experiment software makes the maintenance of the preserved experimental environment very complex.
-CernVM \cite{buncic2010cernvm} treated them as two different categories.
+CernVM~\cite{buncic2010cernvm} treated them as two different categories.
 The preservation of computing environment is implemented with CernVM, and the preservation of software environment is based on a CernVM filesystem(CVMFS) specifically designed for efficient software distribution.
 
-The importance of preserving software in source code format was emphasized in \cite{zabolitzky2002preserving,castagne2013consider}. 
-However, CVMFS \cite{buncic2010cernvm} published pre-built and configured experiment software releases to avoid repeating the time-consuming software building procedure.
+The importance of preserving software in source code format was emphasized in~\cite{zabolitzky2002preserving,castagne2013consider}. 
+However, CVMFS~\cite{buncic2010cernvm} published pre-built and configured experiment software releases to avoid repeating the time-consuming software building procedure.
 
 Attempts from different perspectives to facilitate the reproduction of scientific experiments utilizing preserved software library has been made. 
-The software distribution mechanism over network was discussed in \cite{compostella2010cdf, blomer2011cernvm}.
+The software distribution mechanism over network was discussed in~\cite{compostella2010cdf, blomer2011cernvm}.
 J.
 R.
-Rice et al.
-\cite{rice1996scientific} made the reproduction process easier through the integration of user interface, scientific software libraries, knowledge base into problem-solving environment.
-S. R. Kohn et al. \cite{kohn2001divorcing} tried to enable the creation and distribution of language-independent software library by addressing language interoperability.
-a scalable, distributed and dynamic workflow system for digitization processes was proposed in \cite{schoneberg2013scalable}.
-A distributed archival network was designed in \cite{subotic2013distributed} to facilitate process-oriented automatic long-term digital preservation.
-M. Agosti et al. \cite{agosti2012envisage} aimed to help non-domain users to utilize the digital archive system developed for domain experts.
+Rice et al.~\cite{rice1996scientific} made the reproduction process easier through the integration of user interface, scientific software libraries, knowledge base into problem-solving environment.
+S. R. Kohn et al.~\cite{kohn2001divorcing} tried to enable the creation and distribution of language-independent software library by addressing language interoperability.
+a scalable, distributed and dynamic workflow system for digitization processes was proposed in~\cite{schoneberg2013scalable}.
+A distributed archival network was designed in~\cite{subotic2013distributed} to facilitate process-oriented automatic long-term digital preservation.
+M. Agosti et al.~\cite{agosti2012envisage} aimed to help non-domain users to utilize the digital archive system developed for domain experts.
 
@@
 
-B. Matthews et al. \cite{matthews2008significant} introduced one conceptual framework for software preservation from several case studies of software preservation.
-One tool to capture software preservation properties within a software environment was designed in \cite{matthews2010framework} through a series of case studies conducted to evaluate the software preservation framework.
-L. R. Johnston et al. \cite{johnston2014workflow} proposed one overall data curation workflow for 3-5 case studies of preserving research data.
-Two case studies \cite{borgman2012data} were conducted to figure out the properties of data to be reused in the future, including type, purpose, new users.
+B. Matthews et al.~\cite{matthews2008significant} introduced one conceptual framework for software preservation from several case studies of software preservation.
+One tool to capture software preservation properties within a software environment was designed in~\cite{matthews2010framework} through a series of case studies conducted to evaluate the software preservation framework.
+L. R. Johnston et al.~\cite{johnston2014workflow} proposed one overall data curation workflow for 3-5 case studies of preserving research data.
+Two case studies~\cite{borgman2012data} were conducted to figure out the properties of data to be reused in the future, including type, purpose, new users.
 To figure out how to preserve HEP applications, this paper studies one case of preserving one representative HEP application.
@@
 \section{Postscript}
-By the way, at the beginnig of our case study, we generated one package for the
+By the way, at the beginning of our case study, we generated one package for the
 example based on Solution 4. Several months later, the original machine met

### 2014-03-18 paper.tex
paper reference error hdfs cvmfs

@@
 available on a particular machine available to the author:
-the data to be analyzed was stored on an HDFS~\cite{hadoop} cluster,
-some configuration data was stored on a CVMFS~\cite{cvmfs} filesystem,
+the data to be analyzed was stored on a HDFS~\cite{borthakur2008hdfs} cluster,
+some configuration data was stored on a CVMFS~\cite{blomer2011cernvm} filesystem,
 and a variety of software tools were on an NFS~\cite{howard1988scale},

### 2014-03-18 paper.tex
figure 1

@@
 The application which is the study of this paper is called \emph{TauRoast}
-It searches for cases where the the Higgs boson decays to two tau leptons.
+It searches for cases where the Higgs boson decays to two tau leptons.
 The leptons are not observed directly, but by the particle showers
@@
 distribution released a new version, the target execution environment was upgraded
-to a new operating system, and the experiment deprecated the use of CVS for obtaining
+to a new operating system, and the application deprecated the use of CVS for obtaining
 the software.  While the users of this software seem be accustomed to constant change,
@@
 each software is complex and time-consuming and even impossible for the
-original author. In this experiment, the machine used for the experiment is one
+original author. In this application, the machine used for the application is one
 public machine of physics department, and the original author is one common user without
@@
 
-The relationship of different roles involved in the experiment preservation and
+The relationship of different roles involved in the application preservation and
 reproduction is shown in Figure~\ref{fig:solution3}.  The original author uses the packaging utility to generate the package for one application.
@@
 its map file and description file will be published. When
-another researcher wants to repeat the experiment, one copy of the package will be downloaded into the new machine and the application can be repeated.
+another researcher wants to repeat the application, one copy of the package will be downloaded into the new machine and the application can be repeated.
 
@@
 The script only refers to the dependency variables defined in the map file.
-This design decouples the experiment script and the actual data access targets, which minimizes the impact of the evolution of different data dependencies
+This design decouples the application script and the actual data access targets, which minimizes the impact of the evolution of different data dependencies
 and ensures the transparent access.
@@
 program through ptrace debugging interface, and collect all the names of accessed files. 
-Then one self-contained package containing all the accessed files is generated to help others repeat the experiment.
+Then one self-contained package containing all the accessed files is generated to help others repeat the application.
 
@@
 We evaluated the correctness and overhead of the packaging utility of Solution 4.
-To do it, the experiment was repeated using Solution 2 and 4 on the original machine.
+To do it, the application was repeated using Solution 2 and 4 on the original machine.
 Then, two different virtual machines (VM) - one VM from Notre Dame Cloud Platform based on KVM and one VM from Amazon EC2 Platform based on Xen, were employed to further verify the correctness of Solution 4.
@@
 Once the package is
-generated, many users can directly obtain the package and repeat the experiment
+generated, many users can directly obtain the package and repeat the application 
 separately.
@@
 Table~\ref{table:config-vm} illustrates the configuration of 
-each machine and the execution time of the experiment on each machine.
+each machine and the execution time of the application on each machine.
 All the machines adopt x86\_64 hardware platform and Linux OS.
-Both of the two VMs repeated the experiment with the help of the package generated on the original machine successfully.
+Both of the two VMs repeated the application with the help of the package generated on the original machine successfully.
 The execution time on one machine greatly depends on its hardware configuration.

### 2014-03-19 paper.tex
fix data result of section 3

@@
 While, at some level, the authors and users of these software know of these dependencies, they are often missing in
-informal communications or forgotten once the dependency is install.
+informal communications or forgotten once the dependency is installed.
 However, once known, they are at least expressed explicitly within the script.
@@
 storing a virtual machine image containing the local filesystem. However,
-the application depended on no less than {\bf six} networked filesystems
+the application depended on no less than {\bf five} networked filesystems
 available on a particular machine available to the author:
@@
 some configuration data was stored on a CVMFS~\cite{blomer2011cernvm} filesystem,
-and a variety of software tools were on an NFS~\cite{howard1988scale},
+and a variety of software tools were on a NFS~\cite{howard1988scale},
 PanFS~\cite{welch2008scalable} and AFS~\cite{sandberg1985design} systems.
@@
 only needs a handful of items from that source.  For example, the data is stored on an
-HDFS filesystem with 24TB of data, but only 43GB of that are the input Ntuples,
-and of those only 20GB are actually consumed by the program. The CMSSW repository is 88GB in total
-but only 448MB in source are checked out, and the software actually used only
+HDFS filesystem with 11.6TB of data, but only 43.3GB of that are the input Ntuples,
+and of those only 20GB are actually consumed by the program. The CMSSW repository is 88.1GB in total
+but only 448.3MB in source are checked out, and the software actually used only
 measured 6.3MB.  In a few cases, a source of software is named but never actually accessed.

### 2014-03-19 paper.tex
add . into two places of section 1

@@
 one must be able to first recreate previous results by applying
-the same methods. Historically, reproducibility this has been
+the same methods. Historically, reproducibility has been
 accomplished through painstaking detailed documentation recorded
@@
 knowledge that it only requires three files totalling 300MB out of that
-whole collection
+whole collection.
 
@@
 
-The application which is the study of this paper is called \emph{TauRoast}
+The application which is the study of this paper is called \emph{TauRoast}.
 It searches for cases where the Higgs boson decays to two tau leptons.

### 2014-03-19 paper.tex
figure 2 and reference capital problem
modify email of Dr. Hildreth

@@
 \affaddr{University of Notre Dame}\\
-\affaddr{\{hmeng|mwolf3|pivie|awoodard|mhildreth|dthain\}@nd.edu}
+\affaddr{\{hmeng|mwolf3|pivie|awoodard|mhildret|dthain\}@nd.edu}
 }
@@
 interested reader can obtain and re-use. This approach has
-been used to some success with systems like JVM~\cite{barthe2008preservation}.
+been used to some success with systems mentioned in~\cite{castagne2013consider}.
 \footnote{Of course, we are glossing over the problem that hardware

### 2014-03-19 paper.tex
Edited sections 4 and 5.

@@
 
-The overall reproduction of a computation has three broad components,
+The reproduction of a computation has three broad components,
 each of which suggests somewhat different approaches:
@@
 will be produced.  For a small custom application on a modest
-amount of data, this could be accomplished by capturing the environment,
+amount of data, this could be accomplished by capturing the
+complete environment,
 data, and software within a single virtual machine image,
@@
 the computation only runs correctly on a particular machine, but
-not know this is because it relies on data in a filesystem that
+not know this is because it relies on a filesystem that
 is mounted only on that machine.
@@
 refinements to convert it into an executable and preservable object.
-Then, we develop two techniques for observing and capturing the
-dependencies associated with the system, comparing the cost of capture,
-the size of the preserved object, and the flexibility of the resulting
-object.  
-We propose one fine-grained dependency management toolkit to preserve the application and demonstrate its correctness in two different environments - one virtual machine from Notre Dame Cloud Platform and one virtual machine from Amazon EC2 Platform.
+We then develop techniques for reducing the size of the dependencies
+that are necessary for the object to function, and we demonstrate
+the preserved object functioning correctly in three different
+physical and cloud environments.
 We describe how each of these techniques may interact with
@@
 
-\section{Overview of Tau Analysis}
+\section{Overview of Tau Roast}
 
@@
 that form \emph{TauRoast} are drawn from large repositories through
-multiple steps of reduction.
+multiple steps of reduction.  A preservation strategy must weigh
+whether to store the large repositories completely, the fragments
+used by an artifact, or something in between.
+
+{\bf Code Sources.} Like many scientific codes, the central algorithm
+of \emph{TauRoast} is expressed in a relatively small amount of
+custom code developed by the primary author.  But, the code cannot
+run at all without making use of an enormous collection of software
+dependencies.  Some of these dependencies are standard to operating
+systems worldwide, some are standardized across the entire high-energy
+physics field, some are particular to small collaborative groups,
+and a few are very specific to a single researcher.
+
+The largest of these repositories is the CMS Software Distribution (CMSSW),
+a carefully-curated selection of software packages which is distributed
+in several forms.  Historically, components of CMSSW were obtained by checking components
+of the source out of CVS, or by installing a complete binary package on a shared
+filesystem within an HPC center.  In recent years, distribution has moved to
+an on-demand delivery system known as CVMFS~\cite{blomer2011cernvm}, which
+provides a filesystem interface that transparently accesses a remote repository.
+The content of CMSSW is managed very carefully by a centralized team whose main goal
+is to ensure that the current version of the software operates correctly
+on the operating systems and architectures currently in use.  However,
+preservation is not a specific objective of the system, and so there is
+no particular guarantee that old versions of CMSSW will continue to
+operate indefinitely.
+
+CMSSW contains many different tools, libraries, and utilities.
+No single code uses anywhere close to all of that.
+But, because it is widely used within the community, it is common for users and developers to simply expect that a particular version of the entire repository is available.
 
@@
 analyzed by the tau analysis.
-It is performed by a small custom code framework,
-which is built on top of the CMS software stack, CMSSW~\cite{cms2006cmssw},
-and uses packages provided by several other special interest groups within CMS.
-While the CMSSW framework is installed locally,
-the various packages used are checked out from CVS,
-and the BEAN framework is stored in git.
-This is scheduled to change,
-as the CMSSW distribution model switches to a virtual filesystem mounted via FUSE,
-and special interest groups move their code to git.
+It is performed by a small custom code framework, which is built on top of CMSSW.
 The BEAN format, production code, and
@@
 
-In the second step, which is the beginning of the actual tau analysis,
-the data are reduced to variables relevant to the tau roast procedure, while
-only events matching basic quality criteria are kept.  This results in
+In the second step, the data are reduced to the ``Ntuple'' format,
+which contains only events matching basic quality criteria and
+fields relevant to \emph{TauRoast}. This results in
 a dataset of 43.3$\,$GB.  Again, the Notre Dame CMS groups cluster
@@
 built on CMSSW and the BEAN framework,
-but with output code written and maintained by a few people only.
-Again, the code is stored in a git repository.
+with code written and maintained by a small group.
 
-The final data analysis, investigated below, can be run as a single
+Once the data has been reduced to Ntuples, TauRoast can be run as a single
 process, and contains a stringent event selection to keep only high
@@
 and a few external python dependencies for convenience.
-The latter have to be manually fetched and installed,
-while the analysis program is built by CMSSW after being checked out of git.
-
-{\bf Code Sources.} Like many scientific codes, the central algorithm
-of \emph{TauRoast} is expressed in a relatively small amount of
-custom code developed by the primary author.  But, the code cannot
-run at all without making use of an enormous collection of software
-dependencies.  Some of these dependencies are standard to operating
-systems worldwide, some are standardized across the entire high-energy
-physics field, some are particular to small collaborative groups,
-and a few are very specific to a single researcher.
-
-The largest of these repositories is the CMS Software Distribution (CMSSW),
-a carefully-curated selection of software packages which is distributed
-in several forms.  Historically, components of CMSSW were obtained by checking components
-of the source out of CVS, or by installing a complete binary package on a shared
-filesystem within an HPC center.  In recent years, distribution has moved to
-an on-demand delivery system known as CVMFS~\cite{blomer2011cernvm}.  The content
-of CMSSW is managed very carefully by a centralized team whose main goal
-is to ensure that the current version of the software operates correctly
-on the operating systems and architectures currently in use.  However,
-preservation is not an objective of the group, and so there is
-no guarantee that old versions of CMSSW operate in new environments,
-or vice versa.
 
@@
 capture the entire virtual machine and all of the connected filesystems,
-doing so would be wasteful and prohibitively expensive.  Further, if multiple
+it would require 166.8TB of storage, which would be prohibitively expensive
+for capturing this one application is alone.  Further, if multiple
 similar applications are preserved, we would miss the opportunity to identify
 common dependencies and store them once for multiple artifacts.
+A more structured approach to dependency management is needed.
 
@@
 embedding such constants into the middle of a program is unwise, and so
-we extract all of those identifiers and place them at the beginning
-of the script in the form of variable substitutions.  This makes
-it readily apparent to the reader what the dependencies are.
-
-Form 4 goes a step further and takes all of the dependencies \emph{out}
-of the script itself and places them in a \emph{dependency map}.
+we extract all of those identifiers and place them \emph{outside} the
+script in a \emph{dependency map} or just \emph{map} for short.
 The dependency map lists all of the external dependencies of the application, indicating
@@
 The resulting script then simply refers to abstract file locations such
-as \verb!$CMSSW!, while the map file indicates where they are located.
-If properly constructed, the script should not refer to any external
-resource unless it is indicated in the dependency map.
+as \verb$GIT$ and \verb!$CMSSW!, while the map file indicates where they
+are currently located. If properly constructed, the script should not refer to any external
+resource unless it is indicated in the dependency map.  We call this idealized
+artifact an \emph{abstract script}.
 
-By extracting the dependencies into the external dependency map,
+By extracting the dependencies into the dependency map,
 we introduce great freedom for the curator to move, transform, and otherwise
 manipulate the dependencies of the artifact without damaging the artifact itself.
-For example, it is straightforward for an automated tool to examine
+A Figure~\ref{fig:version-evolution} shows, it is straightforward for an
+automated tool to examine
 all of the dependencies in the map, download those that are missing,
 and then modify the map to point to the local copies of the dependencies.
-(Or, in the case of a dependency upon a reliable external archive,
-the map file could continue to point to the original source.)
-
-\section{Fine Grained Dependency Management}
-
-The difficulty of data access authority acquisition enforces us to find out one
-solution, in which the reproduction of the original analysis can be done
-without any external dependency. One independent and self-contained
-package containing all the data and software dependencies is necessary. 
-Two questions must be answered for this aim.
-
-{\bf First, who should be responsible to generate the package?}
-Someone may suggest that it should be the responsibility of the original author
-to generate the required package. However, letting the original author provide
-the package is unrealistic. 
-Figuring out the underlying dependencies of
-each software is complex and time-consuming and even impossible for the
-original author. In this application, the machine used for the application is one
-public machine of physics department, and the original author is one common user without
-root authority. The underlying OS and supporting softwares are installed and
-maintained by the IT department of the university. On the other hand, the
-architecture design of the required package including all the data and software
-dependencies is not under the research field of physicists.
-Therefore, one packaging utility is necessary to help the original author to generate the package.
-
-{\bf Second, how to figure out the implicit dependencies?}
-With the help of the formulated script, we can easily figure out the explicit dependencies.
-The requirements of the underlying OS and hardware
-architecture can be easily found with system tools such as {\tt uname} or
-{\tt lsb\_release}.
-However, how to figure out the implicit dependencies needs more concerns, because
-directly preserving the whole OS together with the data
-stored on the disk of the original machine or the data from other filesystems
-mounted as local filesystems, such as HDFS and PanFS, is not feasible. One
-efficient mechanism which can figure out the really used parts of all these
-filesystems is necessary. 
-To do this, the file access details of the application should be tracked and utilized.
+If we group the script, dependency map, and dependencies into a \emph{package},
+we now have a self-contained artifact that can be moved from place to place.
+In some cases, it may be safe to allow the dependency map to refer to 
+trusted remote repositories.  Whether this is advisable is a judgement that
+must be made by the user or the curator, taking into account the long-term
+stability of said repositories.
 
@@
 and ensures the transparent access.
-The modification of the package only introduces the minimal changes of the map file on the client side.
+he modification of the package only introduces the minimal changes of the map file on the client side.
 
-\section{One Fine Grained Dependency Management Toolkit Based on Parrot}
+This basic approach to dependency management is a step in the right direction
+for dependencies that are \emph{explicit} and \emph{external} to the
+user's native execution environment.  However, it leaves two other problems unsolved.
+
+First, the basic approach requires that someone be \emph{aware} of the dependencies,
+whether it be the end user, the system administrator, or the archive curator.
+It seems reasonable to expect the user to be aware of a large dependency mentioned in a top-level script.
+But, oftentimes the dependency is embedded invisibly deep within the software stack,
+or is connected to the machine by the local system administrators.  No single party
+is likely to have complete information about all of the dependencies.
+Second, the basic approach assumes that the entire dependency is actually
+consumed by the artifact.  As we have suggested above (and will show below),
+this sort of program often only consumes a small fraction of what it does declare
+as a dependency.
+
+To address both of these problems, users and curators alike need tools that
+will automatically observe the dependencies of complex applications, to
+facilitate automatic and efficient preservation.
+
+\section{Measuring Dependencies}
 
@@
 
-With the help of one
-virtual filesystem access tool, Parrot~\cite{thain2005parrot}, we trap all system calls of one
-program through ptrace debugging interface, and collect all the names of accessed files. 
-Then one self-contained package containing all the accessed files is generated to help others repeat the application.
+We have developed a prototype tool to assist in the measurement and preservation
+of implicit dependencies for complex applications.
+We use Parrot~\cite{thain2005parrot} to explicitly record all
+of the files accessed by our example application, allowing us to observe how
+much of each external dependencies is used, and what local resources are implicitly used.
+Using this information, we create a \emph{reduced package} which contains
+only the files actually used by the application.
 
-Parrot is a virtual filesystem access tool which attaching existing programs to
-a variety of remote {\tt I/O} systems including 
-HTTP, FTP, GridFTP, iRODS, HDFS, XRootD, GROW, and Chirp. It traps all system calls of one program through ptrace
-debugging interface, and replaces them with remote {\tt I/O} operations as desired.
+Parrot is a virtual filesystem access tool which has previously been used to attach
+exisiting programs to a variety of remote I/O systems, such as HTTP, FTP, and CVMFS.
+It works by trapping an application's system calls through the {\tt ptrace} debugging
+interface, and then replacing them with the desired I/O operations.  Parrot is already used
+in the high energy physics community with applications like TauRoast specifically to 
+provide access to the CMSSW software distribution via the CVMFS distributed file system.
+We made small modifications to Parrot to record a \emph{namelist} which lists all 
+of the files that an application actually accesses.
 
-Figure~\ref{fig:workflow-parrot} illustrates the workflow of the fine-grained dependency management toolkit based on Parrot.
+Figure~\ref{fig:workflow-parrot} illustrates the measurement process.
 The starting point of this toolkit is one successful execution of the application on the native machine.
-First, re-execute the actual
-data analysis script under Parrot and get the name list of all the files actually
-accessed during the data analysis process. Then,
-according to the filename list, one package containing all the necessary data
+First, we execute the actual data analysis script under Parrot to generate the namelist.
+Then, using the namelist, we generate a package containing all the necessary data
 and software for one analysis program is generated. When another
-scholar wants to repeat the program, he only needs to obtain the package and
+researcher wants to repeat the program, he only needs to obtain the package and
 execute the actual analysis program inside the package.
 
-The filename list contains the names of 132,047 accessed file, together with the access type of each file, such as
-open, stat, read and write. 
-We noticed that some files appeared multiple times in the filename list. 
-De-duplication and sorting techniques are used to deal with the original filename list, generating one smaller list containing 67,168 items.
-The total size of each involved directory and file is 900.3GB.
+For one execution of \emph{TauRoast}, the namelist 132,047 accessed filenames,
+along with the operation used to access the file, such as {\tt open}, {\tt stat}, {\tt read}, etc.
+With duplicate filenames removed, the list is reduced to 67,168 files.
+Many of those entries do not exist, because they reflect attempts
+by the application to search for programs and libraries in multiple places.
+Only 22,068 entries reflect existing files or directories.
 
-The toolkit iterates each item of the filename list, determines the process
+The packaging tool iterates over each item of the filename list, determines the process
 mode and replication degree according to the file type (common files,
 directories, symbolic links) and the system call type, generates one package
-containing all the necessary file dependencies, and returns the description
-information of the package, as shown in Table~\ref{table:package-info}.  To
-ensure the successful reproduction, the filesystem structure of the original
-execution environment should be preserved as completely as possible. However,
-attempting to copy the whole content of one directory or one file is
-space-consuming and time-consuming, because the original program may 
-only need to know how many items one directory contains and not need the content of the sub-directories or the sub-files.
-Our solution is to
-determine the replication degree of one directory or one file according to the
-system call type. 
-If one file is accessed through system calls like {\tt open}, {\tt read} and {\tt write}, the whole content of the file will be copied into the package.
-However, if the application only needs to check the existence of one file through {\tt stat} system call, we only create an empty file in the package.
-As for a directory item, the sub-items under it will be copied into the package if their contents are necessary.
-Otherwise, we only create empty sub-items in the package to maintain the directory structure.
-The step also runs under Parrot to access data from
-different file systems.
+containing the dependencies, and summarizes the contents of the package
+as shown in Table~\ref{table:package-info}.  To the extent possible,
+the filesystem structure of the original environment is preserved.
 
-\begin{table}
-    \centering
-    \begin{tabular}{|l|}
-    \hline
-     the total size of package: 21GB \\ 
-    the total number of files: 15905\\ 
-    the total number of directory: 1549\\ 
-    the total number of symbolic link: 4614 \\ \hline 
-    \end{tabular}
-    \caption{Package Information}
-    \label{table:package-info}
-\end{table}
+We considered several approaches to constructing the package.
+In a {\bf shallow copy}, we only copied the individual files in the namelist,
+creating only parent directories for each.  Where a directory was listed,
+we created the directory and populated it with empty files as placeholders
+to facilitate a directory listing.  In a {\bf medium copy}, we copied the
+individual files as before.  Where a directory was listed, we created
+the directories and copied the contents of the files in that directory,
+one level deep.  A {\bf deep copy} would duplicate all directories recursively,
+but this would have resulted in TB-sized packages, so we did not consider
+it further.
 
-The package, the Parrot executable program, together with the environment description information of the application, such as hardware platform, OS version and kernel version, will be published.
-
-When another researcher wants to repeat the analysis program,
-one map file, which maintains the relationship between the file access path referred in the program of the application and the actual file location 
-, will be generated, as shown in Table~\ref{table:map-file}.
-The path of the package is {\tt /tmp/package-hep}, so the actual location of one file with the original path {\tt path1} will be {\tt /tmp/package-hep/path1}.
-However, 
-it is impossible to copy the files under certain directories, such as  {\tt /dev}, which contains all the device files.
-Each device file is either a block file or a character file. 
-The new machine may not share the same device configuration with the original machine, so copying block files into the package is meaningless.
-Copying character files such as /dev/tty and /dev/urandom is also meaningless because of their dynamic nature.
-It is meaningless to copy the file under the directory {\tt /proc}, 
-because OS may allocate different process IDs for multiple executions of one application.
-As for these special file paths, letting
-the program directly utilize the files on the new machine, where the new user
-repeats the program, is a better choice. 
-The item {\tt /dev /dev} of Table~\ref{table:map-file}
-illustrates this semantics.
-With the help of the map file and the package, the application can be repeated on one new machine.
+Parrot is required to re-run the packaged artifact, in order to force
+the packaged files to appear to exist in their original locations.
+To this end, the packaging tool creates a \emph{file map} which maps
+the logical names of the files to their current physical locations, as shown in Table~\ref{table:map-file}.
+Parrot reads the file map and redirects system calls at run-time to achieve the desired effect.
+As the example suggests, special device files such as {\tt /proc} and {\tt /dev}
+are not incorporated into the package but are instead accessed natively.
 
@@
 
+\begin{table}
+    \centering
+    \begin{tabular}{|r|r|r|}
+\hline
+                    & \bf Shallow Copy & \bf Medium Copy\\
+\hline
+    Whole Files:    & 1632         & 15642\\ 
+\hline
+    Empty Files:    & 14273        & 263\\
+\hline
+    Directories:    & 1549         & 1549\\ 
+\hline
+    Symbolic Links: & 4614         & ??? \\
+\hline
+    \bf Total Size: & \bf 21GB     & \bf 28GB \\ 
+\hline
+    \end{tabular}
+    \caption{Package Information}
+    \label{table:package-info}
+\end{table}
+
 \section{Evaluation}
+
 We evaluated the correctness and overhead of the packaging utility of Solution 4.
@@
     \hline
-    \bf Task & \bf Solution 2& \bf Solution 4\\ 
-    \bf Category & \bf Time & \bf Time \\ \hline
-    Obtain filename list & N/A & 28min 28s \\ \hline
-    Generate package & N/A & 85min 51s \\ \hline
+    \bf Task & \bf Original& \bf Reduced\\ 
+    \bf Category & \bf Script & \bf Package\\ \hline
+    Obtain Namelist & N/A & 28min 28s \\ \hline
+    Generate Package & N/A & 85min 51s \\ \hline
     Software Acquisition & 8min 11s & N/A \\ \hline
     Environment Build & 5min 49s  & 4s \\ \hline
-    Actual Analysis & 20min 31s & 13min 04s \\ \hline
+    Analysis Code & 20min 31s & 13min 04s \\ \hline
     \end{tabular}

### 2014-03-19 paper.tex
Cleaned up conclusion.

@@
 
-\section{Postscript}
-By the way, at the beginning of our case study, we generated one package for the
-example based on Solution 4. Several months later, the original machine met
-some problems and the access model of CMSSW was also modified. In this case, if
-you want to repeat the example on the original machine, different 
-configurations, including CMSSW\_ARCH, environment variables and CVS access
-authority need to be modified. However, with the generated package and its map file, we can repeat the experiment directly on the same machine without any modification.
+\section{Conclusion}
+
+We began this work in late 2013, generating a reduced package for \emph{TauRoast} based
+on the configuration of a standard machine at Notre Dame at the time.  In the course
+of writing this paper in spring 2014, almost everything about the computing environment
+changed: the operating system was upgraded, a new version of CMSSW was released, and
+our local HEP users switched from using CVS to CVMFS for accessing CMSSW.
+The original script provided by the author failed to run on the same machine.
+But, the reduced package we created three months earlier in the old environment
+worked just fine on the new machine.
 

### 2014-03-19 paper.tex
Added acknowledgements.
remove solution2 and 4

@@
         .h file       & HTTP& 41KB & 41KB & 0KB \\ \hline \hline
-        Ntuples data    & HDFS& 11.6TB & 43.3GB & 20GB \\ \hline
+        Ntuples data    & HDFS& 11.6TB & N/A& 20GB \\ \hline
         Configuration & CVMFS & 7.4GB & N/A & 103MB \\ \hline
@@
 only needs a handful of items from that source.  For example, the data is stored on an
-HDFS filesystem with 11.6TB of data, but only 43.3GB of that are the input Ntuples,
-and of those only 20GB are actually consumed by the program. The CMSSW repository is 88.1GB in total
+HDFS filesystem with 11.6TB of data, but only 20GB are actually consumed by the program. The CMSSW repository is 88.1GB in total
 but only 448.3MB in source are checked out, and the software actually used only
@@
 The resulting script then simply refers to abstract file locations such
-as \verb$GIT$ and \verb!$CMSSW!, while the map file indicates where they
+as \verb$GIT$ and \verb$CVMFS$, while the map file indicates where they
 are currently located. If properly constructed, the script should not refer to any external
@@
 In some cases, it may be safe to allow the dependency map to refer to 
-trusted remote repositories.  Whether this is advisable is a judgement that
+trusted remote repositories.  Whether this is advisable is a judgment that
 must be made by the user or the curator, taking into account the long-term
 stability of said repositories.
+
+However, only having the package and the dependency map is not enough. The successful execution of the application on the original machine also relies on the configuration of environment variables.
+We collected the environment variables of the original machine and transformed it into one executable script.
+If another researcher wants to repeat the application, this executable script will be first executed.
 
@@
 show in Figure~\ref{fig:version-evolution}. 
-The map file clearly defines the real location of each dependency in the format of dependency variables - the real location of dependency variable {\tt GIT} is \path{http://github.com} and the real location of dependency variable {\tt CVMFS}
-is {\tt /tmp/package-hep/cvmfs}.
+The map file clearly defines the real location of each dependency in the format of dependency variables - the real location of dependency variable {\tt GIT} is \path{/data/git/cms-ttH} and the real location of dependency variable {\tt CVMFS}
+is {\tt /data/cvmfs/grid.cern.ch}.
 The script only refers to the dependency variables defined in the map file.
@@
 and ensures the transparent access.
-he modification of the package only introduces the minimal changes of the map file on the client side.
+The modification of the package only introduces the minimal changes of the map file on the client side.
 
@@
 Parrot is a virtual filesystem access tool which has previously been used to attach
-exisiting programs to a variety of remote I/O systems, such as HTTP, FTP, and CVMFS.
+existing programs to a variety of remote I/O systems, such as HTTP, FTP, and CVMFS.
 It works by trapping an application's system calls through the {\tt ptrace} debugging
@@
 \hline
-    Symbolic Links: & 4614         & ??? \\
+    Symbolic Links: & 4614         & 4614 \\
 \hline
@@
 
-We evaluated the correctness and overhead of the packaging utility of Solution 4.
-To do it, the application was repeated using Solution 2 and 4 on the original machine.
-Then, two different virtual machines (VM) - one VM from Notre Dame Cloud Platform based on KVM and one VM from Amazon EC2 Platform based on Xen, were employed to further verify the correctness of Solution 4.
+We evaluated the correctness of the reduced package and the overhead of generating the package.
+To do it, the application was repeated with the help of Script (as shown in Figure~\ref{fig:version-evolution}) on the original machine, mentioned as {\bf Script-Solution} in the following part, 
+one reduced package was generated and verified with the help of Parrot on the original machine, which will be mentioned as {\bf Package-Solution}.
+Then, two different virtual machines (VM) - one VM from Notre Dame Cloud Platform based on KVM and one VM from Amazon EC2 Platform based on Xen, were employed to further verify the correctness of the reduced package.
 
-We first repeated the example from scratch using Solution 2 on the original machine and counted the time consumption and data size. 
-Then based on the successful execution of Solution 2, Solution 4 is evaluated - one package containing necessary dependencies is generated, and then the time consumption and data size is analyzed.
+We first repeated the example from scratch using the Script translated from the original email on the original machine and counted the time consumption and data size. 
+Then based on the successful execution of Script-Solution, Package-Solution is evaluated - one package containing necessary dependencies is generated, and then the time consumption and data size is analyzed.
 
 To measure time consumption, we counted the time used to obtain remote software dependencies, build environment, and analyze the dataset respectively.
-Solution 4 also counted the time used to obtain the filename list and generate the package.
-To measure data size, we can easily figure out the size of each data and code source easily inside the package under Solution 4.
-Solution 2 does not support mining of implicit dependencies.
+We also counted the time used to obtain the filename list and generate the package.
+To measure data size, we can easily figure out the size of each data and code source inside the package under Package-Solution.
+Script-Solution does not support mining of implicit dependencies.
 As for remote sources, we can figure out the named size through the analysis script.
@@
 Table~\ref{table:time-2nd3rd} shows the execution time comparison between
-Solution 2 and 4.
-Solution 4 is faster than Solution 2, because all the software copied into the package has been compiled and the Software Acquisition stage is not necessary.
+Script-Solution and Package-Solution.
+Package-Solution is faster than Script-Solution, because all the software copied into the package has been compiled and the Software Acquisition stage is not necessary.
 and all the environment building only takes 4 seconds.
-We were surprised that Solution 4 even reduces the actual analysis time. 
-The reason for this is that data is obtained through accessing HDFS in Solution 2, but is copied into the package in Solution 4.
+We were surprised that Package-Solution even reduces the actual analysis time. 
+The reason for this is that data is obtained through accessing HDFS in Script-Solution, but is copied into the package in Package-Solution.
 This localization of experimental data speeds up the data analysis process, resulting the actual analysis time reducing from 20 minutes to 13 minutes.
@@
     \end{tabular}
-    \caption{Execution Time Comparison between Solution 2 and 4}
+    \caption{Execution Time Comparison between Script-Solution and Package-Solution}
     \label{table:time-2nd3rd}
@@
 Table~\ref{table:size-original-real} illustrates the total size, named size in the example and actually used size of each remote source (the first 4 items) and local source (the remaining 5 items).
-The third column corresponds to the data size of Solution 4 and can be easily figured out, because all the necessary data has been copied into the package.
-Solution 2 does not support measuring implicit dependencies.
+The third column corresponds to the data size of Package-Solution and can be easily figured out, because all the necessary data has been copied into the package.
+Script-Solution does not support measuring implicit dependencies.
 As for remote sources, we can figure out the named size through the analysis script.
@@
 
-To further verify the correctness of Solution 4 on other machines, two different machines are employed -
+To further verify the correctness of Package-Solution on other machines, two different machines are employed -
 one virtual
@@
 
-\section{Conclusion}
+\section{Postscript}
 
@@
 
+\section{*Acknowledgments}
+
+This work was supported in part by National Science Foundation grants PHY-1247316 (DASPOS)
+and OCI-1148330 (SI2).  We also thank...
+
 \bibliographystyle{abbrv}

### 2014-03-19 paper.tex
Fixed.
use Original-Script and Reduced-Package

@@
 If another researcher wants to repeat the application, this executable script will be first executed.
+The environment variables refer to the dynamic named values defined in the range of one computer, like \verb!$PATH! and \verb!$PYTHONPATH!.
+However, the dependency map refers to the actual storage location of path variables used in one abstract script. For example, the actual storage location of the path variable \verb!CVMFS! 
+is {\tt /data/cvmfs/grid.cern.ch}.
 
@@
 We evaluated the correctness of the reduced package and the overhead of generating the package.
-To do it, the application was repeated with the help of Script (as shown in Figure~\ref{fig:version-evolution}) on the original machine, mentioned as {\bf Script-Solution} in the following part, 
-one reduced package was generated and verified with the help of Parrot on the original machine, which will be mentioned as {\bf Package-Solution}.
+To do it, the application was repeated with the help of Original Script (as shown in Figure~\ref{fig:version-evolution}) on the original machine, mentioned as {\bf Original-Script} in the following part,
+one reduced package was generated and verified with the help of Parrot on the original machine, which will be mentioned as {\bf Reduced-Package}.
 Then, two different virtual machines (VM) - one VM from Notre Dame Cloud Platform based on KVM and one VM from Amazon EC2 Platform based on Xen, were employed to further verify the correctness of the reduced package.
@@
 We first repeated the example from scratch using the Script translated from the original email on the original machine and counted the time consumption and data size. 
-Then based on the successful execution of Script-Solution, Package-Solution is evaluated - one package containing necessary dependencies is generated, and then the time consumption and data size is analyzed.
+Then based on the successful execution of Original-Script, Reduced-Package is evaluated - one package containing necessary dependencies is generated, and then the time consumption and data size is analyzed.
 
@@
 We also counted the time used to obtain the filename list and generate the package.
-To measure data size, we can easily figure out the size of each data and code source inside the package under Package-Solution.
-Script-Solution does not support mining of implicit dependencies.
+To measure data size, we can easily figure out the size of each data and code source inside the package under Reduced-Package.
+Original-Script does not support mining of implicit dependencies.
 As for remote sources, we can figure out the named size through the analysis script.
@@
 Table~\ref{table:time-2nd3rd} shows the execution time comparison between
-Script-Solution and Package-Solution.
-Package-Solution is faster than Script-Solution, because all the software copied into the package has been compiled and the Software Acquisition stage is not necessary.
-and all the environment building only takes 4 seconds.
-We were surprised that Package-Solution even reduces the actual analysis time. 
-The reason for this is that data is obtained through accessing HDFS in Script-Solution, but is copied into the package in Package-Solution.
+Original-Script and Reduced-Package.
+Reduced-Package is faster than Original-Script, because all the software copied into the package has been compiled and the Software Acquisition stage is not necessary.
+and all the environment building only takes 4 seconds,
+We were surprised that Reduced-Package even reduces the actual analysis time. 
+The reason for this is that data is obtained through accessing HDFS in Original-Script, but is copied into the package in Reduced-Package.
 This localization of experimental data speeds up the data analysis process, resulting the actual analysis time reducing from 20 minutes to 13 minutes.
@@
     \end{tabular}
-    \caption{Execution Time Comparison between Script-Solution and Package-Solution}
+    \caption{Execution Time Comparison between Original-Script and Reduced-Package}
     \label{table:time-2nd3rd}
@@
 Table~\ref{table:size-original-real} illustrates the total size, named size in the example and actually used size of each remote source (the first 4 items) and local source (the remaining 5 items).
-The third column corresponds to the data size of Package-Solution and can be easily figured out, because all the necessary data has been copied into the package.
-Script-Solution does not support measuring implicit dependencies.
+The third column corresponds to the data size of Reduced-Package and can be easily figured out, because all the necessary data has been copied into the package.
+Original-Script does not support measuring implicit dependencies.
 As for remote sources, we can figure out the named size through the analysis script.
@@
 
-To further verify the correctness of Package-Solution on other machines, two different machines are employed -
+To further verify the correctness of Reduced-Package on other machines, two different machines are employed -
 one virtual
@@
 
-\section{*Acknowledgments}
+\section*{Acknowledgments}
 

### 2014-03-20 paper.tex
Fine-tune tau analysis section.

@@
 which contains only events matching basic quality criteria and
-fields relevant to \emph{TauRoast}. This results in
-a dataset of 43.3$\,$GB.  Again, the Notre Dame CMS groups cluster
+fields relevant to \emph{TauRoast}.
+Again, the Notre Dame CMS groups cluster
 resources are used to perform this reduction and selection,
@@
 Once the data has been reduced to Ntuples, TauRoast can be run as a single
-process, and contains a stringent event selection to keep only high
-quality candidate events for the underlying physical process (using
-about 20$\,$MB of space).  Quantities from the selected events can be
+process, and contains a stringent event selection to look only at high
+quality candidate events for the underlying physical process.
+Quantities from the relevant events can be
 both plotted and used in multivariate analysis to determine the level

### 2014-03-20 paper.tex
remove completely in section 6

@@
 interested reader can obtain and re-use. This approach has
-been used to some success with systems mentioned in~\cite{castagne2013consider}.
+been used to some success with systems~\cite{castagne2013consider}.
 \footnote{Of course, we are glossing over the problem that hardware
@@
 \hline
-    Whole Files:    & 1632         & 15642\\ 
+    Whole Files    & 1632         & 15642\\ 
 \hline
-    Empty Files:    & 14273        & 263\\
+    Empty Files    & 14273        & 263\\
 \hline
-    Directories:    & 1549         & 1549\\ 
+    Directories    & 1549         & 1549\\ 
 \hline
-    Symbolic Links: & 4614         & 4614 \\
+    Symbolic Links & 4614         & 4614 \\
 \hline
-    \bf Total Size: & \bf 21GB     & \bf 28GB \\ 
+    \bf Total Size & \bf 21GB     & \bf 28GB \\ 
 \hline
@@
 
-Regardless, we demonstrate that the application runs correctly in a completely different environment.
+Regardless, we demonstrate that the application can be repeated with the help of the reduced package on one different machine with the required hardware architecture and OS distribution version.
 %*****hmeng-doubt:Another reason for the packaging utility is that not all the data and software generated by the second version script is used during the the actual data analysis.

### 2014-03-21 paper.tex
merge Dr. Hildreth's comments

@@
 of preservation. 
-We propose one fine-grained dependency management toolkit to preserve the application and demonstrate its correctness in two different environments - one virtual machine from Notre Dame Cloud Platform and one virtual machine from Amazon EC2 Platform.
+We propose one fine-grained dependency management toolkit to preserve the application and demonstrate its correctness in two different environments - one virtual machine from the Notre Dame Cloud Platform and one virtual machine from the Amazon EC2 Platform.
 We report on the completeness, performance,
@@
 and then depositing the virtual
-it into a curated environment.  The publication could
+image into a curated environment.  The publication could
 then simply refer to the identifier of the image, which the
@@
 However, this simple approach is not sufficient for large applications
-that are run in complex social environments.
+that are run in complex environments.
 
@@
 with two top quarks allows to measure the Higgs coupling strength to
-top quarks.  As the Higgs boson is to short-lived to be detected
+top quarks~\cite{chatrchyan2013search}.  As the Higgs boson is too short-lived to be detected
 itself, it has to be reconstructed from its decay products.
@@
 It searches for cases where the Higgs boson decays to two tau leptons.
-The leptons are not observed directly, but by the particle showers
+Since the tau leptons are very short-lived, they are not observed directly, but by the particle decay products 
 that they generate.  So, the analysis must search for detector
@@
 
-The largest of these repositories is the CMS Software Distribution (CMSSW),
+The largest of these repositories is the CMS Software Distribution (CMSSW)~\cite{cms2006cms},
 a carefully-curated selection of software packages which is distributed
 in several forms.  Historically, components of CMSSW were obtained by checking components
-of the source out of CVS, or by installing a complete binary package on a shared
+of the source out of CVS (CMSSW source codes were moved from CVS to git recently), or by installing a complete binary package on a shared
 filesystem within an HPC center.  In recent years, distribution has moved to
@@
 CMSSW contains many different tools, libraries, and utilities.
-No single code uses anywhere close to all of that.
-But, because it is widely used within the community, it is common for users and developers to simply expect that a particular version of the entire repository is available.
+No single code uses anywhere close to all of these.
+But, because it is widely used within the experimental researchers, it is common for users and developers to simply expect that a particular version of the entire repository is available.
 
@@
 reconstructed particles.  This format is based on the RAW output of
-the CMS detector readout electronics and reconstructed world-wide.
+the CMS detector readout electronics and reconstructed world-wide, which is then processed through various algorithms derive signatures of individual particles.
 Both real and simulated data are available for examination.
@@
 As AOD data are too large to be iteratively processed repetitively in
-an physics analysis workflow, it is normally reduced further in
+a physics analysis workflow, it is normally reduced further in
 structural complexity and content.  For the analysis under
 investigation here, this is a two-step process.  First, the AOD data
-are processed at the Notre Dame working group cluster to BEAN events,
+are processed at the Notre Dame working group cluster to BEAN (Boson Exploration Analysis Ntuple) events,
 containing only trivial data containers packed in vectors.  This step
@@
 to obtain all the dependencies and run the artifact correctly.
-(The original email also indicated how to run the application
+(The original instructions introduced in the email also indicated how to run the application
 within a production batch system.  For the purposes of preservation,
@@
 available on a particular machine available to the author:
-the data to be analyzed was stored on a HDFS~\cite{borthakur2008hdfs} cluster,
+the data to be analyzed was stored on an HDFS~\cite{borthakur2008hdfs} cluster,
 some configuration data was stored on a CVMFS~\cite{blomer2011cernvm} filesystem,
-and a variety of software tools were on a NFS~\cite{howard1988scale},
+and a variety of software tools were on an NFS~\cite{howard1988scale},
 PanFS~\cite{welch2008scalable} and AFS~\cite{sandberg1985design} systems.
@@
 only needs a handful of items from that source.  For example, the data is stored on an
-HDFS filesystem with 11.6TB of data, but only 20GB are actually consumed by the program. The CMSSW repository is 88.1GB in total
+HDFS filesystem with 11.6TB of data, but only 20GB are actually consumed by the program. 
+The reason for this great reduction is at first each BEAN event contains a large amount of information, and the TauAnalysis throws away a lot of the irrelevant event information, keeping only the relevant bits.
+The CMSSW repository is 88.1GB in total
 but only 448.3MB in source are checked out, and the software actually used only
@@
 Then, using the namelist, we generate a package containing all the necessary data
-and software for one analysis program is generated. When another
+and software for one analysis program. When another
 researcher wants to repeat the program, he only needs to obtain the package and
@@
 We evaluated the correctness of the reduced package and the overhead of generating the package.
-To do it, the application was repeated with the help of Original Script (as shown in Figure~\ref{fig:version-evolution}) on the original machine, mentioned as {\bf Original-Script} in the following part,
-one reduced package was generated and verified with the help of Parrot on the original machine, which will be mentioned as {\bf Reduced-Package}.
-Then, two different virtual machines (VM) - one VM from Notre Dame Cloud Platform based on KVM and one VM from Amazon EC2 Platform based on Xen, were employed to further verify the correctness of the reduced package.
+To do this, the application was repeated with the help of Original Script (as shown in Figure~\ref{fig:version-evolution}) on the original machine. 
+Then one reduced package was generated and verified with the help of Parrot on the original machine.
+
+Then, two different virtual machines (VM) - one VM from the Notre Dame Cloud Platform based on KVM and one VM from the Amazon EC2 Platform based on Xen, were employed to further verify the correctness of the reduced package.
 
@@
 
-To measure time consumption, we counted the time used to obtain remote software dependencies, build environment, and analyze the dataset respectively.
+To measure time consumption, we counted the time used to obtain remote software dependencies, build the environment, and analyze the dataset.
 We also counted the time used to obtain the filename list and generate the package.
@@
 each machine and the execution time of the application on each machine.
-All the machines adopt x86\_64 hardware platform and Linux OS.
+All the machines adopt the x86\_64 hardware platform and Linux OS.
 Both of the two VMs repeated the application with the help of the package generated on the original machine successfully.
@@
 
-This work was supported in part by National Science Foundation grants PHY-1247316 (DASPOS)
-and OCI-1148330 (SI2).  We also thank...
+This work was supported in part by National Science Foundation grants PHY-1247316 (DASPOS), 
+OCI-1148330 (SI2) and PHY-1312842.  We also thank the support and help of the Center for Research Computing (CRC) of University of Notre Dame.
 

### 2014-03-21 paper.tex
reduce to 9 pages

@@
 No single code uses anywhere close to all of these.
-But, because it is widely used within the experimental researchers, it is common for users and developers to simply expect that a particular version of the entire repository is available.
+But, because it is widely used within the experimental researchers, it is common for users to simply expect that a particular version of the entire repository is available.
 
@@
 
-Parrot is a virtual filesystem access tool which has previously been used to attach
+Parrot is a virtual filesystem access tool which has been used to attach
 existing programs to a variety of remote I/O systems, such as HTTP, FTP, and CVMFS.
@@
 (or very large) remote archive, the dependency may simply be tracked
-instead of ingested. A researcher that wishes to reproduce a given
+. A researcher that wishes to reproduce a given
 result need only refer to the unique identifier of the artifact, and will
@@
 Other possible choices might include intermediate-sized software packages
-(like RPM) or in the case of experimental data, even portions of individual large files.  Clearly, a larger granularity will result in fewer packages,
+(like RPM) or in the case of experimental data, even portions of individual large files.  Clearly, a larger granularity will result in 
 simpler dependency maps, and more wasted space; smaller granularity results
@@
 be able to combine both by storing large granularity dependencies, but
-retain the ability to select sub-items out of objects when efficiency demands it.
+selecting sub-items out of objects when efficiency demands it.
 
@@
 environments, then we must have better methods for understanding the dependencies  of existing programs.  At first, we relied on an expert reader to examine
-the user's script and extract the repository dependencies.  This is clearly
+the user's script and extract the dependencies.  This is clearly
 not a scalable approach.  We then demonstrated an automated method of observing
@@
 The importance of preserving software in source code format was emphasized in~\cite{zabolitzky2002preserving,castagne2013consider}. 
-However, CVMFS~\cite{buncic2010cernvm} published pre-built and configured experiment software releases to avoid repeating the time-consuming software building procedure.
+However, CVMFS~\cite{buncic2010cernvm} published pre-built and configured experiment software releases to avoid the time-consuming software building procedure.
 
@@
 However, this is not always right.
-In some cases, the original author may leave additional code referring to irrelative data and software in the experiment programs.
+In some cases, the original author may leave additional code referring to irrelative data and software in the program.
 One mechanism, which can figure out the absolutely relevant data and software of one experiment, is important for both the preservation and reproduction of scientific experiments.
@@
 L. R. Johnston et al.~\cite{johnston2014workflow} proposed one overall data curation workflow for 3-5 case studies of preserving research data.
-Two case studies~\cite{borgman2012data} were conducted to figure out the properties of data to be reused in the future, including type, purpose, new users.
+Two case studies~\cite{borgman2012data} were conducted to figure out the properties of data to be reused in the future.
 To figure out how to preserve HEP applications, this paper studies one case of preserving one representative HEP application.

### 2014-03-23 paper.tex
acknowledgement to crc
small modify

@@
 \usepackage[flushleft]{threeparttable}
+\hyphenation{resour-ces}
+\hyphenation{approac-hes}
+\hyphenation{har-der}
+\hyphenation{spe-cifically}
 \begin{document}
@@
 \begin{itemize}
-\item The {\bf computing environment}, consisting of the basic hardware and the operating system can be preserved as physical artifacts or as a combination of virtual machine monitor (hardware) and virtual machine image (operating system)~\cite{matthews2009towards}.
+\item The {\bf computing environment}, consisting of the basic hardware and the operating system which can be preserved as physical artifacts or as a combination of virtual machine monitors (hardware) and virtual machine images (operating system)~\cite{matthews2009towards}.
 \item The {\bf scientific data} to be analyzed has historically received the most attention for curation.
@@
 detector, part of the LHC at CERN~\cite{collaboration2008cms}, the Higgs production in association
-with two top quarks allows to measure the Higgs coupling strength to
+with two top quarks allows measuring the Higgs coupling strength to
 top quarks~\cite{chatrchyan2013search}.  As the Higgs boson is too short-lived to be detected
@@
 {\bf Data Sources.}
-The CMS collaboration provides analysis end-users with a pre-processed
+The CMS collaboration provides end-users with a pre-processed
 and reduced data format, AOD~\cite{holtman2001cms}, containing information for events, i.e.,
@@
 reconstructed particles.  This format is based on the RAW output of
-the CMS detector readout electronics and reconstructed world-wide, which is then processed through various algorithms derive signatures of individual particles.
+the CMS detector readout electronics and reconstructed world-wide, which is then processed through various algorithms which derive signatures of individual particles.
 Both real and simulated data are available for examination.
@@
 by the CMS experiment.  Before running any code, {\tt scram} is used to locate
-the appropriate version software,  set environment variables such as the PATH, run any
+the appropriate version of software,  set environment variables such as the PATH, run any
 tool-specific configuration, and do the same for all software on which it depends.
@@
 The CMSSW repository is 88.1GB in total
-but only 448.3MB in source are checked out, and the software actually used only
+but only 448.3MB of source is checked out, and the actually used software only
 measured 6.3MB.  In a few cases, a source of software is named but never actually accessed.
@@
 between collecting the initial email, analyzing the program, and writing this
-paper, the computing environment was under continuous change.  The CMSSW software
+paper, the computing environment continuously changed.  The CMSSW software
 distribution released a new version, the target execution environment was upgraded
@@
 it would require 166.8TB of storage, which would be prohibitively expensive
-for capturing this one application is alone.  Further, if multiple
+for capturing this one application alone.  Further, if multiple
 similar applications are preserved, we would miss the opportunity to identify
@@
 existing programs to a variety of remote I/O systems, such as HTTP, FTP, and CVMFS.
-It works by trapping an application's system calls through the {\tt ptrace} debugging
+It works by trapping an application's system calls through the Linux {\tt ptrace} debugging
 interface, and then replacing them with the desired I/O operations.  Parrot is already used
@@
 
-For one execution of \emph{TauRoast}, the namelist 132,047 accessed filenames,
-along with the operation used to access the file, such as {\tt open}, {\tt stat}, {\tt read}, etc.
+For one execution of \emph{TauRoast}, the generated namelist includes 132,047 accessed filenames,
+along with the system calls used to access the file, such as {\tt open}, {\tt stat}, {\tt read}, etc.
 With duplicate filenames removed, the list is reduced to 67,168 files.
@@
 We evaluated the correctness of the reduced package and the overhead of generating the package.
-To do this, the application was repeated with the help of Original Script (as shown in Figure~\ref{fig:version-evolution}) on the original machine. 
-Then one reduced package was generated and verified with the help of Parrot on the original machine.
+To do this, the application was repeated with the help of \emph{Original Script} (as shown in Figure~\ref{fig:version-evolution}) on the original machine. 
+Then one \emph{reduced package} was generated and verified with the help of Parrot on the original machine.
 
@@
 We first repeated the example from scratch using the Script translated from the original email on the original machine and counted the time consumption and data size. 
-Then based on the successful execution of Original-Script, Reduced-Package is evaluated - one package containing necessary dependencies is generated, and then the time consumption and data size is analyzed.
+Then based on the successful execution of Original Script, we evaluated Reduced Package - one package containing necessary dependencies is generated, and then the time consumption and data size is analyzed.
 
 To measure time consumption, we counted the time used to obtain remote software dependencies, build the environment, and analyze the dataset.
-We also counted the time used to obtain the filename list and generate the package.
-To measure data size, we can easily figure out the size of each data and code source inside the package under Reduced-Package.
-Original-Script does not support mining of implicit dependencies.
+We also counted the time used to obtain the namelist and to generate the package.
+To measure data size, we can easily figure out the size of each data and code source inside the package under Reduced Package.
+Original Script does not support mining of implicit dependencies.
 As for remote sources, we can figure out the named size through the analysis script.
@@
 Table~\ref{table:time-2nd3rd} shows the execution time comparison between
-Original-Script and Reduced-Package.
-Reduced-Package is faster than Original-Script, because all the software copied into the package has been compiled and the Software Acquisition stage is not necessary.
+Original Script and Reduced Package.
+Reduced Package is faster than Original Script, because all the software copied into the package has been compiled and the Software Acquisition stage is not necessary.
 and all the environment building only takes 4 seconds,
-We were surprised that Reduced-Package even reduces the actual analysis time. 
-The reason for this is that data is obtained through accessing HDFS in Original-Script, but is copied into the package in Reduced-Package.
+We were surprised that Reduced Package even reduces the actual analysis time. 
+The reason for this is that data is obtained through accessing HDFS in Original Script, but is copied into the package in Reduced Package.
 This localization of experimental data speeds up the data analysis process, resulting the actual analysis time reducing from 20 minutes to 13 minutes.
@@
     \end{tabular}
-    \caption{Execution Time Comparison between Original-Script and Reduced-Package}
+    \caption{Execution Time Comparison between Original Script and Reduced Package}
     \label{table:time-2nd3rd}
@@
 Table~\ref{table:time-2nd3rd} also illustrates the time used to
-obtain the filename list and generate the package. 
+obtain the namelist and to generate the package. 
 The time used for these two steps is longer than the execution time,
@@
 
-Table~\ref{table:size-original-real} illustrates the total size, named size in the example and actually used size of each remote source (the first 4 items) and local source (the remaining 5 items).
-The third column corresponds to the data size of Reduced-Package and can be easily figured out, because all the necessary data has been copied into the package.
-Original-Script does not support measuring implicit dependencies.
+Table~\ref{table:size-original-real} on page 2 illustrates the total size, named size in the example and actually used size of each remote source (the first 4 items) and local source (the remaining 5 items).
+The third column corresponds to the data size of Reduced Package and can be easily figured out, because all the necessary data has been copied into the package.
+Original Script does not support measuring implicit dependencies.
 As for remote sources, we can figure out the named size through the analysis script.
@@
 
-To further verify the correctness of Reduced-Package on other machines, two different machines are employed -
+To further verify the correctness of Reduced Package on other machines, two different machines are employed -
 one virtual
-machine~\cite{goldberg1974survey} from Notre Dame Cloud Platform based on KVM sharing the same kernel version with the original machine,
-and one virtual machine from amazon EC2~\cite{amazon2010amazon} based on Xen.
+machine~\cite{goldberg1974survey} from the Notre Dame Cloud Platform based on KVM sharing the same kernel version with the original machine,
+and one virtual machine from  the Amazon EC2~\cite{amazon2010amazon} Platform based on Xen.
 
@@
 each machine and the execution time of the application on each machine.
-All the machines adopt the x86\_64 hardware platform and Linux OS.
+All the machines adopt the x86\_64 hardware platform and Linux kernel.
 Both of the two VMs repeated the application with the help of the package generated on the original machine successfully.
@@
     \bf Type   &\bf Version&\bf Cores & (\bf GB) & \bf Time\\ \hline
-    Native &  Red Hat  & 64 & 125 & 13min 04s\\  
+    Original &  Red Hat  & 64 & 125 & 13min 04s\\  
     Machine& 5.10 &&&\\ \hline
@@
 
-Regardless, we demonstrate that the application can be repeated with the help of the reduced package on one different machine with the required hardware architecture and OS distribution version.
+In summary, we demonstrate that the application can be repeated with the help of the reduced package on one different machine with the required hardware architecture and OS kernel version.
 %*****hmeng-doubt:Another reason for the packaging utility is that not all the data and software generated by the second version script is used during the the actual data analysis.
@@
 However, migration often involves the re-compiling and re-configuring
-the source code to accustom a new hardware platform and software environment.
+the source code to accommodate a new hardware platform and software environment.
 Emulation recreates the original software and hardware environment by
@@
 
-Attempts from different perspectives to facilitate the reproduction of scientific experiments utilizing preserved software library has been made. 
+Attempts from different perspectives to facilitate the reproduction of scientific experiments utilizing a preserved software library have been made. 
 The software distribution mechanism over network was discussed in~\cite{compostella2010cdf, blomer2011cernvm}.
@@
 Two case studies~\cite{borgman2012data} were conducted to figure out the properties of data to be reused in the future.
-To figure out how to preserve HEP applications, this paper studies one case of preserving one representative HEP application.
 
@@
 This work was supported in part by National Science Foundation grants PHY-1247316 (DASPOS), 
-OCI-1148330 (SI2) and PHY-1312842.  We also thank the support and help of the Center for Research Computing (CRC) of University of Notre Dame.
-
+OCI-1148330 (SI2) and PHY-1312842.
+The University of Notre Dame Center for Research Computing scientists and engineers provided critical technical assistance throughout this research effort.
 \bibliographystyle{abbrv}

### 2014-12-08 paper.tex
add subtitle and remove copyright info.
Modify acknowledgement
Add network_tracking_parrot into paper.tex (section 5.1)

@@
 \hyphenation{spe-cifically}
+\makeatletter
+\def\@copyrightspace{\relax}
+\makeatother
 \begin{document}
@@
 \title{A Case Study in Preserving a\\High Energy Physics Application}
+\subtitle{DASPOS Technical Report \#2}
 \author{
@@
 
+\subsection{Tracking of Network Dependencies}
+
+\begin{figure}
+\centering
+\includegraphics[width=1\columnwidth]{git-syscall.eps}
+\caption{Exec Syscalls of a git command}
+\label{fig:git-syscall}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=1\columnwidth]{http_packet.eps}
+\caption{HTTP Request and Response}
+\label{fig:http_packet}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=1\columnwidth]{url_redirection.eps}
+\caption{An Example of URL Redirection}
+\label{fig:url_redirection}
+\end{figure}
+
+All the dependencies of one program can be divided into three categories: local file system (e.g., /usr, /lib and /lib64), remote file systems which can be mounted as local directories (e.g., /cvmfs and /hdfs), and other remote network dependencies (e.g.
+http, https and ssh).
+Through utilizing ptrace to trap each file-relevant system call used by a program, the first two categories of dependencies can be collected. 
+Motivation of tracking network dependencies: Linkrot is a common and great threat to the preservation of scientific applications.
+A URL which works normally today may be unavailable permanently.
+A method which can help the scientists figure out all the network dependencies of their applications provides the chance to evaluate the stability of each network dependencies and preserve the unstable network resources before linkrot happens.
+One direct solution to track the third category of dependencies is to utilize ptrace to check each exec system call used by a program and record each network-relevant executable and its parameters.
+However, an executable may create one or more child processes to finish some tasks, and a child process may create their own children processes.
+Figure~\ref{fig:git-syscall} shows all the processes created by a git command.
+A process with PID 998 is created to clone a remote git repository into local machine, which totally has 6 child processes.
+Moreover, a network-relevant executable name collection is necessary to identify network dependencies.
+The diversity of network-relevant executables and the large process tree generated for a network executable make this solution infeasible.
+
+Another solution to track network dependencies is to track the network sockets.
+The user process communicates with the network protocol stacks in the kernel through the network socket layer user interface on Linux.
+From the process tree shown in the above figure, the process with PID 1000 responds to create a socket, connect to a DNS server, send a DNS request packet to the DNS server and receive a DNS response packet from the DNS server.
+The information gained from the network socket tracking can be divided into three categories.
+\begin{itemize}
+\item The information of network sockets used to communicate with remote network dependences (through socket and connect system calls) can be used to figure out the port number, service name (such as, http, https, and ssh), socket type (stream and datagram),  and the domain type (inet and inet6).
+\item The contents of DNS packets can be used to figure out the hostname and IP address of each remote network dependency. 
+\item As for applications based on http protocol, all the http requests and responses can be seen, as shown in Figure~\ref{fig:http_packet}.
+However, as for applications based on https and ssh which encrypt network data using TLS/SSL, tracking network data on the socket level can only see the encrypted data.
+\end{itemize}
+
+The results of tracking network sockets used by a program involves two categories of network resource redirections, dns-level hostname redirection and website-level url redirection. 
+\begin{itemize}
+\item dns-level hostname redirection: Each DNS packet includes five parts, header, question, answer, authority, and additional.
+A DNS response packet with the type CNAME has multiple answers.
+For example, the DNS response packet which tries to resolve {\tt www3.nd.edu} includes two answers.
+The first answer provides an alias of {\tt www3.nd.edu}, {\tt www-vip.cc.nd.edu}, and the second answer maps the alias to the IP address.
+{\tt www3.nd.edu} CNAME {\tt www-vip.cc.nd.edu}
+{\tt www-vip.cc.nd.edu} A {\tt 129.74.12.151}
+The CNAME-type DNS packets leave us a question, among the hostname used by the user, the alias(es), the IP address, what should we preserve?
+\item website-level url redirection: Website-level url redirection happens when a website updates its location and still want their old users access their resources using the old url.
+Figure~\ref{fig:url_redirection} illustrates the url redirection between {\tt \url{www3.nd.edu/~ccl}} and {\tt ccl.cse.nd.edu}.
+Except for the difference of hostnames, the application layer protocols used by the old-version website and the new-version website is also different: the old website provides services through the https protocol, while the new website provides services through the http protocol.
+\end{itemize}
+
+The usage of https protocol makes detecting of website-level url redirections through tracking system calls more difficulty and even impossible.
+All the application data will be encrypted at presentation layer through the TLS/SSL protocol, which is initialized at the session layer and works at the presentation layer.
+
 \section{Evaluation}
@@
 The University of Notre Dame Center for Research Computing scientists and engineers provided critical technical assistance throughout this research effort.
+
+Copyright (C) 2014 The University of Notre Dame
+
+This work is licensed under the Creative Commons Attribution 4.0 License.
+
 \bibliographystyle{abbrv}

### 2014-12-18 paper.tex
Change the template to ICCS
	remove old template and related files

@@
-\documentclass{sig-alternate}
+\documentclass[procedia]{easychair}
 \usepackage{url}
@@
 \makeatother
+
+\title{A Case Study in Preserving a High Energy Physics Application}
+
+% \titlerunning{} has to be set to either the main title or its shorter
+% version for the running heads. When processed by
+% EasyChair, this command is mandatory: a document without \titlerunning
+% will be rejected by EasyChair
+
+\titlerunning{A Case Study in Preserving a High Energy Physics Application}
+
+\author{
+	Haiyan Meng\inst{1}
+\and
+	Matthias Wolf\inst{2}
+\and
+	Douglas Thain\inst{3}
+}
+\institute{
+	Department of Computer Science and Engineering,
+	University of Notre Dame,
+	Notre Dame, Indiana, USA
+	\email{hmeng@nd.edu}
+\and
+	Department of Physics,
+	University of Notre Dame,
+	Notre Dame, Indiana, USA
+	\email{mwolf3@nd.edu}
+\and
+	Department of Computer Science and Engineering,
+	University of Notre Dame,
+	Notre Dame, Indiana, USA
+	\email{dthain@nd.edu}
+}
+
+%  \authorrunning{} has to be set for the shorter version of the authors' names;
+% otherwise a warning will be rendered in the running heads. When processed by
+% EasyChair, this command is mandatory: a document without \authorrunning
+% will be rejected by EasyChair
+
+\authorrunning{Meng, Wolf and Thain}
+
 \begin{document}
 
-\title{A Case Study in Preserving a\\High Energy Physics Application}
-\subtitle{DASPOS Technical Report \#2}
-\author{
-Haiyan Meng, Matthias Wolf, Peter Ivie, Anna Woodard, Michael Hildreth, and Douglas Thain\\
-\affaddr{Department of Physics and Department of Computer Science and Engineering}\\
-\affaddr{University of Notre Dame}\\
-\affaddr{\{hmeng|mwolf3|pivie|awoodard|mhildret|dthain\}@nd.edu}
-}
-\date{15 January 2014}
 \maketitle
+
+\keywords{}
 
@@
 \centering
-\includegraphics[width=.8\columnwidth]{data-code-size.eps}
+\includegraphics[width=.5\textwidth]{data-code-size.eps}
 \caption{Inputs to Tau Roast}
@@
 \end{figure}
-
-\begin{table}[t]
-    \centering
-    \small
-    \begin{tabular}{|l|l|r|r|r|}
-        \hline
-        \bf Name & \bf Location & \bf Total & \bf Named & \bf Used \\ 
-        \hline
-        CMSSW code     & CVS & 88.1GB & 448.3MB & 6.3MB\\ \hline
-        Tau source       & Git & 73.7MB & 73.7MB & 6.7MB \\ \hline
-        PyYAML binaries    & HTTP & 52MB & 52MB & 0KB \\ \hline
-        .h file       & HTTP& 41KB & 41KB & 0KB \\ \hline \hline
-        Ntuples data    & HDFS& 11.6TB & N/A& 20GB \\ \hline
-        Configuration & CVMFS & 7.4GB & N/A & 103MB \\ \hline
-        Linux commands & localFS & 110GB &  N/A & 68.4MB \\ \hline     
-        HOME dir& AFS &12GB & N/A & 32MB\\ \hline
-        Misc commands & PanFS & 155TB & N/A  & 1.6MB \\ \hline
-        Total      &    & 166.8TB            & N/A & 21GB \\ \hline
-    \end{tabular}
-    \begin{tablenotes}
-      \small
-      \item The first column illustrates the total size of each data and software source; 
-            the second column illustrates the size of the named files from each source;
-            the third column illustrates the size of actually used data from each source.
-            N/A denotes it is hard to figure out the named size of implicit dependencies directly.        
-    \end{tablenotes}
-    \caption{Data and Code Used by Tau Roast}
-    \label{table:size-original-real}
-\end{table}
 
@@
 \centering
-\includegraphics[width=1.6\columnwidth]{version-evolution.eps}
+\includegraphics[width=.8\textwidth]{version-evolution.eps}
 \caption{Version Evolution}
@@
 \centering
-\includegraphics[width=.8\columnwidth]{solution3.eps}
+\includegraphics[width=.5\textwidth]{solution3.eps}
 \caption{Relationship of Roles}
@@
 \centering
-\includegraphics[width=1.6\columnwidth]{workflow-parrot.eps}
+\includegraphics[width=.8\textwidth]{workflow-parrot.eps}
 \caption{Workflow of The Fine-Grained Dependency Management Toolkit Based on Parrot}
@@
     \centering
-    \begin{tabular}{|l|l|}
+    \begin{tabular}{ll}
     \hline
@@
     \centering
-    \begin{tabular}{|r|r|r|}
+    \begin{tabular}{rrr}
 \hline
@@
 \centering
-\includegraphics[width=1\columnwidth]{git-syscall.eps}
+\includegraphics[width=.6\textwidth]{git-syscall.eps}
 \caption{Exec Syscalls of a git command}
@@
 \centering
-\includegraphics[width=1\columnwidth]{http_packet.eps}
+\includegraphics[width=.6\textwidth]{http_packet.eps}
 \caption{HTTP Request and Response}
@@
 \centering
-\includegraphics[width=1\columnwidth]{url_redirection.eps}
+\includegraphics[width=.6\textwidth]{url_redirection.eps}
 \caption{An Example of URL Redirection}
@@
     \centering
-    \begin{tabular}{|l|r|r|}
-    \hline
-    \bf Task & \bf Original& \bf Reduced\\ 
-    \bf Category & \bf Script & \bf Package\\ \hline
+    \begin{tabular}{lrr}
+    \hline
+    \bf Task Category & \bf Original Script & \bf Reduced Package \\ \hline
     Obtain Namelist & N/A & 28min 28s \\ \hline
@@
 
+\begin{table}
+	\centering
+	    \begin{tabular}{llrrr}
+	        \hline
+	        \bf Name & \bf Location & \bf Total & \bf Named & \bf Used \\ 
+	        \hline
+	        CMSSW code     & CVS & 88.1GB & 448.3MB & 6.3MB\\ \hline
+	        Tau source       & Git & 73.7MB & 73.7MB & 6.7MB \\ \hline
+	        PyYAML binaries    & HTTP & 52MB & 52MB & 0KB \\ \hline
+	        .h file       & HTTP& 41KB & 41KB & 0KB \\ \hline \hline
+	        Ntuples data    & HDFS& 11.6TB & N/A& 20GB \\ \hline
+	        Configuration & CVMFS & 7.4GB & N/A & 103MB \\ \hline
+	        Linux commands & localFS & 110GB &  N/A & 68.4MB \\ \hline     
+	        HOME dir& AFS &12GB & N/A & 32MB\\ \hline
+	        Misc commands & PanFS & 155TB & N/A  & 1.6MB \\ \hline
+	        Total      &    & 166.8TB            & N/A & 21GB \\ \hline
+	    \end{tabular}
+	    \caption{Data and Code Used by Tau Roast}
+	    \label{table:size-original-real}
+\end{table}
+%	\begin{tablenotes}
+%	      \small
+%	      \item The first column illustrates the total size of each data and software source; 
+%	            the second column illustrates the size of the named files from each source;
+%	            the third column illustrates the size of actually used data from each source.
+%	            N/A denotes it is hard to figure out the named size of implicit dependencies directly.        
+%	    \end{tablenotes}
+
 To further verify the correctness of Reduced Package on other machines, two different machines are employed -
@@
     \centering
-    \begin{tabular}{|l|r|r|r|r|}
-    \hline
-    \bf Machine & \bf Distro & \bf CPU & \bf Mem & \bf Execution\\ 
-    \bf Type   &\bf Version&\bf Cores & (\bf GB) & \bf Time\\ \hline
-    Original &  Red Hat  & 64 & 125 & 13min 04s\\  
-    Machine& 5.10 &&&\\ \hline
-    KVM & CentOS & 4 & 2 & 21min 38s\\
-    (Notre Dame)&5.10 &&&\\ \hline
-    Xen & Red Hat & 16 & 60.5 & 13min 30s\\ 
-    (EC2) &5.9 &&&\\ \hline
+    \begin{tabular}{lrrrr}
+    \hline
+    \bf Machine Type & \bf Distro Version & \bf CPU Cores & \bf Mem (GB) & \bf Execution Time \\ \hline 
+    Original Machine &  Red Hat 5.10 & 64 & 125 & 13min 04s\\  \hline
+    KVM (Notre Dame) & CentOS 5.10 & 4 & 2 & 21min 38s\\ \hline
+    Xen (EC2) & Red Hat 5.9 & 16 & 60.5 & 13min 30s\\ \hline
     \end{tabular}
@@
 \centering
-\includegraphics[width=1\columnwidth]{preservation-integration.eps}
+\includegraphics[width=.6\textwidth]{preservation-integration.eps}
 \caption{Preserving Multiple Artifacts}
@@
 
-\bibliographystyle{abbrv}
+\bibliographystyle{plain}
 \bibliography{cclpapers,this}

### 2015-01-02 paper.tex
Revised Abstract

@@
 \begin{abstract}
-\it The reproducibility of scientific results increasingly
-depends upon the preservation of computational artifacts.
-Although preserving a computation to be used later sounds
-easy, it is surprisingly difficult due to the complexity
-of existing software and systems.  Implicit dependencies,
-networked resources, and shifting compatibility all conspire
-to break applications that appear to work well.  To investigate
-these issues, we present a case study of a complex high energy
-physics application.  We analyze the application and attempt
-several methods at extracting its dependencies for the purposes
-of preservation. 
-We propose one fine-grained dependency management toolkit to preserve the application and demonstrate its correctness in two different environments - one virtual machine from the Notre Dame Cloud Platform and one virtual machine from the Amazon EC2 Platform.
+\it Computational reproducibility depends on being able to isolate necessary and sufficient computational artifacts and preserve them for later re-execution.
+Both isolation and preservation of artifacts can be challenging due to the complexity
+of existing software and systems and the resulting implicit dependencies, resource distribution, and shifting compatibility of systems---all conspiring
+to break the reproducibility of an application. Sandboxing is a technique
+that has been used extensively in OS environments for isolation of computational artifacts.
+Several tools were proposed recently that employ sandboxing as a mechanism to ensure reproducibility.
+However, none of these tools preserve the sandboxed application for re-distribution
+to a larger scientific community---aspects that are equally crucial for ensuring reproducibility as sandboxing itself.
+In this paper, we describe a combined sandboxing and preservation framework, which is efficient and practical and
+useful for large-scale reproducibility. We present a case study of a complex high energy
+physics application and show how the framework can be useful for sandboxing and preserving.
 We report on the completeness, performance,
-and efficiency of each technique, and offer some guidance for
-future work in application preservation.
+and efficiency of the framework, and suggest possible standardization approaches.
 \end{abstract}

### 2015-01-05 paper.tex
Modified Intro

@@
 
-\title{A Case Study in Preserving a High Energy Physics Application}
+\title{An Invariant Framework for Conducting Reproducible Computational Science}
 
@@
 
-\titlerunning{A Case Study in Preserving a High Energy Physics Application}
+\titlerunning{An invariant framework for conducting reproducible computational science}
 
@@
 Both isolation and preservation of artifacts can be challenging due to the complexity
-of existing software and systems and the resulting implicit dependencies, resource distribution, and shifting compatibility of systems---all conspiring
+of existing software and systems and the resulting implicit dependencies, resource distribution, and shifting compatibility of systems as time progresses---all conspiring
 to break the reproducibility of an application. Sandboxing is a technique
@@
 \section{Introduction}
+
+% Reproducibility
+Reproducibility is a cornerstone of the scientific method~\cite{borgman2012data}. 
+Its importance is underscored by its ability to advance science---reproducing by verifying and validating a scientific result leads to improved understanding, thus increasing possibilities of reusing or extending the result.
+Ensuring reproducibility of a scientific result, however, often entails detailed documentation and specification of the involved scientific method.
+Historically, this has been achieved through text and proofs in a publication.
+As computation pervades the sciences and transforms the scientific method, mere text is considered insufficient. 
+In particular, apart from textual descriptions describing the result, a reproducible result must also include several computational artifacts, such as software, data,  environment variables, and state of computation that are involved in the adopted scientific method.
+By including computational artifacts, the scientific result can be obtained again at a later time.
+
+Virtualization has emerged as a promising approach for reproducing computational scientific results.
+One approach is to conduct the entire computation relating to a scientific result within a virtual machine image, and then share the resulting image.
+This way VMIS become an authoritative, encapsulated and executable records of computations, especially computations whose results are destined for publication and/or re-use, and this can be shared easily.
+With this approach, oftentimes, the resulting image is too big in size for share-ability purposes.
+An alternative light-weight form of virtualization allows encapsulating just the application software, along with all its necessary dependencies into a self contained package, thus separating , and not including, the underlying operating system on which it is executed.
+This encapsulation is achieved by interposing application system calls, and copying necessary dependencies (data, libraries, code) into a layered filesystem.
+While both forms of virtualization provides an excellent mechanism for sandboxing the computations associated with a scientific result, neither form of virtualization provides any guarantee that the included pieces of software will indeed reproduce the associated scientific result.
+
+Since reproducibility is significantly about comprehensive documentation, virtualization approaches in its current form only make it easy to capture the computations, but not preserve the computation so that it is easy to understand, install, or alter the implicit dependencies that are part of computation, especially as dependencies and external software components evolve or become deprecated.
+Software delivery mechanisms, such as Linux Containers and Docker have recently emerged that address several of the reproducible challenges that arise due to use of virtualization approaches.
+
+In this paper, we examine how software delivery mechanisms can be combined with traditional virtualization approaches for reproducibility, especially light-weight virtualization approaches.
+To conduct a thorough examination, we consider a real-world complex high energy physics application, independently developed by a group, but must be reproduced  so that the entire high energy physics community can benefit from the analysis obtained from the application.
+We describe challenges in reproducing this application, and consider the extent to which reproducibility can be satisfied with light-weight virtualization approaches and software delivery mechanisms.
+We then propose an invariant framework for computational reproducibility that combines light-weight virtualization with software delivery mechanisms.
+The framework uses light-weight virtualization for capturing a computational environment, but preserves the environment using a software delivery approach, so it can be re-executed later.
+By using standardized delivery mechanisms and expanding the application for future uses, the framework makes it invariant to temporal software changes that may occur in near future.
+We measure the performance overhead of combining light-weight virtualization with software delivery approaches.
+The combination imposes additional overhead due to double virtualization, but saves on context switches, since every system call is not interposed.
+
+The rest of the paper is organized as follows. Section \ref{} describes the high energy physics application and the challenges involved in reproducing it. 
+Section \ref{} describes the light-weight virtualization and software delivery mechanisms, such as linux containers and dockers. 
+In Section \ref{} we describe the combined invariant framework, consisting of capture and preservation phases. 
+Section \ref{} describes how to employ capture, preserve, and distribute phases to reproduce the high-energy physics application.
+Section \ref{} provides the experimental results. Finally, we conclude in Section \ref{}.
+
+-----
+OLD TEXT
 

### 2015-01-06 evaluation.tex
Put each section into a separate tex file

--- 2014-12-18 paper.tex
@@
-\documentclass[procedia]{easychair}
-\usepackage{url}
-\usepackage[flushleft]{threeparttable}
-\hyphenation{resour-ces}
-\hyphenation{approac-hes}
-\hyphenation{har-der}
-\hyphenation{spe-cifically}
-\makeatletter
-\def\@copyrightspace{\relax}
-\makeatother
-
-\title{A Case Study in Preserving a High Energy Physics Application}
-
-% \titlerunning{} has to be set to either the main title or its shorter
-% version for the running heads. When processed by
-% EasyChair, this command is mandatory: a document without \titlerunning
-% will be rejected by EasyChair
-
-\titlerunning{A Case Study in Preserving a High Energy Physics Application}
-
-\author{
-	Haiyan Meng\inst{1}
-\and
-	Matthias Wolf\inst{2}
-\and
-	Douglas Thain\inst{3}
-}
-\institute{
-	Department of Computer Science and Engineering,
-	University of Notre Dame,
-	Notre Dame, Indiana, USA
-	\email{hmeng@nd.edu}
-\and
-	Department of Physics,
-	University of Notre Dame,
-	Notre Dame, Indiana, USA
-	\email{mwolf3@nd.edu}
-\and
-	Department of Computer Science and Engineering,
-	University of Notre Dame,
-	Notre Dame, Indiana, USA
-	\email{dthain@nd.edu}
-}
-
-%  \authorrunning{} has to be set for the shorter version of the authors' names;
-% otherwise a warning will be rendered in the running heads. When processed by
-% EasyChair, this command is mandatory: a document without \authorrunning
-% will be rejected by EasyChair
-
-\authorrunning{Meng, Wolf and Thain}
-
-\begin{document}
-
-\maketitle
-
-\keywords{}
-
-\begin{abstract}
-\it The reproducibility of scientific results increasingly
-depends upon the preservation of computational artifacts.
-Although preserving a computation to be used later sounds
-easy, it is surprisingly difficult due to the complexity
-of existing software and systems.  Implicit dependencies,
-networked resources, and shifting compatibility all conspire
-to break applications that appear to work well.  To investigate
-these issues, we present a case study of a complex high energy
-physics application.  We analyze the application and attempt
-several methods at extracting its dependencies for the purposes
-of preservation. 
-We propose one fine-grained dependency management toolkit to preserve the application and demonstrate its correctness in two different environments - one virtual machine from the Notre Dame Cloud Platform and one virtual machine from the Amazon EC2 Platform.
-We report on the completeness, performance,
-and efficiency of each technique, and offer some guidance for
-future work in application preservation.
-\end{abstract}
-
-% A category with the (minimum) three required fields
-%\category{H.4}{Information Systems Applications}{Miscellaneous}
-%A category including the fourth, optional field follows...
-%\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]
-
-%\terms{Theory}
-
-\section{Introduction}
-
-Reproducibility is a cornerstone of the scientific process~\cite{borgman2012data}.
-In order to understand, verify, and build upon previous work,
-one must be able to first recreate previous results by applying
-the same methods. Historically, reproducibility has been
-accomplished through painstaking detailed documentation recorded
-in lab notebooks, which are then summarized in peer-reviewed publications.
-But as science increasingly depends on computation,
-reproducibility must also encompass the environments, data, and software
-involved in each result~\cite{zabolitzky2002preserving}. It is widely recognized that informal
-descriptions of software and systems -- although common -- are insufficient
-for reproducing a computational result accurately.
-A more automated and comprehensive approach is required.
-
-The reproduction of a computation has three broad components,
-each of which suggests somewhat different approaches:
-
-\begin{itemize}
-\item The {\bf computing environment}, consisting of the basic hardware and the operating system which can be preserved as physical artifacts or as a combination of virtual machine monitors (hardware) and virtual machine images (operating system)~\cite{matthews2009towards}.
-\item The {\bf scientific data} to be analyzed has historically received the most attention for curation.
-In a large, well-organized project, it may be stored in a  data repository or database management system, with associated documentation and a curation strategy.
-In a small effort, it could simply be a handful of files.
-\item The {\bf software environment} includes the source code, binaries, scripts, configuration files, and everything else needed to execute the desired code.
-As with data, the software could be drawn from a well-managed software repository, or it could be a handful custom scripts that exist in the user's home directory.
-\end{itemize}
-
-In a very abstract sense, reproducing a computation is trivial.
-Assuming a computation is deterministic, one must simply
-preserve all of the inputs to a computation, then re-run
-the same code in an equivalent environment, and the same result
-will be produced.  For a small custom application on a modest
-amount of data, this could be accomplished by capturing the
-complete environment,
-data, and software within a single virtual machine image,
-and then depositing the virtual
-image into a curated environment.  The publication could
-then simply refer to the identifier of the image, which the
-interested reader can obtain and re-use. This approach has
-been used to some success with systems~\cite{castagne2013consider}.
-\footnote{Of course, we are glossing over the problem that hardware
-architectures and virtual machines also change, so one must also
-preserve the VMM software necessary to run the image.  The VMM itself
-depends on a software environment which must also be preserved.
-A long-term preservation system might end up running a whole
-stack of nested virtual machines in order to provide the desired
-environment! }
-
-However, this simple approach is not sufficient for large applications
-that are run in complex environments.
-
-\begin{itemize}
-\item There may be {\bf implicit dependencies} on items that are
-not apparent to the end user.  For example, they may understand that
-they rely on a particular data analysis package, but would have
-no reason to know that the package has further dependencies on
-other libraries and configuration files.  Or, they may know that
-the computation only runs correctly on a particular machine, but
-not know this is because it relies on a filesystem that
-is mounted only on that machine.
-
-\item The {\bf granularity} of the dependencies may not be well understood.
-For example, the user may understand that a computation depends upon
-a data collection that is 1TB in overall size, but not have detailed
-knowledge that it only requires three files totalling 300MB out of that
-whole collection.
-
-\item There may be dependencies upon {\bf networked resources} that
-are inherently external to the system, such as a database, a code
-repository~\cite{cms2006cmssw}, or a scalable filesystem~\cite{blomer2011cernvm}.  For such resources, it
-must be decided whether the dependency will simply be noted, or if it
-must be incorporated whole or in part.
-
-\item Where {\bf common dependencies} are widely used, it may be inefficient or
-impossible to store one copy of each dependency for each archived object.
-Some form of sharing or de-duplication is necessary in order to keep
-the archive to a reasonable size.
-\end{itemize}
-
-We do not claim to have solved these problems in any comprehensive
-way.  Rather, our aim in this paper is to highlight the scope
-of the problems by presenting a case study of one complex application.
-The application is presented to us
-first in the form of an email that describes in prose how to install
-the software and run the analysis.  We perform several successive
-refinements to convert it into an executable and preservable object.
-We then develop techniques for reducing the size of the dependencies
-that are necessary for the object to function, and we demonstrate
-the preserved object functioning correctly in three different
-physical and cloud environments.
-We describe how each of these techniques may interact with
-a future archive of preserved software artifacts, and conclude with
-some reflections on the challenges of preservation and advice for future efforts.
-
-\if 0
-Section 2: Overview of Application
-    CMS/LHC introduction.
-    Data sources and reduction of size.
-    Code sources and reduction of size.
-    Prose observations about the script.
-        Uses multiple repos that change over time, with varying level of stability.
-        Low selectivity from the larger repos
-        Significant initialization time to collect everything.
-        Incidental infrastructure tools versus essential objects.
-        Some dependencies were surprising.
-    Figure: Diagram of app with both code and data sources.
-    Table: Show all code and data sources and size within one table.
-
-Section 3: Preservation Strategies
-    Figure: Show app in four stages:
-        Single email.
-        Script with embedded references to dependencies.
-        Script with map file that refers to external dependencies.
-        Script with map file that refers to preserved dependencies.
-
-    Transform to more suitable format that expresses dependencies.
-
-    Incorporate into archive, saving deps and map file.
-
-    But, how to get the dependencies?
-
-    Three strategies:
-        Original - Unmodified application run in original environment.
-        Coarse-Grained - Capture deps at large granularity -- whole filesystems and repositories.
-        Fine-Grained - Capture deps at a fine granularity -- individual files actually used.
-
-    Coarse-Grained Method (Copy Repositories)
-        First, determine dependencies
-        Express app as script + map file
-        Packaging tool downloads deps, rewrites map file.
-        To run packaged application, obtain map, download
-
-    Fine-Trained Toolkit (Parrot)
-        Tool to detect dependencies (Parrot)
-        Express app as script + map file
-        Packaging tool downloads deps, rewrites map file.
-        To run package application, run again with Parrot.
-
-Section 4: Evaluation
-
-    Table: Time and size of preserving using each of the two techniques.
-
-    Explain why the techniques show different performance.
-
-    Is one technique more effective than the other?  Why?
-\fi
-
-\begin{figure}[t]
-\centering
-\includegraphics[width=.5\textwidth]{data-code-size.eps}
-\caption{Inputs to Tau Roast}
-\label{fig:data-code-size}
-\end{figure}
-
-\section{Overview of Tau Roast}
-
-Within the ongoing investigation of the Higgs boson at the CMS
-detector, part of the LHC at CERN~\cite{collaboration2008cms}, the Higgs production in association
-with two top quarks allows measuring the Higgs coupling strength to
-top quarks~\cite{chatrchyan2013search}.  As the Higgs boson is too short-lived to be detected
-itself, it has to be reconstructed from its decay products.
-
-The application which is the study of this paper is called \emph{TauRoast}.
-It searches for cases where the Higgs boson decays to two tau leptons.
-Since the tau leptons are very short-lived, they are not observed directly, but by the particle decay products 
-that they generate.  So, the analysis must search for detector
-events that show a signature of decay products compatible with both hadronic tau and top decays.  Properties of such events are used to distinguish
-the events of interest (Higgs decays) from all other events and
-are also used in further statistical analysis.
-
-Figure~\ref{fig:data-code-size} shows that both the code and data
-that form \emph{TauRoast} are drawn from large repositories through
-multiple steps of reduction.  A preservation strategy must weigh
-whether to store the large repositories completely, the fragments
-used by an artifact, or something in between.
-
-{\bf Code Sources.} Like many scientific codes, the central algorithm
-of \emph{TauRoast} is expressed in a relatively small amount of
-custom code developed by the primary author.  But, the code cannot
-run at all without making use of an enormous collection of software
-dependencies.  Some of these dependencies are standard to operating
-systems worldwide, some are standardized across the entire high-energy
-physics field, some are particular to small collaborative groups,
-and a few are very specific to a single researcher.
-
-The largest of these repositories is the CMS Software Distribution (CMSSW)~\cite{cms2006cms},
-a carefully-curated selection of software packages which is distributed
-in several forms.  Historically, components of CMSSW were obtained by checking components
-of the source out of CVS (CMSSW source codes were moved from CVS to git recently), or by installing a complete binary package on a shared
-filesystem within an HPC center.  In recent years, distribution has moved to
-an on-demand delivery system known as CVMFS~\cite{blomer2011cernvm}, which
-provides a filesystem interface that transparently accesses a remote repository.
-The content of CMSSW is managed very carefully by a centralized team whose main goal
-is to ensure that the current version of the software operates correctly
-on the operating systems and architectures currently in use.  However,
-preservation is not a specific objective of the system, and so there is
-no particular guarantee that old versions of CMSSW will continue to
-operate indefinitely.
-
-CMSSW contains many different tools, libraries, and utilities.
-No single code uses anywhere close to all of these.
-But, because it is widely used within the experimental researchers, it is common for users to simply expect that a particular version of the entire repository is available.
-
-{\bf Data Sources.}
-The CMS collaboration provides end-users with a pre-processed
-and reduced data format, AOD~\cite{holtman2001cms}, containing information for events, i.e.,
-proton-proton collisions with a signature of interest, in the form of
-reconstructed particles.  This format is based on the RAW output of
-the CMS detector readout electronics and reconstructed world-wide, which is then processed through various algorithms which derive signatures of individual particles.
-Both real and simulated data are available for examination.
-
-As AOD data are too large to be iteratively processed repetitively in
-a physics analysis workflow, it is normally reduced further in
-structural complexity and content.  For the analysis under
-investigation here, this is a two-step process.  First, the AOD data
-are processed at the Notre Dame working group cluster to BEAN (Boson Exploration Analysis Ntuple) events,
-containing only trivial data containers packed in vectors.  This step
-is time and CPU intensive and its output contains data of 11.6$\,$TB to be
-analyzed by the tau analysis.
-It is performed by a small custom code framework, which is built on top of CMSSW.
-The BEAN format, production code, and
-data are shared within the analysis group looking at Higgs production
-in association with top quarks, which is formed by groups from a few
-American and European universities,
-consisting of up to a few dozen contributors.
-
-In the second step, the data are reduced to the ``Ntuple'' format,
-which contains only events matching basic quality criteria and
-fields relevant to \emph{TauRoast}.
-Again, the Notre Dame CMS groups cluster
-resources are used to perform this reduction and selection,
-running highly customized software,
-built on CMSSW and the BEAN framework,
-with code written and maintained by a small group.
-
-Once the data has been reduced to Ntuples, TauRoast can be run as a single
-process, and contains a stringent event selection to look only at high
-quality candidate events for the underlying physical process.
-Quantities from the relevant events can be
-both plotted and used in multivariate analysis to determine the level
-of expected signal in real data.
-This package is written using the CMSSW build framework,
-but only utilizes code from ROOT,
-a particle physics toolkit underlying CMSSW,
-and a few external python dependencies for convenience.
-
-\section{Observations}
-
-\emph{TauRoast} was provided to us in the form of an
-email which described, in prose, how to obtain the source,
-build the program, and run it correctly on one specific
-machine at our home institution, with no particular guarantee that
-it will run anywhere else in the world.
-Although this starting point may seem extreme, it is
-perfectly natural for collaborators to share configurations
-with each other in this form, and to rely on the presence
-of a working environment with appropriate dependencies already
-installed.  From this starting point, the authors played the
-role of curators, whose job it is to prepare the application
-for permanent archival.
-
-First, we elaborated the email instructions into an
-executable script that obtains the dependencies and then
-executes the analysis.  The script declares the necessary
-environment variables, downloads and checks out the necessary source code,
-builds it appropriately, calls initialization scripts in
-the dependent software, and then runs the analysis.
-A few rounds of correction with the original author were necessary
-to obtain all the dependencies and run the artifact correctly.
-(The original instructions introduced in the email also indicated how to run the application
-within a production batch system.  For the purposes of preservation,
-we consider the execution infrastructure to be distinct from the application,
-and leave it out of consideration for now.)
-
-The process of elaborating the program into a script revealed
-several observations about this type of application:
-
-\begin{itemize}
-
-\item {\bf Many Explicit External Dependencies.}  TauRoast depends on a large number of
-external dependencies, each with a different access method and data source.
-While we knew in advance that it depended upon the large CMSSW distribution,
-it was not apparent until elaborating the script that it depended upon
-two different Github repositories for the Tau source,
-a CVS server at CERN for some configuration information, a public web page
-for the PyYAML library, and the public home page of a Notre Dame student
-for one missing header file.  (The latter is particularly troubling!)
-While, at some level, the authors and users of these software know of these dependencies, they are often missing in
-informal communications or forgotten once the dependency is installed.
-However, once known, they are at least expressed explicitly within the script.
-
-\item {\bf Many Implicit Local Dependencies.} A much harder problem is that the
-application assumed the presence of many different components in the local
-filesystem view. It would be tempting to capture all of these by simply
-storing a virtual machine image containing the local filesystem. However,
-the application depended on no less than {\bf five} networked filesystems
-available on a particular machine available to the author:
-the data to be analyzed was stored on an HDFS~\cite{borthakur2008hdfs} cluster,
-some configuration data was stored on a CVMFS~\cite{blomer2011cernvm} filesystem,
-and a variety of software tools were on an NFS~\cite{howard1988scale},
-PanFS~\cite{welch2008scalable} and AFS~\cite{sandberg1985design} systems.
-The original authors were not aware of many of these dependencies,
-because they simply relied on local administrators to configure the
-software and make it available.
-
-\item {\bf Configuration Complexity.}  As a means of controlling the complexity
-of dependent software packages, the high energy physics community has developed
-a number of tools that perform run-time configuration and consistency checks
-of the available software.  {\tt scram} is the software management tool used
-by the CMS experiment.  Before running any code, {\tt scram} is used to locate
-the appropriate version of software,  set environment variables such as the PATH, run any
-tool-specific configuration, and do the same for all software on which it depends.
-If the correct versions are not available, {\tt scram} halts and emits an error.
-While this procedure has great value for consistency, it also introduces a significant cost
-because it involves a large number of nested scripts traversing a filesystem,
-repeatedly looking up metadata.  In our example, the time to perform this configuration
-with a cold cache is about 14 minutes, which is almost as large as the actual analysis
-run, which takes 20 minutes.
-
-\begin{figure*}[t]
-\centering
-\includegraphics[width=.8\textwidth]{version-evolution.eps}
-\caption{Version Evolution}
-\label{fig:version-evolution}
-\end{figure*}
-
-\item {\bf High Selectivity.}  Although the total size of the resources accessed by this
-program is very large, the size of the data and software actually used are much smaller.
-Often, an entire repository or data source is named within the script, but the program
-only needs a handful of items from that source.  For example, the data is stored on an
-HDFS filesystem with 11.6TB of data, but only 20GB are actually consumed by the program. 
-The reason for this great reduction is at first each BEAN event contains a large amount of information, and the TauAnalysis throws away a lot of the irrelevant event information, keeping only the relevant bits.
-The CMSSW repository is 88.1GB in total
-but only 448.3MB of source is checked out, and the actually used software only
-measured 6.3MB.  In a few cases, a source of software is named but never actually accessed.
-(For example, our original script includes the Open Science Grid software stack in the PATH, but does not actually use it.)
-We suspect that end users are accustomed to missing dependencies and thus get in the habit of adding commonly used software,
-whether it is needed or not.
-
-\item {\bf Rapid Changes in Dependencies.}  Over the course of three months
-between collecting the initial email, analyzing the program, and writing this
-paper, the computing environment continuously changed.  The CMSSW software
-distribution released a new version, the target execution environment was upgraded
-to a new operating system, and the application deprecated the use of CVS for obtaining
-the software.  While the users of this software seem be accustomed to constant change,
-any preservation technique will have to be very cautious about relying upon an
-external service, even one that may appear to be highly stable.
-
-\end{itemize}
-
-\if 0
-
-\begin{table}
-    \centering
-    \begin{tabular}{|l|}
-        \hline
-        {\bf Version 1: Email}\\ \hline
-        1. Create a CMS release,\\
-            \hspace{9pt} e.g. {\tt cmsrel CMSSW\_5\_3\_11\_patch3} \\
-        2. Install the BEAN packages as the instructions: \\
-            \hspace{9pt} {\tt \url{https://github.com/cms-ttH/BEAN/blob/...}}\\
-        3. Install grid-control: \\ 
-            \hspace{9pt} {\tt svn co \url{https://ekptrac.physik.uni-ka/...}} \\
-        4. INstall the TauAnalysis package: \\
-           \hspace{9pt} {\tt git clone \url{https://github.com/matz-e/...}} \\
-           \hspace{9pt} {\tt scram b -j32} \\
-        5. Fix grid\_control.cfg and run it. \\
-        6. Perform the actual tau roast program. \\ 
-        \hline
-        {\bf Version 2: Script}\\ \hline
-        {\tt setenv CMSSW\_BASE CMSSW\_5\_3\_11\_patch3} \\
-        {\tt cmsrel \$HOME/\$CMSSW\_BASE} \\
-        {\tt cvs co -r V03-09-23 PhysicsTools/PatUtils} \\
-        {\tt git clone \url{https://github.com/cms-ttH/BEAN.git}} \\
-        {\tt wget -r \url{http://nd.edu/~abrinke1/...}} \\
-        {\tt scram b -j32} \\
-        {\tt wget \url{http://pyyaml.org/download/pyyaml/PyYAML...}}\\
-        \#the experiment data is from HDFS \\
-        {\tt cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10}\\
-        {\tt cmsenv}\\
-        {\tt python setup.py install --user} \\
-        {\tt scripts/roaster data/generic\_ttl.yaml} \\ 
-        \hline
-        {\bf version 3: Formulated Script} \\ \hline
-        {\tt setenv CMSSW\_BASE CMSSW\_5\_3\_11\_patch3} \\
-        {\tt setenv {\bf GIT} \url{https://github.com}} \\
-        {\tt setenv {\bf PYYAML} \url{http://pyyaml.org}} \\
-        {\tt setenv {\bf ND} \url{http://nd.edu}} \\
-        {\tt cmsrel \$HOME/\$CMSSW\_BASE} \\
-        {\tt cvs co -r V03-09-23 PhysicsTools/PatUtils} \\
-        {\tt git clone \${\bf GIT}/cms-ttH/BEAN.git} \\
-        {\tt wget -r \${\bf ND}\url{/~abrinke1/ElectronEffectiveArea.h}} \\
-        {\tt scram b -j32} \\
-        {\tt wget \${\bf PYYAML}/download/pyyaml/PyYAML...}\\
-        \#the experiment data is from HDFS \\
-        {\tt cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10}\\
-        {\tt cmsenv}\\
-        {\tt python setup.py install --user} \\
-        {\tt scripts/roaster data/generic\_ttl.yaml} \\ 
-        \hline
-       {\bf Version 4: Fine-Grained Toolkit - Package}\\ \hline
-        {\tt setenv CMSSW\_BASE CMSSW\_5\_3\_11\_patch3} \\
-        {\tt setenv {\bf GIT} \url{https://github.com}} \\
-        {\tt setenv {\bf PYYAML} \url{http://pyyaml.org}} \\
-        {\tt setenv {\bf ND} \url{http://nd.edu}} \\
-        {\tt cmsrel \$HOME/\$CMSSW\_BASE} \\
-        {\tt cvs co -r V03-09-23 PhysicsTools/PatUtils} \\
-        {\tt git clone \${\bf GIT}/cms-ttH/BEAN.git} \\
-        {\tt wget -r \${\bf ND}\url{/~abrinke1/ElectronEffectiveArea.h}} \\
-        {\tt scram b -j32} \\
-        {\tt wget \${\bf PYYAML}/download/pyyaml/PyYAML...}\\
-        \#the experiment data is from HDFS \\
-        {\tt cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10}\\
-        {\tt cmsenv}\\
-        {\tt python setup.py install --user} \\
-        {\tt scripts/roaster data/generic\_ttl.yaml} \\ 
-        \hline
-    \end{tabular}
-    \caption{Scripts of each Solution}
-    \label{table:scripts}
-\end{table}
-
-\fi
-
-\section{Evolving the Artifact}
-
-It is clear that the artifact, as provided, is not in a suitable form
-for preservation.  While it might be technically possible to automatically
-capture the entire virtual machine and all of the connected filesystems,
-it would require 166.8TB of storage, which would be prohibitively expensive
-for capturing this one application alone.  Further, if multiple
-similar applications are preserved, we would miss the opportunity to identify
-common dependencies and store them once for multiple artifacts.
-A more structured approach to dependency management is needed.
-
-Figure~\ref{fig:version-evolution} shows how we have evolved this artifact
-through several stages which make it more suitable for preservation.
-In each step of evolution, we make the dependencies of the artifact
-more explicit and available for analysis and automated processing.
-As noted in the previous section, the original author provided us with
-prose instructions by email which we translated into an
-executable script.  The executable script has embedded in it
-a number of external identifiers such as URLs pointing to repositories
-and paths to networked filesystems.  As a general programming practice,
-embedding such constants into the middle of a program is unwise, and so
-we extract all of those identifiers and place them \emph{outside} the
-script in a \emph{dependency map} or just \emph{map} for short.
-The dependency map lists all of the external dependencies of the application, indicating
-the type, how they are accessed, and where they are currently located.
-The resulting script then simply refers to abstract file locations such
-as \verb$GIT$ and \verb$CVMFS$, while the map file indicates where they
-are currently located. If properly constructed, the script should not refer to any external
-resource unless it is indicated in the dependency map.  We call this idealized
-artifact an \emph{abstract script}.
-
-By extracting the dependencies into the dependency map,
-we introduce great freedom for the curator to move, transform, and otherwise
-manipulate the dependencies of the artifact without damaging the artifact itself.
-A Figure~\ref{fig:version-evolution} shows, it is straightforward for an
-automated tool to examine
-all of the dependencies in the map, download those that are missing,
-and then modify the map to point to the local copies of the dependencies.
-If we group the script, dependency map, and dependencies into a \emph{package},
-we now have a self-contained artifact that can be moved from place to place.
-In some cases, it may be safe to allow the dependency map to refer to 
-trusted remote repositories.  Whether this is advisable is a judgment that
-must be made by the user or the curator, taking into account the long-term
-stability of said repositories.
-
-However, only having the package and the dependency map is not enough. The successful execution of the application on the original machine also relies on the configuration of environment variables.
-We collected the environment variables of the original machine and transformed it into one executable script.
-If another researcher wants to repeat the application, this executable script will be first executed.
-The environment variables refer to the dynamic named values defined in the range of one computer, like \verb!$PATH! and \verb!$PYTHONPATH!.
-However, the dependency map refers to the actual storage location of path variables used in one abstract script. For example, the actual storage location of the path variable \verb!CVMFS! 
-is {\tt /data/cvmfs/grid.cern.ch}.
-
-\begin{figure}
-\centering
-\includegraphics[width=.5\textwidth]{solution3.eps}
-\caption{Relationship of Roles}
-\label{fig:solution3}
-\end{figure}
-
-The relationship of different roles involved in the application preservation and
-reproduction is shown in Figure~\ref{fig:solution3}.  The original author uses the packaging utility to generate the package for one application.
-Then the package, together with
-its map file and description file will be published. When
-another researcher wants to repeat the application, one copy of the package will be downloaded into the new machine and the application can be repeated.
-
-When we try to repeat one application on one new machine, one map file is necessary for the relocation of the data access targets, as
-show in Figure~\ref{fig:version-evolution}. 
-The map file clearly defines the real location of each dependency in the format of dependency variables - the real location of dependency variable {\tt GIT} is \path{/data/git/cms-ttH} and the real location of dependency variable {\tt CVMFS}
-is {\tt /data/cvmfs/grid.cern.ch}.
-The script only refers to the dependency variables defined in the map file.
-This design decouples the application script and the actual data access targets, which minimizes the impact of the evolution of different data dependencies
-and ensures the transparent access.
-The modification of the package only introduces the minimal changes of the map file on the client side.
-
-This basic approach to dependency management is a step in the right direction
-for dependencies that are \emph{explicit} and \emph{external} to the
-user's native execution environment.  However, it leaves two other problems unsolved.
-
-First, the basic approach requires that someone be \emph{aware} of the dependencies,
-whether it be the end user, the system administrator, or the archive curator.
-It seems reasonable to expect the user to be aware of a large dependency mentioned in a top-level script.
-But, oftentimes the dependency is embedded invisibly deep within the software stack,
-or is connected to the machine by the local system administrators.  No single party
-is likely to have complete information about all of the dependencies.
-Second, the basic approach assumes that the entire dependency is actually
-consumed by the artifact.  As we have suggested above (and will show below),
-this sort of program often only consumes a small fraction of what it does declare
-as a dependency.
-
-To address both of these problems, users and curators alike need tools that
-will automatically observe the dependencies of complex applications, to
-facilitate automatic and efficient preservation.
-
-\section{Measuring Dependencies}
-
-\begin{figure*}
-\centering
-\includegraphics[width=.8\textwidth]{workflow-parrot.eps}
-\caption{Workflow of The Fine-Grained Dependency Management Toolkit Based on Parrot}
-\label{fig:workflow-parrot}
-\end{figure*}
-
-We have developed a prototype tool to assist in the measurement and preservation
-of implicit dependencies for complex applications.
-We use Parrot~\cite{thain2005parrot} to explicitly record all
-of the files accessed by our example application, allowing us to observe how
-much of each external dependencies is used, and what local resources are implicitly used.
-Using this information, we create a \emph{reduced package} which contains
-only the files actually used by the application.
-
-Parrot is a virtual filesystem access tool which has been used to attach
-existing programs to a variety of remote I/O systems, such as HTTP, FTP, and CVMFS.
-It works by trapping an application's system calls through the Linux {\tt ptrace} debugging
-interface, and then replacing them with the desired I/O operations.  Parrot is already used
-in the high energy physics community with applications like TauRoast specifically to 
-provide access to the CMSSW software distribution via the CVMFS distributed file system.
-We made small modifications to Parrot to record a \emph{namelist} which lists all 
-of the files that an application actually accesses.
-
-Figure~\ref{fig:workflow-parrot} illustrates the measurement process.
-The starting point of this toolkit is one successful execution of the application on the native machine.
-First, we execute the actual data analysis script under Parrot to generate the namelist.
-Then, using the namelist, we generate a package containing all the necessary data
-and software for one analysis program. When another
-researcher wants to repeat the program, he only needs to obtain the package and
-execute the actual analysis program inside the package.
-
-For one execution of \emph{TauRoast}, the generated namelist includes 132,047 accessed filenames,
-along with the system calls used to access the file, such as {\tt open}, {\tt stat}, {\tt read}, etc.
-With duplicate filenames removed, the list is reduced to 67,168 files.
-Many of those entries do not exist, because they reflect attempts
-by the application to search for programs and libraries in multiple places.
-Only 22,068 entries reflect existing files or directories.
-
-The packaging tool iterates over each item of the filename list, determines the process
-mode and replication degree according to the file type (common files,
-directories, symbolic links) and the system call type, generates one package
-containing the dependencies, and summarizes the contents of the package
-as shown in Table~\ref{table:package-info}.  To the extent possible,
-the filesystem structure of the original environment is preserved.
-
-We considered several approaches to constructing the package.
-In a {\bf shallow copy}, we only copied the individual files in the namelist,
-creating only parent directories for each.  Where a directory was listed,
-we created the directory and populated it with empty files as placeholders
-to facilitate a directory listing.  In a {\bf medium copy}, we copied the
-individual files as before.  Where a directory was listed, we created
-the directories and copied the contents of the files in that directory,
-one level deep.  A {\bf deep copy} would duplicate all directories recursively,
-but this would have resulted in TB-sized packages, so we did not consider
-it further.
-
-Parrot is required to re-run the packaged artifact, in order to force
-the packaged files to appear to exist in their original locations.
-To this end, the packaging tool creates a \emph{file map} which maps
-the logical names of the files to their current physical locations, as shown in Table~\ref{table:map-file}.
-Parrot reads the file map and redirects system calls at run-time to achieve the desired effect.
-As the example suggests, special device files such as {\tt /proc} and {\tt /dev}
-are not incorporated into the package but are instead accessed natively.
-
-\begin{table}
-    \centering
-    \begin{tabular}{ll}
-    \hline
-    \bf Path used in Program & \bf Actual Location \\ \hline
-    {\tt /} & {\tt /tmp/package-hep} \\ \hline
-    {\tt /tmp/package-hep} & {\tt /tmp/package-hep} \\ \hline
-    {\tt /dev} & {\tt /dev} \\ \hline
-    {\tt ...} & {\tt ...}\\ \hline
-    \end{tabular}
-    \caption{Structure of Map File}
-    \label{table:map-file}
-\end{table}
-
-\begin{table}
-    \centering
-    \begin{tabular}{rrr}
-\hline
-                    & \bf Shallow Copy & \bf Medium Copy\\
-\hline
-    Whole Files    & 1632         & 15642\\ 
-\hline
-    Empty Files    & 14273        & 263\\
-\hline
-    Directories    & 1549         & 1549\\ 
-\hline
-    Symbolic Links & 4614         & 4614 \\
-\hline
-    \bf Total Size & \bf 21GB     & \bf 28GB \\ 
-\hline
-    \end{tabular}
-    \caption{Package Information}
-    \label{table:package-info}
-\end{table}
-
-\subsection{Tracking of Network Dependencies}
-
-\begin{figure}
-\centering
-\includegraphics[width=.6\textwidth]{git-syscall.eps}
-\caption{Exec Syscalls of a git command}
-\label{fig:git-syscall}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=.6\textwidth]{http_packet.eps}
-\caption{HTTP Request and Response}
-\label{fig:http_packet}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=.6\textwidth]{url_redirection.eps}
-\caption{An Example of URL Redirection}
-\label{fig:url_redirection}
-\end{figure}
-
-All the dependencies of one program can be divided into three categories: local file system (e.g., /usr, /lib and /lib64), remote file systems which can be mounted as local directories (e.g., /cvmfs and /hdfs), and other remote network dependencies (e.g.
-http, https and ssh).
-Through utilizing ptrace to trap each file-relevant system call used by a program, the first two categories of dependencies can be collected. 
-Motivation of tracking network dependencies: Linkrot is a common and great threat to the preservation of scientific applications.
-A URL which works normally today may be unavailable permanently.
-A method which can help the scientists figure out all the network dependencies of their applications provides the chance to evaluate the stability of each network dependencies and preserve the unstable network resources before linkrot happens.
-One direct solution to track the third category of dependencies is to utilize ptrace to check each exec system call used by a program and record each network-relevant executable and its parameters.
-However, an executable may create one or more child processes to finish some tasks, and a child process may create their own children processes.
-Figure~\ref{fig:git-syscall} shows all the processes created by a git command.
-A process with PID 998 is created to clone a remote git repository into local machine, which totally has 6 child processes.
-Moreover, a network-relevant executable name collection is necessary to identify network dependencies.
-The diversity of network-relevant executables and the large process tree generated for a network executable make this solution infeasible.
-
-Another solution to track network dependencies is to track the network sockets.
-The user process communicates with the network protocol stacks in the kernel through the network socket layer user interface on Linux.
-From the process tree shown in the above figure, the process with PID 1000 responds to create a socket, connect to a DNS server, send a DNS request packet to the DNS server and receive a DNS response packet from the DNS server.
-The information gained from the network socket tracking can be divided into three categories.
-\begin{itemize}
-\item The information of network sockets used to communicate with remote network dependences (through socket and connect system calls) can be used to figure out the port number, service name (such as, http, https, and ssh), socket type (stream and datagram),  and the domain type (inet and inet6).
-\item The contents of DNS packets can be used to figure out the hostname and IP address of each remote network dependency. 
-\item As for applications based on http protocol, all the http requests and responses can be seen, as shown in Figure~\ref{fig:http_packet}.
-However, as for applications based on https and ssh which encrypt network data using TLS/SSL, tracking network data on the socket level can only see the encrypted data.
-\end{itemize}
-
-The results of tracking network sockets used by a program involves two categories of network resource redirections, dns-level hostname redirection and website-level url redirection. 
-\begin{itemize}
-\item dns-level hostname redirection: Each DNS packet includes five parts, header, question, answer, authority, and additional.
-A DNS response packet with the type CNAME has multiple answers.
-For example, the DNS response packet which tries to resolve {\tt www3.nd.edu} includes two answers.
-The first answer provides an alias of {\tt www3.nd.edu}, {\tt www-vip.cc.nd.edu}, and the second answer maps the alias to the IP address.
-{\tt www3.nd.edu} CNAME {\tt www-vip.cc.nd.edu}
-{\tt www-vip.cc.nd.edu} A {\tt 129.74.12.151}
-The CNAME-type DNS packets leave us a question, among the hostname used by the user, the alias(es), the IP address, what should we preserve?
-\item website-level url redirection: Website-level url redirection happens when a website updates its location and still want their old users access their resources using the old url.
-Figure~\ref{fig:url_redirection} illustrates the url redirection between {\tt \url{www3.nd.edu/~ccl}} and {\tt ccl.cse.nd.edu}.
-Except for the difference of hostnames, the application layer protocols used by the old-version website and the new-version website is also different: the old website provides services through the https protocol, while the new website provides services through the http protocol.
-\end{itemize}
-
-The usage of https protocol makes detecting of website-level url redirections through tracking system calls more difficulty and even impossible.
-All the application data will be encrypted at presentation layer through the TLS/SSL protocol, which is initialized at the session layer and works at the presentation layer.
-
 \section{Evaluation}
@@
 %*****hmeng-doubt: this point is not the motivation. but one achievement comes together. out of imagination.
-
-\begin{figure}
-\centering
-\includegraphics[width=.6\textwidth]{preservation-integration.eps}
-\caption{Preserving Multiple Artifacts}
-\label{fig:Preservation integration}
-\end{figure}
-
-\section{Open Problems}
-
-Figure~\ref{fig:Preservation integration} shows the rough information
-architecture of the archive that we imagine for complex
-scientific software like TauRoast.
-Each artifact to be preserved is a package that consists of a top-level
-script to invoke the software, a dependency map, and the dependencies
-themselves, which may be external to the original program.  The artifacts
-are then ingested into the archive, where shared dependencies are stored
-only once.  In cases where an artifact has a dependency on a trusted
-(or very large) remote archive, the dependency may simply be tracked
-. A researcher that wishes to reproduce a given
-result need only refer to the unique identifier of the artifact, and will
-be able to automatically extract all of the dependent components of
-that artifact.
-
-For example, in Figure~\ref{fig:Preservation integration} Script 1 depends on items A, B, and C.
-Items A and B are ingested into the archive, where B is shared with Script 2.
-Item C is stored in another trustworthy repository and is tracked rather than ingested.
-When Script 1 is exported from the repository, items A and B are exported along with it, while C can be copied or remain remote, according to the end user's choice.
-
-As simple as that picture appears, there are a number of problems that must be solved to get there:
-
-{\bf Measure the Mess or Force Cleanliness?}  Two radically different approaches to dependency tracking are possible.
-The first is to allow end users complete freedom to construct their environment as desired, then \emph{measure} what items were actually used.
-As we have shown, this is possible, but has significant overheads and does not fully preserve the structure or intent of the end user.
-The second approach is to \emph{force} users to work in a clean environment in which no resource can be used until a proper dependency has been declared.
-This ensures that all dependencies are known in advance (and made explicit to the end user) but places a variety of restrictions on the user's daily work, and may prevent creative approaches that do not fit within the curator's view of how programs should be structured.
-Whether end users will accept the inconvenience of forced cleanliness for the benefits of reproducibility can only be discovered through experiment.
-
-{\bf Granularity of Dependencies.}  Dependencies could be handled
-at many different levels of granularity.  In this work, we have shown
-how they can be handled at the level of entire repositories or individual files.
-Other possible choices might include intermediate-sized software packages
-(like RPM) or in the case of experimental data, even portions of individual large files.  Clearly, a larger granularity will result in 
-simpler dependency maps, and more wasted space; smaller granularity results
-in complex dependency maps and less wasted space.  A hybrid solution may
-be able to combine both by storing large granularity dependencies, but
-selecting sub-items out of objects when efficiency demands it.
-
-{\bf Scope of Reuse.}  We have presented the data preservation
-problem as primarily one of accurate reproduction: if a result depends
-on running program X, we must be able to run exactly X again.  However,
-the goal of scientific reproducibility is rarely limited to running
-\emph{precisely} what a predecessor did. Often, the objective is to
-change a parameter or a data input in order to see how the result is affected.
-To that end, the preservation system must capture enough of the surrounding
-material to permit modifications to succeed.  From this perspective,
-a larger granularity of preservation is desirable.  A better understanding of
-how end users will consume preserved software will help to shape how
-software is preserved in the first place.
-
-{\bf Dependency Detection.}  If we allow users to work in uncontrolled
-environments, then we must have better methods for understanding the dependencies  of existing programs.  At first, we relied on an expert reader to examine
-the user's script and extract the dependencies.  This is clearly
-not a scalable approach.  We then demonstrated an automated method of observing
-what individual files are accessed by a program. However, this does
-not cover all types of dependencies, particularly those that are networked.
-More sophisticated observation techniques could infer higher-level information,
-such as the RPM package names of the files accessed, the URLs of remote
-repositories named throughout the program, or even the addresses and names of networked dependencies like databases and filesystems.
-
-{\bf Source, Binary, or Both?}  A science archive might choose to retain
-the source code of an artifact or the binary code that can actually run in a given environment.
-While conventional wisdom suggests that access to source code is critical for the long term
-survival and evolution of a piece of software, it also requires the maintenance of an enormous
-amount of supporting software in the form of compilers, linkers, and supporting libraries for
-the target platform.  Rebuilding all of these for every invocation of an artifact is
-likely to have excessive cost.  We suggest that a realistic repository will have to
-maintain \emph{both}: the source describes the ultimate meaning of the code, but
-the binary is an important performance cache, a backup if the compiler toolchain should
-fail to be preserved, and a checksum to ensure that a source artifact was rebuilt correctly.
-
-\section{Related Work }
-
-Generally, there are three approaches to preserve software environment:
-hardware preservation, migration and emulation.  Hardware
-preservation preserves the original software and its original operating
-environment. 
-Software migration technique~\cite{cifuentes1996binary,mancl2001refactoring} was used to facilitate running software on new machines.
-However, migration often involves the re-compiling and re-configuring
-the source code to accommodate a new hardware platform and software environment.
-Emulation recreates the original software and hardware environment by
-programming future platforms and OSs. One common solution to implement this is
-virtual machine. According to the usage and emulation degree of the real
-machine, virtual machine can be divided into system virtual machine and process
-virtual machine. 
-The working principle, design principle and
-performance evaluation of system virtual machine were illustrated in~\cite{goldberg1974survey, smith2005architecture}. 
-The
-functionality of system VM to support different guest operating systems was illustrated in~\cite{barham2003xen,kivity2007kvm,rosenblum1999vmware}.
-F. Esquembre~\cite{esquembre2004easy} illustrated how JVM, one process virtual machine, can expedite the creation of
-scientific simulations in Java. 
-The pros and cons of these three approaches were discussed in~\cite{matthews2009towards,phelps2005no,hong2010software}.
-
-The preservation of computing environment and software environment was treated as one entirety in~\cite{matthews2009towards,phelps2005no,hong2010software}.
-However, frequently changing experiment software makes the maintenance of the preserved experimental environment very complex.
-CernVM~\cite{buncic2010cernvm} treated them as two different categories.
-The preservation of computing environment is implemented with CernVM, and the preservation of software environment is based on a CernVM filesystem(CVMFS) specifically designed for efficient software distribution.
-
-The importance of preserving software in source code format was emphasized in~\cite{zabolitzky2002preserving,castagne2013consider}. 
-However, CVMFS~\cite{buncic2010cernvm} published pre-built and configured experiment software releases to avoid the time-consuming software building procedure.
-
-Attempts from different perspectives to facilitate the reproduction of scientific experiments utilizing a preserved software library have been made. 
-The software distribution mechanism over network was discussed in~\cite{compostella2010cdf, blomer2011cernvm}.
-J.
-R.
-Rice et al.~\cite{rice1996scientific} made the reproduction process easier through the integration of user interface, scientific software libraries, knowledge base into problem-solving environment.
-S. R. Kohn et al.~\cite{kohn2001divorcing} tried to enable the creation and distribution of language-independent software library by addressing language interoperability.
-a scalable, distributed and dynamic workflow system for digitization processes was proposed in~\cite{schoneberg2013scalable}.
-A distributed archival network was designed in~\cite{subotic2013distributed} to facilitate process-oriented automatic long-term digital preservation.
-M. Agosti et al.~\cite{agosti2012envisage} aimed to help non-domain users to utilize the digital archive system developed for domain experts.
-
-Current mechanisms of preserving scientific experiments assume that all the data and software mentioned in the experiments are necessary for the reproduction of the experiments.
-However, this is not always right.
-In some cases, the original author may leave additional code referring to irrelative data and software in the program.
-One mechanism, which can figure out the absolutely relevant data and software of one experiment, is important for both the preservation and reproduction of scientific experiments.
-
-B. Matthews et al.~\cite{matthews2008significant} introduced one conceptual framework for software preservation from several case studies of software preservation.
-One tool to capture software preservation properties within a software environment was designed in~\cite{matthews2010framework} through a series of case studies conducted to evaluate the software preservation framework.
-L. R. Johnston et al.~\cite{johnston2014workflow} proposed one overall data curation workflow for 3-5 case studies of preserving research data.
-Two case studies~\cite{borgman2012data} were conducted to figure out the properties of data to be reused in the future.
-
-\section{Postscript}
-
-We began this work in late 2013, generating a reduced package for \emph{TauRoast} based
-on the configuration of a standard machine at Notre Dame at the time.  In the course
-of writing this paper in spring 2014, almost everything about the computing environment
-changed: the operating system was upgraded, a new version of CMSSW was released, and
-our local HEP users switched from using CVS to CVMFS for accessing CMSSW.
-The original script provided by the author failed to run on the same machine.
-But, the reduced package we created three months earlier in the old environment
-worked just fine on the new machine.
-
-\section*{Acknowledgments}
-
-This work was supported in part by National Science Foundation grants PHY-1247316 (DASPOS), 
-OCI-1148330 (SI2) and PHY-1312842.
-The University of Notre Dame Center for Research Computing scientists and engineers provided critical technical assistance throughout this research effort.
-
-Copyright (C) 2014 The University of Notre Dame
-
-This work is licensed under the Creative Commons Attribution 4.0 License.
-
-\bibliographystyle{plain}
-\bibliography{cclpapers,this}
-
-\end{document}

### 2015-01-06 evolution.tex
Put each section into a separate tex file

--- 2014-12-18 paper.tex
@@
-\documentclass[procedia]{easychair}
-\usepackage{url}
-\usepackage[flushleft]{threeparttable}
-\hyphenation{resour-ces}
-\hyphenation{approac-hes}
-\hyphenation{har-der}
-\hyphenation{spe-cifically}
-\makeatletter
-\def\@copyrightspace{\relax}
-\makeatother
-
-\title{A Case Study in Preserving a High Energy Physics Application}
-
-% \titlerunning{} has to be set to either the main title or its shorter
-% version for the running heads. When processed by
-% EasyChair, this command is mandatory: a document without \titlerunning
-% will be rejected by EasyChair
-
-\titlerunning{A Case Study in Preserving a High Energy Physics Application}
-
-\author{
-	Haiyan Meng\inst{1}
-\and
-	Matthias Wolf\inst{2}
-\and
-	Douglas Thain\inst{3}
-}
-\institute{
-	Department of Computer Science and Engineering,
-	University of Notre Dame,
-	Notre Dame, Indiana, USA
-	\email{hmeng@nd.edu}
-\and
-	Department of Physics,
-	University of Notre Dame,
-	Notre Dame, Indiana, USA
-	\email{mwolf3@nd.edu}
-\and
-	Department of Computer Science and Engineering,
-	University of Notre Dame,
-	Notre Dame, Indiana, USA
-	\email{dthain@nd.edu}
-}
-
-%  \authorrunning{} has to be set for the shorter version of the authors' names;
-% otherwise a warning will be rendered in the running heads. When processed by
-% EasyChair, this command is mandatory: a document without \authorrunning
-% will be rejected by EasyChair
-
-\authorrunning{Meng, Wolf and Thain}
-
-\begin{document}
-
-\maketitle
-
-\keywords{}
-
-\begin{abstract}
-\it The reproducibility of scientific results increasingly
-depends upon the preservation of computational artifacts.
-Although preserving a computation to be used later sounds
-easy, it is surprisingly difficult due to the complexity
-of existing software and systems.  Implicit dependencies,
-networked resources, and shifting compatibility all conspire
-to break applications that appear to work well.  To investigate
-these issues, we present a case study of a complex high energy
-physics application.  We analyze the application and attempt
-several methods at extracting its dependencies for the purposes
-of preservation. 
-We propose one fine-grained dependency management toolkit to preserve the application and demonstrate its correctness in two different environments - one virtual machine from the Notre Dame Cloud Platform and one virtual machine from the Amazon EC2 Platform.
-We report on the completeness, performance,
-and efficiency of each technique, and offer some guidance for
-future work in application preservation.
-\end{abstract}
-
-% A category with the (minimum) three required fields
-%\category{H.4}{Information Systems Applications}{Miscellaneous}
-%A category including the fourth, optional field follows...
-%\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]
-
-%\terms{Theory}
-
-\section{Introduction}
-
-Reproducibility is a cornerstone of the scientific process~\cite{borgman2012data}.
-In order to understand, verify, and build upon previous work,
-one must be able to first recreate previous results by applying
-the same methods. Historically, reproducibility has been
-accomplished through painstaking detailed documentation recorded
-in lab notebooks, which are then summarized in peer-reviewed publications.
-But as science increasingly depends on computation,
-reproducibility must also encompass the environments, data, and software
-involved in each result~\cite{zabolitzky2002preserving}. It is widely recognized that informal
-descriptions of software and systems -- although common -- are insufficient
-for reproducing a computational result accurately.
-A more automated and comprehensive approach is required.
-
-The reproduction of a computation has three broad components,
-each of which suggests somewhat different approaches:
-
-\begin{itemize}
-\item The {\bf computing environment}, consisting of the basic hardware and the operating system which can be preserved as physical artifacts or as a combination of virtual machine monitors (hardware) and virtual machine images (operating system)~\cite{matthews2009towards}.
-\item The {\bf scientific data} to be analyzed has historically received the most attention for curation.
-In a large, well-organized project, it may be stored in a  data repository or database management system, with associated documentation and a curation strategy.
-In a small effort, it could simply be a handful of files.
-\item The {\bf software environment} includes the source code, binaries, scripts, configuration files, and everything else needed to execute the desired code.
-As with data, the software could be drawn from a well-managed software repository, or it could be a handful custom scripts that exist in the user's home directory.
-\end{itemize}
-
-In a very abstract sense, reproducing a computation is trivial.
-Assuming a computation is deterministic, one must simply
-preserve all of the inputs to a computation, then re-run
-the same code in an equivalent environment, and the same result
-will be produced.  For a small custom application on a modest
-amount of data, this could be accomplished by capturing the
-complete environment,
-data, and software within a single virtual machine image,
-and then depositing the virtual
-image into a curated environment.  The publication could
-then simply refer to the identifier of the image, which the
-interested reader can obtain and re-use. This approach has
-been used to some success with systems~\cite{castagne2013consider}.
-\footnote{Of course, we are glossing over the problem that hardware
-architectures and virtual machines also change, so one must also
-preserve the VMM software necessary to run the image.  The VMM itself
-depends on a software environment which must also be preserved.
-A long-term preservation system might end up running a whole
-stack of nested virtual machines in order to provide the desired
-environment! }
-
-However, this simple approach is not sufficient for large applications
-that are run in complex environments.
-
-\begin{itemize}
-\item There may be {\bf implicit dependencies} on items that are
-not apparent to the end user.  For example, they may understand that
-they rely on a particular data analysis package, but would have
-no reason to know that the package has further dependencies on
-other libraries and configuration files.  Or, they may know that
-the computation only runs correctly on a particular machine, but
-not know this is because it relies on a filesystem that
-is mounted only on that machine.
-
-\item The {\bf granularity} of the dependencies may not be well understood.
-For example, the user may understand that a computation depends upon
-a data collection that is 1TB in overall size, but not have detailed
-knowledge that it only requires three files totalling 300MB out of that
-whole collection.
-
-\item There may be dependencies upon {\bf networked resources} that
-are inherently external to the system, such as a database, a code
-repository~\cite{cms2006cmssw}, or a scalable filesystem~\cite{blomer2011cernvm}.  For such resources, it
-must be decided whether the dependency will simply be noted, or if it
-must be incorporated whole or in part.
-
-\item Where {\bf common dependencies} are widely used, it may be inefficient or
-impossible to store one copy of each dependency for each archived object.
-Some form of sharing or de-duplication is necessary in order to keep
-the archive to a reasonable size.
-\end{itemize}
-
-We do not claim to have solved these problems in any comprehensive
-way.  Rather, our aim in this paper is to highlight the scope
-of the problems by presenting a case study of one complex application.
-The application is presented to us
-first in the form of an email that describes in prose how to install
-the software and run the analysis.  We perform several successive
-refinements to convert it into an executable and preservable object.
-We then develop techniques for reducing the size of the dependencies
-that are necessary for the object to function, and we demonstrate
-the preserved object functioning correctly in three different
-physical and cloud environments.
-We describe how each of these techniques may interact with
-a future archive of preserved software artifacts, and conclude with
-some reflections on the challenges of preservation and advice for future efforts.
-
-\if 0
-Section 2: Overview of Application
-    CMS/LHC introduction.
-    Data sources and reduction of size.
-    Code sources and reduction of size.
-    Prose observations about the script.
-        Uses multiple repos that change over time, with varying level of stability.
-        Low selectivity from the larger repos
-        Significant initialization time to collect everything.
-        Incidental infrastructure tools versus essential objects.
-        Some dependencies were surprising.
-    Figure: Diagram of app with both code and data sources.
-    Table: Show all code and data sources and size within one table.
-
-Section 3: Preservation Strategies
-    Figure: Show app in four stages:
-        Single email.
-        Script with embedded references to dependencies.
-        Script with map file that refers to external dependencies.
-        Script with map file that refers to preserved dependencies.
-
-    Transform to more suitable format that expresses dependencies.
-
-    Incorporate into archive, saving deps and map file.
-
-    But, how to get the dependencies?
-
-    Three strategies:
-        Original - Unmodified application run in original environment.
-        Coarse-Grained - Capture deps at large granularity -- whole filesystems and repositories.
-        Fine-Grained - Capture deps at a fine granularity -- individual files actually used.
-
-    Coarse-Grained Method (Copy Repositories)
-        First, determine dependencies
-        Express app as script + map file
-        Packaging tool downloads deps, rewrites map file.
-        To run packaged application, obtain map, download
-
-    Fine-Trained Toolkit (Parrot)
-        Tool to detect dependencies (Parrot)
-        Express app as script + map file
-        Packaging tool downloads deps, rewrites map file.
-        To run package application, run again with Parrot.
-
-Section 4: Evaluation
-
-    Table: Time and size of preserving using each of the two techniques.
-
-    Explain why the techniques show different performance.
-
-    Is one technique more effective than the other?  Why?
-\fi
-
-\begin{figure}[t]
-\centering
-\includegraphics[width=.5\textwidth]{data-code-size.eps}
-\caption{Inputs to Tau Roast}
-\label{fig:data-code-size}
-\end{figure}
-
-\section{Overview of Tau Roast}
-
-Within the ongoing investigation of the Higgs boson at the CMS
-detector, part of the LHC at CERN~\cite{collaboration2008cms}, the Higgs production in association
-with two top quarks allows measuring the Higgs coupling strength to
-top quarks~\cite{chatrchyan2013search}.  As the Higgs boson is too short-lived to be detected
-itself, it has to be reconstructed from its decay products.
-
-The application which is the study of this paper is called \emph{TauRoast}.
-It searches for cases where the Higgs boson decays to two tau leptons.
-Since the tau leptons are very short-lived, they are not observed directly, but by the particle decay products 
-that they generate.  So, the analysis must search for detector
-events that show a signature of decay products compatible with both hadronic tau and top decays.  Properties of such events are used to distinguish
-the events of interest (Higgs decays) from all other events and
-are also used in further statistical analysis.
-
-Figure~\ref{fig:data-code-size} shows that both the code and data
-that form \emph{TauRoast} are drawn from large repositories through
-multiple steps of reduction.  A preservation strategy must weigh
-whether to store the large repositories completely, the fragments
-used by an artifact, or something in between.
-
-{\bf Code Sources.} Like many scientific codes, the central algorithm
-of \emph{TauRoast} is expressed in a relatively small amount of
-custom code developed by the primary author.  But, the code cannot
-run at all without making use of an enormous collection of software
-dependencies.  Some of these dependencies are standard to operating
-systems worldwide, some are standardized across the entire high-energy
-physics field, some are particular to small collaborative groups,
-and a few are very specific to a single researcher.
-
-The largest of these repositories is the CMS Software Distribution (CMSSW)~\cite{cms2006cms},
-a carefully-curated selection of software packages which is distributed
-in several forms.  Historically, components of CMSSW were obtained by checking components
-of the source out of CVS (CMSSW source codes were moved from CVS to git recently), or by installing a complete binary package on a shared
-filesystem within an HPC center.  In recent years, distribution has moved to
-an on-demand delivery system known as CVMFS~\cite{blomer2011cernvm}, which
-provides a filesystem interface that transparently accesses a remote repository.
-The content of CMSSW is managed very carefully by a centralized team whose main goal
-is to ensure that the current version of the software operates correctly
-on the operating systems and architectures currently in use.  However,
-preservation is not a specific objective of the system, and so there is
-no particular guarantee that old versions of CMSSW will continue to
-operate indefinitely.
-
-CMSSW contains many different tools, libraries, and utilities.
-No single code uses anywhere close to all of these.
-But, because it is widely used within the experimental researchers, it is common for users to simply expect that a particular version of the entire repository is available.
-
-{\bf Data Sources.}
-The CMS collaboration provides end-users with a pre-processed
-and reduced data format, AOD~\cite{holtman2001cms}, containing information for events, i.e.,
-proton-proton collisions with a signature of interest, in the form of
-reconstructed particles.  This format is based on the RAW output of
-the CMS detector readout electronics and reconstructed world-wide, which is then processed through various algorithms which derive signatures of individual particles.
-Both real and simulated data are available for examination.
-
-As AOD data are too large to be iteratively processed repetitively in
-a physics analysis workflow, it is normally reduced further in
-structural complexity and content.  For the analysis under
-investigation here, this is a two-step process.  First, the AOD data
-are processed at the Notre Dame working group cluster to BEAN (Boson Exploration Analysis Ntuple) events,
-containing only trivial data containers packed in vectors.  This step
-is time and CPU intensive and its output contains data of 11.6$\,$TB to be
-analyzed by the tau analysis.
-It is performed by a small custom code framework, which is built on top of CMSSW.
-The BEAN format, production code, and
-data are shared within the analysis group looking at Higgs production
-in association with top quarks, which is formed by groups from a few
-American and European universities,
-consisting of up to a few dozen contributors.
-
-In the second step, the data are reduced to the ``Ntuple'' format,
-which contains only events matching basic quality criteria and
-fields relevant to \emph{TauRoast}.
-Again, the Notre Dame CMS groups cluster
-resources are used to perform this reduction and selection,
-running highly customized software,
-built on CMSSW and the BEAN framework,
-with code written and maintained by a small group.
-
-Once the data has been reduced to Ntuples, TauRoast can be run as a single
-process, and contains a stringent event selection to look only at high
-quality candidate events for the underlying physical process.
-Quantities from the relevant events can be
-both plotted and used in multivariate analysis to determine the level
-of expected signal in real data.
-This package is written using the CMSSW build framework,
-but only utilizes code from ROOT,
-a particle physics toolkit underlying CMSSW,
-and a few external python dependencies for convenience.
-
-\section{Observations}
-
-\emph{TauRoast} was provided to us in the form of an
-email which described, in prose, how to obtain the source,
-build the program, and run it correctly on one specific
-machine at our home institution, with no particular guarantee that
-it will run anywhere else in the world.
-Although this starting point may seem extreme, it is
-perfectly natural for collaborators to share configurations
-with each other in this form, and to rely on the presence
-of a working environment with appropriate dependencies already
-installed.  From this starting point, the authors played the
-role of curators, whose job it is to prepare the application
-for permanent archival.
-
-First, we elaborated the email instructions into an
-executable script that obtains the dependencies and then
-executes the analysis.  The script declares the necessary
-environment variables, downloads and checks out the necessary source code,
-builds it appropriately, calls initialization scripts in
-the dependent software, and then runs the analysis.
-A few rounds of correction with the original author were necessary
-to obtain all the dependencies and run the artifact correctly.
-(The original instructions introduced in the email also indicated how to run the application
-within a production batch system.  For the purposes of preservation,
-we consider the execution infrastructure to be distinct from the application,
-and leave it out of consideration for now.)
-
-The process of elaborating the program into a script revealed
-several observations about this type of application:
-
-\begin{itemize}
-
-\item {\bf Many Explicit External Dependencies.}  TauRoast depends on a large number of
-external dependencies, each with a different access method and data source.
-While we knew in advance that it depended upon the large CMSSW distribution,
-it was not apparent until elaborating the script that it depended upon
-two different Github repositories for the Tau source,
-a CVS server at CERN for some configuration information, a public web page
-for the PyYAML library, and the public home page of a Notre Dame student
-for one missing header file.  (The latter is particularly troubling!)
-While, at some level, the authors and users of these software know of these dependencies, they are often missing in
-informal communications or forgotten once the dependency is installed.
-However, once known, they are at least expressed explicitly within the script.
-
-\item {\bf Many Implicit Local Dependencies.} A much harder problem is that the
-application assumed the presence of many different components in the local
-filesystem view. It would be tempting to capture all of these by simply
-storing a virtual machine image containing the local filesystem. However,
-the application depended on no less than {\bf five} networked filesystems
-available on a particular machine available to the author:
-the data to be analyzed was stored on an HDFS~\cite{borthakur2008hdfs} cluster,
-some configuration data was stored on a CVMFS~\cite{blomer2011cernvm} filesystem,
-and a variety of software tools were on an NFS~\cite{howard1988scale},
-PanFS~\cite{welch2008scalable} and AFS~\cite{sandberg1985design} systems.
-The original authors were not aware of many of these dependencies,
-because they simply relied on local administrators to configure the
-software and make it available.
-
-\item {\bf Configuration Complexity.}  As a means of controlling the complexity
-of dependent software packages, the high energy physics community has developed
-a number of tools that perform run-time configuration and consistency checks
-of the available software.  {\tt scram} is the software management tool used
-by the CMS experiment.  Before running any code, {\tt scram} is used to locate
-the appropriate version of software,  set environment variables such as the PATH, run any
-tool-specific configuration, and do the same for all software on which it depends.
-If the correct versions are not available, {\tt scram} halts and emits an error.
-While this procedure has great value for consistency, it also introduces a significant cost
-because it involves a large number of nested scripts traversing a filesystem,
-repeatedly looking up metadata.  In our example, the time to perform this configuration
-with a cold cache is about 14 minutes, which is almost as large as the actual analysis
-run, which takes 20 minutes.
-
-\begin{figure*}[t]
-\centering
-\includegraphics[width=.8\textwidth]{version-evolution.eps}
-\caption{Version Evolution}
-\label{fig:version-evolution}
-\end{figure*}
-
-\item {\bf High Selectivity.}  Although the total size of the resources accessed by this
-program is very large, the size of the data and software actually used are much smaller.
-Often, an entire repository or data source is named within the script, but the program
-only needs a handful of items from that source.  For example, the data is stored on an
-HDFS filesystem with 11.6TB of data, but only 20GB are actually consumed by the program. 
-The reason for this great reduction is at first each BEAN event contains a large amount of information, and the TauAnalysis throws away a lot of the irrelevant event information, keeping only the relevant bits.
-The CMSSW repository is 88.1GB in total
-but only 448.3MB of source is checked out, and the actually used software only
-measured 6.3MB.  In a few cases, a source of software is named but never actually accessed.
-(For example, our original script includes the Open Science Grid software stack in the PATH, but does not actually use it.)
-We suspect that end users are accustomed to missing dependencies and thus get in the habit of adding commonly used software,
-whether it is needed or not.
-
-\item {\bf Rapid Changes in Dependencies.}  Over the course of three months
-between collecting the initial email, analyzing the program, and writing this
-paper, the computing environment continuously changed.  The CMSSW software
-distribution released a new version, the target execution environment was upgraded
-to a new operating system, and the application deprecated the use of CVS for obtaining
-the software.  While the users of this software seem be accustomed to constant change,
-any preservation technique will have to be very cautious about relying upon an
-external service, even one that may appear to be highly stable.
-
-\end{itemize}
-
-\if 0
-
-\begin{table}
-    \centering
-    \begin{tabular}{|l|}
-        \hline
-        {\bf Version 1: Email}\\ \hline
-        1. Create a CMS release,\\
-            \hspace{9pt} e.g. {\tt cmsrel CMSSW\_5\_3\_11\_patch3} \\
-        2. Install the BEAN packages as the instructions: \\
-            \hspace{9pt} {\tt \url{https://github.com/cms-ttH/BEAN/blob/...}}\\
-        3. Install grid-control: \\ 
-            \hspace{9pt} {\tt svn co \url{https://ekptrac.physik.uni-ka/...}} \\
-        4. INstall the TauAnalysis package: \\
-           \hspace{9pt} {\tt git clone \url{https://github.com/matz-e/...}} \\
-           \hspace{9pt} {\tt scram b -j32} \\
-        5. Fix grid\_control.cfg and run it. \\
-        6. Perform the actual tau roast program. \\ 
-        \hline
-        {\bf Version 2: Script}\\ \hline
-        {\tt setenv CMSSW\_BASE CMSSW\_5\_3\_11\_patch3} \\
-        {\tt cmsrel \$HOME/\$CMSSW\_BASE} \\
-        {\tt cvs co -r V03-09-23 PhysicsTools/PatUtils} \\
-        {\tt git clone \url{https://github.com/cms-ttH/BEAN.git}} \\
-        {\tt wget -r \url{http://nd.edu/~abrinke1/...}} \\
-        {\tt scram b -j32} \\
-        {\tt wget \url{http://pyyaml.org/download/pyyaml/PyYAML...}}\\
-        \#the experiment data is from HDFS \\
-        {\tt cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10}\\
-        {\tt cmsenv}\\
-        {\tt python setup.py install --user} \\
-        {\tt scripts/roaster data/generic\_ttl.yaml} \\ 
-        \hline
-        {\bf version 3: Formulated Script} \\ \hline
-        {\tt setenv CMSSW\_BASE CMSSW\_5\_3\_11\_patch3} \\
-        {\tt setenv {\bf GIT} \url{https://github.com}} \\
-        {\tt setenv {\bf PYYAML} \url{http://pyyaml.org}} \\
-        {\tt setenv {\bf ND} \url{http://nd.edu}} \\
-        {\tt cmsrel \$HOME/\$CMSSW\_BASE} \\
-        {\tt cvs co -r V03-09-23 PhysicsTools/PatUtils} \\
-        {\tt git clone \${\bf GIT}/cms-ttH/BEAN.git} \\
-        {\tt wget -r \${\bf ND}\url{/~abrinke1/ElectronEffectiveArea.h}} \\
-        {\tt scram b -j32} \\
-        {\tt wget \${\bf PYYAML}/download/pyyaml/PyYAML...}\\
-        \#the experiment data is from HDFS \\
-        {\tt cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10}\\
-        {\tt cmsenv}\\
-        {\tt python setup.py install --user} \\
-        {\tt scripts/roaster data/generic\_ttl.yaml} \\ 
-        \hline
-       {\bf Version 4: Fine-Grained Toolkit - Package}\\ \hline
-        {\tt setenv CMSSW\_BASE CMSSW\_5\_3\_11\_patch3} \\
-        {\tt setenv {\bf GIT} \url{https://github.com}} \\
-        {\tt setenv {\bf PYYAML} \url{http://pyyaml.org}} \\
-        {\tt setenv {\bf ND} \url{http://nd.edu}} \\
-        {\tt cmsrel \$HOME/\$CMSSW\_BASE} \\
-        {\tt cvs co -r V03-09-23 PhysicsTools/PatUtils} \\
-        {\tt git clone \${\bf GIT}/cms-ttH/BEAN.git} \\
-        {\tt wget -r \${\bf ND}\url{/~abrinke1/ElectronEffectiveArea.h}} \\
-        {\tt scram b -j32} \\
-        {\tt wget \${\bf PYYAML}/download/pyyaml/PyYAML...}\\
-        \#the experiment data is from HDFS \\
-        {\tt cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10}\\
-        {\tt cmsenv}\\
-        {\tt python setup.py install --user} \\
-        {\tt scripts/roaster data/generic\_ttl.yaml} \\ 
-        \hline
-    \end{tabular}
-    \caption{Scripts of each Solution}
-    \label{table:scripts}
-\end{table}
-
-\fi
-
 \section{Evolving the Artifact}
@@
 facilitate automatic and efficient preservation.
-
-\section{Measuring Dependencies}
-
-\begin{figure*}
-\centering
-\includegraphics[width=.8\textwidth]{workflow-parrot.eps}
-\caption{Workflow of The Fine-Grained Dependency Management Toolkit Based on Parrot}
-\label{fig:workflow-parrot}
-\end{figure*}
-
-We have developed a prototype tool to assist in the measurement and preservation
-of implicit dependencies for complex applications.
-We use Parrot~\cite{thain2005parrot} to explicitly record all
-of the files accessed by our example application, allowing us to observe how
-much of each external dependencies is used, and what local resources are implicitly used.
-Using this information, we create a \emph{reduced package} which contains
-only the files actually used by the application.
-
-Parrot is a virtual filesystem access tool which has been used to attach
-existing programs to a variety of remote I/O systems, such as HTTP, FTP, and CVMFS.
-It works by trapping an application's system calls through the Linux {\tt ptrace} debugging
-interface, and then replacing them with the desired I/O operations.  Parrot is already used
-in the high energy physics community with applications like TauRoast specifically to 
-provide access to the CMSSW software distribution via the CVMFS distributed file system.
-We made small modifications to Parrot to record a \emph{namelist} which lists all 
-of the files that an application actually accesses.
-
-Figure~\ref{fig:workflow-parrot} illustrates the measurement process.
-The starting point of this toolkit is one successful execution of the application on the native machine.
-First, we execute the actual data analysis script under Parrot to generate the namelist.
-Then, using the namelist, we generate a package containing all the necessary data
-and software for one analysis program. When another
-researcher wants to repeat the program, he only needs to obtain the package and
-execute the actual analysis program inside the package.
-
-For one execution of \emph{TauRoast}, the generated namelist includes 132,047 accessed filenames,
-along with the system calls used to access the file, such as {\tt open}, {\tt stat}, {\tt read}, etc.
-With duplicate filenames removed, the list is reduced to 67,168 files.
-Many of those entries do not exist, because they reflect attempts
-by the application to search for programs and libraries in multiple places.
-Only 22,068 entries reflect existing files or directories.
-
-The packaging tool iterates over each item of the filename list, determines the process
-mode and replication degree according to the file type (common files,
-directories, symbolic links) and the system call type, generates one package
-containing the dependencies, and summarizes the contents of the package
-as shown in Table~\ref{table:package-info}.  To the extent possible,
-the filesystem structure of the original environment is preserved.
-
-We considered several approaches to constructing the package.
-In a {\bf shallow copy}, we only copied the individual files in the namelist,
-creating only parent directories for each.  Where a directory was listed,
-we created the directory and populated it with empty files as placeholders
-to facilitate a directory listing.  In a {\bf medium copy}, we copied the
-individual files as before.  Where a directory was listed, we created
-the directories and copied the contents of the files in that directory,
-one level deep.  A {\bf deep copy} would duplicate all directories recursively,
-but this would have resulted in TB-sized packages, so we did not consider
-it further.
-
-Parrot is required to re-run the packaged artifact, in order to force
-the packaged files to appear to exist in their original locations.
-To this end, the packaging tool creates a \emph{file map} which maps
-the logical names of the files to their current physical locations, as shown in Table~\ref{table:map-file}.
-Parrot reads the file map and redirects system calls at run-time to achieve the desired effect.
-As the example suggests, special device files such as {\tt /proc} and {\tt /dev}
-are not incorporated into the package but are instead accessed natively.
-
-\begin{table}
-    \centering
-    \begin{tabular}{ll}
-    \hline
-    \bf Path used in Program & \bf Actual Location \\ \hline
-    {\tt /} & {\tt /tmp/package-hep} \\ \hline
-    {\tt /tmp/package-hep} & {\tt /tmp/package-hep} \\ \hline
-    {\tt /dev} & {\tt /dev} \\ \hline
-    {\tt ...} & {\tt ...}\\ \hline
-    \end{tabular}
-    \caption{Structure of Map File}
-    \label{table:map-file}
-\end{table}
-
-\begin{table}
-    \centering
-    \begin{tabular}{rrr}
-\hline
-                    & \bf Shallow Copy & \bf Medium Copy\\
-\hline
-    Whole Files    & 1632         & 15642\\ 
-\hline
-    Empty Files    & 14273        & 263\\
-\hline
-    Directories    & 1549         & 1549\\ 
-\hline
-    Symbolic Links & 4614         & 4614 \\
-\hline
-    \bf Total Size & \bf 21GB     & \bf 28GB \\ 
-\hline
-    \end{tabular}
-    \caption{Package Information}
-    \label{table:package-info}
-\end{table}
-
-\subsection{Tracking of Network Dependencies}
-
-\begin{figure}
-\centering
-\includegraphics[width=.6\textwidth]{git-syscall.eps}
-\caption{Exec Syscalls of a git command}
-\label{fig:git-syscall}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=.6\textwidth]{http_packet.eps}
-\caption{HTTP Request and Response}
-\label{fig:http_packet}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=.6\textwidth]{url_redirection.eps}
-\caption{An Example of URL Redirection}
-\label{fig:url_redirection}
-\end{figure}
-
-All the dependencies of one program can be divided into three categories: local file system (e.g., /usr, /lib and /lib64), remote file systems which can be mounted as local directories (e.g., /cvmfs and /hdfs), and other remote network dependencies (e.g.
-http, https and ssh).
-Through utilizing ptrace to trap each file-relevant system call used by a program, the first two categories of dependencies can be collected. 
-Motivation of tracking network dependencies: Linkrot is a common and great threat to the preservation of scientific applications.
-A URL which works normally today may be unavailable permanently.
-A method which can help the scientists figure out all the network dependencies of their applications provides the chance to evaluate the stability of each network dependencies and preserve the unstable network resources before linkrot happens.
-One direct solution to track the third category of dependencies is to utilize ptrace to check each exec system call used by a program and record each network-relevant executable and its parameters.
-However, an executable may create one or more child processes to finish some tasks, and a child process may create their own children processes.
-Figure~\ref{fig:git-syscall} shows all the processes created by a git command.
-A process with PID 998 is created to clone a remote git repository into local machine, which totally has 6 child processes.
-Moreover, a network-relevant executable name collection is necessary to identify network dependencies.
-The diversity of network-relevant executables and the large process tree generated for a network executable make this solution infeasible.
-
-Another solution to track network dependencies is to track the network sockets.
-The user process communicates with the network protocol stacks in the kernel through the network socket layer user interface on Linux.
-From the process tree shown in the above figure, the process with PID 1000 responds to create a socket, connect to a DNS server, send a DNS request packet to the DNS server and receive a DNS response packet from the DNS server.
-The information gained from the network socket tracking can be divided into three categories.
-\begin{itemize}
-\item The information of network sockets used to communicate with remote network dependences (through socket and connect system calls) can be used to figure out the port number, service name (such as, http, https, and ssh), socket type (stream and datagram),  and the domain type (inet and inet6).
-\item The contents of DNS packets can be used to figure out the hostname and IP address of each remote network dependency. 
-\item As for applications based on http protocol, all the http requests and responses can be seen, as shown in Figure~\ref{fig:http_packet}.
-However, as for applications based on https and ssh which encrypt network data using TLS/SSL, tracking network data on the socket level can only see the encrypted data.
-\end{itemize}
-
-The results of tracking network sockets used by a program involves two categories of network resource redirections, dns-level hostname redirection and website-level url redirection. 
-\begin{itemize}
-\item dns-level hostname redirection: Each DNS packet includes five parts, header, question, answer, authority, and additional.
-A DNS response packet with the type CNAME has multiple answers.
-For example, the DNS response packet which tries to resolve {\tt www3.nd.edu} includes two answers.
-The first answer provides an alias of {\tt www3.nd.edu}, {\tt www-vip.cc.nd.edu}, and the second answer maps the alias to the IP address.
-{\tt www3.nd.edu} CNAME {\tt www-vip.cc.nd.edu}
-{\tt www-vip.cc.nd.edu} A {\tt 129.74.12.151}
-The CNAME-type DNS packets leave us a question, among the hostname used by the user, the alias(es), the IP address, what should we preserve?
-\item website-level url redirection: Website-level url redirection happens when a website updates its location and still want their old users access their resources using the old url.
-Figure~\ref{fig:url_redirection} illustrates the url redirection between {\tt \url{www3.nd.edu/~ccl}} and {\tt ccl.cse.nd.edu}.
-Except for the difference of hostnames, the application layer protocols used by the old-version website and the new-version website is also different: the old website provides services through the https protocol, while the new website provides services through the http protocol.
-\end{itemize}
-
-The usage of https protocol makes detecting of website-level url redirections through tracking system calls more difficulty and even impossible.
-All the application data will be encrypted at presentation layer through the TLS/SSL protocol, which is initialized at the session layer and works at the presentation layer.
-
-\section{Evaluation}
-
-We evaluated the correctness of the reduced package and the overhead of generating the package.
-To do this, the application was repeated with the help of \emph{Original Script} (as shown in Figure~\ref{fig:version-evolution}) on the original machine. 
-Then one \emph{reduced package} was generated and verified with the help of Parrot on the original machine.
-
-Then, two different virtual machines (VM) - one VM from the Notre Dame Cloud Platform based on KVM and one VM from the Amazon EC2 Platform based on Xen, were employed to further verify the correctness of the reduced package.
-
-We first repeated the example from scratch using the Script translated from the original email on the original machine and counted the time consumption and data size. 
-Then based on the successful execution of Original Script, we evaluated Reduced Package - one package containing necessary dependencies is generated, and then the time consumption and data size is analyzed.
-
-To measure time consumption, we counted the time used to obtain remote software dependencies, build the environment, and analyze the dataset.
-We also counted the time used to obtain the namelist and to generate the package.
-To measure data size, we can easily figure out the size of each data and code source inside the package under Reduced Package.
-Original Script does not support mining of implicit dependencies.
-As for remote sources, we can figure out the named size through the analysis script.
-However, it is hard to figure out the named size of each local source.
-Instead, we only knew that total size of each file system is very large.
-
-Table~\ref{table:time-2nd3rd} shows the execution time comparison between
-Original Script and Reduced Package.
-Reduced Package is faster than Original Script, because all the software copied into the package has been compiled and the Software Acquisition stage is not necessary.
-and all the environment building only takes 4 seconds,
-We were surprised that Reduced Package even reduces the actual analysis time. 
-The reason for this is that data is obtained through accessing HDFS in Original Script, but is copied into the package in Reduced Package.
-This localization of experimental data speeds up the data analysis process, resulting the actual analysis time reducing from 20 minutes to 13 minutes.
-
-\begin{table}
-    \centering
-    \begin{tabular}{lrr}
-    \hline
-    \bf Task Category & \bf Original Script & \bf Reduced Package \\ \hline
-    Obtain Namelist & N/A & 28min 28s \\ \hline
-    Generate Package & N/A & 85min 51s \\ \hline
-    Software Acquisition & 8min 11s & N/A \\ \hline
-    Environment Build & 5min 49s  & 4s \\ \hline
-    Analysis Code & 20min 31s & 13min 04s \\ \hline
-    \end{tabular}
-    \caption{Execution Time Comparison between Original Script and Reduced Package}
-    \label{table:time-2nd3rd}
-\end{table}
-
-Table~\ref{table:time-2nd3rd} also illustrates the time used to
-obtain the namelist and to generate the package. 
-The time used for these two steps is longer than the execution time,
-because each filename of the list, together with its system call type, needs to be checked, and the structure of each directory item must be maintained.
-However, 
-this is only done once.
-Once the package is
-generated, many users can directly obtain the package and repeat the application 
-separately.
-
-Table~\ref{table:size-original-real} on page 2 illustrates the total size, named size in the example and actually used size of each remote source (the first 4 items) and local source (the remaining 5 items).
-The third column corresponds to the data size of Reduced Package and can be easily figured out, because all the necessary data has been copied into the package.
-Original Script does not support measuring implicit dependencies.
-As for remote sources, we can figure out the named size through the analysis script.
-However, it is hard to figure out the named size of each local source.
-Instead, we only knew that total size of each file system is very large.
-
-\begin{table}
-	\centering
-	    \begin{tabular}{llrrr}
-	        \hline
-	        \bf Name & \bf Location & \bf Total & \bf Named & \bf Used \\ 
-	        \hline
-	        CMSSW code     & CVS & 88.1GB & 448.3MB & 6.3MB\\ \hline
-	        Tau source       & Git & 73.7MB & 73.7MB & 6.7MB \\ \hline
-	        PyYAML binaries    & HTTP & 52MB & 52MB & 0KB \\ \hline
-	        .h file       & HTTP& 41KB & 41KB & 0KB \\ \hline \hline
-	        Ntuples data    & HDFS& 11.6TB & N/A& 20GB \\ \hline
-	        Configuration & CVMFS & 7.4GB & N/A & 103MB \\ \hline
-	        Linux commands & localFS & 110GB &  N/A & 68.4MB \\ \hline     
-	        HOME dir& AFS &12GB & N/A & 32MB\\ \hline
-	        Misc commands & PanFS & 155TB & N/A  & 1.6MB \\ \hline
-	        Total      &    & 166.8TB            & N/A & 21GB \\ \hline
-	    \end{tabular}
-	    \caption{Data and Code Used by Tau Roast}
-	    \label{table:size-original-real}
-\end{table}
-%	\begin{tablenotes}
-%	      \small
-%	      \item The first column illustrates the total size of each data and software source; 
-%	            the second column illustrates the size of the named files from each source;
-%	            the third column illustrates the size of actually used data from each source.
-%	            N/A denotes it is hard to figure out the named size of implicit dependencies directly.        
-%	    \end{tablenotes}
-
-To further verify the correctness of Reduced Package on other machines, two different machines are employed -
-one virtual
-machine~\cite{goldberg1974survey} from the Notre Dame Cloud Platform based on KVM sharing the same kernel version with the original machine,
-and one virtual machine from  the Amazon EC2~\cite{amazon2010amazon} Platform based on Xen.
-
-Table~\ref{table:config-vm} illustrates the configuration of 
-each machine and the execution time of the application on each machine.
-All the machines adopt the x86\_64 hardware platform and Linux kernel.
-Both of the two VMs repeated the application with the help of the package generated on the original machine successfully.
-The execution time on one machine greatly depends on its hardware configuration.
-
-\begin{table}
-    \centering
-    \begin{tabular}{lrrrr}
-    \hline
-    \bf Machine Type & \bf Distro Version & \bf CPU Cores & \bf Mem (GB) & \bf Execution Time \\ \hline 
-    Original Machine &  Red Hat 5.10 & 64 & 125 & 13min 04s\\  \hline
-    KVM (Notre Dame) & CentOS 5.10 & 4 & 2 & 21min 38s\\ \hline
-    Xen (EC2) & Red Hat 5.9 & 16 & 60.5 & 13min 30s\\ \hline
-    \end{tabular}
-    \caption{Evaluation of Different Machines}
-    \label{table:config-vm}
-\end{table}
-
-In summary, we demonstrate that the application can be repeated with the help of the reduced package on one different machine with the required hardware architecture and OS kernel version.
-%*****hmeng-doubt:Another reason for the packaging utility is that not all the data and software generated by the second version script is used during the the actual data analysis.
-The packaging utility can help us find out the optimal subset of data and software involved in one actual data analysis.
-%*****hmeng-doubt: this point is not the motivation. but one achievement comes together. out of imagination.
-
-\begin{figure}
-\centering
-\includegraphics[width=.6\textwidth]{preservation-integration.eps}
-\caption{Preserving Multiple Artifacts}
-\label{fig:Preservation integration}
-\end{figure}
-
-\section{Open Problems}
-
-Figure~\ref{fig:Preservation integration} shows the rough information
-architecture of the archive that we imagine for complex
-scientific software like TauRoast.
-Each artifact to be preserved is a package that consists of a top-level
-script to invoke the software, a dependency map, and the dependencies
-themselves, which may be external to the original program.  The artifacts
-are then ingested into the archive, where shared dependencies are stored
-only once.  In cases where an artifact has a dependency on a trusted
-(or very large) remote archive, the dependency may simply be tracked
-. A researcher that wishes to reproduce a given
-result need only refer to the unique identifier of the artifact, and will
-be able to automatically extract all of the dependent components of
-that artifact.
-
-For example, in Figure~\ref{fig:Preservation integration} Script 1 depends on items A, B, and C.
-Items A and B are ingested into the archive, where B is shared with Script 2.
-Item C is stored in another trustworthy repository and is tracked rather than ingested.
-When Script 1 is exported from the repository, items A and B are exported along with it, while C can be copied or remain remote, according to the end user's choice.
-
-As simple as that picture appears, there are a number of problems that must be solved to get there:
-
-{\bf Measure the Mess or Force Cleanliness?}  Two radically different approaches to dependency tracking are possible.
-The first is to allow end users complete freedom to construct their environment as desired, then \emph{measure} what items were actually used.
-As we have shown, this is possible, but has significant overheads and does not fully preserve the structure or intent of the end user.
-The second approach is to \emph{force} users to work in a clean environment in which no resource can be used until a proper dependency has been declared.
-This ensures that all dependencies are known in advance (and made explicit to the end user) but places a variety of restrictions on the user's daily work, and may prevent creative approaches that do not fit within the curator's view of how programs should be structured.
-Whether end users will accept the inconvenience of forced cleanliness for the benefits of reproducibility can only be discovered through experiment.
-
-{\bf Granularity of Dependencies.}  Dependencies could be handled
-at many different levels of granularity.  In this work, we have shown
-how they can be handled at the level of entire repositories or individual files.
-Other possible choices might include intermediate-sized software packages
-(like RPM) or in the case of experimental data, even portions of individual large files.  Clearly, a larger granularity will result in 
-simpler dependency maps, and more wasted space; smaller granularity results
-in complex dependency maps and less wasted space.  A hybrid solution may
-be able to combine both by storing large granularity dependencies, but
-selecting sub-items out of objects when efficiency demands it.
-
-{\bf Scope of Reuse.}  We have presented the data preservation
-problem as primarily one of accurate reproduction: if a result depends
-on running program X, we must be able to run exactly X again.  However,
-the goal of scientific reproducibility is rarely limited to running
-\emph{precisely} what a predecessor did. Often, the objective is to
-change a parameter or a data input in order to see how the result is affected.
-To that end, the preservation system must capture enough of the surrounding
-material to permit modifications to succeed.  From this perspective,
-a larger granularity of preservation is desirable.  A better understanding of
-how end users will consume preserved software will help to shape how
-software is preserved in the first place.
-
-{\bf Dependency Detection.}  If we allow users to work in uncontrolled
-environments, then we must have better methods for understanding the dependencies  of existing programs.  At first, we relied on an expert reader to examine
-the user's script and extract the dependencies.  This is clearly
-not a scalable approach.  We then demonstrated an automated method of observing
-what individual files are accessed by a program. However, this does
-not cover all types of dependencies, particularly those that are networked.
-More sophisticated observation techniques could infer higher-level information,
-such as the RPM package names of the files accessed, the URLs of remote
-repositories named throughout the program, or even the addresses and names of networked dependencies like databases and filesystems.
-
-{\bf Source, Binary, or Both?}  A science archive might choose to retain
-the source code of an artifact or the binary code that can actually run in a given environment.
-While conventional wisdom suggests that access to source code is critical for the long term
-survival and evolution of a piece of software, it also requires the maintenance of an enormous
-amount of supporting software in the form of compilers, linkers, and supporting libraries for
-the target platform.  Rebuilding all of these for every invocation of an artifact is
-likely to have excessive cost.  We suggest that a realistic repository will have to
-maintain \emph{both}: the source describes the ultimate meaning of the code, but
-the binary is an important performance cache, a backup if the compiler toolchain should
-fail to be preserved, and a checksum to ensure that a source artifact was rebuilt correctly.
-
-\section{Related Work }
-
-Generally, there are three approaches to preserve software environment:
-hardware preservation, migration and emulation.  Hardware
-preservation preserves the original software and its original operating
-environment. 
-Software migration technique~\cite{cifuentes1996binary,mancl2001refactoring} was used to facilitate running software on new machines.
-However, migration often involves the re-compiling and re-configuring
-the source code to accommodate a new hardware platform and software environment.
-Emulation recreates the original software and hardware environment by
-programming future platforms and OSs. One common solution to implement this is
-virtual machine. According to the usage and emulation degree of the real
-machine, virtual machine can be divided into system virtual machine and process
-virtual machine. 
-The working principle, design principle and
-performance evaluation of system virtual machine were illustrated in~\cite{goldberg1974survey, smith2005architecture}. 
-The
-functionality of system VM to support different guest operating systems was illustrated in~\cite{barham2003xen,kivity2007kvm,rosenblum1999vmware}.
-F. Esquembre~\cite{esquembre2004easy} illustrated how JVM, one process virtual machine, can expedite the creation of
-scientific simulations in Java. 
-The pros and cons of these three approaches were discussed in~\cite{matthews2009towards,phelps2005no,hong2010software}.
-
-The preservation of computing environment and software environment was treated as one entirety in~\cite{matthews2009towards,phelps2005no,hong2010software}.
-However, frequently changing experiment software makes the maintenance of the preserved experimental environment very complex.
-CernVM~\cite{buncic2010cernvm} treated them as two different categories.
-The preservation of computing environment is implemented with CernVM, and the preservation of software environment is based on a CernVM filesystem(CVMFS) specifically designed for efficient software distribution.
-
-The importance of preserving software in source code format was emphasized in~\cite{zabolitzky2002preserving,castagne2013consider}. 
-However, CVMFS~\cite{buncic2010cernvm} published pre-built and configured experiment software releases to avoid the time-consuming software building procedure.
-
-Attempts from different perspectives to facilitate the reproduction of scientific experiments utilizing a preserved software library have been made. 
-The software distribution mechanism over network was discussed in~\cite{compostella2010cdf, blomer2011cernvm}.
-J.
-R.
-Rice et al.~\cite{rice1996scientific} made the reproduction process easier through the integration of user interface, scientific software libraries, knowledge base into problem-solving environment.
-S. R. Kohn et al.~\cite{kohn2001divorcing} tried to enable the creation and distribution of language-independent software library by addressing language interoperability.
-a scalable, distributed and dynamic workflow system for digitization processes was proposed in~\cite{schoneberg2013scalable}.
-A distributed archival network was designed in~\cite{subotic2013distributed} to facilitate process-oriented automatic long-term digital preservation.
-M. Agosti et al.~\cite{agosti2012envisage} aimed to help non-domain users to utilize the digital archive system developed for domain experts.
-
-Current mechanisms of preserving scientific experiments assume that all the data and software mentioned in the experiments are necessary for the reproduction of the experiments.
-However, this is not always right.
-In some cases, the original author may leave additional code referring to irrelative data and software in the program.
-One mechanism, which can figure out the absolutely relevant data and software of one experiment, is important for both the preservation and reproduction of scientific experiments.
-
-B. Matthews et al.~\cite{matthews2008significant} introduced one conceptual framework for software preservation from several case studies of software preservation.
-One tool to capture software preservation properties within a software environment was designed in~\cite{matthews2010framework} through a series of case studies conducted to evaluate the software preservation framework.
-L. R. Johnston et al.~\cite{johnston2014workflow} proposed one overall data curation workflow for 3-5 case studies of preserving research data.
-Two case studies~\cite{borgman2012data} were conducted to figure out the properties of data to be reused in the future.
-
-\section{Postscript}
-
-We began this work in late 2013, generating a reduced package for \emph{TauRoast} based
-on the configuration of a standard machine at Notre Dame at the time.  In the course
-of writing this paper in spring 2014, almost everything about the computing environment
-changed: the operating system was upgraded, a new version of CMSSW was released, and
-our local HEP users switched from using CVS to CVMFS for accessing CMSSW.
-The original script provided by the author failed to run on the same machine.
-But, the reduced package we created three months earlier in the old environment
-worked just fine on the new machine.
-
-\section*{Acknowledgments}
-
-This work was supported in part by National Science Foundation grants PHY-1247316 (DASPOS), 
-OCI-1148330 (SI2) and PHY-1312842.
-The University of Notre Dame Center for Research Computing scientists and engineers provided critical technical assistance throughout this research effort.
-
-Copyright (C) 2014 The University of Notre Dame
-
-This work is licensed under the Creative Commons Attribution 4.0 License.
-
-\bibliographystyle{plain}
-\bibliography{cclpapers,this}
-
-\end{document}

### 2015-01-06 intro.tex
Put each section into a separate tex file

--- 2015-01-05 paper.tex
@@
-\documentclass[procedia]{easychair}
-\usepackage{url}
-\usepackage[flushleft]{threeparttable}
-\hyphenation{resour-ces}
-\hyphenation{approac-hes}
-\hyphenation{har-der}
-\hyphenation{spe-cifically}
-\makeatletter
-\def\@copyrightspace{\relax}
-\makeatother
-
-\title{An Invariant Framework for Conducting Reproducible Computational Science}
-
-% \titlerunning{} has to be set to either the main title or its shorter
-% version for the running heads. When processed by
-% EasyChair, this command is mandatory: a document without \titlerunning
-% will be rejected by EasyChair
-
-\titlerunning{An invariant framework for conducting reproducible computational science}
-
-\author{
-	Haiyan Meng\inst{1}
-\and
-	Matthias Wolf\inst{2}
-\and
-	Douglas Thain\inst{3}
-}
-\institute{
-	Department of Computer Science and Engineering,
-	University of Notre Dame,
-	Notre Dame, Indiana, USA
-	\email{hmeng@nd.edu}
-\and
-	Department of Physics,
-	University of Notre Dame,
-	Notre Dame, Indiana, USA
-	\email{mwolf3@nd.edu}
-\and
-	Department of Computer Science and Engineering,
-	University of Notre Dame,
-	Notre Dame, Indiana, USA
-	\email{dthain@nd.edu}
-}
-
-%  \authorrunning{} has to be set for the shorter version of the authors' names;
-% otherwise a warning will be rendered in the running heads. When processed by
-% EasyChair, this command is mandatory: a document without \authorrunning
-% will be rejected by EasyChair
-
-\authorrunning{Meng, Wolf and Thain}
-
-\begin{document}
-
-\maketitle
-
-\keywords{}
-
-\begin{abstract}
-\it Computational reproducibility depends on being able to isolate necessary and sufficient computational artifacts and preserve them for later re-execution.
-Both isolation and preservation of artifacts can be challenging due to the complexity
-of existing software and systems and the resulting implicit dependencies, resource distribution, and shifting compatibility of systems as time progresses---all conspiring
-to break the reproducibility of an application. Sandboxing is a technique
-that has been used extensively in OS environments for isolation of computational artifacts.
-Several tools were proposed recently that employ sandboxing as a mechanism to ensure reproducibility.
-However, none of these tools preserve the sandboxed application for re-distribution
-to a larger scientific community---aspects that are equally crucial for ensuring reproducibility as sandboxing itself.
-In this paper, we describe a combined sandboxing and preservation framework, which is efficient and practical and
-useful for large-scale reproducibility. We present a case study of a complex high energy
-physics application and show how the framework can be useful for sandboxing and preserving.
-We report on the completeness, performance,
-and efficiency of the framework, and suggest possible standardization approaches.
-\end{abstract}
-
-% A category with the (minimum) three required fields
-%\category{H.4}{Information Systems Applications}{Miscellaneous}
-%A category including the fourth, optional field follows...
-%\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]
-
-%\terms{Theory}
-
 \section{Introduction}
@@
 some reflections on the challenges of preservation and advice for future efforts.
-
-\if 0
-Section 2: Overview of Application
-    CMS/LHC introduction.
-    Data sources and reduction of size.
-    Code sources and reduction of size.
-    Prose observations about the script.
-        Uses multiple repos that change over time, with varying level of stability.
-        Low selectivity from the larger repos
-        Significant initialization time to collect everything.
-        Incidental infrastructure tools versus essential objects.
-        Some dependencies were surprising.
-    Figure: Diagram of app with both code and data sources.
-    Table: Show all code and data sources and size within one table.
-
-Section 3: Preservation Strategies
-    Figure: Show app in four stages:
-        Single email.
-        Script with embedded references to dependencies.
-        Script with map file that refers to external dependencies.
-        Script with map file that refers to preserved dependencies.
-
-    Transform to more suitable format that expresses dependencies.
-
-    Incorporate into archive, saving deps and map file.
-
-    But, how to get the dependencies?
-
-    Three strategies:
-        Original - Unmodified application run in original environment.
-        Coarse-Grained - Capture deps at large granularity -- whole filesystems and repositories.
-        Fine-Grained - Capture deps at a fine granularity -- individual files actually used.
-
-    Coarse-Grained Method (Copy Repositories)
-        First, determine dependencies
-        Express app as script + map file
-        Packaging tool downloads deps, rewrites map file.
-        To run packaged application, obtain map, download
-
-    Fine-Trained Toolkit (Parrot)
-        Tool to detect dependencies (Parrot)
-        Express app as script + map file
-        Packaging tool downloads deps, rewrites map file.
-        To run package application, run again with Parrot.
-
-Section 4: Evaluation
-
-    Table: Time and size of preserving using each of the two techniques.
-
-    Explain why the techniques show different performance.
-
-    Is one technique more effective than the other?  Why?
-\fi
-
-\begin{figure}[t]
-\centering
-\includegraphics[width=.5\textwidth]{data-code-size.eps}
-\caption{Inputs to Tau Roast}
-\label{fig:data-code-size}
-\end{figure}
-
-\section{Overview of Tau Roast}
-
-Within the ongoing investigation of the Higgs boson at the CMS
-detector, part of the LHC at CERN~\cite{collaboration2008cms}, the Higgs production in association
-with two top quarks allows measuring the Higgs coupling strength to
-top quarks~\cite{chatrchyan2013search}.  As the Higgs boson is too short-lived to be detected
-itself, it has to be reconstructed from its decay products.
-
-The application which is the study of this paper is called \emph{TauRoast}.
-It searches for cases where the Higgs boson decays to two tau leptons.
-Since the tau leptons are very short-lived, they are not observed directly, but by the particle decay products 
-that they generate.  So, the analysis must search for detector
-events that show a signature of decay products compatible with both hadronic tau and top decays.  Properties of such events are used to distinguish
-the events of interest (Higgs decays) from all other events and
-are also used in further statistical analysis.
-
-Figure~\ref{fig:data-code-size} shows that both the code and data
-that form \emph{TauRoast} are drawn from large repositories through
-multiple steps of reduction.  A preservation strategy must weigh
-whether to store the large repositories completely, the fragments
-used by an artifact, or something in between.
-
-{\bf Code Sources.} Like many scientific codes, the central algorithm
-of \emph{TauRoast} is expressed in a relatively small amount of
-custom code developed by the primary author.  But, the code cannot
-run at all without making use of an enormous collection of software
-dependencies.  Some of these dependencies are standard to operating
-systems worldwide, some are standardized across the entire high-energy
-physics field, some are particular to small collaborative groups,
-and a few are very specific to a single researcher.
-
-The largest of these repositories is the CMS Software Distribution (CMSSW)~\cite{cms2006cms},
-a carefully-curated selection of software packages which is distributed
-in several forms.  Historically, components of CMSSW were obtained by checking components
-of the source out of CVS (CMSSW source codes were moved from CVS to git recently), or by installing a complete binary package on a shared
-filesystem within an HPC center.  In recent years, distribution has moved to
-an on-demand delivery system known as CVMFS~\cite{blomer2011cernvm}, which
-provides a filesystem interface that transparently accesses a remote repository.
-The content of CMSSW is managed very carefully by a centralized team whose main goal
-is to ensure that the current version of the software operates correctly
-on the operating systems and architectures currently in use.  However,
-preservation is not a specific objective of the system, and so there is
-no particular guarantee that old versions of CMSSW will continue to
-operate indefinitely.
-
-CMSSW contains many different tools, libraries, and utilities.
-No single code uses anywhere close to all of these.
-But, because it is widely used within the experimental researchers, it is common for users to simply expect that a particular version of the entire repository is available.
-
-{\bf Data Sources.}
-The CMS collaboration provides end-users with a pre-processed
-and reduced data format, AOD~\cite{holtman2001cms}, containing information for events, i.e.,
-proton-proton collisions with a signature of interest, in the form of
-reconstructed particles.  This format is based on the RAW output of
-the CMS detector readout electronics and reconstructed world-wide, which is then processed through various algorithms which derive signatures of individual particles.
-Both real and simulated data are available for examination.
-
-As AOD data are too large to be iteratively processed repetitively in
-a physics analysis workflow, it is normally reduced further in
-structural complexity and content.  For the analysis under
-investigation here, this is a two-step process.  First, the AOD data
-are processed at the Notre Dame working group cluster to BEAN (Boson Exploration Analysis Ntuple) events,
-containing only trivial data containers packed in vectors.  This step
-is time and CPU intensive and its output contains data of 11.6$\,$TB to be
-analyzed by the tau analysis.
-It is performed by a small custom code framework, which is built on top of CMSSW.
-The BEAN format, production code, and
-data are shared within the analysis group looking at Higgs production
-in association with top quarks, which is formed by groups from a few
-American and European universities,
-consisting of up to a few dozen contributors.
-
-In the second step, the data are reduced to the ``Ntuple'' format,
-which contains only events matching basic quality criteria and
-fields relevant to \emph{TauRoast}.
-Again, the Notre Dame CMS groups cluster
-resources are used to perform this reduction and selection,
-running highly customized software,
-built on CMSSW and the BEAN framework,
-with code written and maintained by a small group.
-
-Once the data has been reduced to Ntuples, TauRoast can be run as a single
-process, and contains a stringent event selection to look only at high
-quality candidate events for the underlying physical process.
-Quantities from the relevant events can be
-both plotted and used in multivariate analysis to determine the level
-of expected signal in real data.
-This package is written using the CMSSW build framework,
-but only utilizes code from ROOT,
-a particle physics toolkit underlying CMSSW,
-and a few external python dependencies for convenience.
-
-\section{Observations}
-
-\emph{TauRoast} was provided to us in the form of an
-email which described, in prose, how to obtain the source,
-build the program, and run it correctly on one specific
-machine at our home institution, with no particular guarantee that
-it will run anywhere else in the world.
-Although this starting point may seem extreme, it is
-perfectly natural for collaborators to share configurations
-with each other in this form, and to rely on the presence
-of a working environment with appropriate dependencies already
-installed.  From this starting point, the authors played the
-role of curators, whose job it is to prepare the application
-for permanent archival.
-
-First, we elaborated the email instructions into an
-executable script that obtains the dependencies and then
-executes the analysis.  The script declares the necessary
-environment variables, downloads and checks out the necessary source code,
-builds it appropriately, calls initialization scripts in
-the dependent software, and then runs the analysis.
-A few rounds of correction with the original author were necessary
-to obtain all the dependencies and run the artifact correctly.
-(The original instructions introduced in the email also indicated how to run the application
-within a production batch system.  For the purposes of preservation,
-we consider the execution infrastructure to be distinct from the application,
-and leave it out of consideration for now.)
-
-The process of elaborating the program into a script revealed
-several observations about this type of application:
-
-\begin{itemize}
-
-\item {\bf Many Explicit External Dependencies.}  TauRoast depends on a large number of
-external dependencies, each with a different access method and data source.
-While we knew in advance that it depended upon the large CMSSW distribution,
-it was not apparent until elaborating the script that it depended upon
-two different Github repositories for the Tau source,
-a CVS server at CERN for some configuration information, a public web page
-for the PyYAML library, and the public home page of a Notre Dame student
-for one missing header file.  (The latter is particularly troubling!)
-While, at some level, the authors and users of these software know of these dependencies, they are often missing in
-informal communications or forgotten once the dependency is installed.
-However, once known, they are at least expressed explicitly within the script.
-
-\item {\bf Many Implicit Local Dependencies.} A much harder problem is that the
-application assumed the presence of many different components in the local
-filesystem view. It would be tempting to capture all of these by simply
-storing a virtual machine image containing the local filesystem. However,
-the application depended on no less than {\bf five} networked filesystems
-available on a particular machine available to the author:
-the data to be analyzed was stored on an HDFS~\cite{borthakur2008hdfs} cluster,
-some configuration data was stored on a CVMFS~\cite{blomer2011cernvm} filesystem,
-and a variety of software tools were on an NFS~\cite{howard1988scale},
-PanFS~\cite{welch2008scalable} and AFS~\cite{sandberg1985design} systems.
-The original authors were not aware of many of these dependencies,
-because they simply relied on local administrators to configure the
-software and make it available.
-
-\item {\bf Configuration Complexity.}  As a means of controlling the complexity
-of dependent software packages, the high energy physics community has developed
-a number of tools that perform run-time configuration and consistency checks
-of the available software.  {\tt scram} is the software management tool used
-by the CMS experiment.  Before running any code, {\tt scram} is used to locate
-the appropriate version of software,  set environment variables such as the PATH, run any
-tool-specific configuration, and do the same for all software on which it depends.
-If the correct versions are not available, {\tt scram} halts and emits an error.
-While this procedure has great value for consistency, it also introduces a significant cost
-because it involves a large number of nested scripts traversing a filesystem,
-repeatedly looking up metadata.  In our example, the time to perform this configuration
-with a cold cache is about 14 minutes, which is almost as large as the actual analysis
-run, which takes 20 minutes.
-
-\begin{figure*}[t]
-\centering
-\includegraphics[width=.8\textwidth]{version-evolution.eps}
-\caption{Version Evolution}
-\label{fig:version-evolution}
-\end{figure*}
-
-\item {\bf High Selectivity.}  Although the total size of the resources accessed by this
-program is very large, the size of the data and software actually used are much smaller.
-Often, an entire repository or data source is named within the script, but the program
-only needs a handful of items from that source.  For example, the data is stored on an
-HDFS filesystem with 11.6TB of data, but only 20GB are actually consumed by the program. 
-The reason for this great reduction is at first each BEAN event contains a large amount of information, and the TauAnalysis throws away a lot of the irrelevant event information, keeping only the relevant bits.
-The CMSSW repository is 88.1GB in total
-but only 448.3MB of source is checked out, and the actually used software only
-measured 6.3MB.  In a few cases, a source of software is named but never actually accessed.
-(For example, our original script includes the Open Science Grid software stack in the PATH, but does not actually use it.)
-We suspect that end users are accustomed to missing dependencies and thus get in the habit of adding commonly used software,
-whether it is needed or not.
-
-\item {\bf Rapid Changes in Dependencies.}  Over the course of three months
-between collecting the initial email, analyzing the program, and writing this
-paper, the computing environment continuously changed.  The CMSSW software
-distribution released a new version, the target execution environment was upgraded
-to a new operating system, and the application deprecated the use of CVS for obtaining
-the software.  While the users of this software seem be accustomed to constant change,
-any preservation technique will have to be very cautious about relying upon an
-external service, even one that may appear to be highly stable.
-
-\end{itemize}
-
-\if 0
-
-\begin{table}
-    \centering
-    \begin{tabular}{|l|}
-        \hline
-        {\bf Version 1: Email}\\ \hline
-        1. Create a CMS release,\\
-            \hspace{9pt} e.g. {\tt cmsrel CMSSW\_5\_3\_11\_patch3} \\
-        2. Install the BEAN packages as the instructions: \\
-            \hspace{9pt} {\tt \url{https://github.com/cms-ttH/BEAN/blob/...}}\\
-        3. Install grid-control: \\ 
-            \hspace{9pt} {\tt svn co \url{https://ekptrac.physik.uni-ka/...}} \\
-        4. INstall the TauAnalysis package: \\
-           \hspace{9pt} {\tt git clone \url{https://github.com/matz-e/...}} \\
-           \hspace{9pt} {\tt scram b -j32} \\
-        5. Fix grid\_control.cfg and run it. \\
-        6. Perform the actual tau roast program. \\ 
-        \hline
-        {\bf Version 2: Script}\\ \hline
-        {\tt setenv CMSSW\_BASE CMSSW\_5\_3\_11\_patch3} \\
-        {\tt cmsrel \$HOME/\$CMSSW\_BASE} \\
-        {\tt cvs co -r V03-09-23 PhysicsTools/PatUtils} \\
-        {\tt git clone \url{https://github.com/cms-ttH/BEAN.git}} \\
-        {\tt wget -r \url{http://nd.edu/~abrinke1/...}} \\
-        {\tt scram b -j32} \\
-        {\tt wget \url{http://pyyaml.org/download/pyyaml/PyYAML...}}\\
-        \#the experiment data is from HDFS \\
-        {\tt cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10}\\
-        {\tt cmsenv}\\
-        {\tt python setup.py install --user} \\
-        {\tt scripts/roaster data/generic\_ttl.yaml} \\ 
-        \hline
-        {\bf version 3: Formulated Script} \\ \hline
-        {\tt setenv CMSSW\_BASE CMSSW\_5\_3\_11\_patch3} \\
-        {\tt setenv {\bf GIT} \url{https://github.com}} \\
-        {\tt setenv {\bf PYYAML} \url{http://pyyaml.org}} \\
-        {\tt setenv {\bf ND} \url{http://nd.edu}} \\
-        {\tt cmsrel \$HOME/\$CMSSW\_BASE} \\
-        {\tt cvs co -r V03-09-23 PhysicsTools/PatUtils} \\
-        {\tt git clone \${\bf GIT}/cms-ttH/BEAN.git} \\
-        {\tt wget -r \${\bf ND}\url{/~abrinke1/ElectronEffectiveArea.h}} \\
-        {\tt scram b -j32} \\
-        {\tt wget \${\bf PYYAML}/download/pyyaml/PyYAML...}\\
-        \#the experiment data is from HDFS \\
-        {\tt cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10}\\
-        {\tt cmsenv}\\
-        {\tt python setup.py install --user} \\
-        {\tt scripts/roaster data/generic\_ttl.yaml} \\ 
-        \hline
-       {\bf Version 4: Fine-Grained Toolkit - Package}\\ \hline
-        {\tt setenv CMSSW\_BASE CMSSW\_5\_3\_11\_patch3} \\
-        {\tt setenv {\bf GIT} \url{https://github.com}} \\
-        {\tt setenv {\bf PYYAML} \url{http://pyyaml.org}} \\
-        {\tt setenv {\bf ND} \url{http://nd.edu}} \\
-        {\tt cmsrel \$HOME/\$CMSSW\_BASE} \\
-        {\tt cvs co -r V03-09-23 PhysicsTools/PatUtils} \\
-        {\tt git clone \${\bf GIT}/cms-ttH/BEAN.git} \\
-        {\tt wget -r \${\bf ND}\url{/~abrinke1/ElectronEffectiveArea.h}} \\
-        {\tt scram b -j32} \\
-        {\tt wget \${\bf PYYAML}/download/pyyaml/PyYAML...}\\
-        \#the experiment data is from HDFS \\
-        {\tt cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10}\\
-        {\tt cmsenv}\\
-        {\tt python setup.py install --user} \\
-        {\tt scripts/roaster data/generic\_ttl.yaml} \\ 
-        \hline
-    \end{tabular}
-    \caption{Scripts of each Solution}
-    \label{table:scripts}
-\end{table}
-
-\fi
-
-\section{Evolving the Artifact}
-
-It is clear that the artifact, as provided, is not in a suitable form
-for preservation.  While it might be technically possible to automatically
-capture the entire virtual machine and all of the connected filesystems,
-it would require 166.8TB of storage, which would be prohibitively expensive
-for capturing this one application alone.  Further, if multiple
-similar applications are preserved, we would miss the opportunity to identify
-common dependencies and store them once for multiple artifacts.
-A more structured approach to dependency management is needed.
-
-Figure~\ref{fig:version-evolution} shows how we have evolved this artifact
-through several stages which make it more suitable for preservation.
-In each step of evolution, we make the dependencies of the artifact
-more explicit and available for analysis and automated processing.
-As noted in the previous section, the original author provided us with
-prose instructions by email which we translated into an
-executable script.  The executable script has embedded in it
-a number of external identifiers such as URLs pointing to repositories
-and paths to networked filesystems.  As a general programming practice,
-embedding such constants into the middle of a program is unwise, and so
-we extract all of those identifiers and place them \emph{outside} the
-script in a \emph{dependency map} or just \emph{map} for short.
-The dependency map lists all of the external dependencies of the application, indicating
-the type, how they are accessed, and where they are currently located.
-The resulting script then simply refers to abstract file locations such
-as \verb$GIT$ and \verb$CVMFS$, while the map file indicates where they
-are currently located. If properly constructed, the script should not refer to any external
-resource unless it is indicated in the dependency map.  We call this idealized
-artifact an \emph{abstract script}.
-
-By extracting the dependencies into the dependency map,
-we introduce great freedom for the curator to move, transform, and otherwise
-manipulate the dependencies of the artifact without damaging the artifact itself.
-A Figure~\ref{fig:version-evolution} shows, it is straightforward for an
-automated tool to examine
-all of the dependencies in the map, download those that are missing,
-and then modify the map to point to the local copies of the dependencies.
-If we group the script, dependency map, and dependencies into a \emph{package},
-we now have a self-contained artifact that can be moved from place to place.
-In some cases, it may be safe to allow the dependency map to refer to 
-trusted remote repositories.  Whether this is advisable is a judgment that
-must be made by the user or the curator, taking into account the long-term
-stability of said repositories.
-
-However, only having the package and the dependency map is not enough. The successful execution of the application on the original machine also relies on the configuration of environment variables.
-We collected the environment variables of the original machine and transformed it into one executable script.
-If another researcher wants to repeat the application, this executable script will be first executed.
-The environment variables refer to the dynamic named values defined in the range of one computer, like \verb!$PATH! and \verb!$PYTHONPATH!.
-However, the dependency map refers to the actual storage location of path variables used in one abstract script. For example, the actual storage location of the path variable \verb!CVMFS! 
-is {\tt /data/cvmfs/grid.cern.ch}.
-
-\begin{figure}
-\centering
-\includegraphics[width=.5\textwidth]{solution3.eps}
-\caption{Relationship of Roles}
-\label{fig:solution3}
-\end{figure}
-
-The relationship of different roles involved in the application preservation and
-reproduction is shown in Figure~\ref{fig:solution3}.  The original author uses the packaging utility to generate the package for one application.
-Then the package, together with
-its map file and description file will be published. When
-another researcher wants to repeat the application, one copy of the package will be downloaded into the new machine and the application can be repeated.
-
-When we try to repeat one application on one new machine, one map file is necessary for the relocation of the data access targets, as
-show in Figure~\ref{fig:version-evolution}. 
-The map file clearly defines the real location of each dependency in the format of dependency variables - the real location of dependency variable {\tt GIT} is \path{/data/git/cms-ttH} and the real location of dependency variable {\tt CVMFS}
-is {\tt /data/cvmfs/grid.cern.ch}.
-The script only refers to the dependency variables defined in the map file.
-This design decouples the application script and the actual data access targets, which minimizes the impact of the evolution of different data dependencies
-and ensures the transparent access.
-The modification of the package only introduces the minimal changes of the map file on the client side.
-
-This basic approach to dependency management is a step in the right direction
-for dependencies that are \emph{explicit} and \emph{external} to the
-user's native execution environment.  However, it leaves two other problems unsolved.
-
-First, the basic approach requires that someone be \emph{aware} of the dependencies,
-whether it be the end user, the system administrator, or the archive curator.
-It seems reasonable to expect the user to be aware of a large dependency mentioned in a top-level script.
-But, oftentimes the dependency is embedded invisibly deep within the software stack,
-or is connected to the machine by the local system administrators.  No single party
-is likely to have complete information about all of the dependencies.
-Second, the basic approach assumes that the entire dependency is actually
-consumed by the artifact.  As we have suggested above (and will show below),
-this sort of program often only consumes a small fraction of what it does declare
-as a dependency.
-
-To address both of these problems, users and curators alike need tools that
-will automatically observe the dependencies of complex applications, to
-facilitate automatic and efficient preservation.
-
-\section{Measuring Dependencies}
-
-\begin{figure*}
-\centering
-\includegraphics[width=.8\textwidth]{workflow-parrot.eps}
-\caption{Workflow of The Fine-Grained Dependency Management Toolkit Based on Parrot}
-\label{fig:workflow-parrot}
-\end{figure*}
-
-We have developed a prototype tool to assist in the measurement and preservation
-of implicit dependencies for complex applications.
-We use Parrot~\cite{thain2005parrot} to explicitly record all
-of the files accessed by our example application, allowing us to observe how
-much of each external dependencies is used, and what local resources are implicitly used.
-Using this information, we create a \emph{reduced package} which contains
-only the files actually used by the application.
-
-Parrot is a virtual filesystem access tool which has been used to attach
-existing programs to a variety of remote I/O systems, such as HTTP, FTP, and CVMFS.
-It works by trapping an application's system calls through the Linux {\tt ptrace} debugging
-interface, and then replacing them with the desired I/O operations.  Parrot is already used
-in the high energy physics community with applications like TauRoast specifically to 
-provide access to the CMSSW software distribution via the CVMFS distributed file system.
-We made small modifications to Parrot to record a \emph{namelist} which lists all 
-of the files that an application actually accesses.
-
-Figure~\ref{fig:workflow-parrot} illustrates the measurement process.
-The starting point of this toolkit is one successful execution of the application on the native machine.
-First, we execute the actual data analysis script under Parrot to generate the namelist.
-Then, using the namelist, we generate a package containing all the necessary data
-and software for one analysis program. When another
-researcher wants to repeat the program, he only needs to obtain the package and
-execute the actual analysis program inside the package.
-
-For one execution of \emph{TauRoast}, the generated namelist includes 132,047 accessed filenames,
-along with the system calls used to access the file, such as {\tt open}, {\tt stat}, {\tt read}, etc.
-With duplicate filenames removed, the list is reduced to 67,168 files.
-Many of those entries do not exist, because they reflect attempts
-by the application to search for programs and libraries in multiple places.
-Only 22,068 entries reflect existing files or directories.
-
-The packaging tool iterates over each item of the filename list, determines the process
-mode and replication degree according to the file type (common files,
-directories, symbolic links) and the system call type, generates one package
-containing the dependencies, and summarizes the contents of the package
-as shown in Table~\ref{table:package-info}.  To the extent possible,
-the filesystem structure of the original environment is preserved.
-
-We considered several approaches to constructing the package.
-In a {\bf shallow copy}, we only copied the individual files in the namelist,
-creating only parent directories for each.  Where a directory was listed,
-we created the directory and populated it with empty files as placeholders
-to facilitate a directory listing.  In a {\bf medium copy}, we copied the
-individual files as before.  Where a directory was listed, we created
-the directories and copied the contents of the files in that directory,
-one level deep.  A {\bf deep copy} would duplicate all directories recursively,
-but this would have resulted in TB-sized packages, so we did not consider
-it further.
-
-Parrot is required to re-run the packaged artifact, in order to force
-the packaged files to appear to exist in their original locations.
-To this end, the packaging tool creates a \emph{file map} which maps
-the logical names of the files to their current physical locations, as shown in Table~\ref{table:map-file}.
-Parrot reads the file map and redirects system calls at run-time to achieve the desired effect.
-As the example suggests, special device files such as {\tt /proc} and {\tt /dev}
-are not incorporated into the package but are instead accessed natively.
-
-\begin{table}
-    \centering
-    \begin{tabular}{ll}
-    \hline
-    \bf Path used in Program & \bf Actual Location \\ \hline
-    {\tt /} & {\tt /tmp/package-hep} \\ \hline
-    {\tt /tmp/package-hep} & {\tt /tmp/package-hep} \\ \hline
-    {\tt /dev} & {\tt /dev} \\ \hline
-    {\tt ...} & {\tt ...}\\ \hline
-    \end{tabular}
-    \caption{Structure of Map File}
-    \label{table:map-file}
-\end{table}
-
-\begin{table}
-    \centering
-    \begin{tabular}{rrr}
-\hline
-                    & \bf Shallow Copy & \bf Medium Copy\\
-\hline
-    Whole Files    & 1632         & 15642\\ 
-\hline
-    Empty Files    & 14273        & 263\\
-\hline
-    Directories    & 1549         & 1549\\ 
-\hline
-    Symbolic Links & 4614         & 4614 \\
-\hline
-    \bf Total Size & \bf 21GB     & \bf 28GB \\ 
-\hline
-    \end{tabular}
-    \caption{Package Information}
-    \label{table:package-info}
-\end{table}
-
-\subsection{Tracking of Network Dependencies}
-
-\begin{figure}
-\centering
-\includegraphics[width=.6\textwidth]{git-syscall.eps}
-\caption{Exec Syscalls of a git command}
-\label{fig:git-syscall}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=.6\textwidth]{http_packet.eps}
-\caption{HTTP Request and Response}
-\label{fig:http_packet}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=.6\textwidth]{url_redirection.eps}
-\caption{An Example of URL Redirection}
-\label{fig:url_redirection}
-\end{figure}
-
-All the dependencies of one program can be divided into three categories: local file system (e.g., /usr, /lib and /lib64), remote file systems which can be mounted as local directories (e.g., /cvmfs and /hdfs), and other remote network dependencies (e.g.
-http, https and ssh).
-Through utilizing ptrace to trap each file-relevant system call used by a program, the first two categories of dependencies can be collected. 
-Motivation of tracking network dependencies: Linkrot is a common and great threat to the preservation of scientific applications.
-A URL which works normally today may be unavailable permanently.
-A method which can help the scientists figure out all the network dependencies of their applications provides the chance to evaluate the stability of each network dependencies and preserve the unstable network resources before linkrot happens.
-One direct solution to track the third category of dependencies is to utilize ptrace to check each exec system call used by a program and record each network-relevant executable and its parameters.
-However, an executable may create one or more child processes to finish some tasks, and a child process may create their own children processes.
-Figure~\ref{fig:git-syscall} shows all the processes created by a git command.
-A process with PID 998 is created to clone a remote git repository into local machine, which totally has 6 child processes.
-Moreover, a network-relevant executable name collection is necessary to identify network dependencies.
-The diversity of network-relevant executables and the large process tree generated for a network executable make this solution infeasible.
-
-Another solution to track network dependencies is to track the network sockets.
-The user process communicates with the network protocol stacks in the kernel through the network socket layer user interface on Linux.
-From the process tree shown in the above figure, the process with PID 1000 responds to create a socket, connect to a DNS server, send a DNS request packet to the DNS server and receive a DNS response packet from the DNS server.
-The information gained from the network socket tracking can be divided into three categories.
-\begin{itemize}
-\item The information of network sockets used to communicate with remote network dependences (through socket and connect system calls) can be used to figure out the port number, service name (such as, http, https, and ssh), socket type (stream and datagram),  and the domain type (inet and inet6).
-\item The contents of DNS packets can be used to figure out the hostname and IP address of each remote network dependency. 
-\item As for applications based on http protocol, all the http requests and responses can be seen, as shown in Figure~\ref{fig:http_packet}.
-However, as for applications based on https and ssh which encrypt network data using TLS/SSL, tracking network data on the socket level can only see the encrypted data.
-\end{itemize}
-
-The results of tracking network sockets used by a program involves two categories of network resource redirections, dns-level hostname redirection and website-level url redirection. 
-\begin{itemize}
-\item dns-level hostname redirection: Each DNS packet includes five parts, header, question, answer, authority, and additional.
-A DNS response packet with the type CNAME has multiple answers.
-For example, the DNS response packet which tries to resolve {\tt www3.nd.edu} includes two answers.
-The first answer provides an alias of {\tt www3.nd.edu}, {\tt www-vip.cc.nd.edu}, and the second answer maps the alias to the IP address.
-{\tt www3.nd.edu} CNAME {\tt www-vip.cc.nd.edu}
-{\tt www-vip.cc.nd.edu} A {\tt 129.74.12.151}
-The CNAME-type DNS packets leave us a question, among the hostname used by the user, the alias(es), the IP address, what should we preserve?
-\item website-level url redirection: Website-level url redirection happens when a website updates its location and still want their old users access their resources using the old url.
-Figure~\ref{fig:url_redirection} illustrates the url redirection between {\tt \url{www3.nd.edu/~ccl}} and {\tt ccl.cse.nd.edu}.
-Except for the difference of hostnames, the application layer protocols used by the old-version website and the new-version website is also different: the old website provides services through the https protocol, while the new website provides services through the http protocol.
-\end{itemize}
-
-The usage of https protocol makes detecting of website-level url redirections through tracking system calls more difficulty and even impossible.
-All the application data will be encrypted at presentation layer through the TLS/SSL protocol, which is initialized at the session layer and works at the presentation layer.
-
-\section{Evaluation}
-
-We evaluated the correctness of the reduced package and the overhead of generating the package.
-To do this, the application was repeated with the help of \emph{Original Script} (as shown in Figure~\ref{fig:version-evolution}) on the original machine. 
-Then one \emph{reduced package} was generated and verified with the help of Parrot on the original machine.
-
-Then, two different virtual machines (VM) - one VM from the Notre Dame Cloud Platform based on KVM and one VM from the Amazon EC2 Platform based on Xen, were employed to further verify the correctness of the reduced package.
-
-We first repeated the example from scratch using the Script translated from the original email on the original machine and counted the time consumption and data size. 
-Then based on the successful execution of Original Script, we evaluated Reduced Package - one package containing necessary dependencies is generated, and then the time consumption and data size is analyzed.
-
-To measure time consumption, we counted the time used to obtain remote software dependencies, build the environment, and analyze the dataset.
-We also counted the time used to obtain the namelist and to generate the package.
-To measure data size, we can easily figure out the size of each data and code source inside the package under Reduced Package.
-Original Script does not support mining of implicit dependencies.
-As for remote sources, we can figure out the named size through the analysis script.
-However, it is hard to figure out the named size of each local source.
-Instead, we only knew that total size of each file system is very large.
-
-Table~\ref{table:time-2nd3rd} shows the execution time comparison between
-Original Script and Reduced Package.
-Reduced Package is faster than Original Script, because all the software copied into the package has been compiled and the Software Acquisition stage is not necessary.
-and all the environment building only takes 4 seconds,
-We were surprised that Reduced Package even reduces the actual analysis time. 
-The reason for this is that data is obtained through accessing HDFS in Original Script, but is copied into the package in Reduced Package.
-This localization of experimental data speeds up the data analysis process, resulting the actual analysis time reducing from 20 minutes to 13 minutes.
-
-\begin{table}
-    \centering
-    \begin{tabular}{lrr}
-    \hline
-    \bf Task Category & \bf Original Script & \bf Reduced Package \\ \hline
-    Obtain Namelist & N/A & 28min 28s \\ \hline
-    Generate Package & N/A & 85min 51s \\ \hline
-    Software Acquisition & 8min 11s & N/A \\ \hline
-    Environment Build & 5min 49s  & 4s \\ \hline
-    Analysis Code & 20min 31s & 13min 04s \\ \hline
-    \end{tabular}
-    \caption{Execution Time Comparison between Original Script and Reduced Package}
-    \label{table:time-2nd3rd}
-\end{table}
-
-Table~\ref{table:time-2nd3rd} also illustrates the time used to
-obtain the namelist and to generate the package. 
-The time used for these two steps is longer than the execution time,
-because each filename of the list, together with its system call type, needs to be checked, and the structure of each directory item must be maintained.
-However, 
-this is only done once.
-Once the package is
-generated, many users can directly obtain the package and repeat the application 
-separately.
-
-Table~\ref{table:size-original-real} on page 2 illustrates the total size, named size in the example and actually used size of each remote source (the first 4 items) and local source (the remaining 5 items).
-The third column corresponds to the data size of Reduced Package and can be easily figured out, because all the necessary data has been copied into the package.
-Original Script does not support measuring implicit dependencies.
-As for remote sources, we can figure out the named size through the analysis script.
-However, it is hard to figure out the named size of each local source.
-Instead, we only knew that total size of each file system is very large.
-
-\begin{table}
-	\centering
-	    \begin{tabular}{llrrr}
-	        \hline
-	        \bf Name & \bf Location & \bf Total & \bf Named & \bf Used \\ 
-	        \hline
-	        CMSSW code     & CVS & 88.1GB & 448.3MB & 6.3MB\\ \hline
-	        Tau source       & Git & 73.7MB & 73.7MB & 6.7MB \\ \hline
-	        PyYAML binaries    & HTTP & 52MB & 52MB & 0KB \\ \hline
-	        .h file       & HTTP& 41KB & 41KB & 0KB \\ \hline \hline
-	        Ntuples data    & HDFS& 11.6TB & N/A& 20GB \\ \hline
-	        Configuration & CVMFS & 7.4GB & N/A & 103MB \\ \hline
-	        Linux commands & localFS & 110GB &  N/A & 68.4MB \\ \hline     
-	        HOME dir& AFS &12GB & N/A & 32MB\\ \hline
-	        Misc commands & PanFS & 155TB & N/A  & 1.6MB \\ \hline
-	        Total      &    & 166.8TB            & N/A & 21GB \\ \hline
-	    \end{tabular}
-	    \caption{Data and Code Used by Tau Roast}
-	    \label{table:size-original-real}
-\end{table}
-%	\begin{tablenotes}
-%	      \small
-%	      \item The first column illustrates the total size of each data and software source; 
-%	            the second column illustrates the size of the named files from each source;
-%	            the third column illustrates the size of actually used data from each source.
-%	            N/A denotes it is hard to figure out the named size of implicit dependencies directly.        
-%	    \end{tablenotes}
-
-To further verify the correctness of Reduced Package on other machines, two different machines are employed -
-one virtual
-machine~\cite{goldberg1974survey} from the Notre Dame Cloud Platform based on KVM sharing the same kernel version with the original machine,
-and one virtual machine from  the Amazon EC2~\cite{amazon2010amazon} Platform based on Xen.
-
-Table~\ref{table:config-vm} illustrates the configuration of 
-each machine and the execution time of the application on each machine.
-All the machines adopt the x86\_64 hardware platform and Linux kernel.
-Both of the two VMs repeated the application with the help of the package generated on the original machine successfully.
-The execution time on one machine greatly depends on its hardware configuration.
-
-\begin{table}
-    \centering
-    \begin{tabular}{lrrrr}
-    \hline
-    \bf Machine Type & \bf Distro Version & \bf CPU Cores & \bf Mem (GB) & \bf Execution Time \\ \hline 
-    Original Machine &  Red Hat 5.10 & 64 & 125 & 13min 04s\\  \hline
-    KVM (Notre Dame) & CentOS 5.10 & 4 & 2 & 21min 38s\\ \hline
-    Xen (EC2) & Red Hat 5.9 & 16 & 60.5 & 13min 30s\\ \hline
-    \end{tabular}
-    \caption{Evaluation of Different Machines}
-    \label{table:config-vm}
-\end{table}
-
-In summary, we demonstrate that the application can be repeated with the help of the reduced package on one different machine with the required hardware architecture and OS kernel version.
-%*****hmeng-doubt:Another reason for the packaging utility is that not all the data and software generated by the second version script is used during the the actual data analysis.
-The packaging utility can help us find out the optimal subset of data and software involved in one actual data analysis.
-%*****hmeng-doubt: this point is not the motivation. but one achievement comes together. out of imagination.
-
-\begin{figure}
-\centering
-\includegraphics[width=.6\textwidth]{preservation-integration.eps}
-\caption{Preserving Multiple Artifacts}
-\label{fig:Preservation integration}
-\end{figure}
-
-\section{Open Problems}
-
-Figure~\ref{fig:Preservation integration} shows the rough information
-architecture of the archive that we imagine for complex
-scientific software like TauRoast.
-Each artifact to be preserved is a package that consists of a top-level
-script to invoke the software, a dependency map, and the dependencies
-themselves, which may be external to the original program.  The artifacts
-are then ingested into the archive, where shared dependencies are stored
-only once.  In cases where an artifact has a dependency on a trusted
-(or very large) remote archive, the dependency may simply be tracked
-. A researcher that wishes to reproduce a given
-result need only refer to the unique identifier of the artifact, and will
-be able to automatically extract all of the dependent components of
-that artifact.
-
-For example, in Figure~\ref{fig:Preservation integration} Script 1 depends on items A, B, and C.
-Items A and B are ingested into the archive, where B is shared with Script 2.
-Item C is stored in another trustworthy repository and is tracked rather than ingested.
-When Script 1 is exported from the repository, items A and B are exported along with it, while C can be copied or remain remote, according to the end user's choice.
-
-As simple as that picture appears, there are a number of problems that must be solved to get there:
-
-{\bf Measure the Mess or Force Cleanliness?}  Two radically different approaches to dependency tracking are possible.
-The first is to allow end users complete freedom to construct their environment as desired, then \emph{measure} what items were actually used.
-As we have shown, this is possible, but has significant overheads and does not fully preserve the structure or intent of the end user.
-The second approach is to \emph{force} users to work in a clean environment in which no resource can be used until a proper dependency has been declared.
-This ensures that all dependencies are known in advance (and made explicit to the end user) but places a variety of restrictions on the user's daily work, and may prevent creative approaches that do not fit within the curator's view of how programs should be structured.
-Whether end users will accept the inconvenience of forced cleanliness for the benefits of reproducibility can only be discovered through experiment.
-
-{\bf Granularity of Dependencies.}  Dependencies could be handled
-at many different levels of granularity.  In this work, we have shown
-how they can be handled at the level of entire repositories or individual files.
-Other possible choices might include intermediate-sized software packages
-(like RPM) or in the case of experimental data, even portions of individual large files.  Clearly, a larger granularity will result in 
-simpler dependency maps, and more wasted space; smaller granularity results
-in complex dependency maps and less wasted space.  A hybrid solution may
-be able to combine both by storing large granularity dependencies, but
-selecting sub-items out of objects when efficiency demands it.
-
-{\bf Scope of Reuse.}  We have presented the data preservation
-problem as primarily one of accurate reproduction: if a result depends
-on running program X, we must be able to run exactly X again.  However,
-the goal of scientific reproducibility is rarely limited to running
-\emph{precisely} what a predecessor did. Often, the objective is to
-change a parameter or a data input in order to see how the result is affected.
-To that end, the preservation system must capture enough of the surrounding
-material to permit modifications to succeed.  From this perspective,
-a larger granularity of preservation is desirable.  A better understanding of
-how end users will consume preserved software will help to shape how
-software is preserved in the first place.
-
-{\bf Dependency Detection.}  If we allow users to work in uncontrolled
-environments, then we must have better methods for understanding the dependencies  of existing programs.  At first, we relied on an expert reader to examine
-the user's script and extract the dependencies.  This is clearly
-not a scalable approach.  We then demonstrated an automated method of observing
-what individual files are accessed by a program. However, this does
-not cover all types of dependencies, particularly those that are networked.
-More sophisticated observation techniques could infer higher-level information,
-such as the RPM package names of the files accessed, the URLs of remote
-repositories named throughout the program, or even the addresses and names of networked dependencies like databases and filesystems.
-
-{\bf Source, Binary, or Both?}  A science archive might choose to retain
-the source code of an artifact or the binary code that can actually run in a given environment.
-While conventional wisdom suggests that access to source code is critical for the long term
-survival and evolution of a piece of software, it also requires the maintenance of an enormous
-amount of supporting software in the form of compilers, linkers, and supporting libraries for
-the target platform.  Rebuilding all of these for every invocation of an artifact is
-likely to have excessive cost.  We suggest that a realistic repository will have to
-maintain \emph{both}: the source describes the ultimate meaning of the code, but
-the binary is an important performance cache, a backup if the compiler toolchain should
-fail to be preserved, and a checksum to ensure that a source artifact was rebuilt correctly.
-
-\section{Related Work }
-
-Generally, there are three approaches to preserve software environment:
-hardware preservation, migration and emulation.  Hardware
-preservation preserves the original software and its original operating
-environment. 
-Software migration technique~\cite{cifuentes1996binary,mancl2001refactoring} was used to facilitate running software on new machines.
-However, migration often involves the re-compiling and re-configuring
-the source code to accommodate a new hardware platform and software environment.
-Emulation recreates the original software and hardware environment by
-programming future platforms and OSs. One common solution to implement this is
-virtual machine. According to the usage and emulation degree of the real
-machine, virtual machine can be divided into system virtual machine and process
-virtual machine. 
-The working principle, design principle and
-performance evaluation of system virtual machine were illustrated in~\cite{goldberg1974survey, smith2005architecture}. 
-The
-functionality of system VM to support different guest operating systems was illustrated in~\cite{barham2003xen,kivity2007kvm,rosenblum1999vmware}.
-F. Esquembre~\cite{esquembre2004easy} illustrated how JVM, one process virtual machine, can expedite the creation of
-scientific simulations in Java. 
-The pros and cons of these three approaches were discussed in~\cite{matthews2009towards,phelps2005no,hong2010software}.
-
-The preservation of computing environment and software environment was treated as one entirety in~\cite{matthews2009towards,phelps2005no,hong2010software}.
-However, frequently changing experiment software makes the maintenance of the preserved experimental environment very complex.
-CernVM~\cite{buncic2010cernvm} treated them as two different categories.
-The preservation of computing environment is implemented with CernVM, and the preservation of software environment is based on a CernVM filesystem(CVMFS) specifically designed for efficient software distribution.
-
-The importance of preserving software in source code format was emphasized in~\cite{zabolitzky2002preserving,castagne2013consider}. 
-However, CVMFS~\cite{buncic2010cernvm} published pre-built and configured experiment software releases to avoid the time-consuming software building procedure.
-
-Attempts from different perspectives to facilitate the reproduction of scientific experiments utilizing a preserved software library have been made. 
-The software distribution mechanism over network was discussed in~\cite{compostella2010cdf, blomer2011cernvm}.
-J.
-R.
-Rice et al.~\cite{rice1996scientific} made the reproduction process easier through the integration of user interface, scientific software libraries, knowledge base into problem-solving environment.
-S. R. Kohn et al.~\cite{kohn2001divorcing} tried to enable the creation and distribution of language-independent software library by addressing language interoperability.
-a scalable, distributed and dynamic workflow system for digitization processes was proposed in~\cite{schoneberg2013scalable}.
-A distributed archival network was designed in~\cite{subotic2013distributed} to facilitate process-oriented automatic long-term digital preservation.
-M. Agosti et al.~\cite{agosti2012envisage} aimed to help non-domain users to utilize the digital archive system developed for domain experts.
-
-Current mechanisms of preserving scientific experiments assume that all the data and software mentioned in the experiments are necessary for the reproduction of the experiments.
-However, this is not always right.
-In some cases, the original author may leave additional code referring to irrelative data and software in the program.
-One mechanism, which can figure out the absolutely relevant data and software of one experiment, is important for both the preservation and reproduction of scientific experiments.
-
-B. Matthews et al.~\cite{matthews2008significant} introduced one conceptual framework for software preservation from several case studies of software preservation.
-One tool to capture software preservation properties within a software environment was designed in~\cite{matthews2010framework} through a series of case studies conducted to evaluate the software preservation framework.
-L. R. Johnston et al.~\cite{johnston2014workflow} proposed one overall data curation workflow for 3-5 case studies of preserving research data.
-Two case studies~\cite{borgman2012data} were conducted to figure out the properties of data to be reused in the future.
-
-\section{Postscript}
-
-We began this work in late 2013, generating a reduced package for \emph{TauRoast} based
-on the configuration of a standard machine at Notre Dame at the time.  In the course
-of writing this paper in spring 2014, almost everything about the computing environment
-changed: the operating system was upgraded, a new version of CMSSW was released, and
-our local HEP users switched from using CVS to CVMFS for accessing CMSSW.
-The original script provided by the author failed to run on the same machine.
-But, the reduced package we created three months earlier in the old environment
-worked just fine on the new machine.
-
-\section*{Acknowledgments}
-
-This work was supported in part by National Science Foundation grants PHY-1247316 (DASPOS), 
-OCI-1148330 (SI2) and PHY-1312842.
-The University of Notre Dame Center for Research Computing scientists and engineers provided critical technical assistance throughout this research effort.
-
-Copyright (C) 2014 The University of Notre Dame
-
-This work is licensed under the Creative Commons Attribution 4.0 License.
-
-\bibliographystyle{plain}
-\bibliography{cclpapers,this}
-
-\end{document}

### 2015-01-06 measure.tex
Put each section into a separate tex file

--- 2014-12-18 paper.tex
@@
-\documentclass[procedia]{easychair}
-\usepackage{url}
-\usepackage[flushleft]{threeparttable}
-\hyphenation{resour-ces}
-\hyphenation{approac-hes}
-\hyphenation{har-der}
-\hyphenation{spe-cifically}
-\makeatletter
-\def\@copyrightspace{\relax}
-\makeatother
-
-\title{A Case Study in Preserving a High Energy Physics Application}
-
-% \titlerunning{} has to be set to either the main title or its shorter
-% version for the running heads. When processed by
-% EasyChair, this command is mandatory: a document without \titlerunning
-% will be rejected by EasyChair
-
-\titlerunning{A Case Study in Preserving a High Energy Physics Application}
-
-\author{
-	Haiyan Meng\inst{1}
-\and
-	Matthias Wolf\inst{2}
-\and
-	Douglas Thain\inst{3}
-}
-\institute{
-	Department of Computer Science and Engineering,
-	University of Notre Dame,
-	Notre Dame, Indiana, USA
-	\email{hmeng@nd.edu}
-\and
-	Department of Physics,
-	University of Notre Dame,
-	Notre Dame, Indiana, USA
-	\email{mwolf3@nd.edu}
-\and
-	Department of Computer Science and Engineering,
-	University of Notre Dame,
-	Notre Dame, Indiana, USA
-	\email{dthain@nd.edu}
-}
-
-%  \authorrunning{} has to be set for the shorter version of the authors' names;
-% otherwise a warning will be rendered in the running heads. When processed by
-% EasyChair, this command is mandatory: a document without \authorrunning
-% will be rejected by EasyChair
-
-\authorrunning{Meng, Wolf and Thain}
-
-\begin{document}
-
-\maketitle
-
-\keywords{}
-
-\begin{abstract}
-\it The reproducibility of scientific results increasingly
-depends upon the preservation of computational artifacts.
-Although preserving a computation to be used later sounds
-easy, it is surprisingly difficult due to the complexity
-of existing software and systems.  Implicit dependencies,
-networked resources, and shifting compatibility all conspire
-to break applications that appear to work well.  To investigate
-these issues, we present a case study of a complex high energy
-physics application.  We analyze the application and attempt
-several methods at extracting its dependencies for the purposes
-of preservation. 
-We propose one fine-grained dependency management toolkit to preserve the application and demonstrate its correctness in two different environments - one virtual machine from the Notre Dame Cloud Platform and one virtual machine from the Amazon EC2 Platform.
-We report on the completeness, performance,
-and efficiency of each technique, and offer some guidance for
-future work in application preservation.
-\end{abstract}
-
-% A category with the (minimum) three required fields
-%\category{H.4}{Information Systems Applications}{Miscellaneous}
-%A category including the fourth, optional field follows...
-%\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]
-
-%\terms{Theory}
-
-\section{Introduction}
-
-Reproducibility is a cornerstone of the scientific process~\cite{borgman2012data}.
-In order to understand, verify, and build upon previous work,
-one must be able to first recreate previous results by applying
-the same methods. Historically, reproducibility has been
-accomplished through painstaking detailed documentation recorded
-in lab notebooks, which are then summarized in peer-reviewed publications.
-But as science increasingly depends on computation,
-reproducibility must also encompass the environments, data, and software
-involved in each result~\cite{zabolitzky2002preserving}. It is widely recognized that informal
-descriptions of software and systems -- although common -- are insufficient
-for reproducing a computational result accurately.
-A more automated and comprehensive approach is required.
-
-The reproduction of a computation has three broad components,
-each of which suggests somewhat different approaches:
-
-\begin{itemize}
-\item The {\bf computing environment}, consisting of the basic hardware and the operating system which can be preserved as physical artifacts or as a combination of virtual machine monitors (hardware) and virtual machine images (operating system)~\cite{matthews2009towards}.
-\item The {\bf scientific data} to be analyzed has historically received the most attention for curation.
-In a large, well-organized project, it may be stored in a  data repository or database management system, with associated documentation and a curation strategy.
-In a small effort, it could simply be a handful of files.
-\item The {\bf software environment} includes the source code, binaries, scripts, configuration files, and everything else needed to execute the desired code.
-As with data, the software could be drawn from a well-managed software repository, or it could be a handful custom scripts that exist in the user's home directory.
-\end{itemize}
-
-In a very abstract sense, reproducing a computation is trivial.
-Assuming a computation is deterministic, one must simply
-preserve all of the inputs to a computation, then re-run
-the same code in an equivalent environment, and the same result
-will be produced.  For a small custom application on a modest
-amount of data, this could be accomplished by capturing the
-complete environment,
-data, and software within a single virtual machine image,
-and then depositing the virtual
-image into a curated environment.  The publication could
-then simply refer to the identifier of the image, which the
-interested reader can obtain and re-use. This approach has
-been used to some success with systems~\cite{castagne2013consider}.
-\footnote{Of course, we are glossing over the problem that hardware
-architectures and virtual machines also change, so one must also
-preserve the VMM software necessary to run the image.  The VMM itself
-depends on a software environment which must also be preserved.
-A long-term preservation system might end up running a whole
-stack of nested virtual machines in order to provide the desired
-environment! }
-
-However, this simple approach is not sufficient for large applications
-that are run in complex environments.
-
-\begin{itemize}
-\item There may be {\bf implicit dependencies} on items that are
-not apparent to the end user.  For example, they may understand that
-they rely on a particular data analysis package, but would have
-no reason to know that the package has further dependencies on
-other libraries and configuration files.  Or, they may know that
-the computation only runs correctly on a particular machine, but
-not know this is because it relies on a filesystem that
-is mounted only on that machine.
-
-\item The {\bf granularity} of the dependencies may not be well understood.
-For example, the user may understand that a computation depends upon
-a data collection that is 1TB in overall size, but not have detailed
-knowledge that it only requires three files totalling 300MB out of that
-whole collection.
-
-\item There may be dependencies upon {\bf networked resources} that
-are inherently external to the system, such as a database, a code
-repository~\cite{cms2006cmssw}, or a scalable filesystem~\cite{blomer2011cernvm}.  For such resources, it
-must be decided whether the dependency will simply be noted, or if it
-must be incorporated whole or in part.
-
-\item Where {\bf common dependencies} are widely used, it may be inefficient or
-impossible to store one copy of each dependency for each archived object.
-Some form of sharing or de-duplication is necessary in order to keep
-the archive to a reasonable size.
-\end{itemize}
-
-We do not claim to have solved these problems in any comprehensive
-way.  Rather, our aim in this paper is to highlight the scope
-of the problems by presenting a case study of one complex application.
-The application is presented to us
-first in the form of an email that describes in prose how to install
-the software and run the analysis.  We perform several successive
-refinements to convert it into an executable and preservable object.
-We then develop techniques for reducing the size of the dependencies
-that are necessary for the object to function, and we demonstrate
-the preserved object functioning correctly in three different
-physical and cloud environments.
-We describe how each of these techniques may interact with
-a future archive of preserved software artifacts, and conclude with
-some reflections on the challenges of preservation and advice for future efforts.
-
-\if 0
-Section 2: Overview of Application
-    CMS/LHC introduction.
-    Data sources and reduction of size.
-    Code sources and reduction of size.
-    Prose observations about the script.
-        Uses multiple repos that change over time, with varying level of stability.
-        Low selectivity from the larger repos
-        Significant initialization time to collect everything.
-        Incidental infrastructure tools versus essential objects.
-        Some dependencies were surprising.
-    Figure: Diagram of app with both code and data sources.
-    Table: Show all code and data sources and size within one table.
-
-Section 3: Preservation Strategies
-    Figure: Show app in four stages:
-        Single email.
-        Script with embedded references to dependencies.
-        Script with map file that refers to external dependencies.
-        Script with map file that refers to preserved dependencies.
-
-    Transform to more suitable format that expresses dependencies.
-
-    Incorporate into archive, saving deps and map file.
-
-    But, how to get the dependencies?
-
-    Three strategies:
-        Original - Unmodified application run in original environment.
-        Coarse-Grained - Capture deps at large granularity -- whole filesystems and repositories.
-        Fine-Grained - Capture deps at a fine granularity -- individual files actually used.
-
-    Coarse-Grained Method (Copy Repositories)
-        First, determine dependencies
-        Express app as script + map file
-        Packaging tool downloads deps, rewrites map file.
-        To run packaged application, obtain map, download
-
-    Fine-Trained Toolkit (Parrot)
-        Tool to detect dependencies (Parrot)
-        Express app as script + map file
-        Packaging tool downloads deps, rewrites map file.
-        To run package application, run again with Parrot.
-
-Section 4: Evaluation
-
-    Table: Time and size of preserving using each of the two techniques.
-
-    Explain why the techniques show different performance.
-
-    Is one technique more effective than the other?  Why?
-\fi
-
-\begin{figure}[t]
-\centering
-\includegraphics[width=.5\textwidth]{data-code-size.eps}
-\caption{Inputs to Tau Roast}
-\label{fig:data-code-size}
-\end{figure}
-
-\section{Overview of Tau Roast}
-
-Within the ongoing investigation of the Higgs boson at the CMS
-detector, part of the LHC at CERN~\cite{collaboration2008cms}, the Higgs production in association
-with two top quarks allows measuring the Higgs coupling strength to
-top quarks~\cite{chatrchyan2013search}.  As the Higgs boson is too short-lived to be detected
-itself, it has to be reconstructed from its decay products.
-
-The application which is the study of this paper is called \emph{TauRoast}.
-It searches for cases where the Higgs boson decays to two tau leptons.
-Since the tau leptons are very short-lived, they are not observed directly, but by the particle decay products 
-that they generate.  So, the analysis must search for detector
-events that show a signature of decay products compatible with both hadronic tau and top decays.  Properties of such events are used to distinguish
-the events of interest (Higgs decays) from all other events and
-are also used in further statistical analysis.
-
-Figure~\ref{fig:data-code-size} shows that both the code and data
-that form \emph{TauRoast} are drawn from large repositories through
-multiple steps of reduction.  A preservation strategy must weigh
-whether to store the large repositories completely, the fragments
-used by an artifact, or something in between.
-
-{\bf Code Sources.} Like many scientific codes, the central algorithm
-of \emph{TauRoast} is expressed in a relatively small amount of
-custom code developed by the primary author.  But, the code cannot
-run at all without making use of an enormous collection of software
-dependencies.  Some of these dependencies are standard to operating
-systems worldwide, some are standardized across the entire high-energy
-physics field, some are particular to small collaborative groups,
-and a few are very specific to a single researcher.
-
-The largest of these repositories is the CMS Software Distribution (CMSSW)~\cite{cms2006cms},
-a carefully-curated selection of software packages which is distributed
-in several forms.  Historically, components of CMSSW were obtained by checking components
-of the source out of CVS (CMSSW source codes were moved from CVS to git recently), or by installing a complete binary package on a shared
-filesystem within an HPC center.  In recent years, distribution has moved to
-an on-demand delivery system known as CVMFS~\cite{blomer2011cernvm}, which
-provides a filesystem interface that transparently accesses a remote repository.
-The content of CMSSW is managed very carefully by a centralized team whose main goal
-is to ensure that the current version of the software operates correctly
-on the operating systems and architectures currently in use.  However,
-preservation is not a specific objective of the system, and so there is
-no particular guarantee that old versions of CMSSW will continue to
-operate indefinitely.
-
-CMSSW contains many different tools, libraries, and utilities.
-No single code uses anywhere close to all of these.
-But, because it is widely used within the experimental researchers, it is common for users to simply expect that a particular version of the entire repository is available.
-
-{\bf Data Sources.}
-The CMS collaboration provides end-users with a pre-processed
-and reduced data format, AOD~\cite{holtman2001cms}, containing information for events, i.e.,
-proton-proton collisions with a signature of interest, in the form of
-reconstructed particles.  This format is based on the RAW output of
-the CMS detector readout electronics and reconstructed world-wide, which is then processed through various algorithms which derive signatures of individual particles.
-Both real and simulated data are available for examination.
-
-As AOD data are too large to be iteratively processed repetitively in
-a physics analysis workflow, it is normally reduced further in
-structural complexity and content.  For the analysis under
-investigation here, this is a two-step process.  First, the AOD data
-are processed at the Notre Dame working group cluster to BEAN (Boson Exploration Analysis Ntuple) events,
-containing only trivial data containers packed in vectors.  This step
-is time and CPU intensive and its output contains data of 11.6$\,$TB to be
-analyzed by the tau analysis.
-It is performed by a small custom code framework, which is built on top of CMSSW.
-The BEAN format, production code, and
-data are shared within the analysis group looking at Higgs production
-in association with top quarks, which is formed by groups from a few
-American and European universities,
-consisting of up to a few dozen contributors.
-
-In the second step, the data are reduced to the ``Ntuple'' format,
-which contains only events matching basic quality criteria and
-fields relevant to \emph{TauRoast}.
-Again, the Notre Dame CMS groups cluster
-resources are used to perform this reduction and selection,
-running highly customized software,
-built on CMSSW and the BEAN framework,
-with code written and maintained by a small group.
-
-Once the data has been reduced to Ntuples, TauRoast can be run as a single
-process, and contains a stringent event selection to look only at high
-quality candidate events for the underlying physical process.
-Quantities from the relevant events can be
-both plotted and used in multivariate analysis to determine the level
-of expected signal in real data.
-This package is written using the CMSSW build framework,
-but only utilizes code from ROOT,
-a particle physics toolkit underlying CMSSW,
-and a few external python dependencies for convenience.
-
-\section{Observations}
-
-\emph{TauRoast} was provided to us in the form of an
-email which described, in prose, how to obtain the source,
-build the program, and run it correctly on one specific
-machine at our home institution, with no particular guarantee that
-it will run anywhere else in the world.
-Although this starting point may seem extreme, it is
-perfectly natural for collaborators to share configurations
-with each other in this form, and to rely on the presence
-of a working environment with appropriate dependencies already
-installed.  From this starting point, the authors played the
-role of curators, whose job it is to prepare the application
-for permanent archival.
-
-First, we elaborated the email instructions into an
-executable script that obtains the dependencies and then
-executes the analysis.  The script declares the necessary
-environment variables, downloads and checks out the necessary source code,
-builds it appropriately, calls initialization scripts in
-the dependent software, and then runs the analysis.
-A few rounds of correction with the original author were necessary
-to obtain all the dependencies and run the artifact correctly.
-(The original instructions introduced in the email also indicated how to run the application
-within a production batch system.  For the purposes of preservation,
-we consider the execution infrastructure to be distinct from the application,
-and leave it out of consideration for now.)
-
-The process of elaborating the program into a script revealed
-several observations about this type of application:
-
-\begin{itemize}
-
-\item {\bf Many Explicit External Dependencies.}  TauRoast depends on a large number of
-external dependencies, each with a different access method and data source.
-While we knew in advance that it depended upon the large CMSSW distribution,
-it was not apparent until elaborating the script that it depended upon
-two different Github repositories for the Tau source,
-a CVS server at CERN for some configuration information, a public web page
-for the PyYAML library, and the public home page of a Notre Dame student
-for one missing header file.  (The latter is particularly troubling!)
-While, at some level, the authors and users of these software know of these dependencies, they are often missing in
-informal communications or forgotten once the dependency is installed.
-However, once known, they are at least expressed explicitly within the script.
-
-\item {\bf Many Implicit Local Dependencies.} A much harder problem is that the
-application assumed the presence of many different components in the local
-filesystem view. It would be tempting to capture all of these by simply
-storing a virtual machine image containing the local filesystem. However,
-the application depended on no less than {\bf five} networked filesystems
-available on a particular machine available to the author:
-the data to be analyzed was stored on an HDFS~\cite{borthakur2008hdfs} cluster,
-some configuration data was stored on a CVMFS~\cite{blomer2011cernvm} filesystem,
-and a variety of software tools were on an NFS~\cite{howard1988scale},
-PanFS~\cite{welch2008scalable} and AFS~\cite{sandberg1985design} systems.
-The original authors were not aware of many of these dependencies,
-because they simply relied on local administrators to configure the
-software and make it available.
-
-\item {\bf Configuration Complexity.}  As a means of controlling the complexity
-of dependent software packages, the high energy physics community has developed
-a number of tools that perform run-time configuration and consistency checks
-of the available software.  {\tt scram} is the software management tool used
-by the CMS experiment.  Before running any code, {\tt scram} is used to locate
-the appropriate version of software,  set environment variables such as the PATH, run any
-tool-specific configuration, and do the same for all software on which it depends.
-If the correct versions are not available, {\tt scram} halts and emits an error.
-While this procedure has great value for consistency, it also introduces a significant cost
-because it involves a large number of nested scripts traversing a filesystem,
-repeatedly looking up metadata.  In our example, the time to perform this configuration
-with a cold cache is about 14 minutes, which is almost as large as the actual analysis
-run, which takes 20 minutes.
-
-\begin{figure*}[t]
-\centering
-\includegraphics[width=.8\textwidth]{version-evolution.eps}
-\caption{Version Evolution}
-\label{fig:version-evolution}
-\end{figure*}
-
-\item {\bf High Selectivity.}  Although the total size of the resources accessed by this
-program is very large, the size of the data and software actually used are much smaller.
-Often, an entire repository or data source is named within the script, but the program
-only needs a handful of items from that source.  For example, the data is stored on an
-HDFS filesystem with 11.6TB of data, but only 20GB are actually consumed by the program. 
-The reason for this great reduction is at first each BEAN event contains a large amount of information, and the TauAnalysis throws away a lot of the irrelevant event information, keeping only the relevant bits.
-The CMSSW repository is 88.1GB in total
-but only 448.3MB of source is checked out, and the actually used software only
-measured 6.3MB.  In a few cases, a source of software is named but never actually accessed.
-(For example, our original script includes the Open Science Grid software stack in the PATH, but does not actually use it.)
-We suspect that end users are accustomed to missing dependencies and thus get in the habit of adding commonly used software,
-whether it is needed or not.
-
-\item {\bf Rapid Changes in Dependencies.}  Over the course of three months
-between collecting the initial email, analyzing the program, and writing this
-paper, the computing environment continuously changed.  The CMSSW software
-distribution released a new version, the target execution environment was upgraded
-to a new operating system, and the application deprecated the use of CVS for obtaining
-the software.  While the users of this software seem be accustomed to constant change,
-any preservation technique will have to be very cautious about relying upon an
-external service, even one that may appear to be highly stable.
-
-\end{itemize}
-
-\if 0
-
-\begin{table}
-    \centering
-    \begin{tabular}{|l|}
-        \hline
-        {\bf Version 1: Email}\\ \hline
-        1. Create a CMS release,\\
-            \hspace{9pt} e.g. {\tt cmsrel CMSSW\_5\_3\_11\_patch3} \\
-        2. Install the BEAN packages as the instructions: \\
-            \hspace{9pt} {\tt \url{https://github.com/cms-ttH/BEAN/blob/...}}\\
-        3. Install grid-control: \\ 
-            \hspace{9pt} {\tt svn co \url{https://ekptrac.physik.uni-ka/...}} \\
-        4. INstall the TauAnalysis package: \\
-           \hspace{9pt} {\tt git clone \url{https://github.com/matz-e/...}} \\
-           \hspace{9pt} {\tt scram b -j32} \\
-        5. Fix grid\_control.cfg and run it. \\
-        6. Perform the actual tau roast program. \\ 
-        \hline
-        {\bf Version 2: Script}\\ \hline
-        {\tt setenv CMSSW\_BASE CMSSW\_5\_3\_11\_patch3} \\
-        {\tt cmsrel \$HOME/\$CMSSW\_BASE} \\
-        {\tt cvs co -r V03-09-23 PhysicsTools/PatUtils} \\
-        {\tt git clone \url{https://github.com/cms-ttH/BEAN.git}} \\
-        {\tt wget -r \url{http://nd.edu/~abrinke1/...}} \\
-        {\tt scram b -j32} \\
-        {\tt wget \url{http://pyyaml.org/download/pyyaml/PyYAML...}}\\
-        \#the experiment data is from HDFS \\
-        {\tt cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10}\\
-        {\tt cmsenv}\\
-        {\tt python setup.py install --user} \\
-        {\tt scripts/roaster data/generic\_ttl.yaml} \\ 
-        \hline
-        {\bf version 3: Formulated Script} \\ \hline
-        {\tt setenv CMSSW\_BASE CMSSW\_5\_3\_11\_patch3} \\
-        {\tt setenv {\bf GIT} \url{https://github.com}} \\
-        {\tt setenv {\bf PYYAML} \url{http://pyyaml.org}} \\
-        {\tt setenv {\bf ND} \url{http://nd.edu}} \\
-        {\tt cmsrel \$HOME/\$CMSSW\_BASE} \\
-        {\tt cvs co -r V03-09-23 PhysicsTools/PatUtils} \\
-        {\tt git clone \${\bf GIT}/cms-ttH/BEAN.git} \\
-        {\tt wget -r \${\bf ND}\url{/~abrinke1/ElectronEffectiveArea.h}} \\
-        {\tt scram b -j32} \\
-        {\tt wget \${\bf PYYAML}/download/pyyaml/PyYAML...}\\
-        \#the experiment data is from HDFS \\
-        {\tt cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10}\\
-        {\tt cmsenv}\\
-        {\tt python setup.py install --user} \\
-        {\tt scripts/roaster data/generic\_ttl.yaml} \\ 
-        \hline
-       {\bf Version 4: Fine-Grained Toolkit - Package}\\ \hline
-        {\tt setenv CMSSW\_BASE CMSSW\_5\_3\_11\_patch3} \\
-        {\tt setenv {\bf GIT} \url{https://github.com}} \\
-        {\tt setenv {\bf PYYAML} \url{http://pyyaml.org}} \\
-        {\tt setenv {\bf ND} \url{http://nd.edu}} \\
-        {\tt cmsrel \$HOME/\$CMSSW\_BASE} \\
-        {\tt cvs co -r V03-09-23 PhysicsTools/PatUtils} \\
-        {\tt git clone \${\bf GIT}/cms-ttH/BEAN.git} \\
-        {\tt wget -r \${\bf ND}\url{/~abrinke1/ElectronEffectiveArea.h}} \\
-        {\tt scram b -j32} \\
-        {\tt wget \${\bf PYYAML}/download/pyyaml/PyYAML...}\\
-        \#the experiment data is from HDFS \\
-        {\tt cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10}\\
-        {\tt cmsenv}\\
-        {\tt python setup.py install --user} \\
-        {\tt scripts/roaster data/generic\_ttl.yaml} \\ 
-        \hline
-    \end{tabular}
-    \caption{Scripts of each Solution}
-    \label{table:scripts}
-\end{table}
-
-\fi
-
-\section{Evolving the Artifact}
-
-It is clear that the artifact, as provided, is not in a suitable form
-for preservation.  While it might be technically possible to automatically
-capture the entire virtual machine and all of the connected filesystems,
-it would require 166.8TB of storage, which would be prohibitively expensive
-for capturing this one application alone.  Further, if multiple
-similar applications are preserved, we would miss the opportunity to identify
-common dependencies and store them once for multiple artifacts.
-A more structured approach to dependency management is needed.
-
-Figure~\ref{fig:version-evolution} shows how we have evolved this artifact
-through several stages which make it more suitable for preservation.
-In each step of evolution, we make the dependencies of the artifact
-more explicit and available for analysis and automated processing.
-As noted in the previous section, the original author provided us with
-prose instructions by email which we translated into an
-executable script.  The executable script has embedded in it
-a number of external identifiers such as URLs pointing to repositories
-and paths to networked filesystems.  As a general programming practice,
-embedding such constants into the middle of a program is unwise, and so
-we extract all of those identifiers and place them \emph{outside} the
-script in a \emph{dependency map} or just \emph{map} for short.
-The dependency map lists all of the external dependencies of the application, indicating
-the type, how they are accessed, and where they are currently located.
-The resulting script then simply refers to abstract file locations such
-as \verb$GIT$ and \verb$CVMFS$, while the map file indicates where they
-are currently located. If properly constructed, the script should not refer to any external
-resource unless it is indicated in the dependency map.  We call this idealized
-artifact an \emph{abstract script}.
-
-By extracting the dependencies into the dependency map,
-we introduce great freedom for the curator to move, transform, and otherwise
-manipulate the dependencies of the artifact without damaging the artifact itself.
-A Figure~\ref{fig:version-evolution} shows, it is straightforward for an
-automated tool to examine
-all of the dependencies in the map, download those that are missing,
-and then modify the map to point to the local copies of the dependencies.
-If we group the script, dependency map, and dependencies into a \emph{package},
-we now have a self-contained artifact that can be moved from place to place.
-In some cases, it may be safe to allow the dependency map to refer to 
-trusted remote repositories.  Whether this is advisable is a judgment that
-must be made by the user or the curator, taking into account the long-term
-stability of said repositories.
-
-However, only having the package and the dependency map is not enough. The successful execution of the application on the original machine also relies on the configuration of environment variables.
-We collected the environment variables of the original machine and transformed it into one executable script.
-If another researcher wants to repeat the application, this executable script will be first executed.
-The environment variables refer to the dynamic named values defined in the range of one computer, like \verb!$PATH! and \verb!$PYTHONPATH!.
-However, the dependency map refers to the actual storage location of path variables used in one abstract script. For example, the actual storage location of the path variable \verb!CVMFS! 
-is {\tt /data/cvmfs/grid.cern.ch}.
-
-\begin{figure}
-\centering
-\includegraphics[width=.5\textwidth]{solution3.eps}
-\caption{Relationship of Roles}
-\label{fig:solution3}
-\end{figure}
-
-The relationship of different roles involved in the application preservation and
-reproduction is shown in Figure~\ref{fig:solution3}.  The original author uses the packaging utility to generate the package for one application.
-Then the package, together with
-its map file and description file will be published. When
-another researcher wants to repeat the application, one copy of the package will be downloaded into the new machine and the application can be repeated.
-
-When we try to repeat one application on one new machine, one map file is necessary for the relocation of the data access targets, as
-show in Figure~\ref{fig:version-evolution}. 
-The map file clearly defines the real location of each dependency in the format of dependency variables - the real location of dependency variable {\tt GIT} is \path{/data/git/cms-ttH} and the real location of dependency variable {\tt CVMFS}
-is {\tt /data/cvmfs/grid.cern.ch}.
-The script only refers to the dependency variables defined in the map file.
-This design decouples the application script and the actual data access targets, which minimizes the impact of the evolution of different data dependencies
-and ensures the transparent access.
-The modification of the package only introduces the minimal changes of the map file on the client side.
-
-This basic approach to dependency management is a step in the right direction
-for dependencies that are \emph{explicit} and \emph{external} to the
-user's native execution environment.  However, it leaves two other problems unsolved.
-
-First, the basic approach requires that someone be \emph{aware} of the dependencies,
-whether it be the end user, the system administrator, or the archive curator.
-It seems reasonable to expect the user to be aware of a large dependency mentioned in a top-level script.
-But, oftentimes the dependency is embedded invisibly deep within the software stack,
-or is connected to the machine by the local system administrators.  No single party
-is likely to have complete information about all of the dependencies.
-Second, the basic approach assumes that the entire dependency is actually
-consumed by the artifact.  As we have suggested above (and will show below),
-this sort of program often only consumes a small fraction of what it does declare
-as a dependency.
-
-To address both of these problems, users and curators alike need tools that
-will automatically observe the dependencies of complex applications, to
-facilitate automatic and efficient preservation.
-
 \section{Measuring Dependencies}
@@
 All the application data will be encrypted at presentation layer through the TLS/SSL protocol, which is initialized at the session layer and works at the presentation layer.
-
-\section{Evaluation}
-
-We evaluated the correctness of the reduced package and the overhead of generating the package.
-To do this, the application was repeated with the help of \emph{Original Script} (as shown in Figure~\ref{fig:version-evolution}) on the original machine. 
-Then one \emph{reduced package} was generated and verified with the help of Parrot on the original machine.
-
-Then, two different virtual machines (VM) - one VM from the Notre Dame Cloud Platform based on KVM and one VM from the Amazon EC2 Platform based on Xen, were employed to further verify the correctness of the reduced package.
-
-We first repeated the example from scratch using the Script translated from the original email on the original machine and counted the time consumption and data size. 
-Then based on the successful execution of Original Script, we evaluated Reduced Package - one package containing necessary dependencies is generated, and then the time consumption and data size is analyzed.
-
-To measure time consumption, we counted the time used to obtain remote software dependencies, build the environment, and analyze the dataset.
-We also counted the time used to obtain the namelist and to generate the package.
-To measure data size, we can easily figure out the size of each data and code source inside the package under Reduced Package.
-Original Script does not support mining of implicit dependencies.
-As for remote sources, we can figure out the named size through the analysis script.
-However, it is hard to figure out the named size of each local source.
-Instead, we only knew that total size of each file system is very large.
-
-Table~\ref{table:time-2nd3rd} shows the execution time comparison between
-Original Script and Reduced Package.
-Reduced Package is faster than Original Script, because all the software copied into the package has been compiled and the Software Acquisition stage is not necessary.
-and all the environment building only takes 4 seconds,
-We were surprised that Reduced Package even reduces the actual analysis time. 
-The reason for this is that data is obtained through accessing HDFS in Original Script, but is copied into the package in Reduced Package.
-This localization of experimental data speeds up the data analysis process, resulting the actual analysis time reducing from 20 minutes to 13 minutes.
-
-\begin{table}
-    \centering
-    \begin{tabular}{lrr}
-    \hline
-    \bf Task Category & \bf Original Script & \bf Reduced Package \\ \hline
-    Obtain Namelist & N/A & 28min 28s \\ \hline
-    Generate Package & N/A & 85min 51s \\ \hline
-    Software Acquisition & 8min 11s & N/A \\ \hline
-    Environment Build & 5min 49s  & 4s \\ \hline
-    Analysis Code & 20min 31s & 13min 04s \\ \hline
-    \end{tabular}
-    \caption{Execution Time Comparison between Original Script and Reduced Package}
-    \label{table:time-2nd3rd}
-\end{table}
-
-Table~\ref{table:time-2nd3rd} also illustrates the time used to
-obtain the namelist and to generate the package. 
-The time used for these two steps is longer than the execution time,
-because each filename of the list, together with its system call type, needs to be checked, and the structure of each directory item must be maintained.
-However, 
-this is only done once.
-Once the package is
-generated, many users can directly obtain the package and repeat the application 
-separately.
-
-Table~\ref{table:size-original-real} on page 2 illustrates the total size, named size in the example and actually used size of each remote source (the first 4 items) and local source (the remaining 5 items).
-The third column corresponds to the data size of Reduced Package and can be easily figured out, because all the necessary data has been copied into the package.
-Original Script does not support measuring implicit dependencies.
-As for remote sources, we can figure out the named size through the analysis script.
-However, it is hard to figure out the named size of each local source.
-Instead, we only knew that total size of each file system is very large.
-
-\begin{table}
-	\centering
-	    \begin{tabular}{llrrr}
-	        \hline
-	        \bf Name & \bf Location & \bf Total & \bf Named & \bf Used \\ 
-	        \hline
-	        CMSSW code     & CVS & 88.1GB & 448.3MB & 6.3MB\\ \hline
-	        Tau source       & Git & 73.7MB & 73.7MB & 6.7MB \\ \hline
-	        PyYAML binaries    & HTTP & 52MB & 52MB & 0KB \\ \hline
-	        .h file       & HTTP& 41KB & 41KB & 0KB \\ \hline \hline
-	        Ntuples data    & HDFS& 11.6TB & N/A& 20GB \\ \hline
-	        Configuration & CVMFS & 7.4GB & N/A & 103MB \\ \hline
-	        Linux commands & localFS & 110GB &  N/A & 68.4MB \\ \hline     
-	        HOME dir& AFS &12GB & N/A & 32MB\\ \hline
-	        Misc commands & PanFS & 155TB & N/A  & 1.6MB \\ \hline
-	        Total      &    & 166.8TB            & N/A & 21GB \\ \hline
-	    \end{tabular}
-	    \caption{Data and Code Used by Tau Roast}
-	    \label{table:size-original-real}
-\end{table}
-%	\begin{tablenotes}
-%	      \small
-%	      \item The first column illustrates the total size of each data and software source; 
-%	            the second column illustrates the size of the named files from each source;
-%	            the third column illustrates the size of actually used data from each source.
-%	            N/A denotes it is hard to figure out the named size of implicit dependencies directly.        
-%	    \end{tablenotes}
-
-To further verify the correctness of Reduced Package on other machines, two different machines are employed -
-one virtual
-machine~\cite{goldberg1974survey} from the Notre Dame Cloud Platform based on KVM sharing the same kernel version with the original machine,
-and one virtual machine from  the Amazon EC2~\cite{amazon2010amazon} Platform based on Xen.
-
-Table~\ref{table:config-vm} illustrates the configuration of 
-each machine and the execution time of the application on each machine.
-All the machines adopt the x86\_64 hardware platform and Linux kernel.
-Both of the two VMs repeated the application with the help of the package generated on the original machine successfully.
-The execution time on one machine greatly depends on its hardware configuration.
-
-\begin{table}
-    \centering
-    \begin{tabular}{lrrrr}
-    \hline
-    \bf Machine Type & \bf Distro Version & \bf CPU Cores & \bf Mem (GB) & \bf Execution Time \\ \hline 
-    Original Machine &  Red Hat 5.10 & 64 & 125 & 13min 04s\\  \hline
-    KVM (Notre Dame) & CentOS 5.10 & 4 & 2 & 21min 38s\\ \hline
-    Xen (EC2) & Red Hat 5.9 & 16 & 60.5 & 13min 30s\\ \hline
-    \end{tabular}
-    \caption{Evaluation of Different Machines}
-    \label{table:config-vm}
-\end{table}
-
-In summary, we demonstrate that the application can be repeated with the help of the reduced package on one different machine with the required hardware architecture and OS kernel version.
-%*****hmeng-doubt:Another reason for the packaging utility is that not all the data and software generated by the second version script is used during the the actual data analysis.
-The packaging utility can help us find out the optimal subset of data and software involved in one actual data analysis.
-%*****hmeng-doubt: this point is not the motivation. but one achievement comes together. out of imagination.
-
-\begin{figure}
-\centering
-\includegraphics[width=.6\textwidth]{preservation-integration.eps}
-\caption{Preserving Multiple Artifacts}
-\label{fig:Preservation integration}
-\end{figure}
-
-\section{Open Problems}
-
-Figure~\ref{fig:Preservation integration} shows the rough information
-architecture of the archive that we imagine for complex
-scientific software like TauRoast.
-Each artifact to be preserved is a package that consists of a top-level
-script to invoke the software, a dependency map, and the dependencies
-themselves, which may be external to the original program.  The artifacts
-are then ingested into the archive, where shared dependencies are stored
-only once.  In cases where an artifact has a dependency on a trusted
-(or very large) remote archive, the dependency may simply be tracked
-. A researcher that wishes to reproduce a given
-result need only refer to the unique identifier of the artifact, and will
-be able to automatically extract all of the dependent components of
-that artifact.
-
-For example, in Figure~\ref{fig:Preservation integration} Script 1 depends on items A, B, and C.
-Items A and B are ingested into the archive, where B is shared with Script 2.
-Item C is stored in another trustworthy repository and is tracked rather than ingested.
-When Script 1 is exported from the repository, items A and B are exported along with it, while C can be copied or remain remote, according to the end user's choice.
-
-As simple as that picture appears, there are a number of problems that must be solved to get there:
-
-{\bf Measure the Mess or Force Cleanliness?}  Two radically different approaches to dependency tracking are possible.
-The first is to allow end users complete freedom to construct their environment as desired, then \emph{measure} what items were actually used.
-As we have shown, this is possible, but has significant overheads and does not fully preserve the structure or intent of the end user.
-The second approach is to \emph{force} users to work in a clean environment in which no resource can be used until a proper dependency has been declared.
-This ensures that all dependencies are known in advance (and made explicit to the end user) but places a variety of restrictions on the user's daily work, and may prevent creative approaches that do not fit within the curator's view of how programs should be structured.
-Whether end users will accept the inconvenience of forced cleanliness for the benefits of reproducibility can only be discovered through experiment.
-
-{\bf Granularity of Dependencies.}  Dependencies could be handled
-at many different levels of granularity.  In this work, we have shown
-how they can be handled at the level of entire repositories or individual files.
-Other possible choices might include intermediate-sized software packages
-(like RPM) or in the case of experimental data, even portions of individual large files.  Clearly, a larger granularity will result in 
-simpler dependency maps, and more wasted space; smaller granularity results
-in complex dependency maps and less wasted space.  A hybrid solution may
-be able to combine both by storing large granularity dependencies, but
-selecting sub-items out of objects when efficiency demands it.
-
-{\bf Scope of Reuse.}  We have presented the data preservation
-problem as primarily one of accurate reproduction: if a result depends
-on running program X, we must be able to run exactly X again.  However,
-the goal of scientific reproducibility is rarely limited to running
-\emph{precisely} what a predecessor did. Often, the objective is to
-change a parameter or a data input in order to see how the result is affected.
-To that end, the preservation system must capture enough of the surrounding
-material to permit modifications to succeed.  From this perspective,
-a larger granularity of preservation is desirable.  A better understanding of
-how end users will consume preserved software will help to shape how
-software is preserved in the first place.
-
-{\bf Dependency Detection.}  If we allow users to work in uncontrolled
-environments, then we must have better methods for understanding the dependencies  of existing programs.  At first, we relied on an expert reader to examine
-the user's script and extract the dependencies.  This is clearly
-not a scalable approach.  We then demonstrated an automated method of observing
-what individual files are accessed by a program. However, this does
-not cover all types of dependencies, particularly those that are networked.
-More sophisticated observation techniques could infer higher-level information,
-such as the RPM package names of the files accessed, the URLs of remote
-repositories named throughout the program, or even the addresses and names of networked dependencies like databases and filesystems.
-
-{\bf Source, Binary, or Both?}  A science archive might choose to retain
-the source code of an artifact or the binary code that can actually run in a given environment.
-While conventional wisdom suggests that access to source code is critical for the long term
-survival and evolution of a piece of software, it also requires the maintenance of an enormous
-amount of supporting software in the form of compilers, linkers, and supporting libraries for
-the target platform.  Rebuilding all of these for every invocation of an artifact is
-likely to have excessive cost.  We suggest that a realistic repository will have to
-maintain \emph{both}: the source describes the ultimate meaning of the code, but
-the binary is an important performance cache, a backup if the compiler toolchain should
-fail to be preserved, and a checksum to ensure that a source artifact was rebuilt correctly.
-
-\section{Related Work }
-
-Generally, there are three approaches to preserve software environment:
-hardware preservation, migration and emulation.  Hardware
-preservation preserves the original software and its original operating
-environment. 
-Software migration technique~\cite{cifuentes1996binary,mancl2001refactoring} was used to facilitate running software on new machines.
-However, migration often involves the re-compiling and re-configuring
-the source code to accommodate a new hardware platform and software environment.
-Emulation recreates the original software and hardware environment by
-programming future platforms and OSs. One common solution to implement this is
-virtual machine. According to the usage and emulation degree of the real
-machine, virtual machine can be divided into system virtual machine and process
-virtual machine. 
-The working principle, design principle and
-performance evaluation of system virtual machine were illustrated in~\cite{goldberg1974survey, smith2005architecture}. 
-The
-functionality of system VM to support different guest operating systems was illustrated in~\cite{barham2003xen,kivity2007kvm,rosenblum1999vmware}.
-F. Esquembre~\cite{esquembre2004easy} illustrated how JVM, one process virtual machine, can expedite the creation of
-scientific simulations in Java. 
-The pros and cons of these three approaches were discussed in~\cite{matthews2009towards,phelps2005no,hong2010software}.
-
-The preservation of computing environment and software environment was treated as one entirety in~\cite{matthews2009towards,phelps2005no,hong2010software}.
-However, frequently changing experiment software makes the maintenance of the preserved experimental environment very complex.
-CernVM~\cite{buncic2010cernvm} treated them as two different categories.
-The preservation of computing environment is implemented with CernVM, and the preservation of software environment is based on a CernVM filesystem(CVMFS) specifically designed for efficient software distribution.
-
-The importance of preserving software in source code format was emphasized in~\cite{zabolitzky2002preserving,castagne2013consider}. 
-However, CVMFS~\cite{buncic2010cernvm} published pre-built and configured experiment software releases to avoid the time-consuming software building procedure.
-
-Attempts from different perspectives to facilitate the reproduction of scientific experiments utilizing a preserved software library have been made. 
-The software distribution mechanism over network was discussed in~\cite{compostella2010cdf, blomer2011cernvm}.
-J.
-R.
-Rice et al.~\cite{rice1996scientific} made the reproduction process easier through the integration of user interface, scientific software libraries, knowledge base into problem-solving environment.
-S. R. Kohn et al.~\cite{kohn2001divorcing} tried to enable the creation and distribution of language-independent software library by addressing language interoperability.
-a scalable, distributed and dynamic workflow system for digitization processes was proposed in~\cite{schoneberg2013scalable}.
-A distributed archival network was designed in~\cite{subotic2013distributed} to facilitate process-oriented automatic long-term digital preservation.
-M. Agosti et al.~\cite{agosti2012envisage} aimed to help non-domain users to utilize the digital archive system developed for domain experts.
-
-Current mechanisms of preserving scientific experiments assume that all the data and software mentioned in the experiments are necessary for the reproduction of the experiments.
-However, this is not always right.
-In some cases, the original author may leave additional code referring to irrelative data and software in the program.
-One mechanism, which can figure out the absolutely relevant data and software of one experiment, is important for both the preservation and reproduction of scientific experiments.
-
-B. Matthews et al.~\cite{matthews2008significant} introduced one conceptual framework for software preservation from several case studies of software preservation.
-One tool to capture software preservation properties within a software environment was designed in~\cite{matthews2010framework} through a series of case studies conducted to evaluate the software preservation framework.
-L. R. Johnston et al.~\cite{johnston2014workflow} proposed one overall data curation workflow for 3-5 case studies of preserving research data.
-Two case studies~\cite{borgman2012data} were conducted to figure out the properties of data to be reused in the future.
-
-\section{Postscript}
-
-We began this work in late 2013, generating a reduced package for \emph{TauRoast} based
-on the configuration of a standard machine at Notre Dame at the time.  In the course
-of writing this paper in spring 2014, almost everything about the computing environment
-changed: the operating system was upgraded, a new version of CMSSW was released, and
-our local HEP users switched from using CVS to CVMFS for accessing CMSSW.
-The original script provided by the author failed to run on the same machine.
-But, the reduced package we created three months earlier in the old environment
-worked just fine on the new machine.
-
-\section*{Acknowledgments}
-
-This work was supported in part by National Science Foundation grants PHY-1247316 (DASPOS), 
-OCI-1148330 (SI2) and PHY-1312842.
-The University of Notre Dame Center for Research Computing scientists and engineers provided critical technical assistance throughout this research effort.
-
-Copyright (C) 2014 The University of Notre Dame
-
-This work is licensed under the Creative Commons Attribution 4.0 License.
-
-\bibliographystyle{plain}
-\bibliography{cclpapers,this}
-
-\end{document}

### 2015-01-06 observation.tex
Put each section into a separate tex file

--- 2014-12-18 paper.tex
@@
-\documentclass[procedia]{easychair}
-\usepackage{url}
-\usepackage[flushleft]{threeparttable}
-\hyphenation{resour-ces}
-\hyphenation{approac-hes}
-\hyphenation{har-der}
-\hyphenation{spe-cifically}
-\makeatletter
-\def\@copyrightspace{\relax}
-\makeatother
-
-\title{A Case Study in Preserving a High Energy Physics Application}
-
-% \titlerunning{} has to be set to either the main title or its shorter
-% version for the running heads. When processed by
-% EasyChair, this command is mandatory: a document without \titlerunning
-% will be rejected by EasyChair
-
-\titlerunning{A Case Study in Preserving a High Energy Physics Application}
-
-\author{
-	Haiyan Meng\inst{1}
-\and
-	Matthias Wolf\inst{2}
-\and
-	Douglas Thain\inst{3}
-}
-\institute{
-	Department of Computer Science and Engineering,
-	University of Notre Dame,
-	Notre Dame, Indiana, USA
-	\email{hmeng@nd.edu}
-\and
-	Department of Physics,
-	University of Notre Dame,
-	Notre Dame, Indiana, USA
-	\email{mwolf3@nd.edu}
-\and
-	Department of Computer Science and Engineering,
-	University of Notre Dame,
-	Notre Dame, Indiana, USA
-	\email{dthain@nd.edu}
-}
-
-%  \authorrunning{} has to be set for the shorter version of the authors' names;
-% otherwise a warning will be rendered in the running heads. When processed by
-% EasyChair, this command is mandatory: a document without \authorrunning
-% will be rejected by EasyChair
-
-\authorrunning{Meng, Wolf and Thain}
-
-\begin{document}
-
-\maketitle
-
-\keywords{}
-
-\begin{abstract}
-\it The reproducibility of scientific results increasingly
-depends upon the preservation of computational artifacts.
-Although preserving a computation to be used later sounds
-easy, it is surprisingly difficult due to the complexity
-of existing software and systems.  Implicit dependencies,
-networked resources, and shifting compatibility all conspire
-to break applications that appear to work well.  To investigate
-these issues, we present a case study of a complex high energy
-physics application.  We analyze the application and attempt
-several methods at extracting its dependencies for the purposes
-of preservation. 
-We propose one fine-grained dependency management toolkit to preserve the application and demonstrate its correctness in two different environments - one virtual machine from the Notre Dame Cloud Platform and one virtual machine from the Amazon EC2 Platform.
-We report on the completeness, performance,
-and efficiency of each technique, and offer some guidance for
-future work in application preservation.
-\end{abstract}
-
-% A category with the (minimum) three required fields
-%\category{H.4}{Information Systems Applications}{Miscellaneous}
-%A category including the fourth, optional field follows...
-%\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]
-
-%\terms{Theory}
-
-\section{Introduction}
-
-Reproducibility is a cornerstone of the scientific process~\cite{borgman2012data}.
-In order to understand, verify, and build upon previous work,
-one must be able to first recreate previous results by applying
-the same methods. Historically, reproducibility has been
-accomplished through painstaking detailed documentation recorded
-in lab notebooks, which are then summarized in peer-reviewed publications.
-But as science increasingly depends on computation,
-reproducibility must also encompass the environments, data, and software
-involved in each result~\cite{zabolitzky2002preserving}. It is widely recognized that informal
-descriptions of software and systems -- although common -- are insufficient
-for reproducing a computational result accurately.
-A more automated and comprehensive approach is required.
-
-The reproduction of a computation has three broad components,
-each of which suggests somewhat different approaches:
-
-\begin{itemize}
-\item The {\bf computing environment}, consisting of the basic hardware and the operating system which can be preserved as physical artifacts or as a combination of virtual machine monitors (hardware) and virtual machine images (operating system)~\cite{matthews2009towards}.
-\item The {\bf scientific data} to be analyzed has historically received the most attention for curation.
-In a large, well-organized project, it may be stored in a  data repository or database management system, with associated documentation and a curation strategy.
-In a small effort, it could simply be a handful of files.
-\item The {\bf software environment} includes the source code, binaries, scripts, configuration files, and everything else needed to execute the desired code.
-As with data, the software could be drawn from a well-managed software repository, or it could be a handful custom scripts that exist in the user's home directory.
-\end{itemize}
-
-In a very abstract sense, reproducing a computation is trivial.
-Assuming a computation is deterministic, one must simply
-preserve all of the inputs to a computation, then re-run
-the same code in an equivalent environment, and the same result
-will be produced.  For a small custom application on a modest
-amount of data, this could be accomplished by capturing the
-complete environment,
-data, and software within a single virtual machine image,
-and then depositing the virtual
-image into a curated environment.  The publication could
-then simply refer to the identifier of the image, which the
-interested reader can obtain and re-use. This approach has
-been used to some success with systems~\cite{castagne2013consider}.
-\footnote{Of course, we are glossing over the problem that hardware
-architectures and virtual machines also change, so one must also
-preserve the VMM software necessary to run the image.  The VMM itself
-depends on a software environment which must also be preserved.
-A long-term preservation system might end up running a whole
-stack of nested virtual machines in order to provide the desired
-environment! }
-
-However, this simple approach is not sufficient for large applications
-that are run in complex environments.
-
-\begin{itemize}
-\item There may be {\bf implicit dependencies} on items that are
-not apparent to the end user.  For example, they may understand that
-they rely on a particular data analysis package, but would have
-no reason to know that the package has further dependencies on
-other libraries and configuration files.  Or, they may know that
-the computation only runs correctly on a particular machine, but
-not know this is because it relies on a filesystem that
-is mounted only on that machine.
-
-\item The {\bf granularity} of the dependencies may not be well understood.
-For example, the user may understand that a computation depends upon
-a data collection that is 1TB in overall size, but not have detailed
-knowledge that it only requires three files totalling 300MB out of that
-whole collection.
-
-\item There may be dependencies upon {\bf networked resources} that
-are inherently external to the system, such as a database, a code
-repository~\cite{cms2006cmssw}, or a scalable filesystem~\cite{blomer2011cernvm}.  For such resources, it
-must be decided whether the dependency will simply be noted, or if it
-must be incorporated whole or in part.
-
-\item Where {\bf common dependencies} are widely used, it may be inefficient or
-impossible to store one copy of each dependency for each archived object.
-Some form of sharing or de-duplication is necessary in order to keep
-the archive to a reasonable size.
-\end{itemize}
-
-We do not claim to have solved these problems in any comprehensive
-way.  Rather, our aim in this paper is to highlight the scope
-of the problems by presenting a case study of one complex application.
-The application is presented to us
-first in the form of an email that describes in prose how to install
-the software and run the analysis.  We perform several successive
-refinements to convert it into an executable and preservable object.
-We then develop techniques for reducing the size of the dependencies
-that are necessary for the object to function, and we demonstrate
-the preserved object functioning correctly in three different
-physical and cloud environments.
-We describe how each of these techniques may interact with
-a future archive of preserved software artifacts, and conclude with
-some reflections on the challenges of preservation and advice for future efforts.
-
-\if 0
-Section 2: Overview of Application
-    CMS/LHC introduction.
-    Data sources and reduction of size.
-    Code sources and reduction of size.
-    Prose observations about the script.
-        Uses multiple repos that change over time, with varying level of stability.
-        Low selectivity from the larger repos
-        Significant initialization time to collect everything.
-        Incidental infrastructure tools versus essential objects.
-        Some dependencies were surprising.
-    Figure: Diagram of app with both code and data sources.
-    Table: Show all code and data sources and size within one table.
-
-Section 3: Preservation Strategies
-    Figure: Show app in four stages:
-        Single email.
-        Script with embedded references to dependencies.
-        Script with map file that refers to external dependencies.
-        Script with map file that refers to preserved dependencies.
-
-    Transform to more suitable format that expresses dependencies.
-
-    Incorporate into archive, saving deps and map file.
-
-    But, how to get the dependencies?
-
-    Three strategies:
-        Original - Unmodified application run in original environment.
-        Coarse-Grained - Capture deps at large granularity -- whole filesystems and repositories.
-        Fine-Grained - Capture deps at a fine granularity -- individual files actually used.
-
-    Coarse-Grained Method (Copy Repositories)
-        First, determine dependencies
-        Express app as script + map file
-        Packaging tool downloads deps, rewrites map file.
-        To run packaged application, obtain map, download
-
-    Fine-Trained Toolkit (Parrot)
-        Tool to detect dependencies (Parrot)
-        Express app as script + map file
-        Packaging tool downloads deps, rewrites map file.
-        To run package application, run again with Parrot.
-
-Section 4: Evaluation
-
-    Table: Time and size of preserving using each of the two techniques.
-
-    Explain why the techniques show different performance.
-
-    Is one technique more effective than the other?  Why?
-\fi
-
-\begin{figure}[t]
-\centering
-\includegraphics[width=.5\textwidth]{data-code-size.eps}
-\caption{Inputs to Tau Roast}
-\label{fig:data-code-size}
-\end{figure}
-
-\section{Overview of Tau Roast}
-
-Within the ongoing investigation of the Higgs boson at the CMS
-detector, part of the LHC at CERN~\cite{collaboration2008cms}, the Higgs production in association
-with two top quarks allows measuring the Higgs coupling strength to
-top quarks~\cite{chatrchyan2013search}.  As the Higgs boson is too short-lived to be detected
-itself, it has to be reconstructed from its decay products.
-
-The application which is the study of this paper is called \emph{TauRoast}.
-It searches for cases where the Higgs boson decays to two tau leptons.
-Since the tau leptons are very short-lived, they are not observed directly, but by the particle decay products 
-that they generate.  So, the analysis must search for detector
-events that show a signature of decay products compatible with both hadronic tau and top decays.  Properties of such events are used to distinguish
-the events of interest (Higgs decays) from all other events and
-are also used in further statistical analysis.
-
-Figure~\ref{fig:data-code-size} shows that both the code and data
-that form \emph{TauRoast} are drawn from large repositories through
-multiple steps of reduction.  A preservation strategy must weigh
-whether to store the large repositories completely, the fragments
-used by an artifact, or something in between.
-
-{\bf Code Sources.} Like many scientific codes, the central algorithm
-of \emph{TauRoast} is expressed in a relatively small amount of
-custom code developed by the primary author.  But, the code cannot
-run at all without making use of an enormous collection of software
-dependencies.  Some of these dependencies are standard to operating
-systems worldwide, some are standardized across the entire high-energy
-physics field, some are particular to small collaborative groups,
-and a few are very specific to a single researcher.
-
-The largest of these repositories is the CMS Software Distribution (CMSSW)~\cite{cms2006cms},
-a carefully-curated selection of software packages which is distributed
-in several forms.  Historically, components of CMSSW were obtained by checking components
-of the source out of CVS (CMSSW source codes were moved from CVS to git recently), or by installing a complete binary package on a shared
-filesystem within an HPC center.  In recent years, distribution has moved to
-an on-demand delivery system known as CVMFS~\cite{blomer2011cernvm}, which
-provides a filesystem interface that transparently accesses a remote repository.
-The content of CMSSW is managed very carefully by a centralized team whose main goal
-is to ensure that the current version of the software operates correctly
-on the operating systems and architectures currently in use.  However,
-preservation is not a specific objective of the system, and so there is
-no particular guarantee that old versions of CMSSW will continue to
-operate indefinitely.
-
-CMSSW contains many different tools, libraries, and utilities.
-No single code uses anywhere close to all of these.
-But, because it is widely used within the experimental researchers, it is common for users to simply expect that a particular version of the entire repository is available.
-
-{\bf Data Sources.}
-The CMS collaboration provides end-users with a pre-processed
-and reduced data format, AOD~\cite{holtman2001cms}, containing information for events, i.e.,
-proton-proton collisions with a signature of interest, in the form of
-reconstructed particles.  This format is based on the RAW output of
-the CMS detector readout electronics and reconstructed world-wide, which is then processed through various algorithms which derive signatures of individual particles.
-Both real and simulated data are available for examination.
-
-As AOD data are too large to be iteratively processed repetitively in
-a physics analysis workflow, it is normally reduced further in
-structural complexity and content.  For the analysis under
-investigation here, this is a two-step process.  First, the AOD data
-are processed at the Notre Dame working group cluster to BEAN (Boson Exploration Analysis Ntuple) events,
-containing only trivial data containers packed in vectors.  This step
-is time and CPU intensive and its output contains data of 11.6$\,$TB to be
-analyzed by the tau analysis.
-It is performed by a small custom code framework, which is built on top of CMSSW.
-The BEAN format, production code, and
-data are shared within the analysis group looking at Higgs production
-in association with top quarks, which is formed by groups from a few
-American and European universities,
-consisting of up to a few dozen contributors.
-
-In the second step, the data are reduced to the ``Ntuple'' format,
-which contains only events matching basic quality criteria and
-fields relevant to \emph{TauRoast}.
-Again, the Notre Dame CMS groups cluster
-resources are used to perform this reduction and selection,
-running highly customized software,
-built on CMSSW and the BEAN framework,
-with code written and maintained by a small group.
-
-Once the data has been reduced to Ntuples, TauRoast can be run as a single
-process, and contains a stringent event selection to look only at high
-quality candidate events for the underlying physical process.
-Quantities from the relevant events can be
-both plotted and used in multivariate analysis to determine the level
-of expected signal in real data.
-This package is written using the CMSSW build framework,
-but only utilizes code from ROOT,
-a particle physics toolkit underlying CMSSW,
-and a few external python dependencies for convenience.
-
 \section{Observations}
@@
 \fi
-
-\section{Evolving the Artifact}
-
-It is clear that the artifact, as provided, is not in a suitable form
-for preservation.  While it might be technically possible to automatically
-capture the entire virtual machine and all of the connected filesystems,
-it would require 166.8TB of storage, which would be prohibitively expensive
-for capturing this one application alone.  Further, if multiple
-similar applications are preserved, we would miss the opportunity to identify
-common dependencies and store them once for multiple artifacts.
-A more structured approach to dependency management is needed.
-
-Figure~\ref{fig:version-evolution} shows how we have evolved this artifact
-through several stages which make it more suitable for preservation.
-In each step of evolution, we make the dependencies of the artifact
-more explicit and available for analysis and automated processing.
-As noted in the previous section, the original author provided us with
-prose instructions by email which we translated into an
-executable script.  The executable script has embedded in it
-a number of external identifiers such as URLs pointing to repositories
-and paths to networked filesystems.  As a general programming practice,
-embedding such constants into the middle of a program is unwise, and so
-we extract all of those identifiers and place them \emph{outside} the
-script in a \emph{dependency map} or just \emph{map} for short.
-The dependency map lists all of the external dependencies of the application, indicating
-the type, how they are accessed, and where they are currently located.
-The resulting script then simply refers to abstract file locations such
-as \verb$GIT$ and \verb$CVMFS$, while the map file indicates where they
-are currently located. If properly constructed, the script should not refer to any external
-resource unless it is indicated in the dependency map.  We call this idealized
-artifact an \emph{abstract script}.
-
-By extracting the dependencies into the dependency map,
-we introduce great freedom for the curator to move, transform, and otherwise
-manipulate the dependencies of the artifact without damaging the artifact itself.
-A Figure~\ref{fig:version-evolution} shows, it is straightforward for an
-automated tool to examine
-all of the dependencies in the map, download those that are missing,
-and then modify the map to point to the local copies of the dependencies.
-If we group the script, dependency map, and dependencies into a \emph{package},
-we now have a self-contained artifact that can be moved from place to place.
-In some cases, it may be safe to allow the dependency map to refer to 
-trusted remote repositories.  Whether this is advisable is a judgment that
-must be made by the user or the curator, taking into account the long-term
-stability of said repositories.
-
-However, only having the package and the dependency map is not enough. The successful execution of the application on the original machine also relies on the configuration of environment variables.
-We collected the environment variables of the original machine and transformed it into one executable script.
-If another researcher wants to repeat the application, this executable script will be first executed.
-The environment variables refer to the dynamic named values defined in the range of one computer, like \verb!$PATH! and \verb!$PYTHONPATH!.
-However, the dependency map refers to the actual storage location of path variables used in one abstract script. For example, the actual storage location of the path variable \verb!CVMFS! 
-is {\tt /data/cvmfs/grid.cern.ch}.
-
-\begin{figure}
-\centering
-\includegraphics[width=.5\textwidth]{solution3.eps}
-\caption{Relationship of Roles}
-\label{fig:solution3}
-\end{figure}
-
-The relationship of different roles involved in the application preservation and
-reproduction is shown in Figure~\ref{fig:solution3}.  The original author uses the packaging utility to generate the package for one application.
-Then the package, together with
-its map file and description file will be published. When
-another researcher wants to repeat the application, one copy of the package will be downloaded into the new machine and the application can be repeated.
-
-When we try to repeat one application on one new machine, one map file is necessary for the relocation of the data access targets, as
-show in Figure~\ref{fig:version-evolution}. 
-The map file clearly defines the real location of each dependency in the format of dependency variables - the real location of dependency variable {\tt GIT} is \path{/data/git/cms-ttH} and the real location of dependency variable {\tt CVMFS}
-is {\tt /data/cvmfs/grid.cern.ch}.
-The script only refers to the dependency variables defined in the map file.
-This design decouples the application script and the actual data access targets, which minimizes the impact of the evolution of different data dependencies
-and ensures the transparent access.
-The modification of the package only introduces the minimal changes of the map file on the client side.
-
-This basic approach to dependency management is a step in the right direction
-for dependencies that are \emph{explicit} and \emph{external} to the
-user's native execution environment.  However, it leaves two other problems unsolved.
-
-First, the basic approach requires that someone be \emph{aware} of the dependencies,
-whether it be the end user, the system administrator, or the archive curator.
-It seems reasonable to expect the user to be aware of a large dependency mentioned in a top-level script.
-But, oftentimes the dependency is embedded invisibly deep within the software stack,
-or is connected to the machine by the local system administrators.  No single party
-is likely to have complete information about all of the dependencies.
-Second, the basic approach assumes that the entire dependency is actually
-consumed by the artifact.  As we have suggested above (and will show below),
-this sort of program often only consumes a small fraction of what it does declare
-as a dependency.
-
-To address both of these problems, users and curators alike need tools that
-will automatically observe the dependencies of complex applications, to
-facilitate automatic and efficient preservation.
-
-\section{Measuring Dependencies}
-
-\begin{figure*}
-\centering
-\includegraphics[width=.8\textwidth]{workflow-parrot.eps}
-\caption{Workflow of The Fine-Grained Dependency Management Toolkit Based on Parrot}
-\label{fig:workflow-parrot}
-\end{figure*}
-
-We have developed a prototype tool to assist in the measurement and preservation
-of implicit dependencies for complex applications.
-We use Parrot~\cite{thain2005parrot} to explicitly record all
-of the files accessed by our example application, allowing us to observe how
-much of each external dependencies is used, and what local resources are implicitly used.
-Using this information, we create a \emph{reduced package} which contains
-only the files actually used by the application.
-
-Parrot is a virtual filesystem access tool which has been used to attach
-existing programs to a variety of remote I/O systems, such as HTTP, FTP, and CVMFS.
-It works by trapping an application's system calls through the Linux {\tt ptrace} debugging
-interface, and then replacing them with the desired I/O operations.  Parrot is already used
-in the high energy physics community with applications like TauRoast specifically to 
-provide access to the CMSSW software distribution via the CVMFS distributed file system.
-We made small modifications to Parrot to record a \emph{namelist} which lists all 
-of the files that an application actually accesses.
-
-Figure~\ref{fig:workflow-parrot} illustrates the measurement process.
-The starting point of this toolkit is one successful execution of the application on the native machine.
-First, we execute the actual data analysis script under Parrot to generate the namelist.
-Then, using the namelist, we generate a package containing all the necessary data
-and software for one analysis program. When another
-researcher wants to repeat the program, he only needs to obtain the package and
-execute the actual analysis program inside the package.
-
-For one execution of \emph{TauRoast}, the generated namelist includes 132,047 accessed filenames,
-along with the system calls used to access the file, such as {\tt open}, {\tt stat}, {\tt read}, etc.
-With duplicate filenames removed, the list is reduced to 67,168 files.
-Many of those entries do not exist, because they reflect attempts
-by the application to search for programs and libraries in multiple places.
-Only 22,068 entries reflect existing files or directories.
-
-The packaging tool iterates over each item of the filename list, determines the process
-mode and replication degree according to the file type (common files,
-directories, symbolic links) and the system call type, generates one package
-containing the dependencies, and summarizes the contents of the package
-as shown in Table~\ref{table:package-info}.  To the extent possible,
-the filesystem structure of the original environment is preserved.
-
-We considered several approaches to constructing the package.
-In a {\bf shallow copy}, we only copied the individual files in the namelist,
-creating only parent directories for each.  Where a directory was listed,
-we created the directory and populated it with empty files as placeholders
-to facilitate a directory listing.  In a {\bf medium copy}, we copied the
-individual files as before.  Where a directory was listed, we created
-the directories and copied the contents of the files in that directory,
-one level deep.  A {\bf deep copy} would duplicate all directories recursively,
-but this would have resulted in TB-sized packages, so we did not consider
-it further.
-
-Parrot is required to re-run the packaged artifact, in order to force
-the packaged files to appear to exist in their original locations.
-To this end, the packaging tool creates a \emph{file map} which maps
-the logical names of the files to their current physical locations, as shown in Table~\ref{table:map-file}.
-Parrot reads the file map and redirects system calls at run-time to achieve the desired effect.
-As the example suggests, special device files such as {\tt /proc} and {\tt /dev}
-are not incorporated into the package but are instead accessed natively.
-
-\begin{table}
-    \centering
-    \begin{tabular}{ll}
-    \hline
-    \bf Path used in Program & \bf Actual Location \\ \hline
-    {\tt /} & {\tt /tmp/package-hep} \\ \hline
-    {\tt /tmp/package-hep} & {\tt /tmp/package-hep} \\ \hline
-    {\tt /dev} & {\tt /dev} \\ \hline
-    {\tt ...} & {\tt ...}\\ \hline
-    \end{tabular}
-    \caption{Structure of Map File}
-    \label{table:map-file}
-\end{table}
-
-\begin{table}
-    \centering
-    \begin{tabular}{rrr}
-\hline
-                    & \bf Shallow Copy & \bf Medium Copy\\
-\hline
-    Whole Files    & 1632         & 15642\\ 
-\hline
-    Empty Files    & 14273        & 263\\
-\hline
-    Directories    & 1549         & 1549\\ 
-\hline
-    Symbolic Links & 4614         & 4614 \\
-\hline
-    \bf Total Size & \bf 21GB     & \bf 28GB \\ 
-\hline
-    \end{tabular}
-    \caption{Package Information}
-    \label{table:package-info}
-\end{table}
-
-\subsection{Tracking of Network Dependencies}
-
-\begin{figure}
-\centering
-\includegraphics[width=.6\textwidth]{git-syscall.eps}
-\caption{Exec Syscalls of a git command}
-\label{fig:git-syscall}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=.6\textwidth]{http_packet.eps}
-\caption{HTTP Request and Response}
-\label{fig:http_packet}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=.6\textwidth]{url_redirection.eps}
-\caption{An Example of URL Redirection}
-\label{fig:url_redirection}
-\end{figure}
-
-All the dependencies of one program can be divided into three categories: local file system (e.g., /usr, /lib and /lib64), remote file systems which can be mounted as local directories (e.g., /cvmfs and /hdfs), and other remote network dependencies (e.g.
-http, https and ssh).
-Through utilizing ptrace to trap each file-relevant system call used by a program, the first two categories of dependencies can be collected. 
-Motivation of tracking network dependencies: Linkrot is a common and great threat to the preservation of scientific applications.
-A URL which works normally today may be unavailable permanently.
-A method which can help the scientists figure out all the network dependencies of their applications provides the chance to evaluate the stability of each network dependencies and preserve the unstable network resources before linkrot happens.
-One direct solution to track the third category of dependencies is to utilize ptrace to check each exec system call used by a program and record each network-relevant executable and its parameters.
-However, an executable may create one or more child processes to finish some tasks, and a child process may create their own children processes.
-Figure~\ref{fig:git-syscall} shows all the processes created by a git command.
-A process with PID 998 is created to clone a remote git repository into local machine, which totally has 6 child processes.
-Moreover, a network-relevant executable name collection is necessary to identify network dependencies.
-The diversity of network-relevant executables and the large process tree generated for a network executable make this solution infeasible.
-
-Another solution to track network dependencies is to track the network sockets.
-The user process communicates with the network protocol stacks in the kernel through the network socket layer user interface on Linux.
-From the process tree shown in the above figure, the process with PID 1000 responds to create a socket, connect to a DNS server, send a DNS request packet to the DNS server and receive a DNS response packet from the DNS server.
-The information gained from the network socket tracking can be divided into three categories.
-\begin{itemize}
-\item The information of network sockets used to communicate with remote network dependences (through socket and connect system calls) can be used to figure out the port number, service name (such as, http, https, and ssh), socket type (stream and datagram),  and the domain type (inet and inet6).
-\item The contents of DNS packets can be used to figure out the hostname and IP address of each remote network dependency. 
-\item As for applications based on http protocol, all the http requests and responses can be seen, as shown in Figure~\ref{fig:http_packet}.
-However, as for applications based on https and ssh which encrypt network data using TLS/SSL, tracking network data on the socket level can only see the encrypted data.
-\end{itemize}
-
-The results of tracking network sockets used by a program involves two categories of network resource redirections, dns-level hostname redirection and website-level url redirection. 
-\begin{itemize}
-\item dns-level hostname redirection: Each DNS packet includes five parts, header, question, answer, authority, and additional.
-A DNS response packet with the type CNAME has multiple answers.
-For example, the DNS response packet which tries to resolve {\tt www3.nd.edu} includes two answers.
-The first answer provides an alias of {\tt www3.nd.edu}, {\tt www-vip.cc.nd.edu}, and the second answer maps the alias to the IP address.
-{\tt www3.nd.edu} CNAME {\tt www-vip.cc.nd.edu}
-{\tt www-vip.cc.nd.edu} A {\tt 129.74.12.151}
-The CNAME-type DNS packets leave us a question, among the hostname used by the user, the alias(es), the IP address, what should we preserve?
-\item website-level url redirection: Website-level url redirection happens when a website updates its location and still want their old users access their resources using the old url.
-Figure~\ref{fig:url_redirection} illustrates the url redirection between {\tt \url{www3.nd.edu/~ccl}} and {\tt ccl.cse.nd.edu}.
-Except for the difference of hostnames, the application layer protocols used by the old-version website and the new-version website is also different: the old website provides services through the https protocol, while the new website provides services through the http protocol.
-\end{itemize}
-
-The usage of https protocol makes detecting of website-level url redirections through tracking system calls more difficulty and even impossible.
-All the application data will be encrypted at presentation layer through the TLS/SSL protocol, which is initialized at the session layer and works at the presentation layer.
-
-\section{Evaluation}
-
-We evaluated the correctness of the reduced package and the overhead of generating the package.
-To do this, the application was repeated with the help of \emph{Original Script} (as shown in Figure~\ref{fig:version-evolution}) on the original machine. 
-Then one \emph{reduced package} was generated and verified with the help of Parrot on the original machine.
-
-Then, two different virtual machines (VM) - one VM from the Notre Dame Cloud Platform based on KVM and one VM from the Amazon EC2 Platform based on Xen, were employed to further verify the correctness of the reduced package.
-
-We first repeated the example from scratch using the Script translated from the original email on the original machine and counted the time consumption and data size. 
-Then based on the successful execution of Original Script, we evaluated Reduced Package - one package containing necessary dependencies is generated, and then the time consumption and data size is analyzed.
-
-To measure time consumption, we counted the time used to obtain remote software dependencies, build the environment, and analyze the dataset.
-We also counted the time used to obtain the namelist and to generate the package.
-To measure data size, we can easily figure out the size of each data and code source inside the package under Reduced Package.
-Original Script does not support mining of implicit dependencies.
-As for remote sources, we can figure out the named size through the analysis script.
-However, it is hard to figure out the named size of each local source.
-Instead, we only knew that total size of each file system is very large.
-
-Table~\ref{table:time-2nd3rd} shows the execution time comparison between
-Original Script and Reduced Package.
-Reduced Package is faster than Original Script, because all the software copied into the package has been compiled and the Software Acquisition stage is not necessary.
-and all the environment building only takes 4 seconds,
-We were surprised that Reduced Package even reduces the actual analysis time. 
-The reason for this is that data is obtained through accessing HDFS in Original Script, but is copied into the package in Reduced Package.
-This localization of experimental data speeds up the data analysis process, resulting the actual analysis time reducing from 20 minutes to 13 minutes.
-
-\begin{table}
-    \centering
-    \begin{tabular}{lrr}
-    \hline
-    \bf Task Category & \bf Original Script & \bf Reduced Package \\ \hline
-    Obtain Namelist & N/A & 28min 28s \\ \hline
-    Generate Package & N/A & 85min 51s \\ \hline
-    Software Acquisition & 8min 11s & N/A \\ \hline
-    Environment Build & 5min 49s  & 4s \\ \hline
-    Analysis Code & 20min 31s & 13min 04s \\ \hline
-    \end{tabular}
-    \caption{Execution Time Comparison between Original Script and Reduced Package}
-    \label{table:time-2nd3rd}
-\end{table}
-
-Table~\ref{table:time-2nd3rd} also illustrates the time used to
-obtain the namelist and to generate the package. 
-The time used for these two steps is longer than the execution time,
-because each filename of the list, together with its system call type, needs to be checked, and the structure of each directory item must be maintained.
-However, 
-this is only done once.
-Once the package is
-generated, many users can directly obtain the package and repeat the application 
-separately.
-
-Table~\ref{table:size-original-real} on page 2 illustrates the total size, named size in the example and actually used size of each remote source (the first 4 items) and local source (the remaining 5 items).
-The third column corresponds to the data size of Reduced Package and can be easily figured out, because all the necessary data has been copied into the package.
-Original Script does not support measuring implicit dependencies.
-As for remote sources, we can figure out the named size through the analysis script.
-However, it is hard to figure out the named size of each local source.
-Instead, we only knew that total size of each file system is very large.
-
-\begin{table}
-	\centering
-	    \begin{tabular}{llrrr}
-	        \hline
-	        \bf Name & \bf Location & \bf Total & \bf Named & \bf Used \\ 
-	        \hline
-	        CMSSW code     & CVS & 88.1GB & 448.3MB & 6.3MB\\ \hline
-	        Tau source       & Git & 73.7MB & 73.7MB & 6.7MB \\ \hline
-	        PyYAML binaries    & HTTP & 52MB & 52MB & 0KB \\ \hline
-	        .h file       & HTTP& 41KB & 41KB & 0KB \\ \hline \hline
-	        Ntuples data    & HDFS& 11.6TB & N/A& 20GB \\ \hline
-	        Configuration & CVMFS & 7.4GB & N/A & 103MB \\ \hline
-	        Linux commands & localFS & 110GB &  N/A & 68.4MB \\ \hline     
-	        HOME dir& AFS &12GB & N/A & 32MB\\ \hline
-	        Misc commands & PanFS & 155TB & N/A  & 1.6MB \\ \hline
-	        Total      &    & 166.8TB            & N/A & 21GB \\ \hline
-	    \end{tabular}
-	    \caption{Data and Code Used by Tau Roast}
-	    \label{table:size-original-real}
-\end{table}
-%	\begin{tablenotes}
-%	      \small
-%	      \item The first column illustrates the total size of each data and software source; 
-%	            the second column illustrates the size of the named files from each source;
-%	            the third column illustrates the size of actually used data from each source.
-%	            N/A denotes it is hard to figure out the named size of implicit dependencies directly.        
-%	    \end{tablenotes}
-
-To further verify the correctness of Reduced Package on other machines, two different machines are employed -
-one virtual
-machine~\cite{goldberg1974survey} from the Notre Dame Cloud Platform based on KVM sharing the same kernel version with the original machine,
-and one virtual machine from  the Amazon EC2~\cite{amazon2010amazon} Platform based on Xen.
-
-Table~\ref{table:config-vm} illustrates the configuration of 
-each machine and the execution time of the application on each machine.
-All the machines adopt the x86\_64 hardware platform and Linux kernel.
-Both of the two VMs repeated the application with the help of the package generated on the original machine successfully.
-The execution time on one machine greatly depends on its hardware configuration.
-
-\begin{table}
-    \centering
-    \begin{tabular}{lrrrr}
-    \hline
-    \bf Machine Type & \bf Distro Version & \bf CPU Cores & \bf Mem (GB) & \bf Execution Time \\ \hline 
-    Original Machine &  Red Hat 5.10 & 64 & 125 & 13min 04s\\  \hline
-    KVM (Notre Dame) & CentOS 5.10 & 4 & 2 & 21min 38s\\ \hline
-    Xen (EC2) & Red Hat 5.9 & 16 & 60.5 & 13min 30s\\ \hline
-    \end{tabular}
-    \caption{Evaluation of Different Machines}
-    \label{table:config-vm}
-\end{table}
-
-In summary, we demonstrate that the application can be repeated with the help of the reduced package on one different machine with the required hardware architecture and OS kernel version.
-%*****hmeng-doubt:Another reason for the packaging utility is that not all the data and software generated by the second version script is used during the the actual data analysis.
-The packaging utility can help us find out the optimal subset of data and software involved in one actual data analysis.
-%*****hmeng-doubt: this point is not the motivation. but one achievement comes together. out of imagination.
-
-\begin{figure}
-\centering
-\includegraphics[width=.6\textwidth]{preservation-integration.eps}
-\caption{Preserving Multiple Artifacts}
-\label{fig:Preservation integration}
-\end{figure}
-
-\section{Open Problems}
-
-Figure~\ref{fig:Preservation integration} shows the rough information
-architecture of the archive that we imagine for complex
-scientific software like TauRoast.
-Each artifact to be preserved is a package that consists of a top-level
-script to invoke the software, a dependency map, and the dependencies
-themselves, which may be external to the original program.  The artifacts
-are then ingested into the archive, where shared dependencies are stored
-only once.  In cases where an artifact has a dependency on a trusted
-(or very large) remote archive, the dependency may simply be tracked
-. A researcher that wishes to reproduce a given
-result need only refer to the unique identifier of the artifact, and will
-be able to automatically extract all of the dependent components of
-that artifact.
-
-For example, in Figure~\ref{fig:Preservation integration} Script 1 depends on items A, B, and C.
-Items A and B are ingested into the archive, where B is shared with Script 2.
-Item C is stored in another trustworthy repository and is tracked rather than ingested.
-When Script 1 is exported from the repository, items A and B are exported along with it, while C can be copied or remain remote, according to the end user's choice.
-
-As simple as that picture appears, there are a number of problems that must be solved to get there:
-
-{\bf Measure the Mess or Force Cleanliness?}  Two radically different approaches to dependency tracking are possible.
-The first is to allow end users complete freedom to construct their environment as desired, then \emph{measure} what items were actually used.
-As we have shown, this is possible, but has significant overheads and does not fully preserve the structure or intent of the end user.
-The second approach is to \emph{force} users to work in a clean environment in which no resource can be used until a proper dependency has been declared.
-This ensures that all dependencies are known in advance (and made explicit to the end user) but places a variety of restrictions on the user's daily work, and may prevent creative approaches that do not fit within the curator's view of how programs should be structured.
-Whether end users will accept the inconvenience of forced cleanliness for the benefits of reproducibility can only be discovered through experiment.
-
-{\bf Granularity of Dependencies.}  Dependencies could be handled
-at many different levels of granularity.  In this work, we have shown
-how they can be handled at the level of entire repositories or individual files.
-Other possible choices might include intermediate-sized software packages
-(like RPM) or in the case of experimental data, even portions of individual large files.  Clearly, a larger granularity will result in 
-simpler dependency maps, and more wasted space; smaller granularity results
-in complex dependency maps and less wasted space.  A hybrid solution may
-be able to combine both by storing large granularity dependencies, but
-selecting sub-items out of objects when efficiency demands it.
-
-{\bf Scope of Reuse.}  We have presented the data preservation
-problem as primarily one of accurate reproduction: if a result depends
-on running program X, we must be able to run exactly X again.  However,
-the goal of scientific reproducibility is rarely limited to running
-\emph{precisely} what a predecessor did. Often, the objective is to
-change a parameter or a data input in order to see how the result is affected.
-To that end, the preservation system must capture enough of the surrounding
-material to permit modifications to succeed.  From this perspective,
-a larger granularity of preservation is desirable.  A better understanding of
-how end users will consume preserved software will help to shape how
-software is preserved in the first place.
-
-{\bf Dependency Detection.}  If we allow users to work in uncontrolled
-environments, then we must have better methods for understanding the dependencies  of existing programs.  At first, we relied on an expert reader to examine
-the user's script and extract the dependencies.  This is clearly
-not a scalable approach.  We then demonstrated an automated method of observing
-what individual files are accessed by a program. However, this does
-not cover all types of dependencies, particularly those that are networked.
-More sophisticated observation techniques could infer higher-level information,
-such as the RPM package names of the files accessed, the URLs of remote
-repositories named throughout the program, or even the addresses and names of networked dependencies like databases and filesystems.
-
-{\bf Source, Binary, or Both?}  A science archive might choose to retain
-the source code of an artifact or the binary code that can actually run in a given environment.
-While conventional wisdom suggests that access to source code is critical for the long term
-survival and evolution of a piece of software, it also requires the maintenance of an enormous
-amount of supporting software in the form of compilers, linkers, and supporting libraries for
-the target platform.  Rebuilding all of these for every invocation of an artifact is
-likely to have excessive cost.  We suggest that a realistic repository will have to
-maintain \emph{both}: the source describes the ultimate meaning of the code, but
-the binary is an important performance cache, a backup if the compiler toolchain should
-fail to be preserved, and a checksum to ensure that a source artifact was rebuilt correctly.
-
-\section{Related Work }
-
-Generally, there are three approaches to preserve software environment:
-hardware preservation, migration and emulation.  Hardware
-preservation preserves the original software and its original operating
-environment. 
-Software migration technique~\cite{cifuentes1996binary,mancl2001refactoring} was used to facilitate running software on new machines.
-However, migration often involves the re-compiling and re-configuring
-the source code to accommodate a new hardware platform and software environment.
-Emulation recreates the original software and hardware environment by
-programming future platforms and OSs. One common solution to implement this is
-virtual machine. According to the usage and emulation degree of the real
-machine, virtual machine can be divided into system virtual machine and process
-virtual machine. 
-The working principle, design principle and
-performance evaluation of system virtual machine were illustrated in~\cite{goldberg1974survey, smith2005architecture}. 
-The
-functionality of system VM to support different guest operating systems was illustrated in~\cite{barham2003xen,kivity2007kvm,rosenblum1999vmware}.
-F. Esquembre~\cite{esquembre2004easy} illustrated how JVM, one process virtual machine, can expedite the creation of
-scientific simulations in Java. 
-The pros and cons of these three approaches were discussed in~\cite{matthews2009towards,phelps2005no,hong2010software}.
-
-The preservation of computing environment and software environment was treated as one entirety in~\cite{matthews2009towards,phelps2005no,hong2010software}.
-However, frequently changing experiment software makes the maintenance of the preserved experimental environment very complex.
-CernVM~\cite{buncic2010cernvm} treated them as two different categories.
-The preservation of computing environment is implemented with CernVM, and the preservation of software environment is based on a CernVM filesystem(CVMFS) specifically designed for efficient software distribution.
-
-The importance of preserving software in source code format was emphasized in~\cite{zabolitzky2002preserving,castagne2013consider}. 
-However, CVMFS~\cite{buncic2010cernvm} published pre-built and configured experiment software releases to avoid the time-consuming software building procedure.
-
-Attempts from different perspectives to facilitate the reproduction of scientific experiments utilizing a preserved software library have been made. 
-The software distribution mechanism over network was discussed in~\cite{compostella2010cdf, blomer2011cernvm}.
-J.
-R.
-Rice et al.~\cite{rice1996scientific} made the reproduction process easier through the integration of user interface, scientific software libraries, knowledge base into problem-solving environment.
-S. R. Kohn et al.~\cite{kohn2001divorcing} tried to enable the creation and distribution of language-independent software library by addressing language interoperability.
-a scalable, distributed and dynamic workflow system for digitization processes was proposed in~\cite{schoneberg2013scalable}.
-A distributed archival network was designed in~\cite{subotic2013distributed} to facilitate process-oriented automatic long-term digital preservation.
-M. Agosti et al.~\cite{agosti2012envisage} aimed to help non-domain users to utilize the digital archive system developed for domain experts.
-
-Current mechanisms of preserving scientific experiments assume that all the data and software mentioned in the experiments are necessary for the reproduction of the experiments.
-However, this is not always right.
-In some cases, the original author may leave additional code referring to irrelative data and software in the program.
-One mechanism, which can figure out the absolutely relevant data and software of one experiment, is important for both the preservation and reproduction of scientific experiments.
-
-B. Matthews et al.~\cite{matthews2008significant} introduced one conceptual framework for software preservation from several case studies of software preservation.
-One tool to capture software preservation properties within a software environment was designed in~\cite{matthews2010framework} through a series of case studies conducted to evaluate the software preservation framework.
-L. R. Johnston et al.~\cite{johnston2014workflow} proposed one overall data curation workflow for 3-5 case studies of preserving research data.
-Two case studies~\cite{borgman2012data} were conducted to figure out the properties of data to be reused in the future.
-
-\section{Postscript}
-
-We began this work in late 2013, generating a reduced package for \emph{TauRoast} based
-on the configuration of a standard machine at Notre Dame at the time.  In the course
-of writing this paper in spring 2014, almost everything about the computing environment
-changed: the operating system was upgraded, a new version of CMSSW was released, and
-our local HEP users switched from using CVS to CVMFS for accessing CMSSW.
-The original script provided by the author failed to run on the same machine.
-But, the reduced package we created three months earlier in the old environment
-worked just fine on the new machine.
-
-\section*{Acknowledgments}
-
-This work was supported in part by National Science Foundation grants PHY-1247316 (DASPOS), 
-OCI-1148330 (SI2) and PHY-1312842.
-The University of Notre Dame Center for Research Computing scientists and engineers provided critical technical assistance throughout this research effort.
-
-Copyright (C) 2014 The University of Notre Dame
-
-This work is licensed under the Creative Commons Attribution 4.0 License.
-
-\bibliographystyle{plain}
-\bibliography{cclpapers,this}
-
-\end{document}

### 2015-01-06 paper.tex
Put each section into a separate tex file

--- 2015-01-02 paper.tex
@@
 \and
-	Matthias Wolf\inst{2}
-\and
-	Douglas Thain\inst{3}
+	Douglas Thain\inst{2}
 }
@@
 	\email{hmeng@nd.edu}
-\and
-	Department of Physics,
-	University of Notre Dame,
-	Notre Dame, Indiana, USA
-	\email{mwolf3@nd.edu}
 \and
@@
 
-\authorrunning{Meng, Wolf and Thain}
+\authorrunning{Meng, and Thain}
 
@@
 
-\section{Introduction}
+\input {intro}
+\input {tauroast}
+\input {observation}
+\input {evolution}
+\input {measure}
+\input {evaluation}
+\input {problems}
+\input {related_work}
+\input {postscript}
 
-Reproducibility is a cornerstone of the scientific process~\cite{borgman2012data}.
-In order to understand, verify, and build upon previous work,
-one must be able to first recreate previous results by applying
-the same methods. Historically, reproducibility has been
-accomplished through painstaking detailed documentation recorded
-in lab notebooks, which are then summarized in peer-reviewed publications.
-But as science increasingly depends on computation,
-reproducibility must also encompass the environments, data, and software
-involved in each result~\cite{zabolitzky2002preserving}. It is widely recognized that informal
-descriptions of software and systems -- although common -- are insufficient
-for reproducing a computational result accurately.
-A more automated and comprehensive approach is required.
+\section*{Acknowledgments}
 
-The reproduction of a computation has three broad components,
-each of which suggests somewhat different approaches:
+This work was supported in part by National Science Foundation grants PHY-1247316 (DASPOS), 
+OCI-1148330 (SI2) and PHY-1312842.
+The University of Notre Dame Center for Research Computing scientists and engineers provided critical technical assistance throughout this research effort.
 
-\begin{itemize}
-\item The {\bf computing environment}, consisting of the basic hardware and the operating system which can be preserved as physical artifacts or as a combination of virtual machine monitors (hardware) and virtual machine images (operating system)~\cite{matthews2009towards}.
-\item The {\bf scientific data} to be analyzed has historically received the most attention for curation.
-In a large, well-organized project, it may be stored in a  data repository or database management system, with associated documentation and a curation strategy.
-In a small effort, it could simply be a handful of files.
-\item The {\bf software environment} includes the source code, binaries, scripts, configuration files, and everything else needed to execute the desired code.
-As with data, the software could be drawn from a well-managed software repository, or it could be a handful custom scripts that exist in the user's home directory.
-\end{itemize}
+Copyright (C) 2014 The University of Notre Dame
 
-In a very abstract sense, reproducing a computation is trivial.
-Assuming a computation is deterministic, one must simply
-preserve all of the inputs to a computation, then re-run
-the same code in an equivalent environment, and the same result
-will be produced.  For a small custom application on a modest
-amount of data, this could be accomplished by capturing the
-complete environment,
-data, and software within a single virtual machine image,
-and then depositing the virtual
-image into a curated environment.  The publication could
-then simply refer to the identifier of the image, which the
-interested reader can obtain and re-use. This approach has
-been used to some success with systems~\cite{castagne2013consider}.
-\footnote{Of course, we are glossing over the problem that hardware
-architectures and virtual machines also change, so one must also
-preserve the VMM software necessary to run the image.  The VMM itself
-depends on a software environment which must also be preserved.
-A long-term preservation system might end up running a whole
-stack of nested virtual machines in order to provide the desired
-environment! }
+This work is licensed under the Creative Commons Attribution 4.0 License.
 
-However, this simple approach is not sufficient for large applications
-that are run in complex environments.
+\bibliographystyle{plain}
+\bibliography{cclpapers,this}
 
-\begin{itemize}
-\item There may be {\bf implicit dependencies} on items that are
-not apparent to the end user.  For example, they may understand that
-they rely on a particular data analysis package, but would have
-no reason to know that the package has further dependencies on
-other libraries and configuration files.  Or, they may know that
-the computation only runs correctly on a particular machine, but
-not know this is because it relies on a filesystem that
-is mounted only on that machine.
-
-\item The {\bf granularity} of the dependencies may not be well understood.
-For example, the user may understand that a computation depends upon
-a data collection that is 1TB in overall size, but not have detailed
-knowledge that it only requires three files totalling 300MB out of that
-whole collection.
-
-\item There may be dependencies upon {\bf networked resources} that
-are inherently external to the system, such as a database, a code
-repository~\cite{cms2006cmssw}, or a scalable filesystem~\cite{blomer2011cernvm}.  For such resources, it
-must be decided whether the dependency will simply be noted, or if it
-must be incorporated whole or in part.
-
-\item Where {\bf common dependencies} are widely used, it may be inefficient or
-impossible to store one copy of each dependency for each archived object.
-Some form of sharing or de-duplication is necessary in order to keep
-the archive to a reasonable size.
-\end{itemize}
-
-We do not claim to have solved these problems in any comprehensive
-way.  Rather, our aim in this paper is to highlight the scope
-of the problems by presenting a case study of one complex application.
-The application is presented to us
-first in the form of an email that describes in prose how to install
-the software and run the analysis.  We perform several successive
-refinements to convert it into an executable and preservable object.
-We then develop techniques for reducing the size of the dependencies
-that are necessary for the object to function, and we demonstrate
-the preserved object functioning correctly in three different
-physical and cloud environments.
-We describe how each of these techniques may interact with
-a future archive of preserved software artifacts, and conclude with
-some reflections on the challenges of preservation and advice for future efforts.
+\end{document}
 
@@
 \fi
-
-\begin{figure}[t]
-\centering
-\includegraphics[width=.5\textwidth]{data-code-size.eps}
-\caption{Inputs to Tau Roast}
-\label{fig:data-code-size}
-\end{figure}
-
-\section{Overview of Tau Roast}
-
-Within the ongoing investigation of the Higgs boson at the CMS
-detector, part of the LHC at CERN~\cite{collaboration2008cms}, the Higgs production in association
-with two top quarks allows measuring the Higgs coupling strength to
-top quarks~\cite{chatrchyan2013search}.  As the Higgs boson is too short-lived to be detected
-itself, it has to be reconstructed from its decay products.
-
-The application which is the study of this paper is called \emph{TauRoast}.
-It searches for cases where the Higgs boson decays to two tau leptons.
-Since the tau leptons are very short-lived, they are not observed directly, but by the particle decay products 
-that they generate.  So, the analysis must search for detector
-events that show a signature of decay products compatible with both hadronic tau and top decays.  Properties of such events are used to distinguish
-the events of interest (Higgs decays) from all other events and
-are also used in further statistical analysis.
-
-Figure~\ref{fig:data-code-size} shows that both the code and data
-that form \emph{TauRoast} are drawn from large repositories through
-multiple steps of reduction.  A preservation strategy must weigh
-whether to store the large repositories completely, the fragments
-used by an artifact, or something in between.
-
-{\bf Code Sources.} Like many scientific codes, the central algorithm
-of \emph{TauRoast} is expressed in a relatively small amount of
-custom code developed by the primary author.  But, the code cannot
-run at all without making use of an enormous collection of software
-dependencies.  Some of these dependencies are standard to operating
-systems worldwide, some are standardized across the entire high-energy
-physics field, some are particular to small collaborative groups,
-and a few are very specific to a single researcher.
-
-The largest of these repositories is the CMS Software Distribution (CMSSW)~\cite{cms2006cms},
-a carefully-curated selection of software packages which is distributed
-in several forms.  Historically, components of CMSSW were obtained by checking components
-of the source out of CVS (CMSSW source codes were moved from CVS to git recently), or by installing a complete binary package on a shared
-filesystem within an HPC center.  In recent years, distribution has moved to
-an on-demand delivery system known as CVMFS~\cite{blomer2011cernvm}, which
-provides a filesystem interface that transparently accesses a remote repository.
-The content of CMSSW is managed very carefully by a centralized team whose main goal
-is to ensure that the current version of the software operates correctly
-on the operating systems and architectures currently in use.  However,
-preservation is not a specific objective of the system, and so there is
-no particular guarantee that old versions of CMSSW will continue to
-operate indefinitely.
-
-CMSSW contains many different tools, libraries, and utilities.
-No single code uses anywhere close to all of these.
-But, because it is widely used within the experimental researchers, it is common for users to simply expect that a particular version of the entire repository is available.
-
-{\bf Data Sources.}
-The CMS collaboration provides end-users with a pre-processed
-and reduced data format, AOD~\cite{holtman2001cms}, containing information for events, i.e.,
-proton-proton collisions with a signature of interest, in the form of
-reconstructed particles.  This format is based on the RAW output of
-the CMS detector readout electronics and reconstructed world-wide, which is then processed through various algorithms which derive signatures of individual particles.
-Both real and simulated data are available for examination.
-
-As AOD data are too large to be iteratively processed repetitively in
-a physics analysis workflow, it is normally reduced further in
-structural complexity and content.  For the analysis under
-investigation here, this is a two-step process.  First, the AOD data
-are processed at the Notre Dame working group cluster to BEAN (Boson Exploration Analysis Ntuple) events,
-containing only trivial data containers packed in vectors.  This step
-is time and CPU intensive and its output contains data of 11.6$\,$TB to be
-analyzed by the tau analysis.
-It is performed by a small custom code framework, which is built on top of CMSSW.
-The BEAN format, production code, and
-data are shared within the analysis group looking at Higgs production
-in association with top quarks, which is formed by groups from a few
-American and European universities,
-consisting of up to a few dozen contributors.
-
-In the second step, the data are reduced to the ``Ntuple'' format,
-which contains only events matching basic quality criteria and
-fields relevant to \emph{TauRoast}.
-Again, the Notre Dame CMS groups cluster
-resources are used to perform this reduction and selection,
-running highly customized software,
-built on CMSSW and the BEAN framework,
-with code written and maintained by a small group.
-
-Once the data has been reduced to Ntuples, TauRoast can be run as a single
-process, and contains a stringent event selection to look only at high
-quality candidate events for the underlying physical process.
-Quantities from the relevant events can be
-both plotted and used in multivariate analysis to determine the level
-of expected signal in real data.
-This package is written using the CMSSW build framework,
-but only utilizes code from ROOT,
-a particle physics toolkit underlying CMSSW,
-and a few external python dependencies for convenience.
-
-\section{Observations}
-
-\emph{TauRoast} was provided to us in the form of an
-email which described, in prose, how to obtain the source,
-build the program, and run it correctly on one specific
-machine at our home institution, with no particular guarantee that
-it will run anywhere else in the world.
-Although this starting point may seem extreme, it is
-perfectly natural for collaborators to share configurations
-with each other in this form, and to rely on the presence
-of a working environment with appropriate dependencies already
-installed.  From this starting point, the authors played the
-role of curators, whose job it is to prepare the application
-for permanent archival.
-
-First, we elaborated the email instructions into an
-executable script that obtains the dependencies and then
-executes the analysis.  The script declares the necessary
-environment variables, downloads and checks out the necessary source code,
-builds it appropriately, calls initialization scripts in
-the dependent software, and then runs the analysis.
-A few rounds of correction with the original author were necessary
-to obtain all the dependencies and run the artifact correctly.
-(The original instructions introduced in the email also indicated how to run the application
-within a production batch system.  For the purposes of preservation,
-we consider the execution infrastructure to be distinct from the application,
-and leave it out of consideration for now.)
-
-The process of elaborating the program into a script revealed
-several observations about this type of application:
-
-\begin{itemize}
-
-\item {\bf Many Explicit External Dependencies.}  TauRoast depends on a large number of
-external dependencies, each with a different access method and data source.
-While we knew in advance that it depended upon the large CMSSW distribution,
-it was not apparent until elaborating the script that it depended upon
-two different Github repositories for the Tau source,
-a CVS server at CERN for some configuration information, a public web page
-for the PyYAML library, and the public home page of a Notre Dame student
-for one missing header file.  (The latter is particularly troubling!)
-While, at some level, the authors and users of these software know of these dependencies, they are often missing in
-informal communications or forgotten once the dependency is installed.
-However, once known, they are at least expressed explicitly within the script.
-
-\item {\bf Many Implicit Local Dependencies.} A much harder problem is that the
-application assumed the presence of many different components in the local
-filesystem view. It would be tempting to capture all of these by simply
-storing a virtual machine image containing the local filesystem. However,
-the application depended on no less than {\bf five} networked filesystems
-available on a particular machine available to the author:
-the data to be analyzed was stored on an HDFS~\cite{borthakur2008hdfs} cluster,
-some configuration data was stored on a CVMFS~\cite{blomer2011cernvm} filesystem,
-and a variety of software tools were on an NFS~\cite{howard1988scale},
-PanFS~\cite{welch2008scalable} and AFS~\cite{sandberg1985design} systems.
-The original authors were not aware of many of these dependencies,
-because they simply relied on local administrators to configure the
-software and make it available.
-
-\item {\bf Configuration Complexity.}  As a means of controlling the complexity
-of dependent software packages, the high energy physics community has developed
-a number of tools that perform run-time configuration and consistency checks
-of the available software.  {\tt scram} is the software management tool used
-by the CMS experiment.  Before running any code, {\tt scram} is used to locate
-the appropriate version of software,  set environment variables such as the PATH, run any
-tool-specific configuration, and do the same for all software on which it depends.
-If the correct versions are not available, {\tt scram} halts and emits an error.
-While this procedure has great value for consistency, it also introduces a significant cost
-because it involves a large number of nested scripts traversing a filesystem,
-repeatedly looking up metadata.  In our example, the time to perform this configuration
-with a cold cache is about 14 minutes, which is almost as large as the actual analysis
-run, which takes 20 minutes.
-
-\begin{figure*}[t]
-\centering
-\includegraphics[width=.8\textwidth]{version-evolution.eps}
-\caption{Version Evolution}
-\label{fig:version-evolution}
-\end{figure*}
-
-\item {\bf High Selectivity.}  Although the total size of the resources accessed by this
-program is very large, the size of the data and software actually used are much smaller.
-Often, an entire repository or data source is named within the script, but the program
-only needs a handful of items from that source.  For example, the data is stored on an
-HDFS filesystem with 11.6TB of data, but only 20GB are actually consumed by the program. 
-The reason for this great reduction is at first each BEAN event contains a large amount of information, and the TauAnalysis throws away a lot of the irrelevant event information, keeping only the relevant bits.
-The CMSSW repository is 88.1GB in total
-but only 448.3MB of source is checked out, and the actually used software only
-measured 6.3MB.  In a few cases, a source of software is named but never actually accessed.
-(For example, our original script includes the Open Science Grid software stack in the PATH, but does not actually use it.)
-We suspect that end users are accustomed to missing dependencies and thus get in the habit of adding commonly used software,
-whether it is needed or not.
-
-\item {\bf Rapid Changes in Dependencies.}  Over the course of three months
-between collecting the initial email, analyzing the program, and writing this
-paper, the computing environment continuously changed.  The CMSSW software
-distribution released a new version, the target execution environment was upgraded
-to a new operating system, and the application deprecated the use of CVS for obtaining
-the software.  While the users of this software seem be accustomed to constant change,
-any preservation technique will have to be very cautious about relying upon an
-external service, even one that may appear to be highly stable.
-
-\end{itemize}
-
-\if 0
-
-\begin{table}
-    \centering
-    \begin{tabular}{|l|}
-        \hline
-        {\bf Version 1: Email}\\ \hline
-        1. Create a CMS release,\\
-            \hspace{9pt} e.g. {\tt cmsrel CMSSW\_5\_3\_11\_patch3} \\
-        2. Install the BEAN packages as the instructions: \\
-            \hspace{9pt} {\tt \url{https://github.com/cms-ttH/BEAN/blob/...}}\\
-        3. Install grid-control: \\ 
-            \hspace{9pt} {\tt svn co \url{https://ekptrac.physik.uni-ka/...}} \\
-        4. INstall the TauAnalysis package: \\
-           \hspace{9pt} {\tt git clone \url{https://github.com/matz-e/...}} \\
-           \hspace{9pt} {\tt scram b -j32} \\
-        5. Fix grid\_control.cfg and run it. \\
-        6. Perform the actual tau roast program. \\ 
-        \hline
-        {\bf Version 2: Script}\\ \hline
-        {\tt setenv CMSSW\_BASE CMSSW\_5\_3\_11\_patch3} \\
-        {\tt cmsrel \$HOME/\$CMSSW\_BASE} \\
-        {\tt cvs co -r V03-09-23 PhysicsTools/PatUtils} \\
-        {\tt git clone \url{https://github.com/cms-ttH/BEAN.git}} \\
-        {\tt wget -r \url{http://nd.edu/~abrinke1/...}} \\
-        {\tt scram b -j32} \\
-        {\tt wget \url{http://pyyaml.org/download/pyyaml/PyYAML...}}\\
-        \#the experiment data is from HDFS \\
-        {\tt cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10}\\
-        {\tt cmsenv}\\
-        {\tt python setup.py install --user} \\
-        {\tt scripts/roaster data/generic\_ttl.yaml} \\ 
-        \hline
-        {\bf version 3: Formulated Script} \\ \hline
-        {\tt setenv CMSSW\_BASE CMSSW\_5\_3\_11\_patch3} \\
-        {\tt setenv {\bf GIT} \url{https://github.com}} \\
-        {\tt setenv {\bf PYYAML} \url{http://pyyaml.org}} \\
-        {\tt setenv {\bf ND} \url{http://nd.edu}} \\
-        {\tt cmsrel \$HOME/\$CMSSW\_BASE} \\
-        {\tt cvs co -r V03-09-23 PhysicsTools/PatUtils} \\
-        {\tt git clone \${\bf GIT}/cms-ttH/BEAN.git} \\
-        {\tt wget -r \${\bf ND}\url{/~abrinke1/ElectronEffectiveArea.h}} \\
-        {\tt scram b -j32} \\
-        {\tt wget \${\bf PYYAML}/download/pyyaml/PyYAML...}\\
-        \#the experiment data is from HDFS \\
-        {\tt cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10}\\
-        {\tt cmsenv}\\
-        {\tt python setup.py install --user} \\
-        {\tt scripts/roaster data/generic\_ttl.yaml} \\ 
-        \hline
-       {\bf Version 4: Fine-Grained Toolkit - Package}\\ \hline
-        {\tt setenv CMSSW\_BASE CMSSW\_5\_3\_11\_patch3} \\
-        {\tt setenv {\bf GIT} \url{https://github.com}} \\
-        {\tt setenv {\bf PYYAML} \url{http://pyyaml.org}} \\
-        {\tt setenv {\bf ND} \url{http://nd.edu}} \\
-        {\tt cmsrel \$HOME/\$CMSSW\_BASE} \\
-        {\tt cvs co -r V03-09-23 PhysicsTools/PatUtils} \\
-        {\tt git clone \${\bf GIT}/cms-ttH/BEAN.git} \\
-        {\tt wget -r \${\bf ND}\url{/~abrinke1/ElectronEffectiveArea.h}} \\
-        {\tt scram b -j32} \\
-        {\tt wget \${\bf PYYAML}/download/pyyaml/PyYAML...}\\
-        \#the experiment data is from HDFS \\
-        {\tt cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10}\\
-        {\tt cmsenv}\\
-        {\tt python setup.py install --user} \\
-        {\tt scripts/roaster data/generic\_ttl.yaml} \\ 
-        \hline
-    \end{tabular}
-    \caption{Scripts of each Solution}
-    \label{table:scripts}
-\end{table}
-
-\fi
-
-\section{Evolving the Artifact}
-
-It is clear that the artifact, as provided, is not in a suitable form
-for preservation.  While it might be technically possible to automatically
-capture the entire virtual machine and all of the connected filesystems,
-it would require 166.8TB of storage, which would be prohibitively expensive
-for capturing this one application alone.  Further, if multiple
-similar applications are preserved, we would miss the opportunity to identify
-common dependencies and store them once for multiple artifacts.
-A more structured approach to dependency management is needed.
-
-Figure~\ref{fig:version-evolution} shows how we have evolved this artifact
-through several stages which make it more suitable for preservation.
-In each step of evolution, we make the dependencies of the artifact
-more explicit and available for analysis and automated processing.
-As noted in the previous section, the original author provided us with
-prose instructions by email which we translated into an
-executable script.  The executable script has embedded in it
-a number of external identifiers such as URLs pointing to repositories
-and paths to networked filesystems.  As a general programming practice,
-embedding such constants into the middle of a program is unwise, and so
-we extract all of those identifiers and place them \emph{outside} the
-script in a \emph{dependency map} or just \emph{map} for short.
-The dependency map lists all of the external dependencies of the application, indicating
-the type, how they are accessed, and where they are currently located.
-The resulting script then simply refers to abstract file locations such
-as \verb$GIT$ and \verb$CVMFS$, while the map file indicates where they
-are currently located. If properly constructed, the script should not refer to any external
-resource unless it is indicated in the dependency map.  We call this idealized
-artifact an \emph{abstract script}.
-
-By extracting the dependencies into the dependency map,
-we introduce great freedom for the curator to move, transform, and otherwise
-manipulate the dependencies of the artifact without damaging the artifact itself.
-A Figure~\ref{fig:version-evolution} shows, it is straightforward for an
-automated tool to examine
-all of the dependencies in the map, download those that are missing,
-and then modify the map to point to the local copies of the dependencies.
-If we group the script, dependency map, and dependencies into a \emph{package},
-we now have a self-contained artifact that can be moved from place to place.
-In some cases, it may be safe to allow the dependency map to refer to 
-trusted remote repositories.  Whether this is advisable is a judgment that
-must be made by the user or the curator, taking into account the long-term
-stability of said repositories.
-
-However, only having the package and the dependency map is not enough. The successful execution of the application on the original machine also relies on the configuration of environment variables.
-We collected the environment variables of the original machine and transformed it into one executable script.
-If another researcher wants to repeat the application, this executable script will be first executed.
-The environment variables refer to the dynamic named values defined in the range of one computer, like \verb!$PATH! and \verb!$PYTHONPATH!.
-However, the dependency map refers to the actual storage location of path variables used in one abstract script. For example, the actual storage location of the path variable \verb!CVMFS! 
-is {\tt /data/cvmfs/grid.cern.ch}.
-
-\begin{figure}
-\centering
-\includegraphics[width=.5\textwidth]{solution3.eps}
-\caption{Relationship of Roles}
-\label{fig:solution3}
-\end{figure}
-
-The relationship of different roles involved in the application preservation and
-reproduction is shown in Figure~\ref{fig:solution3}.  The original author uses the packaging utility to generate the package for one application.
-Then the package, together with
-its map file and description file will be published. When
-another researcher wants to repeat the application, one copy of the package will be downloaded into the new machine and the application can be repeated.
-
-When we try to repeat one application on one new machine, one map file is necessary for the relocation of the data access targets, as
-show in Figure~\ref{fig:version-evolution}. 
-The map file clearly defines the real location of each dependency in the format of dependency variables - the real location of dependency variable {\tt GIT} is \path{/data/git/cms-ttH} and the real location of dependency variable {\tt CVMFS}
-is {\tt /data/cvmfs/grid.cern.ch}.
-The script only refers to the dependency variables defined in the map file.
-This design decouples the application script and the actual data access targets, which minimizes the impact of the evolution of different data dependencies
-and ensures the transparent access.
-The modification of the package only introduces the minimal changes of the map file on the client side.
-
-This basic approach to dependency management is a step in the right direction
-for dependencies that are \emph{explicit} and \emph{external} to the
-user's native execution environment.  However, it leaves two other problems unsolved.
-
-First, the basic approach requires that someone be \emph{aware} of the dependencies,
-whether it be the end user, the system administrator, or the archive curator.
-It seems reasonable to expect the user to be aware of a large dependency mentioned in a top-level script.
-But, oftentimes the dependency is embedded invisibly deep within the software stack,
-or is connected to the machine by the local system administrators.  No single party
-is likely to have complete information about all of the dependencies.
-Second, the basic approach assumes that the entire dependency is actually
-consumed by the artifact.  As we have suggested above (and will show below),
-this sort of program often only consumes a small fraction of what it does declare
-as a dependency.
-
-To address both of these problems, users and curators alike need tools that
-will automatically observe the dependencies of complex applications, to
-facilitate automatic and efficient preservation.
-
-\section{Measuring Dependencies}
-
-\begin{figure*}
-\centering
-\includegraphics[width=.8\textwidth]{workflow-parrot.eps}
-\caption{Workflow of The Fine-Grained Dependency Management Toolkit Based on Parrot}
-\label{fig:workflow-parrot}
-\end{figure*}
-
-We have developed a prototype tool to assist in the measurement and preservation
-of implicit dependencies for complex applications.
-We use Parrot~\cite{thain2005parrot} to explicitly record all
-of the files accessed by our example application, allowing us to observe how
-much of each external dependencies is used, and what local resources are implicitly used.
-Using this information, we create a \emph{reduced package} which contains
-only the files actually used by the application.
-
-Parrot is a virtual filesystem access tool which has been used to attach
-existing programs to a variety of remote I/O systems, such as HTTP, FTP, and CVMFS.
-It works by trapping an application's system calls through the Linux {\tt ptrace} debugging
-interface, and then replacing them with the desired I/O operations.  Parrot is already used
-in the high energy physics community with applications like TauRoast specifically to 
-provide access to the CMSSW software distribution via the CVMFS distributed file system.
-We made small modifications to Parrot to record a \emph{namelist} which lists all 
-of the files that an application actually accesses.
-
-Figure~\ref{fig:workflow-parrot} illustrates the measurement process.
-The starting point of this toolkit is one successful execution of the application on the native machine.
-First, we execute the actual data analysis script under Parrot to generate the namelist.
-Then, using the namelist, we generate a package containing all the necessary data
-and software for one analysis program. When another
-researcher wants to repeat the program, he only needs to obtain the package and
-execute the actual analysis program inside the package.
-
-For one execution of \emph{TauRoast}, the generated namelist includes 132,047 accessed filenames,
-along with the system calls used to access the file, such as {\tt open}, {\tt stat}, {\tt read}, etc.
-With duplicate filenames removed, the list is reduced to 67,168 files.
-Many of those entries do not exist, because they reflect attempts
-by the application to search for programs and libraries in multiple places.
-Only 22,068 entries reflect existing files or directories.
-
-The packaging tool iterates over each item of the filename list, determines the process
-mode and replication degree according to the file type (common files,
-directories, symbolic links) and the system call type, generates one package
-containing the dependencies, and summarizes the contents of the package
-as shown in Table~\ref{table:package-info}.  To the extent possible,
-the filesystem structure of the original environment is preserved.
-
-We considered several approaches to constructing the package.
-In a {\bf shallow copy}, we only copied the individual files in the namelist,
-creating only parent directories for each.  Where a directory was listed,
-we created the directory and populated it with empty files as placeholders
-to facilitate a directory listing.  In a {\bf medium copy}, we copied the
-individual files as before.  Where a directory was listed, we created
-the directories and copied the contents of the files in that directory,
-one level deep.  A {\bf deep copy} would duplicate all directories recursively,
-but this would have resulted in TB-sized packages, so we did not consider
-it further.
-
-Parrot is required to re-run the packaged artifact, in order to force
-the packaged files to appear to exist in their original locations.
-To this end, the packaging tool creates a \emph{file map} which maps
-the logical names of the files to their current physical locations, as shown in Table~\ref{table:map-file}.
-Parrot reads the file map and redirects system calls at run-time to achieve the desired effect.
-As the example suggests, special device files such as {\tt /proc} and {\tt /dev}
-are not incorporated into the package but are instead accessed natively.
-
-\begin{table}
-    \centering
-    \begin{tabular}{ll}
-    \hline
-    \bf Path used in Program & \bf Actual Location \\ \hline
-    {\tt /} & {\tt /tmp/package-hep} \\ \hline
-    {\tt /tmp/package-hep} & {\tt /tmp/package-hep} \\ \hline
-    {\tt /dev} & {\tt /dev} \\ \hline
-    {\tt ...} & {\tt ...}\\ \hline
-    \end{tabular}
-    \caption{Structure of Map File}
-    \label{table:map-file}
-\end{table}
-
-\begin{table}
-    \centering
-    \begin{tabular}{rrr}
-\hline
-                    & \bf Shallow Copy & \bf Medium Copy\\
-\hline
-    Whole Files    & 1632         & 15642\\ 
-\hline
-    Empty Files    & 14273        & 263\\
-\hline
-    Directories    & 1549         & 1549\\ 
-\hline
-    Symbolic Links & 4614         & 4614 \\
-\hline
-    \bf Total Size & \bf 21GB     & \bf 28GB \\ 
-\hline
-    \end{tabular}
-    \caption{Package Information}
-    \label{table:package-info}
-\end{table}
-
-\subsection{Tracking of Network Dependencies}
-
-\begin{figure}
-\centering
-\includegraphics[width=.6\textwidth]{git-syscall.eps}
-\caption{Exec Syscalls of a git command}
-\label{fig:git-syscall}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=.6\textwidth]{http_packet.eps}
-\caption{HTTP Request and Response}
-\label{fig:http_packet}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=.6\textwidth]{url_redirection.eps}
-\caption{An Example of URL Redirection}
-\label{fig:url_redirection}
-\end{figure}
-
-All the dependencies of one program can be divided into three categories: local file system (e.g., /usr, /lib and /lib64), remote file systems which can be mounted as local directories (e.g., /cvmfs and /hdfs), and other remote network dependencies (e.g.
-http, https and ssh).
-Through utilizing ptrace to trap each file-relevant system call used by a program, the first two categories of dependencies can be collected. 
-Motivation of tracking network dependencies: Linkrot is a common and great threat to the preservation of scientific applications.
-A URL which works normally today may be unavailable permanently.
-A method which can help the scientists figure out all the network dependencies of their applications provides the chance to evaluate the stability of each network dependencies and preserve the unstable network resources before linkrot happens.
-One direct solution to track the third category of dependencies is to utilize ptrace to check each exec system call used by a program and record each network-relevant executable and its parameters.
-However, an executable may create one or more child processes to finish some tasks, and a child process may create their own children processes.
-Figure~\ref{fig:git-syscall} shows all the processes created by a git command.
-A process with PID 998 is created to clone a remote git repository into local machine, which totally has 6 child processes.
-Moreover, a network-relevant executable name collection is necessary to identify network dependencies.
-The diversity of network-relevant executables and the large process tree generated for a network executable make this solution infeasible.
-
-Another solution to track network dependencies is to track the network sockets.
-The user process communicates with the network protocol stacks in the kernel through the network socket layer user interface on Linux.
-From the process tree shown in the above figure, the process with PID 1000 responds to create a socket, connect to a DNS server, send a DNS request packet to the DNS server and receive a DNS response packet from the DNS server.
-The information gained from the network socket tracking can be divided into three categories.
-\begin{itemize}
-\item The information of network sockets used to communicate with remote network dependences (through socket and connect system calls) can be used to figure out the port number, service name (such as, http, https, and ssh), socket type (stream and datagram),  and the domain type (inet and inet6).
-\item The contents of DNS packets can be used to figure out the hostname and IP address of each remote network dependency. 
-\item As for applications based on http protocol, all the http requests and responses can be seen, as shown in Figure~\ref{fig:http_packet}.
-However, as for applications based on https and ssh which encrypt network data using TLS/SSL, tracking network data on the socket level can only see the encrypted data.
-\end{itemize}
-
-The results of tracking network sockets used by a program involves two categories of network resource redirections, dns-level hostname redirection and website-level url redirection. 
-\begin{itemize}
-\item dns-level hostname redirection: Each DNS packet includes five parts, header, question, answer, authority, and additional.
-A DNS response packet with the type CNAME has multiple answers.
-For example, the DNS response packet which tries to resolve {\tt www3.nd.edu} includes two answers.
-The first answer provides an alias of {\tt www3.nd.edu}, {\tt www-vip.cc.nd.edu}, and the second answer maps the alias to the IP address.
-{\tt www3.nd.edu} CNAME {\tt www-vip.cc.nd.edu}
-{\tt www-vip.cc.nd.edu} A {\tt 129.74.12.151}
-The CNAME-type DNS packets leave us a question, among the hostname used by the user, the alias(es), the IP address, what should we preserve?
-\item website-level url redirection: Website-level url redirection happens when a website updates its location and still want their old users access their resources using the old url.
-Figure~\ref{fig:url_redirection} illustrates the url redirection between {\tt \url{www3.nd.edu/~ccl}} and {\tt ccl.cse.nd.edu}.
-Except for the difference of hostnames, the application layer protocols used by the old-version website and the new-version website is also different: the old website provides services through the https protocol, while the new website provides services through the http protocol.
-\end{itemize}
-
-The usage of https protocol makes detecting of website-level url redirections through tracking system calls more difficulty and even impossible.
-All the application data will be encrypted at presentation layer through the TLS/SSL protocol, which is initialized at the session layer and works at the presentation layer.
-
-\section{Evaluation}
-
-We evaluated the correctness of the reduced package and the overhead of generating the package.
-To do this, the application was repeated with the help of \emph{Original Script} (as shown in Figure~\ref{fig:version-evolution}) on the original machine. 
-Then one \emph{reduced package} was generated and verified with the help of Parrot on the original machine.
-
-Then, two different virtual machines (VM) - one VM from the Notre Dame Cloud Platform based on KVM and one VM from the Amazon EC2 Platform based on Xen, were employed to further verify the correctness of the reduced package.
-
-We first repeated the example from scratch using the Script translated from the original email on the original machine and counted the time consumption and data size. 
-Then based on the successful execution of Original Script, we evaluated Reduced Package - one package containing necessary dependencies is generated, and then the time consumption and data size is analyzed.
-
-To measure time consumption, we counted the time used to obtain remote software dependencies, build the environment, and analyze the dataset.
-We also counted the time used to obtain the namelist and to generate the package.
-To measure data size, we can easily figure out the size of each data and code source inside the package under Reduced Package.
-Original Script does not support mining of implicit dependencies.
-As for remote sources, we can figure out the named size through the analysis script.
-However, it is hard to figure out the named size of each local source.
-Instead, we only knew that total size of each file system is very large.
-
-Table~\ref{table:time-2nd3rd} shows the execution time comparison between
-Original Script and Reduced Package.
-Reduced Package is faster than Original Script, because all the software copied into the package has been compiled and the Software Acquisition stage is not necessary.
-and all the environment building only takes 4 seconds,
-We were surprised that Reduced Package even reduces the actual analysis time. 
-The reason for this is that data is obtained through accessing HDFS in Original Script, but is copied into the package in Reduced Package.
-This localization of experimental data speeds up the data analysis process, resulting the actual analysis time reducing from 20 minutes to 13 minutes.
-
-\begin{table}
-    \centering
-    \begin{tabular}{lrr}
-    \hline
-    \bf Task Category & \bf Original Script & \bf Reduced Package \\ \hline
-    Obtain Namelist & N/A & 28min 28s \\ \hline
-    Generate Package & N/A & 85min 51s \\ \hline
-    Software Acquisition & 8min 11s & N/A \\ \hline
-    Environment Build & 5min 49s  & 4s \\ \hline
-    Analysis Code & 20min 31s & 13min 04s \\ \hline
-    \end{tabular}
-    \caption{Execution Time Comparison between Original Script and Reduced Package}
-    \label{table:time-2nd3rd}
-\end{table}
-
-Table~\ref{table:time-2nd3rd} also illustrates the time used to
-obtain the namelist and to generate the package. 
-The time used for these two steps is longer than the execution time,
-because each filename of the list, together with its system call type, needs to be checked, and the structure of each directory item must be maintained.
-However, 
-this is only done once.
-Once the package is
-generated, many users can directly obtain the package and repeat the application 
-separately.
-
-Table~\ref{table:size-original-real} on page 2 illustrates the total size, named size in the example and actually used size of each remote source (the first 4 items) and local source (the remaining 5 items).
-The third column corresponds to the data size of Reduced Package and can be easily figured out, because all the necessary data has been copied into the package.
-Original Script does not support measuring implicit dependencies.
-As for remote sources, we can figure out the named size through the analysis script.
-However, it is hard to figure out the named size of each local source.
-Instead, we only knew that total size of each file system is very large.
-
-\begin{table}
-	\centering
-	    \begin{tabular}{llrrr}
-	        \hline
-	        \bf Name & \bf Location & \bf Total & \bf Named & \bf Used \\ 
-	        \hline
-	        CMSSW code     & CVS & 88.1GB & 448.3MB & 6.3MB\\ \hline
-	        Tau source       & Git & 73.7MB & 73.7MB & 6.7MB \\ \hline
-	        PyYAML binaries    & HTTP & 52MB & 52MB & 0KB \\ \hline
-	        .h file       & HTTP& 41KB & 41KB & 0KB \\ \hline \hline
-	        Ntuples data    & HDFS& 11.6TB & N/A& 20GB \\ \hline
-	        Configuration & CVMFS & 7.4GB & N/A & 103MB \\ \hline
-	        Linux commands & localFS & 110GB &  N/A & 68.4MB \\ \hline     
-	        HOME dir& AFS &12GB & N/A & 32MB\\ \hline
-	        Misc commands & PanFS & 155TB & N/A  & 1.6MB \\ \hline
-	        Total      &    & 166.8TB            & N/A & 21GB \\ \hline
-	    \end{tabular}
-	    \caption{Data and Code Used by Tau Roast}
-	    \label{table:size-original-real}
-\end{table}
-%	\begin{tablenotes}
-%	      \small
-%	      \item The first column illustrates the total size of each data and software source; 
-%	            the second column illustrates the size of the named files from each source;
-%	            the third column illustrates the size of actually used data from each source.
-%	            N/A denotes it is hard to figure out the named size of implicit dependencies directly.        
-%	    \end{tablenotes}
-
-To further verify the correctness of Reduced Package on other machines, two different machines are employed -
-one virtual
-machine~\cite{goldberg1974survey} from the Notre Dame Cloud Platform based on KVM sharing the same kernel version with the original machine,
-and one virtual machine from  the Amazon EC2~\cite{amazon2010amazon} Platform based on Xen.
-
-Table~\ref{table:config-vm} illustrates the configuration of 
-each machine and the execution time of the application on each machine.
-All the machines adopt the x86\_64 hardware platform and Linux kernel.
-Both of the two VMs repeated the application with the help of the package generated on the original machine successfully.
-The execution time on one machine greatly depends on its hardware configuration.
-
-\begin{table}
-    \centering
-    \begin{tabular}{lrrrr}
-    \hline
-    \bf Machine Type & \bf Distro Version & \bf CPU Cores & \bf Mem (GB) & \bf Execution Time \\ \hline 
-    Original Machine &  Red Hat 5.10 & 64 & 125 & 13min 04s\\  \hline
-    KVM (Notre Dame) & CentOS 5.10 & 4 & 2 & 21min 38s\\ \hline
-    Xen (EC2) & Red Hat 5.9 & 16 & 60.5 & 13min 30s\\ \hline
-    \end{tabular}
-    \caption{Evaluation of Different Machines}
-    \label{table:config-vm}
-\end{table}
-
-In summary, we demonstrate that the application can be repeated with the help of the reduced package on one different machine with the required hardware architecture and OS kernel version.
-%*****hmeng-doubt:Another reason for the packaging utility is that not all the data and software generated by the second version script is used during the the actual data analysis.
-The packaging utility can help us find out the optimal subset of data and software involved in one actual data analysis.
-%*****hmeng-doubt: this point is not the motivation. but one achievement comes together. out of imagination.
-
-\begin{figure}
-\centering
-\includegraphics[width=.6\textwidth]{preservation-integration.eps}
-\caption{Preserving Multiple Artifacts}
-\label{fig:Preservation integration}
-\end{figure}
-
-\section{Open Problems}
-
-Figure~\ref{fig:Preservation integration} shows the rough information
-architecture of the archive that we imagine for complex
-scientific software like TauRoast.
-Each artifact to be preserved is a package that consists of a top-level
-script to invoke the software, a dependency map, and the dependencies
-themselves, which may be external to the original program.  The artifacts
-are then ingested into the archive, where shared dependencies are stored
-only once.  In cases where an artifact has a dependency on a trusted
-(or very large) remote archive, the dependency may simply be tracked
-. A researcher that wishes to reproduce a given
-result need only refer to the unique identifier of the artifact, and will
-be able to automatically extract all of the dependent components of
-that artifact.
-
-For example, in Figure~\ref{fig:Preservation integration} Script 1 depends on items A, B, and C.
-Items A and B are ingested into the archive, where B is shared with Script 2.
-Item C is stored in another trustworthy repository and is tracked rather than ingested.
-When Script 1 is exported from the repository, items A and B are exported along with it, while C can be copied or remain remote, according to the end user's choice.
-
-As simple as that picture appears, there are a number of problems that must be solved to get there:
-
-{\bf Measure the Mess or Force Cleanliness?}  Two radically different approaches to dependency tracking are possible.
-The first is to allow end users complete freedom to construct their environment as desired, then \emph{measure} what items were actually used.
-As we have shown, this is possible, but has significant overheads and does not fully preserve the structure or intent of the end user.
-The second approach is to \emph{force} users to work in a clean environment in which no resource can be used until a proper dependency has been declared.
-This ensures that all dependencies are known in advance (and made explicit to the end user) but places a variety of restrictions on the user's daily work, and may prevent creative approaches that do not fit within the curator's view of how programs should be structured.
-Whether end users will accept the inconvenience of forced cleanliness for the benefits of reproducibility can only be discovered through experiment.
-
-{\bf Granularity of Dependencies.}  Dependencies could be handled
-at many different levels of granularity.  In this work, we have shown
-how they can be handled at the level of entire repositories or individual files.
-Other possible choices might include intermediate-sized software packages
-(like RPM) or in the case of experimental data, even portions of individual large files.  Clearly, a larger granularity will result in 
-simpler dependency maps, and more wasted space; smaller granularity results
-in complex dependency maps and less wasted space.  A hybrid solution may
-be able to combine both by storing large granularity dependencies, but
-selecting sub-items out of objects when efficiency demands it.
-
-{\bf Scope of Reuse.}  We have presented the data preservation
-problem as primarily one of accurate reproduction: if a result depends
-on running program X, we must be able to run exactly X again.  However,
-the goal of scientific reproducibility is rarely limited to running
-\emph{precisely} what a predecessor did. Often, the objective is to
-change a parameter or a data input in order to see how the result is affected.
-To that end, the preservation system must capture enough of the surrounding
-material to permit modifications to succeed.  From this perspective,
-a larger granularity of preservation is desirable.  A better understanding of
-how end users will consume preserved software will help to shape how
-software is preserved in the first place.
-
-{\bf Dependency Detection.}  If we allow users to work in uncontrolled
-environments, then we must have better methods for understanding the dependencies  of existing programs.  At first, we relied on an expert reader to examine
-the user's script and extract the dependencies.  This is clearly
-not a scalable approach.  We then demonstrated an automated method of observing
-what individual files are accessed by a program. However, this does
-not cover all types of dependencies, particularly those that are networked.
-More sophisticated observation techniques could infer higher-level information,
-such as the RPM package names of the files accessed, the URLs of remote
-repositories named throughout the program, or even the addresses and names of networked dependencies like databases and filesystems.
-
-{\bf Source, Binary, or Both?}  A science archive might choose to retain
-the source code of an artifact or the binary code that can actually run in a given environment.
-While conventional wisdom suggests that access to source code is critical for the long term
-survival and evolution of a piece of software, it also requires the maintenance of an enormous
-amount of supporting software in the form of compilers, linkers, and supporting libraries for
-the target platform.  Rebuilding all of these for every invocation of an artifact is
-likely to have excessive cost.  We suggest that a realistic repository will have to
-maintain \emph{both}: the source describes the ultimate meaning of the code, but
-the binary is an important performance cache, a backup if the compiler toolchain should
-fail to be preserved, and a checksum to ensure that a source artifact was rebuilt correctly.
-
-\section{Related Work }
-
-Generally, there are three approaches to preserve software environment:
-hardware preservation, migration and emulation.  Hardware
-preservation preserves the original software and its original operating
-environment. 
-Software migration technique~\cite{cifuentes1996binary,mancl2001refactoring} was used to facilitate running software on new machines.
-However, migration often involves the re-compiling and re-configuring
-the source code to accommodate a new hardware platform and software environment.
-Emulation recreates the original software and hardware environment by
-programming future platforms and OSs. One common solution to implement this is
-virtual machine. According to the usage and emulation degree of the real
-machine, virtual machine can be divided into system virtual machine and process
-virtual machine. 
-The working principle, design principle and
-performance evaluation of system virtual machine were illustrated in~\cite{goldberg1974survey, smith2005architecture}. 
-The
-functionality of system VM to support different guest operating systems was illustrated in~\cite{barham2003xen,kivity2007kvm,rosenblum1999vmware}.
-F. Esquembre~\cite{esquembre2004easy} illustrated how JVM, one process virtual machine, can expedite the creation of
-scientific simulations in Java. 
-The pros and cons of these three approaches were discussed in~\cite{matthews2009towards,phelps2005no,hong2010software}.
-
-The preservation of computing environment and software environment was treated as one entirety in~\cite{matthews2009towards,phelps2005no,hong2010software}.
-However, frequently changing experiment software makes the maintenance of the preserved experimental environment very complex.
-CernVM~\cite{buncic2010cernvm} treated them as two different categories.
-The preservation of computing environment is implemented with CernVM, and the preservation of software environment is based on a CernVM filesystem(CVMFS) specifically designed for efficient software distribution.
-
-The importance of preserving software in source code format was emphasized in~\cite{zabolitzky2002preserving,castagne2013consider}. 
-However, CVMFS~\cite{buncic2010cernvm} published pre-built and configured experiment software releases to avoid the time-consuming software building procedure.
-
-Attempts from different perspectives to facilitate the reproduction of scientific experiments utilizing a preserved software library have been made. 
-The software distribution mechanism over network was discussed in~\cite{compostella2010cdf, blomer2011cernvm}.
-J.
-R.
-Rice et al.~\cite{rice1996scientific} made the reproduction process easier through the integration of user interface, scientific software libraries, knowledge base into problem-solving environment.
-S. R. Kohn et al.~\cite{kohn2001divorcing} tried to enable the creation and distribution of language-independent software library by addressing language interoperability.
-a scalable, distributed and dynamic workflow system for digitization processes was proposed in~\cite{schoneberg2013scalable}.
-A distributed archival network was designed in~\cite{subotic2013distributed} to facilitate process-oriented automatic long-term digital preservation.
-M. Agosti et al.~\cite{agosti2012envisage} aimed to help non-domain users to utilize the digital archive system developed for domain experts.
-
-Current mechanisms of preserving scientific experiments assume that all the data and software mentioned in the experiments are necessary for the reproduction of the experiments.
-However, this is not always right.
-In some cases, the original author may leave additional code referring to irrelative data and software in the program.
-One mechanism, which can figure out the absolutely relevant data and software of one experiment, is important for both the preservation and reproduction of scientific experiments.
-
-B. Matthews et al.~\cite{matthews2008significant} introduced one conceptual framework for software preservation from several case studies of software preservation.
-One tool to capture software preservation properties within a software environment was designed in~\cite{matthews2010framework} through a series of case studies conducted to evaluate the software preservation framework.
-L. R. Johnston et al.~\cite{johnston2014workflow} proposed one overall data curation workflow for 3-5 case studies of preserving research data.
-Two case studies~\cite{borgman2012data} were conducted to figure out the properties of data to be reused in the future.
-
-\section{Postscript}
-
-We began this work in late 2013, generating a reduced package for \emph{TauRoast} based
-on the configuration of a standard machine at Notre Dame at the time.  In the course
-of writing this paper in spring 2014, almost everything about the computing environment
-changed: the operating system was upgraded, a new version of CMSSW was released, and
-our local HEP users switched from using CVS to CVMFS for accessing CMSSW.
-The original script provided by the author failed to run on the same machine.
-But, the reduced package we created three months earlier in the old environment
-worked just fine on the new machine.
-
-\section*{Acknowledgments}
-
-This work was supported in part by National Science Foundation grants PHY-1247316 (DASPOS), 
-OCI-1148330 (SI2) and PHY-1312842.
-The University of Notre Dame Center for Research Computing scientists and engineers provided critical technical assistance throughout this research effort.
-
-Copyright (C) 2014 The University of Notre Dame
-
-This work is licensed under the Creative Commons Attribution 4.0 License.
-
-\bibliographystyle{plain}
-\bibliography{cclpapers,this}
-
-\end{document}

### 2015-01-06 postscript.tex
Put each section into a separate tex file

\section{Postscript}

We began this work in late 2013, generating a reduced package for \emph{TauRoast} based
on the configuration of a standard machine at Notre Dame at the time.  In the course
of writing this paper in spring 2014, almost everything about the computing environment
changed: the operating system was upgraded, a new version of CMSSW was released, and
our local HEP users switched from using CVS to CVMFS for accessing CMSSW.
The original script provided by the author failed to run on the same machine.
But, the reduced package we created three months earlier in the old environment
worked just fine on the new machine.

### 2015-01-06 problems.tex
Put each section into a separate tex file

\begin{figure}
\centering
\includegraphics[width=.6\textwidth]{preservation-integration.eps}
\caption{Preserving Multiple Artifacts}
\label{fig:Preservation integration}
\end{figure}

\section{Open Problems}

Figure~\ref{fig:Preservation integration} shows the rough information
architecture of the archive that we imagine for complex
scientific software like TauRoast.
Each artifact to be preserved is a package that consists of a top-level
script to invoke the software, a dependency map, and the dependencies
themselves, which may be external to the original program.  The artifacts
are then ingested into the archive, where shared dependencies are stored
only once.  In cases where an artifact has a dependency on a trusted
(or very large) remote archive, the dependency may simply be tracked
. A researcher that wishes to reproduce a given
result need only refer to the unique identifier of the artifact, and will
be able to automatically extract all of the dependent components of
that artifact.

For example, in Figure~\ref{fig:Preservation integration} Script 1 depends on items A, B, and C.  Items A and B are ingested into the archive, where B is shared with Script 2.  Item C is stored in another trustworthy repository and is tracked rather than ingested.  When Script 1 is exported from the repository, items A and B are exported along with it, while C can be copied or remain remote, according to the end user's choice.

As simple as that picture appears, there are a number of problems that must be solved to get there:

{\bf Measure the Mess or Force Cleanliness?}  Two radically different approaches to dependency tracking are possible.  The first is to allow end users complete freedom to construct their environment as desired, then \emph{measure} what items were actually used.  As we have shown, this is possible, but has significant overheads and does not fully preserve the structure or intent of the end user.   The second approach is to \emph{force} users to work in a clean environment in which no resource can be used until a proper dependency has been declared.  This ensures that all dependencies are known in advance (and made explicit to the end user) but places a variety of restrictions on the user's daily work, and may prevent creative approaches that do not fit within the curator's view of how programs should be structured.  Whether end users will accept the inconvenience of forced cleanliness for the benefits of reproducibility can only be discovered through experiment.

{\bf Granularity of Dependencies.}  Dependencies could be handled
at many different levels of granularity.  In this work, we have shown
how they can be handled at the level of entire repositories or individual files.
Other possible choices might include intermediate-sized software packages
(like RPM) or in the case of experimental data, even portions of individual large files.  Clearly, a larger granularity will result in 
simpler dependency maps, and more wasted space; smaller granularity results
in complex dependency maps and less wasted space.  A hybrid solution may
be able to combine both by storing large granularity dependencies, but
selecting sub-items out of objects when efficiency demands it.

{\bf Scope of Reuse.}  We have presented the data preservation
problem as primarily one of accurate reproduction: if a result depends
on running program X, we must be able to run exactly X again.  However,
the goal of scientific reproducibility is rarely limited to running
\emph{precisely} what a predecessor did. Often, the objective is to
change a parameter or a data input in order to see how the result is affected.
To that end, the preservation system must capture enough of the surrounding
material to permit modifications to succeed.  From this perspective,
a larger granularity of preservation is desirable.  A better understanding of
how end users will consume preserved software will help to shape how
software is preserved in the first place.

{\bf Dependency Detection.}  If we allow users to work in uncontrolled
environments, then we must have better methods for understanding the dependencies  of existing programs.  At first, we relied on an expert reader to examine
the user's script and extract the dependencies.  This is clearly
not a scalable approach.  We then demonstrated an automated method of observing
what individual files are accessed by a program. However, this does
not cover all types of dependencies, particularly those that are networked.
More sophisticated observation techniques could infer higher-level information,
such as the RPM package names of the files accessed, the URLs of remote
repositories named throughout the program, or even the addresses and names of networked dependencies like databases and filesystems.

{\bf Source, Binary, or Both?}  A science archive might choose to retain
the source code of an artifact or the binary code that can actually run in a given environment.
While conventional wisdom suggests that access to source code is critical for the long term
survival and evolution of a piece of software, it also requires the maintenance of an enormous
amount of supporting software in the form of compilers, linkers, and supporting libraries for
the target platform.  Rebuilding all of these for every invocation of an artifact is
likely to have excessive cost.  We suggest that a realistic repository will have to
maintain \emph{both}: the source describes the ultimate meaning of the code, but
the binary is an important performance cache, a backup if the compiler toolchain should
fail to be preserved, and a checksum to ensure that a source artifact was rebuilt correctly.

### 2015-01-06 tauroast.tex
Put each section into a separate tex file

\begin{figure}[t]
\centering
\includegraphics[width=.5\textwidth]{data-code-size.eps}
\caption{Inputs to Tau Roast}
\label{fig:data-code-size}
\end{figure}

\section{Overview of Tau Roast}

Within the ongoing investigation of the Higgs boson at the CMS
detector, part of the LHC at CERN~\cite{collaboration2008cms}, the Higgs production in association
with two top quarks allows measuring the Higgs coupling strength to
top quarks~\cite{chatrchyan2013search}.  As the Higgs boson is too short-lived to be detected
itself, it has to be reconstructed from its decay products.

The application which is the study of this paper is called \emph{TauRoast}.
It searches for cases where the Higgs boson decays to two tau leptons.
Since the tau leptons are very short-lived, they are not observed directly, but by the particle decay products 
that they generate.  So, the analysis must search for detector
events that show a signature of decay products compatible with both hadronic tau and top decays.  Properties of such events are used to distinguish
the events of interest (Higgs decays) from all other events and
are also used in further statistical analysis.

Figure~\ref{fig:data-code-size} shows that both the code and data
that form \emph{TauRoast} are drawn from large repositories through
multiple steps of reduction.  A preservation strategy must weigh
whether to store the large repositories completely, the fragments
used by an artifact, or something in between.

{\bf Code Sources.} Like many scientific codes, the central algorithm
of \emph{TauRoast} is expressed in a relatively small amount of
custom code developed by the primary author.  But, the code cannot
run at all without making use of an enormous collection of software
dependencies.  Some of these dependencies are standard to operating
systems worldwide, some are standardized across the entire high-energy
physics field, some are particular to small collaborative groups,
and a few are very specific to a single researcher.

The largest of these repositories is the CMS Software Distribution (CMSSW)~\cite{cms2006cms},
a carefully-curated selection of software packages which is distributed
in several forms.  Historically, components of CMSSW were obtained by checking components
of the source out of CVS (CMSSW source codes were moved from CVS to git recently), or by installing a complete binary package on a shared
filesystem within an HPC center.  In recent years, distribution has moved to
an on-demand delivery system known as CVMFS~\cite{blomer2011cernvm}, which
provides a filesystem interface that transparently accesses a remote repository.
The content of CMSSW is managed very carefully by a centralized team whose main goal
is to ensure that the current version of the software operates correctly
on the operating systems and architectures currently in use.  However,
preservation is not a specific objective of the system, and so there is
no particular guarantee that old versions of CMSSW will continue to
operate indefinitely.

CMSSW contains many different tools, libraries, and utilities.  No single code uses anywhere close to all of these.  But, because it is widely used within the experimental researchers, it is common for users to simply expect that a particular version of the entire repository is available.

{\bf Data Sources.}
The CMS collaboration provides end-users with a pre-processed
and reduced data format, AOD~\cite{holtman2001cms}, containing information for events, i.e.,
proton-proton collisions with a signature of interest, in the form of
reconstructed particles.  This format is based on the RAW output of
the CMS detector readout electronics and reconstructed world-wide, which is then processed through various algorithms which derive signatures of individual particles.
Both real and simulated data are available for examination.

As AOD data are too large to be iteratively processed repetitively in
a physics analysis workflow, it is normally reduced further in
structural complexity and content.  For the analysis under
investigation here, this is a two-step process.  First, the AOD data
are processed at the Notre Dame working group cluster to BEAN (Boson Exploration Analysis Ntuple) events,
containing only trivial data containers packed in vectors.  This step
is time and CPU intensive and its output contains data of 11.6$\,$TB to be
analyzed by the tau analysis.
It is performed by a small custom code framework, which is built on top of CMSSW.
The BEAN format, production code, and
data are shared within the analysis group looking at Higgs production
in association with top quarks, which is formed by groups from a few
American and European universities,
consisting of up to a few dozen contributors.

In the second step, the data are reduced to the ``Ntuple'' format,
which contains only events matching basic quality criteria and
fields relevant to \emph{TauRoast}.
Again, the Notre Dame CMS groups cluster
resources are used to perform this reduction and selection,
running highly customized software,
built on CMSSW and the BEAN framework,
with code written and maintained by a small group.

Once the data has been reduced to Ntuples, TauRoast can be run as a single
process, and contains a stringent event selection to look only at high
quality candidate events for the underlying physical process.
Quantities from the relevant events can be
both plotted and used in multivariate analysis to determine the level
of expected signal in real data.
This package is written using the CMSSW build framework,
but only utilizes code from ROOT,
a particle physics toolkit underlying CMSSW,
and a few external python dependencies for convenience.

### 2015-01-09 intro.tex
Some rewording

@@
 One approach is to conduct the entire computation relating to a scientific result within a virtual machine image, and then share the resulting image.
-This way VMIS become an authoritative, encapsulated and executable records of computations, especially computations whose results are destined for publication and/or re-use, and this can be shared easily.
+This way VMIs become an authoritative, encapsulated and executable records of computations, especially computations whose results are destined for publication and/or re-use, and the VMIs can be shared easily \cite{}.
 With this approach, oftentimes, the resulting image is too big in size for share-ability purposes.
-An alternative light-weight form of virtualization allows encapsulating just the application software, along with all its necessary dependencies into a self contained package, thus separating , and not including, the underlying operating system on which it is executed.
-This encapsulation is achieved by interposing application system calls, and copying necessary dependencies (data, libraries, code) into a layered filesystem.
-While both forms of virtualization provides an excellent mechanism for sandboxing the computations associated with a scientific result, neither form of virtualization provides any guarantee that the included pieces of software will indeed reproduce the associated scientific result.
+An alternative light-weight form of virtualization allows encapsulation of the application software, along with all its necessary dependencies into a self-contained package, but does not make it executable.
+It thus separates, and does not include the underlying operating system on which the package is executed.
+The encapsulation of the self-contained package is achieved by interposing application system calls, and only copying the necessary dependencies (data, libraries, code) into the package, which also makes it light-weight than a VMI.
+While both forms of virtualization provide mechanisms for sandboxing the computations associated with a scientific result, neither form of virtualization provides any guarantee that the included pieces of software will indeed reproduce the associated scientific result.
 
-Since reproducibility is significantly about comprehensive documentation, virtualization approaches in its current form only make it easy to capture the computations, but not preserve the computation so that it is easy to understand, install, or alter the implicit dependencies that are part of computation, especially as dependencies and external software components evolve or become deprecated.
-Software delivery mechanisms, such as Linux Containers and Docker have recently emerged that address several of the reproducible challenges that arise due to use of virtualization approaches.
+Since reproducibility is significantly about comprehensive documentation, virtualization approaches in their current form only make it easy to capture the computations.
+Preserving the computations, so that they are easy to understand, install, or alter implicit dependencies that are part of computation, especially as dependencies and software components evolve or become deprecated, is not effectively addressed.
+There are two approaches to address the preservation challenge.
+By either introducing tools that help document dependencies and provide software attribution within VMIs or packages, or alternatively by using software delivery mechanisms, such as, centralized package management, linux containers and Docker framework.
+We examined the first approach previously in \cite{}.
+In this paper we examine the the second approach, that is, examine how the documentation and preservation standards that are part of software delivery mechanisms can be combined with traditional virtualization approaches for reproducibility.
+In particular we consider the light-weight virtualization approaches, because, we believe that the combination of light-weight approaches with more standardized software delivery mechanisms can lead to addressing the reproducibility challenge for a wide variety of scientific researchers.
+% they may help the This  We that must also include effective  to deliver the software to a wide audience. We examine the fire
+%have recently emerged  several of the reproducible challenges that arise due to use of virtualization approaches.
 
-In this paper, we examine how software delivery mechanisms can be combined with traditional virtualization approaches for reproducibility, especially light-weight virtualization approaches.
 To conduct a thorough examination, we consider a real-world complex high energy physics application, independently developed by a group, but must be reproduced  so that the entire high energy physics community can benefit from the analysis obtained from the application.
-We describe challenges in reproducing this application, and consider the extent to which reproducibility can be satisfied with light-weight virtualization approaches and software delivery mechanisms.
+The collaborative nature of in which high energy physics science is conducted is a
+We describe challenges in reproducing this application, and consider the extent to which reproducibility can be satisfied, independently with light-weight virtualization approaches and software delivery mechanisms.
 We then propose an invariant framework for computational reproducibility that combines light-weight virtualization with software delivery mechanisms.

### 2015-01-12 evolution.tex
Major cleanup

@@
-\section{Evolving the Artifact}
+\section{The Invariant Framework}
 
-It is clear that the artifact, as provided, is not in a suitable form
-for preservation.  While it might be technically possible to automatically
-capture the entire virtual machine and all of the connected filesystems,
-it would require 166.8TB of storage, which would be prohibitively expensive
-for capturing this one application alone.  Further, if multiple
-similar applications are preserved, we would miss the opportunity to identify
-common dependencies and store them once for multiple artifacts.
-A more structured approach to dependency management is needed.
+Given the challenges of reproducing HEP applications, we now describe components of a framework that must be present for other researchers to effectively reproduce the application. 
+The framework consists of the following components (also shown in Figure \ref{}:
 
-Figure~\ref{fig:version-evolution} shows how we have evolved this artifact
-through several stages which make it more suitable for preservation.
-In each step of evolution, we make the dependencies of the artifact
-more explicit and available for analysis and automated processing.
-As noted in the previous section, the original author provided us with
-prose instructions by email which we translated into an
-executable script.  The executable script has embedded in it
-a number of external identifiers such as URLs pointing to repositories
-and paths to networked filesystems.  As a general programming practice,
-embedding such constants into the middle of a program is unwise, and so
-we extract all of those identifiers and place them \emph{outside} the
-script in a \emph{dependency map} or just \emph{map} for short.
-The dependency map lists all of the external dependencies of the application, indicating
-the type, how they are accessed, and where they are currently located.
-The resulting script then simply refers to abstract file locations such
-as \verb$GIT$ and \verb$CVMFS$, while the map file indicates where they
-are currently located. If properly constructed, the script should not refer to any external
-resource unless it is indicated in the dependency map.  We call this idealized
-artifact an \emph{abstract script}.
+\begin{itemize}
 
-By extracting the dependencies into the dependency map,
-we introduce great freedom for the curator to move, transform, and otherwise
-manipulate the dependencies of the artifact without damaging the artifact itself.
-A Figure~\ref{fig:version-evolution} shows, it is straightforward for an
-automated tool to examine
-all of the dependencies in the map, download those that are missing,
-and then modify the map to point to the local copies of the dependencies.
-If we group the script, dependency map, and dependencies into a \emph{package},
-we now have a self-contained artifact that can be moved from place to place.
-In some cases, it may be safe to allow the dependency map to refer to 
-trusted remote repositories.  Whether this is advisable is a judgment that
-must be made by the user or the curator, taking into account the long-term
-stability of said repositories.
+\item {\bf Capture} In audit phase, PTU captures the execution of the application into a package.
+The resulting package contains the source code, its dependencies (system files, and files on network such as from CernVM-FS) and the data consumed and written by the application.
 
-However, only having the package and the dependency map is not enough. The successful execution of the application on the original machine also relies on the configuration of environment variables.
-We collected the environment variables of the original machine and transformed it into one executable script.
+\item{\bf Preserve} The generated package is transferred to a Docker container of choice, instantiated from a vanilla, bare-bones image from a particular release (eg., CentOS 6.5, Fedora, or Ubuntu).
+The container provides a base execution environment for the package.
+Now, the container with the package can be saved as a docker image.
+
+\item {Distribute} The saved image can be stored and distributed in a repository like Docker Hub. We imagine these repositories would be preserved, and linked with a digital library.
+
+ There are a number of other considerations: is it practical to store the data with the image?
+What if the “application” requires many processing cores to complete its task?
+Can one preserve the “DNA” of the application in one small, practical step, yet store everything needed for future reproductions?
+xHow do we minimize the complexity of the image repository (hub), stemming unnecessary growth and profitably curating the collection?
+
+For purposes of preservation validation, a logical preservation unit (PLU) might be defined which consists of a minimal execution of the software using a small, test data sample, with specified outputs for comparison with future reproduction-validation runs.
+
+A DASPOS preservation testing environment might consist of:
+
+A collection of base images to be used when creating preserved platform-packages
+A tool set that assists users in the 1+2+3 steps outlined above
+A registry/repo service
+A validation service consisting of a number of container slots that can be started on demand
+A nightly testing service (Jenkins-like) that continuously monitors the reproducibility state of the preserved application + dependencies + environment + platform.
+
+\end{itemize}
+
+%\section{Evolving the Artifact}
+%
+%\begin{figure*}[t]
+%\centering
+%\includegraphics[width=.8\textwidth]{version-evolution.eps}
+%\caption{Version Evolution}
+%\label{fig:version-evolution}
+%\end{figure*}
+%
+%It is clear that the artifact, as provided, is not in a suitable form
+%for preservation.  While it might be technically possible to automatically
+%capture the entire virtual machine and all of the connected filesystems,
+%it would require 166.8TB of storage, which would be prohibitively expensive
+%for capturing this one application alone.  Further, if multiple
+%similar applications are preserved, we would miss the opportunity to identify
+%common dependencies and store them once for multiple artifacts.
+%A more structured approach to dependency management is needed.
+%
+%Figure~\ref{fig:version-evolution} shows how we have evolved this artifact
+%through several stages which make it more suitable for preservation.
+%In each step of evolution, we make the dependencies of the artifact
+%more explicit and available for analysis and automated processing.
+%As noted in the previous section, the original author provided us with
+%prose instructions by email which we translated into an
+%executable script.  The executable script has embedded in it
+%a number of external identifiers such as URLs pointing to repositories
+%and paths to networked filesystems.  As a general programming practice,
+%embedding such constants into the middle of a program is unwise, and so
+%we extract all of those identifiers and place them \emph{outside} the
+%script in a \emph{dependency map} or just \emph{map} for short.
+%The dependency map lists all of the external dependencies of the application, indicating
+%the type, how they are accessed, and where they are currently located.
+%The resulting script then simply refers to abstract file locations such
+%as \verb$GIT$ and \verb$CVMFS$, while the map file indicates where they
+%are currently located. If properly constructed, the script should not refer to any external
+%resource unless it is indicated in the dependency map.  We call this idealized
+%artifact an \emph{abstract script}.
+%
+%By extracting the dependencies into the dependency map,
+%we introduce great freedom for the curator to move, transform, and otherwise
+%manipulate the dependencies of the artifact without damaging the artifact itself.
+%A Figure~\ref{fig:version-evolution} shows, it is straightforward for an
+%automated tool to examine
+%all of the dependencies in the map, download those that are missing,
+%and then modify the map to point to the local copies of the dependencies.
+%If we group the script, dependency map, and dependencies into a \emph{package},
+%we now have a self-contained artifact that can be moved from place to place.
+%In some cases, it may be safe to allow the dependency map to refer to 
+%trusted remote repositories.  Whether this is advisable is a judgment that
+%must be made by the user or the curator, taking into account the long-term
+%stability of said repositories.
+%
+%However, only having the package and the dependency map is not enough. The successful execution of the application on the original machine also relies on the configuration of environment variables.
+%We collected the environment variables of the original machine and transformed it into one executable script.
 If another researcher wants to repeat the application, this executable script will be first executed.
-The environment variables refer to the dynamic named values defined in the range of one computer, like \verb!$PATH! and \verb!$PYTHONPATH!.
-However, the dependency map refers to the actual storage location of path variables used in one abstract script. For example, the actual storage location of the path variable \verb!CVMFS! 
-is {\tt /data/cvmfs/grid.cern.ch}.
-
-\begin{figure}
-\centering
-\includegraphics[width=.5\textwidth]{solution3.eps}
-\caption{Relationship of Roles}
-\label{fig:solution3}
-\end{figure}
-
-The relationship of different roles involved in the application preservation and
-reproduction is shown in Figure~\ref{fig:solution3}.  The original author uses the packaging utility to generate the package for one application.
-Then the package, together with
-its map file and description file will be published. When
-another researcher wants to repeat the application, one copy of the package will be downloaded into the new machine and the application can be repeated.
-
-When we try to repeat one application on one new machine, one map file is necessary for the relocation of the data access targets, as
-show in Figure~\ref{fig:version-evolution}. 
-The map file clearly defines the real location of each dependency in the format of dependency variables - the real location of dependency variable {\tt GIT} is \path{/data/git/cms-ttH} and the real location of dependency variable {\tt CVMFS}
-is {\tt /data/cvmfs/grid.cern.ch}.
-The script only refers to the dependency variables defined in the map file.
-This design decouples the application script and the actual data access targets, which minimizes the impact of the evolution of different data dependencies
-and ensures the transparent access.
-The modification of the package only introduces the minimal changes of the map file on the client side.
-
-This basic approach to dependency management is a step in the right direction
-for dependencies that are \emph{explicit} and \emph{external} to the
-user's native execution environment.  However, it leaves two other problems unsolved.
-
-First, the basic approach requires that someone be \emph{aware} of the dependencies,
-whether it be the end user, the system administrator, or the archive curator.
-It seems reasonable to expect the user to be aware of a large dependency mentioned in a top-level script.
-But, oftentimes the dependency is embedded invisibly deep within the software stack,
-or is connected to the machine by the local system administrators.  No single party
-is likely to have complete information about all of the dependencies.
-Second, the basic approach assumes that the entire dependency is actually
-consumed by the artifact.  As we have suggested above (and will show below),
-this sort of program often only consumes a small fraction of what it does declare
-as a dependency.
-
-To address both of these problems, users and curators alike need tools that
-will automatically observe the dependencies of complex applications, to
-facilitate automatic and efficient preservation.
+%The environment variables refer to the dynamic named values defined in the range of one computer, like \verb!$PATH! and \verb!$PYTHONPATH!.
+%However, the dependency map refers to the actual storage location of path variables used in one abstract script. For example, the actual storage location of the path variable \verb!CVMFS! 
+%is {\tt /data/cvmfs/grid.cern.ch}.
+%
+%\begin{figure}
+%\centering
+%\includegraphics[width=.5\textwidth]{solution3.eps}
+%\caption{Relationship of Roles}
+%\label{fig:solution3}
+%\end{figure}
+%
+%The relationship of different roles involved in the application preservation and
+%reproduction is shown in Figure~\ref{fig:solution3}.  The original author uses the packaging utility to generate the package for one application.
+%Then the package, together with
+%its map file and description file will be published. When
+%another researcher wants to repeat the application, one copy of the package will be downloaded into the new machine and the application can be repeated.
+%
+%When we try to repeat one application on one new machine, one map file is necessary for the relocation of the data access targets, as
+%show in Figure~\ref{fig:version-evolution}. 
+%The map file clearly defines the real location of each dependency in the format of dependency variables - the real location of dependency variable {\tt GIT} is \path{/data/git/cms-ttH} and the real location of dependency variable {\tt CVMFS}
+%is {\tt /data/cvmfs/grid.cern.ch}.
+%The script only refers to the dependency variables defined in the map file.
+%This design decouples the application script and the actual data access targets, which minimizes the impact of the evolution of different data dependencies
+%and ensures the transparent access.
+%The modification of the package only introduces the minimal changes of the map file on the client side.
+%
+%This basic approach to dependency management is a step in the right direction
+%for dependencies that are \emph{explicit} and \emph{external} to the
+%user's native execution environment.  However, it leaves two other problems unsolved.
+%
+%First, the basic approach requires that someone be \emph{aware} of the dependencies,
+%whether it be the end user, the system administrator, or the archive curator.
+%It seems reasonable to expect the user to be aware of a large dependency mentioned in a top-level script.
+%But, oftentimes the dependency is embedded invisibly deep within the software stack,
+%or is connected to the machine by the local system administrators.  No single party
+%is likely to have complete information about all of the dependencies.
+%Second, the basic approach assumes that the entire dependency is actually
+%consumed by the artifact.  As we have suggested above (and will show below),
+%this sort of program often only consumes a small fraction of what it does declare
+%as a dependency.
+%
+%To address both of these problems, users and curators alike need tools that
+%will automatically observe the dependencies of complex applications, to
+%facilitate automatic and efficient preservation.
+%

### 2015-01-12 intro.tex
Major cleanup

@@
 
------
-OLD TEXT
-
-Reproducibility is a cornerstone of the scientific process~\cite{borgman2012data}.
-In order to understand, verify, and build upon previous work,
-one must be able to first recreate previous results by applying
-the same methods. Historically, reproducibility has been
-accomplished through painstaking detailed documentation recorded
-in lab notebooks, which are then summarized in peer-reviewed publications.
-But as science increasingly depends on computation,
-reproducibility must also encompass the environments, data, and software
-involved in each result~\cite{zabolitzky2002preserving}. It is widely recognized that informal
-descriptions of software and systems -- although common -- are insufficient
-for reproducing a computational result accurately.
-A more automated and comprehensive approach is required.
-
-The reproduction of a computation has three broad components,
-each of which suggests somewhat different approaches:
-
-\begin{itemize}
-\item The {\bf computing environment}, consisting of the basic hardware and the operating system which can be preserved as physical artifacts or as a combination of virtual machine monitors (hardware) and virtual machine images (operating system)~\cite{matthews2009towards}.
-\item The {\bf scientific data} to be analyzed has historically received the most attention for curation.
+%-----
+%OLD TEXT
+%
+%Reproducibility is a cornerstone of the scientific process~\cite{borgman2012data}.
+%In order to understand, verify, and build upon previous work,
+%one must be able to first recreate previous results by applying
+%the same methods. Historically, reproducibility has been
+%accomplished through painstaking detailed documentation recorded
+%in lab notebooks, which are then summarized in peer-reviewed publications.
+%But as science increasingly depends on computation,
+%reproducibility must also encompass the environments, data, and software
+%involved in each result~\cite{zabolitzky2002preserving}. It is widely recognized that informal
+%descriptions of software and systems -- although common -- are insufficient
+%for reproducing a computational result accurately.
+%A more automated and comprehensive approach is required.
+%
+%The reproduction of a computation has three broad components,
+%each of which suggests somewhat different approaches:
+%
+%\begin{itemize}
+%\item The {\bf computing environment}, consisting of the basic hardware and the operating system which can be preserved as physical artifacts or as a combination of virtual machine monitors (hardware) and virtual machine images (operating system)~\cite{matthews2009towards}.
+%\item The {\bf scientific data} to be analyzed has historically received the most attention for curation.
 In a large, well-organized project, it may be stored in a  data repository or database management system, with associated documentation and a curation strategy.
 In a small effort, it could simply be a handful of files.
-\item The {\bf software environment} includes the source code, binaries, scripts, configuration files, and everything else needed to execute the desired code.
+%\item The {\bf software environment} includes the source code, binaries, scripts, configuration files, and everything else needed to execute the desired code.
 As with data, the software could be drawn from a well-managed software repository, or it could be a handful custom scripts that exist in the user's home directory.
-\end{itemize}
-
-In a very abstract sense, reproducing a computation is trivial.
-Assuming a computation is deterministic, one must simply
-preserve all of the inputs to a computation, then re-run
-the same code in an equivalent environment, and the same result
-will be produced.  For a small custom application on a modest
-amount of data, this could be accomplished by capturing the
-complete environment,
-data, and software within a single virtual machine image,
-and then depositing the virtual
-image into a curated environment.  The publication could
-then simply refer to the identifier of the image, which the
-interested reader can obtain and re-use. This approach has
-been used to some success with systems~\cite{castagne2013consider}.
-\footnote{Of course, we are glossing over the problem that hardware
-architectures and virtual machines also change, so one must also
-preserve the VMM software necessary to run the image.  The VMM itself
-depends on a software environment which must also be preserved.
-A long-term preservation system might end up running a whole
-stack of nested virtual machines in order to provide the desired
-environment! }
-
-However, this simple approach is not sufficient for large applications
-that are run in complex environments.
-
-\begin{itemize}
-\item There may be {\bf implicit dependencies} on items that are
-not apparent to the end user.  For example, they may understand that
-they rely on a particular data analysis package, but would have
-no reason to know that the package has further dependencies on
-other libraries and configuration files.  Or, they may know that
-the computation only runs correctly on a particular machine, but
-not know this is because it relies on a filesystem that
-is mounted only on that machine.
-
-\item The {\bf granularity} of the dependencies may not be well understood.
-For example, the user may understand that a computation depends upon
-a data collection that is 1TB in overall size, but not have detailed
-knowledge that it only requires three files totalling 300MB out of that
-whole collection.
-
-\item There may be dependencies upon {\bf networked resources} that
-are inherently external to the system, such as a database, a code
-repository~\cite{cms2006cmssw}, or a scalable filesystem~\cite{blomer2011cernvm}.  For such resources, it
-must be decided whether the dependency will simply be noted, or if it
-must be incorporated whole or in part.
-
-\item Where {\bf common dependencies} are widely used, it may be inefficient or
-impossible to store one copy of each dependency for each archived object.
-Some form of sharing or de-duplication is necessary in order to keep
-the archive to a reasonable size.
-\end{itemize}
-
-We do not claim to have solved these problems in any comprehensive
-way.  Rather, our aim in this paper is to highlight the scope
-of the problems by presenting a case study of one complex application.
-The application is presented to us
-first in the form of an email that describes in prose how to install
-the software and run the analysis.  We perform several successive
-refinements to convert it into an executable and preservable object.
-We then develop techniques for reducing the size of the dependencies
-that are necessary for the object to function, and we demonstrate
-the preserved object functioning correctly in three different
-physical and cloud environments.
-We describe how each of these techniques may interact with
-a future archive of preserved software artifacts, and conclude with
-some reflections on the challenges of preservation and advice for future efforts.
+%\end{itemize}
+%
+%In a very abstract sense, reproducing a computation is trivial.
+%Assuming a computation is deterministic, one must simply
+%preserve all of the inputs to a computation, then re-run
+%the same code in an equivalent environment, and the same result
+%will be produced.  For a small custom application on a modest
+%amount of data, this could be accomplished by capturing the
+%complete environment,
+%data, and software within a single virtual machine image,
+%and then depositing the virtual
+%image into a curated environment.  The publication could
+%then simply refer to the identifier of the image, which the
+%interested reader can obtain and re-use. This approach has
+%been used to some success with systems~\cite{castagne2013consider}.
+%\footnote{Of course, we are glossing over the problem that hardware
+%architectures and virtual machines also change, so one must also
+%preserve the VMM software necessary to run the image.  The VMM itself
+%depends on a software environment which must also be preserved.
+%A long-term preservation system might end up running a whole
+%stack of nested virtual machines in order to provide the desired
+%environment! }
+%
+%However, this simple approach is not sufficient for large applications
+%that are run in complex environments.
+%
+%\begin{itemize}
+%\item There may be {\bf implicit dependencies} on items that are
+%not apparent to the end user.  For example, they may understand that
+%they rely on a particular data analysis package, but would have
+%no reason to know that the package has further dependencies on
+%other libraries and configuration files.  Or, they may know that
+%the computation only runs correctly on a particular machine, but
+%not know this is because it relies on a filesystem that
+%is mounted only on that machine.
+%
+%\item The {\bf granularity} of the dependencies may not be well understood.
+%For example, the user may understand that a computation depends upon
+%a data collection that is 1TB in overall size, but not have detailed
+%knowledge that it only requires three files totalling 300MB out of that
+%whole collection.
+%
+%\item There may be dependencies upon {\bf networked resources} that
+%are inherently external to the system, such as a database, a code
+%repository~\cite{cms2006cmssw}, or a scalable filesystem~\cite{blomer2011cernvm}.  For such resources, it
+%must be decided whether the dependency will simply be noted, or if it
+%must be incorporated whole or in part.
+%
+%\item Where {\bf common dependencies} are widely used, it may be inefficient or
+%impossible to store one copy of each dependency for each archived object.
+%Some form of sharing or de-duplication is necessary in order to keep
+%the archive to a reasonable size.
+%\end{itemize}
+%
+%We do not claim to have solved these problems in any comprehensive
+%way.  Rather, our aim in this paper is to highlight the scope
+%of the problems by presenting a case study of one complex application.
+%The application is presented to us
+%first in the form of an email that describes in prose how to install
+%the software and run the analysis.  We perform several successive
+%refinements to convert it into an executable and preservable object.
+%We then develop techniques for reducing the size of the dependencies
+%that are necessary for the object to function, and we demonstrate
+%the preserved object functioning correctly in three different
+%physical and cloud environments.
+%We describe how each of these techniques may interact with
+%a future archive of preserved software artifacts, and conclude with
+%some reflections on the challenges of preservation and advice for future efforts.

### 2015-01-12 measure.tex
Major cleanup

@@
+\section{Component Tools for Reproducible Research}
+
 \section{Measuring Dependencies}
@@
 
-\subsection{Tracking of Network Dependencies}
-
-\begin{figure}
-\centering
-\includegraphics[width=.6\textwidth]{git-syscall.eps}
-\caption{Exec Syscalls of a git command}
-\label{fig:git-syscall}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=.6\textwidth]{http_packet.eps}
-\caption{HTTP Request and Response}
-\label{fig:http_packet}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=.6\textwidth]{url_redirection.eps}
-\caption{An Example of URL Redirection}
-\label{fig:url_redirection}
-\end{figure}
-
-All the dependencies of one program can be divided into three categories: local file system (e.g., /usr, /lib and /lib64), remote file systems which can be mounted as local directories (e.g., /cvmfs and /hdfs), and other remote network dependencies (e.g.
+%\subsection{Tracking of Network Dependencies}
+%
+%\begin{figure}
+%\centering
+%\includegraphics[width=.6\textwidth]{git-syscall.eps}
+%\caption{Exec Syscalls of a git command}
+%\label{fig:git-syscall}
+%\end{figure}
+%
+%\begin{figure}
+%\centering
+%\includegraphics[width=.6\textwidth]{http_packet.eps}
+%\caption{HTTP Request and Response}
+%\label{fig:http_packet}
+%\end{figure}
+%
+%\begin{figure}
+%\centering
+%\includegraphics[width=.6\textwidth]{url_redirection.eps}
+%\caption{An Example of URL Redirection}
+%\label{fig:url_redirection}
+%\end{figure}
+%
+%All the dependencies of one program can be divided into three categories: local file system (e.g., /usr, /lib and /lib64), remote file systems which can be mounted as local directories (e.g., /cvmfs and /hdfs), and other remote network dependencies (e.g.
 http, https and ssh).
-Through utilizing ptrace to trap each file-relevant system call used by a program, the first two categories of dependencies can be collected. 
-Motivation of tracking network dependencies: Linkrot is a common and great threat to the preservation of scientific applications.
+%Through utilizing ptrace to trap each file-relevant system call used by a program, the first two categories of dependencies can be collected. 
+%Motivation of tracking network dependencies: Linkrot is a common and great threat to the preservation of scientific applications.
 A URL which works normally today may be unavailable permanently.
 A method which can help the scientists figure out all the network dependencies of their applications provides the chance to evaluate the stability of each network dependencies and preserve the unstable network resources before linkrot happens.
-One direct solution to track the third category of dependencies is to utilize ptrace to check each exec system call used by a program and record each network-relevant executable and its parameters.
+%One direct solution to track the third category of dependencies is to utilize ptrace to check each exec system call used by a program and record each network-relevant executable and its parameters.
 However, an executable may create one or more child processes to finish some tasks, and a child process may create their own children processes.
@@
 The diversity of network-relevant executables and the large process tree generated for a network executable make this solution infeasible.
-
-Another solution to track network dependencies is to track the network sockets.
+%
+%Another solution to track network dependencies is to track the network sockets.
 The user process communicates with the network protocol stacks in the kernel through the network socket layer user interface on Linux.
@@
 The information gained from the network socket tracking can be divided into three categories.
-\begin{itemize}
-\item The information of network sockets used to communicate with remote network dependences (through socket and connect system calls) can be used to figure out the port number, service name (such as, http, https, and ssh), socket type (stream and datagram),  and the domain type (inet and inet6).
-\item The contents of DNS packets can be used to figure out the hostname and IP address of each remote network dependency. 
-\item As for applications based on http protocol, all the http requests and responses can be seen, as shown in Figure~\ref{fig:http_packet}.
+%\begin{itemize}
+%\item The information of network sockets used to communicate with remote network dependences (through socket and connect system calls) can be used to figure out the port number, service name (such as, http, https, and ssh), socket type (stream and datagram),  and the domain type (inet and inet6).
+%\item The contents of DNS packets can be used to figure out the hostname and IP address of each remote network dependency. 
+%\item As for applications based on http protocol, all the http requests and responses can be seen, as shown in Figure~\ref{fig:http_packet}.
 However, as for applications based on https and ssh which encrypt network data using TLS/SSL, tracking network data on the socket level can only see the encrypted data.
-\end{itemize}
-
-The results of tracking network sockets used by a program involves two categories of network resource redirections, dns-level hostname redirection and website-level url redirection. 
-\begin{itemize}
-\item dns-level hostname redirection: Each DNS packet includes five parts, header, question, answer, authority, and additional.
+%\end{itemize}
+%
+%The results of tracking network sockets used by a program involves two categories of network resource redirections, dns-level hostname redirection and website-level url redirection. 
+%\begin{itemize}
+%\item dns-level hostname redirection: Each DNS packet includes five parts, header, question, answer, authority, and additional.
 A DNS response packet with the type CNAME has multiple answers.
@@
 The first answer provides an alias of {\tt www3.nd.edu}, {\tt www-vip.cc.nd.edu}, and the second answer maps the alias to the IP address.
-{\tt www3.nd.edu} CNAME {\tt www-vip.cc.nd.edu}
-{\tt www-vip.cc.nd.edu} A {\tt 129.74.12.151}
-The CNAME-type DNS packets leave us a question, among the hostname used by the user, the alias(es), the IP address, what should we preserve?
-\item website-level url redirection: Website-level url redirection happens when a website updates its location and still want their old users access their resources using the old url.
+%{\tt www3.nd.edu} CNAME {\tt www-vip.cc.nd.edu}
+%{\tt www-vip.cc.nd.edu} A {\tt 129.74.12.151}
+%The CNAME-type DNS packets leave us a question, among the hostname used by the user, the alias(es), the IP address, what should we preserve?
+%\item website-level url redirection: Website-level url redirection happens when a website updates its location and still want their old users access their resources using the old url.
 Figure~\ref{fig:url_redirection} illustrates the url redirection between {\tt \url{www3.nd.edu/~ccl}} and {\tt ccl.cse.nd.edu}.
 Except for the difference of hostnames, the application layer protocols used by the old-version website and the new-version website is also different: the old website provides services through the https protocol, while the new website provides services through the http protocol.
-\end{itemize}
-
-The usage of https protocol makes detecting of website-level url redirections through tracking system calls more difficulty and even impossible.
+%\end{itemize}
+%
+%The usage of https protocol makes detecting of website-level url redirections through tracking system calls more difficulty and even impossible.
 All the application data will be encrypted at presentation layer through the TLS/SSL protocol, which is initialized at the session layer and works at the presentation layer.

### 2015-01-12 observation.tex
Major cleanup

@@
-\section{Observations}
+\section{Challenges and Observations in Reproducing HEP Applications}
 
-\emph{TauRoast} was provided to us in the form of an
+The \emph{TauRoast} and \emph{Athena} application specification was provided to us in the form of an
 email which described, in prose, how to obtain the source,
@@
 machine at our home institution, with no particular guarantee that
-it will run anywhere else in the world.
-Although this starting point may seem extreme, it is
-perfectly natural for collaborators to share configurations
-with each other in this form, and to rely on the presence
-of a working environment with appropriate dependencies already
-installed.  From this starting point, the authors played the
-role of curators, whose job it is to prepare the application
-for permanent archival.
+it will run anywhere else in the world. Such level of documentation and exchange of information about a software is typically routine in the scientific world. 
+We provide the challenges we faced in capturing the application details in a reproducible form and then preserving it for subsequent reuse:
 
-First, we elaborated the email instructions into an
-executable script that obtains the dependencies and then
-executes the analysis.  The script declares the necessary
-environment variables, downloads and checks out the necessary source code,
-builds it appropriately, calls initialization scripts in
-the dependent software, and then runs the analysis.
-A few rounds of correction with the original author were necessary
-to obtain all the dependencies and run the artifact correctly.
-(The original instructions introduced in the email also indicated how to run the application
-within a production batch system.  For the purposes of preservation,
-we consider the execution infrastructure to be distinct from the application,
-and leave it out of consideration for now.)
-
-The process of elaborating the program into a script revealed
-several observations about this type of application:
+%\comment{Although this starting point may seem extreme, it is
+%perfectly natural for collaborators to share configurations
+%with each other in this form, and to rely on the presence
+%of a working environment with appropriate dependencies already
+%installed.  From this starting point, the authors played the
+%role of curators, whose job it is to prepare the application
+%for permanent archival.
+%
+%First, we elaborated the email instructions into an
+%executable script that obtains the dependencies and then
+%executes the analysis.  The script declares the necessary
+%environment variables, downloads and checks out the necessary source code,
+%builds it appropriately, calls initialization scripts in
+%the dependent software, and then runs the analysis.
+%A few rounds of correction with the original author were necessary
+%to obtain all the dependencies and run the artifact correctly.
+%(The original instructions introduced in the email also indicated how to run the application
+%within a production batch system.  For the purposes of preservation,
+%we consider the execution infrastructure to be distinct from the application,
+%and leave it out of consideration for now.)
+%
+%The process of elaborating the program into a script revealed
+%several observations about this type of application:}
 
@@
 
-\item {\bf Many Explicit External Dependencies.}  TauRoast depends on a large number of
-external dependencies, each with a different access method and data source.
-While we knew in advance that it depended upon the large CMSSW distribution,
-it was not apparent until elaborating the script that it depended upon
-two different Github repositories for the Tau source,
-a CVS server at CERN for some configuration information, a public web page
-for the PyYAML library, and the public home page of a Notre Dame student
-for one missing header file.  (The latter is particularly troubling!)
-While, at some level, the authors and users of these software know of these dependencies, they are often missing in
-informal communications or forgotten once the dependency is installed.
-However, once known, they are at least expressed explicitly within the script.
+\item {\bf Many Explicit External Dependencies.}  Due to the distributed nature of HEP applications, the applications typically depend on a large number of networked external resources. 
+Capturing these dependencies is straightforward if they are static in nature and the resources can be accessed without secure cryptographic functions. 
+For instance, in TauRaoast some source code external dependencies can be obtained by simply downloading the specific libraries from a web page. 
+However, other static dependencies require making secure connections to Github resources, and CVS servers for downloading source. 
+While TauRoast is completely local in its execution, dynamic remote dependencies that arise in a distributed execution require auditing dependencies on all machines where execution takes place.
 
-\item {\bf Many Implicit Local Dependencies.} A much harder problem is that the
-application assumed the presence of many different components in the local
-filesystem view. It would be tempting to capture all of these by simply
-storing a virtual machine image containing the local filesystem. However,
-the application depended on no less than {\bf five} networked filesystems
-available on a particular machine available to the author:
-the data to be analyzed was stored on an HDFS~\cite{borthakur2008hdfs} cluster,
+%\begin{TM} 
+%each with a different access method and data source.
+%While we knew in advance that it depended upon the large CMSSW distribution,
+%it was not apparent until elaborating the script that it depended upon
+%two different Github repositories for the Tau source,
+%a CVS server at CERN for some configuration information, a public web page
+%for the PyYAML library, and the public home page of a Notre Dame student
+%for one missing header file.  (The latter is particularly troubling!)
+%While, at some level, the authors and users of these software know of these dependencies, they are often missing in
+%informal communications or forgotten once the dependency is installed.
+%However, once known, they are at least expressed explicitly within the script.
+%\end{TM}
+
+\item {\bf Many Implicit Local Dependencies.} The application data and code is distributed on five networked filesystems, which are 
+typically mounted on a particular machine that is made accessible to the application developer.
+In TauRoast the a large amount of data to be analyzed was stored on an HDFS~\cite{borthakur2008hdfs} cluster,
 some configuration data was stored on a CVMFS~\cite{blomer2011cernvm} filesystem,
 and a variety of software tools were on an NFS~\cite{howard1988scale},
-PanFS~\cite{welch2008scalable} and AFS~\cite{sandberg1985design} systems.
-The original authors were not aware of many of these dependencies,
-because they simply relied on local administrators to configure the
-software and make it available.
+PanFS~\cite{welch2008scalable} and AFS~\cite{sandberg1985design} systems. In \emph{Athena} the data and code were available through CVMFS filesystem. 
+Since these filesystems appear local to the application machine, it is important to check and capture mounted filesystems and their respective mount points.
 
-\item {\bf Configuration Complexity.}  As a means of controlling the complexity
-of dependent software packages, the high energy physics community has developed
-a number of tools that perform run-time configuration and consistency checks
-of the available software.  {\tt scram} is the software management tool used
-by the CMS experiment.  Before running any code, {\tt scram} is used to locate
+%\begin{TM}A much harder problem is that the
+%application assumed the presence of many different components in the local
+%filesystem view. It would be tempting to capture all of these by simply
+%storing a virtual machine image containing the local filesystem. However,
+%the application depended on no less than {\bf five} networked filesystems
+%available on a particular machine available to the author:
+%the data to be analyzed was stored on an HDFS~\cite{borthakur2008hdfs} cluster,
+%some configuration data was stored on a CVMFS~\cite{blomer2011cernvm} filesystem,
+%and a variety of software tools were on an NFS~\cite{howard1988scale},
+%PanFS~\cite{welch2008scalable} and AFS~\cite{sandberg1985design} systems.
+%The original authors were not aware of many of these dependencies,
+%because they simply relied on local administrators to configure the
+%software and make it available.\end{TM}
+
+\item {\bf Configuration Complexity.} To correctly reproduce an application implies that run-time configurations and consistency checks on the available software are effective captured and preserved. 
+For CMS,  {\tt scram} software management tool, is used to locate
 the appropriate version of software,  set environment variables such as the PATH, run any
-tool-specific configuration, and do the same for all software on which it depends.
-If the correct versions are not available, {\tt scram} halts and emits an error.
-While this procedure has great value for consistency, it also introduces a significant cost
-because it involves a large number of nested scripts traversing a filesystem,
-repeatedly looking up metadata.  In our example, the time to perform this configuration
-with a cold cache is about 14 minutes, which is almost as large as the actual analysis
-run, which takes 20 minutes.
+tool-specific configuration, and do the same for all software on which it depends. A reproducible framework must capture the working of such software management tools so that they can conduct similar
+checks on a new machine.
 
-\begin{figure*}[t]
-\centering
-\includegraphics[width=.8\textwidth]{version-evolution.eps}
-\caption{Version Evolution}
-\label{fig:version-evolution}
-\end{figure*}
+%\begin{TM}As a means of controlling the complexity
+%of dependent software packages, the high energy physics community has developed
+%a number of tools that perform run-time configuration and consistency checks
+%of the available software. {\tt scram} is the software management tool used
+%by the CMS experiment.  Before running any code, {\tt scram} is used to locate
+%the appropriate version of software,  set environment variables such as the PATH, run any
+%tool-specific configuration, and do the same for all software on which it depends.
+%If the correct versions are not available, {\tt scram} halts and emits an error.
+%While this procedure has great value for consistency, it also introduces a significant cost
+%because it involves a large number of nested scripts traversing a filesystem,
+%repeatedly looking up metadata.  In our example, the time to perform this configuration
+%with a cold cache is about 14 minutes, which is almost as large as the actual analysis
+%run, which takes 20 minutes.\end{TM}
 
-\item {\bf High Selectivity.}  Although the total size of the resources accessed by this
-program is very large, the size of the data and software actually used are much smaller.
+\item {\bf High Selectivity.}  
+Although the total size of the resources accessed by HEP
+programs is very large, the size of the data and software actually used are much smaller.
 Often, an entire repository or data source is named within the script, but the program
@@
 (For example, our original script includes the Open Science Grid software stack in the PATH, but does not actually use it.)
-We suspect that end users are accustomed to missing dependencies and thus get in the habit of adding commonly used software,
-whether it is needed or not.
+%We suspect that end users are accustomed to missing dependencies and thus get in the habit of adding commonly used software,
+%whether it is needed or not. 
+Thus there is a size tradeoff of capturing dependencies mentioned in the program and dependencies actually used in the program.
+A reproducible framework must include robust rules about not including superfluous dependencies, but including unused dependencies that may potentially get used during program execution.
 
@@
 to a new operating system, and the application deprecated the use of CVS for obtaining
-the software.  While the users of this software seem be accustomed to constant change,
+the software. In Athena, the computing environment can potentially change daily, since upgrades to the software framework occur on a nightly basis.  
+While the users of this software seem be accustomed to constant change,
 any preservation technique will have to be very cautious about relying upon an
@@
 
+\item {\bf Additional Dependencies.} Capturing the necessary and sufficient dependencies that are part of an application is sufficient for repeatability, but possibly for not reproducibility, where is different additional modules
+must also be preserved so that the resulting application can be extended properly.
+In Athena framework, for instance, the software library needed to include basic software programs such as make, awk, sed that can aid further development.
 \end{itemize}

### 2015-01-12 evolution.tex
Framework

@@
 
-Given the challenges of reproducing HEP applications, we now describe components of a framework that must be present for other researchers to effectively reproduce the application. 
-The framework consists of the following components (also shown in Figure \ref{}:
+Given the many challenges of reproducing HEP applications, we now describe a formal framework, which if present within large collaborations, can enable application developers to share their 
+application with other researchers, and for other researchers to reproduce the shared application. In effect, the framework itself should be 
+be invariant to changes in who owns the application (the developer or the reproducer), where it was built and compiled. To satisfy invariance, the framework must include mechanisms for:
 
@@
 
-\item {\bf Capture} In audit phase, PTU captures the execution of the application into a package.
+\item {\bf Capturing Dependencies and Configurations:} Capturing tools must record dependencies that are used by the program, including hardware, OS, kernels, static and dynamic dependencies, local and networked depedencies, source codes and data files.
+Stateful interactions with commercial software, such as proprietary databases and which cannot be captured due to licensing agreements must be persisted so that they can replayed later without the presence of the commercial software.
+In effect, a captured application should behave exactly the same way as the application developer intended it to be.
+% In audit phase, PTU captures the execution of the application into a package.
 The resulting package contains the source code, its dependencies (system files, and files on network such as from CernVM-FS) and the data consumed and written by the application.
 
-\item{\bf Preserve} The generated package is transferred to a Docker container of choice, instantiated from a vanilla, bare-bones image from a particular release (eg., CentOS 6.5, Fedora, or Ubuntu).
-The container provides a base execution environment for the package.
-Now, the container with the package can be saved as a docker image.
+\item{\bf Preservation of Captured Entities:} By preservation we imply appropriate mechanisms for (i) documentation of the application development, and (b) automation of any task that becomes inevitably
+necessary for repeating the application in exactly the same way as the developer executed it.
 
-\item {Distribute} The saved image can be stored and distributed in a repository like Docker Hub. We imagine these repositories would be preserved, and linked with a digital library.
+Documentation and specification during application development can be a onerous. The preservation framework must make literate programming tools available that 
+focus less on documentation, but script, integrate and execute the dependencies so that they are resolved as part of documentation. 
+Automation can extend to various tasks that are necessary for ensuring repeatability such as building software, provisioning of hardware, 
+validation of software against security fixes, new features, or deprecation of old software, and even monitoring the reproducibility state of a preserved application, i.e., its source code, dependencies, environment, and platform.
+Automated builds and provisioning and continuous integration service can significantly lower the barrier to run the application in a new environment.
 
- There are a number of other considerations: is it practical to store the data with the image?
-What if the “application” requires many processing cores to complete its task?
-Can one preserve the “DNA” of the application in one small, practical step, yet store everything needed for future reproductions?
-xHow do we minimize the complexity of the image repository (hub), stemming unnecessary growth and profitably curating the collection?
+In spite of the preservation mechanisms, the application software may not run as intended. For a reproducer's understanding, it may also be useful to include 
+a \emph{logical preservation unit} (PLU) that consists of a minimal execution of the software using a small, test data sample, and with specified outputs.
+The provenance of this PLU must be captured so that the reproducer can make comparison with future reproduction-validation runs.
 
-For purposes of preservation validation, a logical preservation unit (PLU) might be defined which consists of a minimal execution of the software using a small, test data sample, with specified outputs for comparison with future reproduction-validation runs.
-
-A DASPOS preservation testing environment might consist of:
-
-A collection of base images to be used when creating preserved platform-packages
-A tool set that assists users in the 1+2+3 steps outlined above
-A registry/repo service
-A validation service consisting of a number of container slots that can be started on demand
-A nightly testing service (Jenkins-like) that continuously monitors the reproducibility state of the preserved application + dependencies + environment + platform.
+\item {\bf Distribution of Preserved Packages:} A captured and preserved application must be persistently stored and distributed through a repository.
+We imagine these repositories to be themselves preserved, and linked with a digital library.
+Metadata and flexible annotation should be part of this repository for curation over time.
 

### 2015-01-13 measure.tex
More changes

@@
 \section{Component Tools for Reproducible Research}
+
+We describe some tools that can be used as part of the reproducible framework, and ensure invariance:
+
+\subsection{Capture tools} For capture we focus on automated tools for capturing dependencies (both software and data) instead of manual tools such as makefiles and configuration scripts, since the latter cannot ensure invariance.
+%Parrot
+
+\vspace{5pt}
+\noindent {\bf Parrot} Parrot is a virtual filesystem access tool which has been used to attach
+existing programs to a variety of remote I/O systems, such as HTTP, FTP, and CVMFS.
+It works by trapping an application's system calls through the Linux {\tt ptrace} debugging
+interface, and then replacing them with the desired I/O operations. 
+To capture dependencies, Parrot records a \emph{namelist} which lists all 
+of the files that an application actually accesses. Using the namelist, Parrot creates a \emph{reduced package} which contains
+only the files actually used by the application.
+
+Being tightly integrated with I/O systems, the Parrot virtual filesystem is required to be installed for both audit and execution to allow for reproducibility.
+In the high energy physics community, Parrot is already used to 
+provide access to the CMSSW software distribution via the CVMFS distributed file system.
+and is thus invariant for applications like TauRoast. However, unless installed, Parrot cannot ensure invariance for general applications.
+
+% PTU
+\vspace{5pt}
+\noindent{\bf CDE} CDE creates a package of an application by recording program binaries, libraries, scripts, data files, and environment variables, etc.
+It also uses the UNIX ptrace system call interposition to identify the code and data used by the running application.
+The original CDE as available through [13,12] was limited to major Linux kernel versions (e.g.
+2.6.x), but we have removed that restriction by adapting it for the newly released Linux kernel 3.0 as well as for Mac OS X \cite{}.
+Thus CDE, unlike Parrot, provides OS invariance and does not require installation and configuration.
+
+\subsection{Preservation tools}
+
+% Parrot package
+\vspace{5pt}
+\noindent{\bf Parrot:} In Parrot, the package is preserved based on user option.  
+In a {\bf shallow copy}, only individual files in the namelist are copied,
+creating only parent directories for each.  Where a directory was listed,
+a directory is created and populated with empty files as placeholders
+to facilitate a directory listing.  In a {\bf medium copy}, 
+individual files are copied as before and directory contents, one level deep are copied. A {\bf deep copy}, which can duplicate all directories recursively,
+resulting in TB-sized packages, is not allowed.
+
+% PTU package
+\vspace{5pt}
+\noindent{\bf CDE:} In CDE, the complete package is preserved, consisting of all code and data files, however deep the data path is present. 
+However, a CDE binary only captures a single execution path, which is the execution path taken during run-time.
+If different execution paths need different types of dependencies, some dependencies may be left out.
+To preserve these dependencies, we have added addition functionality to CDE.
+In particular, information about other static binaries and required static shared libraries, such as version number, released version of shared libraries, and associated kernel distribution, is preserved using UNIX commands file, ldd, strings, and objdump.
+We also have added a provenance wrapper over CDE.
+This provenance wrapper documents all the dependencies, and provides information about process execution times and memory consumption.
+It creates a graph of the reference execution providing details about how data was created and transformed as part of the execution.
+Thus instead of a PLU, a description of the PLU exists in the package.
+
+Neither the Parrot packages or extended CDE package provide a literate programming environment or a continuous integration environment for changes in software.
+Thus they are partially preserved but not completely.
+
+% Docker images
+
+\subsection{Deployment  Repositories}
+image can be stored and distributed in a repository like Docker Hub. 
+The Hub also provides a convenient dis- tribution service, freely storing the pre-built images, along with their metadata, for download and reuse by others. 
+   The Docker Hub is a free service and an open source software product so that users can run their own private versions of the Hub on their own servers, for instance, if security of the data or the longevity of the public platform is a concern.
 
@@
 
-We have developed a prototype tool to assist in the measurement and preservation
-of implicit dependencies for complex applications.
-We use Parrot~\cite{thain2005parrot} to explicitly record all
-of the files accessed by our example application, allowing us to observe how
-much of each external dependencies is used, and what local resources are implicitly used.
-Using this information, we create a \emph{reduced package} which contains
-only the files actually used by the application.
-
-Parrot is a virtual filesystem access tool which has been used to attach
-existing programs to a variety of remote I/O systems, such as HTTP, FTP, and CVMFS.
-It works by trapping an application's system calls through the Linux {\tt ptrace} debugging
-interface, and then replacing them with the desired I/O operations.  Parrot is already used
-in the high energy physics community with applications like TauRoast specifically to 
-provide access to the CMSSW software distribution via the CVMFS distributed file system.
-We made small modifications to Parrot to record a \emph{namelist} which lists all 
-of the files that an application actually accesses.
-
-Figure~\ref{fig:workflow-parrot} illustrates the measurement process.
-The starting point of this toolkit is one successful execution of the application on the native machine.
-First, we execute the actual data analysis script under Parrot to generate the namelist.
-Then, using the namelist, we generate a package containing all the necessary data
-and software for one analysis program. When another
-researcher wants to repeat the program, he only needs to obtain the package and
-execute the actual analysis program inside the package.
-
-For one execution of \emph{TauRoast}, the generated namelist includes 132,047 accessed filenames,
-along with the system calls used to access the file, such as {\tt open}, {\tt stat}, {\tt read}, etc.
-With duplicate filenames removed, the list is reduced to 67,168 files.
-Many of those entries do not exist, because they reflect attempts
-by the application to search for programs and libraries in multiple places.
-Only 22,068 entries reflect existing files or directories.
-
-The packaging tool iterates over each item of the filename list, determines the process
-mode and replication degree according to the file type (common files,
-directories, symbolic links) and the system call type, generates one package
-containing the dependencies, and summarizes the contents of the package
-as shown in Table~\ref{table:package-info}.  To the extent possible,
-the filesystem structure of the original environment is preserved.
-
-We considered several approaches to constructing the package.
-In a {\bf shallow copy}, we only copied the individual files in the namelist,
-creating only parent directories for each.  Where a directory was listed,
-we created the directory and populated it with empty files as placeholders
-to facilitate a directory listing.  In a {\bf medium copy}, we copied the
-individual files as before.  Where a directory was listed, we created
-the directories and copied the contents of the files in that directory,
-one level deep.  A {\bf deep copy} would duplicate all directories recursively,
-but this would have resulted in TB-sized packages, so we did not consider
-it further.
-
-Parrot is required to re-run the packaged artifact, in order to force
-the packaged files to appear to exist in their original locations.
-To this end, the packaging tool creates a \emph{file map} which maps
-the logical names of the files to their current physical locations, as shown in Table~\ref{table:map-file}.
-Parrot reads the file map and redirects system calls at run-time to achieve the desired effect.
-As the example suggests, special device files such as {\tt /proc} and {\tt /dev}
-are not incorporated into the package but are instead accessed natively.
-
-\begin{table}
-    \centering
-    \begin{tabular}{ll}
-    \hline
-    \bf Path used in Program & \bf Actual Location \\ \hline
-    {\tt /} & {\tt /tmp/package-hep} \\ \hline
-    {\tt /tmp/package-hep} & {\tt /tmp/package-hep} \\ \hline
-    {\tt /dev} & {\tt /dev} \\ \hline
-    {\tt ...} & {\tt ...}\\ \hline
-    \end{tabular}
-    \caption{Structure of Map File}
-    \label{table:map-file}
-\end{table}
-
-\begin{table}
-    \centering
-    \begin{tabular}{rrr}
-\hline
-                    & \bf Shallow Copy & \bf Medium Copy\\
-\hline
-    Whole Files    & 1632         & 15642\\ 
-\hline
-    Empty Files    & 14273        & 263\\
-\hline
-    Directories    & 1549         & 1549\\ 
-\hline
-    Symbolic Links & 4614         & 4614 \\
-\hline
-    \bf Total Size & \bf 21GB     & \bf 28GB \\ 
-\hline
-    \end{tabular}
-    \caption{Package Information}
-    \label{table:package-info}
-\end{table}
+%We have developed a prototype tool to assist in the measurement and preservation
+%of implicit dependencies for complex applications.
+%We use Parrot~\cite{thain2005parrot} to explicitly record all
+%of the files accessed by our example application, allowing us to observe how
+%much of each external dependencies is used, and what local resources are implicitly used.
+%Using this information, we create a \emph{reduced package} which contains
+%only the files actually used by the application.
+%
+%Parrot is a virtual filesystem access tool which has been used to attach
+%existing programs to a variety of remote I/O systems, such as HTTP, FTP, and CVMFS.
+%It works by trapping an application's system calls through the Linux {\tt ptrace} debugging
+%interface, and then replacing them with the desired I/O operations.  Parrot is already used
+%in the high energy physics community with applications like TauRoast specifically to 
+%provide access to the CMSSW software distribution via the CVMFS distributed file system.
+%We made small modifications to Parrot to record a \emph{namelist} which lists all 
+%of the files that an application actually accesses.
+%
+%Figure~\ref{fig:workflow-parrot} illustrates the measurement process.
+%The starting point of this toolkit is one successful execution of the application on the native machine.
+%First, we execute the actual data analysis script under Parrot to generate the namelist.
+%Then, using the namelist, we generate a package containing all the necessary data
+%and software for one analysis program. When another
+%researcher wants to repeat the program, he only needs to obtain the package and
+%execute the actual analysis program inside the package. 
+%
+%For one execution of \emph{TauRoast}, the generated namelist includes 132,047 accessed filenames,
+%along with the system calls used to access the file, such as {\tt open}, {\tt stat}, {\tt read}, etc.
+%With duplicate filenames removed, the list is reduced to 67,168 files.
+%Many of those entries do not exist, because they reflect attempts
+%by the application to search for programs and libraries in multiple places.
+%Only 22,068 entries reflect existing files or directories.
+%
+%The packaging tool iterates over each item of the filename list, determines the process
+%mode and replication degree according to the file type (common files,
+%directories, symbolic links) and the system call type, generates one package
+%containing the dependencies, and summarizes the contents of the package
+%as shown in Table~\ref{table:package-info}.  To the extent possible,
+%the filesystem structure of the original environment is preserved.
+%
+%We considered several approaches to constructing the package.
+%In a {\bf shallow copy}, we only copied the individual files in the namelist,
+%creating only parent directories for each.  Where a directory was listed,
+%we created the directory and populated it with empty files as placeholders
+%to facilitate a directory listing.  In a {\bf medium copy}, we copied the
+%individual files as before.  Where a directory was listed, we created
+%the directories and copied the contents of the files in that directory,
+%one level deep.  A {\bf deep copy} would duplicate all directories recursively,
+%but this would have resulted in TB-sized packages, so we did not consider
+%it further.
+%
+%Parrot is required to re-run the packaged artifact, in order to force
+%the packaged files to appear to exist in their original locations.
+%To this end, the packaging tool creates a \emph{file map} which maps
+%the logical names of the files to their current physical locations, as shown in Table~\ref{table:map-file}.
+%Parrot reads the file map and redirects system calls at run-time to achieve the desired effect.
+%As the example suggests, special device files such as {\tt /proc} and {\tt /dev}
+%are not incorporated into the package but are instead accessed natively.
+%
+%\begin{table}
+%    \centering
+%    \begin{tabular}{ll}
+%    \hline
+%    \bf Path used in Program & \bf Actual Location \\ \hline
+%    {\tt /} & {\tt /tmp/package-hep} \\ \hline
+%    {\tt /tmp/package-hep} & {\tt /tmp/package-hep} \\ \hline
+%    {\tt /dev} & {\tt /dev} \\ \hline
+%    {\tt ...} & {\tt ...}\\ \hline
+%    \end{tabular}
+%    \caption{Structure of Map File}
+%    \label{table:map-file}
+%\end{table}
+%
+%\begin{table}
+%    \centering
+%    \begin{tabular}{rrr}
+%\hline
+%                    & \bf Shallow Copy & \bf Medium Copy\\
+%\hline
+%    Whole Files    & 1632         & 15642\\ 
+%\hline
+%    Empty Files    & 14273        & 263\\
+%\hline
+%    Directories    & 1549         & 1549\\ 
+%\hline
+%    Symbolic Links & 4614         & 4614 \\
+%\hline
+%    \bf Total Size & \bf 21GB     & \bf 28GB \\ 
+%\hline
+%    \end{tabular}
+%    \caption{Package Information}
+%    \label{table:package-info}
+%\end{table}
 

### 2015-01-13 observation.tex
More changes

@@
 
-\item {\bf Many Explicit External Dependencies.}  Due to the distributed nature of HEP applications, the applications typically depend on a large number of networked external resources. 
+\item {\bf Explicit External Dependencies.}  Due to the distributed nature of HEP applications, the applications typically depend on a large number of networked external resources. 
 Capturing these dependencies is straightforward if they are static in nature and the resources can be accessed without secure cryptographic functions. 
@@
 
-\item {\bf Many Implicit Local Dependencies.} The application data and code is distributed on five networked filesystems, which are 
+\item {\bf Implicit Local Dependencies.} The application data and code is distributed on five networked filesystems, which are 
 typically mounted on a particular machine that is made accessible to the application developer.
@@
 HDFS filesystem with 11.6TB of data, but only 20GB are actually consumed by the program. 
-The reason for this great reduction is at first each BEAN event contains a large amount of information, and the TauAnalysis throws away a lot of the irrelevant event information, keeping only the relevant bits.
-The CMSSW repository is 88.1GB in total
-but only 448.3MB of source is checked out, and the actually used software only
-measured 6.3MB.  In a few cases, a source of software is named but never actually accessed.
-(For example, our original script includes the Open Science Grid software stack in the PATH, but does not actually use it.)
+%The reason for this great reduction is at first each BEAN event contains a large amount of information, and the TauAnalysis throws away a lot of the irrelevant event information, keeping only the relevant bits.
+%The CMSSW repository is 88.1GB in total
+%but only 448.3MB of source is checked out, and the actually used software only
+%measured 6.3MB.  In a few cases, a source of software is named but never actually accessed.
+%(For example, our original script includes the Open Science Grid software stack in the PATH, but does not actually use it.)
 %We suspect that end users are accustomed to missing dependencies and thus get in the habit of adding commonly used software,
@@
 
-\item {\bf Additional Dependencies.} Capturing the necessary and sufficient dependencies that are part of an application is sufficient for repeatability, but possibly for not reproducibility, where is different additional modules
+\item {\bf Dependencies for Reproducible Execution.} Capturing the necessary and sufficient dependencies that are part of an application is sufficient for repeatability, but possibly for not reproducibility, where is different additional modules
 must also be preserved so that the resulting application can be extended properly.

### 2015-01-14 evaluation.tex
Add Evaluation Section

@@
 
-We evaluated the correctness of the reduced package and the overhead of generating the package.
-To do this, the application was repeated with the help of \emph{Original Script} (as shown in Figure~\ref{fig:version-evolution}) on the original machine. 
-Then one \emph{reduced package} was generated and verified with the help of Parrot on the original machine.
+We evaluated and compared the correctness and performance of running, packaging, and re-running the Tauroast application using Parrot and PTU.
+To do this, the application was first executed directly, its execution time and output were recorded.
+Then the application was executed under Parrot and PTU, and a self-contained package was created for each case.
+Finally, the application was re-executed using the package.
+The time overhead of each execution and re-execution was collected and compared with the recorded reference.
 
-Then, two different virtual machines (VM) - one VM from the Notre Dame Cloud Platform based on KVM and one VM from the Amazon EC2 Platform based on Xen, were employed to further verify the correctness of the reduced package.
-
-We first repeated the example from scratch using the Script translated from the original email on the original machine and counted the time consumption and data size. 
-Then based on the successful execution of Original Script, we evaluated Reduced Package - one package containing necessary dependencies is generated, and then the time consumption and data size is analyzed.
-
-To measure time consumption, we counted the time used to obtain remote software dependencies, build the environment, and analyze the dataset.
-We also counted the time used to obtain the namelist and to generate the package.
-To measure data size, we can easily figure out the size of each data and code source inside the package under Reduced Package.
-Original Script does not support mining of implicit dependencies.
-As for remote sources, we can figure out the named size through the analysis script.
-However, it is hard to figure out the named size of each local source.
-Instead, we only knew that total size of each file system is very large.
-
-Table~\ref{table:time-2nd3rd} shows the execution time comparison between
-Original Script and Reduced Package.
-Reduced Package is faster than Original Script, because all the software copied into the package has been compiled and the Software Acquisition stage is not necessary.
-and all the environment building only takes 4 seconds,
-We were surprised that Reduced Package even reduces the actual analysis time. 
-The reason for this is that data is obtained through accessing HDFS in Original Script, but is copied into the package in Reduced Package.
-This localization of experimental data speeds up the data analysis process, resulting the actual analysis time reducing from 20 minutes to 13 minutes.
+The Tauroast application checks and evaluates a dataset with the size of 18 GB stored in HDFS, and can be finished about 20 minites when running directly on a server with 64 cores and 126 GB memory.
+The output of the application includes the dataset analysis log and a complete statistics information, and its size is 289 KB.
 
@@
     \centering
-    \begin{tabular}{lrr}
+    \begin{tabular}{lccc}
     \hline
-    \bf Task Category & \bf Original Script & \bf Reduced Package \\ \hline
-    Obtain Namelist & N/A & 28min 28s \\ \hline
-    Generate Package & N/A & 85min 51s \\ \hline
-    Software Acquisition & 8min 11s & N/A \\ \hline
-    Environment Build & 5min 49s  & 4s \\ \hline
-    Analysis Code & 20min 31s & 13min 04s \\ \hline
+    \bf Tool Type & \bf Package Creation Time & \bf Re-Execution Time & \bf Package Size \\ \hline
+	Parrot & 27 min 15 sec & 10 min 24 sec & 17.57 GB \\ \hline
+	PTU & 23 min 30 sec & 8 min 40 sec & 17.57 GB \\ \hline 
     \end{tabular}
-    \caption{Execution Time Comparison between Original Script and Reduced Package}
-    \label{table:time-2nd3rd}
+    \caption{Performance Comparison between Parrot and PTU}
+    \label{table:parrot_ptu}
 \end{table}
 
-Table~\ref{table:time-2nd3rd} also illustrates the time used to
-obtain the namelist and to generate the package. 
-The time used for these two steps is longer than the execution time,
-because each filename of the list, together with its system call type, needs to be checked, and the structure of each directory item must be maintained.
-However, 
-this is only done once.
-Once the package is
-generated, many users can directly obtain the package and repeat the application 
-separately.
+Table~\ref{table:parrot_ptu} compares the performance of preserving the Tauroast application using Parrot and PTU.
+PTU accommplishes the execution procedure and packaging procedure concurrently through multi-threading, bringing 17.5\% additional time overhead.
+Parrot splits the packaging creation procedure into two sequential steps: first, execute the application within Parrot and generate the accessed file namelist (takes 22 min 50 sec); second, traverse the namelist and copy all the accessed files into a self-contained package (takes 4 min 25 sec).
 
-Table~\ref{table:size-original-real} on page 2 illustrates the total size, named size in the example and actually used size of each remote source (the first 4 items) and local source (the remaining 5 items).
-The third column corresponds to the data size of Reduced Package and can be easily figured out, because all the necessary data has been copied into the package.
-Original Script does not support measuring implicit dependencies.
-As for remote sources, we can figure out the named size through the analysis script.
-However, it is hard to figure out the named size of each local source.
-Instead, we only knew that total size of each file system is very large.
+The re-execution time is half or less than half of the original execution time in both cases.
+During the original execution, the input dataset comes from HDFS, which is accessed through FUSE.
+During the package creation procedure, all the input dataset has been copied from HDFS into the package on the local fielsytem.
+So, the re-execution procedure can get its input from the local filesystem instead of obtaining the input dataset from HDFS.
+PTU re-runs the application faster than Parrot due to its efficient internal implementation.
+
+Both packages created by Parrot and PTU are a subset of the root filesystem, which only includes all the accessed files.
+The original relationship, such as symbolic links, between files and directories is maintained.
+The files from pseudo filesystems such as proc and dev, are ignored.
+The re-execution procedure uses these pseudo filesystems from the host machine through redirection techniques.
+The sizes of the packages created by Parrot and PTU are nearly the same. 
+Except for the accessed files, both Parrot and PTU preserve the execution environment of the application. 
+the PTU package also includes a leveldb-format provenance information of the application with the size of 3 MB.
 
@@
 	\centering
-	    \begin{tabular}{llrrr}
+	    \begin{tabular}{lcrr}
 	        \hline
-	        \bf Name & \bf Location & \bf Total & \bf Named & \bf Used \\ 
+	        \bf Dependency Name & \bf Location & \bf Total Size &  \bf Used Size\\ 
 	        \hline
-	        CMSSW code     & CVS & 88.1GB & 448.3MB & 6.3MB\\ \hline
-	        Tau source       & Git & 73.7MB & 73.7MB & 6.7MB \\ \hline
-	        PyYAML binaries    & HTTP & 52MB & 52MB & 0KB \\ \hline
-	        .h file       & HTTP& 41KB & 41KB & 0KB \\ \hline \hline
-	        Ntuples data    & HDFS& 11.6TB & N/A& 20GB \\ \hline
-	        Configuration & CVMFS & 7.4GB & N/A & 103MB \\ \hline
-	        Linux commands & localFS & 110GB &  N/A & 68.4MB \\ \hline     
-	        HOME dir& AFS &12GB & N/A & 32MB\\ \hline
-	        Misc commands & PanFS & 155TB & N/A  & 1.6MB \\ \hline
-	        Total      &    & 166.8TB            & N/A & 21GB \\ \hline
+	        CMSSW code     & CVS & 88.1GB &  5.2MB\\ \hline
+	        Tau source       & Git & 73.7MB & 212KB \\ \hline
+	        PyYAML binaries    & HTTP & 52MB& 0KB \\ \hline
+	        .h file       & HTTP& 41KB & 0KB \\ \hline \hline
+	        Ntuples data    & HDFS& 11.6TB & 18GB \\ \hline
+	        Configuration & CVMFS & 7.4GB & 105MB \\ \hline
+	        Linux commands & localFS & 110GB & 110MB \\ \hline     
+	        HOME dir& AFS &12GB & 24MB\\ \hline
+	        Misc commands & PanFS & 155TB & 8KB \\ \hline
+	        Total      &    & 166.8TB     &  18GB \\ \hline
 	    \end{tabular}
@@
 
-To further verify the correctness of Reduced Package on other machines, two different machines are employed -
-one virtual
-machine~\cite{goldberg1974survey} from the Notre Dame Cloud Platform based on KVM sharing the same kernel version with the original machine,
-and one virtual machine from  the Amazon EC2~\cite{amazon2010amazon} Platform based on Xen.
-
-Table~\ref{table:config-vm} illustrates the configuration of 
-each machine and the execution time of the application on each machine.
-All the machines adopt the x86\_64 hardware platform and Linux kernel.
-Both of the two VMs repeated the application with the help of the package generated on the original machine successfully.
-The execution time on one machine greatly depends on its hardware configuration.
-
-\begin{table}
-    \centering
-    \begin{tabular}{lrrrr}
-    \hline
-    \bf Machine Type & \bf Distro Version & \bf CPU Cores & \bf Mem (GB) & \bf Execution Time \\ \hline 
-    Original Machine &  Red Hat 5.10 & 64 & 125 & 13min 04s\\  \hline
-    KVM (Notre Dame) & CentOS 5.10 & 4 & 2 & 21min 38s\\ \hline
-    Xen (EC2) & Red Hat 5.9 & 16 & 60.5 & 13min 30s\\ \hline
-    \end{tabular}
-    \caption{Evaluation of Different Machines}
-    \label{table:config-vm}
-\end{table}
-
-In summary, we demonstrate that the application can be repeated with the help of the reduced package on one different machine with the required hardware architecture and OS kernel version.
-%*****hmeng-doubt:Another reason for the packaging utility is that not all the data and software generated by the second version script is used during the the actual data analysis.
-The packaging utility can help us find out the optimal subset of data and software involved in one actual data analysis.
-%*****hmeng-doubt: this point is not the motivation. but one achievement comes together. out of imagination.
+Table~\ref{table:size-original-real} illustrates the total size and actually used size of each remote source (the first 4 items) and local source (the remaining 5 items).
+The total size is too large to be put into a separate image. However, the actually used size is greatly reduced to be 18 GB.
+Within the package, the input dataset nearly occupies the whole package. All the other libraries and software dependencies only occupies about 200 MB.
+As the input dataset grows, it can be put outside the package to reduce the shipping time of the package.

### 2015-01-14 paper.tex
Major cleanup
Add Evaluation Section

@@
 
+\usepackage{comment}
+\excludecomment{TM}
+
 \title{An Invariant Framework for Conducting Reproducible Computational Science}
@@
 \author{
-	Haiyan Meng\inst{1}
+	Haiyan Meng\inst{2}
+\and Rupa Kommineni\inst{1}
+\and Quan Pham\inst{1} \\
+\and Robert Gardner\inst{1}
+\and Tanu Malik\inst{1}
 \and
@@
 \institute{
-	Department of Computer Science and Engineering,
-	University of Notre Dame,
-	Notre Dame, Indiana, USA
-	\email{hmeng@nd.edu}
+	Computation Institute,
+	University of Chicago,
+	Chicago, Illinois, USA \\
+	\email{rupa, quan, rob, tanum@uchicago.edu}
 \and
@@
 	University of Notre Dame,
-	Notre Dame, Indiana, USA
-	\email{dthain@nd.edu}
+	Notre Dame, Indiana, USA \\
+	\email{hmeng, dthain@nd.edu}
 }
@@
 
-\authorrunning{Meng, and Thain}
+\authorrunning{Meng et al.}
 

### 2015-01-14 intro.tex
Docker changes

@@
 One approach is to conduct the entire computation relating to a scientific result within a virtual machine image, and then share the resulting image.
-This way VMIs become an authoritative, encapsulated and executable records of computations, especially computations whose results are destined for publication and/or re-use, and the VMIs can be shared easily \cite{}.
+This way VMIs become an authoritative, encapsulated, and executable records of computations, especially computations whose results are destined for publication and/or re-use, and the VMIs can be shared easily \cite{}.
 With this approach, oftentimes, the resulting image is too big in size for share-ability purposes.
 An alternative light-weight form of virtualization allows encapsulation of the application software, along with all its necessary dependencies into a self-contained package, but does not make it executable.
-It thus separates, and does not include the underlying operating system on which the package is executed.
-The encapsulation of the self-contained package is achieved by interposing application system calls, and only copying the necessary dependencies (data, libraries, code) into the package, which also makes it light-weight than a VMI.
+It, thus, separates and does not include the underlying operating system on which the package is executed.
+The encapsulation of the self-contained package is achieved by interposing application system calls, and only copying the necessary dependencies (data, libraries, code, etc) into the package, which also makes it lighter weight than a VMI.
 While both forms of virtualization provide mechanisms for sandboxing the computations associated with a scientific result, neither form of virtualization provides any guarantee that the included pieces of software will indeed reproduce the associated scientific result.
@@
 There are two approaches to address the preservation challenge.
-By either introducing tools that help document dependencies and provide software attribution within VMIs or packages, or alternatively by using software delivery mechanisms, such as, centralized package management, linux containers and Docker framework.
+By either introducing tools that help document dependencies and provide software attribution within VMIs or packages, or alternatively by using software delivery mechanisms, such as, centralized package management, linux containers, and the, more recent, Docker framework.
 We examined the first approach previously in \cite{}.
 In this paper we examine the the second approach, that is, examine how the documentation and preservation standards that are part of software delivery mechanisms can be combined with traditional virtualization approaches for reproducibility.
-In particular we consider the light-weight virtualization approaches, because, we believe that the combination of light-weight approaches with more standardized software delivery mechanisms can lead to addressing the reproducibility challenge for a wide variety of scientific researchers.
+In particular, we consider the light-weight virtualization approaches, because, we believe that the combination of light-weight approaches with more standardized software delivery mechanisms can lead to addressing the reproducibility challenge for a wide variety of scientific researchers.
 % they may help the This  We that must also include effective  to deliver the software to a wide audience. We examine the fire
@@
 
-To conduct a thorough examination, we consider a real-world complex high energy physics application, independently developed by a group, but must be reproduced  so that the entire high energy physics community can benefit from the analysis obtained from the application.
-The collaborative nature of in which high energy physics science is conducted is a
-We describe challenges in reproducing this application, and consider the extent to which reproducibility can be satisfied, independently with light-weight virtualization approaches and software delivery mechanisms.
-We then propose an invariant framework for computational reproducibility that combines light-weight virtualization with software delivery mechanisms.
-The framework uses light-weight virtualization for capturing a computational environment, but preserves the environment using a software delivery approach, so it can be re-executed later.
-By using standardized delivery mechanisms and expanding the application for future uses, the framework makes it invariant to temporal software changes that may occur in near future.
-We measure the performance overhead of combining light-weight virtualization with software delivery approaches.
-The combination imposes additional overhead due to double virtualization, but saves on context switches, since every system call is not interposed.
+To conduct a thorough examination, we consider real-world complex high energy physics (HEP) applications, independently developed by two HEP groups, that must be reproduced so that the entire high energy physics community can benefit from the analysis obtained from the application.
+We describe challenges in reproducing the applications, and consider the extent to which reproducibility requirements can be satisfied with light-weight virtualization approaches and software delivery mechanisms.
+We propose an invariant framework for computational reproducibility that combines light-weight virtualization with software delivery mechanisms for efficiently capturing, invariantly preserving and practically deploying applications.
+In effect, the framework uses light-weight virtualization techniques for efficiently capturing a computational environment, but preserves the environment such that it is invariant to temporal software changes that may occur in near future and can be re-executed later.
+We measure the performance overhead of  light-weight virtualization and software delivery approaches.
+% For later. 
+%The combination imposes additional overhead due to double virtualization, but saves on context switches, since every system call is not interposed.
 

### 2015-01-14 measure.tex
Add preservation_framework figure
Docker changes

@@
 \vspace{5pt}
-\noindent{\bf CDE} CDE creates a package of an application by recording program binaries, libraries, scripts, data files, and environment variables, etc.
-It also uses the UNIX ptrace system call interposition to identify the code and data used by the running application.
-The original CDE as available through [13,12] was limited to major Linux kernel versions (e.g.
-2.6.x), but we have removed that restriction by adapting it for the newly released Linux kernel 3.0 as well as for Mac OS X \cite{}.
-Thus CDE, unlike Parrot, provides OS invariance and does not require installation and configuration.
+\noindent{\bf PTU} PTU creates a package of an application by recording program binaries, libraries, scripts, data files, and environment variables, etc.
+It also uses the UNIX \emph{ptrace} system call interposition to identify the code and data used by the running application.
+PTU was forked from CDE \cite{}, and was thus limited to major Linux kernel versions (e.g.
+2.6.x); consequently we have removed that restriction by adapting it for the newly released Linux kernel 3.0 as well as for Mac OS X \cite{}.
+Thus PTU provides OS invariance and does not require installation and configuration.
 
@@
 \vspace{5pt}
-\noindent{\bf CDE:} In CDE, the complete package is preserved, consisting of all code and data files, however deep the data path is present. 
-However, a CDE binary only captures a single execution path, which is the execution path taken during run-time.
+\noindent{\bf PTU:} Owing to CDE, in PTU, the complete package is preserved, consisting of all code and data files, however deep the data paths are. 
+In CDE a binary only captures a single execution path, which is the execution path taken during run-time.
 If different execution paths need different types of dependencies, some dependencies may be left out.
-To preserve these dependencies, we have added addition functionality to CDE.
-In particular, information about other static binaries and required static shared libraries, such as version number, released version of shared libraries, and associated kernel distribution, is preserved using UNIX commands file, ldd, strings, and objdump.
-We also have added a provenance wrapper over CDE.
+To preserve these dependencies, we have added addition functionality in PTU.
+In particular, information about other static binaries and required static shared libraries, such as version number, released version of shared libraries, and associated kernel distribution, is preserved using UNIX commands file, ldd, strings, and objdump \cite{}.
+We also have added a provenance wrapper over CDE \cite{}.
 This provenance wrapper documents all the dependencies, and provides information about process execution times and memory consumption.
 It creates a graph of the reference execution providing details about how data was created and transformed as part of the execution.
-Thus instead of a PLU, a description of the PLU exists in the package.
+The proevenance description is analgalous to the logically preserved unit.
 
 Neither the Parrot packages or extended CDE package provide a literate programming environment or a continuous integration environment for changes in software.
-Thus they are partially preserved but not completely.
+Thus they are preserved but make break over time as technology changes.
 
  % Docker images
+\vspace{5pt}
+\noindent{\bf Linux Containers and Docker Images}
+
+Linux Containers provide multiple isolated execution instances on top of the same kernel through OS-level virtualization.
+Thus they can be used to persist the captured packages into images.
+Using such containers, Docker now allows to preserve the image in a more user-friendly way.
+In particular, apart from performing Linux container (LXC) based operating system (OS) level virtualization, docker tools provides portable deployment of containers across platforms, documentation of packages in a scriptable format, and versioning of container images.
+The image can be preserved along with dockerfiles, which are plain text files with a literate programming environment: the computational part is similar to shell scripts and can help provision similar to other provisioning tools (e.g.
+Chef, Puppet) or Continuous Integration (CI) platforms (e.g.
+Travis CI), and the text part is for human consumption and more suited for use with a version management system such as subversion or git, which can track any changes made to the Dockerfile.
+Thus dockerfiles can be used to preserve the namelist of Parrot packages and provenance description in PTU.
+Docker is integrated with a continuous build environment which will check and validate the version of the software being used, and use a more recent version to build application software.
 
 \subsection{Deployment  Repositories}
-image can be stored and distributed in a repository like Docker Hub. 
-The Hub also provides a convenient dis- tribution service, freely storing the pre-built images, along with their metadata, for download and reuse by others. 
-   The Docker Hub is a free service and an open source software product so that users can run their own private versions of the Hub on their own servers, for instance, if security of the data or the longevity of the public platform is a concern.
+Deployment repositories, such as Docker Hub, are distribution service for storing the pre-built images, along with their metadata, for download and reuse by others.
+While the architecture of such hubs is beyond the scope of the current paper, the existence of such a repository for reproducible research is vital to ensure security and longevity of preserved packages.
 

### 2015-01-14 paper.tex
Modify Acknowledgement Section; Remove Postscript Section
Docker changes

@@
 	Chicago, Illinois, USA \\
-	\email{rupa, quan, rob, tanum@uchicago.edu}
+	\email{rupa, quanpt, rwg, tanum@uchicago.edu}
 \and
@@
 
-\authorrunning{Meng et al.}
+\authorrunning{Meng, and Thain}
 
@@
 to a larger scientific community---aspects that are equally crucial for ensuring reproducibility as sandboxing itself.
-In this paper, we describe a combined sandboxing and preservation framework, which is efficient and practical and
-useful for large-scale reproducibility. We present a case study of a complex high energy
-physics application and show how the framework can be useful for sandboxing and preserving.
+In this paper, we describe a combined sandboxing and preservation framework, which is efficient, invariant and
+practical for large-scale reproducibility. We present case studies of complex high energy
+physics applications and show how the framework can be useful for sandboxing, preserving and distributing applicatios.
 We report on the completeness, performance,

### 2015-01-14 paper.tex
Acks

@@
 \input {evolution}
-\input {measure}
+%\input {measure}
 \input {evaluation}
@@
 \input {related_work}
-\input {postscript}
+%\input {postscript}
 
@@
 This work was supported in part by National Science Foundation grants PHY-1247316 (DASPOS), 
-OCI-1148330 (SI2) and PHY-1312842.
+OCI-1148330 (SI2), PHY-1312842, ICER-1440327, SES-0951576 (RDCEP), and ICER-1343816 (UChicago subcontract).
 The University of Notre Dame Center for Research Computing scientists and engineers provided critical technical assistance throughout this research effort.
-
-Copyright (C) 2014 The University of Notre Dame
-
-This work is licensed under the Creative Commons Attribution 4.0 License.
+The Open Science Grid at the University of Chicago provided critical technical assistance throughout this research effort.
 

### 2015-01-14 measure.tex
Changes to RW

@@
 \vspace{5pt}
-\noindent{\bf Linux Containers and Docker Images}
-
-Linux Containers provide multiple isolated execution instances on top of the same kernel through OS-level virtualization.
+\noindent{\bf Linux Containers and Docker Images:} Linux Containers provide multiple isolated execution instances on top of the same kernel through OS-level virtualization.
 Thus they can be used to persist the captured packages into images.
@@
 
-\section{Measuring Dependencies}
-
 \begin{figure*}
 \centering
-\includegraphics[width=.8\textwidth]{workflow-parrot.eps}
-\caption{Workflow of The Fine-Grained Dependency Management Toolkit Based on Parrot}
-\label{fig:workflow-parrot}
+\includegraphics[width=.8\textwidth]{preservation_framework.eps}
+\caption{Preservation Framework}
+\label{fig: preservation_framework}
 \end{figure*}
 
+%\section{Measuring Dependencies}
 %We have developed a prototype tool to assist in the measurement and preservation

### 2015-01-14 paper.tex
Changes to RW

@@
 practical for large-scale reproducibility. We present case studies of complex high energy
-physics applications and show how the framework can be useful for sandboxing, preserving and distributing applicatios.
+physics applications and show how the framework can be useful for sandboxing, preserving and distributing applications.
 We report on the completeness, performance,
@@
 \input {evolution}
-%\input {measure}
+\input {measure}
 \input {evaluation}

### 2015-01-15 measure.tex
Worked on implementation section.

@@
 
-We describe some tools that can be used as part of the reproducible framework, and ensure invariance:
+We have constructed a first approximation of the invariant framework
+by using and modifying a variety of existing technologies.  Of course,
+a viable long-term strategy for reproducibility must not depend on a single
+technology, but on multiple technologies that interchange compatible artifacts.
+To this end, we have identified several technologies and techniques
+that can implement each stage of the framework.
 
-\subsection{Capture tools} For capture we focus on automated tools for capturing dependencies (both software and data) instead of manual tools such as makefiles and configuration scripts, since the latter cannot ensure invariance.
-%Parrot
+{\bf Capturing Dependencies.}  The Unix {\tt ptrace} mechanism
+allows a tracing process to observe all of the system calls performed by
+an application, inferring each of the resources upon which an application
+depends.  We have extended two existing tracing tools in order to capture
+dependency information.
 
-\vspace{5pt}
-\noindent {\bf Parrot} Parrot is a virtual filesystem access tool which has been used to attach
-existing programs to a variety of remote I/O systems, such as HTTP, FTP, and CVMFS.
-It works by trapping an application's system calls through the Linux {\tt ptrace} debugging
-interface, and then replacing them with the desired I/O operations. 
-To capture dependencies, Parrot records a \emph{namelist} which lists all 
-of the files that an application actually accesses. Using the namelist, Parrot creates a \emph{reduced package} which contains
-only the files actually used by the application.
+Parrot~\cite{parrot-scpe} is a virtual filesystem access tool which
+is used to attach applications to a variety of remote I/O systems such as HTTP, FTP, and CVMFS. It works by trapping system calls through the {\tt ptrace} interface,
+replacing selected operations with remote accesses.  As a side-effect, Parrot is
+also able to modify the filesystem namespace in arbitrary ways according to user
+needs.  Parrot is particularly used in the high energy physics community
+to provide remote access to application software.
+To capture dependencies, we made small modifications to Parrot to record
+the logical name of every file accessed by an application into an external
+dependency list.  After execution is complete, a second tool is used to copy
+all of the named dependencies into a package.
 
-Being tightly integrated with I/O systems, the Parrot virtual filesystem is required to be installed for both audit and execution to allow for reproducibility.
-In the high energy physics community, Parrot is already used to 
-provide access to the CMSSW software distribution via the CVMFS distributed file system.
-and is thus invariant for applications like TauRoast. However, unless installed, Parrot cannot ensure invariance for general applications.
+PTU~\cite{ptu} is designed to create a package of an application by recording all of the binaries, libraries, scripts, data files, and environment variables used by a program.
+PTU uses the the CDE~\cite{cde} technology to observe system calls, but takes a snapshot of every file at the point of access.
+In addition to files, PTU records \emph{metadata} about the execution environment, such as kernel versions, application versions, and dynamic library versions by using standard Unix commands.
+PTU also records \emph{provenance} in the form of a graph that describes how each file is created or consumed by processes within the application.
+Because PTU is focused solely on the problem of preservation, it can achieve lower overhead than Parrot when remote data access is not a requirement, as we show below.
 
-% PTU
-\vspace{5pt}
-\noindent{\bf PTU} PTU creates a package of an application by recording program binaries, libraries, scripts, data files, and environment variables, etc.
-It also uses the UNIX \emph{ptrace} system call interposition to identify the code and data used by the running application.
-PTU was forked from CDE \cite{}, and was thus limited to major Linux kernel versions (e.g.
-2.6.x); consequently we have removed that restriction by adapting it for the newly released Linux kernel 3.0 as well as for Mac OS X \cite{}.
-Thus PTU provides OS invariance and does not require installation and configuration.
+{\bf Preservation of Dependencies.}  Both Parrot and PTU can observe the precise
+set of files accessed by an application.  If this precise list of files is preserved
+then it should be possible to execute
+\emph{exactly} the same application on \emph{exactly} the same inputs a second
+time.  However, if the objective is to \emph{re-purpose} the application by running it in slightly different configurations, then the preserved package may need to
+be more comprehensive than the strict dependency list.
 
-\subsection{Preservation tools}
+There are many possible heuristics for creating the preserved package
+from the dependency list.  We have implemented three:
+In a {\bf shallow copy}, we simply copy only
+the exact dependencies.
+Where a directory was listed, a directory is created and populated with empty files as placeholders to facilitate a directory listing.
+In a {\bf medium copy},every file in every directory mentioned by the application is preserved one level deep.
+In a {\bf deep copy}, every file in every directory mentioned by the application is copied recursively.
+Obviously, the more aggressive the preservation, the larger the package, but the greater possibility that it can be adapted to other uses.
+Other approaches to package generation might including generating the union
+of multiple dependency sets, or allowing the expert user to manually add
+and remove dependencies.
 
-% Parrot package
-\vspace{5pt}
-\noindent{\bf Parrot:} In Parrot, the package is preserved based on user option.  
-In a {\bf shallow copy}, only individual files in the namelist are copied,
-creating only parent directories for each.  Where a directory was listed,
-a directory is created and populated with empty files as placeholders
-to facilitate a directory listing.  In a {\bf medium copy}, 
-individual files are copied as before and directory contents, one level deep are copied. A {\bf deep copy}, which can duplicate all directories recursively,
-resulting in TB-sized packages, is not allowed.
+Both Parrot and PTU generate packages that consist of plain filesystem trees representing the namespace and data of the preserved application, and can be easily transformed into whatever archive format (e.g.
+ZIP or TGZ) is most suitable.
+This is desirable for long-term preservation that may outlive various deployment technologies.
+However, neither technology yet integrates the literate programming environment
+or the continuous integration environment envisioned above.  Without these techniques, the preserved packages will have diminishing value over time.
 
-% PTU package
-\vspace{5pt}
-\noindent{\bf PTU:} Owing to CDE, in PTU, the complete package is preserved, consisting of all code and data files, however deep the data paths are. 
-In CDE a binary only captures a single execution path, which is the execution path taken during run-time.
-If different execution paths need different types of dependencies, some dependencies may be left out.
-To preserve these dependencies, we have added addition functionality in PTU.
-In particular, information about other static binaries and required static shared libraries, such as version number, released version of shared libraries, and associated kernel distribution, is preserved using UNIX commands file, ldd, strings, and objdump \cite{}.
-We also have added a provenance wrapper over CDE \cite{}.
-This provenance wrapper documents all the dependencies, and provides information about process execution times and memory consumption.
-It creates a graph of the reference execution providing details about how data was created and transformed as part of the execution.
-The proevenance description is analgalous to the logically preserved unit.
+{\bf Distribution and Deployment.}
+Once generated, application packages must be collected, curated, and made
+available through publically shared repositories.  There currently exist a
+wide variety of services and efforts to share binary objects in this way,
+and so we assume such a service will be available in the future.
 
-Neither the Parrot packages or extended CDE package provide a literate programming environment or a continuous integration environment for changes in software.
-Thus they are preserved but make break over time as technology changes.
+Of more immediate interest is the ability to deploy a preserved
+package at a desired execution site.  Again, long-term preservation
+requires artifacts that are independent of any particular technolgy,
+so the package must be sufficiently self-describing
+to work with multiple technologies.  The packages produced by both Parrot and PTU
+can today be re-executed through any of the following mechanisms:
+
+(1) Re-running the application through Parrot, which can dynamically construct
+the desired namespace and limit file accesses to within the preserved package.
+(2) Generating a virtual machine image from the package, which can be loaded
+into a local virtual machine monitor, or transferred to a cloud service provider.
+(3) Converting the package into a Docker image format, enabling it to be
+deployed within a lightweight Linux container.
+
+The latter technology is of considerable interest today
 
@@
 Docker is integrated with a continuous build environment which will check and validate the version of the software being used, and use a more recent version to build application software.
-
-\subsection{Deployment  Repositories}
-Deployment repositories, such as Docker Hub, are distribution service for storing the pre-built images, along with their metadata, for download and reuse by others.
-While the architecture of such hubs is beyond the scope of the current paper, the existence of such a repository for reproducible research is vital to ensure security and longevity of preserved packages.
 

### 2015-01-15 observation.tex
Add Evaluation Section
Worked on implementation section.

@@
-\section{Challenges and Observations in Reproducing HEP Applications}
+\section{Reproducibility Challenges}
 
@@
 only needs a handful of items from that source.  For example, the data is stored on an
-HDFS filesystem with 11.6TB of data, but only 20GB are actually consumed by the program. 
+HDFS filesystem with 11.6TB of data, but only 18GB are actually consumed by the program. 
 %The reason for this great reduction is at first each BEAN event contains a large amount of information, and the TauAnalysis throws away a lot of the irrelevant event information, keeping only the relevant bits.

### 2015-01-15 evaluation.tex
Split the time, add citiations

@@
     \hline
-    \bf Tool Type & \bf Package Creation Time & \bf Re-Execution Time & \bf Package Size \\ \hline
-	Parrot & 27 min 15 sec & 10 min 24 sec & 17.57 GB \\ \hline
-	PTU & 23 min 30 sec & 8 min 40 sec & 17.57 GB \\ \hline 
+    \bf Tool Type & \bf Obtain Namelist & \bf Create Package & \bf Re-Execution \\ \hline
+	Parrot & 22 min 50 sec  & 4 min 25 sec & 10 min 24 sec \\ \hline
+	PTU & --- & 23 min 30 sec & 8 min 40 sec \\ \hline 
     \end{tabular}
-    \caption{Performance Comparison between Parrot and PTU}
+    \caption{Time Comparison between Parrot and PTU}
     \label{table:parrot_ptu}
@@
 
-Table~\ref{table:parrot_ptu} compares the performance of preserving the Tauroast application using Parrot and PTU.
-PTU accommplishes the execution procedure and packaging procedure concurrently through multi-threading, bringing 17.5\% additional time overhead.
+Table~\ref{table:parrot_ptu} compares the time overhead of preserving the Tauroast application using Parrot and PTU.
 Parrot splits the packaging creation procedure into two sequential steps: first, execute the application within Parrot and generate the accessed file namelist (takes 22 min 50 sec); second, traverse the namelist and copy all the accessed files into a self-contained package (takes 4 min 25 sec).
+PTU accommplishes the execution procedure and the package creation procedure concurrently through multi-threading, bringing 17.5\% additional time overhead.
 

### 2015-01-15 measure.tex
Split the time, add citiations

@@
 
-Parrot~\cite{parrot-scpe} is a virtual filesystem access tool which
+Parrot~\cite{thain2005parrot} is a virtual filesystem access tool which
 is used to attach applications to a variety of remote I/O systems such as HTTP, FTP, and CVMFS. It works by trapping system calls through the {\tt ptrace} interface,
@@
 
-PTU~\cite{ptu} is designed to create a package of an application by recording all of the binaries, libraries, scripts, data files, and environment variables used by a program.
-PTU uses the the CDE~\cite{cde} technology to observe system calls, but takes a snapshot of every file at the point of access.
+PTU~\cite{pham2014framework} is designed to create a package of an application by recording all of the binaries, libraries, scripts, data files, and environment variables used by a program.
+PTU uses the the CDE~\cite{guo2011cde} technology to observe system calls, but takes a snapshot of every file at the point of access.
 In addition to files, PTU records \emph{metadata} about the execution environment, such as kernel versions, application versions, and dynamic library versions by using standard Unix commands.

### 2015-01-15 observation.tex
Challenges

@@
-\section{Reproducibility Challenges}
+\section{Challenges and Observations in Reproducing HEP Applications}
 
@@
 
-\item {\bf Explicit External Dependencies.}  Due to the distributed nature of HEP applications, the applications typically depend on a large number of networked external resources. 
-Capturing these dependencies is straightforward if they are static in nature and the resources can be accessed without secure cryptographic functions. 
-For instance, in TauRaoast some source code external dependencies can be obtained by simply downloading the specific libraries from a web page. 
-However, other static dependencies require making secure connections to Github resources, and CVS servers for downloading source. 
-While TauRoast is completely local in its execution, dynamic remote dependencies that arise in a distributed execution require auditing dependencies on all machines where execution takes place.
+\item {\bf Identifying all dependencies.}  Due to the distributed nature of HEP applications, the applications typically depend on a large number of external and local dependencies.
+External dependencies are often explicitly stated, such as when the application makes connections to Github resources, and CVS servers for downloading source. 
+However, when the application has distributed execution then implicit network connections are present requiring us to identify dependencies on all machines where execution takes place. 
+Implicit local dependencies arise due to mounted filesystems. In TauRoast, the application data and code is distributed on five networked filesystems, and in Athena on two networked filesystems. 
+Since these filesystems appear local to the application machine, it is important to check and capture mounted filesystems and their respective mount points.
+
+%networked external resources. 
+%Capturing these dependencies is straightforward if they are static in nature and the resources can be accessed without secure cryptographic functions. 
+%For instance, in TauRaoast some source code external dependencies can be obtained by simply downloading the specific libraries from a web page. 
+%However, other static dependencies require making secure connections to Github resources, and CVS servers for downloading source. 
+%While TauRoast is completely local in its execution, dynamic remote dependencies that arise in a distributed execution 
+%
+%The application data and code is distributed on five networked filesystems, which are 
+%typically mounted on a particular machine that is made accessible to the application developer.
+In TauRoast the a large amount of data to be analyzed was stored on an HDFS~\cite{borthakur2008hdfs} cluster,
+%some configuration data was stored on a CVMFS~\cite{blomer2011cernvm} filesystem,
+%and a variety of software tools were on an NFS~\cite{howard1988scale},
+%PanFS~\cite{welch2008scalable} and AFS~\cite{sandberg1985design} systems. In \emph{Athena} the data and code were available through CVMFS filesystem.
 
@@
 %\end{TM}
-
-\item {\bf Implicit Local Dependencies.} The application data and code is distributed on five networked filesystems, which are 
-typically mounted on a particular machine that is made accessible to the application developer.
-In TauRoast the a large amount of data to be analyzed was stored on an HDFS~\cite{borthakur2008hdfs} cluster,
-some configuration data was stored on a CVMFS~\cite{blomer2011cernvm} filesystem,
-and a variety of software tools were on an NFS~\cite{howard1988scale},
-PanFS~\cite{welch2008scalable} and AFS~\cite{sandberg1985design} systems. In \emph{Athena} the data and code were available through CVMFS filesystem. 
-Since these filesystems appear local to the application machine, it is important to check and capture mounted filesystems and their respective mount points.
 
@@
 checks on a new machine.
+
+%If we allow users to work in uncontrolled
+%environments, then we must have better methods for understanding the dependencies  of existing programs.  At first, we relied on an expert reader to examine
+%the user's script and extract the dependencies.  This is clearly
+%not a scalable approach.  We then demonstrated an automated method of observing
+%what individual files are accessed by a program. However, this does
+%not cover all types of dependencies, particularly those that are networked.
+%More sophisticated observation techniques could infer higher-level information,
+%such as the RPM package names of the files accessed, the URLs of remote
+%repositories named throughout the program, or even the addresses and names of networked dependencies like databases and filesystems.
 
@@
 
-\item {\bf Dependencies for Reproducible Execution.} Capturing the necessary and sufficient dependencies that are part of an application is sufficient for repeatability, but possibly for not reproducibility, where is different additional modules
-must also be preserved so that the resulting application can be extended properly.
+\item {\bf Dependencies for Reproducible Execution.} Capturing the necessary and sufficient dependencies that are part of an application is sufficient for repeatability, but possibly for not reproducibility,
+Repeatability implies if a result depends on running program X, we must be able to run exactly X again. In reproducibility the goal is rarely limited to running
+\emph{precisely} what a predecessor did. Often, the objective is to
+change a parameter or a data input in order to see how the result is affected. To that end, the preservation system must capture enough of the surrounding
+material to permit modifications to succeed.
 In Athena framework, for instance, the software library needed to include basic software programs such as make, awk, sed that can aid further development.
+Further, a better understanding of how end users will consume preserved software will help to shape how
+software is preserved in the first place.
 \end{itemize}

### 2015-01-15 tauroast.tex
Shrink Section 2

@@
 
-Within the ongoing investigation of the Higgs boson at the CMS
-detector, part of the LHC at CERN~\cite{collaboration2008cms}, the Higgs production in association
-with two top quarks allows measuring the Higgs coupling strength to
-top quarks~\cite{chatrchyan2013search}.  As the Higgs boson is too short-lived to be detected
-itself, it has to be reconstructed from its decay products.
-
-The application which is the study of this paper is called \emph{TauRoast}.
-It searches for cases where the Higgs boson decays to two tau leptons.
+The application which is the study of this paper is an CMS application~\cite{collaboration2008cms} called \emph{TauRoast}.
+It searches for cases where the Higgs boson decays to two tau leptons~\cite{chatrchyan2013search}.
 Since the tau leptons are very short-lived, they are not observed directly, but by the particle decay products 
 that they generate.  So, the analysis must search for detector
-events that show a signature of decay products compatible with both hadronic tau and top decays.  Properties of such events are used to distinguish
-the events of interest (Higgs decays) from all other events and
-are also used in further statistical analysis.
+events that show a signature of decay products compatible with both hadronic tau and top decays.
 
@@
 run at all without making use of an enormous collection of software
-dependencies.  Some of these dependencies are standard to operating
-systems worldwide, some are standardized across the entire high-energy
-physics field, some are particular to small collaborative groups,
-and a few are very specific to a single researcher.
-
+dependencies.  
 The largest of these repositories is the CMS Software Distribution (CMSSW)~\cite{cms2006cms},
-a carefully-curated selection of software packages which is distributed
-in several forms.  Historically, components of CMSSW were obtained by checking components
-of the source out of CVS (CMSSW source codes were moved from CVS to git recently), or by installing a complete binary package on a shared
-filesystem within an HPC center.  In recent years, distribution has moved to
-an on-demand delivery system known as CVMFS~\cite{blomer2011cernvm}, which
-provides a filesystem interface that transparently accesses a remote repository.
-The content of CMSSW is managed very carefully by a centralized team whose main goal
-is to ensure that the current version of the software operates correctly
-on the operating systems and architectures currently in use.  However,
-preservation is not a specific objective of the system, and so there is
-no particular guarantee that old versions of CMSSW will continue to
-operate indefinitely.
-
-CMSSW contains many different tools, libraries, and utilities.
+which contains many different tools, libraries, and utilities.
 No single code uses anywhere close to all of these.
@@
 The CMS collaboration provides end-users with a pre-processed
-and reduced data format, AOD~\cite{holtman2001cms}, containing information for events, i.e.,
-proton-proton collisions with a signature of interest, in the form of
-reconstructed particles.  This format is based on the RAW output of
-the CMS detector readout electronics and reconstructed world-wide, which is then processed through various algorithms which derive signatures of individual particles.
-Both real and simulated data are available for examination.
-
+and reduced data format, AOD~\cite{holtman2001cms}, 
+which is based on the RAW output of the CMS detector readout electronics and reconstructed world-wide.
 As AOD data are too large to be iteratively processed repetitively in
@@
 analyzed by the tau analysis.
-It is performed by a small custom code framework, which is built on top of CMSSW.
-The BEAN format, production code, and
-data are shared within the analysis group looking at Higgs production
-in association with top quarks, which is formed by groups from a few
-American and European universities,
-consisting of up to a few dozen contributors.
-
 In the second step, the data are reduced to the ``Ntuple'' format,
@@
 fields relevant to \emph{TauRoast}.
-Again, the Notre Dame CMS groups cluster
-resources are used to perform this reduction and selection,
-running highly customized software,
-built on CMSSW and the BEAN framework,
-with code written and maintained by a small group.
-
 Once the data has been reduced to Ntuples, TauRoast can be run as a single
@@
 of expected signal in real data.
-This package is written using the CMSSW build framework,
-but only utilizes code from ROOT,
-a particle physics toolkit underlying CMSSW,
-and a few external python dependencies for convenience.

### 2015-01-15 evaluation.tex
Size changes
Modify evaluation.tex

@@
 
-We evaluated and compared the correctness and performance of running, packaging, and re-running the Tauroast application using Parrot and PTU.
+We evaluated the correctness and performance of running, packaging, and re-running the Tauroast application using Parrot and PTU.
 To do this, the application was first executed directly, its execution time and output were recorded.
@@
 
-The Tauroast application checks and evaluates a dataset with the size of 18 GB stored in HDFS, and can be finished about 20 minites when running directly on a server with 64 cores and 126 GB memory.
-The output of the application includes the dataset analysis log and a complete statistics information, and its size is 289 KB.
+The Tauroast application checks and evaluates a dataset with the size of 18 GB stored in HDFS, and can be finished in about 20 minites when running directly on a server with 64 cores and 126 GB memory.
+The output of the application includes an event analysis log and a statistics information, and its size is 289 KB.
 
 \begin{table}
+\small
     \centering
@@
     \end{tabular}
+    \normalsize
     \caption{Time Comparison between Parrot and PTU}
@@
 Table~\ref{table:parrot_ptu} compares the time overhead of preserving the Tauroast application using Parrot and PTU.
-Parrot splits the packaging creation procedure into two sequential steps: first, execute the application within Parrot and generate the accessed file namelist (takes 22 min 50 sec); second, traverse the namelist and copy all the accessed files into a self-contained package (takes 4 min 25 sec).
+Parrot splits the packaging creation procedure into two sequential steps: first, execute the application within Parrot and generate the accessed file namelist; second, traverse the namelist and copy all the accessed files into a self-contained package.
 PTU accommplishes the execution procedure and the package creation procedure concurrently through multi-threading, bringing 17.5\% additional time overhead.
@@
 So, the re-execution procedure can get its input from the local filesystem instead of obtaining the input dataset from HDFS.
-PTU re-runs the application faster than Parrot due to its efficient internal implementation.
 
@@
 The re-execution procedure uses these pseudo filesystems from the host machine through redirection techniques.
-The sizes of the packages created by Parrot and PTU are nearly the same. 
+The sizes of the packages created by Parrot and PTU are nearly the same, 18GB. 
 Except for the accessed files, both Parrot and PTU preserve the execution environment of the application. 
@@
 \begin{table}
+\small
 	\centering
@@
 	        PyYAML binaries    & HTTP & 52MB& 0KB \\ \hline
-	        .h file       & HTTP& 41KB & 0KB \\ \hline \hline
+	        .h file       & HTTP& 41KB & 0KB \\ \hline 
 	        Ntuples data    & HDFS& 11.6TB & 18GB \\ \hline
@@
 	    \end{tabular}
-	    \caption{Data and Code Used by Tau Roast}
+	    \normalsize
+	    \caption{Data and Code Size Used by Tauroast}
 	    \label{table:size-original-real}
@@
 
-Table~\ref{table:size-original-real} illustrates the total size and actually used size of each remote source (the first 4 items) and local source (the remaining 5 items).
+Table~\ref{table:size-original-real} illustrates the total size and actually used size of each source.
 The total size is too large to be put into a separate image. However, the actually used size is greatly reduced to be 18 GB.

### 2015-01-15 evaluation.tex
Check spelling

@@
 
-We evaluated the correctness and performance of running, packaging, and re-running the Tauroast application using Parrot and PTU.
+We evaluated the correctness and performance of running, packaging, and re-running the TauRoast application using Parrot and PTU.
 To do this, the application was first executed directly, its execution time and output were recorded.
@@
 
-The Tauroast application checks and evaluates a dataset with the size of 18 GB stored in HDFS, and can be finished in about 20 minites when running directly on a server with 64 cores and 126 GB memory.
+The TauRoast application checks and evaluates a dataset with the size of 18 GB stored in HDFS, and can be finished in about 20 minutes when running directly on a server with 64 cores and 126 GB memory.
 The output of the application includes an event analysis log and a statistics information, and its size is 289 KB.
@@
 
-Table~\ref{table:parrot_ptu} compares the time overhead of preserving the Tauroast application using Parrot and PTU.
+Table~\ref{table:parrot_ptu} compares the time overhead of preserving the TauRoast application using Parrot and PTU.
 Parrot splits the packaging creation procedure into two sequential steps: first, execute the application within Parrot and generate the accessed file namelist; second, traverse the namelist and copy all the accessed files into a self-contained package.
-PTU accommplishes the execution procedure and the package creation procedure concurrently through multi-threading, bringing 17.5\% additional time overhead.
+PTU accomplishes the execution procedure and the package creation procedure concurrently through multi-threading, bringing 17.5\% additional time overhead.
 
@@
 During the original execution, the input dataset comes from HDFS, which is accessed through FUSE.
-During the package creation procedure, all the input dataset has been copied from HDFS into the package on the local fielsytem.
+During the package creation procedure, all the input dataset has been copied from HDFS into the package on the local filesystem.
 So, the re-execution procedure can get its input from the local filesystem instead of obtaining the input dataset from HDFS.
@@
 	    \normalsize
-	    \caption{Data and Code Size Used by Tauroast}
+	    \caption{Data and Code Size Used by TauRoast}
 	    \label{table:size-original-real}

### 2015-01-15 evolution.tex
Check spelling

@@
 
-\item {\bf Capturing Dependencies and Configurations:} Capturing tools must record dependencies that are used by the program, including hardware, OS, kernels, static and dynamic dependencies, local and networked depedencies, source codes and data files.
+\item {\bf Capturing Dependencies and Configurations:} Capturing tools must record dependencies that are used by the program, including hardware, OS, kernels, static and dynamic dependencies, local and networked dependencies, source codes and data files.
 Stateful interactions with commercial software, such as proprietary databases and which cannot be captured due to licensing agreements must be persisted so that they can replayed later without the presence of the commercial software.
@@
 
-\item{\bf Preservation of Captured Entities:} By preservation we imply appropriate mechanisms for (i) documentation of the application development, and (b) automation of any task that becomes inevitably
+\item{\bf Preservation of Captured Entities:} By preservation we imply appropriate mechanisms for (a) documentation of the application development, and (b) automation of any task that becomes inevitably
 necessary for repeating the application in exactly the same way as the developer executed it.

### 2015-01-15 intro.tex
Worked on implementation section.
Check spelling

@@
 We examined the first approach previously in \cite{}.
-In this paper we examine the the second approach, that is, examine how the documentation and preservation standards that are part of software delivery mechanisms can be combined with traditional virtualization approaches for reproducibility.
+In this paper we examine the second approach, that is, examine how the documentation and preservation standards that are part of software delivery mechanisms can be combined with traditional virtualization approaches for reproducibility.
 In particular, we consider the light-weight virtualization approaches, because, we believe that the combination of light-weight approaches with more standardized software delivery mechanisms can lead to addressing the reproducibility challenge for a wide variety of scientific researchers.
@@
 
+\if 0
 The rest of the paper is organized as follows. Section \ref{} describes the high energy physics application and the challenges involved in reproducing it. 
@@
 Section \ref{} provides the experimental results. Finally, we conclude in Section \ref{}. 
+\fi
 

### 2015-01-15 measure.tex
Challenges
Change figure 2 size
Check spelling

@@
 depends.  We have extended two existing tracing tools in order to capture
-dependency information.
+dependency information at the granularity of files and directories. 
+Dependency may refer to source code, if available, or a binary.
 
@@
 PTU~\cite{pham2014framework} is designed to create a package of an application by recording all of the binaries, libraries, scripts, data files, and environment variables used by a program.
-PTU uses the the CDE~\cite{guo2011cde} technology to observe system calls, but takes a snapshot of every file at the point of access.
+PTU uses the CDE~\cite{guo2011cde} technology to observe system calls, but takes a snapshot of every file at the point of access.
 In addition to files, PTU records \emph{metadata} about the execution environment, such as kernel versions, application versions, and dynamic library versions by using standard Unix commands.
@@
 package at a desired execution site.  Again, long-term preservation
-requires artifacts that are independent of any particular technolgy,
+requires artifacts that are independent of any particular technology,
 so the package must be sufficiently self-describing
@@
 \centering
-\includegraphics[width=.8\textwidth]{preservation_framework.eps}
+\includegraphics[width=1.0\textwidth]{preservation_framework.eps}
 \caption{Preservation Framework}

### 2015-01-15 tauroast.tex
Application revision

@@
-\begin{figure}[t]
+\section{High Energy Physics Applications}
+
+We study applications taken from two experiments of the CERN Large Hadron Collider, namely the ATLAS experiment and the CMS experiment. 
+One of the applications of the ATLAS experiment is the \emph{Athena} application, which is a general purpose processing framework including algorithms
+for event reconstruction and data reduction. The CMS experiment is conducted through an application termed  \emph{TauRoast}, which searches for specific 
+cases where the Higgs boson decays to two tau leptons~\cite{chatrchyan2013search}. In LHC, the ATLAS and CMS experiments are distinct, 
+developed independently by two entirely separate physics communities. Consequently, their applications  
+have very different software distribution and data management frameworks, making it interesting to examine if common reproducibility frameworks and 
+tools work across the two communities.
+
+%The application which is the study of this paper is an CMS application~\cite{collaboration2008cms} called \emph{TauRoast}.
+%It searches for cases where the Higgs boson decays to two tau leptons~\cite{chatrchyan2013search}.
+%Since the tau leptons are very short-lived, they are not observed directly, but by the particle decay products 
+%that they generate.  So, the analysis must search for detector
+%events that show a signature of decay products compatible with both hadronic tau and top decays.
+
+Code and data in \emph{TauRoast} is available through five different networked filesystems, namely an HDFS \cite{} cluster for data files, 
+some configuration files were stored on a CVMFS \cite{} filesystem, and a variety of software tools were on an NFS \cite{}, PanFS\cite{} and AFS \cite{} systems.
+In addition, code may exist in version control systems such as Git, CVS, and CMS Software Distribution (CMSSW)~\cite{cms2006cms}. 
+\begin{wrapfigure}{r}{0.4\textwidth}
+\small
 \centering
-\includegraphics[width=.5\textwidth]{data-code-size.eps}
+\includegraphics[width=.48\textwidth]{data-code-size.eps}
 \caption{Inputs to Tau Roast}
 \label{fig:data-code-size}
-\end{figure}
+\end{wrapfigure}
+Data that is input to \emph{TauRoast} is obtained by reducing it through a pipeline, as shown in Figure \ref{fg:data-code-size}. Consequently, the real input data may 
+vary depending upon the science question being researched. Similarly the software may name many possible components but the used components are
+smaller than the named ones.
 
-\section{Overview of Tau Roast}
+In \emph{Athena} data is obtained through an external Dropbox-like system called the FaxBox, but does not go through any reduction steps. Code is obtained through 
+CernVM-FS, which provides the analysis routines. However, depending upon the input data code and the configuration that will be invoked changes. 
+Thus in \emph{Athena} the used code and configuration are dynamic depending upon input data, where as in \emph{TauRoast} the code and data are static, 
+but the amount of data and code to include changes depending on the involved science.
 
-The application which is the study of this paper is an CMS application~\cite{collaboration2008cms} called \emph{TauRoast}.
-It searches for cases where the Higgs boson decays to two tau leptons~\cite{chatrchyan2013search}.
-Since the tau leptons are very short-lived, they are not observed directly, but by the particle decay products 
-that they generate.  So, the analysis must search for detector
-events that show a signature of decay products compatible with both hadronic tau and top decays.
-
-Figure~\ref{fig:data-code-size} shows that both the code and data
-that form \emph{TauRoast} are drawn from large repositories through
-multiple steps of reduction.  A preservation strategy must weigh
-whether to store the large repositories completely, the fragments
-used by an artifact, or something in between.
-
-{\bf Code Sources.} Like many scientific codes, the central algorithm
-of \emph{TauRoast} is expressed in a relatively small amount of
-custom code developed by the primary author.  But, the code cannot
-run at all without making use of an enormous collection of software
-dependencies.  
-The largest of these repositories is the CMS Software Distribution (CMSSW)~\cite{cms2006cms},
-which contains many different tools, libraries, and utilities.
+%In application, code and data that form the applications are drawn from large external repositories through multiple step reductions. 
+%Figure \ref{fg:data-code-size} shows the data and code reduction and reliance on software distribution repositories. There are two observations to be 
+%derived from 
+%of this reduction. First. the actual code contributed by individual groups, in this case the CMS and ATLAS group, is small. 
+%But the contributed software relies on several software dependencies, which
+%are available software distribution repositories such as the CMS Software Distribution (CMSSW)~\cite{cms2006cms}, and the CVMFS. 
+%These repositories contain many different tools, libraries, and utilities, and for ATLAS, the Reco\_TR analysis framework which consists of many analysis routines. 
+%
+%Figure~\ref{fig:data-code-size} shows that both the code and data
+%that form \emph{TauRoast} are drawn from large repositories through
+%multiple steps of reduction.  A preservation strategy must weigh
+%whether to store the large repositories completely, the fragments
+%used by an artifact, or something in between.
+%
+%{\bf Code Sources.} Like many scientific codes, the central algorithm
+%of \emph{TauRoast} is expressed in a relatively small amount of
+%custom code developed by the primary author.  But, the code cannot
+%run at all without making use of an enormous collection of software
+%dependencies.  
+%The largest of these repositories is the CMS Software Distribution (CMSSW)~\cite{cms2006cms},
+%which contains many different tools, libraries, and utilities.
 No single code uses anywhere close to all of these.
 But, because it is widely used within the experimental researchers, it is common for users to simply expect that a particular version of the entire repository is available.
-
-{\bf Data Sources.}
-The CMS collaboration provides end-users with a pre-processed
-and reduced data format, AOD~\cite{holtman2001cms}, 
-which is based on the RAW output of the CMS detector readout electronics and reconstructed world-wide.
-As AOD data are too large to be iteratively processed repetitively in
-a physics analysis workflow, it is normally reduced further in
-structural complexity and content.  For the analysis under
-investigation here, this is a two-step process.  First, the AOD data
-are processed at the Notre Dame working group cluster to BEAN (Boson Exploration Analysis Ntuple) events,
-containing only trivial data containers packed in vectors.  This step
-is time and CPU intensive and its output contains data of 11.6$\,$TB to be
-analyzed by the tau analysis.
-In the second step, the data are reduced to the ``Ntuple'' format,
-which contains only events matching basic quality criteria and
-fields relevant to \emph{TauRoast}.
-Once the data has been reduced to Ntuples, TauRoast can be run as a single
-process, and contains a stringent event selection to look only at high
-quality candidate events for the underlying physical process.
-Quantities from the relevant events can be
-both plotted and used in multivariate analysis to determine the level
-of expected signal in real data.
+% 
+%{\bf Data Sources.}
+%The CMS collaboration provides end-users with a pre-processed
+%and reduced data format, AOD~\cite{holtman2001cms}, 
+%which is based on the RAW output of the CMS detector readout electronics and reconstructed world-wide.
+%As AOD data are too large to be iteratively processed repetitively in
+%a physics analysis workflow, it is normally reduced further in
+%structural complexity and content.  For the analysis under
+%investigation here, this is a two-step process.  First, the AOD data
+%are processed at the Notre Dame working group cluster to BEAN (Boson Exploration Analysis Ntuple) events,
+%containing only trivial data containers packed in vectors.  This step
+%is time and CPU intensive and its output contains data of 11.6$\,$TB to be
+%analyzed by the tau analysis.
+%In the second step, the data are reduced to the ``Ntuple'' format,
+%which contains only events matching basic quality criteria and
+%fields relevant to \emph{TauRoast}.
+%Once the data has been reduced to Ntuples, TauRoast can be run as a single
+%process, and contains a stringent event selection to look only at high
+%quality candidate events for the underlying physical process.
+%Quantities from the relevant events can be
+%both plotted and used in multivariate analysis to determine the level
+%of expected signal in real data.

### 2015-01-15 evaluation.tex
Add citiation into Section 2

@@
 
-We evaluated the correctness and performance of running, packaging, and re-running the TauRoast application using Parrot and PTU.
+We evaluated the correctness and performance of running, packaging, and re-running the \emph{TauRoast} application using Parrot and PTU.
 To do this, the application was first executed directly, its execution time and output were recorded.
@@
 
-The TauRoast application checks and evaluates a dataset with the size of 18 GB stored in HDFS, and can be finished in about 20 minutes when running directly on a server with 64 cores and 126 GB memory.
+The \emph{TauRoast} application checks and evaluates a dataset with the size of 18 GB stored in HDFS, and can be finished in about 20 minutes when running directly on a server with 64 cores and 126 GB memory.
 The output of the application includes an event analysis log and a statistics information, and its size is 289 KB.
@@
 
-Table~\ref{table:parrot_ptu} compares the time overhead of preserving the TauRoast application using Parrot and PTU.
+Table~\ref{table:parrot_ptu} compares the time overhead of preserving the \emph{TauRoast} application using Parrot and PTU.
 Parrot splits the packaging creation procedure into two sequential steps: first, execute the application within Parrot and generate the accessed file namelist; second, traverse the namelist and copy all the accessed files into a self-contained package.
@@
 	    \normalsize
-	    \caption{Data and Code Size Used by TauRoast}
+	    \caption{Data and Code Size Used by \emph{TauRoast}}
 	    \label{table:size-original-real}

### 2015-01-15 tauroast.tex
Add citiation into Section 2

@@
 
-Code and data in \emph{TauRoast} is available through five different networked filesystems, namely an HDFS \cite{} cluster for data files, 
-some configuration files were stored on a CVMFS \cite{} filesystem, and a variety of software tools were on an NFS \cite{}, PanFS\cite{} and AFS \cite{} systems.
+Code and data in \emph{TauRoast} is available through five different networked filesystems, namely an HDFS~\cite{borthakur2008hdfs} cluster for data files, 
+some configuration files were stored on a CVMFS~\cite{blomer2011cernvm} filesystem, and a variety of software tools were on an NFS~\cite{sandberg1985design}, PanFS~\cite{welch2008scalable} and AFS~\cite{howard1988scale} systems.
 In addition, code may exist in version control systems such as Git, CVS, and CMS Software Distribution (CMSSW)~\cite{cms2006cms}. 
@@
 \centering
-\includegraphics[width=.48\textwidth]{data-code-size.eps}
+\includegraphics[width=.4\textwidth]{data-code-size.eps}
 \caption{Inputs to Tau Roast}
@@
 \end{wrapfigure}
-Data that is input to \emph{TauRoast} is obtained by reducing it through a pipeline, as shown in Figure \ref{fg:data-code-size}. Consequently, the real input data may 
+Data that is input to \emph{TauRoast} is obtained by reducing it through a pipeline, as shown in Figure \ref{fig:data-code-size}. Consequently, the real input data may 
 vary depending upon the science question being researched. Similarly the software may name many possible components but the used components are

### 2015-01-15 evaluation.tex
Final

--- 2015-01-15 evaluation.tex
@@
 
-We evaluated the correctness and performance of running, packaging, and re-running the TauRoast application using Parrot and PTU.
+We evaluated the correctness and performance of running, packaging, and re-running the Athena and TauRoast application using Parrot and PTU.
 To do this, the application was first executed directly, its execution time and output were recorded.
@@
 The output of the application includes an event analysis log and a statistics information, and its size is 289 KB.
+The Athena application processes a given input data file to produce four derived data files.
+It uses the nightly release of the Athena framework and
+submits an analysis job to obtain derived data.
 
@@
     \centering
-    \begin{tabular}{lccc}
+    \begin{tabular}{lcccc}
     \hline
-    \bf Tool Type & \bf Obtain Namelist & \bf Create Package & \bf Re-Execution \\ \hline
-	Parrot & 22 min 50 sec  & 4 min 25 sec & 10 min 24 sec \\ \hline
-	PTU & --- & 23 min 30 sec & 8 min 40 sec \\ \hline 
+    \bf Application & \bf Tool Type & \bf Obtain Namelist & \bf Create Package & \bf Re-Execution \\ \hline
+	Athena & Parrot & 10 min 14 sec & 53 sec & 9 min 14 sec \\ \hline
+	Athena & PTU & --- & 8min 48 sec & 7 min 21 sec \\ \hline
+	TauRoast & Parrot & 22 min 50 sec  & 4 min 25 sec & 10 min 24 sec \\ \hline
+	TauRoast & PTU & --- & 23 min 30 sec & 8 min 40 sec \\ \hline 
     \end{tabular}
@@
 
-Table~\ref{table:parrot_ptu} compares the time overhead of preserving the TauRoast application using Parrot and PTU.
+Table~\ref{table:parrot_ptu} compares the time overhead of preserving Athena and TauRoast application using Parrot and PTU.
 Parrot splits the packaging creation procedure into two sequential steps: first, execute the application within Parrot and generate the accessed file namelist; second, traverse the namelist and copy all the accessed files into a self-contained package.
@@
 The re-execution time is half or less than half of the original execution time in both cases.
-During the original execution, the input dataset comes from HDFS, which is accessed through FUSE.
+During the original execution, the input dataset is either locally available or comes from HDFS, which is accessed through FUSE.
 During the package creation procedure, all the input dataset has been copied from HDFS into the package on the local filesystem.
@@
 
-Table~\ref{table:size-original-real} illustrates the total size and actually used size of each source.
+Table~\ref{table:size-original-real} illustrates the total size and actually used size of each source for TauRoast. 
 The total size is too large to be put into a separate image. However, the actually used size is greatly reduced to be 18 GB.
@@
 As the input dataset grows, it can be put outside the package to reduce the shipping time of the package.
+
+In Athena, the input file is 224MB and output files are 16MB. PTU build a 855MB package, while Parrot builds an 825MB package. The overhead is of provenance which is 7MB and 
+some differences is dependency information.

### 2015-01-15 intro.tex
Final

@@
 As computation pervades the sciences and transforms the scientific method, mere text is considered insufficient. 
-In particular, apart from textual descriptions describing the result, a reproducible result must also include several computational artifacts, such as software, data,  environment variables, and state of computation that are involved in the adopted scientific method.
+In particular, apart from textual descriptions describing the result, a reproducible result must also include several computational artifacts, such as software, data,  environment variables, and state of computation that are involved in the adopted scientific method \cite{Sole}.
 By including computational artifacts, the scientific result can be obtained again at a later time.
@@
 One approach is to conduct the entire computation relating to a scientific result within a virtual machine image, and then share the resulting image.
-This way VMIs become an authoritative, encapsulated, and executable records of computations, especially computations whose results are destined for publication and/or re-use, and the VMIs can be shared easily \cite{}.
+This way VMIs become an authoritative, encapsulated, and executable records of computations, especially computations whose results are destined for publication and/or re-use, and the VMIs can be shared easily \cite{Lampoudi}.
 With this approach, oftentimes, the resulting image is too big in size for share-ability purposes.
@@
 By either introducing tools that help document dependencies and provide software attribution within VMIs or packages, or alternatively by using software delivery mechanisms, such as, centralized package management, linux containers, and the, more recent, Docker framework.
-We examined the first approach previously in \cite{}.
+We examined the first approach previously in \cite{SoftProv}.
 In this paper we examine the second approach, that is, examine how the documentation and preservation standards that are part of software delivery mechanisms can be combined with traditional virtualization approaches for reproducibility.

### 2015-01-15 measure.tex
Final

@@
 
-PTU~\cite{pham2014framework} is designed to create a package of an application by recording all of the binaries, libraries, scripts, data files, and environment variables used by a program.
+PTU~\cite{PTU,pham2014framework} is designed to create a package of an application by recording all of the binaries, libraries, scripts, data files, and environment variables used by a program.
 PTU uses the CDE~\cite{guo2011cde} technology to observe system calls, but takes a snapshot of every file at the point of access.

### 2015-01-15 tauroast.tex
Final

@@
 One of the applications of the ATLAS experiment is the \emph{Athena} application, which is a general purpose processing framework including algorithms
-for event reconstruction and data reduction. The CMS experiment is conducted through an application termed  \emph{TauRoast}, which searches for specific 
+for event reconstruction and data reduction \cite{calafiura2005athena}. The CMS experiment is conducted through an application termed  \emph{TauRoast}, which searches for specific 
 cases where the Higgs boson decays to two tau leptons~\cite{chatrchyan2013search}. In LHC, the ATLAS and CMS experiments are distinct, 
@@
 
-Code and data in \emph{TauRoast} is available through five different networked filesystems, namely an HDFS~\cite{borthakur2008hdfs} cluster for data files, 
-some configuration files were stored on a CVMFS~\cite{blomer2011cernvm} filesystem, and a variety of software tools were on an NFS~\cite{sandberg1985design}, PanFS~\cite{welch2008scalable} and AFS~\cite{howard1988scale} systems.
-In addition, code may exist in version control systems such as Git, CVS, and CMS Software Distribution (CMSSW)~\cite{cms2006cms}. 
+Code and data in \emph{TauRoast} is available through five different networked filesystems, namely an HDFS cluster for data files, 
+%~\cite{borthakur2008hdfs},~\cite{sandberg1985design},\cite{welch2008scalable}, ~\cite{howard1988scale}
+some configuration files were stored on a CVMFS~\cite{blomer2011cernvm} filesystem, and a variety of software tools were on an NFS, PanFS and AFS systems.
+In addition, code may exist in version control systems such as Git, CVS, and CMS Software Distribution (CMSSW). %~\cite{cms2006cms}. 
 \begin{wrapfigure}{r}{0.4\textwidth}

### 2015-01-15 evaluation.tex
Minor changes

@@
 
-The re-execution time is half or less than half of the original execution time in both cases.
+The re-execution time is half or less than half of the original execution time in both cases of the \emph{TauRoast} application.
 During the original execution, the input dataset is either locally available or comes from HDFS, which is accessed through FUSE.
@@
 The re-execution procedure uses these pseudo filesystems from the host machine through redirection techniques.
-The sizes of the packages created by Parrot and PTU are nearly the same, 18GB. 
+For the \emph{TauRoast} application, the sizes of the packages created by Parrot and PTU are nearly the same, 18GB. 
 Except for the accessed files, both Parrot and PTU preserve the execution environment of the application. 

### 2015-01-15 observation.tex
Minor changes

@@
 However, when the application has distributed execution then implicit network connections are present requiring us to identify dependencies on all machines where execution takes place. 
-Implicit local dependencies arise due to mounted filesystems. In TauRoast, the application data and code is distributed on five networked filesystems, and in Athena on two networked filesystems. 
+Implicit local dependencies arise due to mounted filesystems.
+In \emph{TauRoast}, the application data and code is distributed on five networked filesystems, and in \emph{Athena} on two networked filesystems.
 Since these filesystems appear local to the application machine, it is important to check and capture mounted filesystems and their respective mount points.
@@
 
-\item {\bf Dependencies for Reproducible Execution.} Capturing the necessary and sufficient dependencies that are part of an application is sufficient for repeatability, but possibly for not reproducibility,
+\item {\bf Dependencies for Reproducible Execution.} Capturing the necessary and sufficient dependencies that are part of an application is sufficient for repeatability, but possibly for not reproducibility.
 Repeatability implies if a result depends on running program X, we must be able to run exactly X again. In reproducibility the goal is rarely limited to running

### 2015-03-16 evolution.tex
Modifications according to the suggestions from reviewers

@@
 
-Given the many challenges of reproducing HEP applications, we now describe a formal framework, which if present within large collaborations, can enable application developers to share their 
-application with other researchers, and for other researchers to reproduce the shared application. In effect, the framework itself should be 
-be invariant to changes in who owns the application (the developer or the reproducer), where it was built and compiled. To satisfy invariance, the framework must include mechanisms for:
+Given the many challenges of reproducing HEP applications, we now describe an invariant framework, which if present within large collaborations, can enable application developers to share their 
+application with other researchers, and for other researchers to reproduce the shared application. 
+To satisfy invariance, the framework must include mechanisms for:
 
@@
 
-Documentation and specification during application development can be a onerous. The preservation framework must make literate programming tools available that 
+Documentation and specification during application development can be an onerous one. The preservation framework must make programming tools available that 
 focus less on documentation, but script, integrate and execute the dependencies so that they are resolved as part of documentation. 
 Automation can extend to various tasks that are necessary for ensuring repeatability such as building software, provisioning of hardware, 
-validation of software against security fixes, new features, or deprecation of old software, and even monitoring the reproducibility state of a preserved application, i.e., its source code, dependencies, environment, and platform.
+validation of software against security fixes, new features, and even monitoring the reproducibility state of a preserved application, i.e., its source code, dependencies, environment, and platform.
 Automated builds and provisioning and continuous integration service can significantly lower the barrier to run the application in a new environment.

### 2015-03-16 intro.tex
Modifications according to the suggestions from reviewers

@@
 In particular, apart from textual descriptions describing the result, a reproducible result must also include several computational artifacts, such as software, data,  environment variables, and state of computation that are involved in the adopted scientific method \cite{Sole}.
-By including computational artifacts, the scientific result can be obtained again at a later time.
 
@@
 An alternative light-weight form of virtualization allows encapsulation of the application software, along with all its necessary dependencies into a self-contained package, but does not make it executable.
-It, thus, separates and does not include the underlying operating system on which the package is executed.
-The encapsulation of the self-contained package is achieved by interposing application system calls, and only copying the necessary dependencies (data, libraries, code, etc) into the package, which also makes it lighter weight than a VMI.
+The encapsulation of the self-contained package is achieved by interposing application system calls, and only copying the necessary dependencies (data, libraries, code, etc.) into the package, which also makes it lighter weight than a VMI.
 While both forms of virtualization provide mechanisms for sandboxing the computations associated with a scientific result, neither form of virtualization provides any guarantee that the included pieces of software will indeed reproduce the associated scientific result.
@@
 There are two approaches to address the preservation challenge.
-By either introducing tools that help document dependencies and provide software attribution within VMIs or packages, or alternatively by using software delivery mechanisms, such as, centralized package management, linux containers, and the, more recent, Docker framework.
+By either introducing tools that help document dependencies and provide software attribution within VMIs or packages, or alternatively by using software delivery mechanisms, such as, centralized package management, Linux containers, and the, more recent, Docker framework.
 We examined the first approach previously in \cite{SoftProv}.
-In this paper we examine the second approach, that is, examine how the documentation and preservation standards that are part of software delivery mechanisms can be combined with traditional virtualization approaches for reproducibility.
+In this paper we examine the second approach. 
 In particular, we consider the light-weight virtualization approaches, because, we believe that the combination of light-weight approaches with more standardized software delivery mechanisms can lead to addressing the reproducibility challenge for a wide variety of scientific researchers.
+A package created by those light-weight approaches encapsulates all the necessary dependencies of an application, and can be used to repeat the application through different sandbox mechanisms, including Parrot, CDE, PTU, chroot, and Docker.
 % they may help the This  We that must also include effective  to deliver the software to a wide audience. We examine the fire
@@
 We propose an invariant framework for computational reproducibility that combines light-weight virtualization with software delivery mechanisms for efficiently capturing, invariantly preserving and practically deploying applications.
-In effect, the framework uses light-weight virtualization techniques for efficiently capturing a computational environment, but preserves the environment such that it is invariant to temporal software changes that may occur in near future and can be re-executed later.
 We measure the performance overhead of  light-weight virtualization and software delivery approaches.
+
+We do not claim our solution is the only way to preserve applications.
+Generally, there are two different approaches to preserve applications: measure the mess and force cleanliness.
+The first approach allows end users to construct the environment as desired, and then measures the dependencies.
+The latter one forces users to specify the execution environment for an application in a well organized way.
+Our objective here is to preserve the mess as-is.
+
 % For later. 

### 2015-03-16 measure.tex
Minor changes
Modifications according to the suggestions from reviewers

@@
 a viable long-term strategy for reproducibility must not depend on a single
-technology, but on multiple technologies that interchange compatible artifacts.
+technology.
 To this end, we have identified several technologies and techniques
@@
 This is desirable for long-term preservation that may outlive various deployment technologies.
-However, neither technology yet integrates the literate programming environment
-or the continuous integration environment envisioned above.  Without these techniques, the preserved packages will have diminishing value over time.
+However, neither technology yet integrates the programming environment envisioned above for the documentation purpose.
+Without these techniques, the preserved packages will have diminishing value over time.
 
@@
 
-The latter technology is of considerable interest today
-
  % Docker images
@@
 Using such containers, Docker now allows to preserve the image in a more user-friendly way. 
-In particular, apart from performing Linux container (LXC) based operating system (OS) level virtualization, docker tools provides portable deployment of containers across platforms, documentation of packages in a scriptable format, and versioning of container images.
-The image can be preserved along with dockerfiles, which are plain text files with a literate programming environment: the computational part is similar to shell scripts and can help provision similar to other provisioning tools (e.g.
-Chef, Puppet) or Continuous Integration (CI) platforms (e.g.
-Travis CI), and the text part is for human consumption and more suited for use with a version management system such as subversion or git, which can track any changes made to the Dockerfile.
+Docker also provides portable deployment of containers across platforms, documentation of packages in a scriptable format, and versioning of container images.
+The image can be preserved along with dockerfiles, which are text files that contain all the commands to build a Docker image: the computational part is similar to shell scripts and can help provision similar to other provisioning tools (e.g.
+Chef, Puppet) and the text part is for human consumption and more suited for use with a version management system such as subversion or git, which can track any changes made to the Dockerfile.
 Thus dockerfiles can be used to preserve the namelist of Parrot packages and provenance description in PTU.

### 2015-03-16 observation.tex
Modifications according to the suggestions from reviewers

@@
 
-\item {\bf Configuration Complexity.} To correctly reproduce an application implies that run-time configurations and consistency checks on the available software are effective captured and preserved. 
+\item {\bf Configuration Complexity.} To correctly reproduce an application implies that run-time configurations and consistency checks on the available software are effectively captured and preserved.
 For CMS,  {\tt scram} software management tool, is used to locate
 the appropriate version of software,  set environment variables such as the PATH, run any
-tool-specific configuration, and do the same for all software on which it depends. A reproducible framework must capture the working of such software management tools so that they can conduct similar
+tool-specific configuration, and do the same for all software on which it depends. A reproducible framework must capture the work of such software management tools so that they can conduct similar
 checks on a new machine.
@@
 material to permit modifications to succeed. 
-In Athena framework, for instance, the software library needed to include basic software programs such as make, awk, sed that can aid further development.
 Further, a better understanding of how end users will consume preserved software will help to shape how
-software is preserved in the first place.
+software should be preserved.
 \end{itemize}

### 2015-03-16 paper.tex
Challenges
Add keywords
Application revision
Final
Modifications according to the suggestions from reviewers

@@
 \usepackage{comment}
+\usepackage{wrapfig}
 \excludecomment{TM}
+%\setlength{\textwidth}{6.25in}
 
@@
 
-\keywords{}
+\keywords{Preservation framework, reproducible research, virtualization, container}
 
@@
 \input {evaluation}
-\input {problems}
+%\input {problems}
 \input {related_work}
 %\input {postscript}
+\section{Conclusions and Future work}
+In this paper, we propose an invariant framework for conducting reproducible computational science - using light-weight virtualization approaches to preserve applications in the format of self-contained packages and using standardized software delivery mechanisms to deliver and distribute preserved packages.
+We use two complex high energy physics applications to illustrate how the framework can help the original authors preserve and distribute the applications, and others reproduce the applications.
+
+This paper focuses on how to measure the mess and track the used dependencies to preserve an application.
+In the following work, we plan to explore how to preserve an application in an organized style - specifying the execution environment clearly.
+How to preserve and improve the availability of remote network resources is another important problem to be explored.
+
+For more details about how to preserve, distribute and repeat an application:
+
+\url{http://ccl.cse.nd.edu/research/data/hep-case-study/case\_study\_redhat6\_5.html}
 
@@
 \bibliographystyle{plain}
-\bibliography{cclpapers,this}
+\bibliography{cclpapers,this,sole}
 

### 2015-03-18 intro.tex
Remove unused stuff

@@
 
-% Reproducibility
 Reproducibility is a cornerstone of the scientific method~\cite{borgman2012data}. 
@@
 A package created by those light-weight approaches encapsulates all the necessary dependencies of an application, and can be used to repeat the application through different sandbox mechanisms, including Parrot, CDE, PTU, chroot, and Docker.
-% they may help the This  We that must also include effective  to deliver the software to a wide audience. We examine the fire
-%have recently emerged  several of the reproducible challenges that arise due to use of virtualization approaches.
 
@@
 Our objective here is to preserve the mess as-is.
-
-% For later. 
-%The combination imposes additional overhead due to double virtualization, but saves on context switches, since every system call is not interposed.
-
-\if 0
-The rest of the paper is organized as follows. Section \ref{} describes the high energy physics application and the challenges involved in reproducing it. 
-Section \ref{} describes the light-weight virtualization and software delivery mechanisms, such as linux containers and dockers. 
-In Section \ref{} we describe the combined invariant framework, consisting of capture and preservation phases. 
-Section \ref{} describes how to employ capture, preserve, and distribute phases to reproduce the high-energy physics application.
-Section \ref{} provides the experimental results. Finally, we conclude in Section \ref{}. 
-\fi
-
-%-----
-%OLD TEXT
-%
-%Reproducibility is a cornerstone of the scientific process~\cite{borgman2012data}.
-%In order to understand, verify, and build upon previous work,
-%one must be able to first recreate previous results by applying
-%the same methods. Historically, reproducibility has been
-%accomplished through painstaking detailed documentation recorded
-%in lab notebooks, which are then summarized in peer-reviewed publications.
-%But as science increasingly depends on computation,
-%reproducibility must also encompass the environments, data, and software
-%involved in each result~\cite{zabolitzky2002preserving}. It is widely recognized that informal
-%descriptions of software and systems -- although common -- are insufficient
-%for reproducing a computational result accurately.
-%A more automated and comprehensive approach is required.
-%
-%The reproduction of a computation has three broad components,
-%each of which suggests somewhat different approaches:
-%
-%\begin{itemize}
-%\item The {\bf computing environment}, consisting of the basic hardware and the operating system which can be preserved as physical artifacts or as a combination of virtual machine monitors (hardware) and virtual machine images (operating system)~\cite{matthews2009towards}.
-%\item The {\bf scientific data} to be analyzed has historically received the most attention for curation.
-In a large, well-organized project, it may be stored in a  data repository or database management system, with associated documentation and a curation strategy.
-In a small effort, it could simply be a handful of files.
-%\item The {\bf software environment} includes the source code, binaries, scripts, configuration files, and everything else needed to execute the desired code.
-As with data, the software could be drawn from a well-managed software repository, or it could be a handful custom scripts that exist in the user's home directory.
-%\end{itemize}
-%
-%In a very abstract sense, reproducing a computation is trivial.
-%Assuming a computation is deterministic, one must simply
-%preserve all of the inputs to a computation, then re-run
-%the same code in an equivalent environment, and the same result
-%will be produced.  For a small custom application on a modest
-%amount of data, this could be accomplished by capturing the
-%complete environment,
-%data, and software within a single virtual machine image,
-%and then depositing the virtual
-%image into a curated environment.  The publication could
-%then simply refer to the identifier of the image, which the
-%interested reader can obtain and re-use. This approach has
-%been used to some success with systems~\cite{castagne2013consider}.
-%\footnote{Of course, we are glossing over the problem that hardware
-%architectures and virtual machines also change, so one must also
-%preserve the VMM software necessary to run the image.  The VMM itself
-%depends on a software environment which must also be preserved.
-%A long-term preservation system might end up running a whole
-%stack of nested virtual machines in order to provide the desired
-%environment! }
-%
-%However, this simple approach is not sufficient for large applications
-%that are run in complex environments.
-%
-%\begin{itemize}
-%\item There may be {\bf implicit dependencies} on items that are
-%not apparent to the end user.  For example, they may understand that
-%they rely on a particular data analysis package, but would have
-%no reason to know that the package has further dependencies on
-%other libraries and configuration files.  Or, they may know that
-%the computation only runs correctly on a particular machine, but
-%not know this is because it relies on a filesystem that
-%is mounted only on that machine.
-%
-%\item The {\bf granularity} of the dependencies may not be well understood.
-%For example, the user may understand that a computation depends upon
-%a data collection that is 1TB in overall size, but not have detailed
-%knowledge that it only requires three files totalling 300MB out of that
-%whole collection.
-%
-%\item There may be dependencies upon {\bf networked resources} that
-%are inherently external to the system, such as a database, a code
-%repository~\cite{cms2006cmssw}, or a scalable filesystem~\cite{blomer2011cernvm}.  For such resources, it
-%must be decided whether the dependency will simply be noted, or if it
-%must be incorporated whole or in part.
-%
-%\item Where {\bf common dependencies} are widely used, it may be inefficient or
-%impossible to store one copy of each dependency for each archived object.
-%Some form of sharing or de-duplication is necessary in order to keep
-%the archive to a reasonable size.
-%\end{itemize}
-%
-%We do not claim to have solved these problems in any comprehensive
-%way.  Rather, our aim in this paper is to highlight the scope
-%of the problems by presenting a case study of one complex application.
-%The application is presented to us
-%first in the form of an email that describes in prose how to install
-%the software and run the analysis.  We perform several successive
-%refinements to convert it into an executable and preservable object.
-%We then develop techniques for reducing the size of the dependencies
-%that are necessary for the object to function, and we demonstrate
-%the preserved object functioning correctly in three different
-%physical and cloud environments.
-%We describe how each of these techniques may interact with
-%a future archive of preserved software artifacts, and conclude with
-%some reflections on the challenges of preservation and advice for future efforts.

### 2015-03-18 observation.tex
Remove unused stuff

@@
 We provide the challenges we faced in capturing the application details in a reproducible form and then preserving it for subsequent reuse:
-
-%\comment{Although this starting point may seem extreme, it is
-%perfectly natural for collaborators to share configurations
-%with each other in this form, and to rely on the presence
-%of a working environment with appropriate dependencies already
-%installed.  From this starting point, the authors played the
-%role of curators, whose job it is to prepare the application
-%for permanent archival.
-%
-%First, we elaborated the email instructions into an
-%executable script that obtains the dependencies and then
-%executes the analysis.  The script declares the necessary
-%environment variables, downloads and checks out the necessary source code,
-%builds it appropriately, calls initialization scripts in
-%the dependent software, and then runs the analysis.
-%A few rounds of correction with the original author were necessary
-%to obtain all the dependencies and run the artifact correctly.
-%(The original instructions introduced in the email also indicated how to run the application
-%within a production batch system.  For the purposes of preservation,
-%we consider the execution infrastructure to be distinct from the application,
-%and leave it out of consideration for now.)
-%
-%The process of elaborating the program into a script revealed
-%several observations about this type of application:}
 
@@
 
-%networked external resources. 
-%Capturing these dependencies is straightforward if they are static in nature and the resources can be accessed without secure cryptographic functions. 
-%For instance, in TauRaoast some source code external dependencies can be obtained by simply downloading the specific libraries from a web page. 
-%However, other static dependencies require making secure connections to Github resources, and CVS servers for downloading source. 
-%While TauRoast is completely local in its execution, dynamic remote dependencies that arise in a distributed execution 
-%
-%The application data and code is distributed on five networked filesystems, which are 
-%typically mounted on a particular machine that is made accessible to the application developer.
-In TauRoast the a large amount of data to be analyzed was stored on an HDFS~\cite{borthakur2008hdfs} cluster,
-%some configuration data was stored on a CVMFS~\cite{blomer2011cernvm} filesystem,
-%and a variety of software tools were on an NFS~\cite{howard1988scale},
-%PanFS~\cite{welch2008scalable} and AFS~\cite{sandberg1985design} systems. In \emph{Athena} the data and code were available through CVMFS filesystem.
-
- %\begin{TM} 
-%each with a different access method and data source.
-%While we knew in advance that it depended upon the large CMSSW distribution,
-%it was not apparent until elaborating the script that it depended upon
-%two different Github repositories for the Tau source,
-%a CVS server at CERN for some configuration information, a public web page
-%for the PyYAML library, and the public home page of a Notre Dame student
-%for one missing header file.  (The latter is particularly troubling!)
-%While, at some level, the authors and users of these software know of these dependencies, they are often missing in
-%informal communications or forgotten once the dependency is installed.
-%However, once known, they are at least expressed explicitly within the script.
-%\end{TM}
-
-%\begin{TM}A much harder problem is that the
-%application assumed the presence of many different components in the local
-%filesystem view. It would be tempting to capture all of these by simply
-%storing a virtual machine image containing the local filesystem. However,
-%the application depended on no less than {\bf five} networked filesystems
-%available on a particular machine available to the author:
-%the data to be analyzed was stored on an HDFS~\cite{borthakur2008hdfs} cluster,
-%some configuration data was stored on a CVMFS~\cite{blomer2011cernvm} filesystem,
-%and a variety of software tools were on an NFS~\cite{howard1988scale},
-%PanFS~\cite{welch2008scalable} and AFS~\cite{sandberg1985design} systems.
-%The original authors were not aware of many of these dependencies,
-%because they simply relied on local administrators to configure the
-%software and make it available.\end{TM}
-
 \item {\bf Configuration Complexity.} To correctly reproduce an application implies that run-time configurations and consistency checks on the available software are effectively captured and preserved.
@@
 checks on a new machine.
-
-%If we allow users to work in uncontrolled
-%environments, then we must have better methods for understanding the dependencies  of existing programs.  At first, we relied on an expert reader to examine
-%the user's script and extract the dependencies.  This is clearly
-%not a scalable approach.  We then demonstrated an automated method of observing
-%what individual files are accessed by a program. However, this does
-%not cover all types of dependencies, particularly those that are networked.
-%More sophisticated observation techniques could infer higher-level information,
-%such as the RPM package names of the files accessed, the URLs of remote
-%repositories named throughout the program, or even the addresses and names of networked dependencies like databases and filesystems.
-
-%\begin{TM}As a means of controlling the complexity
-%of dependent software packages, the high energy physics community has developed
-%a number of tools that perform run-time configuration and consistency checks
-%of the available software. {\tt scram} is the software management tool used
-%by the CMS experiment.  Before running any code, {\tt scram} is used to locate
-%the appropriate version of software,  set environment variables such as the PATH, run any
-%tool-specific configuration, and do the same for all software on which it depends.
-%If the correct versions are not available, {\tt scram} halts and emits an error.
-%While this procedure has great value for consistency, it also introduces a significant cost
-%because it involves a large number of nested scripts traversing a filesystem,
-%repeatedly looking up metadata.  In our example, the time to perform this configuration
-%with a cold cache is about 14 minutes, which is almost as large as the actual analysis
-%run, which takes 20 minutes.\end{TM}
 
@@
 HDFS filesystem with 11.6TB of data, but only 18GB are actually consumed by the program. 
-%The reason for this great reduction is at first each BEAN event contains a large amount of information, and the TauAnalysis throws away a lot of the irrelevant event information, keeping only the relevant bits.
-%The CMSSW repository is 88.1GB in total
-%but only 448.3MB of source is checked out, and the actually used software only
-%measured 6.3MB.  In a few cases, a source of software is named but never actually accessed.
-%(For example, our original script includes the Open Science Grid software stack in the PATH, but does not actually use it.)
-%We suspect that end users are accustomed to missing dependencies and thus get in the habit of adding commonly used software,
-%whether it is needed or not. 
 Thus there is a size tradeoff of capturing dependencies mentioned in the program and dependencies actually used in the program.
@@
 \end{itemize}
-
-\if 0
-
-\begin{table}
-    \centering
-    \begin{tabular}{|l|}
-        \hline
-        {\bf Version 1: Email}\\ \hline
-        1. Create a CMS release,\\
-            \hspace{9pt} e.g. {\tt cmsrel CMSSW\_5\_3\_11\_patch3} \\
-        2. Install the BEAN packages as the instructions: \\
-            \hspace{9pt} {\tt \url{https://github.com/cms-ttH/BEAN/blob/...}}\\
-        3. Install grid-control: \\ 
-            \hspace{9pt} {\tt svn co \url{https://ekptrac.physik.uni-ka/...}} \\
-        4. INstall the TauAnalysis package: \\
-           \hspace{9pt} {\tt git clone \url{https://github.com/matz-e/...}} \\
-           \hspace{9pt} {\tt scram b -j32} \\
-        5. Fix grid\_control.cfg and run it. \\
-        6. Perform the actual tau roast program. \\ 
-        \hline
-        {\bf Version 2: Script}\\ \hline
-        {\tt setenv CMSSW\_BASE CMSSW\_5\_3\_11\_patch3} \\
-        {\tt cmsrel \$HOME/\$CMSSW\_BASE} \\
-        {\tt cvs co -r V03-09-23 PhysicsTools/PatUtils} \\
-        {\tt git clone \url{https://github.com/cms-ttH/BEAN.git}} \\
-        {\tt wget -r \url{http://nd.edu/~abrinke1/...}} \\
-        {\tt scram b -j32} \\
-        {\tt wget \url{http://pyyaml.org/download/pyyaml/PyYAML...}}\\
-        \#the experiment data is from HDFS \\
-        {\tt cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10}\\
-        {\tt cmsenv}\\
-        {\tt python setup.py install --user} \\
-        {\tt scripts/roaster data/generic\_ttl.yaml} \\ 
-        \hline
-        {\bf version 3: Formulated Script} \\ \hline
-        {\tt setenv CMSSW\_BASE CMSSW\_5\_3\_11\_patch3} \\
-        {\tt setenv {\bf GIT} \url{https://github.com}} \\
-        {\tt setenv {\bf PYYAML} \url{http://pyyaml.org}} \\
-        {\tt setenv {\bf ND} \url{http://nd.edu}} \\
-        {\tt cmsrel \$HOME/\$CMSSW\_BASE} \\
-        {\tt cvs co -r V03-09-23 PhysicsTools/PatUtils} \\
-        {\tt git clone \${\bf GIT}/cms-ttH/BEAN.git} \\
-        {\tt wget -r \${\bf ND}\url{/~abrinke1/ElectronEffectiveArea.h}} \\
-        {\tt scram b -j32} \\
-        {\tt wget \${\bf PYYAML}/download/pyyaml/PyYAML...}\\
-        \#the experiment data is from HDFS \\
-        {\tt cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10}\\
-        {\tt cmsenv}\\
-        {\tt python setup.py install --user} \\
-        {\tt scripts/roaster data/generic\_ttl.yaml} \\ 
-        \hline
-       {\bf Version 4: Fine-Grained Toolkit - Package}\\ \hline
-        {\tt setenv CMSSW\_BASE CMSSW\_5\_3\_11\_patch3} \\
-        {\tt setenv {\bf GIT} \url{https://github.com}} \\
-        {\tt setenv {\bf PYYAML} \url{http://pyyaml.org}} \\
-        {\tt setenv {\bf ND} \url{http://nd.edu}} \\
-        {\tt cmsrel \$HOME/\$CMSSW\_BASE} \\
-        {\tt cvs co -r V03-09-23 PhysicsTools/PatUtils} \\
-        {\tt git clone \${\bf GIT}/cms-ttH/BEAN.git} \\
-        {\tt wget -r \${\bf ND}\url{/~abrinke1/ElectronEffectiveArea.h}} \\
-        {\tt scram b -j32} \\
-        {\tt wget \${\bf PYYAML}/download/pyyaml/PyYAML...}\\
-        \#the experiment data is from HDFS \\
-        {\tt cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10}\\
-        {\tt cmsenv}\\
-        {\tt python setup.py install --user} \\
-        {\tt scripts/roaster data/generic\_ttl.yaml} \\ 
-        \hline
-    \end{tabular}
-    \caption{Scripts of each Solution}
-    \label{table:scripts}
-\end{table}
-
-\fi

### 2015-03-18 paper.tex
Remove unused stuff

@@
 \excludecomment{TM}
-%\setlength{\textwidth}{6.25in}
 
 \title{An Invariant Framework for Conducting Reproducible Computational Science}
-
-% \titlerunning{} has to be set to either the main title or its shorter
-% version for the running heads. When processed by
-% EasyChair, this command is mandatory: a document without \titlerunning
-% will be rejected by EasyChair
 
@@
 
-% A category with the (minimum) three required fields
-%\category{H.4}{Information Systems Applications}{Miscellaneous}
-%A category including the fourth, optional field follows...
-%\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]
-
-%\terms{Theory}
-
 \input {intro}
@@
 \input {evaluation}
-%\input {problems}
 \input {related_work}
-%\input {postscript}
 \section{Conclusions and Future work}
@@
 \end{document}
-
-\if 0
-Section 2: Overview of Application
-    CMS/LHC introduction.
-    Data sources and reduction of size.
-    Code sources and reduction of size.
-    Prose observations about the script.
-        Uses multiple repos that change over time, with varying level of stability.
-        Low selectivity from the larger repos
-        Significant initialization time to collect everything.
-        Incidental infrastructure tools versus essential objects.
-        Some dependencies were surprising.
-    Figure: Diagram of app with both code and data sources.
-    Table: Show all code and data sources and size within one table.
-
-Section 3: Preservation Strategies
-    Figure: Show app in four stages:
-        Single email.
-        Script with embedded references to dependencies.
-        Script with map file that refers to external dependencies.
-        Script with map file that refers to preserved dependencies.
-
-    Transform to more suitable format that expresses dependencies.
-
-    Incorporate into archive, saving deps and map file.
-
-    But, how to get the dependencies?
-
-    Three strategies:
-        Original - Unmodified application run in original environment.
-        Coarse-Grained - Capture deps at large granularity -- whole filesystems and repositories.
-        Fine-Grained - Capture deps at a fine granularity -- individual files actually used.
-
-    Coarse-Grained Method (Copy Repositories)
-        First, determine dependencies
-        Express app as script + map file
-        Packaging tool downloads deps, rewrites map file.
-        To run packaged application, obtain map, download
-
-    Fine-Trained Toolkit (Parrot)
-        Tool to detect dependencies (Parrot)
-        Express app as script + map file
-        Packaging tool downloads deps, rewrites map file.
-        To run package application, run again with Parrot.
-
-Section 4: Evaluation
-
-    Table: Time and size of preserving using each of the two techniques.
-
-    Explain why the techniques show different performance.
-
-    Is one technique more effective than the other?  Why?
-\fi

### 2015-03-18 tauroast.tex
Modifications according to the suggestions from reviewers
Remove unused stuff

@@
 
-%The application which is the study of this paper is an CMS application~\cite{collaboration2008cms} called \emph{TauRoast}.
-%It searches for cases where the Higgs boson decays to two tau leptons~\cite{chatrchyan2013search}.
-%Since the tau leptons are very short-lived, they are not observed directly, but by the particle decay products 
-%that they generate.  So, the analysis must search for detector
-%events that show a signature of decay products compatible with both hadronic tau and top decays.
-
 Code and data in \emph{TauRoast} is available through five different networked filesystems, namely an HDFS cluster for data files, 
-%~\cite{borthakur2008hdfs},~\cite{sandberg1985design},\cite{welch2008scalable}, ~\cite{howard1988scale}
 some configuration files were stored on a CVMFS~\cite{blomer2011cernvm} filesystem, and a variety of software tools were on an NFS, PanFS and AFS systems.
@@
 In \emph{Athena} data is obtained through an external Dropbox-like system called the FaxBox, but does not go through any reduction steps. Code is obtained through 
-CernVM-FS, which provides the analysis routines. However, depending upon the input data code and the configuration that will be invoked changes. 
+CVMFS, which provides the analysis routines. However, depending upon the input data code and the configuration that will be invoked changes. 
 Thus in \emph{Athena} the used code and configuration are dynamic depending upon input data, where as in \emph{TauRoast} the code and data are static, 
 but the amount of data and code to include changes depending on the involved science.
-
-%In application, code and data that form the applications are drawn from large external repositories through multiple step reductions. 
-%Figure \ref{fg:data-code-size} shows the data and code reduction and reliance on software distribution repositories. There are two observations to be 
-%derived from 
-%of this reduction. First. the actual code contributed by individual groups, in this case the CMS and ATLAS group, is small. 
-%But the contributed software relies on several software dependencies, which
-%are available software distribution repositories such as the CMS Software Distribution (CMSSW)~\cite{cms2006cms}, and the CVMFS. 
-%These repositories contain many different tools, libraries, and utilities, and for ATLAS, the Reco\_TR analysis framework which consists of many analysis routines. 
-%
-%Figure~\ref{fig:data-code-size} shows that both the code and data
-%that form \emph{TauRoast} are drawn from large repositories through
-%multiple steps of reduction.  A preservation strategy must weigh
-%whether to store the large repositories completely, the fragments
-%used by an artifact, or something in between.
-%
-%{\bf Code Sources.} Like many scientific codes, the central algorithm
-%of \emph{TauRoast} is expressed in a relatively small amount of
-%custom code developed by the primary author.  But, the code cannot
-%run at all without making use of an enormous collection of software
-%dependencies.  
-%The largest of these repositories is the CMS Software Distribution (CMSSW)~\cite{cms2006cms},
-%which contains many different tools, libraries, and utilities.
-No single code uses anywhere close to all of these.
-But, because it is widely used within the experimental researchers, it is common for users to simply expect that a particular version of the entire repository is available.
-% 
-%{\bf Data Sources.}
-%The CMS collaboration provides end-users with a pre-processed
-%and reduced data format, AOD~\cite{holtman2001cms}, 
-%which is based on the RAW output of the CMS detector readout electronics and reconstructed world-wide.
-%As AOD data are too large to be iteratively processed repetitively in
-%a physics analysis workflow, it is normally reduced further in
-%structural complexity and content.  For the analysis under
-%investigation here, this is a two-step process.  First, the AOD data
-%are processed at the Notre Dame working group cluster to BEAN (Boson Exploration Analysis Ntuple) events,
-%containing only trivial data containers packed in vectors.  This step
-%is time and CPU intensive and its output contains data of 11.6$\,$TB to be
-%analyzed by the tau analysis.
-%In the second step, the data are reduced to the ``Ntuple'' format,
-%which contains only events matching basic quality criteria and
-%fields relevant to \emph{TauRoast}.
-%Once the data has been reduced to Ntuples, TauRoast can be run as a single
-%process, and contains a stringent event selection to look only at high
-%quality candidate events for the underlying physical process.
-%Quantities from the relevant events can be
-%both plotted and used in multivariate analysis to determine the level
-%of expected signal in real data.

### 2015-03-20 evaluation.tex
Remove unused stuff
Modification (according to dthain's suggestions)

@@
     \centering
-    \begin{tabular}{lcccc}
+    \begin{tabular}{lcccr}
     \hline
-    \bf Application & \bf Tool Type & \bf Obtain Namelist & \bf Create Package & \bf Re-Execution \\ \hline
-	Athena & Parrot & 10 min 14 sec & 53 sec & 9 min 14 sec \\ \hline
-	Athena & PTU & --- & 8min 48 sec & 7 min 21 sec \\ \hline
-	TauRoast & Parrot & 22 min 50 sec  & 4 min 25 sec & 10 min 24 sec \\ \hline
-	TauRoast & PTU & --- & 23 min 30 sec & 8 min 40 sec \\ \hline 
+    \bf Application & \bf Packaging Tool & \bf Obtain Namelist & \bf Create Package & \bf Re-Run (Tool/Time)\\ \hline
+	Athena & Parrot & 10 min 14 sec & 00 min 53 sec & Parrot / 09 min 14 sec  \\ \hline
+	Athena & PTU & --- & 08 min 48 sec & PTU / 07 min 21 sec  \\ \hline
+	TauRoast & Parrot & 22 min 50 sec  & 04 min 25 sec &chroot / 10 min 24 sec \\ \hline
+	TauRoast & PTU & --- & 23 min 30 sec & PTU / 08 min 40 sec \\ \hline 
     \end{tabular}
@@
 \end{table}
-%	\begin{tablenotes}
-%	      \small
-%	      \item The first column illustrates the total size of each data and software source; 
-%	            the second column illustrates the size of the named files from each source;
-%	            the third column illustrates the size of actually used data from each source.
-%	            N/A denotes it is hard to figure out the named size of implicit dependencies directly.        
-%	    \end{tablenotes}
 
@@
 
-In Athena, the input file is 224MB and output files are 16MB. PTU build a 855MB package, while Parrot builds an 825MB package. The overhead is of provenance which is 7MB and 
+In Athena, the input file is 224MB and output files are 16MB. PTU builds a 855MB package, while Parrot builds an 825MB package. The overhead is of provenance which is 7MB and 
 some differences is dependency information.

### 2015-03-20 intro.tex
Modification (according to dthain's suggestions)

@@
 Historically, this has been achieved through text and proofs in a publication.
-As computation pervades the sciences and transforms the scientific method, mere text is considered insufficient. 
+As computation pervades the sciences and transforms the scientific method, mere text is no longer sufficient. 
 In particular, apart from textual descriptions describing the result, a reproducible result must also include several computational artifacts, such as software, data,  environment variables, and state of computation that are involved in the adopted scientific method \cite{Sole}.
@@
 This way VMIs become an authoritative, encapsulated, and executable records of computations, especially computations whose results are destined for publication and/or re-use, and the VMIs can be shared easily \cite{Lampoudi}.
-With this approach, oftentimes, the resulting image is too big in size for share-ability purposes.
+However, the resulting image may be too big to distribute.
 An alternative light-weight form of virtualization allows encapsulation of the application software, along with all its necessary dependencies into a self-contained package, but does not make it executable.
-The encapsulation of the self-contained package is achieved by interposing application system calls, and only copying the necessary dependencies (data, libraries, code, etc.) into the package, which also makes it lighter weight than a VMI.
-While both forms of virtualization provide mechanisms for sandboxing the computations associated with a scientific result, neither form of virtualization provides any guarantee that the included pieces of software will indeed reproduce the associated scientific result.
+The encapsulation of the self-contained package is achieved by interposing application system calls, and copying the necessary dependencies (data, libraries, code, etc.) into the package, making it lighter weight than a VMI~\cite{guo2011cde}.
+While both approaches provide mechanisms for sandboxing the computations associated with a scientific result, neither form of virtualization provides any guarantee that the included pieces of software will indeed reproduce the associated scientific result.
 
-Since reproducibility is significantly about comprehensive documentation, virtualization approaches in their current form only make it easy to capture the computations.
-Preserving the computations, so that they are easy to understand, install, or alter implicit dependencies that are part of computation, especially as dependencies and software components evolve or become deprecated, is not effectively addressed.
+Since reproducibility includes documentation, virtualization approaches in their current form only make it easy to capture the computations.
+Preserving the computations so that they are easy to understand, install, or alter implicit dependencies that are part of computation is not effectively addressed, especially as dependencies and software components evolve or become deprecated.
 There are two approaches to address the preservation challenge.
@@
 In particular, we consider the light-weight virtualization approaches, because, we believe that the combination of light-weight approaches with more standardized software delivery mechanisms can lead to addressing the reproducibility challenge for a wide variety of scientific researchers.
-A package created by those light-weight approaches encapsulates all the necessary dependencies of an application, and can be used to repeat the application through different sandbox mechanisms, including Parrot, CDE, PTU, chroot, and Docker.
-
-To conduct a thorough examination, we consider real-world complex high energy physics (HEP) applications, independently developed by two HEP groups, that must be reproduced so that the entire high energy physics community can benefit from the analysis obtained from the application.
-We describe challenges in reproducing the applications, and consider the extent to which reproducibility requirements can be satisfied with light-weight virtualization approaches and software delivery mechanisms.
-We propose an invariant framework for computational reproducibility that combines light-weight virtualization with software delivery mechanisms for efficiently capturing, invariantly preserving and practically deploying applications.
-We measure the performance overhead of  light-weight virtualization and software delivery approaches.
+A package created by those light-weight approaches encapsulates all the necessary dependencies of an application, and can be used to repeat the application through different sandbox mechanisms, including Parrot~\cite{thain2005parrot}, CDE, PTU~\cite{PTU}, chroot, and Docker~\cite{boettiger2015introduction}.
 
@@
 Our objective here is to preserve the mess as-is.
+
+To conduct a thorough examination, we consider real-world complex high energy physics (HEP) applications, independently developed by two groups, that must be reproduced so that the entire HEP community can benefit from the analysis.
+We describe challenges in reproducing the applications, and consider the extent to which reproducibility requirements can be satisfied with light-weight virtualization approaches and software delivery mechanisms.
+We propose an invariant framework for computational reproducibility that combines light-weight virtualization with software delivery mechanisms for efficiently capturing, invariantly preserving and practically deploying applications.
+We measure the performance overhead of  light-weight virtualization and software delivery approaches, and show the preserved packages can be distributed to allow reproduction and verification.

### 2015-03-20 measure.tex
Remove unused stuff
Modification (according to dthain's suggestions)

@@
 technology.
-To this end, we have identified several technologies and techniques
+To this end, we have identified multiple technologies 
 that can implement each stage of the framework.
@@
 
-Parrot~\cite{thain2005parrot} is a virtual filesystem access tool which
+Parrot is a virtual filesystem access tool which
 is used to attach applications to a variety of remote I/O systems such as HTTP, FTP, and CVMFS. It works by trapping system calls through the {\tt ptrace} interface,
@@
 needs.  Parrot is particularly used in the high energy physics community
-to provide remote access to application software.
+to provide remote access to application software via CVMFS.
 To capture dependencies, we made small modifications to Parrot to record
@@
 
-PTU~\cite{PTU,pham2014framework} is designed to create a package of an application by recording all of the binaries, libraries, scripts, data files, and environment variables used by a program.
-PTU uses the CDE~\cite{guo2011cde} technology to observe system calls, but takes a snapshot of every file at the point of access.
+PTU~\cite{pham2014framework} is designed to create a package of an application by recording all of the binaries, libraries, scripts, data files, and environment variables used by a program.
+PTU uses the CDE technology to observe system calls, but takes a snapshot of every file at the point of access.
 In addition to files, PTU records \emph{metadata} about the execution environment, such as kernel versions, application versions, and dynamic library versions by using standard Unix commands.
@@
 from the dependency list.  We have implemented three:
-In a {\bf shallow copy}, we simply copy only
+In a {\bf shallow copy}, we copy only
 the exact dependencies.
@@
 wide variety of services and efforts to share binary objects in this way,
-and so we assume such a service will be available in the future.
+and so we assume such multiple services will be available in the future.
 
@@
 \end{figure*}
-
-%\section{Measuring Dependencies}
-%We have developed a prototype tool to assist in the measurement and preservation
-%of implicit dependencies for complex applications.
-%We use Parrot~\cite{thain2005parrot} to explicitly record all
-%of the files accessed by our example application, allowing us to observe how
-%much of each external dependencies is used, and what local resources are implicitly used.
-%Using this information, we create a \emph{reduced package} which contains
-%only the files actually used by the application.
-%
-%Parrot is a virtual filesystem access tool which has been used to attach
-%existing programs to a variety of remote I/O systems, such as HTTP, FTP, and CVMFS.
-%It works by trapping an application's system calls through the Linux {\tt ptrace} debugging
-%interface, and then replacing them with the desired I/O operations.  Parrot is already used
-%in the high energy physics community with applications like TauRoast specifically to 
-%provide access to the CMSSW software distribution via the CVMFS distributed file system.
-%We made small modifications to Parrot to record a \emph{namelist} which lists all 
-%of the files that an application actually accesses.
-%
-%Figure~\ref{fig:workflow-parrot} illustrates the measurement process.
-%The starting point of this toolkit is one successful execution of the application on the native machine.
-%First, we execute the actual data analysis script under Parrot to generate the namelist.
-%Then, using the namelist, we generate a package containing all the necessary data
-%and software for one analysis program. When another
-%researcher wants to repeat the program, he only needs to obtain the package and
-%execute the actual analysis program inside the package. 
-%
-%For one execution of \emph{TauRoast}, the generated namelist includes 132,047 accessed filenames,
-%along with the system calls used to access the file, such as {\tt open}, {\tt stat}, {\tt read}, etc.
-%With duplicate filenames removed, the list is reduced to 67,168 files.
-%Many of those entries do not exist, because they reflect attempts
-%by the application to search for programs and libraries in multiple places.
-%Only 22,068 entries reflect existing files or directories.
-%
-%The packaging tool iterates over each item of the filename list, determines the process
-%mode and replication degree according to the file type (common files,
-%directories, symbolic links) and the system call type, generates one package
-%containing the dependencies, and summarizes the contents of the package
-%as shown in Table~\ref{table:package-info}.  To the extent possible,
-%the filesystem structure of the original environment is preserved.
-%
-%We considered several approaches to constructing the package.
-%In a {\bf shallow copy}, we only copied the individual files in the namelist,
-%creating only parent directories for each.  Where a directory was listed,
-%we created the directory and populated it with empty files as placeholders
-%to facilitate a directory listing.  In a {\bf medium copy}, we copied the
-%individual files as before.  Where a directory was listed, we created
-%the directories and copied the contents of the files in that directory,
-%one level deep.  A {\bf deep copy} would duplicate all directories recursively,
-%but this would have resulted in TB-sized packages, so we did not consider
-%it further.
-%
-%Parrot is required to re-run the packaged artifact, in order to force
-%the packaged files to appear to exist in their original locations.
-%To this end, the packaging tool creates a \emph{file map} which maps
-%the logical names of the files to their current physical locations, as shown in Table~\ref{table:map-file}.
-%Parrot reads the file map and redirects system calls at run-time to achieve the desired effect.
-%As the example suggests, special device files such as {\tt /proc} and {\tt /dev}
-%are not incorporated into the package but are instead accessed natively.
-%
-%\begin{table}
-%    \centering
-%    \begin{tabular}{ll}
-%    \hline
-%    \bf Path used in Program & \bf Actual Location \\ \hline
-%    {\tt /} & {\tt /tmp/package-hep} \\ \hline
-%    {\tt /tmp/package-hep} & {\tt /tmp/package-hep} \\ \hline
-%    {\tt /dev} & {\tt /dev} \\ \hline
-%    {\tt ...} & {\tt ...}\\ \hline
-%    \end{tabular}
-%    \caption{Structure of Map File}
-%    \label{table:map-file}
-%\end{table}
-%
-%\begin{table}
-%    \centering
-%    \begin{tabular}{rrr}
-%\hline
-%                    & \bf Shallow Copy & \bf Medium Copy\\
-%\hline
-%    Whole Files    & 1632         & 15642\\ 
-%\hline
-%    Empty Files    & 14273        & 263\\
-%\hline
-%    Directories    & 1549         & 1549\\ 
-%\hline
-%    Symbolic Links & 4614         & 4614 \\
-%\hline
-%    \bf Total Size & \bf 21GB     & \bf 28GB \\ 
-%\hline
-%    \end{tabular}
-%    \caption{Package Information}
-%    \label{table:package-info}
-%\end{table}
-
-%\subsection{Tracking of Network Dependencies}
-%
-%\begin{figure}
-%\centering
-%\includegraphics[width=.6\textwidth]{git-syscall.eps}
-%\caption{Exec Syscalls of a git command}
-%\label{fig:git-syscall}
-%\end{figure}
-%
-%\begin{figure}
-%\centering
-%\includegraphics[width=.6\textwidth]{http_packet.eps}
-%\caption{HTTP Request and Response}
-%\label{fig:http_packet}
-%\end{figure}
-%
-%\begin{figure}
-%\centering
-%\includegraphics[width=.6\textwidth]{url_redirection.eps}
-%\caption{An Example of URL Redirection}
-%\label{fig:url_redirection}
-%\end{figure}
-%
-%All the dependencies of one program can be divided into three categories: local file system (e.g., /usr, /lib and /lib64), remote file systems which can be mounted as local directories (e.g., /cvmfs and /hdfs), and other remote network dependencies (e.g.
-http, https and ssh).
-%Through utilizing ptrace to trap each file-relevant system call used by a program, the first two categories of dependencies can be collected. 
-%Motivation of tracking network dependencies: Linkrot is a common and great threat to the preservation of scientific applications.
-A URL which works normally today may be unavailable permanently.
-A method which can help the scientists figure out all the network dependencies of their applications provides the chance to evaluate the stability of each network dependencies and preserve the unstable network resources before linkrot happens.
-%One direct solution to track the third category of dependencies is to utilize ptrace to check each exec system call used by a program and record each network-relevant executable and its parameters.
-However, an executable may create one or more child processes to finish some tasks, and a child process may create their own children processes.
-Figure~\ref{fig:git-syscall} shows all the processes created by a git command.
-A process with PID 998 is created to clone a remote git repository into local machine, which totally has 6 child processes.
-Moreover, a network-relevant executable name collection is necessary to identify network dependencies.
-The diversity of network-relevant executables and the large process tree generated for a network executable make this solution infeasible.
-%
-%Another solution to track network dependencies is to track the network sockets.
-The user process communicates with the network protocol stacks in the kernel through the network socket layer user interface on Linux.
-From the process tree shown in the above figure, the process with PID 1000 responds to create a socket, connect to a DNS server, send a DNS request packet to the DNS server and receive a DNS response packet from the DNS server.
-The information gained from the network socket tracking can be divided into three categories.
-%\begin{itemize}
-%\item The information of network sockets used to communicate with remote network dependences (through socket and connect system calls) can be used to figure out the port number, service name (such as, http, https, and ssh), socket type (stream and datagram),  and the domain type (inet and inet6).
-%\item The contents of DNS packets can be used to figure out the hostname and IP address of each remote network dependency. 
-%\item As for applications based on http protocol, all the http requests and responses can be seen, as shown in Figure~\ref{fig:http_packet}.
-However, as for applications based on https and ssh which encrypt network data using TLS/SSL, tracking network data on the socket level can only see the encrypted data.
-%\end{itemize}
-%
-%The results of tracking network sockets used by a program involves two categories of network resource redirections, dns-level hostname redirection and website-level url redirection. 
-%\begin{itemize}
-%\item dns-level hostname redirection: Each DNS packet includes five parts, header, question, answer, authority, and additional.
-A DNS response packet with the type CNAME has multiple answers.
-For example, the DNS response packet which tries to resolve {\tt www3.nd.edu} includes two answers.
-The first answer provides an alias of {\tt www3.nd.edu}, {\tt www-vip.cc.nd.edu}, and the second answer maps the alias to the IP address.
-%{\tt www3.nd.edu} CNAME {\tt www-vip.cc.nd.edu}
-%{\tt www-vip.cc.nd.edu} A {\tt 129.74.12.151}
-%The CNAME-type DNS packets leave us a question, among the hostname used by the user, the alias(es), the IP address, what should we preserve?
-%\item website-level url redirection: Website-level url redirection happens when a website updates its location and still want their old users access their resources using the old url.
-Figure~\ref{fig:url_redirection} illustrates the url redirection between {\tt \url{www3.nd.edu/~ccl}} and {\tt ccl.cse.nd.edu}.
-Except for the difference of hostnames, the application layer protocols used by the old-version website and the new-version website is also different: the old website provides services through the https protocol, while the new website provides services through the http protocol.
-%\end{itemize}
-%
-%The usage of https protocol makes detecting of website-level url redirections through tracking system calls more difficulty and even impossible.
-All the application data will be encrypted at presentation layer through the TLS/SSL protocol, which is initialized at the session layer and works at the presentation layer.

### 2015-03-20 observation.tex
Modification (according to dthain's suggestions)

@@
-\section{Challenges and Observations in Reproducing HEP Applications}
+\section{Challenges in Reproducing HEP Applications}
 
@@
 machine at our home institution, with no particular guarantee that
-it will run anywhere else in the world. Such level of documentation and exchange of information about a software is typically routine in the scientific world. 
+it will run anywhere else in the world. This minimal level of documentation about software is routine in the scientific world. 
 We provide the challenges we faced in capturing the application details in a reproducible form and then preserving it for subsequent reuse:
@@
 
-\item {\bf Identifying all dependencies.}  Due to the distributed nature of HEP applications, the applications typically depend on a large number of external and local dependencies.
+\item {\bf Identifying all dependencies.}  Due to the distributed nature of HEP applications, these applications depend on a large number of external and local dependencies.
 External dependencies are often explicitly stated, such as when the application makes connections to Github resources, and CVS servers for downloading source. 
@@
 \item {\bf Configuration Complexity.} To correctly reproduce an application implies that run-time configurations and consistency checks on the available software are effectively captured and preserved.
-For CMS,  {\tt scram} software management tool, is used to locate
+For CMS,  the {\tt scram} software management tool is used to locate
 the appropriate version of software,  set environment variables such as the PATH, run any
@@
 distribution released a new version, the target execution environment was upgraded
-to a new operating system, and the application deprecated the use of CVS for obtaining
+to a new operating system, and the application switched from CVS to Git for obtaining
 the software. In Athena, the computing environment can potentially change daily, since upgrades to the software framework occur on a nightly basis.  

### 2015-03-20 tauroast.tex
Modification (according to dthain's suggestions)

@@
 We study applications taken from two experiments of the CERN Large Hadron Collider, namely the ATLAS experiment and the CMS experiment. 
-One of the applications of the ATLAS experiment is the \emph{Athena} application, which is a general purpose processing framework including algorithms
-for event reconstruction and data reduction \cite{calafiura2005athena}. The CMS experiment is conducted through an application termed  \emph{TauRoast}, which searches for specific 
-cases where the Higgs boson decays to two tau leptons~\cite{chatrchyan2013search}. In LHC, the ATLAS and CMS experiments are distinct, 
+In LHC, the ATLAS and CMS experiments are distinct, 
 developed independently by two entirely separate physics communities. Consequently, their applications  
@@
 tools work across the two communities. 
+One of the applications of the ATLAS experiment is the \emph{Athena} application, which is a general purpose processing framework including algorithms
+for event reconstruction and data reduction \cite{calafiura2005athena}. The CMS experiment is conducted through an application termed  \emph{TauRoast}, which searches for specific 
+cases where the Higgs boson decays to two tau leptons~\cite{chatrchyan2013search}.
 
-Code and data in \emph{TauRoast} is available through five different networked filesystems, namely an HDFS cluster for data files, 
-some configuration files were stored on a CVMFS~\cite{blomer2011cernvm} filesystem, and a variety of software tools were on an NFS, PanFS and AFS systems.
+Code and data in \emph{TauRoast} is available through five different networked filesystems which are mounted locally, an HDFS cluster for data, 
+some configuration files were stored on CVMFS~\cite{blomer2011cernvm}, and a variety of software tools were on an NFS, PanFS and AFS systems.
 In addition, code may exist in version control systems such as Git, CVS, and CMS Software Distribution (CMSSW). %~\cite{cms2006cms}. 

### 2015-03-24 intro.tex
some changes to intro

@@
 One approach is to conduct the entire computation relating to a scientific result within a virtual machine image, and then share the resulting image.
-This way VMIs become an authoritative, encapsulated, and executable records of computations, especially computations whose results are destined for publication and/or re-use, and the VMIs can be shared easily \cite{Lampoudi}.
-However, the resulting image may be too big to distribute.
-An alternative light-weight form of virtualization allows encapsulation of the application software, along with all its necessary dependencies into a self-contained package, but does not make it executable.
-The encapsulation of the self-contained package is achieved by interposing application system calls, and copying the necessary dependencies (data, libraries, code, etc.) into the package, making it lighter weight than a VMI~\cite{guo2011cde}.
+This way VMIs become an authoritative, encapsulated, and executable record of computations, especially computations whose results are destined for publication and/or re-use; images, like files, can then be shared \cite{Lampoudi}.
+However, the resulting image may be too big to share or distribute widely.
+An alternative light-weight form of virtualization is to encapsulate only the application software, along with all its necessary dependencies, into a self-contained package.
+The encapsulation is achieved by interposing application system calls, and copying the necessary dependencies (data, libraries, code, etc.) into the package, making it lighter weight than a VMI~\cite{guo2011cde}.
+However, the package is not longer an executable record of the computation and still needs an accompanying operating system for execution.
+
 While both approaches provide mechanisms for sandboxing the computations associated with a scientific result, neither form of virtualization provides any guarantee that the included pieces of software will indeed reproduce the associated scientific result.
+Often
 

### 2015-03-25 intro.tex
more changes

@@
 An alternative light-weight form of virtualization is to encapsulate only the application software, along with all its necessary dependencies, into a self-contained package.
-The encapsulation is achieved by interposing application system calls, and copying the necessary dependencies (data, libraries, code, etc.) into the package, making it lighter weight than a VMI~\cite{guo2011cde}.
+The encapsulation is achieved by OS-level sandboxing techniques that interpose application system calls, and copy the necessary dependencies (data, libraries, code, etc.) into a package, making it lighter weight than a VMI~\cite{guo2011cde}.
 However, the package is not longer an executable record of the computation and still needs an accompanying operating system for execution.
 
-While both approaches provide mechanisms for sandboxing the computations associated with a scientific result, neither form of virtualization provides any guarantee that the included pieces of software will indeed reproduce the associated scientific result.
-Often
+While both approaches provide mechanisms for encapsulating the computations associated with a scientific result, neither form of virtualization provides any guarantee that the included pieces of software will indeed reproduce the associated scientific result.
+In general, in the absence of reproducible policy guidelines, such guarantees can be hard to provide.
+However, we can certainly improve upon the guarantees by \emph{preserving} the encapsulated computations in such a way that they are always reproducible.
+A preservation mechanism, if present, can make it easy to install images or packages, alter implicit dependencies that are part of computation as software components evolve or become deprecated, and finally provide  mechanisms for documentation that make computations easy to understand.
 
-Since reproducibility includes documentation, virtualization approaches in their current form only make it easy to capture the computations.
+%Since reproducibility includes documentation, virtualization approaches in their current form only make it easy to capture the computations.
 Preserving the computations so that they are easy to understand, install, or alter implicit dependencies that are part of computation is not effectively addressed, especially as dependencies and software components evolve or become deprecated.
+
 There are two approaches to address the preservation challenge.
@@
 In this paper we examine the second approach.  
-In particular, we consider the light-weight virtualization approaches, because, we believe that the combination of light-weight approaches with more standardized software delivery mechanisms can lead to addressing the reproducibility challenge for a wide variety of scientific researchers.
+In particular, we consider the light-weight virtualization approaches, because, we believe that a combination of light-weight approaches with more standardized software delivery mechanisms can lead to addressing the reproducibility challenge for a wide variety of scientific researchers.
 A package created by those light-weight approaches encapsulates all the necessary dependencies of an application, and can be used to repeat the application through different sandbox mechanisms, including Parrot~\cite{thain2005parrot}, CDE, PTU~\cite{PTU}, chroot, and Docker~\cite{boettiger2015introduction}.
@@
 We do not claim our solution is the only way to preserve applications.
-Generally, there are two different approaches to preserve applications: measure the mess and force cleanliness.
-The first approach allows end users to construct the environment as desired, and then measures the dependencies.
-The latter one forces users to specify the execution environment for an application in a well organized way.
-Our objective here is to preserve the mess as-is.
+Broadly, there are two different approaches to preserve applications: force cleanliness or measure the mess.
+The first approach forces users to specify the execution environment for an application in a well organized way.
+In the latter one end users construct the environment as desired, and the complexity of the environment is measured in terms of its dependencies.
+Our objective here is to measure the mess as-is and then preserve it over time.
 

### 2015-03-30 intro.tex
Proof-reading

@@
 Reproducibility is a cornerstone of the scientific method~\cite{borgman2012data}. 
-Its importance is underscored by its ability to advance science---reproducing by verifying and validating a scientific result leads to improved understanding, thus increasing possibilities of reusing or extending the result.
-Ensuring reproducibility of a scientific result, however, often entails detailed documentation and specification of the involved scientific method.
-Historically, this has been achieved through text and proofs in a publication.
+Its ability to advance science underscores its importance---reproducing by verifying and validating a scientific result leads to improved understanding, thus increasing possibilities of reusing or extending the result.
+Ensuring the reproducibility of a scientific result, however, often entails detailed documentation and specification of the involved scientific method.
+Historically, text and proofs in a publication have achieved this end.
 As computation pervades the sciences and transforms the scientific method, mere text is no longer sufficient. 
-In particular, apart from textual descriptions describing the result, a reproducible result must also include several computational artifacts, such as software, data,  environment variables, and state of computation that are involved in the adopted scientific method \cite{Sole}.
+In particular, apart from textual descriptions describing the result, a reproducible result must also include several computational artifacts, such as software, data,  environment variables, and the state of computation that are involved in the adopted scientific method \cite{Sole}.
 
-Virtualization has emerged as a promising approach for reproducing computational scientific results.
-One approach is to conduct the entire computation relating to a scientific result within a virtual machine image, and then share the resulting image.
+Virtualization has emerged as a promising way to reproduce computational scientific results.
+One such approach is to conduct the entire computation relating to a scientific result within a virtual machine image, and then share the resulting image.
 This way VMIs become an authoritative, encapsulated, and executable record of computations, especially computations whose results are destined for publication and/or re-use; images, like files, can then be shared \cite{Lampoudi}.
-However, the resulting image may be too big to share or distribute widely.
-An alternative light-weight form of virtualization is to encapsulate only the application software, along with all its necessary dependencies, into a self-contained package.
-The encapsulation is achieved by OS-level sandboxing techniques that interpose application system calls, and copy the necessary dependencies (data, libraries, code, etc.) into a package, making it lighter weight than a VMI~\cite{guo2011cde}.
-However, the package is not longer an executable record of the computation and still needs an accompanying operating system for execution.
+The resulting image, however, may be too big to share or distribute widely.
+An alternative light-weight form of virtualization is to encapsulate only the application software along with all its necessary dependencies into a self-contained package.
+The encapsulation is achieved by OS-level sandboxing techniques that interpose application system calls and copy the necessary dependencies (data, libraries, code, etc.) into a package, making it lighter weight than a VMI~\cite{guo2011cde}.
+Yet, the package is not longer an executable record of the computation and still requires an accompanying operating system for execution.
 
 While both approaches provide mechanisms for encapsulating the computations associated with a scientific result, neither form of virtualization provides any guarantee that the included pieces of software will indeed reproduce the associated scientific result.
-In general, in the absence of reproducible policy guidelines, such guarantees can be hard to provide.
-However, we can certainly improve upon the guarantees by \emph{preserving} the encapsulated computations in such a way that they are always reproducible.
-A preservation mechanism, if present, can make it easy to install images or packages, alter implicit dependencies that are part of computation as software components evolve or become deprecated, and finally provide  mechanisms for documentation that make computations easy to understand.
+In general, in the absence of reproducible policy guidelines, such guarantees can be difficult to provide.
+Preserving the encapsulated computations in such a way that they are always reproducible will improve upon the guarantees.
+A preservation mechanism can increase the ease of image or package installation, alter dependencies implicit to computation as software components evolve or become deprecated, and provide mechanisms for documentation that make computations easy to understand.
 
@@
 
-There are two approaches to address the preservation challenge.
-By either introducing tools that help document dependencies and provide software attribution within VMIs or packages, or alternatively by using software delivery mechanisms, such as, centralized package management, Linux containers, and the, more recent, Docker framework.
+The two approaches that address the preservation challenge are as follows: one, the introduction of tools that help document dependencies and provide software attribution within VMIs or packages; and two, the use of software delivery mechanisms such as centralized package management, Linux containers, and the more recent Docker framework.
 We examined the first approach previously in \cite{SoftProv}.
 In this paper we examine the second approach.
-In particular, we consider the light-weight virtualization approaches, because, we believe that a combination of light-weight approaches with more standardized software delivery mechanisms can lead to addressing the reproducibility challenge for a wide variety of scientific researchers.
-A package created by those light-weight approaches encapsulates all the necessary dependencies of an application, and can be used to repeat the application through different sandbox mechanisms, including Parrot~\cite{thain2005parrot}, CDE, PTU~\cite{PTU}, chroot, and Docker~\cite{boettiger2015introduction}.
+We consider in particular the lightweight virtualization because we believe together with more standardized software delivery mechanisms, the two combined can address the reproducibility challenge for a wide variety of scientific researchers.
+A package created by those lightweight approaches encapsulates all the necessary dependencies of an application, and can be used to repeat the application through different sandbox mechanisms, including Parrot
+%In particular, we consider the light-weight virtualization approaches, because, we believe that a combination of light-weight approaches with more standardized software delivery mechanisms can lead to addressing the reproducibility challenge for a wide variety of scientific researchers.
+%A package created by those light-weight approaches encapsulates all the necessary dependencies of an application, and can be used to repeat the application through different sandbox mechanisms, including Parrot
+~\cite{thain2005parrot}, CDE~\cite{Guo}, PTU~\cite{PTU}, chroot, and Docker~\cite{boettiger2015introduction}.
 
-We do not claim our solution is the only way to preserve applications.
+Of course our solution represents only one way to preserve applications.
+Broadly, two different approaches to preserve applications have been adopted: force cleanliness or measure the mess.
+The former forces users to specify the execution environment for an application in a well-organized way.
+The latter causes end users to construct the environment as desired, and the complexity of the environment is measured in terms of its dependencies.
+Our objective here is to measure the mess as-is and then preserve it over time.
+
+%We do not claim our solution is the only way to preserve applications.
 Broadly, there are two different approaches to preserve applications: force cleanliness or measure the mess.
@@
 In the latter one end users construct the environment as desired, and the complexity of the environment is measured in terms of its dependencies.
-Our objective here is to measure the mess as-is and then preserve it over time.
+%Our objective here is to measure the mess as-is and then preserve it over time.
 
 To conduct a thorough examination, we consider real-world complex high energy physics (HEP) applications, independently developed by two groups, that must be reproduced so that the entire HEP community can benefit from the analysis.
+We describe challenges faced in reproducing the applications, and we consider the extent to which reproducibility requirements can be satisfied with lightweight virtualization approaches and software delivery mechanisms.
+We propose an invariant framework for computational reproducibility that combines lightweight virtualization with software delivery mechanisms for efficiently capturing, invariantly preserving, and practically deploying applications.
+We measure the performance overhead of lightweight virtualization and software delivery approaches, and show how the preserved packages can be distributed to allow reproduction and verification.
+%To conduct a thorough examination, we consider real-world complex high energy physics (HEP) applications, independently developed by two groups, that must be reproduced so that the entire HEP community can benefit from the analysis.
 We describe challenges in reproducing the applications, and consider the extent to which reproducibility requirements can be satisfied with light-weight virtualization approaches and software delivery mechanisms.
 We propose an invariant framework for computational reproducibility that combines light-weight virtualization with software delivery mechanisms for efficiently capturing, invariantly preserving and practically deploying applications.
-We measure the performance overhead of  light-weight virtualization and software delivery approaches, and show the preserved packages can be distributed to allow reproduction and verification.
+%We measure the performance overhead of  light-weight virtualization and software delivery approaches, and show the preserved packages can be distributed to allow reproduction and verification.

### 2015-03-30 main.tex
Rename paper.tex to main.tex Use DOI instread of the URL for the DOI
Proof-reading

--- 2015-03-18 paper.tex
@@
 \begin{abstract}
-\it Computational reproducibility depends on being able to isolate necessary and sufficient computational artifacts and preserve them for later re-execution.
-Both isolation and preservation of artifacts can be challenging due to the complexity
-of existing software and systems and the resulting implicit dependencies, resource distribution, and shifting compatibility of systems as time progresses---all conspiring
-to break the reproducibility of an application. Sandboxing is a technique
-that has been used extensively in OS environments for isolation of computational artifacts.
+\it Computational reproducibility depends on the ability to not only isolate necessary and sufficient computational artifacts but also to preserve those artifacts for later re-execution.
+Both isolation and preservation present challenges in large part due to the complexity of existing software and systems as well as the implicit dependencies, resource distribution, and shifting compatibility of systems that result over time---all of which conspire to break the reproducibility of an application.
+Sandboxing is a technique that has been used extensively in OS environments in order to isolate computational artifacts.
 Several tools were proposed recently that employ sandboxing as a mechanism to ensure reproducibility.
-However, none of these tools preserve the sandboxed application for re-distribution
-to a larger scientific community---aspects that are equally crucial for ensuring reproducibility as sandboxing itself.
-In this paper, we describe a combined sandboxing and preservation framework, which is efficient, invariant and
-practical for large-scale reproducibility. We present case studies of complex high energy
-physics applications and show how the framework can be useful for sandboxing, preserving and distributing applications.
-We report on the completeness, performance,
-and efficiency of the framework, and suggest possible standardization approaches.
+However, none of these tools preserve the sandboxed application for re-distribution to a larger scientific community—aspects that are equally crucial for ensuring reproducibility as sandboxing itself.
+In this paper, we describe a framework of combined sandboxing and preservation, which is not only efficient and invariant, but also practical for large-scale reproducibility.
+We present case studies of complex high-energy physics applications and show how the framework can be useful for sandboxing, preserving, and distributing applications.
+We report on the completeness, performance, and efficiency of the framework, and suggest possible standardization approaches.
+
 \end{abstract}
 
+\vspace{-10pt}
 \input {intro}
+\vspace{-10pt}
 \input {tauroast}
+\vspace{-10pt}
 \input {observation}
+\vspace{-10pt}
 \input {evolution}
+\vspace{-10pt}
 \input {measure}
+\vspace{-10pt}
 \input {evaluation}
+\vspace{-10pt}
 \input {related_work}
+\vspace{-10pt}
 \section{Conclusions and Future work}
@@
 We use two complex high energy physics applications to illustrate how the framework can help the original authors preserve and distribute the applications, and others reproduce the applications.
-
 This paper focuses on how to measure the mess and track the used dependencies to preserve an application.
@@
 
-For more details about how to preserve, distribute and repeat an application:
-
-\url{http://ccl.cse.nd.edu/research/data/hep-case-study/case\_study\_redhat6\_5.html}
+\small
+\vspace{-10pt}
+DOI for the experiment involved in the paper: \url{doi:10.7274/R0C24TCG}
 
@@
 
+\vspace{-10pt}
 \bibliographystyle{plain}

### 2015-03-30 observation.tex
Proof-reading

@@
 
-The \emph{TauRoast} and \emph{Athena} application specification was provided to us in the form of an
-email which described, in prose, how to obtain the source,
+The application specifications of \emph{TauRoast} and \emph{Athena} were provided to us in the form of an
+email that described in prose how to obtain the source,
 build the program, and run it correctly on one specific
-machine at our home institution, with no particular guarantee that
+machine at our home institution, but with no particular guarantee that
 it will run anywhere else in the world. This minimal level of documentation about software is routine in the scientific world. 
-We provide the challenges we faced in capturing the application details in a reproducible form and then preserving it for subsequent reuse:
+Below we describe the challenges faced when capturing the application details in a reproducible form and then preserving them for subsequent reuse:
 
@@
 \item {\bf Identifying all dependencies.}  Due to the distributed nature of HEP applications, these applications depend on a large number of external and local dependencies.
-External dependencies are often explicitly stated, such as when the application makes connections to Github resources, and CVS servers for downloading source. 
-However, when the application has distributed execution then implicit network connections are present requiring us to identify dependencies on all machines where execution takes place. 
-Implicit local dependencies arise due to mounted filesystems.
+External dependencies are often explicitly stated, such as when the application makes connections to Github resources, and to CVS servers for downloading the source. 
+When the application has distributed execution then implicit network connections may then be present, thus requiring us to identify dependencies on all machines where execution takes place. 
+Implicit local dependencies arise as a result of mounted filesystems.
 In \emph{TauRoast}, the application data and code is distributed on five networked filesystems, and in \emph{Athena} on two networked filesystems.
@@
 
-\item {\bf Configuration Complexity.} To correctly reproduce an application implies that run-time configurations and consistency checks on the available software are effectively captured and preserved.
+\item {\bf Configuration Complexity.} In order to correctly reproduce an application requires that run-time configurations and consistency checks on the available software are effectively captured and preserved.
 For CMS,  the {\tt scram} software management tool is used to locate
 the appropriate version of software,  set environment variables such as the PATH, run any
-tool-specific configuration, and do the same for all software on which it depends. A reproducible framework must capture the work of such software management tools so that they can conduct similar
+tool-specific configuration, and do the same for all software on which it depends.
+A reproducible framework must capture the work of such software management tools so that the framework can conduct similar
 checks on a new machine.
@@
 \item {\bf High Selectivity.}  
-Although the total size of the resources accessed by HEP
-programs is very large, the size of the data and software actually used are much smaller.
-Often, an entire repository or data source is named within the script, but the program
-only needs a handful of items from that source.  For example, the data is stored on an
-HDFS filesystem with 11.6TB of data, but only 18GB are actually consumed by the program. 
-Thus there is a size tradeoff of capturing dependencies mentioned in the program and dependencies actually used in the program.
-A reproducible framework must include robust rules about not including superfluous dependencies, but including unused dependencies that may potentially get used during program execution.
+Although the total size of the resources accessed by HEP programs is very large, the size of the data and software actually used are much smaller.
+The script will often name an entire repository or data source, but the program needs only a handful of items from that source.
+For example, the data may be stored on an HDFS filesystem with 11.6TB of data, but the program may consume only 18GB.
+Thus there is a size tradeoff in terms of capturing dependencies mentioned in the program and dependencies actually used in the program.
+A reproducible framework must include robust rules about not including superfluous dependencies, but including unused dependencies that may potentially see much use during program execution.
 
-\item {\bf Rapid Changes in Dependencies.}  Over the course of three months
-between collecting the initial email, analyzing the program, and writing this
-paper, the computing environment continuously changed.  The CMSSW software
-distribution released a new version, the target execution environment was upgraded
-to a new operating system, and the application switched from CVS to Git for obtaining
-the software. In Athena, the computing environment can potentially change daily, since upgrades to the software framework occur on a nightly basis.  
-While the users of this software seem be accustomed to constant change,
-any preservation technique will have to be very cautious about relying upon an
-external service, even one that may appear to be highly stable.
+\item {\bf Rapid Changes in Dependencies.}  
+Over the course of three months between collecting the initial email, analyzing the program, and writing this paper, the computing environment saw continuous change.
+The CMSSW software distribution released a new version, the target execution environment was upgraded to a new operating system, and the application switched from CVS to Git for obtaining the software.
+In Athena, the computing environment has the potential for daily change since upgrades to the software framework occur on a nightly basis.
+While the users of this software seem accustomed to constant change, any new technique for preservation that may rely on an external service (every one that may appear highly stable) will require great caution.
 
 \item {\bf Dependencies for Reproducible Execution.} Capturing the necessary and sufficient dependencies that are part of an application is sufficient for repeatability, but possibly for not reproducibility.
-Repeatability implies if a result depends on running program X, we must be able to run exactly X again. In reproducibility the goal is rarely limited to running
+Repeatability implies that if a result depends on running program X, we must be able to run exactly X again. In reproducibility the goal is rarely limited to running
 \emph{precisely} what a predecessor did. Often, the objective is to
 change a parameter or a data input in order to see how the result is affected. To that end, the preservation system must capture enough of the surrounding
-material to permit modifications to succeed. 
+material in order to permit modifications to succeed. 
 Further, a better understanding of how end users will consume preserved software will help to shape how

### 2015-03-30 tauroast.tex
Proof-reading

@@
 developed independently by two entirely separate physics communities. Consequently, their applications  
-have very different software distribution and data management frameworks, making it interesting to examine if common reproducibility frameworks and 
-tools work across the two communities. 
+have very different software distribution and data management frameworks, raising the question of whether common reproducibility frameworks and tools work across the two communities.  
+%making it interesting to examine if common reproducibility frameworks and 
+%tools work across the two communities. 
 One of the applications of the ATLAS experiment is the \emph{Athena} application, which is a general purpose processing framework including algorithms
@@
 
-Code and data in \emph{TauRoast} is available through five different networked filesystems which are mounted locally, an HDFS cluster for data, 
+Code and data in \emph{TauRoast} are available through five different networked filesystems which are mounted locally, an HDFS cluster for data, 
 some configuration files were stored on CVMFS~\cite{blomer2011cernvm}, and a variety of software tools were on an NFS, PanFS and AFS systems.
@@
 Data that is input to \emph{TauRoast} is obtained by reducing it through a pipeline, as shown in Figure \ref{fig:data-code-size}. Consequently, the real input data may 
-vary depending upon the science question being researched. Similarly the software may name many possible components but the used components are
+vary depending upon the topic of research. Similarly the software may name many possible components but the used components are
 smaller than the named ones.
 
-In \emph{Athena} data is obtained through an external Dropbox-like system called the FaxBox, but does not go through any reduction steps. Code is obtained through 
-CVMFS, which provides the analysis routines. However, depending upon the input data code and the configuration that will be invoked changes. 
-Thus in \emph{Athena} the used code and configuration are dynamic depending upon input data, where as in \emph{TauRoast} the code and data are static, 
-but the amount of data and code to include changes depending on the involved science.
+Data in \emph{Athena} is obtained through an external Dropbox-like system called the FaxBox, but does not pass through any reduction steps. Code is obtained through 
+CVMFS, which provides the analysis routines. 
+The invoked configuration will change, however, depending upon the input data code.
+Thus in Athena  the used code and configuration are dynamic depending upon input data, whereas in TauRoast the code and data are static, but the amount of data and code to include changes depending on the science involved.

### 2015-03-30 evolution.tex
Modification (according to dthain's suggestions)
proof reading

@@
 
-Given the many challenges of reproducing HEP applications, we now describe an invariant framework, which if present within large collaborations, can enable application developers to share their 
+Given the many challenges of reproducing HEP applications, we now describe an invariant framework.
+If present within large collaborations, this framework can enable application developers to share their
 application with other researchers, and for other researchers to reproduce the shared application. 
@@
 
-\item {\bf Capturing Dependencies and Configurations:} Capturing tools must record dependencies that are used by the program, including hardware, OS, kernels, static and dynamic dependencies, local and networked dependencies, source codes and data files.
-Stateful interactions with commercial software, such as proprietary databases and which cannot be captured due to licensing agreements must be persisted so that they can replayed later without the presence of the commercial software.
-In effect, a captured application should behave exactly the same way as the application developer intended it to be.
+\item {\bf Capturing Dependencies and Configurations:} 
+Capturing tools must record dependencies that are used by the program, including hardware, OS, kernels, static and dynamic dependencies, local and networked dependencies, source codes and data files.
+Stateful interactions with commercial software, such as proprietary databases and which cannot be captured due to licensing agreements must persist such that replaying later may be accomplished without the presence of the commercial software.
+In effect, a captured application should behave in exactly the way the application developer intended.
 % In audit phase, PTU captures the execution of the application into a package.
@@
 
-\item{\bf Preservation of Captured Entities:} By preservation we imply appropriate mechanisms for (a) documentation of the application development, and (b) automation of any task that becomes inevitably
-necessary for repeating the application in exactly the same way as the developer executed it.
+\item{\bf Preservation of Captured Entities:} By preservation we define appropriate mechanisms for (a) documentation of the application development, and (b) automation of any task that becomes necessary to the repetition of the application in exactly the the way the application developer intended.
 
-Documentation and specification during application development can be an onerous one. The preservation framework must make programming tools available that 
-focus less on documentation, but script, integrate and execute the dependencies so that they are resolved as part of documentation. 
-Automation can extend to various tasks that are necessary for ensuring repeatability such as building software, provisioning of hardware, 
-validation of software against security fixes, new features, and even monitoring the reproducibility state of a preserved application, i.e., its source code, dependencies, environment, and platform.
-Automated builds and provisioning and continuous integration service can significantly lower the barrier to run the application in a new environment.
+Documentation and specification during application development can be onerous.
+The preservation framework must make programming tools available that focus less on documentation, and more on scripts, integration, and execution of the dependencies such that they are resolved as part of documentation.
+Automation can extend to various tasks necessary for ensuring repeatability such as building software, provisioning of hardware, validation of software against security fixes, new features, and even monitoring the reproducibility state of a preserved application, i.e., its source code, dependencies, environment, and platform.
+Automated builds and provisioning and continuous integration service can significantly lower the barriers to running applications in a new environment.
 
-In spite of the preservation mechanisms, the application software may not run as intended. For a reproducer's understanding, it may also be useful to include 
-a \emph{logical preservation unit} (PLU) that consists of a minimal execution of the software using a small, test data sample, and with specified outputs.
-The provenance of this PLU must be captured so that the reproducer can make comparison with future reproduction-validation runs.
+Despite preservation mechanisms, the application software may not run as intended.
+For a reproducer’s understanding, it may also be useful to include a \emph{logical preservation unit} (PLU) that consists of a minimal execution of the software using a small, test data sample and with specified outputs.
+The provenance of this PLU must be captured so that the reproducer can compare the current run with future reproduction-validation runs.
 
@@
 \end{itemize}
-
-%\section{Evolving the Artifact}
-%
-%\begin{figure*}[t]
-%\centering
-%\includegraphics[width=.8\textwidth]{version-evolution.eps}
-%\caption{Version Evolution}
-%\label{fig:version-evolution}
-%\end{figure*}
-%
-%It is clear that the artifact, as provided, is not in a suitable form
-%for preservation.  While it might be technically possible to automatically
-%capture the entire virtual machine and all of the connected filesystems,
-%it would require 166.8TB of storage, which would be prohibitively expensive
-%for capturing this one application alone.  Further, if multiple
-%similar applications are preserved, we would miss the opportunity to identify
-%common dependencies and store them once for multiple artifacts.
-%A more structured approach to dependency management is needed.
-%
-%Figure~\ref{fig:version-evolution} shows how we have evolved this artifact
-%through several stages which make it more suitable for preservation.
-%In each step of evolution, we make the dependencies of the artifact
-%more explicit and available for analysis and automated processing.
-%As noted in the previous section, the original author provided us with
-%prose instructions by email which we translated into an
-%executable script.  The executable script has embedded in it
-%a number of external identifiers such as URLs pointing to repositories
-%and paths to networked filesystems.  As a general programming practice,
-%embedding such constants into the middle of a program is unwise, and so
-%we extract all of those identifiers and place them \emph{outside} the
-%script in a \emph{dependency map} or just \emph{map} for short.
-%The dependency map lists all of the external dependencies of the application, indicating
-%the type, how they are accessed, and where they are currently located.
-%The resulting script then simply refers to abstract file locations such
-%as \verb$GIT$ and \verb$CVMFS$, while the map file indicates where they
-%are currently located. If properly constructed, the script should not refer to any external
-%resource unless it is indicated in the dependency map.  We call this idealized
-%artifact an \emph{abstract script}.
-%
-%By extracting the dependencies into the dependency map,
-%we introduce great freedom for the curator to move, transform, and otherwise
-%manipulate the dependencies of the artifact without damaging the artifact itself.
-%A Figure~\ref{fig:version-evolution} shows, it is straightforward for an
-%automated tool to examine
-%all of the dependencies in the map, download those that are missing,
-%and then modify the map to point to the local copies of the dependencies.
-%If we group the script, dependency map, and dependencies into a \emph{package},
-%we now have a self-contained artifact that can be moved from place to place.
-%In some cases, it may be safe to allow the dependency map to refer to 
-%trusted remote repositories.  Whether this is advisable is a judgment that
-%must be made by the user or the curator, taking into account the long-term
-%stability of said repositories.
-%
-%However, only having the package and the dependency map is not enough. The successful execution of the application on the original machine also relies on the configuration of environment variables.
-%We collected the environment variables of the original machine and transformed it into one executable script.
-If another researcher wants to repeat the application, this executable script will be first executed.
-%The environment variables refer to the dynamic named values defined in the range of one computer, like \verb!$PATH! and \verb!$PYTHONPATH!.
-%However, the dependency map refers to the actual storage location of path variables used in one abstract script. For example, the actual storage location of the path variable \verb!CVMFS! 
-%is {\tt /data/cvmfs/grid.cern.ch}.
-%
-%\begin{figure}
-%\centering
-%\includegraphics[width=.5\textwidth]{solution3.eps}
-%\caption{Relationship of Roles}
-%\label{fig:solution3}
-%\end{figure}
-%
-%The relationship of different roles involved in the application preservation and
-%reproduction is shown in Figure~\ref{fig:solution3}.  The original author uses the packaging utility to generate the package for one application.
-%Then the package, together with
-%its map file and description file will be published. When
-%another researcher wants to repeat the application, one copy of the package will be downloaded into the new machine and the application can be repeated.
-%
-%When we try to repeat one application on one new machine, one map file is necessary for the relocation of the data access targets, as
-%show in Figure~\ref{fig:version-evolution}. 
-%The map file clearly defines the real location of each dependency in the format of dependency variables - the real location of dependency variable {\tt GIT} is \path{/data/git/cms-ttH} and the real location of dependency variable {\tt CVMFS}
-%is {\tt /data/cvmfs/grid.cern.ch}.
-%The script only refers to the dependency variables defined in the map file.
-%This design decouples the application script and the actual data access targets, which minimizes the impact of the evolution of different data dependencies
-%and ensures the transparent access.
-%The modification of the package only introduces the minimal changes of the map file on the client side.
-%
-%This basic approach to dependency management is a step in the right direction
-%for dependencies that are \emph{explicit} and \emph{external} to the
-%user's native execution environment.  However, it leaves two other problems unsolved.
-%
-%First, the basic approach requires that someone be \emph{aware} of the dependencies,
-%whether it be the end user, the system administrator, or the archive curator.
-%It seems reasonable to expect the user to be aware of a large dependency mentioned in a top-level script.
-%But, oftentimes the dependency is embedded invisibly deep within the software stack,
-%or is connected to the machine by the local system administrators.  No single party
-%is likely to have complete information about all of the dependencies.
-%Second, the basic approach assumes that the entire dependency is actually
-%consumed by the artifact.  As we have suggested above (and will show below),
-%this sort of program often only consumes a small fraction of what it does declare
-%as a dependency.
-%
-%To address both of these problems, users and curators alike need tools that
-%will automatically observe the dependencies of complex applications, to
-%facilitate automatic and efficient preservation.
-%

### 2015-03-30 measure.tex
proof reading

@@
 also able to modify the filesystem namespace in arbitrary ways according to user
-needs.  Parrot is particularly used in the high energy physics community
+needs.  Parrot is particularly used in the high-energy physics community
 to provide remote access to application software via CVMFS.
@@
 PTU also records \emph{provenance} in the form of a graph that describes how each file is created or consumed by processes within the application.
-Because PTU is focused solely on the problem of preservation, it can achieve lower overhead than Parrot when remote data access is not a requirement, as we show below.
+Because PTU is focused solely on the problem of preservation, therefore it can achieve lower overhead than Parrot when remote data access is not a requirement, as we show below.
 
@@
 
-There are many possible heuristics for creating the preserved package
+Many possible heuristics exist for creating the preserved package
 from the dependency list.  We have implemented three:
@@
 In a {\bf deep copy}, every file in every directory mentioned by the application is copied recursively.
-Obviously, the more aggressive the preservation, the larger the package, but the greater possibility that it can be adapted to other uses.
+Obviously, the more aggressive the preservation, the larger the package, but also the greater the possibility that the package can be adapted to other uses.
 Other approaches to package generation might including generating the union
-of multiple dependency sets, or allowing the expert user to manually add
+of multiple dependency sets, or allowing an expert user to manually add
 and remove dependencies.
@@
 Once generated, application packages must be collected, curated, and made
-available through publically shared repositories.  There currently exist a
-wide variety of services and efforts to share binary objects in this way,
+available through publically shared repositories.  Currently, a 
+wide variety of services and efforts exist in order to share binary objects in this way,
 and so we assume such multiple services will be available in the future.
@@
 requires artifacts that are independent of any particular technology,
-so the package must be sufficiently self-describing
+so the package must be sufficiently self-describing in order
 to work with multiple technologies.  The packages produced by both Parrot and PTU
@@
 \vspace{5pt}
-\noindent{\bf Linux Containers and Docker Images:} Linux Containers provide multiple isolated execution instances on top of the same kernel through OS-level virtualization.
+\noindent{\bf Linux Containers and Docker Images:} 
+Linux Containers provide multiple isolated instances of execution on top of the same kernel through OS-level virtualization.
 Thus they can be used to persist the captured packages into images.
-Using such containers, Docker now allows to preserve the image in a more user-friendly way. 
+Using such containers, Docker now allows for the preservation of the image in a more user-friendly way.
 Docker also provides portable deployment of containers across platforms, documentation of packages in a scriptable format, and versioning of container images.
-The image can be preserved along with dockerfiles, which are text files that contain all the commands to build a Docker image: the computational part is similar to shell scripts and can help provision similar to other provisioning tools (e.g.
-Chef, Puppet) and the text part is for human consumption and more suited for use with a version management system such as subversion or git, which can track any changes made to the Dockerfile.
+The image can be preserved along with dockerfiles, which are text files that contain all the commands to build a Docker image.
+Similar to shell scripts, the computational section can help other provisioning tools (e.g.
+Chef, Puppet).
+The text section, written for for human consumption, is more suited for use with a version management system such as subversion or git, which can track any changes made to the Dockerfile.
 Thus dockerfiles can be used to preserve the namelist of Parrot packages and provenance description in PTU.
-Docker is integrated with a continuous build environment which will check and validate the version of the software being used, and use a more recent version to build application software.
+Docker is integrated with a continuous build environment that will not only check and validate the version of the software in present use, but also make use of a more recent version to build application software.
 

### 2015-03-30 main.tex
added url

@@
 DOI for the experiment involved in the paper: \url{doi:10.7274/R0C24TCG}
-
+The detailed description of Athena experiment and how it was run is described in detail at: \url{https://sites.google.com/site/invariantcompatlas/} 
 \section*{Acknowledgments}

### 2015-03-31 observation.tex
Stylistic
first paragraph

@@
 email that described in prose how to obtain the source,
-build the program, and run it correctly on one specific
-machine at our home institution, but with no particular guarantee that
-it will run anywhere else in the world. This minimal level of documentation about software is routine in the scientific world. 
-Below we describe the challenges faced when capturing the application details in a reproducible form and then preserving them for subsequent reuse:
+build the program, and run it correctly on a specific
+machine at our home institution.  There was no explicit guarantee that
+it would run on other platforms. This minimal level of documentation about software is routine in the scientific world. 
+Below we describe the challenges faced when capturing application details in reproducible form and then preserving them for subsequent reuse.
 

### 2015-03-31 observation.tex
More stylistic
wording changes - finished with this file.

@@
 
-The application specifications of \emph{TauRoast} and \emph{Athena} were provided to us in the form of an
-email that described in prose how to obtain the source,
-build the program, and run it correctly on a specific
-machine at our home institution.  There was no explicit guarantee that
-it would run on other platforms. This minimal level of documentation about software is routine in the scientific world. 
+The application specifications of \emph{TauRoast} and \emph{Athena} were provided to us from the CMS and ATLAS Collaborations respectively in the form of 
+email describing in prose how to obtain the source, build the program, and run it correctly on a specific platform type available at our home institutions.
+There were no explicit guarantees that it would run on alternative platforms.
+This minimal level of documentation about software is routine in the scientific world.
 Below we describe the challenges faced when capturing application details in reproducible form and then preserving them for subsequent reuse.
@@
 \item {\bf Identifying all dependencies.}  Due to the distributed nature of HEP applications, these applications depend on a large number of external and local dependencies.
-External dependencies are often explicitly stated, such as when the application makes connections to Github resources, and to CVS servers for downloading the source. 
-When the application has distributed execution then implicit network connections may then be present, thus requiring us to identify dependencies on all machines where execution takes place. 
-Implicit local dependencies arise as a result of mounted filesystems.
+External dependencies are often explicitly stated, such as when the application makes connections to Github resources or CVS servers for downloading source files. 
+When the application has initiated execution then implicit network connections may be present that require identification of dependencies on all machines where execution takes place. 
+Implicit local dependencies can arise as a result of mounted filesystems.
 In \emph{TauRoast}, the application data and code is distributed on five networked filesystems, and in \emph{Athena} on two networked filesystems.
@@
 the appropriate version of software,  set environment variables such as the PATH, run any
-tool-specific configuration, and do the same for all software on which it depends.
-A reproducible framework must capture the work of such software management tools so that the framework can conduct similar
-checks on a new machine.
+tool-specific configurations, and do the same for all software on which it depends.
+A reproducible framework must capture the work of such software management tools so that the framework can conduct similar checks on a new machine.
 
 \item {\bf High Selectivity.}  
-Although the total size of the resources accessed by HEP programs is very large, the size of the data and software actually used are much smaller.
+Although the total size of the resources accessed by HEP programs is very large, the size of the data and software actually used are typically much smaller.
 The script will often name an entire repository or data source, but the program needs only a handful of items from that source.
@@
 \item {\bf Rapid Changes in Dependencies.}  
-Over the course of three months between collecting the initial email, analyzing the program, and writing this paper, the computing environment saw continuous change.
+Over the course of three months between collecting the initial email, analyzing the programs, and writing this paper, the computing environment saw continuous change.
 The CMSSW software distribution released a new version, the target execution environment was upgraded to a new operating system, and the application switched from CVS to Git for obtaining the software.
-In Athena, the computing environment has the potential for daily change since upgrades to the software framework occur on a nightly basis.
-While the users of this software seem accustomed to constant change, any new technique for preservation that may rely on an external service (every one that may appear highly stable) will require great caution.
+For Athena, the computing environment has the potential for daily change since upgrades to the software framework occur on a nightly basis.
+While the users of this software seem accustomed to constant change, which is appropriate during algorithm development, any new technique for preservation that may rely on an external service (every one that may appear highly stable) will require caution to choose the actual releases used during the time of publication.
 

### 2015-03-31 intro.tex
fixed a citation
stylist

@@
 Historically, text and proofs in a publication have achieved this end.
-As computation pervades the sciences and transforms the scientific method, mere text is no longer sufficient. 
-In particular, apart from textual descriptions describing the result, a reproducible result must also include several computational artifacts, such as software, data,  environment variables, and the state of computation that are involved in the adopted scientific method \cite{Sole}.
+As computation pervades the sciences and transforms the scientific method, simple text and static images are no longer sufficient. 
+In particular, apart from textual (and numeric) descriptions describing the result, a reproducible result must also include several computational artifacts, such as software, data, environment variables, platform dependencies and the state of computation that are involved in the adopted scientific method \cite{Sole}.
 
-Virtualization has emerged as a promising way to reproduce computational scientific results.
-One such approach is to conduct the entire computation relating to a scientific result within a virtual machine image, and then share the resulting image.
-This way VMIs become an authoritative, encapsulated, and executable record of computations, especially computations whose results are destined for publication and/or re-use; images, like files, can then be shared \cite{Lampoudi}.
-The resulting image, however, may be too big to share or distribute widely.
+Virtualization has emerged as a promising technology to reproduce computational scientific results.
+One such approach is to conduct the entire computation relating to a scientific result within a virtual machine image, and then preserve and share the resulting image.
+This way "VMI"s become an authoritative, encapsulated, and executable record of the computation, especially computations whose results are destined for publication and/or re-use.
+Virtual machine images, like files, can then be shared \cite{Lampoudi}.
+The resulting image, however, may be too large to share or distribute widely.
 An alternative light-weight form of virtualization is to encapsulate only the application software along with all its necessary dependencies into a self-contained package.
-The encapsulation is achieved by OS-level sandboxing techniques that interpose application system calls and copy the necessary dependencies (data, libraries, code, etc.) into a package, making it lighter weight than a VMI~\cite{guo2011cde}.
+The encapsulation is achieved by operating system-level sandboxing techniques that interpose application system calls and copy the necessary dependencies (data, libraries, code, etc.) into a package, making it lighter weight than a VMI~\cite{guo2011cde}.
 Yet, the package is not longer an executable record of the computation and still requires an accompanying operating system for execution.
@@
 Preserving the encapsulated computations in such a way that they are always reproducible will improve upon the guarantees.
-A preservation mechanism can increase the ease of image or package installation, alter dependencies implicit to computation as software components evolve or become deprecated, and provide mechanisms for documentation that make computations easy to understand.
+A preservation mechanism can increase the ease of image or package installation, alter dependencies implicit to computation as software components evolve or become deprecated, and provide mechanisms for documentation that make computations easy to understand after the fact.
 
@@
 %A package created by those light-weight approaches encapsulates all the necessary dependencies of an application, and can be used to repeat the application through different sandbox mechanisms, including Parrot
-~\cite{thain2005parrot}, CDE~\cite{Guo}, PTU~\cite{PTU}, chroot, and Docker~\cite{boettiger2015introduction}.
+~\cite{thain2005parrot}, CDE~\cite{guo2011cde}, PTU~\cite{PTU}, chroot, and Docker~\cite{boettiger2015introduction}.
 

### 2015-03-31 observation.tex
some small changes to observation.tex
stylistic again

@@
 
-\item {\bf Identifying all dependencies.}  Due to the distributed nature of HEP applications, these applications depend on a large number of external and local dependencies.
+\item {\bf Identifying all dependencies.}  Due to the distributed, collaborative nature of HEP software development, these applications depend on a large number of external and local software components.
 External dependencies are often explicitly stated, such as when the application makes connections to Github resources or CVS servers for downloading source files. 

### 2015-03-31 measure.tex
more stylistic
are we missing proper references for CDE and Docker?

@@
 
-{\bf Capturing Dependencies.}  The Unix {\tt ptrace} mechanism
+{\bf Capturing Dependencies.}  
+The Unix {\tt ptrace} mechanism
 allows a tracing process to observe all of the system calls performed by
@@
 dependency information at the granularity of files and directories. 
-Dependency may refer to source code, if available, or a binary.
+Dependency may refer to source code, if available, or a binary file.
 
 Parrot is a virtual filesystem access tool which
-is used to attach applications to a variety of remote I/O systems such as HTTP, FTP, and CVMFS. It works by trapping system calls through the {\tt ptrace} interface,
-replacing selected operations with remote accesses.  As a side-effect, Parrot is
+is used to attach applications to a variety of remote I/O systems such as HTTP, FTP, and CernVM-FS.
+It works by trapping system calls through the {\tt ptrace} interface and replacing selected operations with remote accesses.
+As a side-effect, Parrot is
 also able to modify the filesystem namespace in arbitrary ways according to user
 needs. Parrot is particularly used in the high-energy physics community
-to provide remote access to application software via CVMFS.
+to provide remote access to application software via CernVM-FS.
 To capture dependencies, we made small modifications to Parrot to record
@@
 
-PTU~\cite{pham2014framework} is designed to create a package of an application by recording all of the binaries, libraries, scripts, data files, and environment variables used by a program.
-PTU uses the CDE technology to observe system calls, but takes a snapshot of every file at the point of access.
-In addition to files, PTU records \emph{metadata} about the execution environment, such as kernel versions, application versions, and dynamic library versions by using standard Unix commands.
+The second tool, PTU~\cite{pham2014framework}, is designed to create a package of an application by recording all of the binaries, libraries, scripts, data files, and environment variables used by a program.
+PTU uses the lightweight virtualization software tool Code Data Environment (CDE) to observe system calls, but takes a snapshot of every file at the point of access.
+In addition to files, PTU records \emph{metadata} about the execution environment, such as Linux kernel version, application version, and dynamic library versions by using standard Unix commands.
 PTU also records \emph{provenance} in the form of a graph that describes how each file is created or consumed by processes within the application.
-Because PTU is focused solely on the problem of preservation, therefore it can achieve lower overhead than Parrot when remote data access is not a requirement, as we show below.
+Because PTU is focused solely on the problem of preservation, it can achieve lower overhead than Parrot when remote data access is not a requirement, as we show below.
 
@@
 Where a directory was listed, a directory is created and populated with empty files as placeholders to facilitate a directory listing.
-In a {\bf medium copy},every file in every directory mentioned by the application is preserved one level deep.
+In a {\bf medium copy}, every file in every directory mentioned by the application is preserved one level deep.
 In a {\bf deep copy}, every file in every directory mentioned by the application is copied recursively.
@@
 
-{\bf Distribution and Deployment.}
-Once generated, application packages must be collected, curated, and made
-available through publically shared repositories.  Currently, a 
+{\bf Distribution and Deployment.} Once generated, application packages must be collected, curated, and made
+available through publicly shared repositories.  Currently, a 
 wide variety of services and efforts exist in order to share binary objects in this way,
@@
 \vspace{5pt}
-\noindent{\bf Linux Containers and Docker Images:} 
+\noindent{\bf Linux Containers and Docker Images.} 
 Linux Containers provide multiple isolated instances of execution on top of the same kernel through OS-level virtualization.
@@
 Docker also provides portable deployment of containers across platforms, documentation of packages in a scriptable format, and versioning of container images.
-The image can be preserved along with dockerfiles, which are text files that contain all the commands to build a Docker image.
+The image can be preserved along with \em{dockerfiles}, which are text files containing all the commands to build a Docker image.
 Similar to shell scripts, the computational section can help other provisioning tools (e.g.
 Chef, Puppet).
-The text section, written for for human consumption, is more suited for use with a version management system such as subversion or git, which can track any changes made to the Dockerfile.
+The text section, written for human consumption, is more suited for use with a version management system such as subversion or git, which can track any changes made to the dockerfile.
 Thus dockerfiles can be used to preserve the namelist of Parrot packages and provenance description in PTU.

### 2015-03-31 evaluation.tex
few minor details for athena

@@
 
-We evaluated the correctness and performance of running, packaging, and re-running the Athena and TauRoast application using Parrot and PTU.
-To do this, the application was first executed directly, its execution time and output were recorded.
+We evaluated the correctness and performance of running, packaging, and re-running the Athena and TauRoast applications using the Parrot and PTU tools.
+To do this, each application was first executed directly and its execution time and output were recorded.
 Then the application was executed under Parrot and PTU, and a self-contained package was created for each case.
@@
 
-The TauRoast application checks and evaluates a dataset with the size of 18 GB stored in HDFS, and can be finished in about 20 minutes when running directly on a server with 64 cores and 126 GB memory.
-The output of the application includes an event analysis log and a statistics information, and its size is 289 KB.
-The Athena application processes a given input data file to produce four derived data files.
-It uses the nightly release of the Athena framework and
-submits an analysis job to obtain derived data.
+The TauRoast application checks and evaluates a dataset with the size of 18 GB stored in an HDFS file system, and can be finished in about 20 minutes when running directly on a server with 64 cores and 126 GB memory.
+The output of the application includes an event analysis log and a statistical information, and its size is approximately 289 KB.
+The Athena application processes a given input data file to produce four "derived" data files whereby event selection corresponding to interest physics channels are made.
+It uses the nightly release of the Athena framework and submits an analysis ("event skimming") job to obtain derived data, a common use case in high energy physics data analysis.
 
@@
 The re-execution time is half or less than half of the original execution time in both cases of the \emph{TauRoast} application.
-During the original execution, the input dataset is either locally available or comes from HDFS, which is accessed through FUSE.
+During the original execution, the input dataset is either locally available or comes from HDFS, which is accessed through FUSE kernel modules.
 During the package creation procedure, all the input dataset has been copied from HDFS into the package on the local filesystem.
-So, the re-execution procedure can get its input from the local filesystem instead of obtaining the input dataset from HDFS.
+Thus the re-execution procedure can obtain its input from the local filesystem instead of reading the input dataset from HDFS.
 
 Both packages created by Parrot and PTU are a subset of the root filesystem, which only includes all the accessed files.
-The original relationship, such as symbolic links, between files and directories is maintained.
+The original relationship, such as symbolic links between files and directories is maintained.
 The files from pseudo filesystems such as proc and dev, are ignored.
@@
 Except for the accessed files, both Parrot and PTU preserve the execution environment of the application. 
-the PTU package also includes a leveldb-format provenance information of the application with the size of 3 MB.
+The PTU package also includes a leveldb-format provenance information of the application with the size of 3 MB.
 
@@
 The total size is too large to be put into a separate image. However, the actually used size is greatly reduced to be 18 GB.
-Within the package, the input dataset nearly occupies the whole package. All the other libraries and software dependencies only occupies about 200 MB.
+Within the package, the input dataset nearly occupies the whole package. All the other libraries and software dependencies only occupies about 200~MB.
 As the input dataset grows, it can be put outside the package to reduce the shipping time of the package.
 
-In Athena, the input file is 224MB and output files are 16MB. PTU builds a 855MB package, while Parrot builds an 825MB package. The overhead is of provenance which is 7MB and 
-some differences is dependency information.
+For the Athena application example, the input file was 224~MB and output files were 16~MB each.
+PTU builds a 855~MB package, while Parrot builds an 825~MB package.
+The overhead is of provenance which is 7~MB and some differences is dependency information.

### 2015-03-31 main.tex
formatting changes
Minor changes

--- 2015-03-30 main.tex
@@
 We use two complex high energy physics applications to illustrate how the framework can help the original authors preserve and distribute the applications, and others reproduce the applications.
+
 This paper focuses on how to measure the mess and track the used dependencies to preserve an application.
@@
 
-\small
-\vspace{-10pt}
-DOI for the experiment involved in the paper: \url{doi:10.7274/R0C24TCG}
+The DOI name for the experiment involved in the paper is \url{doi:10.7274/R0C24TCG}, and current information may be found on the web through \url{http://doi.org/doi:10.7274/R0C24TCG}.
+
+The Athena experiment is further preserved at:
+
+\indent \indent \indent \indent \indent \url{https://sites.google.com/site/invariantcompatlas/}
 

### 2015-03-31 evaluation.tex
Submit version

@@
     \centering
-    \begin{tabular}{lcccr}
+    \begin{tabular}{ccccr}
     \hline
-    \bf Application & \bf Packaging Tool & \bf Obtain Namelist & \bf Create Package & \bf Re-Run (Tool/Time)\\ \hline
+    \bf Application & \bf Packaging & \bf Obtain	& \bf Create & \bf Re-Execution \\
+	\bf Name		& \bf Tool		& \bf Namelist	& \bf Package& \bf (Tool / Time) \\ \hline
 	Athena & Parrot & 10 min 14 sec & 00 min 53 sec & Parrot / 09 min 14 sec  \\ \hline

### 2015-03-31 tauroast.tex
Submit version

@@
 
-Code and data in \emph{TauRoast} are available through five different networked filesystems which are mounted locally, an HDFS cluster for data, 
+Code and data in \emph{TauRoast} are available through five different networked filesystems which are mounted locally, an HDFS cluster for the CMS dataset, 
 some configuration files were stored on CVMFS~\cite{blomer2011cernvm}, and a variety of software tools were on an NFS, PanFS and AFS systems.
 In addition, code may exist in version control systems such as Git, CVS, and CMS Software Distribution (CMSSW). %~\cite{cms2006cms}.
+
 \begin{wrapfigure}{r}{0.4\textwidth}
@@
 \end{wrapfigure}
+
 Data that is input to \emph{TauRoast} is obtained by reducing it through a pipeline, as shown in Figure \ref{fig:data-code-size}. Consequently, the real input data may 
